### 2017-10-21 papers/cvpr2018/egpaper_final.tex
Add CVPR2018 template.

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[breaklinks=true,bookmarks=false]{hyperref}

\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{4321}
\begin{document}

%%%%%%%%% TITLE
\title{\LaTeX\ Author Guidelines for CVPR Proceedings}

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
   The ABSTRACT is to be in fully-justified italicized text, at the top
   of the left-hand column, below the author and affiliation
   information. Use the word ``Abstract'' as the title, in 12-point
   Times, boldface type, centered relative to the column, initially
   capitalized. The abstract is to be in 10-point, single-spaced type.
   Leave two blank lines after the Abstract, then begin the main text.
   Look at previous CVPR abstracts to get a feel for style and length.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}

Please follow the steps outlined below when submitting your manuscript to
the IEEE Computer Society Press.  This style guide now has several
important modifications (for example, you are no longer warned against the
use of sticky tape to attach your artwork to the paper), so all authors
should read this new version.

%-------------------------------------------------------------------------
\subsection{Language}

All manuscripts must be in English.

\subsection{Dual submission}

Please refer to the author guidelines on the CVPR 2018 web page for a
discussion of the policy on dual submissions.

\subsection{Paper length}
Papers, excluding the references section,
must be no longer than eight pages in length. The references section
will not be included in the page count, and there is no limit on the
length of the references section. For example, a paper of eight pages
with two pages of references would have a total length of 10 pages.
{\bf There will be no extra page charges for
  CVPR 2018.}

Overlength papers will simply not be reviewed.  This includes papers
where the margins and formatting are deemed to have been significantly
altered from those laid down by this style guide.  Note that this
\LaTeX\ guide already sets figure captions and references in a smaller font.
The reason such papers will not be reviewed is that there is no provision for
supervised revisions of manuscripts.  The reviewing process cannot determine
the suitability of the paper for presentation in eight pages if it is
reviewed in eleven.

%-------------------------------------------------------------------------
\subsection{The ruler}
The \LaTeX\ style defines a printed ruler which should be present in the
version submitted for review.  The ruler is provided in order that
reviewers may comment on particular lines in the paper without
circumlocution.  If you are preparing a document using a non-\LaTeX\
document preparation system, please arrange for an equivalent ruler to
appear on the final output pages.  The presence or absence of the ruler
should not change the appearance of any other content on the page.  The
camera ready copy should not contain a ruler. (\LaTeX\ users may uncomment
the \verb'\cvprfinalcopy' command in the document preamble.)  Reviewers:
note that the ruler measurements do not align well with lines in the paper
--- this turns out to be very difficult to do well when the paper contains
many figures and equations, and, when done, looks ugly.  Just use fractional
references (e.g.\ this line is $095.5$), although in most cases one would
expect that the approximate location will be adequate.

\subsection{Mathematics}

Please number all of your sections and displayed equations.  It is
important for readers to be able to refer to any particular equation.  Just
because you didn't refer to it in the text doesn't mean some future reader
might not need to refer to it.  It is cumbersome to have to use
circumlocutions like ``the equation second from the top of page 3 column
1''.  (Note that the ruler will not be present in the final copy, so is not
an alternative to equation numbers).  All authors will benefit from reading
Mermin's description of how to write mathematics:
\url{http://www.pamitc.org/documents/mermin.pdf}.

\subsection{Blind review}

Many authors misunderstand the concept of anonymizing for blind
review.  Blind review does not mean that one must remove
citations to one's own work---in fact it is often impossible to
review a paper unless the previous citations are known and
available.

Blind review means that you do not use the words ``my'' or ``our''
when citing previous work.  That is all.  (But see below for
techreports.)

Saying ``this builds on the work of Lucy Smith [1]'' does not say
that you are Lucy Smith; it says that you are building on her
work.  If you are Smith and Jones, do not say ``as we show in
[7]'', say ``as Smith and Jones show in [7]'' and at the end of the
paper, include reference 7 as you would any other cited work.

An example of a bad paper just asking to be rejected:
\begin{quote}
\begin{center}
    An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of our
   previous paper [1], and show it to be inferior to all
   previously known methods.  Why the previous paper was
   accepted without this analysis is beyond me.

   [1] Removed for blind review
\end{quote}

An example of an acceptable paper:

\begin{quote}
\begin{center}
     An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of the
   paper of Smith \etal [1], and show it to be inferior to
   all previously known methods.  Why the previous paper
   was accepted without this analysis is beyond me.

   [1] Smith, L and Jones, C. ``The frobnicatable foo
   filter, a fundamental contribution to human knowledge''.
   Nature 381(12), 1-213.
\end{quote}

If you are making a submission to another conference at the same time,
which covers similar or overlapping material, you may need to refer to that
submission in order to explain the differences, just as you would if you
had previously published related work.  In such cases, include the
anonymized parallel submission~\cite{Authors14} as additional material and
cite it as
\begin{quote}
[1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324,
Supplied as additional material {\tt fg324.pdf}.
\end{quote}

Finally, you may feel you need to tell the reader that more details can be
found elsewhere, and refer them to a technical report.  For conference
submissions, the paper must stand on its own, and not {\em require} the
reviewer to go to a techreport for further details.  Thus, you may say in
the body of the paper ``further details may be found
in~\cite{Authors14b}''.  Then submit the techreport as additional material.
Again, you may not assume the reviewers will read this material.

Sometimes your paper is about a problem which you tested using a tool which
is widely known to be restricted to a single institution.  For example,
let's say it's 1969, you have solved a key problem on the Apollo lander,
and you believe that the CVPR70 audience would like to hear about your
solution.  The work is a development of your celebrated 1968 paper entitled
``Zero-g frobnication: How being the only people in the world with access to
the Apollo lander source code makes us a wow at parties'', by Zeus \etal.

You can handle this paper like any other.  Don't write ``We show how to
improve our previous work [Anonymous, 1968].  This time we tested the
algorithm on a lunar lander [name of lander removed for blind review]''.
That would be silly, and would immediately identify the authors. Instead
write the following:
\begin{quotation}
\noindent
   We describe a system for zero-g frobnication.  This
   system is new because it handles the following cases:
   A, B.  Previous systems [Zeus et al. 1968] didn't
   handle case B properly.  Ours handles it by including
   a foo term in the bar integral.

   ...

   The proposed system was integrated with the Apollo
   lunar lander, and went all the way to the moon, don't
   you know.  It displayed the following behaviours
   which show how well we solved cases A and B: ...
\end{quotation}
As you can see, the above text follows standard scientific convention,
reads better than the first version, and does not explicitly name you as
the authors.  A reviewer might think it likely that the new paper was
written by Zeus \etal, but cannot make any decision based on that guess.
He or she would have to be sure that no other authors could have been
contracted to solve problem B.

FAQ: Are acknowledgements OK?  No.  Leave them for the final copy.

\begin{figure}[t]
\begin{center}
\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
\end{center}
   \caption{Example of caption.  It is set in Roman so that mathematics
   (always set in Roman: $B \sin A = A \sin B$) may be included without an
   ugly clash.}
\label{fig:long}
\label{fig:onecol}
\end{figure}

\subsection{Miscellaneous}

\noindent
Compare the following:\\
\begin{tabular}{ll}
 \verb'$conf_a$' &  $conf_a$ \\
 \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
\end{tabular}\\
See The \TeX book, p165.

The space after \eg, meaning ``for example'', should not be a
sentence-ending space. So \eg is correct, {\em e.g.} is not.  The provided
\verb'\eg' macro takes care of this.

When citing a multi-author paper, you may save space by using ``et alia'',
shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word.)
However, use it only when there are three or more authors.  Thus, the
following is correct: ``
   Frobnication has been trendy lately.
   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''

This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...''
because reference~\cite{Alpher03} has just two authors.  If you use the
\verb'\etal' macro provided, then you need not worry about double periods
when used at the end of a sentence as in Alpher \etal.

For this citation style, keep multiple citations in numerical (not
chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
\cite{Alpher02,Alpher03,Authors14}.

\begin{figure*}
\begin{center}
\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
\end{center}
   \caption{Example of a short caption, which should be centered.}
\label{fig:short}
\end{figure*}

%------------------------------------------------------------------------
\section{Formatting your paper}

All text must be in a two-column format. The total allowable width of the
text area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54
cm) high. Columns are to be $3\frac14$ inches (8.25 cm) wide, with a
$\frac{5}{16}$ inch (0.8 cm) space between them. The main title (on the
first page) should begin 1.0 inch (2.54 cm) from the top edge of the
page. The second and following pages should begin 1.0 inch (2.54 cm) from
the top edge. On all pages, the bottom margin should be 1-1/8 inches (2.86
cm) from the bottom edge of the page for $8.5 \times 11$-inch paper; for A4
paper, approximately 1-5/8 inches (4.13 cm) from the bottom edge of the
page.

%-------------------------------------------------------------------------
\subsection{Margins and page numbering}

All printed material, including text, illustrations, and charts, must be kept
within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm)
high.
Page numbers should be in footer with page numbers, centered and .75
inches from the bottom of the page and make it start at the correct page
number rather than the 4321 in the example.  To do this fine the line (around
line 23)
\begin{verbatim}
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{4321}
\end{verbatim}
where the number 4321 is your assigned starting page.

Make sure the first page is numbered by commenting out the first page being
empty on line 46
\begin{verbatim}
%\thispagestyle{empty}
\end{verbatim}

%-------------------------------------------------------------------------
\subsection{Type-style and fonts}

Wherever Times is specified, Times Roman may also be used. If neither is
available on your word processor, please use the font closest in
appearance to Times to which you have access.

MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge of
the first page. The title should be in Times 14-point, boldface type.
Capitalize the first letter of nouns, pronouns, verbs, adjectives, and
adverbs; do not capitalize articles, coordinate conjunctions, or
prepositions (unless the title begins with such a word). Leave two blank
lines after the title.

AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
and printed in Times 12-point, non-boldface type. This information is to
be followed by two blank lines.

The ABSTRACT and MAIN TEXT are to be in a two-column format.

MAIN TEXT. Type main text in 10-point Times, single-spaced. Do NOT use
double-spacing. All paragraphs should be indented 1 pica (approx. 1/6
inch or 0.422 cm). Make sure your text is fully justified---that is,
flush left and flush right. Please do not place any additional blank
lines between paragraphs.

Figure and table captions should be 9-point Roman type as in
Figures~\ref{fig:onecol} and~\ref{fig:short}.  Short captions should be centred.

\noindent Callouts should be 9-point Helvetica, non-boldface type.
Initially capitalize only the first word of section titles and first-,
second-, and third-order headings.

FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction})
should be Times 12-point boldface, initially capitalized, flush left,
with one blank line before, and one blank line after.

SECOND-ORDER HEADINGS. (For example, { \bf 1.1. Database elements})
should be Times 11-point boldface, initially capitalized, flush left,
with one blank line before, and one after. If you require a third-order
heading (we discourage it), use 10-point Times, boldface, initially
capitalized, flush left, preceded by one blank line, followed by a period
and your text on the same line.

%-------------------------------------------------------------------------
\subsection{Footnotes}

Please use footnotes\footnote {This is what a footnote looks like.  It
often distracts the reader from the main flow of the argument.} sparingly.
Indeed, try to avoid footnotes altogether and include necessary peripheral
observations in
the text (within parentheses, if you prefer, as in this sentence).  If you
wish to use a footnote, place it at the bottom of the column on the page on
which it is referenced. Use Times 8-point type, single-spaced.

%-------------------------------------------------------------------------
\subsection{References}

List and number all bibliographical references in 9-point Times,
single-spaced, at the end of your paper. When referenced in the text,
enclose the citation number in square brackets, for
example~\cite{Authors14}.  Where appropriate, include the name(s) of
editors of referenced books.

\begin{table}
\begin{center}
\begin{tabular}{|l|c|}
\hline
Method & Frobnability \\
\hline\hline
Theirs & Frumpy \\
Yours & Frobbly \\
Ours & Makes one's heart Frob\\
\hline
\end{tabular}
\end{center}
\caption{Results.   Ours is better.}
\end{table}

%-------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

All graphics should be centered.  Please ensure that any point you wish to
make is resolvable in a printed copy of the paper.  Resize fonts in figures
to match the font in the body text, and choose line widths which render
effectively in print.  Many readers (and reviewers), even of an electronic
copy, will choose to print your paper in order to read it.  You cannot
insist that they do otherwise, and therefore must not assume that they can
zoom in to see tiny details on a graphic.

When placing figures in \LaTeX, it's almost always best to use
\verb+\includegraphics+, and to specify the  figure width as a multiple of
the line width as in the example below
{\small\begin{verbatim}
   \usepackage[dvips]{graphicx} ...
   \includegraphics[width=0.8\linewidth]
                   {myfile.eps}
\end{verbatim}
}

%-------------------------------------------------------------------------
\subsection{Color}

Please refer to the author guidelines on the CVPR 2018 web page for a discussion
of the use of color in your document.

%------------------------------------------------------------------------
\section{Final copy}

You must include your signed IEEE copyright release form when you submit
your finished paper. We MUST have this form before your paper can be
published in the proceedings.

{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\end{document}

### 2017-10-21 papers/cvpr2018/0_introduction.tex
Add preliminary paper structure.

\section{Introduction}

\begin{itemize}
	\item Connectomics background
	\item Problem Statement
	\item Summary of previous work (lite)
	\item Summary of our method
	\item Summary of contributions
\end{itemize}

### 2017-10-21 papers/cvpr2018/1_related_work.tex
Add preliminary paper structure.

\section{Related Work}

\begin{itemize}
	\item Connectomics in general
	\item Connectomics Skeletonization (+general)
	\item Connectomics Segmentation
	\item Connectomics Agglomeration
	\item Connectomics Proofreading
\end{itemize}

### 2017-10-21 papers/cvpr2018/2_method.tex
Add preliminary paper structure.

\section{Method}

\subsection{Preprocessing}

\begin{itemize}
	\item Skeletonization
	\item Feature generation
\end{itemize}

\subsection{Error Detection}

\begin{itemize}
	\item CNN Architecture
	\item Classifier Inputs
\end{itemize}

\subsection{Agglomeration}

\begin{itemize}
	\item Error Correction
\end{itemize}

### 2017-10-21 papers/cvpr2018/3_evaluation.tex
Add preliminary paper structure.

\section{Evaluation}

\subsection{Datasets}

\subsection{Classifier Training}

\subsection{Experiments}

### 2017-10-21 papers/cvpr2018/5_conclusions.tex
Add preliminary paper structure.

\section{Conclusions}

\begin{itemize}
	\item Impact
	\item Future work
\end{itemize}

### 2017-10-21 papers/cvpr2018/paper.tex
Add preliminary paper structure.

--- 2017-10-21 papers/cvpr2018/egpaper_final.tex
@@
 \usepackage{amssymb}
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage{booktabs}
+\usepackage{makecell}
 
@@
 % run, let it finish, and you should be clear).
-\usepackage[breaklinks=true,bookmarks=false]{hyperref}
+\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
 
-\cvprfinalcopy % *** Uncomment this line for the final submission
+% \cvprfinalcopy % *** Uncomment this line for the final submission
 
@@
 % Pages are numbered in submission mode, and unnumbered in camera-ready
-%\ifcvprfinal\pagestyle{empty}\fi
-\setcounter{page}{4321}
+\ifcvprfinal\pagestyle{empty}\fi
 \begin{document}
@@
 %%%%%%%%% TITLE
-\title{\LaTeX\ Author Guidelines for CVPR Proceedings}
+\title{Robust Agglomeration of Labeled Neurons using 3D Skeletonization}
 
-\author{First Author\\
-Institution1\\
-Institution1 address\\
-{\tt\small firstauthor@i1.org}
+\author{Brian Matejek\\
+Harvard University\\
+Cambridge, MA 02138, USA\\
+{\tt\small bmatejek@seas.harvard.edu}
 % For a paper whose authors are all at the same institution,
@@
 % To save space, use either the email address or home page, not both
-\and
-Second Author\\
-Institution2\\
-First line of institution2 address\\
-{\tt\small secondauthor@i2.org}
+%\and
+%Second Author\\
+%Institution2\\
+%First line of institution2 address\\
+%{\tt\small secondauthor@i2.org}
 }
@@
 \begin{abstract}
-   The ABSTRACT is to be in fully-justified italicized text, at the top
-   of the left-hand column, below the author and affiliation
-   information. Use the word ``Abstract'' as the title, in 12-point
-   Times, boldface type, centered relative to the column, initially
-   capitalized. The abstract is to be in 10-point, single-spaced type.
-   Leave two blank lines after the Abstract, then begin the main text.
-   Look at previous CVPR abstracts to get a feel for style and length.
+THE ABSTRACT
 \end{abstract}
@@
 %%%%%%%%% BODY TEXT
-\section{Introduction}
+\input{0_introduction}
 
-Please follow the steps outlined below when submitting your manuscript to
-the IEEE Computer Society Press.  This style guide now has several
-important modifications (for example, you are no longer warned against the
-use of sticky tape to attach your artwork to the paper), so all authors
-should read this new version.
+\input{1_related_work}
 
-%-------------------------------------------------------------------------
-\subsection{Language}
+\input{2_method}
 
-All manuscripts must be in English.
+\input{3_evaluation}
 
-\subsection{Dual submission}
+\input{4_results}
 
-Please refer to the author guidelines on the CVPR 2018 web page for a
-discussion of the policy on dual submissions.
-
-\subsection{Paper length}
-Papers, excluding the references section,
-must be no longer than eight pages in length. The references section
-will not be included in the page count, and there is no limit on the
-length of the references section. For example, a paper of eight pages
-with two pages of references would have a total length of 10 pages.
-{\bf There will be no extra page charges for
-  CVPR 2018.}
-
-Overlength papers will simply not be reviewed.  This includes papers
-where the margins and formatting are deemed to have been significantly
-altered from those laid down by this style guide.  Note that this
-\LaTeX\ guide already sets figure captions and references in a smaller font.
-The reason such papers will not be reviewed is that there is no provision for
-supervised revisions of manuscripts.  The reviewing process cannot determine
-the suitability of the paper for presentation in eight pages if it is
-reviewed in eleven.
-
-%-------------------------------------------------------------------------
-\subsection{The ruler}
-The \LaTeX\ style defines a printed ruler which should be present in the
-version submitted for review.  The ruler is provided in order that
-reviewers may comment on particular lines in the paper without
-circumlocution.  If you are preparing a document using a non-\LaTeX\
-document preparation system, please arrange for an equivalent ruler to
-appear on the final output pages.  The presence or absence of the ruler
-should not change the appearance of any other content on the page.  The
-camera ready copy should not contain a ruler. (\LaTeX\ users may uncomment
-the \verb'\cvprfinalcopy' command in the document preamble.)  Reviewers:
-note that the ruler measurements do not align well with lines in the paper
---- this turns out to be very difficult to do well when the paper contains
-many figures and equations, and, when done, looks ugly.  Just use fractional
-references (e.g.\ this line is $095.5$), although in most cases one would
-expect that the approximate location will be adequate.
-
-\subsection{Mathematics}
-
-Please number all of your sections and displayed equations.  It is
-important for readers to be able to refer to any particular equation.  Just
-because you didn't refer to it in the text doesn't mean some future reader
-might not need to refer to it.  It is cumbersome to have to use
-circumlocutions like ``the equation second from the top of page 3 column
-1''.  (Note that the ruler will not be present in the final copy, so is not
-an alternative to equation numbers).  All authors will benefit from reading
-Mermin's description of how to write mathematics:
-\url{http://www.pamitc.org/documents/mermin.pdf}.
-
-\subsection{Blind review}
-
-Many authors misunderstand the concept of anonymizing for blind
-review.  Blind review does not mean that one must remove
-citations to one's own work---in fact it is often impossible to
-review a paper unless the previous citations are known and
-available.
-
-Blind review means that you do not use the words ``my'' or ``our''
-when citing previous work.  That is all.  (But see below for
-techreports.)
-
-Saying ``this builds on the work of Lucy Smith [1]'' does not say
-that you are Lucy Smith; it says that you are building on her
-work.  If you are Smith and Jones, do not say ``as we show in
-[7]'', say ``as Smith and Jones show in [7]'' and at the end of the
-paper, include reference 7 as you would any other cited work.
-
-An example of a bad paper just asking to be rejected:
-\begin{quote}
-\begin{center}
-    An analysis of the frobnicatable foo filter.
-\end{center}
-
-   In this paper we present a performance analysis of our
-   previous paper [1], and show it to be inferior to all
-   previously known methods.  Why the previous paper was
-   accepted without this analysis is beyond me.
-
-   [1] Removed for blind review
-\end{quote}
-
-An example of an acceptable paper:
-
-\begin{quote}
-\begin{center}
-     An analysis of the frobnicatable foo filter.
-\end{center}
-
-   In this paper we present a performance analysis of the
-   paper of Smith \etal [1], and show it to be inferior to
-   all previously known methods.  Why the previous paper
-   was accepted without this analysis is beyond me.
-
-   [1] Smith, L and Jones, C. ``The frobnicatable foo
-   filter, a fundamental contribution to human knowledge''.
-   Nature 381(12), 1-213.
-\end{quote}
-
-If you are making a submission to another conference at the same time,
-which covers similar or overlapping material, you may need to refer to that
-submission in order to explain the differences, just as you would if you
-had previously published related work.  In such cases, include the
-anonymized parallel submission~\cite{Authors14} as additional material and
-cite it as
-\begin{quote}
-[1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324,
-Supplied as additional material {\tt fg324.pdf}.
-\end{quote}
-
-Finally, you may feel you need to tell the reader that more details can be
-found elsewhere, and refer them to a technical report.  For conference
-submissions, the paper must stand on its own, and not {\em require} the
-reviewer to go to a techreport for further details.  Thus, you may say in
-the body of the paper ``further details may be found
-in~\cite{Authors14b}''.  Then submit the techreport as additional material.
-Again, you may not assume the reviewers will read this material.
-
-Sometimes your paper is about a problem which you tested using a tool which
-is widely known to be restricted to a single institution.  For example,
-let's say it's 1969, you have solved a key problem on the Apollo lander,
-and you believe that the CVPR70 audience would like to hear about your
-solution.  The work is a development of your celebrated 1968 paper entitled
-``Zero-g frobnication: How being the only people in the world with access to
-the Apollo lander source code makes us a wow at parties'', by Zeus \etal.
-
-You can handle this paper like any other.  Don't write ``We show how to
-improve our previous work [Anonymous, 1968].  This time we tested the
-algorithm on a lunar lander [name of lander removed for blind review]''.
-That would be silly, and would immediately identify the authors. Instead
-write the following:
-\begin{quotation}
-\noindent
-   We describe a system for zero-g frobnication.  This
-   system is new because it handles the following cases:
-   A, B.  Previous systems [Zeus et al. 1968] didn't
-   handle case B properly.  Ours handles it by including
-   a foo term in the bar integral.
-
-   ...
-
-   The proposed system was integrated with the Apollo
-   lunar lander, and went all the way to the moon, don't
-   you know.  It displayed the following behaviours
-   which show how well we solved cases A and B: ...
-\end{quotation}
-As you can see, the above text follows standard scientific convention,
-reads better than the first version, and does not explicitly name you as
-the authors.  A reviewer might think it likely that the new paper was
-written by Zeus \etal, but cannot make any decision based on that guess.
-He or she would have to be sure that no other authors could have been
-contracted to solve problem B.
-
-FAQ: Are acknowledgements OK?  No.  Leave them for the final copy.
-
-\begin{figure}[t]
-\begin{center}
-\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
-\end{center}
-   \caption{Example of caption.  It is set in Roman so that mathematics
-   (always set in Roman: $B \sin A = A \sin B$) may be included without an
-   ugly clash.}
-\label{fig:long}
-\label{fig:onecol}
-\end{figure}
-
-\subsection{Miscellaneous}
-
-\noindent
-Compare the following:\\
-\begin{tabular}{ll}
- \verb'$conf_a$' &  $conf_a$ \\
- \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
-\end{tabular}\\
-See The \TeX book, p165.
-
-The space after \eg, meaning ``for example'', should not be a
-sentence-ending space. So \eg is correct, {\em e.g.} is not.  The provided
-\verb'\eg' macro takes care of this.
-
-When citing a multi-author paper, you may save space by using ``et alia'',
-shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word.)
-However, use it only when there are three or more authors.  Thus, the
-following is correct: ``
-   Frobnication has been trendy lately.
-   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
-   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''
-
-This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...''
-because reference~\cite{Alpher03} has just two authors.  If you use the
-\verb'\etal' macro provided, then you need not worry about double periods
-when used at the end of a sentence as in Alpher \etal.
-
-For this citation style, keep multiple citations in numerical (not
-chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
-\cite{Alpher02,Alpher03,Authors14}.
-
-\begin{figure*}
-\begin{center}
-\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-\end{center}
-   \caption{Example of a short caption, which should be centered.}
-\label{fig:short}
-\end{figure*}
-
-%------------------------------------------------------------------------
-\section{Formatting your paper}
-
-All text must be in a two-column format. The total allowable width of the
-text area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54
-cm) high. Columns are to be $3\frac14$ inches (8.25 cm) wide, with a
-$\frac{5}{16}$ inch (0.8 cm) space between them. The main title (on the
-first page) should begin 1.0 inch (2.54 cm) from the top edge of the
-page. The second and following pages should begin 1.0 inch (2.54 cm) from
-the top edge. On all pages, the bottom margin should be 1-1/8 inches (2.86
-cm) from the bottom edge of the page for $8.5 \times 11$-inch paper; for A4
-paper, approximately 1-5/8 inches (4.13 cm) from the bottom edge of the
-page.
-
-%-------------------------------------------------------------------------
-\subsection{Margins and page numbering}
-
-All printed material, including text, illustrations, and charts, must be kept
-within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm)
-high.
-Page numbers should be in footer with page numbers, centered and .75
-inches from the bottom of the page and make it start at the correct page
-number rather than the 4321 in the example.  To do this fine the line (around
-line 23)
-\begin{verbatim}
-%\ifcvprfinal\pagestyle{empty}\fi
-\setcounter{page}{4321}
-\end{verbatim}
-where the number 4321 is your assigned starting page.
-
-Make sure the first page is numbered by commenting out the first page being
-empty on line 46
-\begin{verbatim}
-%\thispagestyle{empty}
-\end{verbatim}
-
-%-------------------------------------------------------------------------
-\subsection{Type-style and fonts}
-
-Wherever Times is specified, Times Roman may also be used. If neither is
-available on your word processor, please use the font closest in
-appearance to Times to which you have access.
-
-MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge of
-the first page. The title should be in Times 14-point, boldface type.
-Capitalize the first letter of nouns, pronouns, verbs, adjectives, and
-adverbs; do not capitalize articles, coordinate conjunctions, or
-prepositions (unless the title begins with such a word). Leave two blank
-lines after the title.
-
-AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
-and printed in Times 12-point, non-boldface type. This information is to
-be followed by two blank lines.
-
-The ABSTRACT and MAIN TEXT are to be in a two-column format.
-
-MAIN TEXT. Type main text in 10-point Times, single-spaced. Do NOT use
-double-spacing. All paragraphs should be indented 1 pica (approx. 1/6
-inch or 0.422 cm). Make sure your text is fully justified---that is,
-flush left and flush right. Please do not place any additional blank
-lines between paragraphs.
-
-Figure and table captions should be 9-point Roman type as in
-Figures~\ref{fig:onecol} and~\ref{fig:short}.  Short captions should be centred.
-
-\noindent Callouts should be 9-point Helvetica, non-boldface type.
-Initially capitalize only the first word of section titles and first-,
-second-, and third-order headings.
-
-FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction})
-should be Times 12-point boldface, initially capitalized, flush left,
-with one blank line before, and one blank line after.
-
-SECOND-ORDER HEADINGS. (For example, { \bf 1.1. Database elements})
-should be Times 11-point boldface, initially capitalized, flush left,
-with one blank line before, and one after. If you require a third-order
-heading (we discourage it), use 10-point Times, boldface, initially
-capitalized, flush left, preceded by one blank line, followed by a period
-and your text on the same line.
-
-%-------------------------------------------------------------------------
-\subsection{Footnotes}
-
-Please use footnotes\footnote {This is what a footnote looks like.  It
-often distracts the reader from the main flow of the argument.} sparingly.
-Indeed, try to avoid footnotes altogether and include necessary peripheral
-observations in
-the text (within parentheses, if you prefer, as in this sentence).  If you
-wish to use a footnote, place it at the bottom of the column on the page on
-which it is referenced. Use Times 8-point type, single-spaced.
-
-%-------------------------------------------------------------------------
-\subsection{References}
-
-List and number all bibliographical references in 9-point Times,
-single-spaced, at the end of your paper. When referenced in the text,
-enclose the citation number in square brackets, for
-example~\cite{Authors14}.  Where appropriate, include the name(s) of
-editors of referenced books.
-
-\begin{table}
-\begin{center}
-\begin{tabular}{|l|c|}
-\hline
-Method & Frobnability \\
-\hline\hline
-Theirs & Frumpy \\
-Yours & Frobbly \\
-Ours & Makes one's heart Frob\\
-\hline
-\end{tabular}
-\end{center}
-\caption{Results.   Ours is better.}
-\end{table}
-
-%-------------------------------------------------------------------------
-\subsection{Illustrations, graphs, and photographs}
-
-All graphics should be centered.  Please ensure that any point you wish to
-make is resolvable in a printed copy of the paper.  Resize fonts in figures
-to match the font in the body text, and choose line widths which render
-effectively in print.  Many readers (and reviewers), even of an electronic
-copy, will choose to print your paper in order to read it.  You cannot
-insist that they do otherwise, and therefore must not assume that they can
-zoom in to see tiny details on a graphic.
-
-When placing figures in \LaTeX, it's almost always best to use
-\verb+\includegraphics+, and to specify the  figure width as a multiple of
-the line width as in the example below
-{\small\begin{verbatim}
-   \usepackage[dvips]{graphicx} ...
-   \includegraphics[width=0.8\linewidth]
-                   {myfile.eps}
-\end{verbatim}
-}
-
-%-------------------------------------------------------------------------
-\subsection{Color}
-
-Please refer to the author guidelines on the CVPR 2018 web page for a discussion
-of the use of color in your document.
-
-%------------------------------------------------------------------------
-\section{Final copy}
-
-You must include your signed IEEE copyright release form when you submit
-your finished paper. We MUST have this form before your paper can be
-published in the proceedings.
+\input{5_conclusions}
 
@@
 \bibliographystyle{ieee}
-\bibliography{egbib}
-}
+\bibliography{paper}}
 

### 2017-10-27 papers/cvpr2018/2_method.tex
papers: began to add template

@@
 \section{Method}
+
+Our method works on top of existing $EM$ agglomeration algorithms such as \textit{NeuroProof} or \textit{GALA} (CITE BOTH).
+First we use a 3D U-net to generate voxel affinities predicting the probability that two voxels belong to the same neuron.
+The \textit{zwatershed} algorithms takes these affinities and generates an oversegmentation of the neurons (CITE).
+\textit{NeuroProof} agglomerates these supervoxels by training a multi-level random forest classifier.
+We use a low threshold for neuroproof to generate an oversegmentation.
+
+NEED TO ADD BETTER OVERVIEW
 
@@
 
+Our pipeline builds a level on top of current agglomeration techniques.
+Our goal is to identify and merge segments based on their overall shape.
+Figure (ADD FIGURE) shows two examples of nearby segments output by \textit{NeuroProof}.
+The right pair should merge and the left pair should not.
+
+We consider the skeletons of the segments.
+We use the teasFigure (ADD FIGURE) shows two examples of skeletons generated for two neuron segments.
+The skeletons are generated using the TEASER: Tree-structure Extraction Algorithm for Accurate and Robust Skeletons (CITE TEASER).
+The algorithm iteratively chooses locations that are the furthest distance $d$ from the boundary of the segment.
+Each locations becomes a ``joint" and a sphere of radius $d$ centered at the joint is masked out.
+The algorithm continually finds points and removes the corresponding sphere until every point with a distance greater than $d^*$ is removed.
+We use a $d^*$ of 50 voxels which was the standard parameter from the original paper (Is it?).
+
+We use the above skeletons to extract feature locations to consider merges. The algorithm is described in the pseudocode in (ADD CITE).
+
+ADD IN PSEUDOCODE
+
 \begin{itemize}
+
 	\item Skeletonization
@@
 \subsection{Error Detection}
+
+\begin{figure*}[t]
+	\centering
+	\includegraphics[width=0.8\linewidth]{figures/architecture.png}
+	\caption{The architecture for the neural networks follows the \textit{VGG} style of double convolutions followed by a max pooling operation.
+The number of filters doubles each layer leading to a fully connected layer and a sigmoid activation function.}
+	\label{fig:architecture}
+\end{figure*}
+
+NEED TO CITE VGG, LeakyReLU, BatchNormalization
+
+The above skeletonization strategies produces locations in 3D that require further consideration.
+From these locations we extract a region of $800nm \times 800nm \times 800nm$ and resample the segmentations to fit in a box of $18 \times 52 \times 52$ voxels.
+Consider a location corresponding to a potential merge between labels $l_1$ and $l_2$.
+The input to the neural network is a three binary channel cube of size $3 \times 18 \times 52 \times 52$.
+The first channel is $1$ if the voxel belongs to $l_1$.
+The second channel is 1 if the voxel belongs to $l_2$.
+The third channel is $1$ if the voxel belongs to either $l_1$ or $l_2$.
+
+We train a 3D convolutional neural network on the the generated examples.
+The network has four layers of double convolutions followed by a max pooling step.
+The filter sizes are $(3, 3, 3)$ and the max pooling is by a factor of $2$ for every level in the $x$ and $y$ dimensions.
+We downsample the $z$ dimension only in the final two layers.
+The number of channels is $16$ for the first layer and each subsequent layer has twice as many channels.
+The output of the convolutions is flattened and input into two dense layers.
+We apply batch normalization after every convolution, pooling, and dense layer except for the final layer.
+We use the \textit{LeakyReLU} activation function with $\alpha = 0.001$.
+We use the \textit{Adam} optimizer with an initial learning rate of $0.001$, $\beta_1 = 0.99$, $\beta_2 = 0.999$, and a weight decay of $5*10^{-8}$.
+The loss function is binary crossentropy.
+We use a batch size of 20.
+
+Since the datasets have a limited number of examples, we augment the examples by considering all combinations with rotations along the $xy$-plane and mirrors along the $yz$- and $xy$- planes.
+This produces 16 times more training data.
 
@@
 
+The above neural network produces probabilities that two nearby segments belong to the same neuron.
+To use the graph-based optimization algorithms we need to take the oversegmentation and construct a graph.
+We generate one node for every segment.
+The skeletonization algorithm generates edges between nodes.
+
 \begin{itemize}

### 2017-10-27 papers/cvpr2018/3_evaluation.tex
papers: began to add template

@@
 
+This is probably where I should talk about neuroproof.
+
+\subsection{Preprocessing}
+
+What percent of edges are considered.
+
+Figure (ADD FIGURE) shows a few segments that were not considered.
+
 \subsection{Classifier Training}
 
+Here I need to produce the precision and recall curves, (ROC) as well as the final results with thresholding. Also include the training/validation loss functions overtime
+
 \subsection{Experiments}

### 2017-10-27 cnns/skeleton/train.py
skeleton: sped up training by removing allocation in loop

@@ -1,4 +1,3 @@
-import time
 import numpy as np
 import os
 import sys
@@ -179,12 +178,12 @@ def SkeletonCandidateGenerator(prefix, network_distance, candidates, parameters,
     else:
         nbatches = (rotations * ncandidates / batch_size)
 
+    examples = np.zeros((batch_size, nchannels, width[IB_Z + 1], width[IB_Y + 1], width[IB_X + 1]), dtype=np.uint8)
+    labels = np.zeros(batch_size, dtype=np.uint8)
+    
     while True:
         index = 0
         for _ in range(nbatches):
-            examples = np.zeros((batch_size, nchannels, width[IB_Z + 1], width[IB_Y + 1], width[IB_X + 1]), dtype=np.uint8)
-            labels = np.zeros(batch_size, dtype=np.uint8)
-
             for iv in range(batch_size):
                 # get the candidate index and the rotation
                 rotation = index / ncandidates
@@ -197,6 +196,7 @@ def SkeletonCandidateGenerator(prefix, network_distance, candidates, parameters,
                 # provide overflow relief
                 index += 1
                 if index >= ncandidates * rotations: index = 0
+                
             yield (examples, labels)
 
 
@@ -216,8 +216,6 @@ def Train(prefix, model_prefix, threshold, maximum_distance, network_distance, w
     
     # set up the keras model
     model = SkeletonNetwork(parameters, width)
-
-
     
     # make sure the folder for the model prefix exists
     root_location = model_prefix.rfind('/')

### 2017-10-27 cnns/skeleton/train.py
cnns: updated train to be normalized between -0.5 and 0.5

@@ -178,8 +178,8 @@ def SkeletonCandidateGenerator(prefix, network_distance, candidates, parameters,
     else:
         nbatches = (rotations * ncandidates / batch_size)
 
-    examples = np.zeros((batch_size, nchannels, width[IB_Z + 1], width[IB_Y + 1], width[IB_X + 1]), dtype=np.uint8)
-    labels = np.zeros(batch_size, dtype=np.uint8)
+    examples = np.zeros((batch_size, nchannels, width[IB_Z + 1], width[IB_Y + 1], width[IB_X + 1]), dtype=np.float32)
+    labels = np.zeros(batch_size, dtype=np.float32)
     
     while True:
         index = 0

### 2017-10-27 cnns/skeleton/util.py

@@ -46,8 +46,8 @@ def ScaleSegment(segment, width, labels):
     nchannels = width[0]
 
     # create the example to be returned
-    example = np.zeros((1, nchannels, width[IB_Z + 1], width[IB_Y + 1], width[IB_X + 1]), dtype=np.uint8)
-
+    example = np.zeros((1, nchannels, width[IB_Z + 1], width[IB_Y + 1], width[IB_X + 1]), dtype=np.float32)
+    
     # iterate over the example coordinates
     for iz in range(width[IB_Z + 1]):
         for iy in range(width[IB_Y + 1]):
@@ -56,7 +56,7 @@ def ScaleSegment(segment, width, labels):
                 iw = int(float(zres) / float(width[IB_Z + 1]) * iz)
                 iv = int(float(yres) / float(width[IB_Y + 1]) * iy)
                 iu = int(float(xres) / float(width[IB_X + 1]) * ix)
-                
+
                 if nchannels == 1 and (segment[iw,iv,iu] == label_one or segment[iw,iv,iu] == label_two):
                     example[0,0,iz,iy,ix] = 1
                 else:
@@ -68,6 +68,8 @@ def ScaleSegment(segment, width, labels):
                     # add third channel 
                     if nchannels == 3 and (segment[iw,iv,iu] == label_one or segment[iw,iv,iu] == label_two):
                         example[0,2,iz,iy,ix] = 1
+
+    example = example - 0.5
 
     return example
 

### 2017-10-31 papers/cvpr2018/0_introduction.tex
paper: major updates

@@
 \section{Introduction}
+
+Connectomics, the field of large-scale nanometer reconstruction of the wiring diagram of the brain, has created datasets petabytes in size (FIX).
+These datasets are too large for manual reconstruction.
 
@@
 \end{itemize}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.42\linewidth]{./figures/intro-slice.png}
+	\hspace{0.085\linewidth}
+	\includegraphics[width=0.42\linewidth]{./figures/intro-cube.png}
+\end{figure}
+
+The lowest-level frameworks in connectomics focus on per-pixel decisions using localized information. 
+In addition, (write names) et al. use the multi-cut segmentation algorithm on the raw image data to produce segmentations.
+Recently, significant research focuses on developing per-pixel affinity and boundary membrane predictions using 3D convolutional neural networks (CITE VD2D3D, U-NET).
+Although these low-level algorithms have seen dramatic improvements in recent years, they do not fully leverage all available information.
+Therefore, researchers began constructing algorithms that build another level of abstraction above the per-pixel level that trained random forest classifiers using shape features at the superpixel level (CITE GALA, NeuroProof).
+
+Although these most recent advances produce impressive improvements on the original per-pixel algorithms, they do not fully integrate the full information provided by the datasets.
+In this paper we provide a new framework which builds a new level of abstraction on top of the existing research. 
+We construct a graphical representation from the outputs of the per-superpixel agglomeration strategies to further improve the merging results.
+We focus on the shapes of the segments to make merge and split decisions. 
+We provide three main contributions: using a skeleton representation of the 3D segments to predict merge locations, training a 3D convolutional neural network on the segment shapes to predict merging, and a new level of abstraction on the data that considers the data in a graphical form.

### 2017-10-31 papers/cvpr2018/1_related_work.tex
paper: major updates

@@
 \section{Related Work}
+Much works has gone into segmentation algorithms at the per-pixel level in connectomics and more generally computer vision.
+Early advances in connectomics worked on generating segmentations by applying multi-cut algorithms to raw pixel values.
+More recently, 3D convolutional neural networks predict voxel membrane probabilities and affinities between voxels (CITE VD2D3D, U-Net, SriniNET).
+Recently, U-Net has been very successful in a wide range of segmentation tasks in the large medical imaging community.
+When generating affinities, every voxel has three outputs corresponding to the probability that the voxel (x, y, z) belongs to the same neuron as (x + 1, y, z), (x, y + 1, z) and (x, y, z + 1).
+Most connectomics segmentation pipelines begin by predicting membrane probabilities or voxel affinities and agglomerating voxels using this information.
+Zwatershed is a common 3D agglomeration strategy that builds on the output of voxel affinities (CITE ZWATERSHED).
+However, these methods fall short of the desired accuracy and thus the pipelines often rely on random forest classifiers to merge the oversegmented supervoxels.
+GALA and NeuroProof train random forest classifiers with hand designed shape features at various RESOLUTIONS.
+Recently, (CITE Srini) has attempted to generate the segmentation with a front-to-back artificial neural network.
+These flood filling networks have shown some process are expensive to run and have not been applied to large datasets.
+There has been extensive research into the skeletonization of 3D binary volumes in computer graphics, mathematics, and biomedical visualization.
+(CITE) focus on generation of topologically consistent skeletons using linear recursive methods.
+In the graphics community, extensive research has considered the medial axis problem of 3D renderings (CITE).
+In the field of connectomics, the Tree-structure Extraction Algorithm for Accurate and Robust Skeletons (TEASER) computes skeletons for individual neurons in EM images.
 

### 2017-10-31 papers/cvpr2018/2_method.tex
paper: major updates

--- 2017-10-21 papers/cvpr2018/2_method.tex
@@
 
-\subsection{Preprocessing}
+Our method works on top of existing $EM$ agglomeration algorithms such as \textit{NeuroProof} or \textit{GALA} (CITE BOTH).
+First we use a 3D U-net to generate voxel affinities predicting the probability that two voxels belong to the same neuron.
+The \textit{zwatershed} algorithms takes these affinities and generates an oversegmentation of the neurons (CITE).
+\textit{NeuroProof} agglomerates these supervoxels by training a multi-level random forest classifier.
+We use a low threshold for neuroproof to generate an oversegmentation.
 
-\begin{itemize}
-	\item Skeletonization
-	\item Feature generation
-\end{itemize}
+In order to use graph-based optimization strategies we need to generate nodes $N$ and edges $E$ for the graph $G$.
 
-\subsection{Error Detection}
+\subsection{Graph Creation}
 
-\begin{itemize}
-	\item CNN Architecture
-	\item Classifier Inputs
-\end{itemize}
+\subsubsection{Node Generation}
+
+The simplest method of generating nodes is to create one node for every unique segment label in a volume.
+However, there are many small segments that remain after NeuroProof that only introduce noise when moving to a higher level of abstraction.
+For now, we decide to remove these segments from consideration and focus on the only the large segments that have expansive spans through the volume.
+Every segment with fewer than $20,000$ voxels is pruned from the set of considered nodes.
+Figure \ref{fig:skeletonization} shows two typical segments that each have one corresponding node in the graph $G$.
+
+\subsubsection{Edge Generation}
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=0.42\linewidth]{./figures/merge_candidate1.png}
+	\hspace{0.085\linewidth}
+	\includegraphics[width=0.42\linewidth]{./figures/merge_candidate2.png}
+	\caption{Two erroneously split segments that should merge together. Most segments that we want to merge have the same general structure.}
+	\label{fig:merge_candidates}
+\end{figure}
+
+The na\"ive edge generation approach is just to simply consider all nodes whose segmentations have a neighboring voxel.
+Current agglomeration approaches such as NeuroProof or GALA use this criteria for deciding which segments could potentially form one neuron.
+However, this produces too many edges in our graph, many of which are easily prunable.
+In fact, many of the segments that we need to merge have very similar structures.
+Consider Figure \ref{fig:merge_candidates} which shows two erroneously split segments.
+In both instances the segments around the break follow the same general shape.
+The segment is more-or-less tubular in the close vicinity with an abrupt break at the end of segment where the next segment begins.
+The following algorithm identifies these locations without introducing as much ``noise" as using the na\"ive strategy.
+
+We begin by generating skeletons for every segment.
+The intuition behind this decision is that a skeleton is a simplified representation of the overarching shape of a segment.
+Figure \ref{fig:skeletonization} shows two example segments and their corresponding skeletons in white.
+These skeletons were generated using the Tree-structure Extraction Algorithm for Accurate and Robust Skeletons (TEASER) \cite{sato2000teasar} which has been used in connectomics research previously \cite{zhao2014automatic}.
+The skeleton consists of a series of \textit{joints} with edges between neighboring joints.
+Joints that have only one neighbor are also called \textit{endpoints}.
+Joints that are within $50$ voxels of each other are pruned to reduce unnecessary branching.
+
+After skeletonization, we proceed to identify locations between segments that we should consider for merging.
+The algorithm proceeds in two passes.
+In the first pass we iterate over every endpoint, $e$, in all of the skeletons and create a set $S_e$ where the set includes every segment that has a single voxel with $t_{low}$nm from the endpoint.
+This first pass often includes too many negative merge candidates leaving a very unbalanced set of merge/split candidates (FIX THIS).
+Therefore, in our second pass we iterate over all of the endpoints and their corresponding sets.
+We find the closest endpoint for a given segment $s \in S_e$ to the endpoint $e$.
+If the closest endpoint is less than $t_{high}$nm from the original endpoint $e$, we add an edge in the graph between these two segments.
+We also store the midpoint between the closest endpoint and the original endpoint $e$, which will be useful in the following section.
+Algorithm \ref{alg:generate-edges} provides pseudocode for this edge generation algorithm.
+The results in this paper follow from $t_{low} = 240nm$ and $t_{high} = 600nm$.
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=0.42\linewidth]{./figures/skeleton1.png}
+	\hspace{0.085\linewidth}
+	\includegraphics[width=0.42\linewidth]{./figures/skeleton2.png}
+	\caption{Two example outputs of the TEASER skeletonization algorithm.}
+	\label{fig:skeletonization}
+\end{figure}
+
+\begin{algorithm}
+	\begin{algorithmic}
+		\Function{GenerateEdges}{$skeletons$}
+			\For {$skeleton$ in $skeletons$}
+				\State $candidates$ = set()
+				\For {$endpoint$ in $skeleton$}
+
+				\EndFor
+			\EndFor
+		\EndFunction
+	\end{algorithmic}
+	\caption{Edge generation function}
+	\label{alg:generate-edges}
+\end{algorithm}
+\subsection{Edge Probabilities}
+
+The previous section outlines how to generate edges between nodes in our graph structure.
+Here we will introduce a neural network architecture for generating probabilities that two nodes sharing an edge belong to the same neuron.
+The neural network takes as input only data from the input segmentation.
+
+\subsubsection{Network Architecture}
+
+\begin{figure*}[t]
+	\centering
+	\includegraphics[width=0.3\linewidth]{./figures/network_distance_400.png}
+	\includegraphics[width=0.3\linewidth]{./figures/network_distance_600.png}
+	\includegraphics[width=0.3\linewidth]{./figures/network_distance_800.png}	
+	\caption{The white outlines show three different possible cubic sizes to input into the neural network.
+The left example ($800\textrm{nm}$) provides less local context than the middle example ($1200\textrm{nm}$).
+The right example ($1600\textrm{nm}$) extracts too large of a local region that produces noise as one of the segments leaves the bounding box only to reenter.}
+	\label{fig:network-radius}
+\end{figure*}
+
+The above skeletonization algorithm produces 3D locations that require further consideration for merging.
+To determine which of these segments should actually merge, we train a 3-D convolutional neural network.
+We extract a cubic region with length $1200\textrm{nm}$ centered at these locations.
+These cubes will provide the local information for the neural network to predict which neighboring segments belong to the same neuron.
+A cubic length of $1200\textrm{nm}$ provides enough local shape context for the network without introducing an excessive amount of noise.
+Figure \ref{fig:network-radius} shows cubes of lengths $800\textrm{nm}, 1200\textrm{nm},$ and $1600\textrm{nm}$.
+
+We transform the extracted cubes for input into the neural network.
+The network takes three input channels for each voxel in the 3-D volume corresponding to the following mapping.
+Consider a pair of segments with labels $l_1$ and $l_2$ for every voxel $v$ in the cube of interest.
+The first channel is $0.5$ if $v = l_1$ and $-0.5$ otherwise, the second channel is $0.5$ if $v = l_2$ and $-0.5$ otherwise, and the third channel is $0.5$ if $v = l_1$ or $v = l_2$ and $-0.5$ otherwise.
+
+Each 3-channel volume is subsequently downsampled into an array of size $(3, 22, 68, 68)$ using nearest-neighbor interpolation.
+Our neural network trains on these 4-D arrays to generate probabilities that $l_1$ and $l_2$ should merge for every input.
+
+Our network architecture has three layers of double convolutions followed by a max pooling step \cite{chatfield2014return}.
+As described above, the input with into the network is $(22, 68, 68)$ with $3$ channels.
+The filter size of the layers are 16, 32, and 64 with size doubling deeper into the network.
+The first two max pooling layers are anisotropic with pooling only in $x$ and $y$ to match the anisotropic nature of our EM datasets.
+All convolutions have kernel sizes of $(3, 3, 3)$.
+The output size of the final max pooling layer is $(5, 5, 5)$ with $64$ channels.
+The output is flattened into a 1-D vector with $8000$ entries which enters two fully connected layers with $512$ and $1$ dimensions in the output respectively.
+All activation functions are LeakyReLU with $\alpha=0.001$ except for the final activation which uses a sigmoid function \cite{funahashi1989approximate,maas2013rectifier}.
+There is a dropout of $0.2$ after every pooling layer and the first dense layer.
+There is a dropout of $0.5$ after the final dense layer.
+The above method uses stochastic gradient descent with Nesterov's Accelerated Gradient \cite{nesterov1983method}.
+This optimizer has an initial learning rate of $0.01$, momentum of $0.9$, and a decay rate of $5*10^{-8}$.
+Figure \ref{fig:architecture} provides an overview of the proposed architecture.
+
+\begin{figure*}[t]
+	\centering
+	\includegraphics[width=0.95\linewidth]{figures/architecture.png}
+	\caption{The architecture for the neural networks follows the \textit{VGG} style of double convolutions followed by a max pooling operation.
+The number of filters doubles each layer leading to a fully connected layer and a sigmoid activation function.}
+	\label{fig:architecture}
+\end{figure*}
+
+\subsubsection{Data Augmentation}
+
+Manual labeling of connectomics datasets is time intensive and expensive (CITE?).
+As we consider higher levels of abstractions of the data, the amount of useful labeled data decreases.
+This follows from the simple fact that manual annotation of the data happens at the per-pixel level, so starting with larger agglomerated segments leads to fewer unique human labels (THIS DOESN'T MAKE SENSE YET).
+
+Therefore, we apply some data augmentation to the generated examples to increase the size of the training datasets.
+We consider all rotations of $90$ degrees along the $xy$-plane in addition to mirrors along the $x$ and $z$ axes.
+This produces an additional 16 times more training data.
 
@@
 
-\begin{itemize}
-	\item Error Correction
-\end{itemize}
+After constructing the above graph structure we can apply a graph-based segmentation strategy.
+There are many formulations of graph-based optimization strategies that provide different guarantees on their output.
+Neurons in the brain should be acyclic, i.e.
+the output shape should have a genus of zero.
+Current connectomics agglomeration techniques do not leverage this additional information but rather consider neighboring regions in successive order without regard to created loops.
+In our graph formulation we can enforce this topological property by applying a multicut partition onto the graph which generates a forest on the nodes.
+There are several heuristics that solve the multicut problem.
+For our purposes we use the Kernighan-Lin algorithm \cite{kernighan1970efficient}.

### 2017-10-31 papers/cvpr2018/3_evaluation.tex
paper: major updates

@@
 
-This is probably where I should talk about neuroproof.
+We evaluate our methods on EM datasets.
+The first dataset is the Kashtui dataset  which is a mouse brain (ADD IN STUFF) with an anisotropic resolution of $3\textrm{nm} \times 3 \textrm{nm} \times 30 \textrm{nm}$.
+The second dataset is from FlyEM and is a (ADD STUFF HERE) with an anisotropic resolution of $3 \textrm{nm} \times 3\textrm{nm} \times 30\textrm{nm}$.
 

### 2017-10-31 papers/cvpr2018/4_results.tex
paper: major updates

\section{Results}

Here we show the results for the three main contributions for this paper: merge consideration using skeleton pruning, merge probabilities output from the trained convolutional neural network, and the final output of the pipeline.

\subsection{Skeleton Pruning}

\subsubsection{Finding Merge Candidates}

\subsubsection{Finding Split Candidates}

Effective pruning for merge candidates should have high precision and recall for segments that should be merged.

\subsection{Neural Network Classification}

\subsubsection{Merge Network}

\begin{figure}
	\includegraphics[width=0.85\linewidth]{figures/skeleton-training-curve.png}
	\caption{The training and validation loss when training the neural network on the L. Cylinder data set.}
	\label{fig:training-curve}
\end{figure}

\begin{figure}
	\includegraphics[width=0.85\linewidth]{figures/roc-microns-300-test.png}
	\caption{The ROC curve for the training and validation datasets.}
	\label{fig:roc-curve}
\end{figure}

Figure \ref{fig:training-curve} shows the training and validation loss during the training of the neural network.

\begin{figure*}[t]
	\includegraphics[width=0.45\linewidth]{figures/variation_of_information-train.png}
	\hspace{0.0825\linewidth}
	\includegraphics[width=0.45\linewidth]{figures/variation_of_information-test.png}	
\end{figure*}

\subsubsection{Split Network}

\subsection{Graph-based Error Correction}

### 2017-10-31 papers/cvpr2018/paper.tex
paper: major updates

@@
 \usepackage{makecell}
+\usepackage{algpseudocode}
+\usepackage{algorithm}
 
@@
 
-\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
+\def\cvprPaperID{446} % *** Enter the CVPR Paper ID here
 \def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
@@
 \begin{abstract}
-THE ABSTRACT
+Advanced in electron microscopy (EM) image acquisitions has created massive petabyte datasets that are too large for complete manual segmentation.
+Previous automatic segmentation algorithms work by applying various techniques at the per-voxel level.
+Oftentimes an agglomeration strategy will build on the per-voxel results to create larger clusters of supervoxels.
+These results provide a good baseline but are not scalable with the size of the data.
+We propose a novel framework for building on top of these agglomeration strategies that scales with larger datasets using graph-based optimization strategies.
 \end{abstract}

### 2017-10-31 papers/cvpr2018/1_related_work.tex
paper: Major updates to related works

--- 2017-10-21 papers/cvpr2018/1_related_work.tex
@@
 
-\begin{itemize}
-	\item Connectomics in general
-	\item Connectomics Skeletonization (+general)
-	\item Connectomics Segmentation
-	\item Connectomics Agglomeration
-	\item Connectomics Proofreading
-\end{itemize}
+Significant research in connectomics has focused on extracting information from the pixel data of the raw electron microscopy (EM) images.
+Building off previous work in computer vision that used normalized cuts and other graph partitioning algoirithms on images \cite{kappes2016higher,shi2000normalized,tatiraju2008image}, some of the methods apply computationally expensive graph partitioning techniques on the per-voxel images \cite{andres2012globally}.
+Other approaches at the per-pixel level have focused on training 2-D convolutional networks to predict membrane probabilities \cite{ciresan2012deep}.
+More recent work has expanded on these early networks by adding the $z$-dimension to create 3-D networks \cite{lee2015recursive}.
+Oftentimes these networks now predict affinities between voxels rather than membrane probabilities \cite{ronneberger2015u}.
+Extensive research has focused on enhancing the loss functions and optimizers for these networks \cite{chatfield2014return,maas2013rectifier,nesterov1983method}.
+
+ADD SECTION ON CORRECTING SPLIT ERRORS
+
+These neural networks produce probabilities that neighboring voxels belong to the same neuron.
+Many algorithms build on top of these affinities by agglomerating voxels to produce reconstructed label volumes of the EM images \cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic} (CITE NEUROPROOF, ZWATERSHED).
+Despite the successes of these algorithms they often make early local mistakes leading to errors in the segmentation.
+Proofreading methods create a "human-in-the-loop" framework that allows users to find errors and correct them \cite{haehn2017scalable,haehn2017guided,haehn2014design}.
+Flood-filling networks merge these two steps by training an end-to-end network that takes as input raw image data and produces a segmentation \cite{januszewski2016flood}.
+Although these networks have produced impressed segmentation accuracies, they are currently too slow for large scale connectomics reconstructions.
+
+The fields of computer graphics, mathematics, and biomedical visualization have produced extensive research into the skeletonization of 3D binary volumes.
+A large amount of research has explored topologically consistent thinning algorithms and potential medical applications of these methods \cite{palagyi20003d,palagyi2001sequential}.
+In computer graphics, fast medial axis algorithms allow animators to quickly move characters through successive frames \cite{baran2007automatic,bharaj2012automatically}.
+The Tree-structure Extraction Algorithm for Accurate and Robust Skeletons (TEASER) has been used by connectomics researchers to parameterize 3-D shapes \cite{sato2000teasar,zhao2014automatic}.
+
+ADD SECTION ON LEARNED SHAPE FEATURES
+
+ADD SECTION ON GRAPH PARTITIONING

### 2017-11-01 papers/cvpr2018/0_introduction.tex
papers: expanded introduction

--- 2017-10-21 papers/cvpr2018/0_introduction.tex
@@
 
-\begin{itemize}
-	\item Connectomics background
-	\item Problem Statement
-	\item Summary of previous work (lite)
-	\item Summary of our method
-	\item Summary of contributions
-\end{itemize}
+\begin{figure}
+	\centering
+	\includegraphics[width=0.42\linewidth]{./figures/intro-slice.png}
+	\hspace{0.085\linewidth}
+	\includegraphics[width=0.42\linewidth]{./figures/intro-cube.png}
+\end{figure}
+
+Connectomics, the field of large-scale nanometer reconstruction of the wiring diagram of the brain, has created datasets petabytes in size.
+With recent advancements in image acquisition, neuroscientists are producing a terabyte of raw electron micronscopy image data every hour \cite{hildebrand2017whole}.
+Needless to say, it is impossible for domain experts to manually label this bulk of 3-D image data.
+However, many neuroscientists believe that they will be able to explore new insights into the workings of the brain by creating a complete wiring diagram of the brain \cite{kasthuri2015saturated}.
+These observations will create new advancements in neuromedicine, artificial intelligence, and (CITE).
+
+The access to significant datasets and potential for significant scientific contributions to the field of medicine has created a ripe environment for automatic reconstruction of these EM images.
+Significant research in the field has focused on extracting complete neuron reconstructions using the raw EM images.
+These techniques use only the image values acquired from the microscopes to agglomerate pixels into neuron predictions.
+Frequently, convolutional neural networks predict affinities between pixels \cite{ronneberger2015u,lee2015recursive}.
+
+Using only pixel data is not enough for full reconstruction of these datasets (CITE), and so researchers create a level of abstraction on top of the per-pixel algorithms.
+Under the new domain, researchers used these per-pixel algorithms as input to agglomerate pixels into super-pixels and create larger neuron reconstructions \cite{nunez2014graph} (CITE NEUROPROOF).
+These algorithms considered higher level information such as the boundary statistics between pixel regions and simple shape descriptors (CITE LASH).
+These algorithms outperform the per-pixel methods from before but still do not fully leverage the wealth of information available.
+
+Here we present another level of abstraction above the agglomeration strategies of the last few years.
+Our algorithms focus on the overarching shapes of the an oversegmented label volume to determine potential merge candidates.
+After identifying merge regions, we present a 3-D convolutional neural network to predict merges using only as input the shapes of the regions considered.
+Lastly, we build all of these techniques into a graph representation of the label volume.
+This enables us to enforce global constraints on the resulting segmentation that more closely match the biological principles.

### 2017-11-01 papers/cvpr2018/2_method.tex
paper: Major updates to related works
papers: expanded introduction

@@
 
-\begin{algorithm}
+%\begin{algorithm}
 	\begin{algorithmic}
@@
 	\end{algorithmic}
-	\caption{Edge generation function}
-	\label{alg:generate-edges}
-\end{algorithm}
+%	\caption{Edge generation function}
+%	\label{alg:generate-edges}
+%\end{algorithm}
+
+It is important to note that the above algorithm does not enforce neighboring voxel constraints on nearby segments.
+There are instances where two segments belong to the same neuron but the segments produced by the per-pixel and per-superpixel algorithms are non-adjacent.
+Figure (ADD FIGURE) shows two such examples that are not considered by previous research in this field.
+Finding and merge these examples is one of the benefits of retreating from per-pixel algorithms.
+Neither of these examples could merge under the GALA or NeuroProof pipelines.
+
 \subsection{Edge Probabilities}

### 2017-11-01 papers/cvpr2018/3_evaluation.tex
papers: expanded introduction

--- 2017-10-21 papers/cvpr2018/3_evaluation.tex
@@
 
+We evaluate our methods on three EM datasets.
+
+\subsubsection{NeuroProof Pipeline}
+
+Our methods build on top of existing agglomeration strategies. For the purpose of this paper we used the outputs from two established pipelines.
+
+TODO: Toufiq description of neuroproof pipeline, description of FlyEM pipeline
+
+\subsection{Preprocessing}
+
+We perform significant pruning of potential merge candidates by considering only pairs of skeleton endpoints produced by Algorithm \ref{alg:generate-edges}.
+This strategy greatly reduced the number of false merge candidates that we considered.
+However, we evaluate the overall effectiveness of this strategy both in reducing trivial split candidates while maintaining a large majority of the candidates which should merge.
+
+Our candidate generation strategy doesn't enforce an adjacency constraint which allows us to merge candidates that are not consider under existing frameworks.
+We examine the success of our pipeline in merging said candidates.
+
 \subsection{Classifier Training}
 
-\subsection{Experiments}
+DISCUSS PARAMETERS FOR CLASSIFICATION
+
+\subsection{Graph Optimization}
+
+We evaluate the improvement of using a graph optimization strategy over a na\"ive approach that performs hierarchical clustering for all segments above a certain threshold.

### 2017-11-01 papers/cvpr2018/0_introduction.tex
paper: finished a good first draft of the abstract and introduction

--- 2017-10-21 papers/cvpr2018/0_introduction.tex
@@
 
-\begin{itemize}
-	\item Connectomics background
-	\item Problem Statement
-	\item Summary of previous work (lite)
-	\item Summary of our method
-	\item Summary of contributions
-\end{itemize}
+\begin{figure}
+	\centering
+	\includegraphics[width=0.42\linewidth]{./figures/intro-slice.png}
+	\hspace{0.085\linewidth}
+	\includegraphics[width=0.42\linewidth]{./figures/intro-cube.png}
+\end{figure}
+
+The field of connectomics concerns the wiring diagram of the brain at nanometer resolutions. 
+Recent advancements in image acquisition using serial-section electron microscopy (ssEM) has allowed neuroscientists to produce a terabyte of electron micrscopy (EM) image data every hour~\cite{hildebrand2017whole}.
+It is not feasible for domain experts to manually segment the vast amount of 3-D image data to model an entire brain.
+Neuroscientists believe that reconstructing an entire mammilian brain at fine resolution will enable new insights into the workings of the brain~\cite{kasthuri2015saturated}. 
+These observations will allow for new advancements in neuromedicine and artificial intelligence (CITE).
+
+A significant amount of research focuses on automatic reconstruction of the neurons in these EM images because of the scope and importance of the problem. 
+Several of these algorithms attempt to extract complete neurons through the 3-D volumes using only the raw image data as input.
+Oftentimes, convolutional neural networks predict membrane probabilities or affinities between voxels and apply simple thresholds to agglomerate the voxels into clusters~\cite{lee2015recursive,ronneberger2015u}.
+These \textit{per-voxel} algorithms produce useful outputs but currently fall short of complete reconstructions with sufficient accuracy.
+
+Researches currently address the failures of the per-voxel algorithms by training random-forest classifiers to agglomerate an oversegmentation of voxels~\cite{nunez2014graph} (CITE NEUROPROOF). 
+These classifiers take the output of the per-voxel algorithms as input and generate high-level statistics such as affinity distributions between pixel regions. 
+Presently, these methods use hand-designed features despite the evidence that machine-learned features perform better~\cite{bogovic2013learned}. 
+These \textit{per-supervoxel} algorithms outperform the per-voxel algorithms but still do not provide the accuracy needed for large scale reconstruction of the brain.
+Additionally, these methods do not fully leverage the wealth of shape information available.
+
+Here we present a \textit{shape-based} strategy that builds on top of the outputs of per-supervoxel methods. 
+Similarly we take as input the output of the per-supervoxel methods. 
+However, we focus on the overarching shapes traversing through the label volumes to identify potential merge candidates. 
+From these locations we extract machine-learned features and generate a probability that two segments should merge. 
+Lastly, we construct a graphical representation of the input label volume and apply a global segmentation algorithm to produce a better reconstruction.
+Using graph-based optimization strategies enables us to enforce global constraints that more closely match the underlying biology of the images.

### 2017-11-01 papers/cvpr2018/paper.tex
paper: Major updates to related works
paper: finished a good first draft of the abstract and introduction

--- 2017-10-21 papers/cvpr2018/paper.tex
@@
 \usepackage{makecell}
+\usepackage{algpseudocode}
+\usepackage{algorithmicx}
 
@@
 \begin{abstract}
-THE ABSTRACT
+Advancements in electron microscopy image acquisition has created massive datasets petabytes in size that are too large for complete manual segmentation. 
+Several previous strategies for automatic segmentation of these datasets rely work at the per-voxel level.
+Oftentimes, agglomeration strategies build on top of this layer to produce neuron reconstructions.
+Despite the success of these algorithms, there is significant room for improvement.
+Here, we propose a novel framework for correcting errors in existing agglomeration strategies. 
+We create a level of abstraction on top of the existing methods by reformulating the segmentations as a graph and applying global graph-based optimization strategies. 
+In the process we provide key insights into the use of machine-learned shape features for fixing errors. 
 \end{abstract}

### 2017-11-01 papers/cvpr2018/1_related_work.tex
introduction: added one sentence to explain segmentation process

@@
 
-Significant research in connectomics has focused on extracting information from the pixel data of the raw electron microscopy (EM) images.
-Building off previous work in computer vision that used normalized cuts and other graph partitioning algoirithms on images \cite{kappes2016higher,shi2000normalized,tatiraju2008image}, some of the methods apply computationally expensive graph partitioning techniques on the per-voxel images \cite{andres2012globally}.
-Other approaches at the per-pixel level have focused on training 2-D convolutional networks to predict membrane probabilities \cite{ciresan2012deep}.
-More recent work has expanded on these early networks by adding the $z$-dimension to create 3-D networks \cite{lee2015recursive}.
-Oftentimes these networks now predict affinities between voxels rather than membrane probabilities \cite{ronneberger2015u}.
-Extensive research has focused on enhancing the loss functions and optimizers for these networks \cite{chatfield2014return,maas2013rectifier,nesterov1983method}.
+A large amount of connectomics research considers the problem of extracting segmentation information at the voxel level from the raw EM images. 
+Some methods apply computationally expensive graph partitioning techniques with a node per voxel~\cite{andres2012globally} following the previous work in computer vision using normalized cuts for image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}.
+Meanwhile, others focus on training 2-D convolutional neural networks to predict membrane probabilities per image slice~\cite{ciresan2012deep}. 
+More recent strategies augment these neural networks with the $z$-dimension creating full 3-D convolutional networks~\cite{lee2015recursive}
+Oftentimes these networks now produce probabilities for the affinity between voxels rather than probabilities for a voxel belonging to a cell membrane~\cite{ronneberger2015u}. 
+An extensive amount of research in computer vision, applied mathematics, and statistics evaluates the loss functions and optimizers for these networks~\cite{chatfield2014return,maas2013rectifier,nesterov1983method}.
 
-ADD SECTION ON CORRECTING SPLIT ERRORS
+These above neural networks generate probabilities that neighboring voxels belong to the same neuron.
+Many algorithms work at a level above these networks and train random-forest classifiers to produce segmentations of the EM images where every unique neuron in the volume has a unique label~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image} (CITE NEUROPROOF).
 
-These neural networks produce probabilities that neighboring voxels belong to the same neuron.
-Many algorithms build on top of these affinities by agglomerating voxels to produce reconstructed label volumes of the EM images \cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic} (CITE NEUROPROOF, ZWATERSHED).
 Despite the successes of these algorithms they often make early local mistakes leading to errors in the segmentation.
@@
 Although these networks have produced impressed segmentation accuracies, they are currently too slow for large scale connectomics reconstructions.
+
+ADD SECTION ON CORRECTING SPLIT ERRORS
 

### 2017-11-01 papers/cvpr2018/1_related_work.tex
papers: updated related work

@@
 Many algorithms work at a level above these networks and train random-forest classifiers to produce segmentations of the EM images where every unique neuron in the volume has a unique label~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image} (CITE NEUROPROOF).
+Despite the success of these classifiers, they often make mistakes based on the local information leading to errors in the segmentation. 
+Proofreading methods create a ``human-in-the-loop" framework that allows users to find errors and correct them \cite{haehn2017scalable,haehn2017guided,haehn2014design,DBLP:journals/corr/abs-1708-02599}.
+More recently, flood-filling networks merge the process of generating voxel affinities and then producing segmentations by training an end-to-end neural network that outputs segmentations~\cite{januszewski2016flood}.
+Although these networks produce impressive segmentation accuracies, they are currently too slow for large scale connectomics reconstructions.
 
-Despite the successes of these algorithms they often make early local mistakes leading to errors in the segmentation.
-Proofreading methods create a "human-in-the-loop" framework that allows users to find errors and correct them \cite{haehn2017scalable,haehn2017guided,haehn2014design}.
-Flood-filling networks merge these two steps by training an end-to-end network that takes as input raw image data and produces a segmentation \cite{januszewski2016flood}.
-Although these networks have produced impressed segmentation accuracies, they are currently too slow for large scale connectomics reconstructions.
+Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally}. 
+The multicut graph partitioning algorithm extracts segments the graph and remove edges such that there are no cycles. 
+This closely resembles the biological constraint that neurons have a topological genus of zero. 
+There are several useful multicut heuristics which provide good approximations with reasonable computational costs~\cite{horvnakova2017analysis,kernighan1970efficient,keuper2015efficient}
 
-ADD SECTION ON CORRECTING SPLIT ERRORS
+A sizable amount of computer vision research analyzes various hand-designed shape features for determining similarity between objects~\cite{osada2002shape} and for segmentation\cite{conners1984segmentation}.
+Currently, the random-forest classifiers used in connectomics rely on hand-designed features to make merge decisions.
+Some of these features encode the distribution of probabilities that voxels along a segment boundary belong to the same neuron as their neighbors~\cite{nunez2014graph,ren2003learning}.
+However, there is evidence that machine-learned features outperform hand-designed ones~\cite{bogovic2013learned}.
 
-The fields of computer graphics, mathematics, and biomedical visualization have produced extensive research into the skeletonization of 3D binary volumes.
-A large amount of research has explored topologically consistent thinning algorithms and potential medical applications of these methods \cite{palagyi20003d,palagyi2001sequential}.
-In computer graphics, fast medial axis algorithms allow animators to quickly move characters through successive frames \cite{baran2007automatic,bharaj2012automatically}.
-The Tree-structure Extraction Algorithm for Accurate and Robust Skeletons (TEASER) has been used by connectomics researchers to parameterize 3-D shapes \cite{sato2000teasar,zhao2014automatic}.
-
-ADD SECTION ON LEARNED SHAPE FEATURES
-
-ADD SECTION ON GRAPH PARTITIONING
+The fields of computer graphics, mathematics, and biomedical visualization produce extensive research into the skeletonization of 3D binary volumes. 
+Some of the research explores topologically consistent thinning algorithms and potential medical applications of these methods~\cite{palagyi20003d,palagyi2001sequential}. 
+In computer graphics, fast medial axis algorithms allow animators to quickly move characters through successive frames~\cite{baran2007automatic,bharaj2012automatically}. 
+In these works, the skeleton acts as the simplest representation of a 3-D volume. 
+The Tree-structure Extraction Algorithm for Accurate and Robust Skeletons (TEASER) has been used by connectomics researchers to parameterize 3-D shapes~\cite{sato2000teasar,zhao2014automatic}.

### 2017-11-01 papers/cvpr2018/2_method.tex
paper: some updates to methods

--- 2017-10-31 papers/cvpr2018/2_method.tex
@@
 
-Our method works on top of existing $EM$ agglomeration algorithms such as \textit{NeuroProof} or \textit{GALA} (CITE BOTH).
-First we use a 3D U-net to generate voxel affinities predicting the probability that two voxels belong to the same neuron.
-The \textit{zwatershed} algorithms takes these affinities and generates an oversegmentation of the neurons (CITE).
-\textit{NeuroProof} agglomerates these supervoxels by training a multi-level random forest classifier.
-We use a low threshold for neuroproof to generate an oversegmentation.
-
-In order to use graph-based optimization strategies we need to generate nodes $N$ and edges $E$ for the graph $G$.
+Our method takes as input an existing oversegmentation of an $EM$ image volume. 
+Section~\ref{sec:neuroproof} discusses two preexisting pipelines for generating these segmentations.
+We evaluate our proposed method on the outputs from both of these pipelines.
 
@@
 
+We need to generate nodes $N$ and edges $E$ to apply a graph-based optimization strategy for segmentation. 
+In addition, these edges need non-negative weights.
+
 \subsubsection{Node Generation}
 
-The simplest method of generating nodes is to create one node for every unique segment label in a volume.
-However, there are many small segments that remain after NeuroProof that only introduce noise when moving to a higher level of abstraction.
-For now, we decide to remove these segments from consideration and focus on the only the large segments that have expansive spans through the volume.
-Every segment with fewer than $20,000$ voxels is pruned from the set of considered nodes.
-Figure \ref{fig:skeletonization} shows two typical segments that each have one corresponding node in the graph $G$.
+The simplest node generation strategy creates one node for every unique segment label in the input volume.
+However, there are often a small number of labels in the volume corresponding to very small regions.
+It is difficult to extract useful shape features from these segments because of their small, and often random, shape. 
+These segments are pruned from the graph and do not have corresponding nodes. 
+For the proposed framework, we remove segments with fewer than $20,000$ voxels (ADD PERCENT, current estimate less than 10\%).
+Figure~\ref{fig:skeletonization} shows two typical input segments that receive a corresponding node in the graph. .
 
 \subsubsection{Edge Generation}
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=0.42\linewidth]{./figures/skeleton1.png}
+	\hspace{0.085\linewidth}
+	\includegraphics[width=0.42\linewidth]{./figures/skeleton2.png}
+	\caption{Two example outputs of the TEASER skeletonization algorithm.}
+	\label{fig:skeletonization}
+\end{figure}
+
+A na\"ive approach to generating edges simply produces an edge between all segments that have a single pair of neighboring voxels.
+Current agglomeration strategies such as NeuroProof or GALA use this criteria when deciding pairs of segments to merge into one neuron.
+However, for us this method will produce too many edges in our graph, many of which are easily prunable. 
+Many of the segments that are erroneously split have a similar structure. 
+Consider Figure~\ref{fig:merge_candidates} which shows two such pairs.
+In both instances the segments around the break follow the same general shape. 
+The segment is tubular in the close vicinity with an abrupt break perpendicular to the elongated direction.
+We present the following algorithm to identify these locations.
+
+We generate a skeleton for every segment following the intuition that a skeleton represents a simplified representation of the overall shape of an object. 
+We use the Tree-structure Extraction Algorithm for Accurate and Robust Skeletons (TEASER)~\cite{sato2000teasar,zhao2014automatic}. 
+These skeletons consist of a sequence of \textit{joints} with edges between successive joints. 
+We prune the joints that are within $50$ voxels of each other to reduce unnecessary branching.
+For the purposes of this algorithm, joints that have only one connected neighbor are referred to as \textit{endpoints}. 
+Figure~\ref{fig:skeletonization} shows the skeletons in white of two typical segments from the label volume.
+After skeletonization, we begin to identify segments for merge consideration with the following two-pass heuristic.
+In the first pass, we iterate over all endpoints $e$ belonging to a segment $S$ and create a set of segments $\mathbb{S}_e^\prime$ which includes all labels that have a single voxel within $t_{low}$ nanometers from $e$.
+This first pass often includes too many candidates that should not merge so we apply an additional pass to prune these sets.
+In the second pass, we consider all of the segments $\mathbb{S}_e^\prime$ for every endpoint $e$. 
+If a segment $S^\prime \in \mathbb{S}_e^\prime$ has an endpoint within $t_{high}$ nanometers of $e$, the segment $S$ and $S^\prime$ are considered for merging. 
+We store the midpoint between the two endpoints as the ``center" of the potential merge.
+Algorithm (ADD REF) provides pseudocode for this edge generation algorithm. 
+The results in this paper follow from $t_{low} = 240$ and $t_{high} = 600$.
 
@@
 
-The na\"ive edge generation approach is just to simply consider all nodes whose segmentations have a neighboring voxel.
-Current agglomeration approaches such as NeuroProof or GALA use this criteria for deciding which segments could potentially form one neuron.
-However, this produces too many edges in our graph, many of which are easily prunable.
-In fact, many of the segments that we need to merge have very similar structures.
-Consider Figure \ref{fig:merge_candidates} which shows two erroneously split segments.
-In both instances the segments around the break follow the same general shape.
-The segment is more-or-less tubular in the close vicinity with an abrupt break at the end of segment where the next segment begins.
-The following algorithm identifies these locations without introducing as much ``noise" as using the na\"ive strategy.
-
-We begin by generating skeletons for every segment.
-The intuition behind this decision is that a skeleton is a simplified representation of the overarching shape of a segment.
-Figure \ref{fig:skeletonization} shows two example segments and their corresponding skeletons in white.
-These skeletons were generated using the Tree-structure Extraction Algorithm for Accurate and Robust Skeletons (TEASER) \cite{sato2000teasar} which has been used in connectomics research previously \cite{zhao2014automatic}.
-The skeleton consists of a series of \textit{joints} with edges between neighboring joints.
-Joints that have only one neighbor are also called \textit{endpoints}.
-Joints that are within $50$ voxels of each other are pruned to reduce unnecessary branching.
-
-After skeletonization, we proceed to identify locations between segments that we should consider for merging.
-The algorithm proceeds in two passes.
-In the first pass we iterate over every endpoint, $e$, in all of the skeletons and create a set $S_e$ where the set includes every segment that has a single voxel with $t_{low}$nm from the endpoint.
-This first pass often includes too many negative merge candidates leaving a very unbalanced set of merge/split candidates (FIX THIS).
-Therefore, in our second pass we iterate over all of the endpoints and their corresponding sets.
-We find the closest endpoint for a given segment $s \in S_e$ to the endpoint $e$.
-If the closest endpoint is less than $t_{high}$nm from the original endpoint $e$, we add an edge in the graph between these two segments.
-We also store the midpoint between the closest endpoint and the original endpoint $e$, which will be useful in the following section.
-Algorithm \ref{alg:generate-edges} provides pseudocode for this edge generation algorithm.
-The results in this paper follow from $t_{low} = 240nm$ and $t_{high} = 600nm$.
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.42\linewidth]{./figures/skeleton1.png}
-	\hspace{0.085\linewidth}
-	\includegraphics[width=0.42\linewidth]{./figures/skeleton2.png}
-	\caption{Two example outputs of the TEASER skeletonization algorithm.}
-	\label{fig:skeletonization}
-\end{figure}
-
-\begin{algorithm}
 \begin{algorithmic}
@@
 			\For {$endpoint$ in $skeleton$}
-
+				\State TODO ADD CODE
 			\EndFor
@@
 \end{algorithmic}
-	\caption{Edge generation function}
-	\label{alg:generate-edges}
-\end{algorithm}
+
+Note that the above algorithm does not enforce any segment adjacency constraints.
+Figure (ADD FIGURE) shows two examples that would not be considered in previous research since they are not adjacent.
+Finding and merging these examples is one of the benefits of retreating from per-pixel algorithms.
+
 \subsection{Edge Probabilities}
@@
 The previous section outlines how to generate edges between nodes in our graph structure. 
-Here we will introduce a neural network architecture for generating probabilities that two nodes sharing an edge belong to the same neuron.
+Here we introduce a neural network architecture for generating probabilities that two nodes sharing an edge belong to the same neuron. 
 The neural network takes as input only data from the input segmentation.
@@
 
-The above skeletonization algorithm produces 3D locations that require further consideration for merging.
+The above skeletonization algorithm produces 3-D locations that require further consideration for merging. 
 To determine which of these segments should actually merge, we train a 3-D convolutional neural network. 
@@
 A cubic length of $1200\textrm{nm}$ provides enough local shape context for the network without introducing an excessive amount of noise. 
-Figure \ref{fig:network-radius} shows cubes of lengths $800\textrm{nm}, 1200\textrm{nm},$ and $1600\textrm{nm}$.
+Figure~\ref{fig:network-radius} shows cubes of lengths $800\textrm{nm}, 1200\textrm{nm},$ and $1600\textrm{nm}$.
 
@@
 The first channel is $0.5$ if $v = l_1$ and $-0.5$ otherwise, the second channel is $0.5$ if $v = l_2$ and $-0.5$ otherwise, and the third channel is $0.5$ if $v = l_1$ or $v = l_2$ and $-0.5$ otherwise.
-
 Each 3-channel volume is subsequently downsampled into an array of size $(3, 22, 68, 68)$ using nearest-neighbor interpolation. 
-Our neural network trains on these 4-D arrays to generate probabilities that $l_1$ and $l_2$ should merge for every input.
+Our neural network trains on these 4-D arrays to generate probabilities that $l_1$ and $l_2$ should merge.
 
@@
 The output is flattened into a 1-D vector with $8000$ entries which enters two fully connected layers with $512$ and $1$ dimensions in the output respectively. 
-All activation functions are LeakyReLU with $\alpha=0.001$ except for the final activation which uses a sigmoid function \cite{funahashi1989approximate,maas2013rectifier}.
+All activation functions are LeakyReLU with $\alpha=0.001$ except for the final activation which uses a sigmoid function~\cite{funahashi1989approximate,maas2013rectifier}. 
 There is a dropout of $0.2$ after every pooling layer and the first dense layer. 
 There is a dropout of $0.5$ after the final dense layer. 
-The above method uses stochastic gradient descent with Nesterov's Accelerated Gradient \cite{nesterov1983method}.
-This optimizer has an initial learning rate of $0.01$, momentum of $0.9$, and a decay rate of $5*10^{-8}$.
-Figure \ref{fig:architecture} provides an overview of the proposed architecture.
+The above method uses stochastic gradient descent with Nesterov's accelerated gradient~\cite{nesterov1983method}. 
+This optimizer has an initial learning rate of $0.01$, momentum of $0.9$, and a decay rate of $5*10^{-8}$. Figure~\ref{fig:architecture} provides an overview of the proposed architecture.
 
@@
 
-Manual labeling of connectomics datasets is time intensive and expensive (CITE?).
-As we consider higher levels of abstractions of the data, the amount of useful labeled data decreases.
-This follows from the simple fact that manual annotation of the data happens at the per-pixel level, so starting with larger agglomerated segments leads to fewer unique human labels (THIS DOESN'T MAKE SENSE YET).
-
-Therefore, we apply some data augmentation to the generated examples to increase the size of the training datasets.
+We apply some data augmentation to the generated examples to increase the size of the training datasets. 
 We consider all rotations of $90$ degrees along the $xy$-plane in addition to mirrors along the $x$ and $z$ axes. 
@@
 There are many formulations of graph-based optimization strategies that provide different guarantees on their output. 
-Neurons in the brain should be acyclic, i.e.
-the output shape should have a genus of zero.
-Current connectomics agglomeration techniques do not leverage this additional information but rather consider neighboring regions in successive order without regard to created loops.
+Neurons in the brain should be acyclic, i.e. the output shape should have a genus of zero. 
+Current connectomics agglomeration techniques do not leverage this additional information but rather consider neighboring regions in successive order without regard to loop creation. 
 In our graph formulation we can enforce this topological property by applying a multicut partition onto the graph which generates a forest on the nodes. 
-There are several heuristics that solve the multicut problem.
-For our purposes we use the Kernighan-Lin algorithm \cite{kernighan1970efficient}.
+There are several heuristics that solve the multicut problem. For our purposes we use the Kernighan-Lin algorithm~\cite{kernighan1970efficient}.

### 2017-11-01 papers/cvpr2018/3_evaluation.tex
paper: some updates to methods

@@
 We evaluate our methods on three EM datasets. 
+TODO: Toufiq: add description of the EM datasets (volume size, resolution, type of animal, type of image scan)
 
 \subsubsection{NeuroProof Pipeline}
-
+\label{sec:neuroproof}
 Our methods build on top of existing agglomeration strategies. For the purpose of this paper we used the outputs from two established pipelines. 
-
 TODO: Toufiq description of neuroproof pipeline, description of FlyEM pipeline
@@
 We evaluate the improvement of using a graph optimization strategy over a na\"ive approach that performs hierarchical clustering for all segments above a certain threshold.
+Using a heuristic for multicut prevents the creation of cycles. 
+Using a simple agglomeration strategy generates this many cycles.

### 2017-11-01 papers/cvpr2018/4_results.tex
paper: some updates to methods

@@
 
-\begin{figure}
-	\includegraphics[width=0.85\linewidth]{figures/skeleton-training-curve.png}
-	\caption{The training and validation loss when training the neural network on the L. Cylinder data set.}
-	\label{fig:training-curve}
-\end{figure}
+%\begin{figure}
+%	\includegraphics[width=0.85\linewidth]{figures/skeleton-training-curve.png}
+%	\caption{The training and validation loss when training the neural network on the L. Cylinder data set.}
+%	\label{fig:training-curve}
+%\end{figure}
 
-\begin{figure}
-	\includegraphics[width=0.85\linewidth]{figures/roc-microns-300-test.png}
-	\caption{The ROC curve for the training and validation datasets.}
-	\label{fig:roc-curve}
-\end{figure}
+%\begin{figure}
+%	\includegraphics[width=0.85\linewidth]{figures/roc-microns-300-test.png}
+%	\caption{The ROC curve for the training and validation datasets.}
+%	\label{fig:roc-curve}
+%\end{figure}
 
@@
 
-\begin{figure*}[t]
-	\includegraphics[width=0.45\linewidth]{figures/variation_of_information-train.png}
-	\hspace{0.0825\linewidth}
-	\includegraphics[width=0.45\linewidth]{figures/variation_of_information-test.png}	
-\end{figure*}
+%\begin{figure*}[t]
+%	\includegraphics[width=0.45\linewidth]{figures/variation_of_information-train.png}
+%	\hspace{0.0825\linewidth}
+%	\includegraphics[width=0.45\linewidth]{figures/variation_of_information-test.png}	
+%\end{figure*}
 

### 2017-11-05 papers/cvpr2018/3_evaluation.tex
papers: created outline for evaluation and results

--- 2017-10-31 papers/cvpr2018/3_evaluation.tex
@@
 \section{Evaluation}
+
+We evaluate our proposed methods on two different connectomics datasets from two different species.
 
@@
 
-We evaluate our methods on EM datasets.
-The first dataset is the Kashtui dataset  which is a mouse brain (ADD IN STUFF) with an anisotropic resolution of $3\textrm{nm} \times 3 \textrm{nm} \times 30 \textrm{nm}$.
-The second dataset is from FlyEM and is a (ADD STUFF HERE) with an anisotropic resolution of $3 \textrm{nm} \times 3\textrm{nm} \times 30\textrm{nm}$.
+\subsubsection{Kasthuri}
 
-\subsection{Preprocessing}
+\subsubsection{FlyEM}
 
-What percent of edges are considered.
+\subsubsection{Segmentation Pipeline and Baseline}
 
-Figure (ADD FIGURE) shows a few segments that were not considered.
+\subsection{Skeleton Pruning}
+
+HOW DO WE EVALUATE THE PRUNING METHOD
+HOW MANY EXAMPLES DO WE MISS
 
@@
 
-Here I need to produce the precision and recall curves, (ROC) as well as the final results with thresholding. Also include the training/validation loss functions overtime
+HOW DO WE TRAIN THE CLASSIFIER - split the data in half and have training and validation
+DATA AUGMENTATION
+HOW MANY LEARNABLE PARAMETERS
+WHAT NETWORKS DID WE TRY
+HAVE A TABLE WITH PARAMETERS: ITERATIONS, momentum, batch size, learning rate
 
-\subsection{Experiments}
+\subsection{Graph-based Strategies}
+
+%We evaluate our method on two different connectomics datasets of different species.
+
+%\subsection{Datasets}
+
+%\subsubsection{Kasthuri}
+
+%The first dataset is the left part of the mouse cortex volume of Kasthuri et al.
+(CITE).
+We divide the dataset into a training and validation half and a testing half.
+The dataset resolution is $3 \times 3 \times 30 \textrm{nm}^3/\textrm{voxel}$.
+
+%\subsubsection{FlyEM}
+
+%We evaluate our methods on three EM datasets. 
+%TODO: Toufiq: add description of the EM datasets (volume size, resolution, type of animal, type of image scan)
+
+%\subsubsection{NeuroProof Pipeline}
+%\label{sec:neuroproof}
+%Our methods build on top of existing agglomeration strategies. For the purpose of this paper we used the outputs from two established pipelines. 
+%TODO: Toufiq description of neuroproof pipeline, description of FlyEM pipeline
+
+%\subsection{Preprocessing}
+
+%We perform significant pruning of potential merge candidates by considering only pairs of skeleton endpoints produced by Algorithm \ref{alg:generate-edges}.
+This strategy greatly reduced the number of false merge candidates that we considered.
+However, we evaluate the overall effectiveness of this strategy both in reducing trivial split candidates while maintaining a large majority of the candidates which should merge.
+
+%Our candidate generation strategy doesn't enforce an adjacency constraint which allows us to merge candidates that are not consider under existing frameworks.
+We examine the success of our pipeline in merging said candidates.
+
+%\subsection{Classifier Training}
+
+%DISCUSS PARAMETERS FOR CLASSIFICATION
+
+%\subsection{Graph Optimization}
+
+%We evaluate the improvement of using a graph optimization strategy over a na\"ive approach that performs hierarchical clustering for all segments above a certain threshold.
+%Using a heuristic for multicut prevents the creation of cycles. 
+%Using a simple agglomeration strategy generates this many cycles.

### 2017-11-05 papers/cvpr2018/4_results.tex
papers: created outline for evaluation and results

@@
 \section{Results}
-
-Here we show the results for the three main contributions for this paper: merge consideration using skeleton pruning, merge probabilities output from the trained convolutional neural network, and the final output of the pipeline.
 
@@
 
-\subsubsection{Finding Merge Candidates}
+\subsubsection{Kasthuri}
 
-\subsubsection{Finding Split Candidates}
+\subsubsection{FlyEM}
 
-Effective pruning for merge candidates should have high precision and recall for segments that should be merged.
+\subsection{Classification Performance}
 
-\subsection{Neural Network Classification}
+\subsubsection{Kasthuri}
 
-\subsubsection{Merge Network}
+\subsubsection{FlyEM}
+
+\subsection{Graph Based Strategies}
+
+\subsubsection{Kasthuri}
+
+\subsubsection{FlyEM}
+
+%Here we show the results for the three main contributions for this paper: merge consideration using skeleton pruning, merge probabilities output from the trained convolutional neural network, and the final output of the pipeline.
+
+%\subsection{Skeleton Pruning}
+
+%\subsubsection{Finding Merge Candidates}
+
+%\subsubsection{Finding Split Candidates}
+
+%Effective pruning for merge candidates should have high precision and recall for segments that should be merged.
+
+%\subsection{Neural Network Classification}
+
+%\subsubsection{Merge Network}
 
@@
 
-Figure \ref{fig:training-curve} shows the training and validation loss during the training of the neural network.
+%Figure \ref{fig:training-curve} shows the training and validation loss during the training of the neural network.
 
@@
 
-\subsubsection{Split Network}
+%\subsubsection{Split Network}
 
-\subsection{Graph-based Error Correction}
+%\subsection{Graph-based Error Correction}

### 2017-11-06 papers/cvpr2018/0_introduction.tex
introduction: added one sentence to explain segmentation process
Address HP's comments for the introduction. I also re-wrote the whole abstract.

@@
 \section{Introduction}
+
+The field of connectomics is concerned with reconstructing the wiring diagram of the brain at nanometer resolutions. 
+Recent advancements in image acquisition using multi-beam serial-section electron microscopy (sSEM) has allowed neuroscientists to produce terabytes of electron micrsocopy (EM) image data every hour~\cite{hildebrand2017whole}.
+Neuroscientists believe that reconstructing an entire mammilian brain at fine resolution will enable new insights into the workings of the brain~\cite{kasthuri2015saturated}. 
+These observations will allow for new advancements in neuromedicine and artificial intelligence (CITE). 
+Segmentation is part of this reconstruction process, assigning a unique label for every neuron in the EM image.
+It is not feasible for domain experts to manually segment the vast amount of 3-D image data to model an entire brain.
+
+A significant amount of research focuses on automatic reconstruction of the neurons in EM images because of the scope and importance of the problem (ADD REFERENCES).%TODO SEVERAL REFERENCES FOR AUTOMATIC SEGMENTATIONS
+All of these algorithms extract neuronal processes through the 3-D volumes using only the raw image data as input.
+Oftentimes, convolutional neural networks (CNNs) predict membrane probabilities or affinities between voxels and apply simple thresholds to agglomerate the voxels into clusters~\cite{lee2015recursive,ronneberger2015u}.
+These \textit{per-voxel} algorithms produce excellent results but currently fall short of complete reconstructions with error rates of approximately $X\%$. %TODO ADD ERROR RATES
 
@@
 	\centering
-	\includegraphics[width=0.42\linewidth]{./figures/intro-slice.png}
+	\includegraphics[width=0.42\linewidth]{./figures/merge_candidate1.png}
 	\hspace{0.085\linewidth}
 	\includegraphics[width=0.42\linewidth]{./figures/intro-cube.png}
+	\caption{We use 3D skeletons to combine neuron labels to full reconstructions.}
 \end{figure}
-
-The field of connectomics concerns the wiring diagram of the brain at nanometer resolutions. 
-Recent advancements in image acquisition using serial-section electron microscopy (ssEM) has allowed neuroscientists to produce a terabyte of electron micrscopy (EM) image data every hour~\cite{hildebrand2017whole}.
-It is not feasible for domain experts to manually segment the vast amount of 3-D image data to model an entire brain.
-Neuroscientists believe that reconstructing an entire mammilian brain at fine resolution will enable new insights into the workings of the brain~\cite{kasthuri2015saturated}. 
-These observations will allow for new advancements in neuromedicine and artificial intelligence (CITE).
-
-A significant amount of research focuses on automatic reconstruction of the neurons in these EM images because of the scope and importance of the problem. 
-Several of these algorithms attempt to extract complete neurons through the 3-D volumes using only the raw image data as input.
-Oftentimes, convolutional neural networks predict membrane probabilities or affinities between voxels and apply simple thresholds to agglomerate the voxels into clusters~\cite{lee2015recursive,ronneberger2015u}.
-These \textit{per-voxel} algorithms produce useful outputs but currently fall short of complete reconstructions with sufficient accuracy.
 
@@
 Presently, these methods use hand-designed features despite the evidence that machine-learned features perform better~\cite{bogovic2013learned}. 
-These \textit{per-supervoxel} algorithms outperform the per-voxel algorithms but still do not provide the accuracy needed for large scale reconstruction of the brain.
+These \textit{per-supervoxel} algorithms outperform the per-voxel algorithms but still do not provide the accuracy needed for large scale reconstructions of the brain.
 Additionally, these methods do not fully leverage the wealth of shape information available.
+E.g., it is well known that neurons angle at less than $30$ degrees (CITE).
+%TODO ADD CITATION FOR NEURON SHAPES
 
-Here we present a \textit{shape-based} strategy that builds on top of the outputs of per-supervoxel methods. 
-Similarly we take as input the output of the per-supervoxel methods. 
-However, we focus on the overarching shapes traversing through the label volumes to identify potential merge candidates. 
-From these locations we extract machine-learned features and generate a probability that two segments should merge. 
-Lastly, we construct a graphical representation of the input label volume and apply a global segmentation algorithm to produce a better reconstruction.
+Here we present a \textit{graph-based} strategy that builds on top of the outputs of per-supervoxel methods by taking neuronal shape properties into account. 
+Similarly we take as input automatic segmentations. 
+However, we focus on general neuron shapes, traversing through the label volumes to identify potential merge candidates. 
+From these locations we extract machine-learned features and generate a probability that two label segments should be joined. 
+We construct a graph representation of the input label volume. 
 Using graph-based optimization strategies enables us to enforce global constraints that more closely match the underlying biology of the images.
+Lastly, we apply a global segmentation algorithm to produce a better reconstruction.

### 2017-11-06 papers/cvpr2018/1_related_work.tex
Update related work according to HP's feedback.

@@
 
-A large amount of connectomics research considers the problem of extracting segmentation information at the voxel level from the raw EM images. 
-Some methods apply computationally expensive graph partitioning techniques with a node per voxel~\cite{andres2012globally} following the previous work in computer vision using normalized cuts for image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}.
-Meanwhile, others focus on training 2-D convolutional neural networks to predict membrane probabilities per image slice~\cite{ciresan2012deep}. 
-More recent strategies augment these neural networks with the $z$-dimension creating full 3-D convolutional networks~\cite{lee2015recursive}
-Oftentimes these networks now produce probabilities for the affinity between voxels rather than probabilities for a voxel belonging to a cell membrane~\cite{ronneberger2015u}. 
+\paragraph{Voxel-based methods.} A large amount of connectomics research considers the problem of extracting segmentation information at the voxel level from the raw EM images. 
+Such works focus on training 2-D convolutional neural networks to predict membrane probabilities per image slice~\cite{ciresan2012deep,jain2010boundary,amelio_segmentation,rhoananet,kaynig2015large}. 
+More recent strategies augment these neural networks with the $z$-dimension creating full 3-D convolutional networks~\cite{lee2015recursive}.
+Oftentimes these networks produce probabilities for the affinity between voxels rather than probabilities for a voxel belonging to a cell membrane~\cite{ronneberger2015u}. 
+A sizable amount of computer vision research analyzes various hand-designed shape features for determining similarity between objects~\cite{osada2002shape} and for segmentation\cite{conners1984segmentation}.
+Currently, the random-forest classifiers used in connectomics rely on hand-designed features to make merge decisions.
+Some of these features encode the distribution of probabilities that voxels along a segment boundary belong to the same neuron as their neighbors~\cite{nunez2014graph,ren2003learning}.
+However, there is evidence that machine-learned features outperform hand-designed ones~\cite{bogovic2013learned}.
 An extensive amount of research in computer vision, applied mathematics, and statistics evaluates the loss functions and optimizers for these networks~\cite{chatfield2014return,maas2013rectifier,nesterov1983method}.
 
-These above neural networks generate probabilities that neighboring voxels belong to the same neuron.
-Many algorithms work at a level above these networks and train random-forest classifiers to produce segmentations of the EM images where every unique neuron in the volume has a unique label~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image} (CITE NEUROPROOF).
+\paragraph{Super-voxel methods.} These approaches generate probabilities that neighboring voxels belong to the same neuron.
+Many algorithms work at the resulting super-voxel level and train random-forest classifiers to produce segmentations of the EM images where every unique neuron in the volume has a unique label~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image} (CITE NEUROPROOF).
 Despite the success of these classifiers, they often make mistakes based on the local information leading to errors in the segmentation. 
-Proofreading methods create a ``human-in-the-loop" framework that allows users to find errors and correct them \cite{haehn2017scalable,haehn2017guided,haehn2014design,DBLP:journals/corr/abs-1708-02599}.
+Proofreading methods create a ``human-in-the-loop" framework that allows users to find errors and correct them \cite{haehn2017scalable,haehn2017guided,haehn2014design,error_correction_using_CNN}.
+
 More recently, flood-filling networks merge the process of generating voxel affinities and then producing segmentations by training an end-to-end neural network that outputs segmentations~\cite{januszewski2016flood}.
-Although these networks produce impressive segmentation accuracies, they are currently too slow for large scale connectomics reconstructions.
+These networks produce impressive segmentation accuracies of over $X\%$.%TODO ADD ACCURACY FOR FLOOD FILLING NETWORKS
+%, they are currently too slow for large scale connectomics reconstructions.
 
-Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally}. 
+\paragraph{Graph-based methods}.
+Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}.
 The multicut graph partitioning algorithm extracts segments the graph and remove edges such that there are no cycles. 
@@
 
-A sizable amount of computer vision research analyzes various hand-designed shape features for determining similarity between objects~\cite{osada2002shape} and for segmentation\cite{conners1984segmentation}.
-Currently, the random-forest classifiers used in connectomics rely on hand-designed features to make merge decisions.
-Some of these features encode the distribution of probabilities that voxels along a segment boundary belong to the same neuron as their neighbors~\cite{nunez2014graph,ren2003learning}.
-However, there is evidence that machine-learned features outperform hand-designed ones~\cite{bogovic2013learned}.
-
-The fields of computer graphics, mathematics, and biomedical visualization produce extensive research into the skeletonization of 3D binary volumes. 
+\paragraph{Skeletonization methods.} We use a graph-based abstraction of segmentation data based on skeletonizations. 
+This topic is the focus of extensive research in the fields of computer graphics, mathematics, and biomedical visualization.
+%The fields of computer graphics, mathematics, and biomedical visualization produce extensive research into the skeletonization of 3D binary volumes. 
 Some of the research explores topologically consistent thinning algorithms and potential medical applications of these methods~\cite{palagyi20003d,palagyi2001sequential}. 

### 2017-11-06 papers/cvpr2018/0_introduction.tex
Add one more todo.

@@
 	\includegraphics[width=0.42\linewidth]{./figures/intro-cube.png}
-	\caption{We use 3D skeletons to combine neuron labels to full reconstructions.}
+	\caption{We use 3D skeletons to combine neuron labels to full reconstructions.
+(TODO: Add schematic figure showing the difference between voxel-based / super-voxel based / graph-based algorithms with connections and hierarchy)} %TODO: SCHEMATIC FIGURE
 \end{figure}

### 2017-11-06 papers/cvpr2018/1_related_work.tex
paper: updated evaluation and results

@@
 
-\paragraph{Graph-based methods}.
-Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}.
+\paragraph{Graph-based methods.} Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}.
 The multicut graph partitioning algorithm extracts segments the graph and remove edges such that there are no cycles. 

### 2017-11-06 papers/cvpr2018/3_evaluation.tex
paper: updated evaluation and results

@@
 
-We evaluate our proposed methods on two different connectomics datasets from two different species.
+We evaluate our proposed methods on two different connectomics datasets, one anisotropic and the other isotropic, from two different species.
 
@@
 \subsubsection{Kasthuri}
+The Kasthuri dataset images the neocortex of a mouse brain produced by a scanning electron microscope \cite{kasthuri2015saturated}. 
+This dataset is $338 \times 3618 \times  5342$ voxels in size. 
+The resolution of the dataset is $3 \times 3 \times 30 \textrm{nm}^3$. 
+We evaluate our methods using the left cylinder of this 3-cylinder dataset.
 
@@
 
+The FlyEM dataset comes from the mushroom body of a 5-day old adult male \textit{Drosophila} fly imaged by a focused ion-beam milling scanning electron microscopy.  
+The mushroom body is this species is the major site of associative learning \cite{takemura2017connectome}. 
+The original dataset contains a $40 \mu\textrm{m} \times 50\mu\textrm{m} \times 120\mu\textrm{m}$ volume of which we use two subsections of size $1000 \times 1000 \times 1000$ voxels.  
+The resolution of this dataset is $10 \times 10 \times 10 \mu\textrm{m}^3$ per voxel. 
+The image data and the accompanying ground truth is available (CITE).
+
 \subsubsection{Segmentation Pipeline and Baseline}
+
+Our algorithm takes the output of a supervoxel based agglomeration strategy such as NeuroProof or GALA.
+For our experiments we use the output from NeuroProof (CITE).
+We generate voxel affinities from the raw image data using the U-Net architecture \cite{ronneberger2015u}.
+The Zwatershed algorithm (CITE) creates an oversegmentation of the neurons given these voxel affinities.
+We input the raw image data, the voxel affinities, and the oversegmentation into NeuroProof which performs a hierarchical agglomeration strategy to merge the supervoxels into larger and larger segments.
+Two neighboring segments receive a merge-likelihood score based on various extracted features such as the distribution of affinities along the segment boundary.
+A random forest classifier generates probabilities based on these features.
+(TODO: TOUFIQ ADD HERE)
 
@@
 
-HOW DO WE EVALUATE THE PRUNING METHOD
-HOW MANY EXAMPLES DO WE MISS
+Our method prunes potential merge candidates by considering the skeleton as a simplification of the segment shape.
+Segment skeletons that have nearby endpoints are merge candidates.
+The underlying assumption in this model is that the segments break in a particular fashion, primarily perpendicular to the direction of travel (CONFUSING).
+We perform a series of experiments to evaluate the effectiveness of this idea.
+First, we examine how many merge candidates are not considered using our method that would have been if we employed the strategy of considering all neighboring segments.
+These are locations that we cannot possibly correct and therefore we want this number to be as low as possible.
+The second experiment considers how many locations are not considered that should not be merged.
+We want this number to be as large as possible since we want to avoid making mistakes by merging these segments.
+At best, these segments waste time and at worst they lead to incorrect merges.
 
@@
 
-HOW DO WE TRAIN THE CLASSIFIER - split the data in half and have training and validation
-DATA AUGMENTATION
-HOW MANY LEARNABLE PARAMETERS
-WHAT NETWORKS DID WE TRY
-HAVE A TABLE WITH PARAMETERS: ITERATIONS, momentum, batch size, learning rate
+We divide both datasets into half to train the classifier.
+We generate all valid examples for merge consideration based on the skeletonization algorithm.
+In the training dataset, $80\%$ of the examples are used for training and the remaining examples are used for validation.
+To start, we consider networks of varying sizes, optimization functions, and loss functions.
+The supplemental material has additional information concerning the tuning of the network.
+There are XXX,XXX learnable parameters in our final architecture.
+The training ran for XX epochs.
+Table \ref{table:architecture} provides the final network parameters.
+
+\begin{table}[h!]
+	\centering
+	\begin{tabular}{l l} \hline
+		\textbf{Parameters} & \textbf{Values} \\ \hline
+		Loss Function & Mean Squared Error \\
+		Optimizer & SGD  with Nesterov Momentum \\
+		Momentum & 0.9 \\
+		Initial Learning Rate & 0.01 \\
+		Decay Rate & $5 * 10^{-8}$ \\
+		Activation & LeakyReLU $(\alpha = 0.001)$ \\
+		Kernel Sizes & $3 \times 3 \times 3$ \\
+		Filter Sizes & $16 \to 32 \to 64$ \\ \hline
+	\end{tabular}
+	\caption{The parameters for the trained neural network.}
+	\label{table:architecture}
+\end{table}
+
+\paragraph{Data Augmentation.}
+We apply some data augmentation to the generated examples to increase the size of the training datasets. 
+We consider all rotations of $90$ degrees along the $xy$-plane in addition to mirrors along the $x$ and $z$ axes. 
+This produces an additional 16 times more training data.
 
 \subsection{Graph-based Strategies}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.8\linewidth]{./figures/multicut.png}
+	\caption{An example of the benefits of using multicut over simpler agglomeration schemes.
+If we input this example into a na\"ive agglomeration strategy that collapses all edges with a threshold greater than 0.5, this entire segment will merge together despite the fact that nodes 2 and 4 and nodes 3 and 5 have low affinities.}
+	\label{fig:multicut}
+\end{figure}
+
+Most current agglomeration strategies in connectomics consider all pairs of neighboring segments.
+A classifier produces a probability that each pair belongs to the same segment.
+All segment pairs with a probability above a certain threshold are merged together.
+Consider the simple example in Figure \ref{fig:multicut}.
+Under the existing agglomeration schemes this entire graph would become one segment.
+However multicut eliminates all cycles within the graph creating two unique segments.
+We compare our results using both the traditional hierarchical agglomeration strategy with the graph-based approach we propose.
+
+\subsection{Variation of Information}
+
+We use the variation of information metric to determine the accuracy of our pipeline.
+The variation of information measures the distance between two segmentations and is similar to mutual information.
+A lower variation of information score corresponds to a segmentation closer to the ground truth.
+(TODO: TOUFIQ ADD HERE)
 

### 2017-11-06 papers/cvpr2018/4_results.tex
paper: updated evaluation and results

--- 2017-10-31 papers/cvpr2018/4_results.tex
@@
 
-\subsubsection{Finding Merge Candidates}
+\paragraph{Finding Positive Examples.}
 
-\subsubsection{Finding Split Candidates}
+As a baseline, we consider all pairs of segments that have neighboring voxels and see what percent of these segments are considered for merging.
+In the L.
+Cylinder dataset, there are XXX neighboring segments which have at least adjacent voxels.
+Our method which uses skeletons to prune the considered candidates finds XXX of these segments, or XX\% percent.
+On the FlyEM dataset, there are XXX adjacent segments with XXX found (XX\% percent).
+Figure \ref{fig:skeleton-results} shows some of the missed examples.
+The most common errors are the dendrite spines where the larger segment did not have an endpoint near the split.
+However, our algorithm does not require segments to be adjacent to merge.
+This offers a great benefit compared to traditional methods.
+In our datasets XXX and XXX segments are candidates for merging despite not having adjacent voxels.
+Figure \ref{fig:skeleton-results} gives one such pair which is merged given the results of our algorithm.
 
-Effective pruning for merge candidates should have high precision and recall for segments that should be merged.
+\paragraph{Pruning Negative Examples.}
 
-\subsection{Neural Network Classification}
+Traditional agglomeration strategies consider a large number of negative candidates that we hope to prune.
+The original approach of considering adjacent supervoxels has XX,XXX and XX,XXX candidates which do not belong to the same neuron.
+With our pruning algorithm, this reduces to X,XXX and X,XXX, a factor of over XX times.
+This allows a more reasonable training environment with greater balance between the positive and negative merge examples.
 
-\subsubsection{Merge Network}
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=0.42\linewidth]{./figures/merge_candidate1.png}
+	\hspace{0.085\linewidth}
+	\includegraphics[width=0.42\linewidth]{./figures/merge_candidate2.png}
+	\caption{Two erroneously split segments that should merge together. Most segments that we want to merge have the same general structure.}
+	\label{fig:skeleton-results}
+\end{figure}
+
+\subsection{Classification Performance}
+
+Table \ref{table:classification} shows the precision and recall for all of the datasets.
+Our methods are more general than traditional connectomics examples allowing us to train the network on an anisotropic dataset and get impressive results on an isotropic dataset.
+Our initial network does not take in any image data, only the segment shapes, so we merely extract the $1200 \textrm{nm}^3$ region from any dataset and rescale as input into the neural network.
+For each of the tables, the top left square gives the number of segments which should merge that we predict merge.
+The bottom right square gives the number of segments which should not merge that we predict should not merge.
+The bottom left quadrant indicates the amount of false positives, candidates which we predict merge which do not.
+The top right quadrant gives the amount of false negatives where we predict split although the candidates should merge.
+Figure \ref{fig:network-results} shows the receiver operating characteristic (ROC) curve for all four datasets.
 
 \begin{figure}
-	\includegraphics[width=0.85\linewidth]{figures/skeleton-training-curve.png}
-	\caption{The training and validation loss when training the neural network on the L. Cylinder data set.}
-	\label{fig:training-curve}
+	\includegraphics[width=0.9\linewidth]{./figures/roc-microns-300-test.png}
+	\caption{The receiver operating characteristic (ROC) curve for all four datasets.}
+	\label{fig:network-results}
 \end{figure}
 
-\begin{figure}
-	\includegraphics[width=0.85\linewidth]{figures/roc-microns-300-test.png}
-	\caption{The ROC curve for the training and validation datasets.}
-	\label{fig:roc-curve}
-\end{figure}
+\subsection{Graph Based Strategies}
 
-Figure \ref{fig:training-curve} shows the training and validation loss during the training of the neural network.
+Using a graph-based optimization strategy prevents XX segments from merging compared to the simple hierarchical agglomeration strategy with an optimal threshold cut off.
+Since correcting merge errors is significantly more difficult than correcting split errors, it is desirable to limit the number of false merges.
+The graph-based strategies significantly improve this error type.
 
-\begin{figure*}[t]
-	\includegraphics[width=0.45\linewidth]{figures/variation_of_information-train.png}
-	\hspace{0.0825\linewidth}
-	\includegraphics[width=0.45\linewidth]{figures/variation_of_information-test.png}	
+\subsection{Variation of Information Improvements}
+
+The final metric for comparing two connectomics segmentations is computing the variation of information with respect to an expert-labeled ground truth dataset.
+Figure \ref{fig:variation-of-information} shows the results on the datasets compared to the baseline (green) and an oracle (blue).
+
+\begin{figure*}[t!]
+	\centering
+	\includegraphics[width=0.42\linewidth]{./figures/variation_of_information-train.png}
+	\hspace{0.085\linewidth}
+	\includegraphics[width=0.42\linewidth]{./figures/variation_of_information-test.png}
+	\caption{The improvement on variation of information from the baseline NeuroProof segmentation (green). Results closer to the origin are better.}
+	\label{fig:variation-of-information}
 \end{figure*}
-
-\subsubsection{Split Network}
-
-\subsection{Graph-based Error Correction}

### 2017-11-06 papers/cvpr2018/0_introduction.tex
Major changes to method

@@
 
-A significant amount of research focuses on automatic reconstruction of the neurons in EM images because of the scope and importance of the problem (ADD REFERENCES).%TODO SEVERAL REFERENCES FOR AUTOMATIC SEGMENTATIONS
+A significant amount of research focuses on automatic reconstruction of the neurons in EM images because of the scope and importance of the problem~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image}.%TODO DOUBLE CHECL REFERENCES
 All of these algorithms extract neuronal processes through the 3-D volumes using only the raw image data as input.
@@
 These \textit{per-supervoxel} algorithms outperform the per-voxel algorithms but still do not provide the accuracy needed for large scale reconstructions of the brain.
-Additionally, these methods do not fully leverage the wealth of shape information available.
-E.g., it is well known that neurons angle at less than $30$ degrees (CITE).
+Additionally, these methods do not fully leverage the wealth of shape information available (e.g., it is well known that neurons angle at less than $30$ degrees (CITE)).
 %TODO ADD CITATION FOR NEURON SHAPES
@@
 Using graph-based optimization strategies enables us to enforce global constraints that more closely match the underlying biology of the images.
-Lastly, we apply a global segmentation algorithm to produce a better reconstruction.
+Lastly, we apply a globally optimal algorithm to produce a better reconstruction.

### 2017-11-06 papers/cvpr2018/1_related_work.tex
Major changes to method

@@
 
-\paragraph{Voxel-based methods.} A large amount of connectomics research considers the problem of extracting segmentation information at the voxel level from the raw EM images. 
+\paragraph{Voxel-based methods.} 
+A large amount of connectomics research considers the problem of extracting segmentation information at the voxel level from the raw EM images to produce label volumes.
+In a label volume, every voxels receives a segment label corresponding to a unique neuron.
+Voxels with the same segment label belong to the same neuron. 
 Such works focus on training 2-D convolutional neural networks to predict membrane probabilities per image slice~\cite{ciresan2012deep,jain2010boundary,amelio_segmentation,rhoananet,kaynig2015large}. 
@@
 
-\paragraph{Super-voxel methods.} These approaches generate probabilities that neighboring voxels belong to the same neuron.
-Many algorithms work at the resulting super-voxel level and train random-forest classifiers to produce segmentations of the EM images where every unique neuron in the volume has a unique label~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image} (CITE NEUROPROOF).
+\paragraph{Super-voxel methods.} 
+These approaches generate probabilities that neighboring voxels belong to the same neuron.
+Many algorithms work at the resulting supervoxel level and train random-forest classifiers to produce segmentations of the EM images where every unique neuron in the volume has a unique label~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image} (CITE NEUROPROOF).
 Despite the success of these classifiers, they often make mistakes based on the local information leading to errors in the segmentation. 
@@
 These networks produce impressive segmentation accuracies of over $X\%$.%TODO ADD ACCURACY FOR FLOOD FILLING NETWORKS
-%, they are currently too slow for large scale connectomics reconstructions.
 
-\paragraph{Graph-based methods.} Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}.
+\paragraph{Graph-based methods.} 
+Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}.
 The multicut graph partitioning algorithm extracts segments the graph and remove edges such that there are no cycles. 

### 2017-11-06 papers/cvpr2018/2_method.tex
paper: updated evaluation and results
Major changes to method

@@
 
-Our method takes as input an existing oversegmentation of an $EM$ image volume. 
-Section~\ref{sec:neuroproof} discusses two preexisting pipelines for generating these segmentations.
-We evaluate our proposed method on the outputs from both of these pipelines.
+There are two types of errors that can occur in image segmentation problems.
+The first, called a split error, occurs when there are two segments that should have been merged.
+The second, called a merge error, happens when one segment should be split into two.
+Generally, it is much more difficult to correct merge errors than to correct split errors (CITE). 
+Our method takes as input an oversegmentation of an $EM$ image volume where there are many more split errors than merge errors.
+Our goal is to identify locations of split errors and merge the corresponding segments.
+Section~\ref{sec:neuroproof} discusses two pipelines for generating these segmentations.
+
+From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with weights $w_e$. 
+The nodes correspond to label segments from the segmentation and the edges between segments considered for merging.
+Ideally, our graph has edges corresponding to all of the segments which were erroneously split with few edges between correctly split segments.
+We generate a skeleton for every segment following the intuition that a skeleton represents a simplified representation of the overall shape of an object. 
+We locate merge candidates and produce corresponding edges based on these skeletons.
+A CNN generates the edge weights by learning a merge function given two segments as input. 
+A multicut heuristic generates a partition on the graph where nodes in the same partition are assigned the same output label. 
+Thus there are three major components to our framework: skeletonization for constructing a graph, network training for determining edge weights, and graph-partitioning using a multicut heuristic algorithm.
+(INSERT FIGURE HERE)
 
@@
 
-We need to generate nodes $N$ and edges $E$ to apply a graph-based optimization strategy for segmentation. 
+We generate nodes $N$ and edges $E$ to apply a graph-based optimization strategy for segmentation. 
 In addition, these edges need non-negative weights.
@@
 The simplest node generation strategy creates one node for every unique segment label in the input volume.
-However, there are often a small number of labels in the volume corresponding to very small regions.
+However, some of the millions of labels in the volume correspond to very small regions. 
+Usually these locations have noisy image data so the voxel-based methods could not provide enough information to generate a larger segment.
 It is difficult to extract useful shape features from these segments because of their small, and often random, shape. 
-These segments are pruned from the graph and do not have corresponding nodes. 
-For the proposed framework, we remove segments with fewer than $20,000$ voxels (ADD PERCENT, current estimate less than 10\%).
-Figure~\ref{fig:skeletonization} shows two typical input segments that receive a corresponding node in the graph. .
+We prune these nodes from the graph by removing all segments with fewer than $20,000$ voxels. 
+On a typical connectomics dataset this only remove XX$\%$ of segments.
 
@@
 
-A na\"ive approach to generating edges simply produces an edge between all segments that have a single pair of neighboring voxels.
-Current agglomeration strategies such as NeuroProof or GALA use this criteria when deciding pairs of segments to merge into one neuron.
-However, for us this method will produce too many edges in our graph, many of which are easily prunable. 
-Many of the segments that are erroneously split have a similar structure. 
-Consider Figure~\ref{fig:merge_candidates} which shows two such pairs.
-In both instances the segments around the break follow the same general shape. 
-The segment is tubular in the close vicinity with an abrupt break perpendicular to the elongated direction.
-We present the following algorithm to identify these locations.
+A na\"ive approach to generating edges produces an edge between all adjacent segments.
+Two segments $l_1$ and $l_2$ are considered adjacent if there is a pair of adjacent voxels where one has label $l_1$ and the other has label $l_2$. 
+NeuroProof and GALA consider all pairs of adjacent segments for merging. 
+This method produces too many edges in the graph for us.
+Therefore we present the following algorithm to identify pairs of segments to consider merging.
 
-We generate a skeleton for every segment following the intuition that a skeleton represents a simplified representation of the overall shape of an object. 
-We use the Tree-structure Extraction Algorithm for Accurate and Robust Skeletons (TEASER)~\cite{sato2000teasar,zhao2014automatic}. 
-These skeletons consist of a sequence of \textit{joints} with edges between successive joints. 
+First, we extract a skeleton from each segment using the TEASER algorithm~\cite{sato2000teasar,zhao2014automatic}.
+Figure~\ref{fig:skeletonization} shows the skeletons in white of two segments from the label volume.
+These skeletons consist of a sequence of \textit{joints}, locations that are a local maximum distance from the segment boundary, with line segments connecting successive joints. 
 We prune the joints that are within $50$ voxels of each other to reduce unnecessary branching.
-For the purposes of this algorithm, joints that have only one connected neighbor are referred to as \textit{endpoints}. 
-Figure~\ref{fig:skeletonization} shows the skeletons in white of two typical segments from the label volume.
+For the purposes of our algorithm, joints that have only one connected neighbor are referred to as \textit{endpoints}. 
+Many of the segments that are erroneously split follow a similar pattern (Figure~\ref{fig:merge_candidates}). 
+In these split instances the skeletons have nearby endpoints.
+
 After skeletonization, we begin to identify segments for merge consideration with the following two-pass heuristic.
-In the first pass, we iterate over all endpoints $e$ belonging to a segment $S$ and create a set of segments $\mathbb{S}_e^\prime$ which includes all labels that have a single voxel within $t_{low}$ nanometers from $e$.
-This first pass often includes too many candidates that should not merge so we apply an additional pass to prune these sets.
+In the first pass, we iterate over all endpoints $e$ belonging to a segment $S$ and create a set of segments $\mathbb{S}_e^\prime$ that includes all labels that have a single voxel within $t_{low}$ voxels from $e$.
+Elements of these sets are candidates for merging.
+However the first pass often has too many candidates that should remain split so we apply an additional pass for further pruning.
 In the second pass, we consider all of the segments $\mathbb{S}_e^\prime$ for every endpoint $e$. 
-If a segment $S^\prime \in \mathbb{S}_e^\prime$ has an endpoint within $t_{high}$ nanometers of $e$, the segment $S$ and $S^\prime$ are considered for merging. 
+If a segment $S^\prime \in \mathbb{S}_e^\prime$ has an endpoint within $t_{high}$ voxels of $e$, the segment $S$ and $S^\prime$ are considered for merging. 
 We store the midpoint between the two endpoints as the ``center" of the potential merge.
 Algorithm (ADD REF) provides pseudocode for this edge generation algorithm.
-The results in this paper follow from $t_{low} = 240$ and $t_{high} = 600$.
 
@@
 
-Note that the above algorithm does not enforce any segment adjacency constraints.
-Figure (ADD FIGURE) shows two examples that would not be considered in previous research since they are not adjacent.
-Finding and merging these examples is one of the benefits of retreating from per-pixel algorithms.
+Note that this algorithm does not enforce any segment adjacency constraints.
+Figure (ADD FIGURE) shows two examples that would not be considered in NeuroProof or GALA since these algorithms only consider merging adjacent segments.
 
@@
 
-\begin{figure*}[t]
-	\centering
-	\includegraphics[width=0.3\linewidth]{./figures/network_distance_400.png}
-	\includegraphics[width=0.3\linewidth]{./figures/network_distance_600.png}
-	\includegraphics[width=0.3\linewidth]{./figures/network_distance_800.png}	
-	\caption{The white outlines show three different possible cubic sizes to input into the neural network.
-The left example ($800\textrm{nm}$) provides less local context than the middle example ($1200\textrm{nm}$).
-The right example ($1600\textrm{nm}$) extracts too large of a local region that produces noise as one of the segments leaves the bounding box only to reenter.}
-	\label{fig:network-radius}
-\end{figure*}
-
-The above skeletonization algorithm produces 3-D locations that require further consideration for merging. 
-To determine which of these segments should actually merge, we train a 3-D convolutional neural network. 
-We extract a cubic region with length $1200\textrm{nm}$ centered at these locations. 
-These cubes will provide the local information for the neural network to predict which neighboring segments belong to the same neuron. 
-A cubic length of $1200\textrm{nm}$ provides enough local shape context for the network without introducing an excessive amount of noise. 
-Figure~\ref{fig:network-radius} shows cubes of lengths $800\textrm{nm}, 1200\textrm{nm},$ and $1600\textrm{nm}$.
+Our graph generation algorithm produces 3-D locations that require further consideration for merging. 
+To determine which of these segments should actually merge, we train a 3-D CNN using the oversegmentation and the corresponding manually labeled ground truth data (Section~\ref{sec:dataset}).
+We extract a cubic region of interest around these locations as input to the CNN. 
+These regions of interests will provide the local information for the neural network to predict which neighboring segments belong to the same neuron.
 
@@
 The network takes three input channels for each voxel in the 3-D volume corresponding to the following mapping. 
-Consider a pair of segments with labels $l_1$ and $l_2$ for every voxel $v$ in the cube of interest. 
+Consider a pair of segments with labels $l_1$ and $l_2$ for every voxel $v$ in the region of interest. 
 The first channel is $0.5$ if $v = l_1$ and $-0.5$ otherwise, the second channel is $0.5$ if $v = l_2$ and $-0.5$ otherwise, and the third channel is $0.5$ if $v = l_1$ or $v = l_2$ and $-0.5$ otherwise.
@@
 
-Our network architecture has three layers of double convolutions followed by a max pooling step \cite{chatfield2014return}. 
-As described above, the input with into the network is $(22, 68, 68)$ with $3$ channels. 
-The filter size of the layers are 16, 32, and 64 with size doubling deeper into the network. 
-The first two max pooling layers are anisotropic with pooling only in $x$ and $y$ to match the anisotropic nature of our EM datasets. 
-All convolutions have kernel sizes of $(3, 3, 3)$. 
-The output size of the final max pooling layer is $(5, 5, 5)$ with $64$ channels. 
-The output is flattened into a 1-D vector with $8000$ entries which enters two fully connected layers with $512$ and $1$ dimensions in the output respectively. 
-All activation functions are LeakyReLU with $\alpha=0.001$ except for the final activation which uses a sigmoid function~\cite{funahashi1989approximate,maas2013rectifier}. 
-There is a dropout of $0.2$ after every pooling layer and the first dense layer. 
-There is a dropout of $0.5$ after the final dense layer. 
-The above method uses stochastic gradient descent with Nesterov's accelerated gradient~\cite{nesterov1983method}. 
-This optimizer has an initial learning rate of $0.01$, momentum of $0.9$, and a decay rate of $5*10^{-8}$. Figure~\ref{fig:architecture} provides an overview of the proposed architecture.
+Figure~\ref{fig:architecture} provides an overview of our architecture. 
+Our network architecture has three layers of double convolutions followed by a max pooling step following the work of Chatfield et al.
+that found such a framework improves on single convolution layers~\cite{chatfield2014return}.
+The first two max pooling layers are anisotropic with pooling only in the $x$ and $y$ dimensions to account for the anisotropic nature of the datasets.
+The output after this final pooling step is flattened into a 1-D vector which is input into two fully connected layers.
+The final layer produces a probability with a sigmoid activation function~\cite{funahashi1989approximate}. 
+All of the other activation functions are LeakyReLU~\cite{maas2013rectifier}. 
+We use a stochastic gradient descent optimizer with Nesterov's accelerated gradient~\cite{nesterov1983method}. 
+There are dropouts of $0.2$ after every pooling layer and the first dense layer, and a dropout of $0.5$ after the final dense layer. 
+This prevents overfitting of the training data.
 
@@
 
-\subsubsection{Data Augmentation}
-
-We apply some data augmentation to the generated examples to increase the size of the training datasets. 
-We consider all rotations of $90$ degrees along the $xy$-plane in addition to mirrors along the $x$ and $z$ axes. 
-This produces an additional 16 times more training data.
-
 \subsection{Agglomeration}
 
-After constructing the above graph structure we can apply a graph-based segmentation strategy. 
+After constructing the graph structure we apply a graph-based segmentation strategy. 
 There are many formulations of graph-based optimization strategies that provide different guarantees on their output. 
@@
 Current connectomics agglomeration techniques do not leverage this additional information but rather consider neighboring regions in successive order without regard to loop creation. 
-In our graph formulation we can enforce this topological property by applying a multicut partition onto the graph which generates a forest on the nodes. 
+In our graph formulation we enforce this topological property by applying a multicut partition onto the graph that generates a \textit{forest} on the nodes. 
+A forest is a partitioning of a graph into a set of trees (i.e. no segment has a cycle). 
 There are several heuristics that solve the multicut problem. For our purposes we use the Kernighan-Lin algorithm~\cite{kernighan1970efficient}.
+The running time of this algorithm is $\mathcal{O}(N^3)$, where $N$ is the number of nodes in the graph (DOUBLE CHECK).

### 2017-11-06 papers/cvpr2018/3_evaluation.tex
Major changes to method

@@
 \subsection{Datasets}
-
+\label{sec:dataset}
 \subsubsection{Kasthuri}
@@
 \subsubsection{Segmentation Pipeline and Baseline}
-
+\label{sec:neuroproof}
 Our algorithm takes the output of a supervoxel based agglomeration strategy such as NeuroProof or GALA.
@@
 At best, these segments waste time and at worst they lead to incorrect merges.
-
+%TODO: The results in this paper follow from \$t\_\{low\} = 240\$ and \$t\_\{high\} = 600\$.
 \subsection{Classifier Training}
@@
 Table \ref{table:architecture} provides the final network parameters.
+%TODO: why do we use 1200nm
+%TODO: A cubic length of $1200\textrm{nm}$ provides enough local shape context for the network without introducing an excessive amount of noise. 
+%TODO: Figure~\ref{fig:network-radius} shows cubes of lengths $800\textrm{nm}, 1200\textrm{nm},$ and $1600\textrm{nm}$.
+
+%TODO: The filter size of the layers are 16, 32, and 64 with size doubling deeper into the network. 
+%TODO: All convolutions have kernel sizes of $(3, 3, 3)$. 
+%TODO: The output size of the final max pooling layer is $(5, 5, 5)$ with $64$ channels. 
+%TODO: This optimizer has an initial learning rate of $0.01$, momentum of $0.9$, and a decay rate of $5*10^{-8}$.
 
@@
 \paragraph{Data Augmentation.}
-We apply some data augmentation to the generated examples to increase the size of the training datasets. 
-We consider all rotations of $90$ degrees along the $xy$-plane in addition to mirrors along the $x$ and $z$ axes. 
-This produces an additional 16 times more training data.
+We apply data augmentation to the generated examples to increase the size of the training datasets. 
+We consider all rotations of $90$ degrees along the $xy$-plane in addition to mirroring along the $x$ and $z$ axes. 
+This produces 16 times more training data.
 

### 2017-11-06 algorithms/multicut.pyx
multicut: changed standard output

@@ -37,10 +37,7 @@ def CollapseGraph(segmentation, candidates, collapsed_edges, probabilities):
 
     # output the results for multicut
     PrecisionAndRecall(ground_truth, predictions)
-    
-    #import sys
-    #sys.exit()
-    
+
     # create an empty union find data structure
     max_value = np.uint64(np.amax(segmentation) + 1)
     union_find = [unionfind.UnionFindElement(iv) for iv in range(max_value)]

### 2017-11-06 cnns/skeleton/generate_features.py

@@ -40,7 +40,7 @@ def SaveCandidates(output_filename, positive_candidates, negative_candidates, in
             negative_candidates = negative_candidates[negative_threshold:]
 
             
-        # get the minimum length of the two candidates - train in pairs
+        # get the maximum length of the two candidates - train in pairs
         npoints = max(len(positive_candidates), len(negative_candidates))
         positive_index = 0
         negative_index = 0

### 2017-11-06 papers/cvpr2018/2_method.tex

@@
 From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with weights $w_e$. 
-The nodes correspond to label segments from the segmentation and the edges between segments considered for merging.
+The nodes correspond to label segments from the segmentation with edges between segments considered for merging.
 Ideally, our graph has edges corresponding to all of the segments which were erroneously split with few edges between correctly split segments.
@@
 
-We transform the extracted cubes for input into the neural network. 
-The network takes three input channels for each voxel in the 3-D volume corresponding to the following mapping. 
-Consider a pair of segments with labels $l_1$ and $l_2$ for every voxel $v$ in the region of interest. 
-The first channel is $0.5$ if $v = l_1$ and $-0.5$ otherwise, the second channel is $0.5$ if $v = l_2$ and $-0.5$ otherwise, and the third channel is $0.5$ if $v = l_1$ or $v = l_2$ and $-0.5$ otherwise.
-Each 3-channel volume is subsequently downsampled into an array of size $(3, 22, 68, 68)$ using nearest-neighbor interpolation. 
-Our neural network trains on these 4-D arrays to generate probabilities that $l_1$ and $l_2$ should merge.
+The networks receives three input channels for every voxel in the region of interest around segments $l_1$ and $l_2$. 
+The input to all of the channels is in the set $\{-0.5, 0.5\}$. 
+The first channel is $0.5$ only if the corresponding voxel has label $l_1$. 
+The second channel is $0.5$ only if the corresponding voxel has label $l_2$. 
+The third channel is $0.5$ if the corresponding voxel is either $l_1$ or $l_2$.
 

### 2017-11-06 papers/cvpr2018/paper.tex

--- 2017-10-21 papers/cvpr2018/paper.tex
@@
 %%%%%%%%% TITLE
-\title{Robust Agglomeration of Labeled Neurons using 3D Skeletonization}
+\title{Graph-based Neuron Agglomeration using 3D Skeletons}
+
+%Robust Agglomeration using 3D Skeletonization of Labeled for Connectomics}
 
@@
 \begin{abstract}
-THE ABSTRACT
+Advancements in electron microscopy image acquisition have created massive connectomics datasets which are petabytes in size and make manual segmentation not feasible. 
+Proposed methods for automatic segmentations generate super-pixel approximations of neural membranes followed by agglomeration strategies to create full neuron reconstructions. 
+However, pixel-based segmentation results widely neglect global geometric properties.
+We generate skeletons of membrane labels to approximate neural pathways in 3D.
+This allows us to efficiently apply graph-based optimization strategies and to train automatic classifiers for shape description against manually labeled ground truth.
+Our classifiers detect feasible and impossible neural pathways by looking at geometric properties alone, and are able to improve the segmentation labels accordingly.
+We demonstrate the performance of our classifiers on multiple real-world connectomics datasets with average variation of information improvement of $X\times$.
+We discuss our findings and provide insights to learning shape features for neuron agglomeration.
 \end{abstract}

### 2017-11-06 papers/cvpr2018/1_related_work.tex
Added overview of existing methods figure

@@
 \section{Related Work}
+
+\begin{figure*}[!ht]
+	\centering
+	\includegraphics[width=0.22\linewidth]{./figures/pipeline/image.png}
+	\hspace{0.025\linewidth}
+	\includegraphics[width=0.22\linewidth]{./figures/pipeline/affinities.png}
+	\hspace{0.025\linewidth}
+	\includegraphics[width=0.22\linewidth]{./figures/pipeline/watershed.png}
+	\hspace{0.025\linewidth}
+	\includegraphics[width=0.22\linewidth]{./figures/pipeline/neuroproof.png}
+	\caption{An overview of the existing methods.
+On the left is the original EM image data.
+A neural network (here VD2D3D) predicts the affinities between neighboring voxels.
+The Zwatershed algorithm clusters these voxels into supervoxels.
+NeuroProof agglomerates these supervoxels to create larger segments.}
+	\label{fig:pipeline}
+\end{figure*}
 

### 2017-11-08 papers/cvpr2018/3_evaluation.tex
paper: added in Toufiq edits

@@
 \label{sec:neuroproof}
-Our algorithm takes the output of a supervoxel based agglomeration strategy such as NeuroProof or GALA.
-For our experiments we use the output from NeuroProof (CITE).
-We generate voxel affinities from the raw image data using the U-Net architecture \cite{ronneberger2015u}.
-The Zwatershed algorithm (CITE) creates an oversegmentation of the neurons given these voxel affinities.
-We input the raw image data, the voxel affinities, and the oversegmentation into NeuroProof which performs a hierarchical agglomeration strategy to merge the supervoxels into larger and larger segments.
-Two neighboring segments receive a merge-likelihood score based on various extracted features such as the distribution of affinities along the segment boundary.
-A random forest classifier generates probabilities based on these features.
-(TODO: TOUFIQ ADD HERE)
+The segmentation on [Cite Kasthuri Cell2015] dataset was computed by agglomerating 3D supervoxels produced by zwatershed [Cite Zlatesky arXiv2015] from 3D affinity predictions. 
+A recent study by Funke et.al. [Funke arXiv2017] demonstrated superior performance of such method over existing ones on anisotropic data. 
+We learned 3d affinities in x,y,z using MALIS [Cite Turaga, NIPS 2009] loss with a U-net [Ronneberger, MICCAI 2015]. 
+We apply the zwatershed algorithm, with suitable parameters, to compute an 3D over-segmentation of the volume. 
+The resulting 3D over-segmentation is then agglomerated using the technique of [Parag, Plos One 2015] to generate the final segmentation.
+The VI values at different stopping thresholds of agglomeration correspond to the points on the curve plotted in Figure YYY.
+
+We have collected two 1000x1000x1000 voxel (10x10x10 um) volumes from the authors of [Takemura, elife 2017]. 
+Based on the authors' suggestion, we applied the algorithm of [Parag, ICCV 2015] that showed improved performance on this dataset than the pipeline used in [Takemura, elife2017]. 
+The segmentation framework of [Parag, ICCV 2015] learns voxel and supervoxel classifier with an emphasis to minimize under-segmentation error and, at the same time, is capable of producing lower over-segmentation that standard algorithms.
+This algorithm first computes a multi-channel 3D predictions for membrane, cell interior, mitochondria, etc. 
+The membrane prediction channel is utilized to produce an over-segmented volume by 3D watershed, which is then agglomerated hierarchically up to a certain confidence threshold. 
+We used exactly same parameters for the publicly available code for this algorithm and used different agglomerations thresholds to plot the VI error curve.
 

### 2017-11-08 papers/cvpr2018/3_evaluation.tex
paper: Major improvements to evaluation

--- 2017-11-06 papers/cvpr2018/3_evaluation.tex
@@
 
-We evaluate our proposed methods on two different connectomics datasets, one anisotropic and the other isotropic, from two different species.
+We evaluate our schema on two different connectomics datasets, one anisotropic and the other isotropic, from two different species.
 
 \subsection{Datasets}
+\label{sec:dataset}
+\paragraph{Kasthuri.}
+The Kasthuri dataset images the neocortex of a mouse brain produced by a scanning electron microscope \cite{kasthuri2015saturated}. 
+This dataset is $5342 \times 3618 \times 338$ voxels in size. 
+The resolution of the dataset is $\SI[product-units=single]{3 x 3 x 30}{\nano\meter}^3$ per voxel. 
+We evaluate our methods using the left cylinder of this 3-cylinder dataset. 
+We downsample the dataset in the $x$ and $y$ dimensions to give a final resolution of $\SI[product-units=single]{6 x 6 x 30}{\nano\meter}^3$ per voxel. 
+We divide the dataset into two volumes along the $x$ dimension.
+Thus, each volume is $\SI[product-units=single]{8.0 x 10.9 x 10.1}{\micro\meter}^3$.
 
-\subsubsection{Kasthuri}
-The Kasthuri dataset images the neocortex of a mouse brain produced by a scanning electron microscope \cite{kasthuri2015saturated}. 
-This dataset is $338 \times 3618 \times  5342$ voxels in size. 
-The resolution of the dataset is $3 \times 3 \times 30 \textrm{nm}^3$. 
-We evaluate our methods using the left cylinder of this 3-cylinder dataset.
-
-\subsubsection{FlyEM}
-
+\paragraph{FlyEM.}
 The FlyEM dataset comes from the mushroom body of a 5-day old adult male \textit{Drosophila} fly imaged by a focused ion-beam milling scanning electron microscopy.  
 The mushroom body is this species is the major site of associative learning \cite{takemura2017connectome}. 
-The original dataset contains a $40 \mu\textrm{m} \times 50\mu\textrm{m} \times 120\mu\textrm{m}$ volume of which we use two subsections of size $1000 \times 1000 \times 1000$ voxels.  
-The resolution of this dataset is $10 \times 10 \times 10 \mu\textrm{m}^3$ per voxel. 
-The image data and the accompanying ground truth is available (CITE).
+The original dataset contains a $\SI[product-units=single]{40 x 50 x 120}{\micro\meter}^3$ volume of which we use two cubes of size $\SI[product-units=single]{10 x 10 x 10}{\micro\meter}^3$. 
+The resolution of this dataset is $\SI[product-units=single]{10 x 10 x 10}{\nano\meter}^3$ so each volume has $1000$ voxels in each dimension.
 
-\subsubsection{Segmentation Pipeline and Baseline}
+\paragraph{Segmentation Pipeline and Baseline.}
+\label{sec:neuroproof}
+The segmentation on the Kasthuri dataset was computed by agglomerating 3D supervoxels produced by zwatershed from 3D affinity predictions~\cite{zlateski2015image}. 
+A recent study by Funke et.al. demonstrated superior performance of such method over existing ones on anisotropic data \cite{schlegel2017learning}. 
+We learned 3d affinities in x,y,z using MALIS loss with a U-net~\cite{Turaga:2009,ronneberger2015u}. 
+We apply the zwatershed algorithm, with suitable parameters, to compute an 3D over-segmentation of the volume. 
+The resulting 3D over-segmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}. 
+The VI values at different stopping thresholds of agglomeration correspond to the points on the curve plotted in Figure YYY.
 
-Our algorithm takes the output of a supervoxel based agglomeration strategy such as NeuroProof or GALA.
-For our experiments we use the output from NeuroProof (CITE).
-We generate voxel affinities from the raw image data using the U-Net architecture \cite{ronneberger2015u}.
-The Zwatershed algorithm (CITE) creates an oversegmentation of the neurons given these voxel affinities.
-We input the raw image data, the voxel affinities, and the oversegmentation into NeuroProof which performs a hierarchical agglomeration strategy to merge the supervoxels into larger and larger segments.
-Two neighboring segments receive a merge-likelihood score based on various extracted features such as the distribution of affinities along the segment boundary.
-A random forest classifier generates probabilities based on these features.
-(TODO: TOUFIQ ADD HERE)
+We have collected two $1000 \times 1000 \times 1000$ voxel ($\SI[product-units=single]{10x10x10}{\micro\meter}^3$) volumes from the authors~\cite{takemura2017connectome}. 
+Based on the authors' suggestion, we applied the context-aware delayed agglomeration algorithm~\cite{10.1371/journal.pone.0125825} that shows improved performance on this dataset than the pipeline used in the original publication.
+This segmentation framework learns voxel and supervoxel classifiers with an emphasis to minimize under-segmentation error.
+At the same time this framework produces lower over-segmentation than standard algorithms. 
+This algorithm first computes multi-channel 3D predictions for membranes, cell interiors, and mitochondria, among other cell features. 
+The membrane prediction channel is utilized to produce an over-segmented volume using 3D watershed, which is then agglomerated hierarchically up to a certain confidence threshold. 
+We used exactly same parameters for the publicly available code for this algorithm and used different agglomerations thresholds to plot the VI error curve.
 
-\subsection{Skeleton Pruning}
+\subsection{Pruning via Skeletonization}
 
-Our method prunes potential merge candidates by considering the skeleton as a simplification of the segment shape.
-Segment skeletons that have nearby endpoints are merge candidates.
-The underlying assumption in this model is that the segments break in a particular fashion, primarily perpendicular to the direction of travel (CONFUSING).
-We perform a series of experiments to evaluate the effectiveness of this idea.
-First, we examine how many merge candidates are not considered using our method that would have been if we employed the strategy of considering all neighboring segments.
-These are locations that we cannot possibly correct and therefore we want this number to be as low as possible.
-The second experiment considers how many locations are not considered that should not be merged.
-We want this number to be as large as possible since we want to avoid making mistakes by merging these segments.
-At best, these segments waste time and at worst they lead to incorrect merges.
+We prune potential merge candidates by running Algorithm \ref{alg:skeletonization} on the input dataset. 
+There are two essential parameters to the algorithm: $t_{low}$ and $t_{high}$. 
+Ideally, the merge candidates output by this algorithm will contains all possible positive examples with a very limited number of negative examples. 
+After considering various thresholds, we find that $t_{low} = \SI{240}{\nano\meter}$ and $t_{high} = \SI{600}{\nano\meter}$ produces the best results given this objective function. 
+Note that these thresholds are in nanometers and not voxels. 
+Connectomics datasets often have different sample resolutions and downsampling in $z$. 
+Using nanometers allows us to have uniform units across all of these datasets and calculate the thresholds in voxels at runtime. 
+The thresholds are $t_{low} = (40, 40, 8)$ voxels and $t_{high} = (100, 100, 20)$ voxels for the Kasthuri dataset $t_{low} = (24, 24, 24)$ voxels and $t_{high} = (60, 60, 60)$ voxels for the FlyEM dataset.
+The thresholds are anisotropic or isotropic depending on the corresponding isotropy of the dataset.
+Table \ref{table:skeletonization} shows the overall success of this method of candidate pruning.
+
+\begin{table}
+	\centering
+	\begin{tabular}{c c c c}
+		Dataset & Adjacency Strategy & Applying $t_{low}$ & Applying $t_{high}$ \\ \hline
+		Kasthuri Vol. 1 & & & \\
+		Kasthuri Vol. 2 & & & \\
+		FlyEM Vol. 1 & & & \\
+		FlyEM Vol. 2 & & & 
+	\end{tabular}
+	\caption{The results of the pruning algorithm compared to the previous approach of considering all adjacent segments.}
+	\label{table:skeletonization}
+\end{table}
+
+TODO FINISH TABLE + DO I ADD IN FIGURE TO SHOW CHANGE OVER THRESHOLDS?
 
@@
 
-We divide both datasets into half to train the classifier.
-We generate all valid examples for merge consideration based on the skeletonization algorithm.
-In the training dataset, $80\%$ of the examples are used for training and the remaining examples are used for validation.
-To start, we consider networks of varying sizes, optimization functions, and loss functions.
-The supplemental material has additional information concerning the tuning of the network.
-There are XXX,XXX learnable parameters in our final architecture.
-The training ran for XX epochs.
-Table \ref{table:architecture} provides the final network parameters.
+We use the Kasthuri Vol. 1 dataset for training and validation. 
+We train on 80\% of the potential merge candidates for this volume.
+The validation the neural network classifier on the remaining 20\% of candidates. 
+We consider networks with varying input sizes, optimizers, loss functions, filter sizes, learning rates, and activation functions. 
+The supplemental material includes information on the experiments that determined these final parameters. 
+Table \ref{table:architecture} provides the parameters in the final network.
+There are 7,294,705 learnable parameters in our final architecture.
+All the parameters are randomly initialized following the Xavier uniform distribution~\cite{glorot2010understanding}. 
+Training concluded after 34 epochs.
 
@@
 	\end{tabular}
-	\caption{The parameters for the trained neural network.}
+	\caption{Parameters for the CNN}
 	\label{table:architecture}
@@
 
-Most current agglomeration strategies in connectomics consider all pairs of neighboring segments.
-A classifier produces a probability that each pair belongs to the same segment.
-All segment pairs with a probability above a certain threshold are merged together.
-Consider the simple example in Figure \ref{fig:multicut}.
-Under the existing agglomeration schemes this entire graph would become one segment.
-However multicut eliminates all cycles within the graph creating two unique segments.
-We compare our results using both the traditional hierarchical agglomeration strategy with the graph-based approach we propose.
+Applying a top-down globally optimal partitioning function allows us to enforce some domain-specific constraints on the reconstruction.
+In connectomics, we want to enforce the topological restrictions that each partition in the graph has a genus of zero. 
+The greedy-additive heuristic solves the multicut graph partitioning problem by enforcing this constraint.
+Previous agglomeration strategies at the per-region level consider neighboring superpixels in order of merge probability. 
+These superpixels are clustered hierarchically without concern for global constraints.
+We compare the benefits of a top-down partitioning function versus the traditional bottom-up clustering methods.
 
@@
 
-We use the variation of information metric to determine the accuracy of our pipeline.
-The variation of information measures the distance between two segmentations and is similar to mutual information.
-A lower variation of information score corresponds to a segmentation closer to the ground truth.
-(TODO: TOUFIQ ADD HERE)
-
-%We evaluate our method on two different connectomics datasets of different species.
-
-%\subsection{Datasets}
-
-%\subsubsection{Kasthuri}
-
-%The first dataset is the left part of the mouse cortex volume of Kasthuri et al.
-(CITE).
-We divide the dataset into a training and validation half and a testing half.
-The dataset resolution is $3 \times 3 \times 30 \textrm{nm}^3/\textrm{voxel}$.
-
-%\subsubsection{FlyEM}
-
-%We evaluate our methods on three EM datasets. 
-%TODO: Toufiq: add description of the EM datasets (volume size, resolution, type of animal, type of image scan)
-
-%\subsubsection{NeuroProof Pipeline}
-%\label{sec:neuroproof}
-%Our methods build on top of existing agglomeration strategies. For the purpose of this paper we used the outputs from two established pipelines. 
-%TODO: Toufiq description of neuroproof pipeline, description of FlyEM pipeline
-
-%\subsection{Preprocessing}
-
-%We perform significant pruning of potential merge candidates by considering only pairs of skeleton endpoints produced by Algorithm \ref{alg:generate-edges}.
-This strategy greatly reduced the number of false merge candidates that we considered.
-However, we evaluate the overall effectiveness of this strategy both in reducing trivial split candidates while maintaining a large majority of the candidates which should merge.
-
-%Our candidate generation strategy doesn't enforce an adjacency constraint which allows us to merge candidates that are not consider under existing frameworks.
-We examine the success of our pipeline in merging said candidates.
-
-%\subsection{Classifier Training}
-
-%DISCUSS PARAMETERS FOR CLASSIFICATION
-
-%\subsection{Graph Optimization}
-
-%We evaluate the improvement of using a graph optimization strategy over a na\"ive approach that performs hierarchical clustering for all segments above a certain threshold.
-%Using a heuristic for multicut prevents the creation of cycles. 
-%Using a simple agglomeration strategy generates this many cycles.
+We evaluate the performance of our methods using the split version of the variance of information~\cite{meila2003comparing}. 
+Consider a ground truth labeling $GT$ and our automatically reconstructed segmentation $SG$. 
+Over and undersegmentation are quanitified by the conditional entropy $H(GT | SG)$ and $H(SG | GT)$ respectively. 
+Since we are measuring the entropy between two clusterings, better split variation of information scores are closer to the origin.

### 2017-11-09 papers/cvpr2018/3_evaluation.tex
updated results section on skeleton pruning

@@
 Table \ref{table:skeletonization} shows the overall success of this method of candidate pruning.
-
-\begin{table}
-	\centering
-	\begin{tabular}{c c c c}
-		Dataset & Adjacency Strategy & Applying $t_{low}$ & Applying $t_{high}$ \\ \hline
-		Kasthuri Vol. 1 & & & \\
-		Kasthuri Vol. 2 & & & \\
-		FlyEM Vol. 1 & & & \\
-		FlyEM Vol. 2 & & & 
-	\end{tabular}
-	\caption{The results of the pruning algorithm compared to the previous approach of considering all adjacent segments.}
-	\label{table:skeletonization}
-\end{table}
-
-TODO FINISH TABLE + DO I ADD IN FIGURE TO SHOW CHANGE OVER THRESHOLDS?
 

### 2017-11-09 papers/cvpr2018/4_results.tex
paper: added in Toufiq edits
updated results section on skeleton pruning

@@
 
-\subsection{Skeleton Pruning}
+\subsection{Pruning via Skeletonization}
 
-\paragraph{Finding Positive Examples.}
+\begin{table}
+	\centering
+	\small
+	\begin{tabular}{c c c} \hline
+		\textbf{Dataset} & \textbf{Baseline} & \textbf{After Pruning} \\ \hline
+		Kasthuri Vol. 1 & 763 / 21242 (3.47\%) & 753 / 3459 (17.88\%) \\
+		Kasthuri Vol. 2 & 1010 / 26073 (3.73\%) & 904 / 4327 (17.28\%) \\
+		FlyEM Vol. 1 & 269 / 14875 (1.78\%) & 262 / 946 (21.69\%) \\
+		FlyEM Vol. 2 & 270 / 16808 (1.58\%) & 285 / 768 (27.07\%)\\ \hline
+	\end{tabular}
+	\caption{The results of our pruning heuristic compared to the current baseline.}
+	\label{table:skeletonization}
+\end{table}
 
-As a baseline, we consider all pairs of segments that have neighboring voxels and see what percent of these segments are considered for merging.
-In the L.
-Cylinder dataset, there are XXX neighboring segments which have at least adjacent voxels.
-Our method which uses skeletons to prune the considered candidates finds XXX of these segments, or XX\% percent.
-On the FlyEM dataset, there are XXX adjacent segments with XXX found (XX\% percent).
-Figure \ref{fig:skeleton-results} shows some of the missed examples.
-The most common errors are the dendrite spines where the larger segment did not have an endpoint near the split.
-However, our algorithm does not require segments to be adjacent to merge.
-This offers a great benefit compared to traditional methods.
-In our datasets XXX and XXX segments are candidates for merging despite not having adjacent voxels.
-Figure \ref{fig:skeleton-results} gives one such pair which is merged given the results of our algorithm.
+Table \ref{table:skeletonization} shows the results of pruning using the skeletonization heuristic.
+The baseline algorithm considers all adjacent regions for merging. 
+Our method removes a significant portion of these candidates while maintaining a large number of the true merge locations.
+This edge pruning is essential for the graph partitioning algorithms which have a computational complexity dependence on the number of edges (CHECK). 
+Our pruning heuristic removes at least $6\times$ the number of edges between correctly split segments on all datasets, achieving a maximum removal ratio of $20\times$. 
+Equally important is the number of split errors that remain after pruning.
+These are the locations that we want to merge to create a more accurate reconstruction.
+For every dataset, the number of positive candidates remains relatively even. 
+However, since our heuristic does not enforce an adjacency constraint of two regions when constructing edges in the graph, the difference does not indicate the number of examples excluded by pruning. 
+In fact, our method finds a number of examples which are non-adjacent.
+Figure \ref{fig:skeleton-results} shows two example segments which are split errors.
+The top example our algorithm missed but the segments are adjacent. 
+The bottom example our algorithm found despite the fact that they are not adjacent.
 
-\paragraph{Pruning Negative Examples.}
-
-Traditional agglomeration strategies consider a large number of negative candidates that we hope to prune.
-The original approach of considering adjacent supervoxels has XX,XXX and XX,XXX candidates which do not belong to the same neuron.
-With our pruning algorithm, this reduces to X,XXX and X,XXX, a factor of over XX times.
-This allows a more reasonable training environment with greater balance between the positive and negative merge examples.
-
-\begin{figure}[t]
+\begin{figure}[t!]
 	\centering
-	\includegraphics[width=0.42\linewidth]{./figures/merge_candidate1.png}
-	\hspace{0.085\linewidth}
-	\includegraphics[width=0.42\linewidth]{./figures/merge_candidate2.png}
-	\caption{Two erroneously split segments that should merge together. Most segments that we want to merge have the same general structure.}
+	\includegraphics[width=0.85\linewidth]{./figures/merge_candidate1.png}
+	\includegraphics[width=0.85\linewidth]{./figures/merge_candidate2.png}
+	\caption{Example merge candidates.}
 	\label{fig:skeleton-results}
@@
 \subsection{Classification Performance}
+
+\begin{table}
+	\centering
+	\begin{tabular}{c c c c} \hline
+	\textbf{Dataset} & \textbf{Precision} & \textbf{Recall} & \textbf{Accuracy} \\ \hline
+	Kasthuri Training & & & \\
+	Kasthuri Testing & & & \\
+	FlyEM Vol. 1 & & & \\
+	FlyEM Vol. 2 & & & \\ \hline
+	\end{tabular}
+	\caption{Precision and recall for the training and three test datasets.}
+	\label{fig:classification}
+\end{table}
 

### 2017-11-09 papers/cvpr2018/supplemental/skeletonization.tex
Add supplemental material template.

\section{Skeletonization}

more details regarding the skeletonization approach, which I believe was extra fast?

\subsection{Parameters}

\subsection{Performance Tests}

### 2017-11-10 papers/cvpr2018/paper.tex
paper: Major improvements to evaluation
Add supplemental material template.
added some figures

@@
 \usepackage{algorithmicx}
+\usepackage{siunitx}
 
@@
 
-\def\cvprPaperID{446} % *** Enter the CVPR Paper ID here
+\def\cvprPaperID{0446} % *** Enter the CVPR Paper ID here
 \def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
@@
 %\thispagestyle{empty}
+
+\begin{figure}[t]\footnotesize
+	\vspace{-2.04in}
+	\newcommand{\FigureWidth}{0.23\textwidth}
+	\newcommand{\FigureShift}{\hspace{-0.42cm}}
+	\newcommand{\figureShift}{\hspace{-0.3cm}}
+	\begin{minipage}{\textwidth}
+		\begin{center}
+			\begin{tabular}{cccc}
+				\FigureShift \includegraphics[width=\FigureWidth]{figures/schema/teaser-image.png} \includegraphics[width=\FigureWidth]{figures/schema/teaser-segmentation.png} &
+				\FigureShift \includegraphics[width=\FigureWidth]{figures/schema/pre-multicut.png} &
+				\FigureShift \includegraphics[width=\FigureWidth]{figures/schema/multicut-graph.png}&
+				\FigureShift \includegraphics[width=\FigureWidth]{figures/schema/post-multicut.png}\\
+				\figureShift (a) Input & \FigureShift (b)  Our results & \FigureShift(c) Dark channel of (a) & \FigureShift (d) Dark channel of (b)\\
+			\end{tabular}
+		\end{center}
+		\vspace{-3mm}
+		\caption{Deblurring result on a challenging low-light image.
+The blur process makes the dark channel of the blurred image less sparse~(c).
+Enforcing sparsity on the dark channel of the recovered image favors clean images over blurred ones.}
+		\label{fig:teaser}
+		%
+	\end{minipage}
+\end{figure}
 

### 2017-11-10 papers/cvpr2018/0_introduction.tex
added some figures
paper: majors updates to intro/related works/conclusion

--- 2017-11-06 papers/cvpr2018/0_introduction.tex
@@
 Recent advancements in image acquisition using multi-beam serial-section electron microscopy (sSEM) has allowed neuroscientists to produce terabytes of electron micrsocopy (EM) image data every hour~\cite{hildebrand2017whole}.
-Neuroscientists believe that reconstructing an entire mammilian brain at fine resolution will enable new insights into the workings of the brain~\cite{kasthuri2015saturated}. 
-These observations will allow for new advancements in neuromedicine and artificial intelligence (CITE). 
-Segmentation is part of this reconstruction process, assigning a unique label for every neuron in the EM image.
+Neuroscientists believe that reconstructing an entire mammalian brain at fine resolution will enable new insights into the workings of the brain~\cite{kasthuri2015saturated}. 
+These observations will allow for new advancements in neuromedicine and artificial intelligence.
+
+Segmenting the image stack into a label volume is a substantial component of this reconstruction process.
+In a label volume, every voxel receives a segment label corresponding to a unique neuron. 
+Voxels with the same label belong to the same neuron.
 It is not feasible for domain experts to manually segment the vast amount of 3-D image data to model an entire brain.
+Here we introduce a scalable top-down segmentation algorithm that also leverages local information.
+The top-down partitioning strategy allows us to apply domain-specific constraints to the segmentation task.
 
-A significant amount of research focuses on automatic reconstruction of the neurons in EM images because of the scope and importance of the problem (ADD REFERENCES).%TODO SEVERAL REFERENCES FOR AUTOMATIC SEGMENTATIONS
-All of these algorithms extract neuronal processes through the 3-D volumes using only the raw image data as input.
+A significant amount of research focuses on automatic reconstruction of the neurons in EM images~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image}.
+%TODO DOUBLE CHECK REFERENCES
+All of these algorithms extract neuronal processes through the 3-D volumes using the raw image data as input.
 Oftentimes, convolutional neural networks (CNNs) predict membrane probabilities or affinities between voxels and apply simple thresholds to agglomerate the voxels into clusters~\cite{lee2015recursive,ronneberger2015u}.
-These \textit{per-voxel} algorithms produce excellent results but currently fall short of complete reconstructions with error rates of approximately $X\%$. %TODO ADD ERROR RATES
+These \textit{pixel-based} algorithms produce excellent results but currently fall short of complete reconstructions with error rates of approximately $X\%$. %TODO ADD ERROR RATES
 
-\begin{figure}
+\begin{figure*}[h!]
 	\centering
-	\includegraphics[width=0.42\linewidth]{./figures/merge_candidate1.png}
-	\hspace{0.085\linewidth}
-	\includegraphics[width=0.42\linewidth]{./figures/intro-cube.png}
-	\caption{We use 3D skeletons to combine neuron labels to full reconstructions.}
-\end{figure}
+	\includegraphics[width=0.22\linewidth]{./figures/pipeline/image.png}
+	\hspace{0.025\linewidth}
+	\includegraphics[width=0.22\linewidth]{./figures/pipeline/affinities.png}
+	\hspace{0.025\linewidth}
+	\includegraphics[width=0.22\linewidth]{./figures/pipeline/watershed.png}
+	\hspace{0.025\linewidth}
+	\includegraphics[width=0.22\linewidth]{./figures/pipeline/neuroproof.png}
+	\caption{An overview of an existing pipeline in segmentation for connectomics.
+From left to right: the original EM image data, the output of a CNN predicting voxel affinities, clustering of the affinities using a watershed algorithm, an agglomeration of the supervoxels into larger segments.}
+	\label{fig:pipeline}
+\end{figure*}
 
-Researches currently address the failures of the per-voxel algorithms by training random-forest classifiers to agglomerate an oversegmentation of voxels~\cite{nunez2014graph} (CITE NEUROPROOF). 
-These classifiers take the output of the per-voxel algorithms as input and generate high-level statistics such as affinity distributions between pixel regions. 
+Researchers currently address the failures of these pixel-based algorithms by training random-forest classifiers to agglomerate an oversegmentation of voxels~\cite{nunez2014graph,10.1371/journal.pone.0125825}.
+These classifiers take the output of the pixel-based algorithms as input and generate high-level statistics such as affinity distributions between pixel regions. 
 Presently, these methods use hand-designed features despite the evidence that machine-learned features perform better~\cite{bogovic2013learned}. 
-These \textit{per-supervoxel} algorithms outperform the per-voxel algorithms but still do not provide the accuracy needed for large scale reconstructions of the brain.
-Additionally, these methods do not fully leverage the wealth of shape information available.
-E.g., it is well known that neurons angle at less than $30$ degrees (CITE).
-%TODO ADD CITATION FOR NEURON SHAPES
+These \textit{region-based} algorithms outperform the pixel-based algorithms but still do not provide the accuracy needed for large scale reconstructions of the brain.
 
-Here we present a \textit{graph-based} strategy that builds on top of the outputs of per-supervoxel methods by taking neuronal shape properties into account. 
-Similarly we take as input automatic segmentations. 
-However, we focus on general neuron shapes, traversing through the label volumes to identify potential merge candidates. 
-From these locations we extract machine-learned features and generate a probability that two label segments should be joined. 
-We construct a graph representation of the input label volume. 
-Using graph-based optimization strategies enables us to enforce global constraints that more closely match the underlying biology of the images.
-Lastly, we apply a global segmentation algorithm to produce a better reconstruction.
+We present a \textit{segment-based} strategy that extends on the outputs of region-based methods.
+We only take as input a segmentation from a previous agglomeration algorithm and not the raw image data. 
+This allows us to train on connectomics datasets at a resolution and image type different than the test datasets.
+We consider the 3-D skeletons of each segments as a simplification of its shape. 
+We can then quickly extract a graph from the input segmentation using the skeletonization of the segments in the volume.
+
+We add edge weights to our graph using a 3-D CNN to predict the probabilities that nearby segments belong to the same neuron.
+Using a graph-based optimization strategy enables us to enforce domain-specific global constraints such as the underlying neuronal biology.
+From here we apply a global partitioning algorithm that minimizes a cost function of separating adjacent nodes in the graph.
+
+Our method takes the output of any bottom-up segmentation strategy and creates a graph on top of this segmentation. 
+We enforce domain-specific global constraints by reasoning at the graph level.
+This strategy scales to massive connectomics datasets and improves accuracy over existing methods.

### 2017-11-10 papers/cvpr2018/1_related_work.tex
paper: majors updates to intro/related works/conclusion

--- 2017-11-06 papers/cvpr2018/1_related_work.tex
@@
 
-\paragraph{Voxel-based methods.} A large amount of connectomics research considers the problem of extracting segmentation information at the voxel level from the raw EM images. 
-Such works focus on training 2-D convolutional neural networks to predict membrane probabilities per image slice~\cite{ciresan2012deep,jain2010boundary,amelio_segmentation,rhoananet,kaynig2015large}. 
-More recent strategies augment these neural networks with the $z$-dimension creating full 3-D convolutional networks~\cite{lee2015recursive}.
-Oftentimes these networks produce probabilities for the affinity between voxels rather than probabilities for a voxel belonging to a cell membrane~\cite{ronneberger2015u}. 
-A sizable amount of computer vision research analyzes various hand-designed shape features for determining similarity between objects~\cite{osada2002shape} and for segmentation\cite{conners1984segmentation}.
-Currently, the random-forest classifiers used in connectomics rely on hand-designed features to make merge decisions.
-Some of these features encode the distribution of probabilities that voxels along a segment boundary belong to the same neuron as their neighbors~\cite{nunez2014graph,ren2003learning}.
-However, there is evidence that machine-learned features outperform hand-designed ones~\cite{bogovic2013learned}.
-An extensive amount of research in computer vision, applied mathematics, and statistics evaluates the loss functions and optimizers for these networks~\cite{chatfield2014return,maas2013rectifier,nesterov1983method}.
+A significant amount of research in computer vision focuses segmentation of images \cite{zaitoun2015survey}. 
+Here, we review some of the most successful methods that have been applied to large-scale EM images.
 
-\paragraph{Super-voxel methods.} These approaches generate probabilities that neighboring voxels belong to the same neuron.
-Many algorithms work at the resulting super-voxel level and train random-forest classifiers to produce segmentations of the EM images where every unique neuron in the volume has a unique label~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image} (CITE NEUROPROOF).
+\paragraph{Pixel-based methods.}
+
+A large amount of connectomics research considers the problem of extracting segmentation information at the voxel level from the raw EM images to produce label volumes.
+Some early techniques apply computationally expensive graph partitioning techniques with a single node per voxel  \cite{andres2012globally}, however these methods do not scale to terabyte datasets.
+Since then, several methods train 2-D CNNs to predict membrane probabilities per image slice~\cite{ciresan2012deep,jain2010boundary,kaynig2015large,rhoananet,amelio_segmentation}. 
+More recent strategies augment these neural networks with the $z$-dimension creating full 3-D CNNs~\cite{lee2015recursive,ronneberger2015u}.
+Oftentimes these networks produce probabilities for the affinity between voxels, i.e., the probability that adjacent voxels belong to the same neuron.
+More recently, flood-filling networks produce segmentations by training an end-to-end neural network that takes EM images to label volumes~\cite{januszewski2016flood}.
+These networks produce very impressive accuracies but are much too slow to scale to larger datasets.
+
+\paragraph{Region-based methods.}
+
+Several of these pixel-based approaches generate probabilities that neighboring voxels belong to the same neuron.
+Many algorithms build on top of these methods and train random-forest classifiers to produce segmentations of the EM images~\cite{seymour2016rhoananet,nunez2014graph,10.1371/journal.pone.0125825,parag2017anisotropic,zlateski2015image}.
 Despite the success of these classifiers, they often make mistakes based on the local information leading to errors in the segmentation. 
-Proofreading methods create a ``human-in-the-loop" framework that allows users to find errors and correct them \cite{haehn2017scalable,haehn2017guided,haehn2014design,error_correction_using_CNN}.
+Additionally, many recent advancements in segmentation use artificial neural networks given the evidence that machine-learned features outperform hand-designed ones~\cite{bogovic2013learned}.
+A significant amount of research focuses on the training and optimization of these deep neural networks~\cite{chatfield2014return,maas2013rectifier,nesterov1983method}.
 
-More recently, flood-filling networks merge the process of generating voxel affinities and then producing segmentations by training an end-to-end neural network that outputs segmentations~\cite{januszewski2016flood}.
-These networks produce impressive segmentation accuracies of over $X\%$.%TODO ADD ACCURACY FOR FLOOD FILLING NETWORKS
-%, they are currently too slow for large scale connectomics reconstructions.
+\paragraph{Segment-based methods.}
 
-\paragraph{Graph-based methods.} Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}.
-The multicut graph partitioning algorithm extracts segments the graph and remove edges such that there are no cycles. 
+Some limited research builds on top of the region-based methods to correct errors in the segmentation \cite{rolnick2017morphological,error_correction_using_CNN}.
+Similarly, proofreading methods create a ``human-in-the-loop" framework that allows users to find errors and correct them \cite{haehn2017scalable,haehn2017guided,haehn2014design}. 
+Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}.
+The multicut graph partitioning algorithm produces a set of segments where no segment contains a cycles.
 This closely resembles the biological constraint that neurons have a topological genus of zero. 
-There are several useful multicut heuristics which provide good approximations with reasonable computational costs~\cite{horvnakova2017analysis,kernighan1970efficient,keuper2015efficient}
-
-\paragraph{Skeletonization methods.} We use a graph-based abstraction of segmentation data based on skeletonizations. 
-This topic is the focus of extensive research in the fields of computer graphics, mathematics, and biomedical visualization.
-%The fields of computer graphics, mathematics, and biomedical visualization produce extensive research into the skeletonization of 3D binary volumes. 
-Some of the research explores topologically consistent thinning algorithms and potential medical applications of these methods~\cite{palagyi20003d,palagyi2001sequential}. 
-In computer graphics, fast medial axis algorithms allow animators to quickly move characters through successive frames~\cite{baran2007automatic,bharaj2012automatically}. 
-In these works, the skeleton acts as the simplest representation of a 3-D volume. 
-The Tree-structure Extraction Algorithm for Accurate and Robust Skeletons (TEASER) has been used by connectomics researchers to parameterize 3-D shapes~\cite{sato2000teasar,zhao2014automatic}.
+Unfortunately the graph partitioning formulation is NP-Hard~\cite{demaine2006correlation}.
+However, there are several useful multicut heuristics which provide good approximations with reasonable computational costs~\cite{horvnakova2017analysis,kernighan1970efficient,keuper2015efficient}.

### 2017-11-10 papers/cvpr2018/2_method.tex
Added overview of existing methods figure
added some figures
paper: majors updates to intro/related works/conclusion

@@
 \section{Method}
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=0.92\linewidth]{./figures/skeleton1.png}
+	\includegraphics[width=0.92\linewidth]{./figures/skeleton2.png}
+	\caption{Skeletons using the TEASER algorithm.}
+	\label{fig:skeletonization}
+\end{figure}
 
@@
 Thus there are three major components to our framework: skeletonization for constructing a graph, network training for determining edge weights, and graph-partitioning using a multicut heuristic algorithm.
-(INSERT FIGURE HERE)
 
@@
 \subsubsection{Edge Generation}
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.42\linewidth]{./figures/skeleton1.png}
-	\hspace{0.085\linewidth}
-	\includegraphics[width=0.42\linewidth]{./figures/skeleton2.png}
-	\caption{Two example outputs of the TEASER skeletonization algorithm.}
-	\label{fig:skeletonization}
-\end{figure}
 
@@
 	\centering
-	\includegraphics[width=0.42\linewidth]{./figures/merge_candidate1.png}
-	\hspace{0.085\linewidth}
-	\includegraphics[width=0.42\linewidth]{./figures/merge_candidate2.png}
+	\includegraphics[width=0.92\linewidth]{./figures/split_error1.png}
+	\includegraphics[width=0.92\linewidth]{./figures/split_error2.png}
 	\caption{Two erroneously split segments that should merge together. Most segments that we want to merge have the same general structure.}
@@
 A forest is a partitioning of a graph into a set of trees (i.e. no segment has a cycle). 
-There are several heuristics that solve the multicut problem. For our purposes we use the Kernighan-Lin algorithm~\cite{kernighan1970efficient}.
-The running time of this algorithm is $\mathcal{O}(N^3)$, where $N$ is the number of nodes in the graph (DOUBLE CHECK).
+There are several heuristics that solve the multicut problem. For our purposes we use the greedy-additive algorithm~\cite{keuper2015efficient}.

### 2017-11-10 papers/cvpr2018/3_evaluation.tex
paper: majors updates to intro/related works/conclusion

@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=0.8\linewidth]{./figures/multicut.png}
-	\caption{An example of the benefits of using multicut over simpler agglomeration schemes.
-If we input this example into a na\"ive agglomeration strategy that collapses all edges with a threshold greater than 0.5, this entire segment will merge together despite the fact that nodes 2 and 4 and nodes 3 and 5 have low affinities.}
-	\label{fig:multicut}
-\end{figure}
-
 Applying a top-down globally optimal partitioning function allows us to enforce some domain-specific constraints on the reconstruction.

### 2017-11-10 papers/cvpr2018/4_results.tex
paper: majors updates to intro/related works/conclusion

@@
 Our method removes a significant portion of these candidates while maintaining a large number of the true merge locations.
-This edge pruning is essential for the graph partitioning algorithms which have a computational complexity dependence on the number of edges (CHECK). 
+This edge pruning is essential for the graph partitioning algorithms which have a computational complexity dependence on the number of edges. 
 Our pruning heuristic removes at least $6\times$ the number of edges between correctly split segments on all datasets, achieving a maximum removal ratio of $20\times$. 
@@
 	\textbf{Dataset} & \textbf{Precision} & \textbf{Recall} & \textbf{Accuracy} \\ \hline
-	Kasthuri Training & & & \\
-	Kasthuri Testing & & & \\
-	FlyEM Vol. 1 & & & \\
-	FlyEM Vol. 2 & & & \\ \hline
+	Kasthuri Training & 0.919 & 0.936 & 0.974 \\
+	Kasthuri Testing & 0.737 & 0.717 & 0.907 \\
+	FlyEM Vol. 1 & 0.796 & 0.478 & 0.862 \\ 
+	FlyEM Vol. 2 & 0.762 & 0.422 & 0.810 \\ \hline
 	\end{tabular}
 	\caption{Precision and recall for the training and three test datasets.}
-	\label{fig:classification}
+	\label{table:classification}
 \end{table}
@@
 Our initial network does not take in any image data, only the segment shapes, so we merely extract the $1200 \textrm{nm}^3$ region from any dataset and rescale as input into the neural network. 
-For each of the tables, the top left square gives the number of segments which should merge that we predict merge.
-The bottom right square gives the number of segments which should not merge that we predict should not merge.
-The bottom left quadrant indicates the amount of false positives, candidates which we predict merge which do not.
-The top right quadrant gives the amount of false negatives where we predict split although the candidates should merge.
 Figure \ref{fig:network-results} shows the receiver operating characteristic (ROC) curve for all four datasets.

### 2017-11-10 papers/cvpr2018/5_conclusions.tex
paper: majors updates to intro/related works/conclusion

@@
 
-\begin{itemize}
-	\item Impact
-	\item Future work
-\end{itemize}
+We present a novel method for framework neuronal processes in connectomics image datasets.
+We extend on top of existing region-based agglomeration strategies and show significant accuracy improvement on two datasets from two different species. 
+By extracting skeletons from every segment in the input we can quickly produce a graph with $N$ nodes and $E$ weighted edges from the input. 
+We populate the edge weights using a 3-D CNN that, unlike previous methods, does not use the raw image data.
+Separating the neural network from the images allows us to train on anisotropic data and test on isotropic data with different sample resolution. 
+This is exceptionally important in connectomics because of the extreme labor-intensive cost of manually segmenting ground truth data.

### 2017-11-10 papers/cvpr2018/paper.tex
paper: majors updates to intro/related works/conclusion

--- 2017-11-06 papers/cvpr2018/paper.tex
@@
 \usepackage{algorithmicx}
+\usepackage{siunitx}
+\usepackage{float}
 
@@
 
+\begin{figure}[t]\footnotesize
+	\vspace{-2.04in}
+	\begin{minipage}{\textwidth}
+		\begin{minipage}{0.125\textheight}
+			\includegraphics[width=\linewidth]{figures/schema/teaser-image.png}
+			\includegraphics[width=\linewidth]{figures/schema/teaser-segmentation.png}
+		\end{minipage}
+		\begin{minipage}{0.24\textwidth}
+			\includegraphics[width=\linewidth]{figures/schema/pre-multicut.png}
+		\end{minipage}
+		\begin{minipage}{0.34\textwidth}
+			\includegraphics[width=\linewidth]{figures/schema/multicut-graph.png}
+		\end{minipage}
+		\begin{minipage}{0.24\textwidth}
+			\includegraphics[width=\linewidth]{figures/schema/post-multicut.png}
+		\end{minipage}
+		\caption{We take as input the results of a region-based agglomeration algorithm. We extract a graph from this segmentation and apply a top-down partitioning algorithm to improve accuracy.}
+		\label{fig:teaser}
+	\end{minipage}
+\end{figure}
+
 %%%%%%%%% ABSTRACT
 \begin{abstract}
-Advancements in electron microscopy image acquisition have created massive connectomics datasets which are petabytes in size and make manual segmentation not feasible. 
+Advancements in electron microscopy image acquisition have created massive connectomics datasets which are petabytes in size and make manual segmentation infeasible. 
 Proposed methods for automatic segmentations generate super-pixel approximations of neural membranes followed by agglomeration strategies to create full neuron reconstructions. 

### 2017-11-10 papers/cvpr2018/0_introduction.tex
paper: updated entire paper

@@
 It is not feasible for domain experts to manually segment the vast amount of 3-D image data to model an entire brain.
-Here we introduce a scalable top-down segmentation algorithm that also leverages local information.
-The top-down partitioning strategy allows us to apply domain-specific constraints to the segmentation task.
+Here we introduce a scalable, top-down segmentation algorithm that also leverages local information.
+Partitioning from a top-down approach allows us to apply domain-specific constraints to the segmentation task.
 
@@
 
-Researchers currently address the failures of these pixel-based algorithms by training random-forest classifiers to agglomerate an oversegmentation of voxels~\cite{nunez2014graph,10.1371/journal.pone.0125825}.
-These classifiers take the output of the pixel-based algorithms as input and generate high-level statistics such as affinity distributions between pixel regions. 
+Researchers address the failures of these pixel-based algorithms by training random-forest classifiers to agglomerate an oversegmentation of voxels~\cite{nunez2014graph,10.1371/journal.pone.0125825}.
+These classifiers take the output of the pixel-based algorithms as input and generate high-level statistics such as affinity distributions between regions. 
 Presently, these methods use hand-designed features despite the evidence that machine-learned features perform better~\cite{bogovic2013learned}. 
-These \textit{region-based} algorithms outperform the pixel-based algorithms but still do not provide the accuracy needed for large scale reconstructions of the brain.
+These \textit{region-based} algorithms outperform the pixel-based algorithms but do not provide the accuracy needed for large scale reconstructions of the brain.
 
-We present a \textit{segment-based} strategy that extends on the outputs of region-based methods.
-We only take as input a segmentation from a previous agglomeration algorithm and not the raw image data. 
-This allows us to train on connectomics datasets at a resolution and image type different than the test datasets.
-We consider the 3-D skeletons of each segments as a simplification of its shape. 
-We can then quickly extract a graph from the input segmentation using the skeletonization of the segments in the volume.
+We present a \textit{segment-based} strategy that builds on the outputs of region-based methods (Figure \ref{fig:teaser}).
+We only take as input a segmentation from the region-based agglomeration algorithm. 
+This allows us to train on connectomics datasets at a given resolution and image type and test on another resolution.
+This is a huge plus considering the sheer amount of expert-hours needed to generate ground truth for these massive datasets.
+We extract a graph representation from the input segmentation.
+By simplifying the 3-D segments by their skeletons, we can quickly generate the graph nodes and edges. 
+We train a 3-D CNN to populate the graph edge weights with bottom-up local information. 
+We enforce domain-specific global constraints, such as the underlying biology, using a graph-based partitioning heuristic.
+In this we can leverage both local and global information to produce a more accurate segmentation.
 
-We add edge weights to our graph using a 3-D CNN to predict the probabilities that nearby segments belong to the same neuron.
-Using a graph-based optimization strategy enables us to enforce domain-specific global constraints such as the underlying neuronal biology.
-From here we apply a global partitioning algorithm that minimizes a cost function of separating adjacent nodes in the graph.
-
-Our method takes the output of any bottom-up segmentation strategy and creates a graph on top of this segmentation. 
-We enforce domain-specific global constraints by reasoning at the graph level.
-This strategy scales to massive connectomics datasets and improves accuracy over existing methods.
+Our novel approach creates a level of abstraction over existing region-based agglomeration strategies. 
+We take the output of these methods as input and extract a graph structure from that.
+This allows us to enforce restrictions on our output that closely follow the underlying biology of these connectomics datasets. 
+We use bottom-up information to weight the edges in our graph and top-down information when partitioning the graph. 
+This dual approach of assessing local decisions in a global framework produces improvements over the existing region-based methods.

### 2017-11-10 papers/cvpr2018/1_related_work.tex
paper: updated entire paper

@@
 
-A significant amount of research in computer vision focuses segmentation of images \cite{zaitoun2015survey}. 
-Here, we review some of the most successful methods that have been applied to large-scale EM images.
+A significant amount of research in computer vision focuses on the segmentation of images \cite{zaitoun2015survey}. 
+Here, we review some of the most successful methods that have been applied to large-scale EM images. Figure \ref{fig:pipeline} shows the results of a typical segmentation pipeline on these images.
 
@@
 A large amount of connectomics research considers the problem of extracting segmentation information at the voxel level from the raw EM images to produce label volumes.
-Some early techniques apply computationally expensive graph partitioning techniques with a single node per voxel  \cite{andres2012globally}, however these methods do not scale to terabyte datasets.
+Some early techniques apply computationally expensive graph partitioning algorithms with a single node per voxel~\cite{andres2012globally}, however these methods do not scale to terabyte datasets.
 Since then, several methods train 2-D CNNs to predict membrane probabilities per image slice~\cite{ciresan2012deep,jain2010boundary,kaynig2015large,rhoananet,amelio_segmentation}. 
 More recent strategies augment these neural networks with the $z$-dimension creating full 3-D CNNs~\cite{lee2015recursive,ronneberger2015u}.
-Oftentimes these networks produce probabilities for the affinity between voxels, i.e., the probability that adjacent voxels belong to the same neuron.
+Oftentimes these networks produce probabilities for the affinity between two voxels (i.e., the probability that adjacent voxels belong to the same neuron).
+The MALIS cost function is specifically designed for generating affinities that produce good segmentations~\cite{briggman2009maximin}. 
 More recently, flood-filling networks produce segmentations by training an end-to-end neural network that takes EM images to label volumes~\cite{januszewski2016flood}.
-These networks produce very impressive accuracies but are much too slow to scale to larger datasets.
+These flood-filling networks produce very impressive accuracies but at too high a computational cost.
 
@@
 Despite the success of these classifiers, they often make mistakes based on the local information leading to errors in the segmentation. 
-Additionally, many recent advancements in segmentation use artificial neural networks given the evidence that machine-learned features outperform hand-designed ones~\cite{bogovic2013learned}.
+Lately, many recent advancements in segmentation use artificial neural networks since machine-learned features outperform hand-designed ones~\cite{bogovic2013learned}.
 A significant amount of research focuses on the training and optimization of these deep neural networks~\cite{chatfield2014return,maas2013rectifier,nesterov1983method}.
@@
 
-Some limited research builds on top of the region-based methods to correct errors in the segmentation \cite{rolnick2017morphological,error_correction_using_CNN}.
-Similarly, proofreading methods create a ``human-in-the-loop" framework that allows users to find errors and correct them \cite{haehn2017scalable,haehn2017guided,haehn2014design}. 
-Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}.
-The multicut graph partitioning algorithm produces a set of segments where no segment contains a cycles.
-This closely resembles the biological constraint that neurons have a topological genus of zero. 
-Unfortunately the graph partitioning formulation is NP-Hard~\cite{demaine2006correlation}.
-However, there are several useful multicut heuristics which provide good approximations with reasonable computational costs~\cite{horvnakova2017analysis,kernighan1970efficient,keuper2015efficient}.
+Some limited research builds on top of the region-based methods to correct errors in the segmentation \cite{rolnick2017morphological,error_correction_using_CNN,haehn2017guided}. 
+However, to our knowledge, we are the first to extract a graph representation from these region-based methods. 
+Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for traditional image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}.
+We can enforce domain-specific constraints using graph-based paritioning algorithms.  
+Unfortunately graph partitioning is an NP-Hard problem~\cite{demaine2006correlation}.
+However, there are several useful multicut heuristics which provide good approximations with reasonable computational costs~\cite{horvnakova2017analysis,keuper2015efficient}.

### 2017-11-10 papers/cvpr2018/2_method.tex
paper: updated entire paper

@@
 \subsection{Graph Creation}
-
+\label{sec:skeletonization}
 We generate nodes $N$ and edges $E$ to apply a graph-based optimization strategy for segmentation. 
-In addition, these edges need non-negative weights.
+In addition, these edges receive non-negative weights.
 
@@
 The simplest node generation strategy creates one node for every unique segment label in the input volume.
-However, some of the millions of labels in the volume correspond to very small regions. 
-Usually these locations have noisy image data so the voxel-based methods could not provide enough information to generate a larger segment.
+However, some of the millions of labels in the volume correspond to very small volumes. 
+Usually these locations have noisy image data so the pixel-based methods could not provide enough information to generate a larger segment.
 It is difficult to extract useful shape features from these segments because of their small, and often random, shape. 
 We prune these nodes from the graph by removing all segments with fewer than $20,000$ voxels. 
-On a typical connectomics dataset this only remove XX$\%$ of segments.
+This removes XX\% of segments on a typical connectomics dataset.
 
@@
 NeuroProof and GALA consider all pairs of adjacent segments for merging. 
-This method produces too many edges in the graph for us.
-Therefore we present the following algorithm to identify pairs of segments to consider merging.
+For us, this method produces too many edges in the graph. 
+Therefore we present the following algorithm to identify pairs of segments to consider for merging.
 
@@
 Many of the segments that are erroneously split follow a similar pattern (Figure~\ref{fig:merge_candidates}). 
-In these split instances the skeletons have nearby endpoints.
+In these split instances the two skeletons have nearby endpoints.
 
@@
 We store the midpoint between the two endpoints as the ``center" of the potential merge.
-Algorithm (ADD REF) provides pseudocode for this edge generation algorithm.
 
@@
 	\includegraphics[width=0.92\linewidth]{./figures/split_error2.png}
-	\caption{Two erroneously split segments that should merge together. Most segments that we want to merge have the same general structure.}
+	\caption{Two erroneously split segments.}
 	\label{fig:merge_candidates}
 \end{figure}
-
-\begin{algorithmic}
-	\Function{GenerateEdges}{$skeletons$}
-		\For {$skeleton$ in $skeletons$}
-			\State $candidates$ = set()
-			\For {$endpoint$ in $skeleton$}
-				\State TODO ADD CODE
-			\EndFor
-		\EndFor
-	\EndFunction
-\end{algorithmic}
-
-Note that this algorithm does not enforce any segment adjacency constraints.
-Figure (ADD FIGURE) shows two examples that would not be considered in NeuroProof or GALA since these algorithms only consider merging adjacent segments.
 
@@
 We extract a cubic region of interest around these locations as input to the CNN. 
-These regions of interests will provide the local information for the neural network to predict which neighboring segments belong to the same neuron.
+These regions of interest provide the local information for the neural network to predict which neighboring segments belong to the same neuron.
 
@@
 Our network architecture has three layers of double convolutions followed by a max pooling step following the work of Chatfield et al.
-that found such a framework improves on single convolution layers~\cite{chatfield2014return}.
-The first two max pooling layers are anisotropic with pooling only in the $x$ and $y$ dimensions to account for the anisotropic nature of the datasets.
+that found this technique improves on single convolution layers~\cite{chatfield2014return}.
+The first max pooling layer is anisotropic with pooling only in the $x$ and $y$ dimensions.
 The output after this final pooling step is flattened into a 1-D vector which is input into two fully connected layers.
@@
 We use a stochastic gradient descent optimizer with Nesterov's accelerated gradient~\cite{nesterov1983method}. 
-There are dropouts of $0.2$ after every pooling layer and the first dense layer, and a dropout of $0.5$ after the final dense layer. 
-This prevents overfitting of the training data.
+There are dropouts of $0.2$ after every pooling layer and the first dense layer, and a dropout of $0.5$ after the final dense layer to prevent overfitting. 
+We discuss all other network parameters in Section~\ref{sec:network-parameters}.
 
@@
 
-\subsection{Agglomeration}
+\subsection{Graph Partitioning}
 
 After constructing the graph structure we apply a graph-based segmentation strategy. 
-There are many formulations of graph-based optimization strategies that provide different guarantees on their output. 
-Neurons in the brain should be acyclic, i.e. the output shape should have a genus of zero. 
-Current connectomics agglomeration techniques do not leverage this additional information but rather consider neighboring regions in successive order without regard to loop creation. 
-In our graph formulation we enforce this topological property by applying a multicut partition onto the graph that generates a \textit{forest} on the nodes. 
+There are many graph partitioning minimization functions that provide different constraints on their output. 
+Neurons in the brain should be acyclic (i.e. the output shape should have a genus of zero). 
+We enforce this constraint by finding a multicut partition of the graph that generates a \textit{forest} on the nodes. 
 A forest is a partitioning of a graph into a set of trees (i.e. no segment has a cycle). 
-There are several heuristics that solve the multicut problem. For our purposes we use the greedy-additive algorithm~\cite{keuper2015efficient}.
+There are several heuristics that solve the multicut problem (which is NP-Hard). 
+We use the greedy-additive algorithm~\cite{keuper2015efficient}.

### 2017-11-10 papers/cvpr2018/3_evaluation.tex
paper: updated entire paper

@@
 The FlyEM dataset comes from the mushroom body of a 5-day old adult male \textit{Drosophila} fly imaged by a focused ion-beam milling scanning electron microscopy.  
-The mushroom body is this species is the major site of associative learning \cite{takemura2017connectome}. 
+The mushroom body in this species is the major site of associative learning \cite{takemura2017connectome}. 
 The original dataset contains a $\SI[product-units=single]{40 x 50 x 120}{\micro\meter}^3$ volume of which we use two cubes of size $\SI[product-units=single]{10 x 10 x 10}{\micro\meter}^3$. 
@@
 \label{sec:neuroproof}
-The segmentation on the Kasthuri dataset was computed by agglomerating 3D supervoxels produced by zwatershed from 3D affinity predictions~\cite{zlateski2015image}. 
-A recent study by Funke et.al. demonstrated superior performance of such method over existing ones on anisotropic data \cite{schlegel2017learning}. 
-We learned 3d affinities in x,y,z using MALIS loss with a U-net~\cite{Turaga:2009,ronneberger2015u}. 
-We apply the zwatershed algorithm, with suitable parameters, to compute an 3D over-segmentation of the volume. 
-The resulting 3D over-segmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}. 
-The VI values at different stopping thresholds of agglomeration correspond to the points on the curve plotted in Figure YYY.
+The segmentation on the Kasthuri dataset was computed by agglomerating 3-D supervoxels produced by zwatershed from 3-D affinity predictions~\cite{zlateski2015image}. 
+A recent study by Funke et.al. demonstrated superior performance of such methods over existing ones on anisotropic data \cite{schlegel2017learning}. 
+We learned 3-D affinities using MALIS loss with a U-net~\cite{Turaga:2009,ronneberger2015u}. 
+We apply the zwatershed algorithm, with suitable parameters, to compute a 3-D oversegmentation of the volume. 
+The resulting 3-D oversegmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}. 
+The variation of information (Section~\ref{sec:variation-of-information}) values at different stopping thresholds of agglomeration correspond to the curve plotted in Figure~\ref{fig:variation-of-information}.
 
 We have collected two $1000 \times 1000 \times 1000$ voxel ($\SI[product-units=single]{10x10x10}{\micro\meter}^3$) volumes from the authors~\cite{takemura2017connectome}. 
-Based on the authors' suggestion, we applied the context-aware delayed agglomeration algorithm~\cite{10.1371/journal.pone.0125825} that shows improved performance on this dataset than the pipeline used in the original publication.
-This segmentation framework learns voxel and supervoxel classifiers with an emphasis to minimize under-segmentation error.
+Based on the authors' suggestion, we applied the context-aware delayed agglomeration algorithm~\cite{10.1371/journal.pone.0125825} that shows improved performance on this dataset over the pipeline used in the original publication.
+This segmentation framework learns voxel and supervoxel classifiers with an emphasis to minimize undersegmentation error.
 At the same time this framework produces lower over-segmentation than standard algorithms. 
-This algorithm first computes multi-channel 3D predictions for membranes, cell interiors, and mitochondria, among other cell features. 
-The membrane prediction channel is utilized to produce an over-segmented volume using 3D watershed, which is then agglomerated hierarchically up to a certain confidence threshold. 
-We used exactly same parameters for the publicly available code for this algorithm and used different agglomerations thresholds to plot the VI error curve.
+This algorithm first computes multi-channel 3-D predictions for membranes, cell interiors, and mitochondria, among other cell features. 
+The membrane prediction channel is utilized to produce an oversegmented volume using 3-D watershed, which is then agglomerated hierarchically up to a certain confidence threshold. 
+We used exactly the same parameters for the publicly available code for this algorithm and used different agglomerations thresholds to plot the variation of information error curve.
 
@@
 
-We prune potential merge candidates by running Algorithm \ref{alg:skeletonization} on the input dataset. 
+We prune potential merge candidates with the algorithm described in Section~\ref{sec:skeletonization}. 
 There are two essential parameters to the algorithm: $t_{low}$ and $t_{high}$. 
@@
 Using nanometers allows us to have uniform units across all of these datasets and calculate the thresholds in voxels at runtime. 
-The thresholds are $t_{low} = (40, 40, 8)$ voxels and $t_{high} = (100, 100, 20)$ voxels for the Kasthuri dataset $t_{low} = (24, 24, 24)$ voxels and $t_{high} = (60, 60, 60)$ voxels for the FlyEM dataset.
+The thresholds are $t_{low} = (40, 40, 8)$ voxels and $t_{high} = (100, 100, 20)$ voxels for the Kasthuri dataset and $t_{low} = (24, 24, 24)$ voxels and $t_{high} = (60, 60, 60)$ voxels for the FlyEM dataset.
 The thresholds are anisotropic or isotropic depending on the corresponding isotropy of the dataset.
@@
 \subsection{Classifier Training}
-
+\label{sec:network-parameters}
 We use the Kasthuri Vol. 1 dataset for training and validation. 
 We train on 80\% of the potential merge candidates for this volume.
-The validation the neural network classifier on the remaining 20\% of candidates. 
+We validate the neural network classifier on the remaining 20\% of candidates. 
 We consider networks with varying input sizes, optimizers, loss functions, filter sizes, learning rates, and activation functions. 
@@
 \subsection{Variation of Information}
-
-We evaluate the performance of our methods using the split version of the variance of information~\cite{meila2003comparing}. 
+\label{sec:variation-of-information}
+We evaluate the performance of our methods using the split version of variance of information~\cite{meila2003comparing}. 
 Consider a ground truth labeling $GT$ and our automatically reconstructed segmentation $SG$. 

### 2017-11-10 papers/cvpr2018/4_results.tex
paper: updated entire paper

@@
 Our method removes a significant portion of these candidates while maintaining a large number of the true merge locations.
-This edge pruning is essential for the graph partitioning algorithms which have a computational complexity dependence on the number of edges. 
+This edge pruning is essential for the graph partitioning algorithm which has a computational complexity dependence on the number of edges. 
 Our pruning heuristic removes at least $6\times$ the number of edges between correctly split segments on all datasets, achieving a maximum removal ratio of $20\times$. 
@@
 Table \ref{table:classification} shows the precision and recall for all of the datasets. 
-Our methods are more general than traditional connectomics examples allowing us to train the network on an anisotropic dataset and get impressive results on an isotropic dataset. 
-Our initial network does not take in any image data, only the segment shapes, so we merely extract the $1200 \textrm{nm}^3$ region from any dataset and rescale as input into the neural network. 
+Since, our method does not rely on the image data, we can train the network on an anisotropic dataset and get impressive results on an isotropic dataset. 
 Figure \ref{fig:network-results} shows the receiver operating characteristic (ROC) curve for all four datasets.
@@
 	\includegraphics[width=0.9\linewidth]{./figures/roc-microns-300-test.png}
-	\caption{The receiver operating characteristic (ROC) curve for all four datasets.}
+	\caption{(NOT CORRECT) The receiver operating characteristic (ROC) curve for all four datasets.}
 	\label{fig:network-results}
@@
 
+TODO - ADD QUALITATIVE RESULTS
+
 \subsection{Graph Based Strategies}
+
+TODO - QUANTIFY IMPROVEMENT BY MULTICUT - READERS CAN SKIP SECTION FOR NOW
 
@@
 
-The final metric for comparing two connectomics segmentations is computing the variation of information with respect to an expert-labeled ground truth dataset.
+We compute the variation of information for our segmentations against the expert-labeled ground truth datasets. 
+The input segmentation to our network serves as a baseline. 
+We evaluate NeuroProof (our input) at several different thresholds to create a variation of information curve. 
+Similarly, we run the greedy-additive heuristic with varying parameters that increase the probability needed for merging nodes. 
 Figure \ref{fig:variation-of-information} shows the results on the datasets compared to the baseline (green) and an oracle (blue). 
+The oracles sees the entire constructed graph from our algorithm and correctly partitions the graph based on the ground truth. 
+Our methods decreases the split variation of information by a factor of XX\% and only increases the merge variation of information by a factor of XX\% on the test datasets. 
+Table \ref{table:variation-of-information} provides a quantitative overview for the changes in variation of information.
+
+TODO - ADD QUALITATIVE RESULTS
+
+\begin{table}
+	\centering
+	\begin{tabular}{c c c} \hline
+		\textbf{Dataset} & \textbf{VI Split} & \textbf{VI Merge} \\ \hline
+		Kasthuri Training &  & \\
+		Kasthuri Testing & & \\
+		FlyEM Vol. 1 & & \\
+		FlyEM Vol. 2 & & \\ \hline
+	\end{tabular}
+	\caption{Variation of Information Change}
+	\label{table:variation-of-information}
+\end{table}
 

### 2017-11-10 papers/cvpr2018/5_conclusions.tex
paper: updated entire paper

@@
 We extend on top of existing region-based agglomeration strategies and show significant accuracy improvement on two datasets from two different species. 
-By extracting skeletons from every segment in the input we can quickly produce a graph with $N$ nodes and $E$ weighted edges from the input. 
+By extracting skeletons from every segment in the input we can quickly produce a graph $G$ with $N$ nodes and $E$ weighted edges from the input. 
 We populate the edge weights using a 3-D CNN that, unlike previous methods, does not use the raw image data.
@@
 This is exceptionally important in connectomics because of the extreme labor-intensive cost of manually segmenting ground truth data. 
+We use existing graph partitioning strategies on the $G$, enabling us to enforce domain-constraints on the resulting segmentation.
+For us, our constraints follow from the topology of neurons.
+However, this framework extends to other domains with varying constraints.

### 2017-11-13 papers/cvpr2018/0_introduction.tex
Changed sections 1 and 2 and some other errors such as duplicate bibtex.

@@
 The field of connectomics is concerned with reconstructing the wiring diagram of the brain at nanometer resolutions. 
-Recent advancements in image acquisition using multi-beam serial-section electron microscopy (sSEM) has allowed neuroscientists to produce terabytes of electron micrsocopy (EM) image data every hour~\cite{hildebrand2017whole}.
-Neuroscientists believe that reconstructing an entire mammalian brain at fine resolution will enable new insights into the workings of the brain~\cite{kasthuri2015saturated}. 
+Recent advancements in image acquisition using multi-beam serial-section electron microscopy (sSEM) has allowed researchers to produce terabytes of electron microscopy (EM) image data every hour~\cite{hildebrand2017whole}.
+Neuroscientists believe that reconstructing an entire mammalian brain at fine resolution will enable new insights into the workings of the brain~\cite{kasthuri2015saturated,haehn2017scalable}. 
 These observations will allow for new advancements in neuromedicine and artificial intelligence.
@@
 Voxels with the same label belong to the same neuron.
-It is not feasible for domain experts to manually segment the vast amount of 3-D image data to model an entire brain.
+It is not feasible for domain experts to manually segment the vast amount of 3-D image data to model an entire brain~\cite{haehn2014design}.
 Here we introduce a scalable, top-down segmentation algorithm that also leverages local information.
-Partitioning from a top-down approach allows us to apply domain-specific constraints to the segmentation task.
+Partitioning globally allows us to apply domain-specific constraints to the segmentation task.
 
-A significant amount of research focuses on automatic reconstruction of the neurons in EM images~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image}.
-%TODO DOUBLE CHECK REFERENCES
-All of these algorithms extract neuronal processes through the 3-D volumes using the raw image data as input.
-Oftentimes, convolutional neural networks (CNNs) predict membrane probabilities or affinities between voxels and apply simple thresholds to agglomerate the voxels into clusters~\cite{lee2015recursive,ronneberger2015u}.
-These \textit{pixel-based} algorithms produce excellent results but currently fall short of complete reconstructions with error rates of approximately $X\%$. %TODO ADD ERROR RATES
-
-\begin{figure*}[h!]
+\begin{figure*}[t!]
 	\centering
@@
 
+A significant amount of research focuses on automatic reconstruction of the neurons in EM images~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image}.
+%TODO DOUBLE CHECK REFERENCES
+All of these algorithms extract neuronal processes through the 3-D volumes using the raw image data as input.
+Oftentimes, convolutional neural networks (CNNs) predict membrane probabilities or affinities between voxels and apply simple thresholds to agglomerate the voxels into clusters~\cite{lee2015recursive,ronneberger2015u}.
+These \textit{pixel-based} algorithms produce excellent results but currently fall short of complete reconstructions with error rates of approximately $X\%$. %TODO ADD ERROR RATES
+
 Researchers address the failures of these pixel-based algorithms by training random-forest classifiers to agglomerate an oversegmentation of voxels~\cite{nunez2014graph,10.1371/journal.pone.0125825}.
@@
 We present a \textit{segment-based} strategy that builds on the outputs of region-based methods (Figure \ref{fig:teaser}).
-We only take as input a segmentation from the region-based agglomeration algorithm. 
-This allows us to train on connectomics datasets at a given resolution and image type and test on another resolution.
+For training a classifier based on a CNN, we only take as input the segmentation from a region-based agglomeration algorithm. 
+This renders our classifier independent of image resolution and characteristics such as anisotropy and for instance, allows the application to isotropic data without retraining.
 This is a huge plus considering the sheer amount of expert-hours needed to generate ground truth for these massive datasets.
@@
 
-Our novel approach creates a level of abstraction over existing region-based agglomeration strategies. 
+Our approach creates a level of abstraction over existing region-based agglomeration strategies. 
 We take the output of these methods as input and extract a graph structure from that.
-This allows us to enforce restrictions on our output that closely follow the underlying biology of these connectomics datasets. 
-We use bottom-up information to weight the edges in our graph and top-down information when partitioning the graph. 
+This allows us to enforce global restrictions on our output that closely follow the underlying biology of these connectomics datasets such as limiting the allowed angles of neuron branching. 
+In addition we use local information such as shape priors to weight the edges in our graph.
 This dual approach of assessing local decisions in a global framework produces improvements over the existing region-based methods.

### 2017-11-13 papers/cvpr2018/1_related_work.tex
Changed sections 1 and 2 and some other errors such as duplicate bibtex.

@@
 Some early techniques apply computationally expensive graph partitioning algorithms with a single node per voxel~\cite{andres2012globally}, however these methods do not scale to terabyte datasets.
-Since then, several methods train 2-D CNNs to predict membrane probabilities per image slice~\cite{ciresan2012deep,jain2010boundary,kaynig2015large,rhoananet,amelio_segmentation}. 
+Since then, several methods train 2-D CNNs to predict membrane probabilities per image slice~\cite{ciresan2012deep,jain2010boundary,kaynig2015large,seymour2016rhoananet,amelio_segmentation}. 
 More recent strategies augment these neural networks with the $z$-dimension creating full 3-D CNNs~\cite{lee2015recursive,ronneberger2015u}.
@@
 More recently, flood-filling networks produce segmentations by training an end-to-end neural network that takes EM images to label volumes~\cite{januszewski2016flood}.
-These flood-filling networks produce very impressive accuracies but at too high a computational cost.
+These flood-filling networks produce very impressive accuracies but at a high computational cost.
 

### 2017-11-13 papers/cvpr2018/paper.tex
paper: updated entire paper
Changed sections 1 and 2 and some other errors such as duplicate bibtex.

@@
 \usepackage{makecell}
+\usepackage{algorithm}
 \usepackage{algpseudocode}
-\usepackage{algorithmicx}
 \usepackage{siunitx}
@@
 %%%%%%%%% TITLE
-\title{Graph-based Neuron Agglomeration using 3D Skeletons}
+\title{Top-down Segment-based Neuron Reconstruction}
 
@@
 		\end{minipage}
-		\caption{We take as input the results of a region-based agglomeration algorithm. We extract a graph from this segmentation and apply a top-down partitioning algorithm to improve accuracy.}
+		\caption{To reconstruct neurons, we take as input the results of a region-based agglomeration algorithm.
+We extract a graph from this segmentation and apply a partitioning algorithm with local and global features to improve accuracy.}
 		\label{fig:teaser}

### 2017-11-13 papers/cvpr2018/2_method.tex
paper: major changes

@@
 
-There are two types of errors that can occur in image segmentation problems.
-The first, called a split error, occurs when there are two segments that should have been merged.
-The second, called a merge error, happens when one segment should be split into two.
-Generally, it is much more difficult to correct merge errors than to correct split errors (CITE). 
-Our method takes as input an oversegmentation of an $EM$ image volume where there are many more split errors than merge errors.
-Our goal is to identify locations of split errors and merge the corresponding segments.
-Section~\ref{sec:neuroproof} discusses two pipelines for generating these segmentations.
+There are two types of possible errors in image segmentation problems.
+A \textit{split error} occurs when there are two segments which should be one. 
+A \textit{merge error} happens when one segment should not have been merged. 
+Generally, it is much more difficult to correct merge errors than to correct split errors. 
+Therefore, we take an oversegmentation of the $EM$ image volume as input so that most of the errors are split errors. 
+We identify these split error locations and merge the offending segments.
+Section~\ref{sec:neuroproof} discusses two pipelines for generating the oversegmentations.
 
 From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with weights $w_e$. 
-The nodes correspond to label segments from the segmentation with edges between segments considered for merging.
+The nodes correspond to unique labels from the segmentation.
+There is an edge between all nodes which we consider for merging. 
 Ideally, our graph has edges corresponding to all of the segments which were erroneously split with few edges between correctly split segments.
-We generate a skeleton for every segment following the intuition that a skeleton represents a simplified representation of the overall shape of an object. 
-We locate merge candidates and produce corresponding edges based on these skeletons.
-A CNN generates the edge weights by learning a merge function given two segments as input. 
-A multicut heuristic generates a partition on the graph where nodes in the same partition are assigned the same output label. 
-Thus there are three major components to our framework: skeletonization for constructing a graph, network training for determining edge weights, and graph-partitioning using a multicut heuristic algorithm.
+We consider an object's skeleton as a simplified representation of its shape.
+We use these skeletons to identify merge candidates and add an edge to the graph.
+A CNN produces a probability that two candidates should merge, and we assign the corresponding edge this probability as a weight. 
+A multicut heuristic partitions the graph to produce an output segmentation.
+Thus there are three major components to our framework: skeletonization for constructing a graph, network training for determining edge weights, and graph-partitioning using a multicut heuristic.
 
@@
 \label{sec:skeletonization}
-We generate nodes $N$ and edges $E$ to apply a graph-based optimization strategy for segmentation. 
-In addition, these edges receive non-negative weights.
-
 \subsubsection{Node Generation}
@@
 The simplest node generation strategy creates one node for every unique segment label in the input volume.
-However, some of the millions of labels in the volume correspond to very small volumes. 
-Usually these locations have noisy image data so the pixel-based methods could not provide enough information to generate a larger segment.
-It is difficult to extract useful shape features from these segments because of their small, and often random, shape. 
+However, some of the millions of labels correspond to very small volumes. 
+Usually these locations have noisy image data so the pixel-based methods cannot provide enough information to generate a larger segment.
+It is difficult to extract useful shape features from these segments because of their small, and often random, appearance. 
 We prune these nodes from the graph by removing all segments with fewer than $20,000$ voxels. 
@@
 
-After skeletonization, we begin to identify segments for merge consideration with the following two-pass heuristic.
+We identify segments for merge consideration with the following two-pass heuristic.
 In the first pass, we iterate over all endpoints $e$ belonging to a segment $S$ and create a set of segments $\mathbb{S}_e^\prime$ that includes all labels that have a single voxel within $t_{low}$ voxels from $e$.
-Elements of these sets are candidates for merging.
-However the first pass often has too many candidates that should remain split so we apply an additional pass for further pruning.
+Oftentimes this first pass produces too many candidates.
 In the second pass, we consider all of the segments $\mathbb{S}_e^\prime$ for every endpoint $e$. 
@@
 
-\subsection{Edge Probabilities}
-
-The previous section outlines how to generate edges between nodes in our graph structure. 
-Here we introduce a neural network architecture for generating probabilities that two nodes sharing an edge belong to the same neuron. 
-The neural network takes as input only data from the input segmentation.
-
-\subsubsection{Network Architecture}
+\subsection{Edge Weights}
 
@@
 Figure~\ref{fig:architecture} provides an overview of our architecture. 
-Our network architecture has three layers of double convolutions followed by a max pooling step following the work of Chatfield et al.
+The network architecture has three layers of double convolutions followed by a max pooling step based on the work of Chatfield et al.
 that found this technique improves on single convolution layers~\cite{chatfield2014return}.
 The first max pooling layer is anisotropic with pooling only in the $x$ and $y$ dimensions.
-The output after this final pooling step is flattened into a 1-D vector which is input into two fully connected layers.
+The filters after the final pooling step are flattened into a 1-D vector which is input into two fully connected layers.
 The final layer produces a probability with a sigmoid activation function~\cite{funahashi1989approximate}. 
 All of the other activation functions are LeakyReLU~\cite{maas2013rectifier}. 
-We use a stochastic gradient descent optimizer with Nesterov's accelerated gradient~\cite{nesterov1983method}. 
+We use the stochastic gradient descent optimizer with Nesterov's accelerated gradient~\cite{nesterov1983method}. 
 There are dropouts of $0.2$ after every pooling layer and the first dense layer, and a dropout of $0.5$ after the final dense layer to prevent overfitting. 

### 2017-11-13 papers/cvpr2018/3_evaluation.tex
paper: major changes

@@
 \section{Evaluation}
-
-We evaluate our schema on two different connectomics datasets, one anisotropic and the other isotropic, from two different species.
 
@@
 This segmentation framework learns voxel and supervoxel classifiers with an emphasis to minimize undersegmentation error.
-At the same time this framework produces lower over-segmentation than standard algorithms. 
+At the same time this framework produces lower oversegmentation than standard algorithms. 
 This algorithm first computes multi-channel 3-D predictions for membranes, cell interiors, and mitochondria, among other cell features. 

### 2017-11-13 papers/cvpr2018/0_introduction.tex
added HP comments

--- 2017-11-10 papers/cvpr2018/0_introduction.tex
@@
+% !TEX root =  paper.tex
 \section{Introduction}
 
-The field of connectomics is concerned with reconstructing the wiring diagram of the brain at nanometer resolutions. 
-Recent advancements in image acquisition using multi-beam serial-section electron microscopy (sSEM) has allowed neuroscientists to produce terabytes of electron micrsocopy (EM) image data every hour~\cite{hildebrand2017whole}.
-Neuroscientists believe that reconstructing an entire mammalian brain at fine resolution will enable new insights into the workings of the brain~\cite{kasthuri2015saturated}. 
-These observations will allow for new advancements in neuromedicine and artificial intelligence.
+The field of connectomics is concerned with reconstructing the wiring diagram of the brain at nanometer resolutions to enable new insights into the workings of the brain~\cite{kasthuri2015saturated,haehn2017scalable}.
+Recent advancements in image acquisition using multi-beam serial-section electron microscopy (sSEM) have allowed researchers to produce terabytes of image data every hour~\cite{hildebrand2017whole}.
+It is not feasible for domain experts to manually reconstruct thousands or millions of neurons from this vast amount of image data~\cite{haehn2014design}.
+State-of-the-art automatic reconstruction approaches use pixel-based segmentation with convolutional neural networks (CNNs) followed by agglomeration strategies~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image,lee2015recursive,ronneberger2015u}.
+%TODO DOUBLE CHECK REFERENCES
+These \textit{bottom-up pixel-based} algorithms produce excellent results but still fall short of acceptable error rates for large volumes.
 
-Segmenting the image stack into a label volume is a substantial component of this reconstruction process.
-In a label volume, every voxel receives a segment label corresponding to a unique neuron. 
-Voxels with the same label belong to the same neuron.
-It is not feasible for domain experts to manually segment the vast amount of 3-D image data to model an entire brain.
-Here we introduce a scalable top-down segmentation algorithm that also leverages local information.
-The top-down partitioning strategy allows us to apply domain-specific constraints to the segmentation task.
-
-A significant amount of research focuses on automatic reconstruction of the neurons in EM images~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image}.
-%TODO DOUBLE CHECK REFERENCES
-All of these algorithms extract neuronal processes through the 3-D volumes using the raw image data as input.
-Oftentimes, convolutional neural networks (CNNs) predict membrane probabilities or affinities between voxels and apply simple thresholds to agglomerate the voxels into clusters~\cite{lee2015recursive,ronneberger2015u}.
-These \textit{pixel-based} algorithms produce excellent results but currently fall short of complete reconstructions with error rates of approximately $X\%$. %TODO ADD ERROR RATES
-
-\begin{figure*}[h!]
+\begin{figure*}[t!]
 	\centering
-	\includegraphics[width=0.22\linewidth]{./figures/pipeline/image.png}
+	(a) \includegraphics[width=0.18\linewidth]{./figures/pipeline/image.png}
 	\hspace{0.025\linewidth}
-	\includegraphics[width=0.22\linewidth]{./figures/pipeline/affinities.png}
+	(b) \includegraphics[width=0.18\linewidth]{./figures/pipeline/affinities.png}
 	\hspace{0.025\linewidth}
-	\includegraphics[width=0.22\linewidth]{./figures/pipeline/watershed.png}
+	(c) \includegraphics[width=0.18\linewidth]{./figures/pipeline/watershed.png}
 	\hspace{0.025\linewidth}
-	\includegraphics[width=0.22\linewidth]{./figures/pipeline/neuroproof.png}
-	\caption{An overview of an existing pipeline in segmentation for connectomics.
-From left to right: the original EM image data, the output of a CNN predicting voxel affinities, clustering of the affinities using a watershed algorithm, an agglomeration of the supervoxels into larger segments.}
+	(d) \includegraphics[width=0.18\linewidth]{./figures/pipeline/neuroproof.png}
+	\caption{An overview of a pixel-based connectomics segmentation pipeline.
+(a) Original EM image data (b) Output of a CNN predicting voxel affinities (c) Clustering of the affinities using a watershed algorithm (d) Agglomeration of the super-voxels into larger segments.}
 	\label{fig:pipeline}
@@
 
-Researchers currently address the failures of these pixel-based algorithms by training random-forest classifiers to agglomerate an oversegmentation of voxels~\cite{nunez2014graph,10.1371/journal.pone.0125825}.
-These classifiers take the output of the pixel-based algorithms as input and generate high-level statistics such as affinity distributions between pixel regions. 
-Presently, these methods use hand-designed features despite the evidence that machine-learned features perform better~\cite{bogovic2013learned}. 
-These \textit{region-based} algorithms outperform the pixel-based algorithms but still do not provide the accuracy needed for large scale reconstructions of the brain.
+%Researchers address the failures of these pixel-based algorithms by training random-forest classifiers to agglomerate an oversegmentation of voxels~\cite{nunez2014graph,10.1371/journal.pone.0125825}.
+%These classifiers take the output of the pixel-based algorithms as input and generate high-level statistics such as affinity distributions between regions.
+%Presently, these methods use hand-designed features despite the evidence that machine-learned features perform better~\cite{bogovic2013learned}.
+%These \textit{region-based} algorithms outperform the pixel-based algorithms but do not provide the accuracy needed for large scale reconstructions of the brain.
 
-We present a \textit{segment-based} strategy that extends on the outputs of region-based methods.
-We only take as input a segmentation from a previous agglomeration algorithm and not the raw image data. 
-This allows us to train on connectomics datasets at a resolution and image type different than the test datasets.
-We consider the 3-D skeletons of each segments as a simplification of its shape. 
-We can then quickly extract a graph from the input segmentation using the skeletonization of the segments in the volume.
+%Here we introduce a scalable, top-down segmentation algorithm that also leverages local information.
+%Partitioning globally allows us to apply domain-specific constraints to the segmentation task.
+%We extract a graph representation from the input segmentation.
+%By simplifying the 3-D segments by their skeletons, we can quickly generate the graph nodes and edges.
 
-We add edge weights to our graph using a 3-D CNN to predict the probabilities that nearby segments belong to the same neuron.
-Using a graph-based optimization strategy enables us to enforce domain-specific global constraints such as the underlying neuronal biology.
-From here we apply a global partitioning algorithm that minimizes a cost function of separating adjacent nodes in the graph.
+We present a \textit{top-down graph-based} method that builds on the outputs of bottom-up pixel-based segmentation approaches (Fig.~\ref{fig:teaser}a).
+We first extract 3D skeletons from the input segmentation (Fig.~\ref{fig:teaser}b) and generate a simplified 3D graph (Fig.~\ref{fig:teaser}c).
+We train a 3D CNN classifier on the agglomerated regions in the segmentation data to detect errors.
+During test time, we run the classifier to populate the graph edge weights with error probabilities.
+We then use a graph optimization algorithm to partition the graph into the final reconstruction by enforcing domain-specific global constraints from the underlying biology (Fig.~\ref{fig:teaser}d).
 
-Our method takes the output of any bottom-up segmentation strategy and creates a graph on top of this segmentation. 
-We enforce domain-specific global constraints by reasoning at the graph level.
-This strategy scales to massive connectomics datasets and improves accuracy over existing methods.
+Our approach operates at a level of abstraction above existing pixel-based methods.
+This allows us to leverage both local and global information to produce more accurate reconstructions.
+Because it uses agglomerated regions our classifier is independent of image resolution and acquisition parameters, enabling its application to isotropic and anisotropic image data without retraining.
+Using the 3D graph of the segmentation allows us to enforce global constraints on the reconstruction that closely follow the underlying biology, such as limiting the angles of neuron branchings to the biologically plausible range.
+We can also use local information such as shape priors to weight the edges in our graph.
+This dual approach of assessing local decisions in a global context yields accuracy improvements over the existing reconstruction methods.
+
+This work makes the following following contributions: (1) a novel top-down graph-based method for neural reconstruction of connectomics data; (2) a region-based CNN classifier to detect errors under global constraints; (3) an empirical evaluation of our method on several connectomics datasets; (4) our method yields improved performance over the state-of-the-art on X out of Y datasets, and competitive results on the remaining data.
+On average, we improve the Variation of Information (VI) metric across all datasets by X percent without drastically increasing the running time.

### 2017-11-13 papers/cvpr2018/1_related_work.tex
added HP comments

--- 2017-11-10 papers/cvpr2018/1_related_work.tex
@@
+% !TEX root =  paper.tex
 \section{Related Work}
 
-A significant amount of research in computer vision focuses on the segmentation of images \cite{zaitoun2015survey}. 
-Here, we review some of the most successful methods that have been applied to large-scale EM images. Figure \ref{fig:pipeline} shows the results of a typical segmentation pipeline on these images.
+A significant amount of research in computer vision focuses on the segmentation of images~\cite{zaitoun2015survey}.
+Here, we review some of the most successful methods that have been applied to large-scale EM images in connectomics.
+Fig.~\ref{fig:pipeline} shows the results of a typical connectomics segmentation pipeline.
 
-\paragraph{Pixel-based methods.}
+%\paragraph{Pixel-based methods.}
 
-A large amount of connectomics research considers the problem of extracting segmentation information at the voxel level from the raw EM images to produce label volumes.
-Some early techniques apply computationally expensive graph partitioning algorithms with a single node per voxel~\cite{andres2012globally}, however these methods do not scale to terabyte datasets.
-Since then, several methods train 2-D CNNs to predict membrane probabilities per image slice~\cite{ciresan2012deep,jain2010boundary,kaynig2015large,rhoananet,amelio_segmentation}. 
-More recent strategies augment these neural networks with the $z$-dimension creating full 3-D CNNs~\cite{lee2015recursive,ronneberger2015u}.
+A large amount of connectomics research considers the problem of extracting segmentation information at the pixel (i.e., voxel) level from the raw EM images.
+Some early techniques apply computationally expensive graph partitioning algorithms with a single node per pixel~\cite{andres2012globally}.
+However these methods do not scale to terabyte datasets.
+More recent methods train classifiers to predict membrane probabilities per image slice either using 2D~\cite{ciresan2012deep,jain2010boundary,kaynig2015large,seymour2016rhoananet,amelio_segmentation} or 3D CNNs~\cite{lee2015recursive,ronneberger2015u}.\hp{add more refs}
+
 Oftentimes these networks produce probabilities for the affinity between two voxels (i.e., the probability that adjacent voxels belong to the same neuron).
 The MALIS cost function is specifically designed for generating affinities that produce good segmentations~\cite{briggman2009maximin}.
-More recently, flood-filling networks produce segmentations by training an end-to-end neural network that takes EM images to label volumes~\cite{januszewski2016flood}.
-These flood-filling networks produce very impressive accuracies but at too high a computational cost.
+\hp{add seung ref} More recently, flood-filling networks produce segmentations by training an end-to-end neural network that goes from EM images directly to label volumes~\cite{januszewski2016flood}.
+These flood-filling networks produce impressive accuracies but at a high computational cost.
 
-\paragraph{Region-based methods.}
+%\paragraph{Region-based methods.}
 
-Several of these pixel-based approaches generate probabilities that neighboring voxels belong to the same neuron.
-Many algorithms build on top of these methods and train random-forest classifiers to produce segmentations of the EM images~\cite{seymour2016rhoananet,nunez2014graph,10.1371/journal.pone.0125825,parag2017anisotropic,zlateski2015image}.
-Despite the success of these classifiers, they often make mistakes based on the local information leading to errors in the segmentation. 
-Lately, many recent advancements in segmentation use artificial neural networks since machine-learned features outperform hand-designed ones~\cite{bogovic2013learned}.
-A significant amount of research focuses on the training and optimization of these deep neural networks~\cite{chatfield2014return,maas2013rectifier,nesterov1983method}.
+%Lately, many recent advancements in segmentation use artificial neural networks since machine-learned features outperform hand-designed ones~\cite{bogovic2013learned}.
+%A significant amount of research focuses on the training and optimization of these deep neural networks~\cite{chatfield2014return,maas2013rectifier,nesterov1983method}.
 
-\paragraph{Segment-based methods.}
+Several pixel-based approaches generate probabilities that neighboring pixels belong to the same neuron.
+Many methods build on top of these methods and train random-forest classifiers \hp{really?} to produce region-based (i.e., super-pixel) segmentations~\cite{seymour2016rhoananet,nunez2014graph,10.1371/journal.pone.0125825,parag2017anisotropic,zlateski2015image}.
+\hp{are these agglomeration techniques based on watershed?}
 
-Some limited research builds on top of the region-based methods to correct errors in the segmentation \cite{rolnick2017morphological,error_correction_using_CNN,haehn2017guided}. 
-However, to our knowledge, we are the first to extract a graph representation from these region-based methods. 
+%\paragraph{Segment-based methods.}
+
+Some recent research builds on top of these region-based methods to correct errors in the segmentation~\cite{rolnick2017morphological,error_correction_using_CNN,haehn2017guided}.
+However, to our knowledge, our method is the first to extract a 3D graph from pixel-based agglomerated segmentations for a true top-down reconstruction approach.
+This allows us to enforce domain-specific constraints using graph-based partitioning algorithms.
 Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for traditional image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}.
-We can enforce domain-specific constraints using graph-based paritioning algorithms.  
-Unfortunately graph partitioning is an NP-Hard problem~\cite{demaine2006correlation}.
-However, there are several useful multicut heuristics which provide good approximations with reasonable computational costs~\cite{horvnakova2017analysis,keuper2015efficient}.
+Even though graph partitioning is an NP-Hard problem~\cite{demaine2006correlation} there are several useful multicut heuristics that provide good approximations with reasonable computational costs~\cite{horvnakova2017analysis,keuper2015efficient}.
+We use the method of X et al.\hp{add ref} to partition the extracted 3D graph into the final neuron reconstruction.

### 2017-11-13 papers/cvpr2018/2_method.tex
added HP comments

--- 2017-11-10 papers/cvpr2018/2_method.tex
@@
 
-There are two types of errors that can occur in image segmentation problems.
+There are two types of errors that can occur in connectomics segmentation.
 The first, called a split error, occurs when there are two segments that should have been merged.
 The second, called a merge error, happens when one segment should be split into two.
-Generally, it is much more difficult to correct merge errors than to correct split errors (CITE). 
-Our method takes as input an oversegmentation of an $EM$ image volume where there are many more split errors than merge errors.
-Our goal is to identify locations of split errors and merge the corresponding segments.
-Section~\ref{sec:neuroproof} discusses two pipelines for generating these segmentations.
+Generally, it is much more difficult to correct merge errors than to correct split errors (CITE)\hp{add}, which is why most reconstruction approaches are tuned towards over-segmentation with many more split than merge errors.
+Our method takes as input over-segmentations of EM image volumes generated by state-of-the-art connectomics reconstruction pieplines (Sec.~\ref{sec:neuroproof}).
+Our goal is to identify locations of split errors and merge the corresponding segments automatically.
 
@@
 Ideally, our graph has edges corresponding to all of the segments which were erroneously split with few edges between correctly split segments.
-We generate a skeleton for every segment following the intuition that a skeleton represents a simplified representation of the overall shape of an object. 
-We locate merge candidates and produce corresponding edges based on these skeletons.
-A CNN generates the edge weights by learning a merge function given two segments as input. 
+We generate a skeleton for every segment based on the intuition that a skeleton represents a simplified representation of the overall shape of the neuron.
+We generate a simplified 3D graph from the skeletons by locating merge candidates and producing corresponding edges.\hp{check prior sentence} We train a CNN to  generate the edge weights by learning a merge function from ground truth data.
 A multicut heuristic generates a partition on the graph where nodes in the same partition are assigned the same output label.
-Thus there are three major components to our framework: skeletonization for constructing a graph, network training for determining edge weights, and graph-partitioning using a multicut heuristic algorithm.
+We will now discuss the three major components to our framework (skeletonization, CNN, and graph-partition) in more detail.
+\hp{stopped here}
 

### 2017-11-13 papers/cvpr2018/paper.tex
added HP comments

@@
 
+\newcommand{\hp}[1]{\textcolor{red}{HP: #1}}
+
 % Pages are numbered in submission mode, and unnumbered in camera-ready
@@
 %%%%%%%%% TITLE
-\title{Top-down Segment-based Neuron Reconstruction}
+\title{Top-Down Graph-Based Neuron Reconstruction}
 
@@
 \begin{figure}[t]\footnotesize
-	\vspace{-2.04in}
+	\vspace{-2.3in}
 	\begin{minipage}{\textwidth}
-		\begin{minipage}{0.125\textheight}
+		\begin{minipage}{0.2\textwidth}
 			 \includegraphics[width=\linewidth]{figures/schema/teaser-image.png}
-			\includegraphics[width=\linewidth]{figures/schema/teaser-segmentation.png}
+			(a)\includegraphics[width=\linewidth]{figures/schema/teaser-segmentation.png}
 		\end{minipage}
-		\begin{minipage}{0.24\textwidth}
-			\includegraphics[width=\linewidth]{figures/schema/pre-multicut.png}
+		\begin{minipage}{0.2\textwidth}
+			(b)\includegraphics[width=\linewidth]{figures/schema/pre-multicut.png}
 		\end{minipage}
-		\begin{minipage}{0.34\textwidth}
-			\includegraphics[width=\linewidth]{figures/schema/multicut-graph.png}
+		\begin{minipage}{0.3\textwidth}
+			(c)\includegraphics[width=\linewidth]{figures/schema/multicut-graph.png}
 		\end{minipage}
-		\begin{minipage}{0.24\textwidth}
-			\includegraphics[width=\linewidth]{figures/schema/post-multicut.png}
+		\begin{minipage}{0.2\textwidth}
+			(d)\includegraphics[width=\linewidth]{figures/schema/post-multicut.png}
 		\end{minipage}
-		\caption{To reconstruct neurons, we take as input the results of a region-based agglomeration algorithm.
-We extract a graph from this segmentation and apply a partitioning algorithm with local and global features to improve accuracy.}
+		\caption{Outline of our approach.
+(a) Raw EM image data (top) and results of pixel-based segmentation and agglomeration algorithms (bottom).
+(b) Extracted 3D skeleton from the segmentation.
+(c) Simplified 3D graph with error probabilities from trained classifier (schematic).
+(d) Result of graph partitioning algorithm with local and global geometric features (schematic).
+(d) Improved 3D reconstruction.}
 		\label{fig:teaser}
@@
 \begin{abstract}
-Advancements in electron microscopy image acquisition have created massive connectomics datasets which are petabytes in size and make manual segmentation infeasible. 
-Proposed methods for automatic segmentations generate super-pixel approximations of neural membranes followed by agglomeration strategies to create full neuron reconstructions. 
-However, pixel-based segmentation results widely neglect global geometric properties.
-We generate skeletons of membrane labels to approximate neural pathways in 3D.
-This allows us to efficiently apply graph-based optimization strategies and to train automatic classifiers for shape description against manually labeled ground truth.
-Our classifiers detect feasible and impossible neural pathways by looking at geometric properties alone, and are able to improve the segmentation labels accordingly.
-We demonstrate the performance of our classifiers on multiple real-world connectomics datasets with average variation of information improvement of $X\times$.
-We discuss our findings and provide insights to learning shape features for neuron agglomeration.
+Advancements in electron microscopy image acquisition have created massive connectomics datasets in the terabyte range that make manual reconstruction of neuronal structures infeasible.
+Current state-of-the-art automatic methods segment neural membranes at the pixel level followed by agglomeration methods to create full neuron reconstructions.
+However, these approaches widely neglect global geometric properties that are inherent in the graph structure of neural wiring diagrams.
+Instead, we follow bottom-up pixel-based reconstruction by a top-down graph-based method to more accurately approximate neural pathways.
+Using the membrane labels of the pixel-based segmentation we first generate skeletons in 3D.
+Using this 3D graph we train automatic classifiers for shape description to detect impossible neural pathways by looking at geometric properties.
+We then apply efficient graph-based optimization strategies to improve the segmentation labels.
+We demonstrate the performance of our approach on multiple real-world connectomics datasets with average variation of information improvement of $X\times$.
+The paper provides insights into learning shape features for top-down graph-based neuron reconstruction.
 \end{abstract}

### 2017-11-14 papers/cvpr2018/1_related_work.tex
paper: addressed HP comments

@@
 However these methods do not scale to terabyte datasets.
-More recent methods train classifiers to predict membrane probabilities per image slice either using 2D~\cite{ciresan2012deep,jain2010boundary,kaynig2015large,seymour2016rhoananet,amelio_segmentation} or 3D CNNs~\cite{lee2015recursive,ronneberger2015u}.\hp{add more refs}
+More recent methods train classifiers to predict membrane probabilities per image slice either using 2D~\cite{ciresan2012deep,jain2010boundary,kaynig2015large,seymour2016rhoananet,amelio_segmentation} or 3D CNNs~\cite{lee2015recursive,ronneberger2015u,turaga2010convolutional}.
 
@@
 Several pixel-based approaches generate probabilities that neighboring pixels belong to the same neuron.
-Many methods build on top of these methods and train random-forest classifiers \hp{really?} to produce region-based (i.e., super-pixel) segmentations~\cite{seymour2016rhoananet,nunez2014graph,10.1371/journal.pone.0125825,parag2017anisotropic,zlateski2015image}.
-\hp{are these agglomeration techniques based on watershed?}
+Often a watershed algorithm will cluster pixels into small super-pixels~\cite{zlateski2015image}. 
+Many methods build on top of these strategies and train random-forest classifiers to produce region-based (i.e., super-pixel) segmentations~\cite{seymour2016rhoananet,nunez2014graph,10.1371/journal.pone.0125825,parag2017anisotropic,zlateski2015image}.
 
@@
 Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for traditional image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}.
-Even though graph partitioning is an NP-Hard problem~\cite{demaine2006correlation} there are several useful multicut heuristics that provide good approximations with reasonable computational costs~\cite{horvnakova2017analysis,keuper2015efficient}.
-We use the method of X et al.\hp{add ref} to partition the extracted 3D graph into the final neuron reconstruction.
+Even though graph partitioning is an NP-Hard problem~\cite{demaine2006correlation} there are several useful multicut heuristics that provide good approximations with reasonable computational costs~\cite{horvnakova2017analysis}.
+We use the method of Keuper et al.
+to partition the extracted 3D graph into the final neuron reconstruction~\cite{keuper2015efficient}.

### 2017-11-14 papers/cvpr2018/2_method.tex
paper: addressed HP comments

@@
 The second, called a merge error, happens when one segment should be split into two.
-Generally, it is much more difficult to correct merge errors than to correct split errors (CITE)\hp{add}, which is why most reconstruction approaches are tuned towards over-segmentation with many more split than merge errors.
+Generally, it is much more difficult to correct merge errors than to correct split errors~\cite{parag2015properties}, which is why most reconstruction approaches are tuned towards over-segmentation with many more split than merge errors.
 Our method takes as input over-segmentations of EM image volumes generated by state-of-the-art connectomics reconstruction pieplines (Sec.~\ref{sec:neuroproof}).
@@
 We generate a skeleton for every segment based on the intuition that a skeleton represents a simplified representation of the overall shape of the neuron. 
-We generate a simplified 3D graph from the skeletons by locating merge candidates and producing corresponding edges.\hp{check prior sentence} We train a CNN to  generate the edge weights by learning a merge function from ground truth data.
+From this skeleton we quickly identify potential merge locations and produce the corresponding edges for the graph. 
+We train a CNN to  generate the edge weights by learning a merge function from ground truth data.
 A multicut heuristic generates a partition on the graph where nodes in the same partition are assigned the same output label.

### 2017-11-14 papers/cvpr2018/3_evaluation.tex
paper: added HP comments

--- 2017-11-10 papers/cvpr2018/3_evaluation.tex
@@
+% !TEX root =  paper.tex
 \section{Evaluation}
-
-We evaluate our schema on two different connectomics datasets, one anisotropic and the other isotropic, from two different species.
 
@@
 \label{sec:dataset}
-\paragraph{Kasthuri.}
-The Kasthuri dataset images the neocortex of a mouse brain produced by a scanning electron microscope \cite{kasthuri2015saturated}. 
+
+We use the following two datasets for training and experimental evaluation.
+
+\paragraph{\bf Kasthuri.}
+The Kasthuri dataset consists of scanning electron microscope images of the neocortex of a mouse brain~\cite{kasthuri2015saturated}.
 This dataset is $5342 \times 3618 \times 338$ voxels in size.
@@
 We downsample the dataset in the $x$ and $y$ dimensions to give a final resolution of $\SI[product-units=single]{6 x 6 x 30}{\nano\meter}^3$ per voxel.
-We divide the dataset into two volumes along the $x$ dimension.
-Thus, each volume is $\SI[product-units=single]{8.0 x 10.9 x 10.1}{\micro\meter}^3$.
+We divide the dataset into two volumes along the $x$ dimension where each volume is $\SI[product-units=single]{8.0 x 10.9 x 10.1}{\micro\meter}^3$.
 
-\paragraph{FlyEM.}
-The FlyEM dataset comes from the mushroom body of a 5-day old adult male \textit{Drosophila} fly imaged by a focused ion-beam milling scanning electron microscopy.  
-The mushroom body is this species is the major site of associative learning \cite{takemura2017connectome}. 
+\paragraph{\bf FlyEM.}
+The FlyEM dataset comes from the mushroom body of a 5-day old adult male Drosophila fly imaged by a focused ion-beam milling scanning electron microscopy.
+\hp{add ref} The mushroom body in this species is the major site of associative learning~\cite{takemura2017connectome}.
 The original dataset contains a $\SI[product-units=single]{40 x 50 x 120}{\micro\meter}^3$ volume of which we use two cubes of size $\SI[product-units=single]{10 x 10 x 10}{\micro\meter}^3$.
-The resolution of this dataset is $\SI[product-units=single]{10 x 10 x 10}{\nano\meter}^3$ so each volume has $1000$ voxels in each dimension.
+The resolution of this dataset is $\SI[product-units=single]{10 x 10 x 10}{\nano\meter}^3$ or $1000$ voxels in each dimension in each of the two volumes.
 
-\paragraph{Segmentation Pipeline and Baseline.}
+\subsection{Pixel-Based Segmentation Pipelines}
 \label{sec:neuroproof}
-The segmentation on the Kasthuri dataset was computed by agglomerating 3D supervoxels produced by zwatershed from 3D affinity predictions~\cite{zlateski2015image}. 
-A recent study by Funke et.al. demonstrated superior performance of such method over existing ones on anisotropic data \cite{schlegel2017learning}. 
-We learned 3d affinities in x,y,z using MALIS loss with a U-net~\cite{Turaga:2009,ronneberger2015u}. 
-We apply the zwatershed algorithm, with suitable parameters, to compute an 3D over-segmentation of the volume. 
-The resulting 3D over-segmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}. 
-The VI values at different stopping thresholds of agglomeration correspond to the points on the curve plotted in Figure YYY.
 
-We have collected two $1000 \times 1000 \times 1000$ voxel ($\SI[product-units=single]{10x10x10}{\micro\meter}^3$) volumes from the authors~\cite{takemura2017connectome}. 
-Based on the authors' suggestion, we applied the context-aware delayed agglomeration algorithm~\cite{10.1371/journal.pone.0125825} that shows improved performance on this dataset than the pipeline used in the original publication.
+The segmentation on the Kasthuri dataset was computed by agglomerating 3D supervoxels produced by the z-watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}.
+A recent study by Funke et al.~\cite{schlegel2017learning} demonstrated superior performance of such methods over existing ones on anisotropic data.
+We learn 3D affinities using MALIS loss with a U-net~\cite{Turaga:2009,ronneberger2015u}.
+We apply the z-watershed algorithm with suitable parameters to compute a 3D oversegmentation of the volume.
+The resulting 3D oversegmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}.
+
+For the FlyEM data we collected two $1000 \times 1000 \times 1000$ voxel ($\SI[product-units=single]{10x10x10}{\micro\meter}^3$) volumes from the authors~\cite{takemura2017connectome}.
+Based on the authors' suggestion, we applied a context-aware delayed agglomeration algorithm~\cite{10.1371/journal.pone.0125825} that shows improved performance on this dataset over the pipeline used in the original publication.
 This segmentation framework learns voxel and supervoxel classifiers with an emphasis to minimize under-segmentation error.
-At the same time this framework produces lower over-segmentation than standard algorithms. 
-This algorithm first computes multi-channel 3D predictions for membranes, cell interiors, and mitochondria, among other cell features. 
-The membrane prediction channel is utilized to produce an over-segmented volume using 3D watershed, which is then agglomerated hierarchically up to a certain confidence threshold. 
-We used exactly same parameters for the publicly available code for this algorithm and used different agglomerations thresholds to plot the VI error curve.
+At the same time this framework produces lower oversegmentation than standard algorithms.
+The algorithm first computes multi-channel 3-D predictions for membranes, cell interiors, and mitochondria, among other cell features.
+The membrane prediction channel is used to produce an over-segmented volume using 3D watershed, which is then agglomerated hierarchically up to a certain confidence threshold.
+We used exactly the same parameters as the publicly available code for this algorithm.
 
-\subsection{Pruning via Skeletonization}
+\subsection{Error Metric}
+\label{sec:variation-of-information}
 
-We prune potential merge candidates by running Algorithm \ref{alg:skeletonization} on the input dataset. 
-There are two essential parameters to the algorithm: $t_{low}$ and $t_{high}$. 
+We evaluate the performance of the different methods using the split version of variance of information~\cite{meila2003comparing}.
+Given a ground truth labeling $GT$ and our automatically reconstructed segmentation $SG$.
+Over and under-segmentation are quantified by the conditional entropy $H(GT | SG)$ and $H(SG | GT)$, respectively.
+Since we are measuring the entropy between two clusterings, better split variation of information scores are closer to the origin.
+The variation of information values of the original segmentation approaches at different stopping thresholds of agglomeration for both algorithms are shown in Fig.~\ref{fig:variation-of-information}.
+\hp{check}
+
+\subsection{Graph Creation Parameters}
+
+There are two essential parameters to the edge generation algorithm described in Section~\ref{sec:skeletonization}: $t_{low}$ and $t_{high}$.
 Ideally, the merge candidates output by this algorithm will contains all possible positive examples with a very limited number of negative examples.
-After considering various thresholds, we find that $t_{low} = \SI{240}{\nano\meter}$ and $t_{high} = \SI{600}{\nano\meter}$ produces the best results given this objective function. 
-Note that these thresholds are in nanometers and not voxels. 
-Connectomics datasets often have different sample resolutions and downsampling in $z$. 
+After considering various thresholds, we find that $t_{low} = \SI{240}{\nano\meter}$ and $t_{high} = \SI{600}{\nano\meter}$ produce the best results considering this objective.
+
+In our implementation we use nanometers for these thresholds and not voxels.
+Connectomics datasets often have lower sample resolutions in $z$.
 Using nanometers allows us to have uniform units across all of these datasets and calculate the thresholds in voxels at runtime.
-The thresholds are $t_{low} = (40, 40, 8)$ voxels and $t_{high} = (100, 100, 20)$ voxels for the Kasthuri dataset $t_{low} = (24, 24, 24)$ voxels and $t_{high} = (60, 60, 60)$ voxels for the FlyEM dataset.
-The thresholds are anisotropic or isotropic depending on the corresponding isotropy of the dataset.
-Table \ref{table:skeletonization} shows the overall success of this method of candidate pruning.
+For example, the thresholds in voxels are $t_{low} = (40, 40, 8)$ and $t_{high} = (100, 100, 20)$ for the anisotropic Kasthuri dataset and $t_{low} = (24, 24, 24)$ and $t_{high} = (60, 60, 60)$ for the isotropic FlyEM dataset.
+
+Table \ref{table:skeletonization} shows the overall success of our graph creation method with candidate pruning.
+\hp{not clear what this table is showing--explain.
+put this in the experiment section where you discuss the results}
 
 \subsection{Classifier Training}
+\label{sec:network-parameters}
 
-We use the Kasthuri Vol. 1 dataset for training and validation. 
-We train on 80\% of the potential merge candidates for this volume.
-The validation the neural network classifier on the remaining 20\% of candidates. 
+We use the first cylinder of the Kasthuri dataset \hp{check} for training and validation. We train on 80\% of the potential merge candidates for this volume.
+We validate the CNN classifier on the remaining 20\% of candidates.
+We apply data augmentation to the generated examples to increase the size of the training datasets.
+We consider all rotations of $90$ degrees along the $xy$-plane in addition to mirroring along the $x$ and $z$ axes.
+This produces 16 times more training data.
+
 We consider networks with varying input sizes, optimizers, loss functions, filter sizes, learning rates, and activation functions.
 The supplemental material includes information on the experiments that determined these final parameters.
-Table \ref{table:architecture} provides the parameters in the final network.
+Table~\ref{table:architecture} provides the parameters of the final network.
 There are 7,294,705 learnable parameters in our final architecture.
@@
 	\end{tabular}
-	\caption{Parameters for the CNN}
+	\caption{Training parameters.}
 	\label{table:architecture}
@@
 
-\paragraph{Data Augmentation.}
-We apply data augmentation to the generated examples to increase the size of the training datasets. 
-We consider all rotations of $90$ degrees along the $xy$-plane in addition to mirroring along the $x$ and $z$ axes. 
-This produces 16 times more training data.
+%\subsection{Graph-based Strategies}
 
-\subsection{Graph-based Strategies}
-
-Applying a top-down globally optimal partitioning function allows us to enforce some domain-specific constraints on the reconstruction.
-In connectomics, we want to enforce the topological restrictions that each partition in the graph has a genus of zero. 
-The greedy-additive heuristic solves the multicut graph partitioning problem by enforcing this constraint.
-Previous agglomeration strategies at the per-region level consider neighboring superpixels in order of merge probability. 
-These superpixels are clustered hierarchically without concern for global constraints.
-We compare the benefits of a top-down partitioning function versus the traditional bottom-up clustering methods.
-
-\subsection{Variation of Information}
-
-We evaluate the performance of our methods using the split version of the variance of information~\cite{meila2003comparing}. 
-Consider a ground truth labeling $GT$ and our automatically reconstructed segmentation $SG$. 
-Over and undersegmentation are quanitified by the conditional entropy $H(GT | SG)$ and $H(SG | GT)$ respectively. 
-Since we are measuring the entropy between two clusterings, better split variation of information scores are closer to the origin.
+%Applying a top-down globally optimal partitioning function allows us to enforce some domain-specific constraints on the reconstruction.
+%In connectomics, we want to enforce the topological restrictions that each partition in the graph has a genus of zero.
+%The greedy-additive heuristic solves the multicut graph partitioning problem by enforcing this constraint.
+%Previous agglomeration strategies at the per-region level consider neighboring superpixels in order of merge probability.
+%These superpixels are clustered hierarchically without concern for global constraints.
+%We compare the benefits of a top-down partitioning function versus the traditional bottom-up clustering methods.

### 2017-11-14 papers/cvpr2018/1_related_work.tex

@@
 The MALIS cost function is specifically designed for generating affinities that produce good segmentations~\cite{briggman2009maximin}.
-\hp{add seung ref} More recently, flood-filling networks produce segmentations by training an end-to-end neural network that goes from EM images directly to label volumes~\cite{januszewski2016flood}.
+More recently, flood-filling networks produce segmentations by training an end-to-end neural network that goes from EM images directly to label volumes~\cite{januszewski2016flood}.
 These flood-filling networks produce impressive accuracies but at a high computational cost.

### 2017-11-14 papers/cvpr2018/2_method.tex
paper: added Toufiq comments

@@
+% !TEX root =  paper.tex
 \section{Method}
@@
 	\includegraphics[width=0.92\linewidth]{./figures/skeleton2.png}
-	\caption{Skeletons using the TEASER algorithm.}
+	\caption{Example skeletons (in white) extracted from segments (blue and green) using the TEASER algorithm.}
 	\label{fig:skeletonization}
@@
 
-From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with weights $w_e$.
+From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with non-negative edge weights $w_e$.
 The nodes correspond to label segments from the segmentation with edges between segments considered for merging.
-Ideally, our graph has edges corresponding to all of the segments which were erroneously split with few edges between correctly split segments.
-We generate a skeleton for every segment based on the intuition that a skeleton represents a simplified representation of the overall shape of the neuron. 
-From this skeleton we quickly identify potential merge locations and produce the corresponding edges for the graph. 
-We train a CNN to  generate the edge weights by learning a merge function from ground truth data.
-A multicut heuristic generates a partition on the graph where nodes in the same partition are assigned the same output label.
-We will now discuss the three major components to our framework (skeletonization, CNN, and graph-partition) in more detail.
-\hp{stopped here}
+Ideally, our graph has edges corresponding to all of the segments that were erroneously split.
+To compute this graph we generate a skeleton for every segment in the pixel-based segmentation.
+The skeleton is a simplified representation of the overall shape of the neurons.
+From this skeleton we  identify potential merge locations and produce the corresponding edges for the graph.
+To find actual merges we run a classification CNN to generate edge weights that correspond to probabilites of merging.
+We then use a multicut heuristic to generate a partition on the graph where nodes in the same partition are assigned the same output label in the improved segmentation.
+We will now discuss the three major components to our framework (graph creation, edge probabilities, and graph partitioning) in more detail.
 
@@
 \label{sec:skeletonization}
-We generate nodes $N$ and edges $E$ to apply a graph-based optimization strategy for segmentation.
-In addition, these edges receive non-negative weights.
+
+%We generate nodes $N$ and edges $E$ to apply a graph-based optimization strategy for segmentation.
+%In addition, these edges receive non-negative weights.
 
@@
 The simplest node generation strategy creates one node for every unique segment label in the input volume.
-However, some of the millions of labels in the volume correspond to very small volumes.
-Usually these locations have noisy image data so the pixel-based methods could not provide enough information to generate a larger segment.
+However, some of the millions of labels in the volume correspond to very small structures that are likely the result of segmentation errors.
+This typically happens in regions with noisy image data such that pixel-based methods could not generate the correct segments.
 It is difficult to extract useful shape features from these segments because of their small, and often random, shape.
-We prune these nodes from the graph by removing all segments with fewer than $20,000$ voxels.
-This removes XX\% of segments on a typical connectomics dataset.
+We prune these nodes from the graph by removing all segments with fewer than a threshold of $t_{seg}$ voxels.
+We use $t_{seg} = 20,000$ voxels, which removed on average XX\% \hp{add} of the segments in our  datasets (Sec.~\ref{sec:dataset}).
 
@@
 
-A na\"ive approach to generating edges produces an edge between all adjacent segments.
+A typical approach to generating edges produces an edge between all adjacent segments.
 Two segments $l_1$ and $l_2$ are considered adjacent if there is a pair of adjacent voxels where one has label $l_1$ and the other has label $l_2$.
-NeuroProof and GALA consider all pairs of adjacent segments for merging.
-For us, this method produces too many edges in the graph.
-Therefore we present the following algorithm to identify pairs of segments to consider for merging.
+For example, pixel-based agglomeration methods such as NeuroProof~\cite{} and GALA~\cite{} \hp{add refs} consider all pairs of adjacent segments for merging.
+However, this method produces too many edges in the graph for graph-based optimization approaches.
+We identify a smaller number of pairs of segments to consider as graph edges using the following algorithm.
 
 First, we extract a skeleton from each segment using the TEASER algorithm~\cite{sato2000teasar,zhao2014automatic}.
-Figure~\ref{fig:skeletonization} shows the skeletons in white of two segments from the label volume.
-These skeletons consist of a sequence of \textit{joints}, locations that are a local maximum distance from the segment boundary, with line segments connecting successive joints.
-We prune the joints that are within $50$ voxels of each other to reduce unnecessary branching.
+Fig.~\ref{fig:skeletonization} shows an example of two extracted skeletons (in white) of two segments from the label volume.
+These skeletons consist of a sequence of \textit{joints}, i.e., locations that are a local maximum distance from the segment boundary, with line segments connecting successive joints.
+We prune the joints that are within $t_{jnt} = 50$ voxels of each other to reduce unnecessary branching.
 For the purposes of our algorithm, joints that have only one connected neighbor are referred to as \textit{endpoints}.
-Many of the segments that are erroneously split follow a similar pattern (Figure~\ref{fig:merge_candidates}).
-In these split instances the two skeletons have nearby endpoints.
+Many of the segments that are erroneously split have nearby endpoints  (Fig.~\ref{fig:merge_candidates}).
+We will make use of this fact to merge segments with the following two-pass heuristic.
 
-After skeletonization, we begin to identify segments for merge consideration with the following two-pass heuristic.
-In the first pass, we iterate over all endpoints $e$ belonging to a segment $S$ and create a set of segments $\mathbb{S}_e^\prime$ that includes all labels that have a single voxel within $t_{low}$ voxels from $e$.
-Elements of these sets are candidates for merging.
-However the first pass often has too many candidates that should remain split so we apply an additional pass for further pruning.
-In the second pass, we consider all of the segments $\mathbb{S}_e^\prime$ for every endpoint $e$.
+In the first pass, we iterate over all endpoints $e$ belonging to a segment $S$ and create a set of segments $\mathbb{S}_e^\prime$ that includes all labels that are within $t_{low}$ voxels from $e$.
+Elements of $\mathbb{S}_e^\prime$ are candidates for merging.
+However, this first pass often leads to too many candidates, requiring an additional pass for further pruning.
+In the second pass, we consider all of the segments in $\mathbb{S}_e^\prime$ for every endpoint $e$.
 If a segment $S^\prime \in \mathbb{S}_e^\prime$ has an endpoint within $t_{high}$ voxels of $e$, the segment $S$ and $S^\prime$ are considered for merging.
-We store the midpoint between the two endpoints as the ``center" of the potential merge.
+We store the midpoints between the two endpoints as the center of the potential merges in the set $\mathbb{S}_c$.
 
@@
 	\includegraphics[width=0.92\linewidth]{./figures/split_error2.png}
-	\caption{Two erroneously split segments.}
+	\caption{Two erroneously split segments. \hp{split in top figure impossible to see - use brighter colors. both figures are too dark - increase brightness of segments}}
 	\label{fig:merge_candidates}
@@
 
-The previous section outlines how to generate edges between nodes in our graph structure.
-Here we introduce a neural network architecture for generating probabilities that two nodes sharing an edge belong to the same neuron.
-The neural network takes as input only data from the input segmentation.
+Our non-negative edge weights $w_e$ correspond to probabilities that two endpoints $e$ in $\mathbb{S}_c$ belong to the same neuron and should be merged.
+\hp{check} To compute these probabilities we train a 3D CNN classifier using the oversegmentation input volume and corresponding manually labeled ground truth data (Sec.~\ref{sec:dataset}).
 
-\subsubsection{Network Architecture}
+\subsubsection{Classifier Input}
 
-Our graph generation algorithm produces 3-D locations that require further consideration for merging.
-To determine which of these segments should actually merge, we train a 3-D CNN using the oversegmentation and the corresponding manually labeled ground truth data (Section~\ref{sec:dataset}).
-We extract a cubic region of interest around these locations as input to the CNN.
+We extract a cubic region of interest around each endpoints $e$ in $\mathbb{S}_c$ as input to the CNN.
 These regions of interest provide the local information for the neural network to predict which neighboring segments belong to the same neuron.
-
-The networks receives three input channels for every voxel in the region of interest around segments $l_1$ and $l_2$.
-The input to all of the channels is in the set $\{-0.5, 0.5\}$.
+The CNN receives three input channels for every voxel in the region of interest around segments $l_1$ and $l_2$.
+The input in all of the channels is in the range $\{-0.5, 0.5\}$.
 The first channel is $0.5$ only if the corresponding voxel has label $l_1$.
@@
 
-Figure~\ref{fig:architecture} provides an overview of our architecture.
-Our network architecture has three layers of double convolutions followed by a max pooling step following the work of Chatfield et al.
-that found this technique improves on single convolution layers~\cite{chatfield2014return}.
+\subsubsection{Network Architecture \& Training}
+
+Fig.~\ref{fig:architecture} provides an overview of our CNN architecture.
+Similar to Chatfield et al.~\cite{chatfield2014return} it consists of three layers of double convolutions followed by a max pooling step.
 The first max pooling layer is anisotropic with pooling only in the $x$ and $y$ dimensions.
-The output after this final pooling step is flattened into a 1-D vector which is input into two fully connected layers.
-The final layer produces a probability with a sigmoid activation function~\cite{funahashi1989approximate}.
+The output of this final pooling step is flattened into a 1D vector that is input into two fully connected layers.
+The final layer produces probabilities with a sigmoid activation function~\cite{funahashi1989approximate}.
 All of the other activation functions are LeakyReLU~\cite{maas2013rectifier}.
-We use a stochastic gradient descent optimizer with Nesterov's accelerated gradient~\cite{nesterov1983method}.
-There are dropouts of $0.2$ after every pooling layer and the first dense layer, and a dropout of $0.5$ after the final dense layer to prevent overfitting.
-We discuss all other network parameters in Section~\ref{sec:network-parameters}.
+
+We use a stochastic gradient descent optimizer with Nesterov's accelerated gradient~\cite{nesterov1983method} for training.
+We employ dropouts of $0.2$ after every pooling layer and the first dense layer, and a dropout of $0.5$ after the final dense layer to prevent overfitting.
+We discuss all other network parameters in Sec.~\ref{sec:network-parameters}.
 
@@
 	\includegraphics[width=0.95\linewidth]{figures/architecture.png}
-	\caption{The architecture for the neural networks follows the \textit{VGG} style of double convolutions followed by a max pooling operation.
-The number of filters doubles each layer leading to a fully connected layer and a sigmoid activation function.}
+	\caption{The architecture for our classification CNN uses double convolutions followed by max pooling.
+The number of filters doubles each layer, with a final fully connected layer and sigmoid activation function.}
 	\label{fig:architecture}
@@
 
-After constructing the graph structure we apply a graph-based segmentation strategy.
-There are many graph partitioning minimization functions that provide different constraints on their output.
-Neurons in the brain should be acyclic (i.e. the output shape should have a genus of zero).
-We enforce this constraint by finding a multicut partition of the graph that generates a \textit{forest} on the nodes.
-A forest is a partitioning of a graph into a set of trees (i.e. no segment has a cycle).
-There are several heuristics that solve the multicut problem (which is NP-Hard).
-We use the greedy-additive algorithm~\cite{keuper2015efficient}.
+After constructing the 3D graph we apply graph-based partitioning to compute the final segmentation.
+Using graph partitioning from the top down allows us to apply biological constraints on the output.
+Neuroscientists know that neuronal connectivity graphs in the brain are acyclic (i.e., the graphs have a genus of zero).
+We enforce this constraint by finding a multicut partition of the graph that generates a \textit{forest} of nodes.
+A forest is a partitioning of a graph into a set of trees where no segment has a cycle.
+To solve this constraing multicut problem we use the method by Keuper et al.~\cite{keuper2015efficient} that produces a feasible solution by greedy additive edge contraction.
+Adding additional constraints and improving the graph partition algorithm are areas for future work.

### 2017-11-14 papers/cvpr2018/paper.tex

@@
 			 \includegraphics[width=\linewidth]{figures/schema/teaser-image.png}
-			(a)\includegraphics[width=\linewidth]{figures/schema/teaser-segmentation.png}
+			\includegraphics[width=\linewidth]{figures/schema/teaser-segmentation.png}
 		\end{minipage}
 		\begin{minipage}{0.2\textwidth}
-			(b)\includegraphics[width=\linewidth]{figures/schema/pre-multicut.png}
+			\includegraphics[width=\linewidth]{figures/schema/pre-multicut.png}
 		\end{minipage}
 		\begin{minipage}{0.3\textwidth}
-			(c)\includegraphics[width=\linewidth]{figures/schema/multicut-graph.png}
+			\includegraphics[width=\linewidth]{figures/schema/multicut-graph.png}
 		\end{minipage}
 		\begin{minipage}{0.2\textwidth}
-			(d)\includegraphics[width=\linewidth]{figures/schema/post-multicut.png}
+			\includegraphics[width=\linewidth]{figures/schema/post-multicut.png}
+		\end{minipage}
+		\begin{minipage}{0.221\textwidth}
+			\begin{center}
+				(a)
+			\end{center}
+		\end{minipage}
+		\begin{minipage}{0.221\textwidth}
+			\begin{center}
+				(b)
+			\end{center}
+		\end{minipage}
+		\begin{minipage}{0.160\textwidth}
+			\begin{center}
+				(c)
+			\end{center}
+		\end{minipage}
+		\begin{minipage}{0.160\textwidth}
+			\begin{center}
+				(d)
+			\end{center}
+		\end{minipage}
+		\begin{minipage}{0.221\textwidth}
+			\begin{center}
+				(e)
+			\end{center}
 		\end{minipage}
@@
 (d) Result of graph partitioning algorithm with local and global geometric features (schematic).
-(d) Improved 3D reconstruction.}
+(e) Improved 3D reconstruction.}
 		\label{fig:teaser}
@@
 
-%%%%%%%%% BODY TEXT
+%%%%%%%%	% BODY TEXT
 \input{0_introduction}

### 2017-11-14 papers/cvpr2018/0_introduction.tex
Donglai's rough pass on sec1-3

@@
 \section{Introduction}
-
+\donglai{usually, top-down means split.. but we are also bottom-up, but with different representation}
 The field of connectomics is concerned with reconstructing the wiring diagram of the brain at nanometer resolutions to enable new insights into the workings of the brain~\cite{kasthuri2015saturated,haehn2017scalable}.

### 2017-11-14 papers/cvpr2018/2_method.tex
Donglai's rough pass on sec1-3

@@
 The second, called a merge error, happens when one segment should be split into two.
-Generally, it is much more difficult to correct merge errors than to correct split errors~\cite{parag2015properties}, which is why most reconstruction approaches are tuned towards over-segmentation with many more split than merge errors.
+Generally, it is much more difficult to correct merge errors than to correct split errors,
+as the space of possible split proposals grow quickly~\cite{parag2015properties},.
+Thus, most reconstruction approaches are tuned towards over-segmentation with many more split than merge errors.
 Our method takes as input over-segmentations of EM image volumes generated by state-of-the-art connectomics reconstruction pieplines (Sec.~\ref{sec:neuroproof}).
@@
 We then use a multicut heuristic to generate a partition on the graph where nodes in the same partition are assigned the same output label in the improved segmentation.
-We will now discuss the three major components to our framework (graph creation, edge probabilities, and graph partitioning) in more detail.
+We will now discuss the three major components to our framework (graph creation, edge weights assignment, and graph partitioning) in more detail.
 
@@
 \label{sec:skeletonization}
-
+\donglai{need some overview sentence}
 %We generate nodes $N$ and edges $E$ to apply a graph-based optimization strategy for segmentation.
@@
 
-\subsection{Edge Probabilities}
-
-Our non-negative edge weights $w_e$ correspond to probabilities that two endpoints $e$ in $\mathbb{S}_c$ belong to the same neuron and should be merged.
-\hp{check} To compute these probabilities we train a 3D CNN classifier using the oversegmentation input volume and corresponding manually labeled ground truth data (Sec.~\ref{sec:dataset}).
+\subsection{Edge Weights Assignment}
+We aim to assign non-negative edge weights $w_e$, where adjacent nodes (endpoints $e$ in $\mathbb{S}_c$) connected with a big edge weight has higher chance to be merged to the same segment.
+Instead of using handcrafted features to compute the similarity between adjacent nodes, we train a 3D CNN classifier to learn from the manually labeled oversegmentation input volume (Sec.~\ref{sec:dataset}).
+%Our  edge weights  correspond to probabilities that two endpoints $e$ in $\mathbb{S}_c$ belong to the same neuron and should be merged. \hp{check}
 

### 2017-11-14 papers/cvpr2018/3_evaluation.tex
Donglai's rough pass on sec1-3

@@
 \section{Evaluation}
+In this section, we describe the dataset, evaluation metric ...
+\donglai{current organization is a bit unnatural.. too much details/overhead for the experiment setup, which can be put in the supplementary}
 
@@
 
-\paragraph{\bf Kasthuri.}
+\noindent\textbf{Kasthuri.}
 The Kasthuri dataset consists of scanning electron microscope images of the neocortex of a mouse brain~\cite{kasthuri2015saturated}.
@@
 
-\paragraph{\bf FlyEM.}
+\noindent\textbf{FlyEM.}
 The FlyEM dataset comes from the mushroom body of a 5-day old adult male Drosophila fly imaged by a focused ion-beam milling scanning electron microscopy.
@@
 
-We evaluate the performance of the different methods using the split version of variance of information~\cite{meila2003comparing}.
+We evaluate the performance of the different methods using the split version of variance of information~\cite{meila2003comparing} (VI-s).
 Given a ground truth labeling $GT$ and our automatically reconstructed segmentation $SG$.
 Over and under-segmentation are quantified by the conditional entropy $H(GT | SG)$ and $H(SG | GT)$, respectively.
-Since we are measuring the entropy between two clusterings, better split variation of information scores are closer to the origin.
-The variation of information values of the original segmentation approaches at different stopping thresholds of agglomeration for both algorithms are shown in Fig.~\ref{fig:variation-of-information}.
-\hp{check}
+Since we are measuring the entropy between two clusterings, better VI-s scores are closer to the origin.
+In Fig.~\ref{fig:variation-of-information}, we compute VI-s scores for the input over-segmentation result at different stopping thresholds of agglomeration.
 
@@
 
-Table \ref{table:skeletonization} shows the overall success of our graph creation method with candidate pruning.
+%Table \ref{table:skeletonization} shows the overall success of our graph creation method with candidate pruning.
 \hp{not clear what this table is showing--explain.

### 2017-11-14 papers/cvpr2018/paper.tex
Donglai's rough pass on sec1-3

@@
 \newcommand{\hp}[1]{\textcolor{red}{HP: #1}}
+\newcommand{\donglai}[1]{\textcolor{blue}{[Donglai: #1]}}
 
@@
 \begin{abstract}
-Advancements in electron microscopy image acquisition have created massive connectomics datasets in the terabyte range that make manual reconstruction of neuronal structures infeasible.
+Advancements in electron microscopy image acquisition hour have created massive connectomics datasets in the terabyte range that make manual reconstruction of neuronal structures infeasible.
 Current state-of-the-art automatic methods  segment neural membranes at the pixel level followed by agglomeration methods to create full neuron reconstructions.
 However, these approaches widely neglect global geometric properties that are inherent in the graph structure of neural wiring diagrams.
-Instead, we follow bottom-up pixel-based reconstruction by a top-down graph-based method to more accurately approximate neural pathways.
+
+In this work, we follow bottom-up pixel-based reconstruction by a top-down graph-based method to more accurately approximate neural pathways. 
 Using the membrane labels of the pixel-based segmentation we first generate skeletons in 3D.
@@
 We demonstrate the performance of our approach on multiple real-world connectomics datasets with average variation of information improvement of $X\times$.
-The paper provides insights into learning shape features for top-down graph-based neuron reconstruction.
+%The paper provides insights into learning shape features for top-down graph-based neuron reconstruction.
 \end{abstract}
+%%%%%%%%	% BODY TEXT
+\vspace{0.3in}
 
-%%%%%%%%	% BODY TEXT
 \input{0_introduction}

### 2017-11-14 algorithms/cpp-multicut.cpp
small changes to master before switch

@@ -23,8 +23,9 @@ unsigned char *CppMulticut(unsigned long nvertices, unsigned long nedges, unsign
     for (unsigned long ie = 0; ie < nedges; ++ie) {
         graph.insertEdge(vertex_ones[ie], vertex_twos[ie]);
 
-        // a low beta value encouranges not merging
-        weights[ie] = log(edge_weights[ie] / (1.0 - edge_weights[ie])) + log((1 - beta) / beta);
+        // a low beta value encouranges not merging - note the edge_weights are probability of merging
+        // compared to the original greedy-additive algorithm which was probablity of boundary
+        weights[ie] = log(edge_weights[ie] / (1.0 - edge_weights[ie])) + log((1.0 - beta) / beta);
     }
 
     // create empty edge labels and call the kernighan-lin algorithm

### 2017-11-14 algorithms/multicut.pyx

@@ -7,7 +7,7 @@ cimport numpy as np
 import ctypes
 
 import ibex.cnns.skeleton.util
-from ibex.transforms import seg2seg
+from ibex.transforms import seg2seg, seg2gold
 from ibex.utilities import dataIO
 from ibex.data_structures import unionfind
 from ibex.evaluation.classification import *
@@ -22,7 +22,7 @@ cdef extern from 'cpp-multicut.h':
 
 
 # collapse the edges from multicut
-def CollapseGraph(segmentation, candidates, collapsed_edges, probabilities):
+def CollapseGraph(segmentation, gold, candidates, collapsed_edges, probabilities):
     # read the candidates
     ncandidates = len(candidates)
 
@@ -32,8 +32,6 @@ def CollapseGraph(segmentation, candidates, collapsed_edges, probabilities):
     for iv in range(ncandidates):
         ground_truth[iv] = candidates[iv].ground_truth
         predictions[iv] = 1 - collapsed_edges[iv]
-        #if predictions[iv] and not ground_truth[iv]:
-        #    print '{} {} {}'.format(iv, candidates[iv].labels, probabilities[iv])
 
     # output the results for multicut
     PrecisionAndRecall(ground_truth, predictions)
@@ -52,9 +50,36 @@ def CollapseGraph(segmentation, candidates, collapsed_edges, probabilities):
         unionfind.Union(union_find[label_one], union_find[label_two])
 
     # create a mapping for the labels
-    mapping = np.zeros(max_value, dtype=np.uint64)
+    mapping = np.zeros(max_value, dtype=np.int64)
     for iv in range(max_value):
         mapping[iv] = unionfind.Find(union_find[iv]).label
+
+    # find the largest number that were connected
+    max_label = np.amax(mapping) + 1
+    nunions = np.zeros(max_label, dtype=np.int64)
+
+    for iv in range(max_value):
+        nunions[mapping[iv]] += 1
+
+    # go through all unions and see if they are correct
+    seg2gold_mapping = seg2gold.Mapping(segmentation, gold)
+    correct = np.ones(max_label, dtype=np.bool)
+    for iv in range(max_value):
+        # if this candidate iv has a different ground truth to the sample it maps to (ignore missing ground truth)
+        if seg2gold_mapping[mapping[iv]] != seg2gold_mapping[iv] and seg2gold_mapping[iv]:
+            correct[mapping[iv]] = False
+
+    # output results
[…]

### 2017-11-14 cnns/skeleton/__init__.py

@@ -2,3 +2,4 @@
 from train import Train
 from forward import Forward
 from generate_features import GenerateFeatures
+from oracle import Oracle

### 2017-11-14 cnns/skeleton/generate_features.py

@@ -111,27 +111,7 @@ def FindNeighboringCandidates(segmentation, centroid, candidates, maximum_distan
                 neighbor_label = segmentation[iz,iy,ix]
                 candidates.add(neighbor_label)
 
-@jit(nopython=True)
-def Baseline(segmentation, baseline_candidates):
-    # find all candidates that have adjacent voxels
-    zres, yres, xres = segmentation.shape
 
-    for iz in range(zres):
-        for iy in range(yres):
-            for ix in range(xres):
-                if not segmentation[iz,iy,ix]: continue
-                label = segmentation[iz,iy,ix]
-
-                # get the 6-connected neighbors to this segment
-                if iz and segmentation[iz-1,iy,ix]:
-                    baseline_candidates.add((label, segmentation[iz-1,iy,ix]))
-                    baseline_candidates.add((segmentation[iz-1,iy,ix], label))
-                if iy and segmentation[iz,iy-1,ix]:
-                    baseline_candidates.add((label, segmentation[iz,iy-1,ix]))
-                    baseline_candidates.add((segmentation[iz,iy-1,ix], label))
-                if ix and segmentation[iz,iy,ix-1]:
-                    baseline_candidates.add((label, segmentation[iz,iy,ix-1]))
-                    baseline_candidates.add((segmentation[iz,iy,ix-1], label))
 
 # generate features for this prefix
 def GenerateFeatures(prefix, threshold, maximum_distance, network_distance, endpoint_distance, training_data):
@@ -147,35 +127,6 @@ def GenerateFeatures(prefix, threshold, maximum_distance, network_distance, endp
     # remove small connceted components
     segmentation = seg2seg.RemoveSmallConnectedComponents(segmentation, threshold=threshold).astype(np.int64)
     max_label = np.amax(segmentation) + 1
-
-    # get the set of baseline candidates
-    baseline_candidates = set()
-    baseline_candidates.add((np.int64(0), np.int64(0)))
-
-    Baseline(segmentation, baseline_candidates)
-
-    baseline_positive = []
-    baseline_negative = []
-
-    for candidate in baseline_candidates:
-        label_one = candidate[0]
-        label_two = candidate[1]
-
-        if not label_one or not label_two: continue
-
-        # only consider (label_one, label_two) where label_two is larger
-        if (label_two <= label_one): continue
-        if not seg2gold_mapping[label_one] or not seg2gold_mapping[label_two]: continue
-
[…]

### 2017-11-14 transforms/seg2gold.pyx

@@ -12,7 +12,7 @@ def Mapping(segmentation, gold, low_threshold=0.10, high_threshold=0.80):
     cdef np.ndarray[int, ndim=3, mode='c'] cpp_gold
     cpp_gold = np.ascontiguousarray(gold, dtype=ctypes.c_int32)
 
-    max_segmentation = np.amax(segmentation)
+    max_segmentation = np.amax(segmentation) + 1
 
     cdef long *mapping = CppMapping(&(cpp_segmentation[0,0,0]), &(cpp_gold[0,0,0]), segmentation.size, low_threshold, high_threshold)
 

### 2017-11-14 utilities/dataIO.py

@@ -2,6 +2,8 @@ import os
 import h5py
 import numpy as np
 from ibex.data_structures import meta_data, swc
+from ibex.utilities.constants import *
+
 
 def GetWorldBBox(prefix):
     # return the bounding box for this segment
@@ -31,6 +33,11 @@ def ReadH5File(filename, dataset=None):
     # return the data
     return data
 
+
+
+def IsIsotropic(prefix):
+    resolution = Resolution(prefix)
+    return (resolution[IB_Z] == resolution[IB_Y]) and (resolution[IB_Z] == resolution[IB_X])
 
 
 def WriteH5File(data, filename, dataset):

### 2017-11-14 papers/cvpr2018/2_method.tex
paper: added qualitative results

@@
 We prune these nodes from the graph by removing all segments with fewer than a threshold of $t_{seg}$ voxels.
-We use $t_{seg} = 20,000$ voxels, which removed on average XX\% \hp{add} of the segments in our  datasets (Sec.~\ref{sec:dataset}).
+We use $t_{seg} = 20,000$ voxels, which removed on average 56\% of the segments in our  datasets (Sec.~\ref{sec:dataset}).
+Despite the large number of segments, these regions only take up 1.6\% of the total volume on average.
 
@@
 Two segments $l_1$ and $l_2$ are considered adjacent if there is a pair of adjacent voxels where one has label $l_1$ and the other has label $l_2$.
-For example, pixel-based agglomeration methods such as NeuroProof~\cite{} and GALA~\cite{} \hp{add refs} consider all pairs of adjacent segments for merging.
+For example, pixel-based agglomeration methods such as NeuroProof~\cite{10.1371/journal.pone.0125825} and GALA~\cite{nunez2014graph} consider all pairs of adjacent segments for merging.
 However, this method produces too many edges in the graph for graph-based optimization approaches.

### 2017-11-14 papers/cvpr2018/3_evaluation.tex
paper: added qualitative results

@@
 \noindent\textbf{FlyEM.}
-The FlyEM dataset comes from the mushroom body of a 5-day old adult male Drosophila fly imaged by a focused ion-beam milling scanning electron microscopy.
-\hp{add ref} The mushroom body in this species is the major site of associative learning~\cite{takemura2017connectome}.
+The FlyEM dataset comes from the mushroom body of a 5-day old adult male Drosophila fly imaged by a focused ion-beam milling scanning electron microscopy~\cite{takemura2017connectome}.
+The mushroom body in this species is the major site of associative learning.
 The original dataset contains a $\SI[product-units=single]{40 x 50 x 120}{\micro\meter}^3$ volume of which we use two cubes of size $\SI[product-units=single]{10 x 10 x 10}{\micro\meter}^3$.
@@
 
-We use the first cylinder of the Kasthuri dataset \hp{check} for training and validation. We train on 80\% of the potential merge candidates for this volume.
+We use the left cylinder of the Kasthuri dataset for training and validation. We train on 80\% of the potential merge candidates for this volume.
 We validate the CNN classifier on the remaining 20\% of candidates.

### 2017-11-14 papers/cvpr2018/4_results.tex
paper: added qualitative results

@@
+\begin{figure*}[t!]
+	\centering
+	\includegraphics[width=0.23\linewidth]{./figures/variation_of_information-microns-train-600.png}
+	\includegraphics[width=0.23\linewidth]{./figures/variation_of_information-microns-test-600.png}
+	\includegraphics[width=0.23\linewidth]{./figures/variation_of_information-FlyEM-train-600.png}
+	\includegraphics[width=0.23\linewidth]{./figures/variation_of_information-FlyEM-test-600.png}
+	\caption{Our improvement (reD) on variation of information from the baseline NeuroProof segmentation (green). The blue dot represents an oracle which correctly partitions the graph.}
+	\label{fig:variation-of-information}
+\end{figure*}
+
 \section{Results}
+
+\subsection{Variation of Information Improvement}
+
+We compute the variation of information for our segmentations against the expert-labeled ground truth datasets. 
+The input segmentation to our network serves as a baseline. 
+We evaluate NeuroProof (our input) at several different thresholds to create a variation of information curve. 
+Figure \ref{fig:variation-of-information} shows the results on the datasets compared to the baseline (green) and an oracle (blue). 
+The oracles sees the graph from our algorithm and correctly partitions the graph based on the ground truth. 
+%TODO{Our methods decreases the split variation of information by a factor of XX\% and only increases the merge variation of information by a factor of XX\% on the test datasets.}
+Figure \ref{fig:positive-results} shows some successful merges on the Kasthuri Vol. 2. 
+Several of these successful examples combine multiple consecutive segments. 
+The third example shows the correction of an oversegmented dendrite. 
+Figure \ref{fig:negative-results} shows some errors made. 
+In two of these examples the algorithm correctly predicted several merges but made just one error.
+In the third example, an error in the initial segmentation propagated in our pipeline. 
+In the next three subsections we show how each step in the pipeline contributes to this final result.
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=0.85\linewidth]{./figures/multicut-correct1.png}
+	\includegraphics[width=0.85\linewidth]{./figures/multicut-correct2.png}
+	\includegraphics[width=0.85\linewidth]{./figures/multicut-correct3.png}
+	\includegraphics[width=0.85\linewidth]{./figures/multicut-correct4.png}
+	\includegraphics[width=0.85\linewidth]{./figures/multicut-correct5.png}
+	\caption{Some correctly predicted results from our framework.}
+	\label{fig:positive-results}
+\end{figure}
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=0.85\linewidth]{./figures/multicut-incorrect1.png}
+	\includegraphics[width=0.85\linewidth]{./figures/multicut-incorrect2.png}
+	\includegraphics[width=0.85\linewidth]{./figures/multicut-incorrect3.png}
+	\includegraphics[width=0.85\linewidth]{./figures/multicut-incorrect4.png}
+	\caption{Mistakes made by the proposed framework.}
+	\label{fig:negative-results}
+\end{figure}
 
@@
 
-\begin{figure}[t!]
+\begin{figure}[h!]
 	\centering
@@
 
-\begin{table}
+Table \ref{table:classification} shows the precision and recall for all of the datasets. 
+Since, our method does not rely on the image data, we can train the network on an anisotropic dataset and get impressive results on an isotropic dataset.
+
+\begin{table}[h]
 	\centering
@@
 
-Table \ref{table:classification} shows the precision and recall for all of the datasets. 
-Since, our method does not rely on the image data, we can train the network on an anisotropic dataset and get impressive results on an isotropic dataset. 
-Figure \ref{fig:network-results} shows the receiver operating characteristic (ROC) curve for all four datasets.
-
-\begin{figure}
-	\includegraphics[width=0.9\linewidth]{./figures/roc-microns-300-test.png}
-	\caption{(NOT CORRECT) The receiver operating characteristic (ROC) curve for all four datasets.}
-	\label{fig:network-results}
-\end{figure}
-
-TODO - ADD QUALITATIVE RESULTS
-
 \subsection{Graph Based Strategies}
 
-TODO - QUANTIFY IMPROVEMENT BY MULTICUT - READERS CAN SKIP SECTION FOR NOW
+Applying a graph-based optimization strategy increases the accuracy over the CNN alone. 
+In our test datasets, we note an increase in precision on all datasets. 
+For our segmentation problems we prefer a higher precision since it is more difficult to correct merge-errors. 
+Table \ref{table:multicut} shows the changes in precision, recall, and accuracy for all three datasets in relation to the CNN.
 
-Using a graph-based optimization strategy prevents XX segments from merging compared to the simple hierarchical agglomeration strategy with an optimal threshold cut off.
-Since correcting merge errors is significantly more difficult than correcting split errors, it is desirable to limit the number of false merges.
-The graph-based strategies significantly improve this error type.
-
-\subsection{Variation of Information Improvements}
-
-We compute the variation of information for our segmentations against the expert-labeled ground truth datasets. 
-The input segmentation to our network serves as a baseline. 
-We evaluate NeuroProof (our input) at several different thresholds to create a variation of information curve. 
-Similarly, we run the greedy-additive heuristic with varying parameters that increase the probability needed for merging nodes. 
-Figure \ref{fig:variation-of-information} shows the results on the datasets compared to the baseline (green) and an oracle (blue). 
-The oracles sees the entire constructed graph from our algorithm and correctly partitions the graph based on the ground truth. 
-Our methods decreases the split variation of information by a factor of XX\% and only increases the merge variation of information by a factor of XX\% on the test datasets. 
-Table \ref{table:variation-of-information} provides a quantitative overview for the changes in variation of information.
-
-TODO - ADD QUALITATIVE RESULTS
-
-\begin{table}
+\begin{table}[h]
 	\centering
-	\begin{tabular}{c c c} \hline
-		\textbf{Dataset} & \textbf{VI Split} & \textbf{VI Merge} \\ \hline
-		Kasthuri Training &  & \\
-		Kasthuri Testing & & \\
-		FlyEM Vol. 1 & & \\
-		FlyEM Vol. 2 & & \\ \hline
+	\begin{tabular}{c c c c} \hline
+		\textbf{Dataset} & $\Delta$ \textbf{Precision} & $\Delta$ \textbf{Recall} & $\Delta$ \textbf{Accuracy} \\ \hline
+		Kasthuri Training & +3.60\% & -0.01\% & +0.60\% \\
+		Kasthuri Testing & +7.59\% & -1.77\% & +1.38\% \\
+		FlyEM Vol. 1 & +2.68\% & +0.76\% & +0.66\% \\ 
+		FlyEM Vol. 2 & +2.22\% & -1.05\% & +0.29\% \\ \hline
 	\end{tabular}
-	\caption{Variation of Information Change}
-	\label{table:variation-of-information}
+	\caption{Precision and recall for the training and three test datasets.}
+	\label{table:multicut}
 \end{table}
-
-\begin{figure*}[t!]
-	\centering
-	\includegraphics[width=0.42\linewidth]{./figures/variation_of_information-train.png}
-	\hspace{0.085\linewidth}
-	\includegraphics[width=0.42\linewidth]{./figures/variation_of_information-test.png}
-	\caption{The improvement on variation of information from the baseline NeuroProof segmentation (green). Results closer to the origin are better.}
-	\label{fig:variation-of-information}
-\end{figure*}

### 2017-11-14 papers/cvpr2018/2_method.tex
paper: cleaned up wording

@@
 \subsection{Edge Weights Assignment}
-We aim to assign non-negative edge weights $w_e$, where adjacent nodes (endpoints $e$ in $\mathbb{S}_c$) connected with a big edge weight has higher chance to be merged to the same segment.
+We assign non-negative edge weights $w_e$ to each edge where the weight corresponds to the probability two nodes belong to the same neuron.
 Instead of using handcrafted features to compute the similarity between adjacent nodes, we train a 3D CNN classifier to learn from the manually labeled oversegmentation input volume (Sec.~\ref{sec:dataset}).

### 2017-11-14 papers/cvpr2018/3_evaluation.tex
paper: cleaned up wording

@@
 Over and under-segmentation are quantified by the conditional entropy $H(GT | SG)$ and $H(SG | GT)$, respectively.
-Since we are measuring the entropy between two clusterings, better VI-s scores are closer to the origin.
-In Fig.~\ref{fig:variation-of-information}, we compute VI-s scores for the input over-segmentation result at different stopping thresholds of agglomeration.
+Since we are measuring the entropy between two clusterings, better VI scores are closer to the origin.
+In Fig.~\ref{fig:variation-of-information}, we compute VI scores for the input over-segmentation at different stopping thresholds of agglomeration.
 

### 2017-11-15 graphics/render.py
graphics: added rendering functions for blender

@@ -1,0 +1,63 @@
+import numpy as np
+
+from skimage import measure
+from stl import mesh
+
+from ibex.utilities.constants import *
+from ibex.utilities import dataIO
+
+
+from numba import jit
+
+
+@jit(nopython=True)
+def Downsample(segmentation, factor):
+    zres, yres, xres = segmentation.shape
+    newz, newy, newx = (zres / factor[IB_Z], yres / factor[IB_Y], xres / factor[IB_X])
+
+    downsampled_segmentation = np.zeros((newz, newy, newx), dtype=np.int32)
+
+    for iz in range(newz):
+        for iy in range(newy):
+            for ix in range(newx):
+                iw = iz * factor[IB_Z]
+                iv = iy * factor[IB_Y]
+                iu = ix * factor[IB_X]
+
+                downsampled_segmentation[iz,iy,ix] = segmentation[iw,iv,iu]
+
+    return downsampled_segmentation
+
+
+
+# run the marching cube algorithm for these labels
+def MarchingCubes(prefix, labels):
+    downsample_rate = (1, 2, 2)
+    segmentation = Downsample(dataIO.ReadSegmentationData(prefix), downsample_rate)
+    resolution = dataIO.Resolution(prefix)
+
+    for label in labels:
+        binary_image = np.zeros(segmentation.shape, dtype=np.uint8)
+
+        binary_image[segmentation == label] = 1
+
+        # get the meshes from the marching cubes
+        verts, faces, normals, values = measure.marching_cubes_lewiner(binary_image)
+        nverts = verts.shape[0]
+        nfaces = faces.shape[0]
+
+        # center all of the vertices
+        scale_factor = 500.0
+        for iv in range(nverts):
+            verts[iv,0] = resolution[IB_Z] * downsample_rate[IB_Z] * (verts[iv,0] - segmentation.shape[IB_Z] / 2.0) / scale_factor
+            verts[iv,1] = resolution[IB_Y] * downsample_rate[IB_Y] * (verts[iv,1] - segmentation.shape[IB_Y] / 2.0) / scale_factor
+            verts[iv,2] = resolution[IB_X] * downsample_rate[IB_X] * (verts[iv,2] - segmentation.shape[IB_X] / 2.0) / scale_factor
+
+        stl_mesh = mesh.Mesh(np.zeros(nfaces, dtype=mesh.Mesh.dtype))
+        for ii, face in enumerate(faces):
+            for jj in range(3):
[…]

### 2017-11-15 papers/cvpr2018/3_evaluation.tex
paper: updated figures and added HP edits

@@
 % !TEX root =  paper.tex
-\section{Evaluation}
-In this section, we describe the dataset, evaluation metric ...
-\donglai{current organization is a bit unnatural.. too much details/overhead for the experiment setup, which can be put in the supplementary}
+\section{Experimental Results}
+
+We evaluate our method on two connectomics datasets and compare it to a state-of-the-art pixel-based reconstruction method using the variation of information (VI) metric.
+\hp{depending on space we can shorten this and put details into the supplemental material}
 
@@
 We downsample the dataset in the $x$ and $y$ dimensions to give a final resolution of $\SI[product-units=single]{6 x 6 x 30}{\nano\meter}^3$ per voxel.
-We divide the dataset into two volumes along the $x$ dimension where each volume is $\SI[product-units=single]{8.0 x 10.9 x 10.1}{\micro\meter}^3$.
+We divide the dataset into two volumes (Vol.
+1 and Vol.
+2) along the $x$ dimension where each volume is $\SI[product-units=single]{8.0 x 10.9 x 10.1}{\micro\meter}^3$.
 
@@
 
-\subsection{Pixel-Based Segmentation Pipelines}
+\subsection{Pixel-Based Segmentations}
 \label{sec:neuroproof}
@@
 The resulting 3D oversegmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}.
+We use this segmentation as our baseline for comparisons with our method.
 
@@
 
-\subsection{Error Metric}
-\label{sec:variation-of-information}
+\subsection{Graph Generation Parameters}
 
-We evaluate the performance of the different methods using the split version of variance of information~\cite{meila2003comparing} (VI-s).
-Given a ground truth labeling $GT$ and our automatically reconstructed segmentation $SG$.
-Over and under-segmentation are quantified by the conditional entropy $H(GT | SG)$ and $H(SG | GT)$, respectively.
-Since we are measuring the entropy between two clusterings, better VI scores are closer to the origin.
-In Fig.~\ref{fig:variation-of-information}, we compute VI scores for the input over-segmentation at different stopping thresholds of agglomeration.
-
-\subsection{Graph Creation Parameters}
-
-There are two essential parameters to the edge generation algorithm described in Section~\ref{sec:skeletonization}: $t_{low}$ and $t_{high}$.
+There are two essential parameters to the graph generation algorithm described in Section~\ref{sec:skeletonization}: $t_{low}$ and $t_{high}$.
 Ideally, the merge candidates output by this algorithm will contains all possible positive examples with a very limited number of negative examples.

### 2017-11-15 papers/cvpr2018/4_results.tex
paper: updated figures and added HP edits

@@
+% !TEX root =  paper.tex
+
 \begin{figure*}[t!]
 	\centering
-	\includegraphics[width=0.23\linewidth]{./figures/variation_of_information-microns-train-600.png}
-	\includegraphics[width=0.23\linewidth]{./figures/variation_of_information-microns-test-600.png}
-	\includegraphics[width=0.23\linewidth]{./figures/variation_of_information-FlyEM-train-600.png}
-	\includegraphics[width=0.23\linewidth]{./figures/variation_of_information-FlyEM-test-600.png}
-	\caption{Our improvement (reD) on variation of information from the baseline NeuroProof segmentation (green). The blue dot represents an oracle which correctly partitions the graph.}
+	\includegraphics[width=0.45\linewidth]{./figures/variation_of_information-microns-train-600.png}
+	\includegraphics[width=0.45\linewidth]{./figures/variation_of_information-microns-test-600.png}
+	\includegraphics[width=0.45\linewidth]{./figures/variation_of_information-FlyEM-train-600.png}
+	\includegraphics[width=0.45\linewidth]{./figures/variation_of_information-FlyEM-test-600.png}
+	\caption{VI scores of our method (red) compared to the baseline segmentation (green) and an oracle (blue) that optimally partitions the graph based on ground truth.}
 	\label{fig:variation-of-information}
@@
 
-We compute the variation of information for our segmentations against the expert-labeled ground truth datasets. 
-The input segmentation to our network serves as a baseline. 
-We evaluate NeuroProof (our input) at several different thresholds to create a variation of information curve. 
-Figure \ref{fig:variation-of-information} shows the results on the datasets compared to the baseline (green) and an oracle (blue). 
-The oracles sees the graph from our algorithm and correctly partitions the graph based on the ground truth. 
+\subsection{Error Metric}
+\label{sec:variation-of-information}
+
+We evaluate the performance of the different methods using the split version of variance of information~\cite{meila2003comparing} (VI-s).
+Given a ground truth labeling $GT$ and our automatically reconstructed segmentation $SG$.
+Over and under-segmentation are quantified by the conditional entropy $H(GT | SG)$ and $H(SG | GT)$, respectively.
+Since we are measuring the entropy between two clusterings, better VI scores are closer to the origin.
+
+In Fig.~\ref{fig:variation-of-information}, we show VI scores for the input over-segmentation of the Kasthuri data \hp{check} at different thresholds of agglomeration (green) compared to our method (red).
+We also show the comparison to an oracle (blue) that correctly partitions the graph from our algorithm based on ground truth.
+\hp{add discussion of the results}
+
+%The oracles sees the graph from our algorithm and correctly partitions the graph based on the ground truth.
 %TODO{Our methods decreases the split variation of information by a factor of XX\% and only increases the merge variation of information by a factor of XX\% on the test datasets.}
-Figure \ref{fig:positive-results} shows some successful merges on the Kasthuri Vol. 2. 
+
+Fig.~\ref{fig:positive-results} shows successful merges on the Kasthuri Vol.
+2.
 Several of these successful examples combine multiple consecutive segments.
-The third example shows the correction of an oversegmented dendrite. 
-Figure \ref{fig:negative-results} shows some errors made. 
-In two of these examples the algorithm correctly predicted several merges but made just one error.
-In the third example, an error in the initial segmentation propagated in our pipeline. 
-In the next three subsections we show how each step in the pipeline contributes to this final result.
+The third example in the figure shows the correction of an over-segmented dendrite.
+Fig.~\ref{fig:negative-results} shows some failure cases. In two of these examples the algorithm correctly predicted several merges and made one error.
+In the third example a catastrophic merge error \hp{check} in the initial segmentation propagated to the output. We now analyze how each major component of our method contributes to the final result.
 
@@
 	\includegraphics[width=0.85\linewidth]{./figures/multicut-correct5.png}
-	\caption{Some correctly predicted results from our framework.}
+	\caption{Correctly segmented neurons from our method.}
 	\label{fig:positive-results}
@@
 	\includegraphics[width=0.85\linewidth]{./figures/multicut-incorrect4.png}
-	\caption{Mistakes made by the proposed framework.}
+	\caption{Errors made by our method.}
 	\label{fig:negative-results}
@@
 
-\subsection{Pruning via Skeletonization}
+\subsection{Graph Creation}
 
@@
 	\end{tabular}
-	\caption{The results of our pruning heuristic compared to the current baseline.}
+	\caption{The results of our skeleton graph pruning heuristic compared to the baseline segmentation.}
 	\label{table:skeletonization}
@@
 
-Table \ref{table:skeletonization} shows the results of pruning using the skeletonization heuristic.
+Table \ref{table:skeletonization} shows the results of pruning the skeleton graph using the heuristic discussed in Sec.~\ref{sec:skeletonization}.
 The baseline algorithm considers all adjacent regions for merging.
 Our method removes a significant portion of these candidates while maintaining a large number of the true merge locations.
-This edge pruning is essential for the graph partitioning algorithm which has a computational complexity dependence on the number of edges. 
+This edge pruning is essential for the graph partitioning algorithm, which has a computational complexity dependence on the number of edges.
 Our pruning heuristic removes at least $6\times$ the number of edges between correctly split segments on all datasets, achieving a maximum removal ratio of $20\times$.
+
 Equally important is the number of split errors that remain after pruning.
 These are the locations that we want to merge to create a more accurate reconstruction.
-For every dataset, the number of positive candidates remains relatively even. 
+For every dataset, the number of positive candidates \hp{what is a positive candidate?} remains relatively equal.
+\hp{equal to what?}
 However, since our heuristic does not enforce an adjacency constraint of two regions when constructing edges in the graph, the difference does not indicate the number of examples excluded by pruning.
-In fact, our method finds a number of examples which are non-adjacent.
-Figure \ref{fig:skeleton-results} shows two example segments which are split errors.
-The top example our algorithm missed but the segments are adjacent. 
-The bottom example our algorithm found despite the fact that they are not adjacent.
+In fact, our method finds a number of examples that are non-adjacent.
+Figure \ref{fig:skeleton-results} shows two example segments with split errors, one that our algorithm missed (top) and one that it identified (bottom), despite the fact that the split segments are not adjacent.
 
@@
 
-Table \ref{table:classification} shows the precision and recall for all of the datasets. 
-Since, our method does not rely on the image data, we can train the network on an anisotropic dataset and get impressive results on an isotropic dataset.
+Table \ref{table:classification} shows the precision and recall rates for all of the datasets. We can train the CNN on anisotropic data and get good results on isotropic data. \hp{add more discussion}
 
@@
 	\end{tabular}
-	\caption{Precision and recall for the training and three test datasets.}
+	\caption{Precision and recall rates for the training and three test datasets.}
 	\label{table:classification}
@@
 Applying a graph-based optimization strategy increases the accuracy over the CNN alone.
-In our test datasets, we note an increase in precision on all datasets. 
+In our test scores, we note an increase in precision on all datasets.
 For our segmentation problems we prefer a higher precision since it is more difficult to correct merge-errors.
-Table \ref{table:multicut} shows the changes in precision, recall, and accuracy for all three datasets in relation to the CNN.
+Table \ref{table:multicut} shows the changes in precision, recall, and accuracy for all three datasets in relation to the CNN without graph-based optimization.
+\hp{add more discussion}
 

### 2017-11-15 papers/cvpr2018/5_conclusions.tex
paper: major changes
paper: updated figures and added HP edits

--- 2017-10-21 papers/cvpr2018/5_conclusions.tex
@@
+% !TEX root =  paper.tex
 \section{Conclusions}
 
-\begin{itemize}
-	\item Impact
-	\item Future work
-\end{itemize}
+We present a novel method for reconstructing neuronal processes in connectomics datasets.
+We extend existing pixel-based reconstruction strategies using a morphological 3D skeleton graph and show significant accuracy improvement on two datasets from two different species.
+Our approach enables enforcing domain-constraints on the resulting segmentation.
+We believe this approach extends beyond connectomics to other domains with different constraints.
+\hp{add more future work}

### 2017-11-15 papers/cvpr2018/0_introduction.tex
Fix layout and text and images for abstract, section 1, and 2.

--- 2017-11-13 papers/cvpr2018/0_introduction.tex
@@
 
+\begin{figure}[t]
+	\subfloat[]{
+	\includegraphics[width=.47\linewidth]{figures/schema/pre-multicut-with-arrows.pdf}
+	}	
+	\subfloat[]{
+	\includegraphics[width=.47\linewidth]{figures/schema/post-multicut.png}	
+	}
+	\caption{Example improvement of neural reconstruction.
+(a) We extract 3D skeletons from pixel-based segmentation algorithms to create a graph representation with error probabilities indicated by the red arrows.
+(b) We then improve the accuracy of segmentation labels using graph partitioning algorithms with local and global geometric features.}
+	\label{fig:teaser}
+\end{figure}
+
+%\donglai{usually, top-down means split.. but we are also bottom-up, but with different representation}
 The field of connectomics is concerned with reconstructing the wiring diagram of the brain at nanometer resolutions to enable new insights into the workings of the brain~\cite{kasthuri2015saturated,haehn2017scalable}.
@@
 
-\begin{figure*}[t!]
+\begin{figure*}[t]
 	\centering
-	(a) \includegraphics[width=0.18\linewidth]{./figures/pipeline/image.png}
-	\hspace{0.025\linewidth}
-	(b) \includegraphics[width=0.18\linewidth]{./figures/pipeline/affinities.png}
-	\hspace{0.025\linewidth}
-	(c) \includegraphics[width=0.18\linewidth]{./figures/pipeline/watershed.png}
-	\hspace{0.025\linewidth}
-	(d) \includegraphics[width=0.18\linewidth]{./figures/pipeline/neuroproof.png}
+	\subfloat[]{
+	\includegraphics[width=.24\linewidth]{./figures/pipeline/image.png}
+	}	
+	\subfloat[]{
+	\includegraphics[width=.24\linewidth]{./figures/pipeline/affinities.png}	
+	}
+	\subfloat[]{
+	\includegraphics[width=.24\linewidth]{./figures/pipeline/watershed.png}	
+	}
+	\subfloat[]{
+	\includegraphics[width=.24\linewidth]{./figures/pipeline/neuroproof.png}	
+	}		
 	\caption{An overview of a pixel-based connectomics segmentation pipeline.
@@
 
+%
+%\begin{figure*}[t!]
+%	\centering
+%	(a) \includegraphics[width=0.18\linewidth]{./figures/pipeline/image.png}
+%	\hspace{0.025\linewidth}
+%	(b) \includegraphics[width=0.18\linewidth]{./figures/pipeline/affinities.png}
+%	\hspace{0.025\linewidth}
+%	(c) \includegraphics[width=0.18\linewidth]{./figures/pipeline/watershed.png}
+%	\hspace{0.025\linewidth}
+%	(d) \includegraphics[width=0.18\linewidth]{./figures/pipeline/neuroproof.png}
+%	\caption{An overview of a pixel-based connectomics segmentation pipeline.
+(a) Original EM image data (b) Output of a CNN predicting voxel affinities (c) Clustering of the affinities using a watershed algorithm (d) Agglomeration of the super-voxels into larger segments.}
+%	\label{fig:pipeline}
+%\end{figure*}
+%
 %Researchers address the failures of these pixel-based algorithms by training random-forest classifiers to agglomerate an oversegmentation of voxels~\cite{nunez2014graph,10.1371/journal.pone.0125825}.
@@
 
-We present a \textit{top-down graph-based} method that builds on the outputs of bottom-up pixel-based segmentation approaches (Fig.~\ref{fig:teaser}a).
-We first extract 3D skeletons from the input segmentation (Fig.~\ref{fig:teaser}b) and generate a simplified 3D graph (Fig.~\ref{fig:teaser}c).
+We present a \textit{top-down graph-based} method that builds on the outputs of bottom-up pixel-based segmentation approaches.
+We first extract 3D skeletons from the input segmentation (Fig.~\ref{fig:pipeline}) and generate a simplified 3D graph (Fig.~\ref{fig:teaser}a).
 We train a 3D CNN classifier on the agglomerated regions in the segmentation data to detect errors.
 During test time, we run the classifier to populate the graph edge weights with error probabilities.
-We then use a graph optimization algorithm to partition the graph into the final reconstruction by enforcing domain-specific global constraints from the underlying biology (Fig.~\ref{fig:teaser}d).
+We then use a graph optimization algorithm to partition the graph into the final reconstruction by enforcing domain-specific global constraints from the underlying biology (Fig.~\ref{fig:teaser}b).
 

### 2017-11-15 papers/cvpr2018/1_related_work.tex
Fix layout and text and images for abstract, section 1, and 2.

@@
 
-%\paragraph{Pixel-based methods.}
-
+\paragraph{Pixel-based methods.}
 A large amount of connectomics research considers the problem of extracting segmentation information at the pixel (i.e., voxel) level from the raw EM images.
@@
 
-%\paragraph{Region-based methods.}
-
+\paragraph{Region-based methods.}
 %Lately, many recent advancements in segmentation use artificial neural networks since machine-learned features outperform hand-designed ones~\cite{bogovic2013learned}.
 %A significant amount of research focuses on the training and optimization of these deep neural networks~\cite{chatfield2014return,maas2013rectifier,nesterov1983method}.
-
 Several pixel-based approaches generate probabilities that neighboring pixels belong to the same neuron.
@@
 
-%\paragraph{Segment-based methods.}
-
+\paragraph{Segment-based methods.}
 Some recent research builds on top of these region-based methods to correct errors in the segmentation~\cite{rolnick2017morphological,error_correction_using_CNN,haehn2017guided}.

### 2017-11-15 papers/cvpr2018/paper.tex
Fix layout and text and images for abstract, section 1, and 2.

@@
 \usepackage{cvpr}
+\usepackage{subfig}
 \usepackage{times}
@@
 \usepackage{caption}
-\usepackage{subcaption}
+%\usepackage{subcaption}
 \usepackage{booktabs}
@@
 \def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
-
+%
 \newcommand{\hp}[1]{\textcolor{red}{HP: #1}}
@@
 
-% Pages are numbered in submission mode, and unnumbered in camera-ready
+%% Pages are numbered in submission mode, and unnumbered in camera-ready
 \ifcvprfinal\pagestyle{empty}\fi
@@
 %%%%%%%%% TITLE
-\title{Top-Down Graph-Based Neuron Reconstruction}
+\title{Graph-Based Neural Reconstruction from Morphological Skeletons}
 
@@
 
-\author{Brian Matejek\\
-Harvard University\\
-Cambridge, MA 02138, USA\\
-{\tt\small bmatejek@seas.harvard.edu}
-% For a paper whose authors are all at the same institution,
-% omit the following lines up until the closing ``}''.
-% Additional authors and addresses can be added with ``\and'',
-% just like the second author.
-% To save space, use either the email address or home page, not both
-%\and
-%Second Author\\
-%Institution2\\
-%First line of institution2 address\\
-%{\tt\small secondauthor@i2.org}
-}
+%\author{Brian Matejek\\
+%Harvard University\\
+%Cambridge, MA 02138, USA\\
+%{\tt\small bmatejek@seas.harvard.edu}
+%% For a paper whose authors are all at the same institution,
+%% omit the following lines up until the closing ``}''.
+%% Additional authors and addresses can be added with ``\and'',
+%% just like the second author.
+%% To save space, use either the email address or home page, not both
+%%\and
+%%Second Author\\
+%%Institution2\\
+%%First line of institution2 address\\
+%%{\tt\small secondauthor@i2.org}
+%}
 
@@
 %\thispagestyle{empty}
-
-\begin{figure}[t]\footnotesize
-	\vspace{-2.3in}
-	\begin{minipage}{\textwidth}
-		\begin{minipage}{0.2\textwidth}
-			 \includegraphics[width=\linewidth]{figures/schema/teaser-image.png}
-			\includegraphics[width=\linewidth]{figures/schema/teaser-segmentation.png}
-		\end{minipage}
-		\begin{minipage}{0.2\textwidth}
-			\includegraphics[width=\linewidth]{figures/schema/pre-multicut.png}
-		\end{minipage}
-		\begin{minipage}{0.3\textwidth}
-			\includegraphics[width=\linewidth]{figures/schema/multicut-graph.png}
-		\end{minipage}
-		\begin{minipage}{0.2\textwidth}
-			\includegraphics[width=\linewidth]{figures/schema/post-multicut.png}
-		\end{minipage}
-		\begin{minipage}{0.221\textwidth}
-			\begin{center}
-				(a)
-			\end{center}
-		\end{minipage}
-		\begin{minipage}{0.221\textwidth}
-			\begin{center}
-				(b)
-			\end{center}
-		\end{minipage}
-		\begin{minipage}{0.160\textwidth}
-			\begin{center}
-				(c)
-			\end{center}
-		\end{minipage}
-		\begin{minipage}{0.160\textwidth}
-			\begin{center}
-				(d)
-			\end{center}
-		\end{minipage}
-		\begin{minipage}{0.221\textwidth}
-			\begin{center}
-				(e)
-			\end{center}
-		\end{minipage}
-		\caption{Outline of our approach.
-(a) Raw EM image data (top) and results of pixel-based segmentation and agglomeration algorithms (bottom).
-(b) Extracted 3D skeleton from the segmentation.
-(c) Simplified 3D graph with error probabilities from trained classifier (schematic).
-(d) Result of graph partitioning algorithm with local and global geometric features (schematic).
-(e) Improved 3D reconstruction.}
-		\label{fig:teaser}
-	\end{minipage}
-\end{figure}
+%
 
@@
 \begin{abstract}
-Advancements in electron microscopy image acquisition hour have created massive connectomics datasets in the terabyte range that make manual reconstruction of neuronal structures infeasible.
+Advancements in electron microscopy image acquisition have created massive connectomics datasets in the terabyte range that make manual reconstruction of neuronal structures infeasible. 
 Current state-of-the-art automatic methods segment neural membranes at the pixel level followed by agglomeration methods to create full neuron reconstructions. 
 However, these approaches widely neglect global geometric properties that are inherent in the graph structure of neural wiring diagrams.
-
 In this work, we follow bottom-up pixel-based reconstruction by a top-down graph-based method to more accurately approximate neural pathways. 
@@
 %%%%%%%%	% BODY TEXT
-\vspace{0.3in}
 

### 2017-11-15 papers/cvpr2018/0_introduction.tex
Further cleanup.

@@
 
-This work makes the following following contributions: (1) a novel top-down graph-based method for neural reconstruction of connectomics data; (2) a region-based CNN classifier to detect errors under global constraints; (3) an empirical evaluation of our method on several connectomics datasets; (4) our method yields improved performance over the state-of-the-art on X out of Y datasets, and competitive results on the remaining data.
-On average, we improve the Variation of Information (VI) metric across all datasets by X percent without drastically increasing the running time.
+This work makes the following following contributions: (1) a novel top-down graph-based method for neural reconstruction of connectomics data; (2) a region-based CNN classifier to detect errors under global constraints; (3) an empirical evaluation of our method on several connectomics datasets; (4) our method yields improved performance over the state-of-the-art on \FIX{X out of Y} datasets, and competitive results on the remaining data.
+On average, we improve the Variation of Information (VI) metric across all datasets by \FIX{X} percent without drastically increasing the running time.

### 2017-11-15 papers/cvpr2018/2_method.tex
Further cleanup.

@@
 Generally, it is much more difficult to correct merge errors than to correct split errors,
-as the space of possible split proposals grow quickly~\cite{parag2015properties},.
+as the space of possible split proposals grow quickly~\cite{parag2015properties}.
 Thus, most reconstruction approaches are tuned towards over-segmentation with many more split than merge errors.
@@
 From this skeleton we  identify potential merge locations and produce the corresponding edges for the graph.
-To find actual merges we run a classification CNN to generate edge weights that correspond to probabilites of merging.
+To find actual merges we run a classification CNN to generate edge weights that correspond to probabilities of merging.
 We then use a multicut heuristic to generate a partition on the graph where nodes in the same partition are assigned the same output label in the improved segmentation.
@@
 
-\subsection{Graph Creation}
-\label{sec:skeletonization}
+%\subsection{Graph Creation}
+
 \donglai{need some overview sentence}
@@
 
-\subsubsection{Node Generation}
+\subsection{Node Generation}
+%\subsubsection{Node Generation}
+\label{sec:skeletonization}
 
@@
 
-\subsubsection{Edge Generation}
+\subsection{Edge Generation}
 

### 2017-11-15 papers/cvpr2018/3_evaluation.tex
Further cleanup.

@@
 
-\noindent\textbf{Kasthuri.}
+\paragraph{Kasthuri.}
 The Kasthuri dataset consists of scanning electron microscope images of the neocortex of a mouse brain~\cite{kasthuri2015saturated}.
@@
 
-\noindent\textbf{FlyEM.}
+\paragraph{FlyEM.}
 The FlyEM dataset comes from the mushroom body of a 5-day old adult male Drosophila fly imaged by a focused ion-beam milling scanning electron microscopy~\cite{takemura2017connectome}.

### 2017-11-15 papers/cvpr2018/paper.tex
Further cleanup.

@@
 %
+\newcommand{\FIX}[1]{\textcolor{red}{#1}}
 \newcommand{\hp}[1]{\textcolor{red}{HP: #1}}
@@
 We then apply efficient graph-based optimization strategies to improve the segmentation labels.
-We demonstrate the performance of our approach on multiple real-world connectomics datasets with average variation of information improvement of $X\times$.
+We demonstrate the performance of our approach on multiple real-world connectomics datasets with average variation of information improvement of \FIX{$X\times$}.
 %The paper provides insights into learning shape features for top-down graph-based neuron reconstruction.

### 2017-11-15 papers/cvpr2018/5_conclusions.tex
paper: added some future work

@@
 We believe this approach extends beyond connectomics to other domains with different constraints.
-\hp{add more future work}
+
+There is significant room for additional research following this topic. 
+Finding the multicut partition of the graph provides some nice constraints on our reconstruction. 
+However, we can further improve the results by tweaking the partitioning cost functions to more closely match the underlying biology.
+For example, we can take the outputs of synaptic detectors to enforce that a given segment only has post- or pre-synaptic connections.
+
+Additionally, there is a lot of possible information we can extract from the skeletonization of the segments. 
+Currently we use the skeletons to identify potential locations that should merge.
+In the future, we can also find locations that are improperly merged in the input segmentation. 
+Figure \ref{fig:negative-results} shows an error made by our algorithm that follows from a merge-error in the input. 
+By training a CNN on the skeletons themselves, we can also receive information about whether a sequence of segments belong to the same neuron, rather than comparing pairs alone.

### 2017-11-15 algorithms/multicut.pyx

@@ -12,7 +12,7 @@ from ibex.utilities import dataIO
 from ibex.data_structures import unionfind
 from ibex.evaluation.classification import *
 from PixelPred2Seg import comparestacks
-
+import partition_comparison
 
 
 # c++ external definition
@@ -92,7 +92,8 @@ def Multicut(segmentation, gold, candidates, edge_weights, beta):
     segmentation = CollapseGraph(segmentation, candidates, collapsed_edges)
 
     # evaluate before and after multicut
-    comparestacks.Evaluate(segmentation, gold, filtersize=20000, anisotropic=False)
+    print partition_comparison.variation_of_information(segmentation.ravel().astype(np.int64), gold.ravel().astype(np.int64))
+    #comparestacks.Evaluate(segmentation, gold, filtersize=20000, anisotropic=False)
 
 
 

### 2017-11-15 papers/cvpr2018/2_method.tex
paper: updated figures with better meshes and created ROC curve

@@
 	\includegraphics[width=0.92\linewidth]{./figures/skeleton2.png}
-	\caption{Example skeletons (in white) extracted from segments (blue and green) using the TEASER algorithm.}
+	\caption{Example skeletons (in black) extracted from segments (blue and green) using the TEASER algorithm.}
 	\label{fig:skeletonization}
@@
 	\includegraphics[width=0.92\linewidth]{./figures/split_error2.png}
-	\caption{Two erroneously split segments. \hp{split in top figure impossible to see - use brighter colors. both figures are too dark - increase brightness of segments}}
+	\caption{Two erroneously split segments.}
 	\label{fig:merge_candidates}

### 2017-11-15 algorithms/multicut.pyx
paper: changes to multicut

@@ -92,8 +92,8 @@ def Multicut(segmentation, gold, candidates, edge_weights, beta):
     segmentation = CollapseGraph(segmentation, candidates, collapsed_edges)
 
     # evaluate before and after multicut
-    print partition_comparison.variation_of_information(segmentation.ravel().astype(np.int64), gold.ravel().astype(np.int64))
-    #comparestacks.Evaluate(segmentation, gold, filtersize=20000, anisotropic=False)
+    #print partition_comparison.variation_of_information(segmentation.ravel().astype(np.int64), gold.ravel().astype(np.int64))
+    comparestacks.Evaluate(segmentation, gold, filtersize=20000, anisotropic=False)
 
 
 

### 2017-11-15 papers/cvpr2018/0_introduction.tex
paper: BM updates

@@
 %\donglai{usually, top-down means split.. but we are also bottom-up, but with different representation}
-The field of connectomics is concerned with reconstructing the wiring diagram of the brain at nanometer resolutions to enable new insights into the workings of the brain~\cite{kasthuri2015saturated,haehn2017scalable}.
+The field of connectomics is concerned with reconstructing the wiring diagram of the brain at nanometer resolutions to enable new insights into the workings of the brain~\cite{haehn2017scalable,kasthuri2015saturated}.
 Recent advancements in image acquisition using multi-beam serial-section electron microscopy (sSEM) have allowed researchers to produce terabytes of image data every hour~\cite{hildebrand2017whole}.
 It is not feasible for domain experts to manually reconstruct thousands or millions of neurons from this vast amount of image data~\cite{haehn2014design}.
-State-of-the-art automatic reconstruction approaches use pixel-based segmentation with convolutional neural networks (CNNs) followed by agglomeration strategies~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image,lee2015recursive,ronneberger2015u}.
+State-of-the-art automatic reconstruction approaches use pixel-based segmentation with convolutional neural networks (CNNs) followed by agglomeration strategies~\cite{seymour2016rhoananet,lee2015recursive,nunez2014graph,parag2017anisotropic,ronneberger2015u,zlateski2015image}.
 %TODO DOUBLE CHECK REFERENCES
@@
 This allows us to leverage both local and global information to produce more accurate reconstructions.
-Because it uses agglomerated regions our classifier is independent of image resolution and acquisition parameters, enabling its application to isotropic and anisotropic image data without retraining.
-Using the 3D graph of the segmentation allows us to enforce global constraints on the reconstruction that closely follow the underlying biology, such as limiting the angles of neuron branchings to the biologically plausible range.
+Since it uses agglomerated regions, our classifier is independent of image resolution and acquisition parameters, enabling its application to isotropic and anisotropic image data without retraining.
+Using the 3D graph of the segmentation allows us to enforce global constraints on the reconstruction that closely follow the underlying biology.
 We can also use local information such as shape priors to weight the edges in our graph.
@@
 
-This work makes the following following contributions: (1) a novel top-down graph-based method for neural reconstruction of connectomics data; (2) a region-based CNN classifier to detect errors under global constraints; (3) an empirical evaluation of our method on several connectomics datasets; (4) our method yields improved performance over the state-of-the-art on \FIX{X out of Y} datasets, and competitive results on the remaining data.
+This work makes the following following contributions: (1) a novel top-down graph-based method for neural reconstruction of connectomics data; (2) a region-based CNN classifier to detect errors under global constraints; (3) an empirical evaluation of our method on several connectomics datasets; (4) our method yields improved performance over the state-of-the-art on three testing datasets.
 On average, we improve the Variation of Information (VI) metric across all datasets by \FIX{X} percent without drastically increasing the running time.

### 2017-11-15 papers/cvpr2018/2_method.tex
paper: BM updates

@@
 
-\donglai{need some overview sentence}
 %We generate nodes $N$ and edges $E$ to apply a graph-based optimization strategy for segmentation.
@@
 First, we extract a skeleton from each segment using the TEASER algorithm~\cite{sato2000teasar,zhao2014automatic}.
-Fig.~\ref{fig:skeletonization} shows an example of two extracted skeletons (in white) of two segments from the label volume.
+Fig.~\ref{fig:skeletonization} shows an example of two extracted skeletons (in black) of two segments from the label volume.
 These skeletons consist of a sequence of \textit{joints}, i.e., locations that are a local maximum distance from the segment boundary, with line segments connecting successive joints.
@@
 Many of the segments that are erroneously split have nearby endpoints  (Fig.~\ref{fig:merge_candidates}).
-We will make use of this fact to merge segments with the following two-pass heuristic.
+We make use of this fact to merge segments with the following two-pass heuristic.
 
@@
 
-We extract a cubic region of interest around each endpoints $e$ in $\mathbb{S}_c$ as input to the CNN.
+We extract a cubic region of interest around each endpoint $e$ in $\mathbb{S}_c$ as input to the CNN.
 These regions of interest provide the local information for the neural network to predict which neighboring segments belong to the same neuron.
@@
 	\centering
-	\includegraphics[width=0.95\linewidth]{figures/architecture.png}
+	\includegraphics[width=0.85\linewidth]{figures/architecture.png}
 	\caption{The architecture for our classification CNN uses double convolutions followed by max pooling.

### 2017-11-15 papers/cvpr2018/4_results.tex
paper: BM updates

@@
 
-\subsection{Variation of Information Improvement}
-
 \subsection{Error Metric}
@@
 
-We evaluate the performance of the different methods using the split version of variance of information~\cite{meila2003comparing} (VI-s).
-Given a ground truth labeling $GT$ and our automatically reconstructed segmentation $SG$.
-Over and under-segmentation are quantified by the conditional entropy $H(GT | SG)$ and $H(SG | GT)$, respectively.
+We evaluate the performance of the different methods using the split version of variance of information (VI)~\cite{meila2003comparing}. 
+Given a ground truth labeling $GT$ and our automatically reconstructed segmentation $SG$, over and undersegmentation are quantified by the conditional entropy $H(GT | SG)$ and $H(SG | GT)$, respectively.
 Since we are measuring the entropy between two clusterings, better VI scores are closer to the origin.
 
-In Fig.~\ref{fig:variation-of-information}, we show VI scores for the input over-segmentation of the Kasthuri data \hp{check} at different thresholds of agglomeration (green) compared to our method (red).
-We also show the comparison to an oracle (blue) that correctly partitions the graph from our algorithm based on ground truth.
-\hp{add discussion of the results}
+\subsection{Variation of Information Improvement}
 
-%The oracles sees the graph from our algorithm and correctly partitions the graph based on the ground truth.
-%TODO{Our methods decreases the split variation of information by a factor of XX\% and only increases the merge variation of information by a factor of XX\% on the test datasets.}
+In Fig.~\ref{fig:variation-of-information}, we show the VI results of NeuroProof on the Kasthuri and FlyEM data at varying thresholds of agglomeration (green). 
+The green circle represents the variation of information for our input segmentation (a threshold of 0.3 for all datasets). 
+Our results are in red.  
+We show the comparison to an oracle (blue) that correctly partitions the graph from our algorithm based on ground truth.
 
-Fig.~\ref{fig:positive-results} shows successful merges on the Kasthuri Vol.
-2.
-Several of these successful examples combine multiple consecutive segments.
-The third example in the figure shows the correction of an over-segmented dendrite.
-Fig.~\ref{fig:negative-results} shows some failure cases. In two of these examples the algorithm correctly predicted several merges and made one error.
-In the third example a catastrophic merge error \hp{check} in the initial segmentation propagated to the output. We now analyze how each major component of our method contributes to the final result.
+Our algorithm improves the accuracy of the input segmentation on every dataset, reducing the VI split score on average by \FIX{X\%} and only increasing the VI merge score by \FIX{X\%}. 
+Scores closer to the origin are better for this metric, and in every instance we are below the green curve. 
+We see significant improvements on the Kasthuri datasets (VI split reduction of \FIX{X\%} and \FIX{X\%} on the training and testing datasets respectively) and slightly more modest improvements on the FlyEM datasets (reduction of \FIX{X\%} and \FIX{X\%}).
+However, our baseline, NeuroProof performs much better on the FlyEM datasets reducing the potential improvement. 
+Isotropic datasets are easier to segment using state-of-the-art region-based methods than anisotropic ones~\cite{plaza2014annotating}.
+Thus there is less room for improvement on these datasets.
+
+Fig.~\ref{fig:positive-results} shows successful merges on the Kasthuri Vol. 2 dataset. 
+Several of these examples combine multiple consecutive segments that span the volume. 
+In the third example we correct the oversegmentation of a dendrite.
+Fig.~\ref{fig:negative-results} shows some failure cases. 
+In two of these examples the algorithm correctly predicted several merges but made one error.
+In the third example a merge error in the initial segmentation propagated to our output. 
+We now analyze how each major component of our method contributes to this final result.
 
@@
 These are the locations that we want to merge to create a more accurate reconstruction.
-For every dataset, the number of positive candidates \hp{what is a positive candidate?} remains relatively equal.
-\hp{equal to what?}
+For every dataset, the number of true split errors remains constant before and after pruning.
 However, since our heuristic does not enforce an adjacency constraint of two regions when constructing edges in the graph, the difference does not indicate the number of examples excluded by pruning.
@@
 Figure \ref{fig:skeleton-results} shows two example segments with split errors, one that our algorithm missed (top) and one that it identified (bottom), despite the fact that the split segments are not adjacent.
+Of the successful examples in Figure \ref{fig:positive-results}, the second and fourth groupings contain pairs of non-adjacent segments that merge with our algorithm.
 
@@
 
-Table \ref{table:classification} shows the precision and recall rates for all of the datasets. We can train the CNN on anisotropic data and get good results on isotropic data. \hp{add more discussion}
+Figure \ref{fig:receiver-operating-characteristic} shows the receiver operating characteristic (ROC) curve for all of the datasets. 
+We train our CNN using one of the Kasthuri volumes and test using the other three datasets.
+Since our CNN only takes as input a region of the label volume we can train on an anisotropic dataset and infer on an isotropic one. 
+This provides a major benefit given the time-intensive task of manually generating ground truth data at various resolutions.
 
-\begin{table}[h]
+As evidenced by the ROC curve, the test results on the Kasthuri data are better than the results for FlyEM.
+We believe this is in part because of the differences in the datasets (i.e., isotropy and $xy$ resolution). 
+To test this hypothesis, we also evaluate the performance of the FlyEM datasets when the network trains on FlyEM Vol.
+1 and infers on FlyEM Vol.
+2.\footnote{Since the FlyEM datasets have significantly fewer examples, we initialize the network with the weights from the Kasthuri training and have an initial learning rate of $10^{-4}$.}
+The dotted lines in the figure represent these tests. 
+There is a slight performance increase for FlyEM Vol. 2.
+However, the FlyEM datasets have reasonable results when the network is trained by the Kasthuri data, and the results outside of this section follow from that setup.
+
+\begin{figure}
 	\centering
-	\begin{tabular}{c c c c} \hline
-		\textbf{Dataset} & \textbf{Precision} & \textbf{Recall} & \textbf{Accuracy} \\ \hline
-		Kasthuri Training & 0.919 & 0.936 & 0.974 \\
-		Kasthuri Testing & 0.737 & 0.717 & 0.907 \\
-		FlyEM Vol. 1 & 0.796 & 0.478 & 0.862 \\
-		FlyEM Vol. 2 & 0.762 & 0.422 & 0.810 \\ \hline
-	\end{tabular}
-	\caption{Precision and recall rates for the training and three test datasets.}
-	\label{table:classification}
-\end{table}
+	\includegraphics[width=0.95\linewidth]{./figures/receiver-operating-characteristic.jpg}
+	\caption{The receiver operating characteristic for all four datasets.}
+	\label{fig:receiver-operating-characteristic}
+\end{figure}
 
@@
 
-Applying a graph-based optimization strategy increases the accuracy over the CNN alone.
-In our test scores, we note an increase in precision on all datasets.
-For our segmentation problems we prefer a higher precision since it is more difficult to correct merge-errors.
-Table \ref{table:multicut} shows the changes in precision, recall, and accuracy for all three datasets in relation to the CNN without graph-based optimization.
-\hp{add more discussion}
+The graph-based optimization strategy increases our correction accuracy over using just the CNN. 
+In particular, the precision increases on each dataset, although the recall decreases on all but one of the datasets. 
+Since it is more difficult to correct merge errors than split errors, it is often desirable to sacrifice recall for precision. 
+Table \ref{table:multicut} shows the changes in precision, recall, and accuracy for all four datasets compared to the CNN. 
+Over the three testing datasets, applying a graph-based partitioning strategy reduced the number of merge errors by \FIX{X}, \FIX{Y}, and \FIX{Z}.
 

### 2017-11-15 papers/cvpr2018/5_conclusions.tex
paper: BM updates

--- 2017-11-15 papers/cvpr2018/5_conclusions.tex
@@
 We present a novel method for reconstructing neuronal processes in connectomics datasets. 
-We extend existing pixel-based reconstruction strategies using a morphological 3D skeleton graph and show significant accuracy improvement on two datasets from two different species.
+We extend existing region-based reconstruction strategies using a morphological 3D skeleton graph and show significant accuracy improvement on two datasets from two different species. 
 Our approach enables enforcing domain-constraints on the resulting segmentation. 
 We believe this approach extends beyond connectomics to other domains with different constraints.
-\hp{add more future work}
+
+There is significant room for additional research related to this topic.
+We can still extract a lot more information from the skeletons of each segment.
+Currently these skeletons identify potential merge locations.
+However, these representations can be used to identify improperly merged segments.
+Additionally, we can further improve our results by tweaking the partitioning cost functions to more closely match the underlying biology.
+One such extension might take the outputs of a synaptic detector to enforce the constraint that a given segment only has post- or pre-synaptic connections.

### 2017-11-15 papers/cvpr2018/paper.tex
paper: BM updates

@@
 We then apply efficient graph-based optimization strategies to improve the segmentation labels.
-We demonstrate the performance of our approach on multiple real-world connectomics datasets with average variation of information improvement of \FIX{$X\times$}.
+We demonstrate the performance of our approach on multiple real-world connectomics datasets with an average variation of information improvement of \FIX{$X\times$}.
 %The paper provides insights into learning shape features for top-down graph-based neuron reconstruction.

### 2017-11-15 papers/cvpr2018/0_introduction.tex
new title; edits to abstract and intro

@@
 	\caption{Example improvement of neural reconstruction.
-(a) We extract 3D skeletons from pixel-based segmentation algorithms to create a graph representation with error probabilities indicated by the red arrows.
-(b) We then improve the accuracy of segmentation labels using graph partitioning algorithms with local and global geometric features.}
+(a) We extract 3D skeletons from pixel-based segmentation algorithms to create a 3D graph representation.
+Edges with high segmentation error probabilities are indicated by the red arrows.
+(b) We improve the accuracy of segmentation  using a graph partitioning algorithm, leveraging both local and global information.}
 	\label{fig:teaser}
@@
 Recent advancements in image acquisition using multi-beam serial-section electron microscopy (sSEM) have allowed researchers to produce terabytes of image data every hour~\cite{hildebrand2017whole}.
-It is not feasible for domain experts to manually reconstruct thousands or millions of neurons from this vast amount of image data~\cite{haehn2014design}.
+It is not feasible for domain experts to manually reconstruct this vast amount of image data~\cite{haehn2014design}.
 State-of-the-art automatic reconstruction approaches use pixel-based segmentation with convolutional neural networks (CNNs) followed by agglomeration strategies~\cite{seymour2016rhoananet,lee2015recursive,nunez2014graph,parag2017anisotropic,ronneberger2015u,zlateski2015image}.
-%TODO DOUBLE CHECK REFERENCES
-These \textit{bottom-up pixel-based} algorithms produce excellent results but still fall short of acceptable error rates for large volumes.
+These \textit{bottom-up pixel-based} methods produce excellent results but still fall short of acceptable error rates for large volumes.
 
@@
 We present a \textit{top-down graph-based} method that builds on the outputs of bottom-up pixel-based segmentation approaches.
-We first extract 3D skeletons from the input segmentation (Fig.~\ref{fig:pipeline}) and generate a simplified 3D graph (Fig.~\ref{fig:teaser}a).
-We train a 3D CNN classifier on the agglomerated regions in the segmentation data to detect errors.
-During test time, we run the classifier to populate the graph edge weights with error probabilities.
-We then use a graph optimization algorithm to partition the graph into the final reconstruction by enforcing domain-specific global constraints from the underlying biology (Fig.~\ref{fig:teaser}b).
+We first extract 3D skeleton networks from the input segmentation (Fig.~\ref{fig:pipeline}) and generate a simplified 3D graph (Fig.~\ref{fig:teaser}a).
+We train a CNN classifier on the agglomerated regions in the segmentation data to detect errors.
+We run the classifier to populate the graph edge weights with error probabilities.
+We then use a graph optimization algorithm to partition the graph into the final improved reconstruction by enforcing domain-specific global constraints from biology (Fig.~\ref{fig:teaser}b).
 
@@
 This allows us to leverage both local and global information to produce more accurate reconstructions.
-Since it uses agglomerated regions, our classifier is independent of image resolution and acquisition parameters, enabling its application to isotropic and anisotropic image data without retraining.
-Using the 3D graph of the segmentation allows us to enforce global constraints on the reconstruction that closely follow the underlying biology.
-We can also use local information such as shape priors to weight the edges in our graph.
-This dual approach of assessing local decisions in a global context yields accuracy improvements over the existing reconstruction methods.
+Our method is independent of image resolution and acquisition parameters, enabling its application to isotropic and anisotropic image data without retraining.
+Using the 3D graph induced by the segmentation allows us to enforce global biological constraints on the reconstruction.
+Our dual approach of assessing local decisions in a global context yields accuracy improvements over existing reconstruction methods.
 
-This work makes the following following contributions: (1) a novel top-down graph-based method for neural reconstruction of connectomics data; (2) a region-based CNN classifier to detect errors under global constraints; (3) an empirical evaluation of our method on several connectomics datasets; (4) our method yields improved performance over the state-of-the-art on three testing datasets.
-On average, we improve the Variation of Information (VI) metric across all datasets by \FIX{X} percent without drastically increasing the running time.
+This work makes the following contributions: (1) a novel top-down method using  graphs from skeletonized 3D networks for improved neural reconstruction of connectomics data; (2) a region-based CNN classifier to detect errors using the 3D graph as global constraint; (3) an empirical evaluation of our method on several connectomics datasets; (4) our method yields improved performance over a state-of-the-art pixel-based reconstruction approach on average by \FIX{X} percent without drastically increasing the running time.

### 2017-11-15 papers/cvpr2018/paper.tex
new title; edits to abstract and intro

@@
 %%%%%%%%% TITLE
-\title{Graph-Based Neural Reconstruction from Morphological Skeletons}
-
+\title{Graph-Based Neural Reconstruction \\ from Skeletonized 3D Networks}
+% Neural Reconstruction Using Skeletonized 3D Networks
+% Neural Reconstruction with Top-Down Enhancements from Skeletonized 3D Networks
+% Graph-Based Neural Reconstruction from Morphological Skeletons
 %Robust Agglomeration using 3D Skeletonization of Labeled for Connectomics}
@@
 In this work, we follow bottom-up pixel-based reconstruction by a top-down graph-based method to more accurately approximate neural pathways.
-Using the membrane labels of the pixel-based segmentation we first generate skeletons in 3D.
-Using this 3D graph we train automatic classifiers for shape description to detect impossible neural pathways by looking at geometric properties.
-We then apply efficient graph-based optimization strategies to improve the segmentation labels.
+We first generate skeletons in 3D from the membrane labels of the pixel-based segmentation.
+We then simplify this skeletonized 3D network into a 3D graph with nodes corresponding to labels from the segmentation and edges identifying potential locations of segmentation errors.
+We use a CNN classifier trained on ground truth data to generate edge weights on the 3D graph corresponding to error probabilities.
+We then apply a multicut algorithm to generate a partition on the graph that improves the final segmentation.
+Because the 3D graph is small and encodes top-down information our method is efficient and globally improves the neural reconstruction.
 We demonstrate the performance of our approach on multiple real-world connectomics datasets with an average variation of information improvement of \FIX{$X\times$}.

### 2017-11-15 papers/cvpr2018/1_related_work.tex
paper: BM updates
Updated related work and bib file

@@
 
-A significant amount of research in computer vision focuses on the segmentation of images~\cite{zaitoun2015survey}.
-Here, we review some of the most successful methods that have been applied to large-scale EM images in connectomics.
+We review some of the most successful segmentation methods that have been applied to large-scale EM images in connectomics.
 Fig.~\ref{fig:pipeline} shows the results of a typical connectomics segmentation pipeline.
@@
 Some early techniques apply computationally expensive graph partitioning algorithms with a single node per pixel~\cite{andres2012globally}.
-However these methods do not scale to terabyte datasets.
+However, these methods do not scale to terabyte datasets.
 More recent methods train classifiers to predict membrane probabilities per image slice either using 2D~\cite{ciresan2012deep,jain2010boundary,kaynig2015large,seymour2016rhoananet,amelio_segmentation} or 3D CNNs~\cite{lee2015recursive,ronneberger2015u,turaga2010convolutional}.
@@
 More recently, flood-filling networks produce segmentations by training an end-to-end neural network that goes from EM images directly to label volumes~\cite{januszewski2016flood}.
-These flood-filling networks produce impressive accuracies but at a high computational cost.
+These networks produce impressive accuracies but at a high computational cost.
 
@@
 Several pixel-based approaches generate probabilities that neighboring pixels belong to the same neuron.
-Often a watershed algorithm will cluster pixels into small super-pixels~\cite{zlateski2015image}.
-Many methods build on top of these strategies and train random-forest classifiers to produce region-based (i.e., super-pixel) segmentations~\cite{seymour2016rhoananet,nunez2014graph,10.1371/journal.pone.0125825,parag2017anisotropic,zlateski2015image}.
+Often a watershed algorithm will then cluster pixels into super-pixels~\cite{zlateski2015image}.
+Many methods build on top of these region-based strategies and train random-forest classifiers to produce the final segmentations~\cite{seymour2016rhoananet,nunez2014graph,10.1371/journal.pone.0125825,parag2017anisotropic,zlateski2015image}.
 
-\paragraph{Segment-based methods.}
-Some recent research builds on top of these region-based methods to correct errors in the segmentation~\cite{rolnick2017morphological,error_correction_using_CNN,haehn2017guided}.
-However, to our knowledge, our method is the first to extract a 3D graph from pixel-based agglomerated segmentations for a true top-down reconstruction approach.
-This allows us to enforce domain-specific constraints using graph-based partitioning algorithms.
+\paragraph{Error-correction methods.}
+Some recent research builds on top of these region-based methods to correct errors in the segmentation either using human proofreading~\cite{raveler,mojo2,haehn_dojo_2014,haehn2017guided} or fully automatically~\cite{rolnick2017morphological,error_correction_using_CNN}.
+However, to our knowledge, our method is the first to extract a 3D graph from pixel-based segmentations for a true top-down error correction approach.
+This allows us to enforce domain-specific biology constraints and efficient graph partitioning algorithms.
 Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for traditional image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}.
 Even though graph partitioning is an NP-Hard problem~\cite{demaine2006correlation} there are several useful multicut heuristics that provide good approximations with reasonable computational costs~\cite{horvnakova2017analysis}.
-We use the method of Keuper et al.
-to partition the extracted 3D graph into the final neuron reconstruction~\cite{keuper2015efficient}.
+We use the method of Keuper et al.~\cite{keuper2015efficient} to partition the extracted 3D graph into the final neural reconstruction.

### 2017-11-15 papers/cvpr2018/0_introduction.tex
Updated related work and bib file
Removed Fig. 2

@@
 
-\begin{figure*}[t]
-	\centering
-	\subfloat[]{
-	\includegraphics[width=.24\linewidth]{./figures/pipeline/image.png}
-	}
-	\subfloat[]{
-	\includegraphics[width=.24\linewidth]{./figures/pipeline/affinities.png}
-	}
-	\subfloat[]{
-	\includegraphics[width=.24\linewidth]{./figures/pipeline/watershed.png}
-	}
-	\subfloat[]{
-	\includegraphics[width=.24\linewidth]{./figures/pipeline/neuroproof.png}
-	}
-	\caption{An overview of a pixel-based connectomics segmentation pipeline.
+%\begin{figure*}[t]
+%	\centering
+%	\subfloat[]{
+%	\includegraphics[width=.24\linewidth]{./figures/pipeline/image.png}
+%	}
+%	\subfloat[]{
+%	\includegraphics[width=.24\linewidth]{./figures/pipeline/affinities.png}
+%	}
+%	\subfloat[]{
+%	\includegraphics[width=.24\linewidth]{./figures/pipeline/watershed.png}
+%	}
+%	\subfloat[]{
+%	\includegraphics[width=.24\linewidth]{./figures/pipeline/neuroproof.png}
+%	}
+%	\caption{An overview of a pixel-based connectomics segmentation pipeline.
 (a) Original EM image data (b) Output of a CNN predicting voxel affinities (c) Clustering of the affinities using a watershed algorithm (d) Agglomeration of the super-voxels into larger segments.}
-	\label{fig:pipeline}
-\end{figure*}
+%	\label{fig:pipeline}
+%\end{figure*}
 
@@
 We present a \textit{top-down graph-based} method that builds on the outputs of bottom-up pixel-based segmentation approaches.
-We first extract 3D skeleton networks from the input segmentation (Fig.~\ref{fig:pipeline}) and generate a simplified 3D graph (Fig.~\ref{fig:teaser}a).
+We first extract 3D skeleton networks from the input segmentation and generate a simplified 3D graph (Fig.~\ref{fig:teaser}a).
 We train a CNN classifier on the agglomerated regions in the segmentation data to detect errors.

### 2017-11-15 papers/cvpr2018/2_method.tex
edit on method section; removed network fig.

@@
 Thus, most reconstruction approaches are tuned towards over-segmentation with many more split than merge errors.
-Our method takes as input over-segmentations of EM image volumes generated by state-of-the-art connectomics reconstruction pieplines (Sec.~\ref{sec:neuroproof}).
+Our method takes as input over-segmentations of EM image volumes generated by state-of-the-art connectomics reconstruction pipelines (Sec.~\ref{sec:neuroproof}).
 Our goal is to identify locations of split errors and merge the corresponding segments automatically.
@@
 To compute this graph we generate a skeleton for every segment in the pixel-based segmentation.
-The skeleton is a simplified representation of the overall shape of the neurons.
-From this skeleton we  identify potential merge locations and produce the corresponding edges for the graph.
-To find actual merges we run a classification CNN to generate edge weights that correspond to probabilities of merging.
-We then use a multicut heuristic to generate a partition on the graph where nodes in the same partition are assigned the same output label in the improved segmentation.
+The skeletonized 3D network is a simplified representation of the overall branching structure of the neurons.
+From these skeletons we identify potential merge locations and produce the corresponding edges for the graph.
+To find actual merges we run a classification CNN to generate edge weights corresponding to merge probabilities.
+We then use a multicut algorithm to generate a partition on the graph where nodes in the same partition are assigned the same output label in the improved segmentation.
 We will now discuss the three major components to our framework (graph creation, edge weights assignment, and graph partitioning) in more detail.
@@
 The simplest node generation strategy creates one node for every unique segment label in the input volume.
-However, some of the millions of labels in the volume correspond to very small structures that are likely the result of segmentation errors.
-This typically happens in regions with noisy image data such that pixel-based methods could not generate the correct segments.
-It is difficult to extract useful shape features from these segments because of their small, and often random, shape.
-We prune these nodes from the graph by removing all segments with fewer than a threshold of $t_{seg}$ voxels.
-We use $t_{seg} = 20,000$ voxels, which removed on average 56\% of the segments in our  datasets (Sec.~\ref{sec:dataset}).
+However, some of the millions of labels in the volume correspond to very small structures that are likely the result of segmentation errors, typically in regions with noisy raw image data.
+It is difficult to extract useful shape features from these segments because of their small, often random, shape.
+We prune these nodes from the graph by removing all segments with fewer than a threshold $t_{seg} = 20,000$ voxels.
+This removed on average 56\% of the segments in our  datasets (Sec.~\ref{sec:dataset}).
 Despite the large number of segments, these regions only take up 1.6\% of the total volume on average.
@@
 A typical approach to generating edges produces an edge between all adjacent segments.
-Two segments $l_1$ and $l_2$ are considered adjacent if there is a pair of adjacent voxels where one has label $l_1$ and the other has label $l_2$.
+Two segments $l_1$ and $l_2$ are considered adjacent if there is a pair of adjacent voxels with one labeled $l_1$ and the other labeled $l_2$.
 For example, pixel-based agglomeration methods such as NeuroProof~\cite{10.1371/journal.pone.0125825} and GALA~\cite{nunez2014graph} consider all pairs of adjacent segments for merging.
 However, this method produces too many edges in the graph for graph-based optimization approaches.
-We identify a smaller number of pairs of segments to consider as graph edges using the following algorithm.
+We identify a smaller number of pairs of segments to consider as graph edges using the following approach.
 
-First, we extract a skeleton from each segment using the TEASER algorithm~\cite{sato2000teasar,zhao2014automatic}.
-Fig.~\ref{fig:skeletonization} shows an example of two extracted skeletons (in black) of two segments from the label volume.
-These skeletons consist of a sequence of \textit{joints}, i.e., locations that are a local maximum distance from the segment boundary, with line segments connecting successive joints.
+First, we extract a skeleton from each segment in the label volume using the TEASER algorithm~\cite{sato2000teasar,zhao2014automatic}.
+Fig.~\ref{fig:skeletonization} shows an example of two extracted skeletons (in black).
+These skeletons consist of a sequence of \textit{joints}, i.e., locations that are locally a maximum distance from the segment boundary, with line segments connecting successive joints.
 We prune the joints that are within $t_{jnt} = 50$ voxels of each other to reduce unnecessary branching.
-For the purposes of our algorithm, joints that have only one connected neighbor are referred to as \textit{endpoints}.
+We refer to joints that have only one connected neighbor as \textit{endpoints}.
 Many of the segments that are erroneously split have nearby endpoints  (Fig.~\ref{fig:merge_candidates}).
-We make use of this fact to merge segments with the following two-pass heuristic.
+We make use of this fact to merge segments with the following two-pass pruning algorithm.
 
@@
 We store the midpoints between the two endpoints as the center of the potential merges in the set $\mathbb{S}_c$.
+\hp{add how the final graph is constructed}
 
@@
 \subsection{Edge Weights Assignment}
-We assign non-negative edge weights $w_e$ to each edge where the weight corresponds to the probability two nodes belong to the same neuron.
+We assign non-negative edge weights $w_e$ to each edge where the weight corresponds to the probability that two nodes belong to the same neuron.
 Instead of using handcrafted features to compute the similarity between adjacent nodes, we train a 3D CNN classifier to learn from the manually labeled oversegmentation input volume (Sec.~\ref{sec:dataset}).
@@
 
-We extract a cubic region of interest around each endpoint $e$ in $\mathbb{S}_c$ as input to the CNN.
-These regions of interest provide the local information for the neural network to predict which neighboring segments belong to the same neuron.
-The CNN receives three input channels for every voxel in the region of interest around segments $l_1$ and $l_2$.
+We extract a cubic region of interest (ROI) around each endpoint $e$ in $\mathbb{S}_c$ as input to the CNN.
+The CNN receives three input channels for every voxel in the ROI around segments $l_1$ and $l_2$.
 The input in all of the channels is in the range $\{-0.5, 0.5\}$.
@@
 
-Fig.~\ref{fig:architecture} provides an overview of our CNN architecture.
-Similar to Chatfield et al.~\cite{chatfield2014return} it consists of three layers of double convolutions followed by a max pooling step.
+%Fig.~\ref{fig:architecture} provides an overview of our CNN architecture.
+We use the CNN architecture by Chatfield et al.~\cite{chatfield2014return}.
+It consists of three layers of double convolutions followed by a max pooling step.
 The first max pooling layer is anisotropic with pooling only in the $x$ and $y$ dimensions.
@@
 
-We use a stochastic gradient descent optimizer with Nesterov's accelerated gradient~\cite{nesterov1983method} for training.
+For training we use a stochastic gradient descent optimizer with Nesterov's accelerated gradient~\cite{nesterov1983method}.
 We employ dropouts of $0.2$ after every pooling layer and the first dense layer, and a dropout of $0.5$ after the final dense layer to prevent overfitting.
@@
 
-\begin{figure*}[t]
-	\centering
-	\includegraphics[width=0.85\linewidth]{figures/architecture.png}
-	\caption{The architecture for our classification CNN uses double convolutions followed by max pooling.
+%\begin{figure*}[t]
+%	\centering
+%	\includegraphics[width=0.85\linewidth]{figures/architecture.png}
+%	\caption{The architecture for our classification CNN uses double convolutions followed by max pooling.
 The number of filters doubles each layer, with a final fully connected layer and sigmoid activation function.}
-	\label{fig:architecture}
-\end{figure*}
+%	\label{fig:architecture}
+%\end{figure*}
 
@@
 
-After constructing the 3D graph we apply graph-based partitioning to compute the final segmentation.
-Using graph partitioning from the top down allows us to apply biological constraints on the output.
+After constructing the 3D graph we apply graph partitioning using multicut to compute the final segmentation.
+Using top-down graph partitioning allows us to apply biological constraints on the output.
 Neuroscientists know that neuronal connectivity graphs in the brain are acyclic (i.e., the graphs have a genus of zero).
-We enforce this constraint by finding a multicut partition of the graph that generates a \textit{forest} of nodes.
-A forest is a partitioning of a graph into a set of trees where no segment has a cycle.
+We enforce this constraint by finding a multicut partition of the graph that generates a \textit{forest} of nodes, i.e., a set of trees where no segment has a cycle.
 To solve this constraing multicut problem we use the method by Keuper et al.~\cite{keuper2015efficient} that produces a feasible solution by greedy additive edge contraction.
-Adding additional constraints and improving the graph partition algorithm are areas for future work.

### 2017-11-15 algorithms/multicut.pyx
multicut

@@ -54,33 +54,6 @@ def CollapseGraph(segmentation, gold, candidates, collapsed_edges, probabilities
     for iv in range(max_value):
         mapping[iv] = unionfind.Find(union_find[iv]).label
 
-    # find the largest number that were connected
-    max_label = np.amax(mapping) + 1
-    nunions = np.zeros(max_label, dtype=np.int64)
-
-    for iv in range(max_value):
-        nunions[mapping[iv]] += 1
-
-    # go through all unions and see if they are correct
-    seg2gold_mapping = seg2gold.Mapping(segmentation, gold)
-    correct = np.ones(max_label, dtype=np.bool)
-    for iv in range(max_value):
-        # if this candidate iv has a different ground truth to the sample it maps to (ignore missing ground truth)
-        if seg2gold_mapping[mapping[iv]] != seg2gold_mapping[iv] and seg2gold_mapping[iv]:
-            correct[mapping[iv]] = False
-
-    # output results
-    with open('cvpr/microns-300-test-skeleton-multicut.txt', 'w') as fd:
-        # write the number of labels
-        fd.write('{}\n'.format(max_label))
-
-        # go through each label
-        for iv in range(max_label):
-            fd.write('{},{}\n'.format(nunions[iv], int(correct[iv])))
-            for ix in range(max_value):
-                if mapping[ix] == iv:
-                    fd.write('{}\n'.format(ix))
-
     segmentation = seg2seg.MapLabels(segmentation, mapping)
 
     return segmentation
@@ -119,7 +92,7 @@ def Multicut(segmentation, gold, candidates, edge_weights, beta, threshold, anis
     segmentation = CollapseGraph(segmentation, gold, candidates, collapsed_edges, edge_weights)
 
     # evaluate before and after multicut
-    #comparestacks.Evaluate(segmentation, gold, threshold, anisotropic)
+    comparestacks.Evaluate(segmentation, gold, threshold, anisotropic)
 
 
 

### 2017-11-15 papers/cvpr2018/3_evaluation.tex
added HP evaluation and results

@@
 
-We evaluate our method on two connectomics datasets and compare it to a state-of-the-art pixel-based reconstruction method using the variation of information (VI) metric.
-\hp{depending on space we can shorten this and put details into the supplemental material}
+We evaluate our method by comparing it to a state-of-the-art pixel-based reconstruction approach using datasets from two different animals.
 
@@
 \label{sec:dataset}
-
-We use the following two datasets for training and experimental evaluation.
 
@@
 1 and Vol.
-2) along the $x$ dimension where each volume is $\SI[product-units=single]{8.0 x 10.9 x 10.1}{\micro\meter}^3$.
+2) along the $x$ dimension, where each volume is $\SI[product-units=single]{8.0 x 10.9 x 10.1}{\micro\meter}^3$ or $X \times Y \times Z$ voxels.
+\hp{add voxels}
 
@@
 The mushroom body in this species is the major site of associative learning.
-The original dataset contains a $\SI[product-units=single]{40 x 50 x 120}{\micro\meter}^3$ volume of which we use two cubes of size $\SI[product-units=single]{10 x 10 x 10}{\micro\meter}^3$.
-The resolution of this dataset is $\SI[product-units=single]{10 x 10 x 10}{\nano\meter}^3$ or $1000$ voxels in each dimension in each of the two volumes.
+The original dataset contains a $\SI[product-units=single]{40 x 50 x 120}{\micro\meter}^3$ volume with a resolution of $\SI[product-units=single]{10 x 10 x 10}{\nano\meter}^3$ per voxel.
+We use two cubes (Vol.
+1 and Vol.
+2) of size $\SI[product-units=single]{10 x 10 x 10}{\micro\meter}^3$ or $1000 \times 1000 \times 1000$ voxels.
 
@@
 The resulting 3D oversegmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}.
-We use this segmentation as our baseline for comparisons with our method.
+We use results from this NeuroProof algorithm as the baseline for our comparisons.
 
-For the FlyEM data we collected two $1000 \times 1000 \times 1000$ voxel ($\SI[product-units=single]{10x10x10}{\micro\meter}^3$) volumes from the authors~\cite{takemura2017connectome}.
-Based on the authors' suggestion, we applied a context-aware delayed agglomeration algorithm~\cite{10.1371/journal.pone.0125825} that shows improved performance on this dataset over the pipeline used in the original publication.
+For the FlyEM data, based on the authors' suggestion~\cite{takemura2017connectome}, we applied a context-aware delayed agglomeration algorithm~\cite{10.1371/journal.pone.0125825} that shows improved performance on this dataset over the pipeline used in the original publication.
 This segmentation framework learns voxel and supervoxel classifiers with an emphasis to minimize under-segmentation error.
-At the same time this framework produces lower oversegmentation than standard algorithms.
+At the same time this framework produces lower over-segmentation than standard algorithms.
 The algorithm first computes multi-channel 3-D predictions for membranes, cell interiors, and mitochondria, among other cell features.

### 2017-11-15 papers/cvpr2018/3_evaluation.tex
added HP changes

@@
 The resulting 3D oversegmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}.
-We use results from this NeuroProof algorithm as the baseline for our comparisons.
 
@@
 
-\subsection{Graph Generation Parameters}
+\subsection{Graph Pruning Parameters}
 
-There are two essential parameters to the graph generation algorithm described in Section~\ref{sec:skeletonization}: $t_{low}$ and $t_{high}$.
+The two parameters for the graph pruning algorithm (Sec.~\ref{sec:skeletonization}) are $t_{low}$ and $t_{high}$.
 Ideally, the merge candidates output by this algorithm will contains all possible positive examples with a very limited number of negative examples.

### 2017-11-15 papers/cvpr2018/4_results.tex
added HP evaluation and results
added HP changes

@@
 
-\section{Results}
+%\section{Results}
 
@@
 
-\subsection{Variation of Information Improvement}
+\subsection{Variation of Information Results}
 
-In Fig.~\ref{fig:variation-of-information}, we show the VI results of NeuroProof on the Kasthuri and FlyEM data at varying thresholds of agglomeration (green). 
-The green circle represents the variation of information for our input segmentation (a threshold of 0.3 for all datasets). 
-Our results are in red.  
-We show the comparison to an oracle (blue) that correctly partitions the graph from our algorithm based on ground truth.
+In Fig.~\ref{fig:variation-of-information}, we show the VI results of the pixel-based reconstructions of the Kasthuri and FlyEM data (Sec.~\ref{sec:neuroproof}) for varying thresholds of agglomeration (green).
+We use one of these segmentations (green circle) as out input dataset with an agglomeration threshold of 0.3 for all datasets.
+The results from our method are shown in red for varying X \hp{add} parameters.
+We show comparisons to an oracle (blue) that correctly partitions the graph from our method based on ground truth.
 
-Our algorithm improves the accuracy of the input segmentation on every dataset, reducing the VI split score on average by \FIX{X\%} and only increasing the VI merge score by \FIX{X\%}. 
-Scores closer to the origin are better for this metric, and in every instance we are below the green curve. 
-We see significant improvements on the Kasthuri datasets (VI split reduction of \FIX{X\%} and \FIX{X\%} on the training and testing datasets respectively) and slightly more modest improvements on the FlyEM datasets (reduction of \FIX{X\%} and \FIX{X\%}).
-However, our baseline, NeuroProof performs much better on the FlyEM datasets reducing the potential improvement. 
-Isotropic datasets are easier to segment using state-of-the-art region-based methods than anisotropic ones~\cite{plaza2014annotating}.
-Thus there is less room for improvement on these datasets.
+Our algorithm improves the accuracy of the reconstruction for every dataset, reducing the VI split score on average by \FIX{X\%} and only increasing the VI merge score by \FIX{X\%}.
+Scores closer to the origin are better for this metric, and in every instance our results are below the green curve.
+We see significant improvements on the Kasthuri datasets (VI split reduction of \FIX{X\%} and \FIX{X\%} on the training and testing datasets respectively) and more modest improvements on the FlyEM datasets (reduction of \FIX{X\%} and \FIX{X\%}).
+This is because the baseline segmentation algorithm for the isotropic FlyEM data (Sec.~\ref{sec:neuroproof}) performs much better, reducing the potential for improvements.
+It is well known that isotropic datasets are easier to segment using state-of-the-art region-based methods than anisotropic ones~\cite{plaza2014annotating}.
 
-Fig.~\ref{fig:positive-results} shows successful merges on the Kasthuri Vol. 2 dataset. 
-Several of these examples combine multiple consecutive segments that span the volume. 
-In the third example we correct the oversegmentation of a dendrite.
-Fig.~\ref{fig:negative-results} shows some failure cases. 
+Fig.~\ref{fig:positive-results} shows successful merges on the Kasthuri Vol. 2 dataset. Several of these examples combine multiple consecutive segments that span the volume.
+In the third example we correct the over-segmentation of a dendrite.
+Fig.~\ref{fig:negative-results} shows some failure cases (red circles)
 In two of these examples the algorithm correctly predicted several merges but made one error.
-In the third example a merge error in the initial segmentation propagated to our output. 
+In the third example (blue circle) a merge error in the initial segmentation propagated to our output.
 We now analyze how each major component of our method contributes to this final result.
@@
 	\includegraphics[width=0.85\linewidth]{./figures/multicut-correct5.png}
-	\caption{Correctly segmented neurons from our method.}
+	\caption{Segments of neurons that were correctly merged by our method.}
 	\label{fig:positive-results}
@@
 	\includegraphics[width=0.85\linewidth]{./figures/multicut-incorrect4.png}
-	\caption{Errors made by our method.}
+	\caption{Circles indicate areas of wrong merges by our method (red) or by the initial pixel-based segmentation (blue).}
 	\label{fig:negative-results}
@@
 
-\subsection{Graph Creation}
+\subsection{Graph Pruning Results}
 
@@
 		\textbf{Dataset} & \textbf{Baseline} & \textbf{After Pruning} \\ \hline
-		Kasthuri Vol. 1 & 763 / 21242 (3.47\%) & 753 / 3459 (17.88\%) \\
-		Kasthuri Vol. 2 & 1010 / 26073 (3.73\%) & 904 / 4327 (17.28\%) \\
-		FlyEM Vol. 1 & 269 / 14875 (1.78\%) & 262 / 946 (21.69\%) \\
-		FlyEM Vol. 2 & 270 / 16808 (1.58\%) & 285 / 768 (27.07\%)\\ \hline
+		Kasthuri Vol. 1 & 763 / 21,242 & 753 / 3,459 \\
+		Kasthuri Vol. 2 & 1,010 / 26,073 & 904 / 4,327 \\
+		FlyEM Vol. 1 & 269 / 14,875 & 262 / 946 \\
+		FlyEM Vol. 2 & 270 / 16,808 & 285 / 768 \\ \hline
+%		Kasthuri Vol. 1 & 763 / 21242 (3.47\%) & 753 / 3459 (17.88\%) \\
+%		Kasthuri Vol. 2 & 1010 / 26073 (3.73\%) & 904 / 4327 (17.28\%) \\
+%		FlyEM Vol. 1 & 269 / 14875 (1.78\%) & 262 / 946 (21.69\%) \\
+%		FlyEM Vol. 2 & 270 / 16808 (1.58\%) & 285 / 768 (27.07\%)\\ \hline
 	\end{tabular}
-	\caption{The results of our skeleton graph pruning heuristic compared to the baseline segmentation.}
+	\caption{The results of our graph pruning approach compared to the baseline graph with all adjacent regions.
+We show the number of true merge locations (e.g., 763) compared to total number of edges in the graph (e.g., 21,242) for each case.}
 	\label{table:skeletonization}
@@
 
-Table \ref{table:skeletonization} shows the results of pruning the skeleton graph using the heuristic discussed in Sec.~\ref{sec:skeletonization}.
+Table \ref{table:skeletonization} shows the results of pruning the skeleton graph using the algorithm discussed in Sec.~\ref{sec:skeletonization}.
+This edge pruning is essential for the graph partitioning algorithm, which has a computational complexity dependence on the number of edges.
 The baseline algorithm considers all adjacent regions for merging.
-Our method removes a significant portion of these candidates while maintaining a large number of the true merge locations.
-This edge pruning is essential for the graph partitioning algorithm, which has a computational complexity dependence on the number of edges.
-Our pruning heuristic removes at least $6\times$ the number of edges between correctly split segments on all datasets, achieving a maximum removal ratio of $20\times$.
+Our method removes a significant portion of these candidates while maintaining a large number of the true merge locations (e.g., 753 compared to 763).
+Our pruning heuristic removes at least $6\times$ the number of edges on all datasets, achieving a maximum removal rate of $20\times$.
 
 Equally important is the number of split errors that remain after pruning.
-These are the locations that we want to merge to create a more accurate reconstruction.
+These are the locations that we want to merge to create a more accurate reconstructions.
 For every dataset, the number of true split errors remains constant before and after pruning.
+\hp{not sure what you mean}
 However, since our heuristic does not enforce an adjacency constraint of two regions when constructing edges in the graph, the difference does not indicate the number of examples excluded by pruning.
-In fact, our method finds a number of examples that are non-adjacent.
-Figure \ref{fig:skeleton-results} shows two example segments with split errors, one that our algorithm missed (top) and one that it identified (bottom), despite the fact that the split segments are not adjacent.
-Of the successful examples in Figure \ref{fig:positive-results}, the second and fourth groupings contain pairs of non-adjacent segments that merge with our algorithm.
+Fig.~\ref{fig:skeleton-results} shows an example segment with a split error (green segment) that our algorithm missed.
+Of the successful examples in Fig.~\ref{fig:positive-results}, the second and fourth groupings contain pairs of non-adjacent segments that were merged by our method.
+\hp{this paragraph needs more work to make it clearer}
 
@@
 
-\subsection{Classification Performance}
+\subsection{CNN Classification Results}
 
-Figure \ref{fig:receiver-operating-characteristic} shows the receiver operating characteristic (ROC) curve for all of the datasets. 
-We train our CNN using one of the Kasthuri volumes and test using the other three datasets.
-Since our CNN only takes as input a region of the label volume we can train on an anisotropic dataset and infer on an isotropic one. 
-This provides a major benefit given the time-intensive task of manually generating ground truth data at various resolutions.
+Figure \ref{fig:receiver-operating-characteristic} shows the receiver operating characteristic (ROC) curve of our CNN classifier for all datasets.
+%We train our CNN using one of the Kasthuri volumes and test using the other three datasets.
+Since our CNN only takes as input a region of the label volume we can train on  anisotropic data and test on isotropic data.
+This provides a major benefit given the time-intensive task of manually generating ground truth for each dataset at various resolutions.
 
-As evidenced by the ROC curve, the test results on the Kasthuri data are better than the results for FlyEM.
+As shown by the ROC curve, the test results on the Kasthuri data are better than the results for FlyEM.
 We believe this is in part because of the differences in the datasets (i.e., isotropy and $xy$ resolution).
@@
 2.\footnote{Since the FlyEM datasets have significantly fewer examples, we initialize the network with the weights from the Kasthuri training and have an initial learning rate of $10^{-4}$.}
-The dotted lines in the figure represent these tests. 
-There is a slight performance increase for FlyEM Vol. 2.
-However, the FlyEM datasets have reasonable results when the network is trained by the Kasthuri data, and the results outside of this section follow from that setup.
+The blue dotted curve in the figure shows a slight performance increase in this case.
+However, the improvement is minor, which led us to use the CNN trained on the anisotropic data for the rest of our experiments.
 
@@
 	\includegraphics[width=0.95\linewidth]{./figures/receiver-operating-characteristic.jpg}
-	\caption{The receiver operating characteristic for all four datasets.}
+	\caption{The receiver operating characteristic (ROC) curves of our CNN for all four datasets.}
 	\label{fig:receiver-operating-characteristic}
@@
 
-\subsection{Graph Based Strategies}
+\subsection{Graph Optimization Results}
 
-The graph-based optimization strategy increases our correction accuracy over using just the CNN. 
-In particular, the precision increases on each dataset, although the recall decreases on all but one of the datasets. 
+The graph optimization strategy using multicut increases our accuracy over using just the CNN.
+Table \ref{table:multicut} shows the changes in precision, recall, and accuracy for all four datasets compared to the CNN.
+The precision increases on each dataset, although the recall decreases on all but one of the datasets.
 Since it is more difficult to correct merge errors than split errors, it is often desirable to sacrifice recall for precision.
-Table \ref{table:multicut} shows the changes in precision, recall, and accuracy for all four datasets compared to the CNN. 
-Over the three testing datasets, applying a graph-based partitioning strategy reduced the number of merge errors by \FIX{X}, \FIX{Y}, and \FIX{Z}.
+Over the three testing datasets, applying a graph-based partitioning strategy reduced the number of merge errors by \FIX{X}, \FIX{Y}, and \FIX{Z}, respectively.
+\hp{would be good to show the actual precision / recall numbers, too (at least in supplemental).
+maybe swap the ROC figure with a precision /recall figure?}
 
@@
 	\end{tabular}
-	\caption{Precision and recall for the training and three test datasets.}
+	\caption{Precision, recall, and accuracy changes between CNN only and graph-optimized reconstructions for the training and three test datasets.}
 	\label{table:multicut}

### 2017-11-15 papers/cvpr2018/2_method.tex
major updates to paper figures

@@
 \section{Method}
+
+\begin{figure*}[t!]
+	\begin{center}
+	\includegraphics[width=0.24\linewidth]{./figures/methods/multicut_input.png}
+	\includegraphics[width=0.24\linewidth]{./figures/methods/pre-multicut.png}
+	\includegraphics[width=0.24\linewidth]{./figures/methods/multicut-graph.png}
+	\includegraphics[width=0.24\linewidth]{./figures/methods/post-multicut.png}
+	\end{center}
+	\caption{Overview of the proposed methods.}
+	\label{fig:overview}
+\end{figure*}
 

### 2017-11-15 papers/cvpr2018/4_results.tex
major updates to paper figures

@@
 	\centering
-	\includegraphics[width=0.85\linewidth]{./figures/multicut-correct1.png}
-	\includegraphics[width=0.85\linewidth]{./figures/multicut-correct2.png}
-	\includegraphics[width=0.85\linewidth]{./figures/multicut-correct3.png}
-	\includegraphics[width=0.85\linewidth]{./figures/multicut-correct4.png}
-	\includegraphics[width=0.85\linewidth]{./figures/multicut-correct5.png}
+	\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-correct1.png}
+	\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-correct2.png}
+	\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-correct3.png}
+	\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-correct4.png}
+	\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-correct5.png}
 	\caption{Segments of neurons that were correctly merged by our method.}
@@
 	\centering
-	\includegraphics[width=0.85\linewidth]{./figures/multicut-incorrect1.png}
-	\includegraphics[width=0.85\linewidth]{./figures/multicut-incorrect2.png}
-	\includegraphics[width=0.85\linewidth]{./figures/multicut-incorrect3.png}
-	\includegraphics[width=0.85\linewidth]{./figures/multicut-incorrect4.png}
+	\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-incorrect1.png}
+	\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-incorrect2.png}
+	\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-incorrect3.png}
+	\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-incorrect4.png}
 	\caption{Circles indicate areas of wrong merges by our method (red) or by the initial pixel-based segmentation (blue).}

### 2017-11-15 papers/cvpr2018/5_conclusions.tex
major updates to paper figures

--- 2017-11-15 papers/cvpr2018/5_conclusions.tex
@@
 
-We present a novel method for reconstructing neuronal processes in connectomics datasets.
-We extend existing pixel-based reconstruction strategies using a morphological 3D skeleton graph and show significant accuracy improvement on two datasets from two different species.
-Our approach enables enforcing domain-constraints on the resulting segmentation.
-We believe this approach extends beyond connectomics to other domains with different constraints.
-\hp{add more future work}
+We present a novel method for improved neuronal reconstruction in connectomics that extends existing pixel-based reconstruction strategies using skeletonized 3D networks.
+We show significant accuracy improvements on datasets from two different species.
+The main benefits of our approach are that it enforces domain-specific constraints at the global graph level while incorporating pixel-based classification information.
+
+There is significant room for additional research and improvements.
+We can augment the graph with additional information from the image data, such as synaptic locations, cell morphology, locations of mitochondria, etc.
+This would allow us to enforce additional biological constraints during graph partitioning.
+For example, we could then enforce the constraint that a given segment only has post- or pre-synaptic connections.
+An augmented graph would also be helpful for splitting improperly merged segments by adding additional terms to the partitioning cost function.
+Finally, we believe that the benefits of top-down enhancements from graph optimization can extend beyond connectomics to other domains, such as medical image segmentation.

### 2017-11-15 papers/cvpr2018/2_method.tex
paper: updated figures and addressed HP comments

@@
 Many of the segments that are erroneously split have nearby endpoints  (Fig.~\ref{fig:merge_candidates}).
-We make use of this fact to merge segments with the following two-pass pruning algorithm.
+We make use of this fact to find merge candidates with the following two-pass pruning algorithm.
 
@@
 We store the midpoints between the two endpoints as the center of the potential merges in the set $\mathbb{S}_c$.
-\hp{add how the final graph is constructed}
+This algorithm produces a set of segments to consider for merging.
+Only these pairs have a corresponding edge in the constructed graph.
 
@@
 	\includegraphics[width=0.92\linewidth]{./figures/split_error1.png}
-	\includegraphics[width=0.92\linewidth]{./figures/split_error2.png}
-	\caption{Two erroneously split segments.}
+	\includegraphics[width=0.92\linewidth]{./figures/split_error2.png}		\includegraphics[width=0.85\linewidth]{./figures/merge_candidate2.png}
+	\caption{Three erroneously split segments.}
 	\label{fig:merge_candidates}
@@
 \subsection{Edge Weights Assignment}
-We assign non-negative edge weights $w_e$ to each edge where the weight corresponds to the probability that two nodes belong to the same neuron.
+We assign edge weights $w_e$ to each edge where the weight corresponds to the probability that two nodes belong to the same neuron.
 Instead of using handcrafted features to compute the similarity between adjacent nodes, we train a 3D CNN classifier to learn from the manually labeled oversegmentation input volume (Sec.~\ref{sec:dataset}).
+If the probability of the nodes belonging to the same neuron is $p_e$, the edge weight $w_e = \log{\frac{p_e}{1 - p_e}} + \log{\frac{1 - \beta}{\beta}}$, where $\beta$ is a tunable parameter that encourages over or undersegmentation.
 %Our  edge weights  correspond to probabilities that two endpoints $e$ in $\mathbb{S}_c$ belong to the same neuron and should be merged. \hp{check}

### 2017-11-15 papers/cvpr2018/3_evaluation.tex
major updates to paper figures
paper: updated figures and addressed HP comments

@@
 1 and Vol.
-2) along the $x$ dimension, where each volume is $\SI[product-units=single]{8.0 x 10.9 x 10.1}{\micro\meter}^3$ or $X \times Y \times Z$ voxels.
-\hp{add voxels}
+2) along the $x$ dimension, where each volume is $\SI[product-units=single]{8.0 x 10.9 x 10.1}{\micro\meter}^3$ or $1335 \times 1809 \times 338$ voxels.
 
@@
 A recent study by Funke et al.~\cite{schlegel2017learning} demonstrated superior performance of such methods over existing ones on anisotropic data.
-We learn 3D affinities using MALIS loss with a U-net~\cite{Turaga:2009,ronneberger2015u}.
+We learn 3D affinities using MALIS loss with a U-net~\cite{ronneberger2015u,Turaga:2009}.
 We apply the z-watershed algorithm with suitable parameters to compute a 3D oversegmentation of the volume.

### 2017-11-15 papers/cvpr2018/4_results.tex
paper: updated figures and addressed HP comments

@@
 We use one of these segmentations (green circle) as out input dataset with an agglomeration threshold of 0.3 for all datasets.
-The results from our method are shown in red for varying X \hp{add} parameters.
+The results from our method are shown in red for varying the $\beta$ parameter.
 We show comparisons to an oracle (blue) that correctly partitions the graph from our method based on ground truth.
@@
 
-Equally important is the number of split errors that remain after pruning.
-These are the locations that we want to merge to create a more accurate reconstructions.
-For every dataset, the number of true split errors remains constant before and after pruning.
-\hp{not sure what you mean}
-However, since our heuristic does not enforce an adjacency constraint of two regions when constructing edges in the graph, the difference does not indicate the number of examples excluded by pruning.
-Fig.~\ref{fig:skeleton-results} shows an example segment with a split error (green segment) that our algorithm missed.
-Of the successful examples in Fig.~\ref{fig:positive-results}, the second and fourth groupings contain pairs of non-adjacent segments that were merged by our method.
-\hp{this paragraph needs more work to make it clearer}
+We generate edges in our graph by using information from the skeletons. 
+In particular, we do not enforce the constraint that edges in our graph correspond to adjacent segments.
+Although neurons are continuous, the EM images often have noisy spots which cause a break in the input segmentation.
+We still want to reconstruct these neurons despite the fact that the initial segmentation is non-continuous. 
+The second and fourth examples in Fig.~\ref{fig:positive-results} show correctly reconstructed neurons where two of the segments are non-adjacent. 
+This is a large benefit over enforcing segment adjacency.
+
+There are some pairs of segments which we do not consider for merging because of our reliance on the skeletons. 
+Fig.~\ref{fig:skeleton-results} shows such an example segment that our algorithm missed. 
+The endpoints of both segments are circled.
+In this example the small segment is carved from the larger segment in a location where there are no skeleton endpoints.
 
@@
 	\includegraphics[width=0.85\linewidth]{./figures/merge_candidate1.png}
-	\includegraphics[width=0.85\linewidth]{./figures/merge_candidate2.png}
 	\caption{Example merge candidates.}
@@
 Over the three testing datasets, applying a graph-based partitioning strategy reduced the number of merge errors by \FIX{X}, \FIX{Y}, and \FIX{Z}, respectively.
-\hp{would be good to show the actual precision / recall numbers, too (at least in supplemental).
-maybe swap the ROC figure with a precision /recall figure?}
 

### 2017-11-15 algorithms/multicut.cpp
tmp multicut files

@@ -14,9 +14,17 @@
         ], 
         "include_dirs": [
             "/home/bmatejek/software/miniconda2/envs/ibex_env/lib/python2.7/site-packages/numpy/core/include", 
-            "/home/bmatejek/software/graph/include"
+            "/home/bmatejek/software/graph/include", 
+            "/opt/gurobi702/linux64/include"
         ], 
         "language": "c++", 
+        "libraries": [
+            "gurobi70", 
+            "gurobi_c++"
+        ], 
+        "library_dirs": [
+            "/opt/gurobi702/linux64/lib"
+        ], 
         "name": "multicut", 
         "sources": [
             "multicut.pyx", 
@@ -1911,9 +1919,6 @@ static struct __pyx_typeinfo_string __Pyx_TypeInfoToFormat(__Pyx_TypeInfo *type)
 static CYTHON_INLINE unsigned long __Pyx_PyInt_As_unsigned_long(PyObject *);
 
 /* CIntFromPy.proto */
-static CYTHON_INLINE unsigned int __Pyx_PyInt_As_unsigned_int(PyObject *);
-
-/* CIntFromPy.proto */
 static CYTHON_INLINE unsigned char __Pyx_PyInt_As_unsigned_char(PyObject *);
 
 /* CIntFromPy.proto */
@@ -2129,7 +2134,6 @@ static const char __pyx_k_dtype[] = "dtype";
 static const char __pyx_k_enter[] = "__enter__";
 static const char __pyx_k_error[] = "error";
 static const char __pyx_k_flags[] = "flags";
-static const char __pyx_k_int64[] = "int64";
 static const char __pyx_k_label[] = "label";
 static const char __pyx_k_numpy[] = "numpy";
 static const char __pyx_k_range[] = "range";
@@ -2165,13 +2169,11 @@ static const char __pyx_k_c_double[] = "c_double";
 static const char __pyx_k_c_uint64[] = "c_uint64";
 static const char __pyx_k_itemsize[] = "itemsize";
 static const char __pyx_k_pyx_type[] = "__pyx_type";
-static const char __pyx_k_seg2gold[] = "seg2gold";
 static const char __pyx_k_skeleton[] = "skeleton";
[…]

### 2017-11-15 algorithms/multicut.pyx

@@ -93,7 +93,7 @@ def Multicut(segmentation, gold, candidates, edge_weights, beta):
 
     # evaluate before and after multicut
     #print partition_comparison.variation_of_information(segmentation.ravel().astype(np.int64), gold.ravel().astype(np.int64))
-    comparestacks.Evaluate(segmentation, gold, filtersize=20000, anisotropic=False)
+    comparestacks.Evaluate(segmentation, gold, filtersize=20000, anisotropic=True)
 
 
 

### 2017-11-16 papers/cvpr2018/1_related_work.tex
Removed Fig. 2
final edit pass

@@
 % !TEX root =  paper.tex
+
 \section{Related Work}
@@
 We review some of the most successful segmentation methods that have been applied to large-scale EM images in connectomics.
-Fig.~\ref{fig:pipeline} shows the results of a typical connectomics segmentation pipeline.
+%Fig.~\ref{fig:pipeline} shows the results of a typical connectomics segmentation pipeline.
 
@@
 \paragraph{Error-correction methods.}
-Some recent research builds on top of these region-based methods to correct errors in the segmentation either using human proofreading~\cite{raveler,mojo2,haehn_dojo_2014,haehn2017guided} or fully automatically~\cite{rolnick2017morphological,error_correction_using_CNN}.
+Some recent research builds on top of these region-based methods to correct errors in the segmentation either using human proofreading~\cite{mojo2,haehn2014design,haehn2017guided} or fully automatically~\cite{rolnick2017morphological,error_correction_using_CNN}.
 However, to our knowledge, our method is the first to extract a 3D graph from pixel-based segmentations for a true top-down error correction approach.

### 2017-11-16 papers/cvpr2018/2_method.tex
final edit pass

@@
 
-\begin{figure*}[t!]
+\begin{figure*}[htbp]
 	\begin{center}
@@
 	\end{center}
-	\caption{Overview of the proposed methods.}
+	\caption{Outline of our approach, from left to right: Result of the pixel-based segmentation and agglomeration algorithm; segments of several selected neurons from the initial segmentation; extracted skeletonized 3D network of those segments; improved 3D reconstruction of the selected segments after graph construction and partitioning with constraints.}
 	\label{fig:overview}
@@
 	\includegraphics[width=0.92\linewidth]{./figures/skeleton2.png}
-	\caption{Example skeletons (in black) extracted from segments (blue and green) using the TEASER algorithm.}
+	\caption{Example skeletons (in black) extracted from segments (blue and green) using the TEASER algorithm. \hp{there is enough space to add another example in this figure}}
 	\label{fig:skeletonization}
@@
 Ideally, our graph has edges corresponding to all of the segments that were erroneously split.
-To compute this graph we generate a skeleton for every segment in the pixel-based segmentation.
+To compute this graph we generate a skeleton for every segment in the pixel-based segmentation (Fig.~\ref{fig:overview}).
 The skeletonized 3D network is a simplified representation of the overall branching structure of the neurons.

### 2017-11-16 algorithms/multicut.pyx
revert later

@@ -92,7 +92,7 @@ def Multicut(segmentation, gold, candidates, edge_weights, beta, threshold, anis
     segmentation = CollapseGraph(segmentation, gold, candidates, collapsed_edges, edge_weights)
 
     # evaluate before and after multicut
-    comparestacks.Evaluate(segmentation, gold, threshold, anisotropic)
+    comparestacks.Evaluate(segmentation, gold, filtersize=threshold, anisotropic=True)
 
 
 
@@ -116,4 +116,4 @@ def RunMulticut(prefix, model_prefix, threshold, maximum_distance, network_dista
     gold = dataIO.ReadGoldData(prefix)
 
     # run the multicut algorithm
-    Multicut(segmentation, gold, candidates, edge_weights, beta, threshold, not dataIO.IsIsotropic(prefix), heuristic)
+    Multicut(segmentation, gold, candidates, edge_weights, beta, threshold, dataIO.IsIsotropic(prefix), heuristic)

### 2017-11-16 cnns/skeleton/generate_features.py

@@ -222,40 +222,32 @@ def GenerateFeatures(prefix, threshold, maximum_distance, network_distance, endp
     negative_candidates = []
     undetermined_candidates = []
 
-    index = 0
     for label_one in range(0, max_label):
         for label_two in range(label_one + 1, max_label):
             if smallest_distances[label_one,label_two] > endpoint_distance: continue
-            location = midpoints[label_one,label_two,:]
-            small_segmentation = segmentation[location[IB_Z]-network_radii[IB_Z]:location[IB_Z]+network_radii[IB_Z],location[IB_Y]-network_radii[IB_Y]:location[IB_Y]+network_radii[IB_Y],location[IB_X]-network_radii[IB_X]:location[IB_X]+network_radii[IB_X]]
-            small_gold = gold[location[IB_Z]-network_radii[IB_Z]:location[IB_Z]+network_radii[IB_Z],location[IB_Y]-network_radii[IB_Y]:location[IB_Y]+network_radii[IB_Y],location[IB_X]-network_radii[IB_X]:location[IB_X]+network_radii[IB_X]]
-            
-            small_seg2gold_mapping = seg2gold.Mapping(small_segmentation, small_gold)
-            if label_one < np.amax(small_segmentation) and label_two <= np.amax(small_segmentation): small_ground_truth = small_seg2gold_mapping[label_one] == small_seg2gold_mapping[label_two]
-            else: small_ground_truth = (seg2gold_mapping[label_one] == seg2gold_mapping[label_two])
             
             ground_truth = (seg2gold_mapping[label_one] == seg2gold_mapping[label_two])
-            candidate = SkeletonCandidate((label_one, label_two), midpoints[label_one,label_two,:], small_ground_truth)
+            candidate = SkeletonCandidate((label_one, label_two), midpoints[label_one,label_two,:], ground_truth)
 
-            if ground_truth != small_ground_truth: 
-                print 'Here {}'.format(index)
-                index += 1
-            
             if not seg2gold_mapping[label_one] or not seg2gold_mapping[label_two]: undetermined_candidates.append(candidate)
             elif ground_truth: positive_candidates.append(candidate)
             else: negative_candidates.append(candidate)
 
     # # save the files
-    # train_filename = 'features/skeleton/{}-{}-{}nm-{}nm-training.candidates'.format(prefix, threshold, maximum_distance, network_distance)
[…]

### 2017-11-16 papers/cvpr2018/2_method.tex
Another pass.

@@
 Generally, it is much more difficult to correct merge errors than to correct split errors,
-as the space of possible split proposals grow quickly~\cite{parag2015properties}.
+as the space of possible split proposals grows quickly~\cite{parag2015properties}.
 Thus, most reconstruction approaches are tuned towards over-segmentation with many more split than merge errors.
@@
 
-A typical approach to generating edges produces an edge between all adjacent segments.
+A typical approach for generating edges produces one between all adjacent segments.
 Two segments $l_1$ and $l_2$ are considered adjacent if there is a pair of adjacent voxels with one labeled $l_1$ and the other labeled $l_2$.

### 2017-11-16 papers/cvpr2018/3_evaluation.tex
Another pass.

@@
 
-We evaluate our method by comparing it to a state-of-the-art pixel-based reconstruction approach using datasets from two different animals.
+We evaluate our method by comparing it to a state-of-the-art pixel-based reconstruction approach using datasets from two different species.
 
@@
 \paragraph{FlyEM.}
-The FlyEM dataset comes from the mushroom body of a 5-day old adult male Drosophila fly imaged by a focused ion-beam milling scanning electron microscopy~\cite{takemura2017connectome}.
+The FlyEM dataset comes from the mushroom body of a 5-day old adult male \textit{Drosophila} fly imaged by a focused ion-beam milling scanning electron microscopy~\cite{takemura2017connectome}.
 The mushroom body in this species is the major site of associative learning.
@@
 
-The segmentation on the Kasthuri dataset was computed by agglomerating 3D supervoxels produced by the z-watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}.
+The segmentation of the Kasthuri dataset was computed by agglomerating 3D supervoxels produced by the z-watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}.
 A recent study by Funke et al.~\cite{schlegel2017learning} demonstrated superior performance of such methods over existing ones on anisotropic data.
@@
 The two parameters for the graph pruning algorithm (Sec.~\ref{sec:skeletonization}) are $t_{low}$ and $t_{high}$.
-Ideally, the merge candidates output by this algorithm will contains all possible positive examples with a very limited number of negative examples.
+Ideally, the merge candidates output by this algorithm will contain all possible positive examples with a very limited number of negative examples.
 After considering various thresholds, we find that $t_{low} = \SI{240}{\nano\meter}$ and $t_{high} = \SI{600}{\nano\meter}$ produce the best results considering this objective.
@@
 In our implementation we use nanometers for these thresholds and not voxels.
-Connectomics datasets often have lower sample resolutions in $z$.
+Connectomics datasets often have lower sample resolutions in $z$ because of limitations during sample preparation.
 Using nanometers allows us to have uniform units across all of these datasets and calculate the thresholds in voxels at runtime.

### 2017-11-16 papers/cvpr2018/4_results.tex
paper: changed location of table
Another pass.

@@
 	\includegraphics[width=0.45\linewidth]{./figures/variation_of_information-FlyEM-test-600.png}
-	\caption{VI scores of our method (red) compared to the baseline segmentation (green) and an oracle (blue) that optimally partitions the graph based on ground truth.}
+	\caption{VI scores of our method (red) compared to the baseline segmentation (green) and an oracle (blue) that optimally partitions the graph based on ground truth.
+Lower scores are better.
+Our method improves the accuracy of the segmentation in all cases.}
 	\label{fig:variation-of-information}
@@
 
-We evaluate the performance of the different methods using the split version of variance of information (VI)~\cite{meila2003comparing}.
-Given a ground truth labeling $GT$ and our automatically reconstructed segmentation $SG$, over and undersegmentation are quantified by the conditional entropy $H(GT | SG)$ and $H(SG | GT)$, respectively.
-Since we are measuring the entropy between two clusterings, better VI scores are closer to the origin.
+We evaluate the performance of the different methods using variation of information (VI)~\cite{meila2003comparing}.
+Given a ground truth labeling $GT$ and our automatically reconstructed segmentation $SG$, over and undersegmentation are quantified by the conditional entropies $H(GT | SG)$ and $H(SG | GT)$, respectively.
+Since we are measuring the entropies between two clusterings, lower VI scores are better.
 
@@
 This is because the baseline segmentation algorithm for the isotropic FlyEM data (Sec.~\ref{sec:neuroproof}) performs much better, reducing the potential for improvements.
-It is well known that isotropic datasets are easier to segment using state-of-the-art region-based methods than anisotropic ones~\cite{plaza2014annotating}.
+Isotropic datasets are easier to segment using state-of-the-art region-based methods than anisotropic ones~\cite{plaza2014annotating}.
 
 Fig.~\ref{fig:positive-results} shows successful merges on the Kasthuri Vol. 2 dataset. Several of these examples combine multiple consecutive segments that span the volume.
-In the third example we correct the over-segmentation of a dendrite.
-Fig.~\ref{fig:negative-results} shows some failure cases (red circles)
-In two of these examples the algorithm correctly predicted several merges but made one error.
+In the third example we correct the over-segmentation of a dendrite and attached spine-necks.
+Fig.~\ref{fig:negative-results} shows typical failure cases of our method (red circles).
+In two of these examples the algorithm correctly predicted several merges before a single error rendered the segment as wrong.
 In the third example (blue circle) a merge error in the initial segmentation propagated to our output.
@@
 
+Table \ref{table:skeletonization} shows the results of pruning the skeleton graph using the algorithm discussed in Sec.~\ref{sec:skeletonization}.
+This edge pruning is essential for the graph partitioning algorithm, which has a computational complexity dependence on the number of edges.
+The baseline algorithm considers all adjacent regions for merging.
+Our method removes a significant portion of these candidates while maintaining a large number of the true merge locations (e.g., 753 compared to 763).
+Our pruning heuristic removes at least $6\times$ the number of edges on all datasets, achieving a maximum removal rate of $20\times$.
+
 \begin{table}
@@
 
-Table \ref{table:skeletonization} shows the results of pruning the skeleton graph using the algorithm discussed in Sec.~\ref{sec:skeletonization}.
-This edge pruning is essential for the graph partitioning algorithm, which has a computational complexity dependence on the number of edges.
-The baseline algorithm considers all adjacent regions for merging.
-Our method removes a significant portion of these candidates while maintaining a large number of the true merge locations (e.g., 753 compared to 763).
-Our pruning heuristic removes at least $6\times$ the number of edges on all datasets, achieving a maximum removal rate of $20\times$.
-
 We generate edges in our graph by using information from the skeletons. 
 In particular, we do not enforce the constraint that edges in our graph correspond to adjacent segments.
-Although neurons are continuous, the EM images often have noisy spots which cause a break in the input segmentation.
+Although neurons are continuous, the EM images often have noisy spots which cause an interruption in the input segmentation.
 We still want to reconstruct these neurons despite the fact that the initial segmentation is non-continuous. 
@@
 There are some pairs of segments which we do not consider for merging because of our reliance on the skeletons. 
-Fig.~\ref{fig:skeleton-results} shows such an example segment that our algorithm missed. 
+Fig.~\ref{fig:skeleton-results} shows such a case. 
 The endpoints of both segments are circled.
@@
 	\includegraphics[width=0.85\linewidth]{./figures/merge_candidate1.png}
-	\caption{Example merge candidates.}
+	\caption{A false negative example of our method due graph pruning. The distance between the endpoints (circled) of the two segments is too far to be flagged as a merge candidate.}
 	\label{fig:skeleton-results}
@@
 
-Figure \ref{fig:receiver-operating-characteristic} shows the receiver operating characteristic (ROC) curve of our CNN classifier for all datasets.
+Fig.~\ref{fig:receiver-operating-characteristic} shows the receiver operating characteristic (ROC) curve of our CNN classifier for all datasets.
 %We train our CNN using one of the Kasthuri volumes and test using the other three datasets.
@@
 	\includegraphics[width=0.95\linewidth]{./figures/receiver-operating-characteristic.jpg}
-	\caption{The receiver operating characteristic (ROC) curves of our CNN for all four datasets.}
+	\caption{The receiver operating characteristic (ROC) curves of our classifier on three connectomics datasets.
+The classifier works best on previously unseen data of the Kasthuri volume.
+The dashed blue line indicates better performance on the FlyEM datasets with retraining compared to without (solid blue).}
 	\label{fig:receiver-operating-characteristic}
@@
 	\end{tabular}
-	\caption{Precision, recall, and accuracy changes between CNN only and graph-optimized reconstructions for the training and three test datasets.}
+	\caption{Precision, recall, and accuracy changes between CNN only and CNN paired with graph-optimized reconstructions for the training and three test datasets.
+The combined method results in better precision and accuracy.}
 	\label{table:multicut}

### 2017-11-16 papers/cvpr2018/4_results.tex
updated figures

@@
 		\textbf{Dataset} & \textbf{Baseline} & \textbf{After Pruning} \\ \hline
-		Kasthuri Vol. 1 & 763 / 21,242 & 753 / 3,459 \\
+		Kasthuri Training & 763 / 21,242 & 753 / 3,459 \\
 		Kasthuri Vol. 2 & 1,010 / 26,073 & 904 / 4,327 \\
@@
 		\textbf{Dataset} & $\Delta$ \textbf{Precision} & $\Delta$ \textbf{Recall} & $\Delta$ \textbf{Accuracy} \\ \hline
-		Kasthuri Training & +3.60\% & -0.01\% & +0.60\% \\
-		Kasthuri Testing & +7.59\% & -1.77\% & +1.38\% \\
+		Kasthuri Training & +3.61\% & -0.53\% & +0.60\% \\
+		Kasthuri Vol. 2 & +7.59\% & -1.77\% & +1.38\% \\
 		FlyEM Vol. 1 & +2.68\% & +0.76\% & +0.66\% \\

### 2017-11-16 papers/cvpr2018/0_introduction.tex
final edit pass
paper: BM updates

@@
 Edges with high segmentation error probabilities are indicated by the red arrows.
-(b) We improve the accuracy of segmentation  using a graph partitioning algorithm, leveraging both local and global information.}
+(b) We improve the segmentation accuracy using a graph partitioning algorithm, leveraging both local and global information.}
 	\label{fig:teaser}
@@
 
-This work makes the following contributions: (1) a novel top-down method using  graphs from skeletonized 3D networks for improved neural reconstruction of connectomics data; (2) a region-based CNN classifier to detect errors using the 3D graph as global constraint; (3) an empirical evaluation of our method on several connectomics datasets; (4) our method yields improved performance over a state-of-the-art pixel-based reconstruction approach on average by \FIX{X} percent without drastically increasing the running time.
+This work makes the following contributions: (1) a novel top-down method using  graphs from skeletonized 3D networks for improved neural reconstruction of connectomics data; (2) a region-based CNN classifier to detect errors using the 3D graph as global constraint; (3) an empirical evaluation of our method on several connectomics datasets; (4) our method yields improved performance over a state-of-the-art pixel-based reconstruction approach on average by 19.3\% without drastically increasing the running time.

### 2017-11-16 papers/cvpr2018/1_related_work.tex
paper: BM updates

@@
 \paragraph{Error-correction methods.}
-Some recent research builds on top of these region-based methods to correct errors in the segmentation either using human proofreading~\cite{mojo2,haehn2014design,haehn2017guided} or fully automatically~\cite{rolnick2017morphological,error_correction_using_CNN}.
+Some recent research builds on top of these region-based methods to correct errors in the segmentation either using human proofreading~\cite{haehn2017guided,haehn2014design,mojo2} or fully automatically~\cite{rolnick2017morphological,error_correction_using_CNN}.
 However, to our knowledge, our method is the first to extract a 3D graph from pixel-based segmentations for a true top-down error correction approach.
-This allows us to enforce domain-specific biology constraints and efficient graph partitioning algorithms.
+This allows us to enforce domain-specific biology constraints and use efficient graph partitioning algorithms.
 Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for traditional image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}.

### 2017-11-16 papers/cvpr2018/4_results.tex
paper: BM updates

@@
 
-Our algorithm improves the accuracy of the reconstruction for every dataset, reducing the VI split score on average by \FIX{X\%} and only increasing the VI merge score by \FIX{X\%}.
+Our algorithm improves the accuracy of the reconstruction for every dataset, reducing the VI split score on average by 19.3\% on the three testing datasets. 
 Scores closer to the origin are better for this metric, and in every instance our results are below the green curve.
-We see significant improvements on the Kasthuri datasets (VI split reduction of \FIX{X\%} and \FIX{X\%} on the training and testing datasets respectively) and more modest improvements on the FlyEM datasets (reduction of \FIX{X\%} and \FIX{X\%}).
+We see significant improvements on the Kasthuri datasets (VI split reduction of 27.7\% and 24.8\% on the training and testing datasets respectively) and more modest improvements on the FlyEM datasets (reduction of 15.2\% and 18.0\%).
 This is because the baseline segmentation algorithm for the isotropic FlyEM data (Sec.~\ref{sec:neuroproof}) performs much better, reducing the potential for improvements.

### 2017-11-16 papers/cvpr2018/4_results.tex
BM: final update

@@
 
-We evaluate the performance of the different methods using variation of information (VI)~\cite{meila2003comparing}.
-Given a ground truth labeling $GT$ and our automatically reconstructed segmentation $SG$, over and undersegmentation are quantified by the conditional entropies $H(GT | SG)$ and $H(SG | GT)$, respectively.
+We evaluate the performance of the different methods using the split variation of information (VI)~\cite{meila2003comparing}.
+Given a ground truth labeling $GT$ and our automatically reconstructed segmentation $SG$, over- and under-segmentation are quantified by the conditional entropies $H(GT | SG)$ and $H(SG | GT)$, respectively.
 Since we are measuring the entropies between two clusterings, lower VI scores are better.
@@
 	\includegraphics[width=0.85\linewidth]{./figures/merge_candidate1.png}
-	\caption{A false negative example of our method due graph pruning. The distance between the endpoints (circled) of the two segments is too far to be flagged as a merge candidate.}
+	\caption{A false negative example of our method due to graph pruning. The distance between the endpoints (circled) of the two segments is too far to be flagged as a merge candidate.}
 	\label{fig:skeleton-results}
@@
 
-Fig.~\ref{fig:receiver-operating-characteristic} shows the receiver operating characteristic (ROC) curve of our CNN classifier for all datasets.
+Fig.~\ref{fig:receiver-operating-characteristic} shows the receiver operating characteristic (ROC) curve of our CNN classifier for all test datasets.
 %We train our CNN using one of the Kasthuri volumes and test using the other three datasets.
@@
 Since it is more difficult to correct merge errors than split errors, it is often desirable to sacrifice recall for precision.
-Over the three testing datasets, applying a graph-based partitioning strategy reduced the number of merge errors by \FIX{X}, \FIX{Y}, and \FIX{Z}, respectively.
+Over the three testing datasets, applying a graph-based partitioning strategy reduced the number of merge errors by 36.1\%, 12.2\%, and 13.6\%, respectively.
 

### 2017-11-22 papers/cvpr2018/supplemental/skeletonization.tex
updated supplemental

@@
 
-\subsection{Parameters}
+\subsection{Node Pruning}
+
+\subsection{Edge Pruning}
+
+\subsection{CNN Parameters}
+
+We considered the following sets of parameters for the neural network and ran a brute-force search over the parameters.
+
+\begin{table}
+	\footnotesize
+	\begin{tabular}{c c} \hline
+		\textbf{Parameter} & \textbf{Considered Options} \\ \hline
+		Optimizer & \textbf{SGD with Nesterov}, Adam \\
+		Loss Function & Binary Cross Entropy, \textbf{Mean Squared Error} \\
+		Output Size & 3, 4, 5, \textbf{6}, 7 \\
+		Batch Normalization & On, \textbf{Off} \\ \hline
+	\end{tabular}
+\end{table}
+
+We also consider networks with four layers of double convolutions and increased filter sizes $(16\times32\times64)$ but both these configurations have two many parameters to learn with such small datasets.
 
 \subsection{Performance Tests}
+
+We use a XX GHz Processor with a PASCAL TitanX 1080 GPU with 64GB of RAM for all of our performance tests. 
+Inference for the CNN takes an average of $6.2$ seconds per $1000$ examples on our network of size

### 2017-11-22 papers/cvpr2018/supplemental/classifier.tex
supplemental: added lots of stuff

\section{CNN Classifier}

\subsection{Region of Interest Size}

From the skeletons we generate locations in the center of potential merges. 
We extract a cubic region of interest around each location.
We experimented with three different region of interest side lengths: $800 \textrm{nm}$, $1200 \textrm{nm}$, and $1600 \textrm{nm}$. 
Side lengths of $1600 \textrm{nm}$ performed better on the training and validation data on our network.

\subsection{CNN Parameters}

We experimented with several different network architectures before deciding on the one presented in our paper. 
We considered stochastic gradient descent with Nesterov momentum and the Adam optimizer.
In addition we toggled between a binary cross entropy and mean squared error loss function.
Also, we considered four varying input sizes that corresponding to different cube sizes output from the final max pooling layer. 
After running a brute force search over all of these possible architectures, we found that the best architecture used a SGD optimizer with Nesterov momentum, a mean squared error loss function, and an input size of $76 \times 76 \times 24$.

\subsection{Architecture}

\begin{figure*}
	\centering
	\includegraphics[width=0.9\linewidth]{./figures/architecture.png}
	\caption{The final architecture presented in this paper.}
	\label{fig:architecture}
\end{figure*}

Figure \ref{fig:architecture} shows the final architecture that produced the best results on the validation data. 
The input data was $76 \times 76 \times 24$ voxels in size with $3$ channels per voxel. 
This corresponds to an output size from the third layer of double convolution of $6 \times 6 \times 6$. 
This flattens to a vector of size $13,824$ which enters a dense layer of output size $512$ followed by another dense layer of output size $1$. 
All activation layers are Leaky ReLU with $\alpha=0.001$ except for the final layer which has a sigmoid activation layer.

### 2017-11-22 papers/cvpr2018/supplemental/performance.tex
supplemental: added lots of stuff

\section{Running Times}

\subsection{System}

All performance experiments ran on an Intel i7-6800K CPU 3.4 0GHz with a PASCAL Titan X GPU. 
All code is written in Python and will be freely available upon the paper decision.
We use the Keras deep learning library for our neural networks with Theano backend with cuDNN 7 acceleration for cuda 8.0.

\subsection{Performance}

The network trained for $34$ epochs with each epoch taking approximately $1200$ seconds to complete.
The following tables show the total running time for each dataset for graph creation, CNN inference, and multicut partitioning. 
In all instances the time for these three steps was less than 100 seconds.
Currently extracting the skeletons with the TEASER algorithm is the bottleneck to the process.
The skeleton for each segment takes around $20-30$ seconds to generate. 
However, the skeleton process is parallelizable and each segment can be processed independently.
Faster skeleton extraction is an important area for future research.

\begin{table}[t]
	\centering
	\small
	\begin{tabular}{c c c } \hline
		& Kasthuri Vol. 1 & Kasthuri Vol. 2 \\ \hline
		Graph Generation & 34.76s & 35.90s \\
		Inference & 38.47s & 37.13s \\
		Multicut & 22.94s & 22.90s \\ \hline
		Total Time & 96.17s & 95.93s \\ \hline
	\end{tabular}
	\begin{tabular}{c c c } \hline
		& FlyEM Vol. 1 & FlyEM Vol. 2 \\ \hline
		Graph Generation & 46.52s & 48.97s \\
		Inference & 12.55s & 10.91s \\
		Multicut & 30.30s & 30.14s \\ \hline
		Total Time & 89.37s & 90.02s \\ \hline
	\end{tabular}
\end{table}

### 2017-11-22 papers/cvpr2018/supplemental/skeletonization.tex
supplemental: added lots of stuff

--- 2017-11-09 papers/cvpr2018/supplemental/skeletonization.tex
@@
-\section{Skeletonization}
+\section{Graph Creation}
 
-more details regarding the skeletonization approach, which I believe was extra fast?
+\subsection{Node Pruning}
 
-\subsection{Parameters}
+In Section 3.1 we introduce the parameter $t_{seg}$ where any segment with fewer voxels does not receive a node in the graph.
+Figure \ref{fig:node-pruning} shows the results of varying this threshold on two quantities for the Kasthuri training volume. 
+The blue corresponds to the number of nodes remaining in the graph.
+As we increased the minimum size threshold for a label in the volume the number of nodes decreases.
+However, the rate of reduction decreases for larger thresholds.
+We also consider the percent of voxels with a label that is removed from the graph.
+Ideally this number is low since we want to only remove small segments which do not contribute much to the overall volume.
+As also seen in the curve, this number grows at an increasing rate. 
+Based on these curves we decided to set $t_{seg} = 20000$ voxels since it prunes over half of the labels that correspond to a very small chunk of the overall volume.
 
-\subsection{Performance Tests}
+\subsection{Edge Pruning}
+
+We call the two parameters form the algorithm presented in Section 3.2 $t_{low}$ and $t_{high}$. 
+With these parameters we want to retain the highest possible percentage of split errors in the graph as possible while keeping the number of total edges low. 
+We perform a search over varying thresholds for $40\textrm{nm} \leq t_{low} \leq 300 \textrm{nm}$ and $300 \textrm{nm} \leq t_{high} \leq 800 \textrm{nm}$ on the Kasthuri training dataset to find the parameter with the highest retention of true splits that keeps the number of total edges less than $6 \times$ the number of split errors.
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=0.95\linewidth]{./figures/node-threshold.png}
+		\caption{The number of remaining labels after increasing the threshold (blue) and the number of voxels with this label as a percent of the total volume (green). }
+		\label{fig:node-pruning}
+	\end{center}
+\end{figure}

### 2017-11-22 papers/cvpr2018/supplemental/classifier.tex
supplemental: cleaned up the writing

@@
 
-From the skeletons we generate locations in the center of potential merges. 
-We extract a cubic region of interest around each location.
+We generate locations for the potential merges from the skeletons using the algorithm in Section 3.2.
+From these locations we extract a cubic region of interest.
 We experimented with three different region of interest side lengths: $800 \textrm{nm}$, $1200 \textrm{nm}$, and $1600 \textrm{nm}$. 
-Side lengths of $1600 \textrm{nm}$ performed better on the training and validation data on our network.
+Side lengths of $1600 \textrm{nm}$ performed better on the training and validation data on our networks.
 
@@
 We experimented with several different network architectures before deciding on the one presented in our paper. 
-We considered stochastic gradient descent with Nesterov momentum and the Adam optimizer.
-In addition we toggled between a binary cross entropy and mean squared error loss function.
-Also, we considered four varying input sizes that corresponding to different cube sizes output from the final max pooling layer. 
+We considered two optimizers: stochastic gradient descent with Nesterov momentum and Adam~\cite{kingma2014adam}.
+In addition we tried two different loss functions: binary cross entropy and mean squared error.
+We also experimented with four different input sizes that correspond to different cube sizes output from the final max pooling layer. 
 After running a brute force search over all of these possible architectures, we found that the best architecture used a SGD optimizer with Nesterov momentum, a mean squared error loss function, and an input size of $76 \times 76 \times 24$.
@@
 Figure \ref{fig:architecture} shows the final architecture that produced the best results on the validation data. 
-The input data was $76 \times 76 \times 24$ voxels in size with $3$ channels per voxel. 
-This corresponds to an output size from the third layer of double convolution of $6 \times 6 \times 6$. 
-This flattens to a vector of size $13,824$ which enters a dense layer of output size $512$ followed by another dense layer of output size $1$. 
-All activation layers are Leaky ReLU with $\alpha=0.001$ except for the final layer which has a sigmoid activation layer.
+The input data was $76 \times 76 \times 24$ voxels with $3$ channels per voxel. 
+This corresponds to an output size from the third max pooling layer of $6 \times 6 \times 6$. 
+This flattens to a $13,824$-element vector and two dense layers of output size $512$ and $1$ follow. 
+All activation layers are Leaky ReLU with $\alpha=0.001$ except for the final layer which has a sigmoid activation.

### 2017-11-22 papers/cvpr2018/supplemental/performance.tex
supplemental: cleaned up the writing

@@
 
-All performance experiments ran on an Intel i7-6800K CPU 3.4 0GHz with a PASCAL Titan X GPU. 
+All performance experiments ran on an Intel Core i7-6800K CPU 3.40 GHz with a Titan X Pascal GPU. 
 All code is written in Python and will be freely available upon the paper decision.
-We use the Keras deep learning library for our neural networks with Theano backend with cuDNN 7 acceleration for cuda 8.0.
+We use the Keras deep learning library for our neural networks with Theano backend and cuDNN 7 acceleration for cuda 8.0.
 
@@
 The network trained for $34$ epochs with each epoch taking approximately $1200$ seconds to complete.
-The following tables show the total running time for each dataset for graph creation, CNN inference, and multicut partitioning. 
-In all instances the time for these three steps was less than 100 seconds.
-Currently extracting the skeletons with the TEASER algorithm is the bottleneck to the process.
-The skeleton for each segment takes around $20-30$ seconds to generate. 
-However, the skeleton process is parallelizable and each segment can be processed independently.
-Faster skeleton extraction is an important area for future research.
+Table \ref{table:performance} shows the total running time for each dataset for graph creation, CNN inference, and multicut partitioning. 
+In all instances the time for these three steps combined was less than 100 seconds.
+Currently extracting the skeletons with the TEASER algorithm is the bottleneck.
+The skeleton for each label takes around $20-30$ seconds to generate. 
+However, the process is parallelizable as each segment can be processed independently.
+Faster skeleton extraction is an important area for future research, particularly to consider algorithms in different fields~\cite{fazekas2008skeletonization}.
+There is some existing research of fast topologically preserving skeleton generation and their applications to existing medical images (e.g. blood vessels, the colon)~\cite{palagyi2001sequential}.
 
@@
 	\begin{tabular}{c c c } \hline
-		& Kasthuri Vol. 1 & Kasthuri Vol. 2 \\ \hline
+		& \textbf{Kasthuri Vol. 1} & \textbf{Kasthuri Vol. 2} \\ \hline
 		Graph Generation & 34.76s & 35.90s \\
@@
 		Total Time & 96.17s & 95.93s \\ \hline
-	\end{tabular}
-	\begin{tabular}{c c c } \hline
-		& FlyEM Vol. 1 & FlyEM Vol. 2 \\ \hline
+		& \textbf{FlyEM Vol. 1} & \textbf{FlyEM Vol. 2} \\ \hline
 		Graph Generation & 46.52s & 48.97s \\
@@
 	\end{tabular}
+	\caption{Performance of each step of the framework for all four datasets.}
+	\label{table:performance}
 \end{table}

### 2017-11-22 papers/cvpr2018/supplemental/skeletonization.tex
supplemental: cleaned up the writing

--- 2017-11-09 papers/cvpr2018/supplemental/skeletonization.tex
@@
-\section{Skeletonization}
+\section{Graph Creation}
 
-more details regarding the skeletonization approach, which I believe was extra fast?
+\subsection{Node Pruning}
 
-\subsection{Parameters}
+We remove all nodes from the graph corresponding to labels with fewer than $t_{seg}$ voxels (Section 3.1).
+Figure \ref{fig:node-pruning} shows the results of varying $t_{seg}$ on two different quantities for the Kasthuri training volume. 
+The blue line indicates the number of nodes remaining in the graph.
+The rate of node reduction decreases for larger thresholds since there are fewer labels of larger size. 
+The green line shows the percent of voxels with a label pruned from the graph.
+Ideally this number is low since we want to remove small segments which do not contribute much to the overall volume.
+These are locations which we cannot improve the variation of information scores.
+This ``volume lost" grows at an increasing rate as the larger segments are removed. 
+Based on these curves we set $t_{seg} = 20000$ voxels.
+With this threshold, we prune over half of the labels that correspond to around $1.5\%$ of the total volume.
 
-\subsection{Performance Tests}
+\subsection{Edge Pruning}
+
+There are two parameters in the two-pass edge pruning algorithm, $t_{low}$ and $t_{high}$ (Section 3.2). 
+The resulting graph should have the highest possible percentage of split errors still present while keeping the number of total edges low. 
+We perform a search over varying thresholds for $40\textrm{nm} \leq t_{low} \leq 300 \textrm{nm}$ and $300 \textrm{nm} \leq t_{high} \leq 800 \textrm{nm}$ on the Kasthuri training dataset to find the parameter with the highest retention of true splits that keeps the number of total edges less than $6 \times$ the number of split errors.
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=0.95\linewidth]{./figures/node-threshold.png}
+		\caption{The number of remaining nodes after increasing the threshold (blue) and the number of voxels with this label as a percent of the total volume (green). }
+		\label{fig:node-pruning}
+	\end{center}
+\end{figure}

### 2017-11-22 papers/cvpr2018/supplemental/classifier.tex
supplemental: final updates

@@
 From these locations we extract a cubic region of interest.
-We experimented with three different region of interest side lengths: $800 \textrm{nm}$, $1200 \textrm{nm}$, and $1600 \textrm{nm}$. 
-Side lengths of $1600 \textrm{nm}$ performed better on the training and validation data on our networks.
+We experimented with three different cube side lengths: $800 \textrm{nm}$, $1200 \textrm{nm}$, and $1600 \textrm{nm}$. 
+Side lengths of $1600 \textrm{nm}$ performed better on the training and validation data on our network.
 
@@
 We considered two optimizers: stochastic gradient descent with Nesterov momentum and Adam~\cite{kingma2014adam}.
-In addition we tried two different loss functions: binary cross entropy and mean squared error.
-We also experimented with four different input sizes that correspond to different cube sizes output from the final max pooling layer. 
-After running a brute force search over all of these possible architectures, we found that the best architecture used a SGD optimizer with Nesterov momentum, a mean squared error loss function, and an input size of $76 \times 76 \times 24$.
+In addition we tried two different loss functions: binary cross-entropy and mean squared error.
+We also experimented with four different input sizes based on the output size of the last max pooling layer.
+After running a brute force search over all of these architectures, we found that the best architecture used a SGD optimizer with Nesterov momentum, a mean squared error loss function, and an input size of $76 \times 76 \times 24$.
 
@@
 The input data was $76 \times 76 \times 24$ voxels with $3$ channels per voxel. 
-This corresponds to an output size from the third max pooling layer of $6 \times 6 \times 6$. 
-This flattens to a $13,824$-element vector and two dense layers of output size $512$ and $1$ follow. 
+This corresponds to an output size from the third max pooling layer of $6 \times 6 \times 6$ with 64 filters. 
+This flattens to a $13,824$ element vector and two dense layers of output size $512$ and $1$ follow. 
 All activation layers are Leaky ReLU with $\alpha=0.001$ except for the final layer which has a sigmoid activation.

### 2017-11-28 cnns/skeleton/bckup-generate_features.py
removed timing for supplemental material

@@ -1,304 +1,0 @@
-import numpy as np
-import random
-import struct
-import math
-from numba import jit
-
-from ibex.utilities.constants import *
-from ibex.utilities import dataIO
-from ibex.transforms import seg2seg, seg2gold
-from ibex.cnns.skeleton.util import SkeletonCandidate
-from ibex.data_structures import unionfind
-from PixelPred2Seg import comparestacks
-
-
-
-
-# save the candidate files for the CNN
-def SaveCandidates(output_filename, positive_candidates, negative_candidates, inference=False, undetermined_candidates=None):
-    if not undetermined_candidates == None:
-        candidates = undetermined_candidates
-        random.shuffle(candidates)
-    elif inference:
-        # concatenate the two lists
-        candidates = positive_candidates + negative_candidates
-        random.shuffle(candidates)
-    else:
-        # randomly shuffle the arrays
-        random.shuffle(positive_candidates)
-        random.shuffle(negative_candidates)
-
-        # get the minimum length of the two candidates - train in pairs
-        npoints = max(len(positive_candidates), len(negative_candidates))
-        positive_index = 0
-        negative_index = 0
-
-        # train in pairs, duplicate when needed
-        candidates = []
-        for _ in range(npoints):
-            candidates.append(positive_candidates[positive_index])
-            candidates.append(negative_candidates[negative_index])
-
-            # increment the indices
-            positive_index += 1
-            negative_index += 1
-
-            # handle dimension mismatch by reseting index and reshuffling array
-            if positive_index >= len(positive_candidates): 
-                positive_index = 0
-                random.shuffle(positive_candidates)
-            if negative_index >= len(negative_candidates): 
-                negative_index = 0
-                random.shuffle(negative_candidates)
-            
-    # write all candidates to the file
-    with open(output_filename, 'wb') as fd:
-        fd.write(struct.pack('i', len(candidates)))
-
-        # add every candidate to the binary file
-        for candidate in candidates:
-            # get the labels for this candidate
-            label_one = candidate.labels[0]
-            label_two = candidate.labels[1]
-
-            # get the location of this candidate
[…]

### 2017-11-28 cnns/skeleton/bckup-train.py

@@ -1,240 +1,0 @@
-import time
-import numpy as np
-import os
-
-
-from ibex.utilities.constants import *
-from ibex.utilities import dataIO
-from ibex.cnns.skeleton.util import FindCandidates, ExtractFeature
-
-
-from keras.models import Sequential
-from keras.layers import Activation, BatchNormalization, Convolution3D, Dense, Dropout, Flatten, MaxPooling3D
-from keras.layers.advanced_activations import LeakyReLU
-from keras.optimizers import Adam, SGD
-from keras import backend
-
-
-
-# add a convolutional layer to the model
-def ConvolutionalLayer(model, filter_size, kernel_size, padding, activation, normalization, input_shape=None):
-    if not input_shape == None: model.add(Convolution3D(filter_size, kernel_size, padding=padding, input_shape=input_shape))
-    else: model.add(Convolution3D(filter_size, kernel_size, padding=padding))
-
-    # add activation layer
-    if activation == 'LeakyReLU': model.add(LeakyReLU(alpha=0.001))
-    else: model.add(Activation(activation))
-    
-    # add normalization after activation
-    if normalization: model.add(BatchNormalization())
-
-
-
-# add a pooling layer to the model
-def PoolingLayer(model, pool_size, dropout, normalization):
-    model.add(MaxPooling3D(pool_size=pool_size))
-
-    # add normalization before dropout
-    if normalization: model.add(BatchNormalization())
-
-    # add dropout layer
-    if dropout > 0.0: model.add(Dropout(dropout))
-
-
-
-# add a flattening layer to the model
-def FlattenLayer(model):
-    model.add(Flatten())
-
-
-
-# add a dense layer to the model
-def DenseLayer(model, filter_size, dropout, activation, normalization):
-    model.add(Dense(filter_size))
-    if (dropout > 0.0): model.add(Dropout(dropout))
-
-    # add activation layer
-    if activation == 'LeakyReLU': model.add(LeakyReLU(alpha=0.001))
-    else: model.add(Activation(activation))
-
-    # add normalization after activation
-    if normalization: model.add(BatchNormalization())
-
-
-
-def SkeletonNetwork(parameters, width):
-    # identify convenient variables
-    initial_learning_rate = parameters['initial_learning_rate']
-    decay_rate = parameters['decay_rate']
-    activation = parameters['activation']
-    normalization = parameters['normalization']
[…]

### 2017-11-28 cnns/skeleton/forward.py

@@ -55,6 +55,7 @@ def Forward(prefix, model_prefix, threshold, maximum_distance, network_distance,
     ncandidates = len(candidates)
 
     # get the probabilities
+    start_time = time.time()
     probabilities = model.predict_generator(SkeletonCandidateGenerator(prefix, network_distance, candidates, width), ncandidates, max_q_size=200)
     predictions = Prob2Pred(np.squeeze(probabilities))
 

### 2017-11-28 cnns/skeleton/generate_features.py

@@ -1,5 +1,4 @@
 import math
-import time
 import numpy as np
 import random
 import struct
@@ -123,11 +122,11 @@ def GenerateFeatures(prefix, threshold, maximum_distance, network_distance, endp
 
     # get the mapping from segmentation to gold
     seg2gold_mapping = seg2gold.Mapping(segmentation, gold, low_threshold=0.10, high_threshold=0.80)
-
+    
     # remove small connceted components
     segmentation = seg2seg.RemoveSmallConnectedComponents(segmentation, threshold=threshold).astype(np.int64)
     max_label = np.amax(segmentation) + 1
-
+    
     # get the grid size and the world resolution
     grid_size = segmentation.shape
     world_res = dataIO.Resolution(prefix)
@@ -233,15 +232,15 @@ def GenerateFeatures(prefix, threshold, maximum_distance, network_distance, endp
             elif ground_truth: positive_candidates.append(candidate)
             else: negative_candidates.append(candidate)
 
-    # # save the files
+    # save the files
     train_filename = 'features/skeleton/{}-{}-{}nm-{}nm-training.candidates'.format(prefix, threshold, maximum_distance, network_distance)
     validation_filename = 'features/skeleton/{}-{}-{}nm-{}nm-validation.candidates'.format(prefix, threshold, maximum_distance, network_distance)
     forward_filename = 'features/skeleton/{}-{}-{}nm-{}nm-inference.candidates'.format(prefix, threshold, maximum_distance, network_distance)
     undetermined_filename = 'features/skeleton/{}-{}-{}nm-{}nm-undetermined.candidates'.format(prefix, threshold, maximum_distance, network_distance)
     
     if training_data:
-        SaveCandidates(train_filename, positive_candidates, negative_candidates, inference=False, validation=False)
-        SaveCandidates(validation_filename, positive_candidates, negative_candidates, inference=False, validation=True)
+       SaveCandidates(train_filename, positive_candidates, negative_candidates, inference=False, validation=False)
+       SaveCandidates(validation_filename, positive_candidates, negative_candidates, inference=False, validation=True)
     SaveCandidates(forward_filename, positive_candidates, negative_candidates, inference=True)
     SaveCandidates(undetermined_filename, positive_candidates, negative_candidates, undetermined_candidates=undetermined_candidates)
 

### 2017-11-28 papers/cvpr2018/2_method.tex
updated figures

@@
 	\end{center}
-	\caption{Outline of our approach, from left to right: Result of the pixel-based segmentation and agglomeration algorithm; segments of several selected neurons from the initial segmentation; extracted skeletonized 3D network of those segments; improved 3D reconstruction of the selected segments after graph construction and partitioning with constraints.}
+	\caption{Outline of our approach, from left to right: result of the pixel-based segmentation and agglomeration algorithm; segments of several selected neurons from the initial segmentation; extracted skeletonized 3D network of those segments; improved 3D reconstruction of the selected segments after graph construction and partitioning with constraints.}
 	\label{fig:overview}
@@
 	\centering
-	\includegraphics[width=0.92\linewidth]{./figures/skeleton1.png}
-	\includegraphics[width=0.92\linewidth]{./figures/skeleton2.png}
-	\caption{Example skeletons (in black) extracted from segments (blue and green) using the TEASER algorithm. \hp{there is enough space to add another example in this figure}}
+	\includegraphics[width=0.82\linewidth]{./figures/skeleton1.png}
+	\includegraphics[width=0.82\linewidth]{./figures/skeleton2.png}
+	\includegraphics[width=0.82\linewidth]{./figures/skeleton3.png}
+	\caption{Example skeletons (in black) extracted from segments using the TEASER algorithm.}
 	\label{fig:skeletonization}
@@
 
-From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with non-negative edge weights $w_e$.
+From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with weights $w_e$.
 The nodes correspond to label segments from the segmentation with edges between segments considered for merging.
@@
 First, we extract a skeleton from each segment in the label volume using the TEASER algorithm~\cite{sato2000teasar,zhao2014automatic}.
-Fig.~\ref{fig:skeletonization} shows an example of two extracted skeletons (in black).
+Fig.~\ref{fig:skeletonization} shows an example of three extracted skeletons (in black).
 These skeletons consist of a sequence of \textit{joints}, i.e., locations that are locally a maximum distance from the segment boundary, with line segments connecting successive joints.
@@
 Instead of using handcrafted features to compute the similarity between adjacent nodes, we train a 3D CNN classifier to learn from the manually labeled oversegmentation input volume (Sec.~\ref{sec:dataset}).
-If the probability of the nodes belonging to the same neuron is $p_e$, the edge weight $w_e = \log{\frac{p_e}{1 - p_e}} + \log{\frac{1 - \beta}{\beta}}$, where $\beta$ is a tunable parameter that encourages over or undersegmentation.
+If the probability that the nodes belong to the same neuron is $p_e$, the edge weight $w_e = \log{\frac{p_e}{1 - p_e}} + \log{\frac{1 - \beta}{\beta}}$, where $\beta$ is a tunable parameter that encourages over- or under-segmentation.
 %Our  edge weights  correspond to probabilities that two endpoints $e$ in $\mathbb{S}_c$ belong to the same neuron and should be merged. \hp{check}
@@
 It consists of three layers of double convolutions followed by a max pooling step.
-The first max pooling layer is anisotropic with pooling only in the $x$ and $y$ dimensions.
+The first two max pooling layers are anisotropic with pooling only in the $x$ and $y$ dimensions.
 The output of this final pooling step is flattened into a 1D vector that is input into two fully connected layers.

### 2017-11-28 papers/cvpr2018/paper.tex
updated figures

@@
 %%%%%%%%% TITLE
-\title{Graph-Based Neural Reconstruction \\ from Skeletonized 3D Networks}
+\title{Graph-Based Neural Reconstruction from Skeletonized 3D Networks}
 % Neural Reconstruction Using Skeletonized 3D Networks
@@
 In this work, we follow bottom-up pixel-based reconstruction by a top-down graph-based method to more accurately approximate neural pathways.
-We first generate skeletons in 3D from the membrane labels of the pixel-based segmentation.
+We first generate skeletons in 3D from the neuron labels of the pixel-based segmentation.
 We then simplify this skeletonized 3D network into a 3D graph with nodes corresponding to labels from the segmentation and edges identifying potential locations of segmentation errors.
@@
 Because the 3D graph is small and encodes top-down information our method is efficient and globally improves the neural reconstruction.
-We demonstrate the performance of our approach on multiple real-world connectomics datasets with an average variation of information improvement of \FIX{$X\times$}.
+We demonstrate the performance of our approach on multiple real-world connectomics datasets with an average split variation of information improvement of 19.3\%.
 %The paper provides insights into learning shape features for top-down graph-based neuron reconstruction.

### 2017-11-28 papers/cvpr2018/supplemental/performance.tex

@@
 All code is written in Python and will be freely available upon the paper decision.
-We use the Keras deep learning library for our neural networks with Theano backend and cuDNN 7 acceleration for cuda 8.0.
+We use the Keras deep learning library for our neural networks with Theano backend and cuDNN 7 acceleration for CUDA 8.0.
 
@@
 
-The network trained for $34$ epochs with each epoch taking approximately $1200$ seconds to complete.
+We train the network for $34$ epochs with each epoch taking approximately $1200$ seconds to complete.
 Table \ref{table:performance} shows the total running time for each dataset for graph creation, CNN inference, and multicut partitioning. 
-In all instances the time for these three steps combined was less than 100 seconds.
+In all instances the time for these three steps combined is less than 100 seconds.
 Currently extracting the skeletons with the TEASER algorithm is the bottleneck.
-The skeleton for each label takes around $20-30$ seconds to generate. 
+The skeleton for each label takes around $20$ to $30$ seconds to generate. 
 However, the process is parallelizable as each segment can be processed independently.
-Faster skeleton extraction is an important area for future research, particularly to consider algorithms in different fields~\cite{fazekas2008skeletonization}.
-There is some existing research of fast topologically preserving skeleton generation and their applications to existing medical images (e.g. blood vessels, the colon)~\cite{palagyi2001sequential}.
+Faster skeleton extraction is an important area for future research.
+There is some existing research on fast skeleton generation and its applications to existing medical images (e.g. blood vessels, the colon)~\cite{palagyi2001sequential}.
 
@@
 		& \textbf{Kasthuri Vol. 1} & \textbf{Kasthuri Vol. 2} \\ \hline
-		Graph Generation & 34.76s & 35.90s \\
+		Graph Creation & 34.76s & 35.90s \\
 		Inference & 38.47s & 37.13s \\
@@
 		& \textbf{FlyEM Vol. 1} & \textbf{FlyEM Vol. 2} \\ \hline
-		Graph Generation & 46.52s & 48.97s \\
+		Graph Creation & 46.52s & 48.97s \\
 		Inference & 12.55s & 10.91s \\

### 2017-11-28 papers/cvpr2018/supplemental/skeletonization.tex

@@
 Ideally this number is low since we want to remove small segments which do not contribute much to the overall volume.
-These are locations which we cannot improve the variation of information scores.
 This ``volume lost" grows at an increasing rate as the larger segments are removed. 
-Based on these curves we set $t_{seg} = 20000$ voxels.
-With this threshold, we prune over half of the labels that correspond to around $1.5\%$ of the total volume.
+Based on these curves we set $t_{seg} = 20,000$ voxels.
+With this threshold, we prune over half of the labels and only lose $1.5\%$ of the total volume.
 
@@
 There are two parameters in the two-pass edge pruning algorithm, $t_{low}$ and $t_{high}$ (Section 3.2). 
-The resulting graph should have the highest possible percentage of split errors still present while keeping the number of total edges low. 
-We perform a search over varying thresholds for $40\textrm{nm} \leq t_{low} \leq 300 \textrm{nm}$ and $300 \textrm{nm} \leq t_{high} \leq 800 \textrm{nm}$ on the Kasthuri training dataset to find the parameter with the highest retention of true splits that keeps the number of total edges less than $6 \times$ the number of split errors.
+The resulting graph should have a high percentage of the original split errors still present while keeping the number of total edges low. 
+We perform a search over several thresholds from $40\textrm{nm} \leq t_{low} \leq 300 \textrm{nm}$ and $300 \textrm{nm} \leq t_{high} \leq 800 \textrm{nm}$ on the Kasthuri training dataset to find the parameter with the highest retention of split errors while keeping the total number of edges less than $6 \times$ the number of split errors.
 

### 2018-01-24 papers/cvpr2018/rebuttal/egrebuttal.tex
papers: fixed missing dependencies and added rebuttal

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{0446} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{\LaTeX\ Guidelines for Author Response}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
\section{Introduction}

After receiving paper reviews, authors may optionally submit a rebuttal to address the reviewers' comments, which will be limited to a {\bf one page} PDF file.  Please follow the steps and style guidelines outlined below for submitting your author response.

Note that the author rebuttal is optional and, following similar guidelines to previous CVPR conferences, it is meant to provide you with an opportunity to rebut factual errors or to supply additional information requested by the reviewers. It is NOT intended to add new contributions (theorems, algorithms, experiments) that were not included in the original submission and were not requested by the reviewers. You may optionally add a figure, graph or proof to your rebuttal to better illustrate your answer to the reviewers' comments.

The rebuttal must adhere to the same blind-submission as the original submission and must comply with this rebuttal-formatted template.

%-------------------------------------------------------------------------

\subsection{Response length}
Author responses must be no longer than 1 page in length including any references and figures.  Overlength responses will simply not be reviewed.  This includes responses where the margins and formatting are deemed to have been significantly altered from those laid down by this style guide.  Note that this \LaTeX\ guide already sets figure captions and references in a smaller font.

%------------------------------------------------------------------------
\section{Formatting your Response}

{\bf Make sure to update the paper title and paper ID in the appropriate place in the tex file.}

All text must be in a two-column format. The total allowable width of the text
area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54 cm) high.
Columns are to be $3\frac14$ inches (8.25 cm) wide, with a $\frac{5}{16}$ inch
(0.8 cm) space between them. The top margin should begin
1.0 inch (2.54 cm) from the top edge of the page.  The bottom margin should be
1-1/8 inches (2.86 cm) from the bottom edge of the page for $8.5 \times
11$-inch paper; for A4 paper, approximately 1-5/8 inches (4.13 cm) from the
bottom edge of the page.

Please number all of your sections and any displayed equations.  It is important
for readers to be able to refer to any particular equation.

Wherever Times is specified, Times Roman may also be used.  Main text should be
in 10-point Times, single-spaced. Section headings should be in 10 or 12 point
Times.  All paragraphs should be indented 1 pica (approx. 1/6 inch or 0.422
cm).  Figure and table captions should be 9-point Roman type as in
Figure~\ref{fig:onecol}.

%-------------------------------------------------------------------------
\subsection{References}

List and number all bibliographical references in 9-point Times, single-spaced,
at the end of your response. When referenced in the text, enclose the citation
number in square brackets, for example~\cite{Authors14}.  Where appropriate,
include the name(s) of editors of referenced books.

\begin{figure}[t]
\begin{center}
\fbox{\rule{0pt}{1.8in} \rule{0.9\linewidth}{0pt}}
   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
\end{center}
   \caption{Example of caption.  It is set in Roman so that mathematics
   (always set in Roman: $B \sin A = A \sin B$) may be included without an
   ugly clash.}
\label{fig:long}
\label{fig:onecol}
\end{figure}

%-------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

All graphics should be centered.  Please ensure that any point you wish to make is resolvable in a printed copy of the response.  Resize fonts in figures to match the font in the body text, and choose line widths which render effectively in print.  Many readers (and reviewers), even of an electronic copy, will choose to print your response in order to read it.  You cannot insist that they do otherwise, and therefore must not assume that they can zoom in to see tiny details on a graphic.

When placing figures in \LaTeX, it's almost always best to use \verb+\includegraphics+, and to specify the  figure width as a multiple of the line width as in the example below
{\small\begin{verbatim}
   \usepackage[dvips]{graphicx} ...
   \includegraphics[width=0.8\linewidth]
                   {myfile.eps}
\end{verbatim}
}

{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\end{document}

### 2018-01-24 super_resolution/single_image_sr.py
Merging super resolution

@@ -375,7 +375,7 @@ def SuperResolution(parameters, hierarchies, n):
     blurs = [Gaussian(pow(scale, iv), truncate) for iv in range(n + 1)]
 
     # use example based or classical only
-    classical_only = False
+    classical_only = True
     example_only = False
     assert (not example_only or not classical_only)
 

### 2018-01-24 papers/cvpr2018/rebuttal/egrebuttal.tex
updated rebuttal

@@
 %%%%%%%%% TITLE - PLEASE UPDATE
-\title{\LaTeX\ Guidelines for Author Response}  % **** Enter the paper title here
+\title{Graph-Based Neural Reconstruction from Skeletonized 3D Networks}  % **** Enter the paper title here
 
@@
 %%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
-\section{Introduction}
 
-After receiving paper reviews, authors may optionally submit a rebuttal to address the reviewers' comments, which will be limited to a {\bf one page} PDF file.
-Please follow the steps and style guidelines outlined below for submitting your author response.
+We would like to thank the reviewers for their time.
 
-Note that the author rebuttal is optional and, following similar guidelines to previous CVPR conferences, it is meant to provide you with an opportunity to rebut factual errors or to supply additional information requested by the reviewers.
-It is NOT intended to add new contributions (theorems, algorithms, experiments) that were not included in the original submission and were not requested by the reviewers.
-You may optionally add a figure, graph or proof to your rebuttal to better illustrate your answer to the reviewers' comments.
+\section*{Reviewer 1}
 
-The rebuttal must adhere to the same blind-submission as the original submission and must comply with this rebuttal-formatted template.
+\textbf{A1.} We thank the reviewer for linking to these four recent papers, although they are working on a different issue.
+Our algorithm works by correcting the merge errors generated by current segmentation algorithms.
+The Funke et al.
+paper is actually a pre-paper arxiv submission for the CVPR conference.
+We take issue with the statement that ``the paper does not adequately reflect prior art, rendering its own conclusions questionable.'' In fact, reviewer 3 wrote as a strength ``the list of references is impressive, demonstrating comprehensive knowledge of both recent methods and the application domain''.
 
-%-------------------------------------------------------------------------
+\textbf{A2.} This claim refers to building on-top of existing segmentation pipelines.
+We will clarify this point in the next revision.
+LASH extracts a graph from superpixels generated from a watershed.
+We extract a graph from this output at a different abstraction layer.
 
-\subsection{Response length}
-Author responses must be no longer than 1 page in length including any references and figures.
-Overlength responses will simply not be reviewed.
-This includes responses where the margins and formatting are deemed to have been significantly altered from those laid down by this style guide.
-Note that this \LaTeX\ guide already sets figure captions and references in a smaller font.
+\textbf{A3.} We don't agree with the assertion that these are ``drastic'' examples but rather honest mistakes.
+We can easily add an additional reference for U-Net that extends the original paper to 3D.
+In fact, citing reference [18] for the multicut algorithm is not a mistake at all.
+We use the graph optimization library from Bjoern Andres\footnote{http://www.andres.sc/graph.html} which cites [18] (his own work) for the multicut package.
+We will update the reference to Funke et al. as this was a simple LaTex citation mistake.
 
-%------------------------------------------------------------------------
-\section{Formatting your Response}
+\textbf{B1.} We agree that skeletonization can improve but our goal for this paper is to use an existing method and explore its application to new ideas.
 
-{\bf Make sure to update the paper title and paper ID in the appropriate place in the tex file.}
+\textbf{B2.} This is incorrect, the skeletons from the figures are from the Kasthuri et al. data.
 
-All text must be in a two-column format. The total allowable width of the text
-area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54 cm) high.
-Columns are to be $3\frac14$ inches (8.25 cm) wide, with a $\frac{5}{16}$ inch
-(0.8 cm) space between them. The top margin should begin
-1.0 inch (2.54 cm) from the top edge of the page.  The bottom margin should be
-1-1/8 inches (2.86 cm) from the bottom edge of the page for $8.5 \times
-11$-inch paper; for A4 paper, approximately 1-5/8 inches (4.13 cm) from the
-bottom edge of the page.
+\textbf{B3.} This is addressed in the paper.
+First the cubic region of interest is in nanometers, not voxels.
+From section 4.8, ``Since our CNN only takes as input a region of the label volume we can train on anisotropic data and test on isotropic data.'' In the same section we show the results when training on isotropic data (Fig.
+9).
 
-Please number all of your sections and any displayed equations.  It is important
-for readers to be able to refer to any particular equation.
+\textbf{B4.} We address this in the supplemental material. We can include a reference to the supplemental material in the future.
 
-Wherever Times is specified, Times Roman may also be used.  Main text should be
-in 10-point Times, single-spaced. Section headings should be in 10 or 12 point
-Times.  All paragraphs should be indented 1 pica (approx. 1/6 inch or 0.422
-cm).  Figure and table captions should be 9-point Roman type as in
-Figure~\ref{fig:onecol}.
+\textbf{B5.} Without the images, we avoid retraining for every new dataset that has different staining or resolution, which is every dataset that we receive from our biology collaborators.
+We will clarify this point in a revision.
 
-%-------------------------------------------------------------------------
-\subsection{References}
+\textbf{B6.} This analysis is provided in Sec. 4.7 and Table 2.
 
-List and number all bibliographical references in 9-point Times, single-spaced,
-at the end of your response. When referenced in the text, enclose the citation
-number in square brackets, for example~\cite{Authors14}.  Where appropriate,
-include the name(s) of editors of referenced books.
+\textbf{B7.} We are not using ``lifted'' multicut but only the greedy-edge contraction method.
 
-\begin{figure}[t]
-\begin{center}
-\fbox{\rule{0pt}{1.8in} \rule{0.9\linewidth}{0pt}}
-   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
-\end{center}
-   \caption{Example of caption.  It is set in Roman so that mathematics
-   (always set in Roman: $B \sin A = A \sin B$) may be included without an
-   ugly clash.}
-\label{fig:long}
-\label{fig:onecol}
-\end{figure}
+\textbf{B8.
+Section 3.4 states that acyclic partitionings are enforced.
+Since acyclic regions are not an inherent outcome of the multicut algorithm, this requires a modified multicut, but the modification is unspecified.}
 
-%-------------------------------------------------------------------------
-\subsection{Illustrations, graphs, and photographs}
+\textbf{B9.} Here we reference the possibility for additional constraints using our new novel framework.
+Currently that enforces neurons to be acyclic but in the future can use other information.
+The important idea was that this framework allows domain-specific constraints.
 
-All graphics should be centered.
-Please ensure that any point you wish to make is resolvable in a printed copy of the response.
-Resize fonts in figures to match the font in the body text, and choose line widths which render effectively in print.
-Many readers (and reviewers), even of an electronic copy, will choose to print your response in order to read it.
-You cannot insist that they do otherwise, and therefore must not assume that they can zoom in to see tiny details on a graphic.
+\textbf{C1.} We use NeuroProof because it scales to terabyte datasets.
+Flood filling networks provide better accuracy but are 25x slower and work on a single neuron at a time.
+For dense reconstruction, NeuroProof is state-of-the-art.
+Variation of Information overcomes previous limitations of rand error and is more widely used by the community~\cite{lee2017superhuman,nunez2013machine}.
+The SNEMI3D dataset is considered outdated as concluded in~\cite{lee2017superhuman}.
 
-When placing figures in \LaTeX, it's almost always best to use \verb+\includegraphics+, and to specify the  figure width as a multiple of the line width as in the example below
-{\small\begin{verbatim}
-   \usepackage[dvips]{graphicx} ...
-   \includegraphics[width=0.8\linewidth]
-                   {myfile.eps}
-\end{verbatim}
-}
+\textbf{C2.} Most of the current state-of-the-art methods are too slow to run on very large datasets.
+
+\section*{Reviewer 2}
+
+Unfortunately the challenge datasets (SNEMI3D, CREMI) are too small for meaningful improvement. The datasets presented in our paper are roughly ten times the size of these challenge datasets.
+
+\section*{Reviewer 3}
+
+\textbf{Address acyclic nature of graph.}
+
+There are some polynomial time algorithms for finding the general minimum spanning forest on a general graph ($O(V^2 E)$).
+The multicut algorithm we use has a running time of $O(V^2 log(V))$, although provides an approximation to the optimal solution.
+Exploring both of these algorithms is reasonable in a future revision.
 

### 2018-01-24 papers/cvpr2018/rebuttal/egrebuttal.tex
updated tone of supplemental material

@@
 
-\textbf{A1.} We thank the reviewer for linking to these four recent papers, although they are working on a different issue.
-Our algorithm works by correcting the merge errors generated by current segmentation algorithms.
-The Funke et al.
-paper is actually a pre-paper arxiv submission for the CVPR conference.
-We take issue with the statement that ``the paper does not adequately reflect prior art, rendering its own conclusions questionable.'' In fact, reviewer 3 wrote as a strength ``the list of references is impressive, demonstrating comprehensive knowledge of both recent methods and the application domain''.
+\textbf{A1.} 
+We thank the reviewer for showing us these four recent papers, and we will cite them in the next revision. 
+However, we believe that our work focuses on a slightly different problem. 
+Our algorithm corrects the split errors generated by current segmentation algorithms. 
+These papers show impressive results but are fundamentally pixel-based methods whereas our method explores higher level error correction. 
+We take issue with the statement that ``the paper does not adequately reflect prior art, rendering its own conclusions questionable.'' 
+In fact, reviewer 3 wrote ``the list of references is impressive, demonstrating comprehensive knowledge of both recent methods and the application domain.''
 
-\textbf{A2.} This claim refers to building on-top of existing segmentation pipelines.
-We will clarify this point in the next revision.
-LASH extracts a graph from superpixels generated from a watershed.
-We extract a graph from this output at a different abstraction layer.
+\textbf{A2.} 
+This claim refers to building on-top of existing segmentation pipelines. 
+We will clarify this point in our revision. 
+In \textit{Learning to Agglomerate Superpixel Hierarchies}, Jain et al. extract a graph from superpixels generated by a watershed algorithm. 
+We, on the other hand, would use the output of \textit{LASH} as input to our framework. 
+Then, We extract a graph from this input.
 
-\textbf{A3.} We don't agree with the assertion that these are ``drastic'' examples but rather honest mistakes.
-We can easily add an additional reference for U-Net that extends the original paper to 3D.
+\textbf{A3.} 
+We do not agree with the assertion that these are ``drastic'' errors but rather honest mistakes. 
 In fact, citing reference [18] for the multicut algorithm is not a mistake at all. 
-We use the graph optimization library from Bjoern Andres\footnote{http://www.andres.sc/graph.html} which cites [18] (his own work) for the multicut package.
-We will update the reference to Funke et al. as this was a simple LaTex citation mistake.
+We use the graph optimization library from Bjoern Andres' website\footnote{http://www.andres.sc/graph.html} which cites [18] (his own work) for the multicut package. 
+We will add an additional reference for U-Net that extends the original paper to 3D.
+We will update the reference to Funke et al.; this was an accidental LaTex citation omission.
 
-\textbf{B1.} We agree that skeletonization can improve but our goal for this paper is to use an existing method and explore its application to new ideas.
+\textbf{B1.} 
+We agree that the skeletonization algorithm can improve but our goal for this paper is to use an existing method and explore its application to new ideas.
+We chose this method with its corresponding default parameters because it has been used previously for neuron skeletonization.
 
-\textbf{B2.} This is incorrect, the skeletons from the figures are from the Kasthuri et al. data.
+\textbf{B2.} 
+The skeletons from the figures are actually from the anisotropic Kasthuri dataset.
 
-\textbf{B3.} This is addressed in the paper.
-First the cubic region of interest is in nanometers, not voxels.
-From section 4.8, ``Since our CNN only takes as input a region of the label volume we can train on anisotropic data and test on isotropic data.'' In the same section we show the results when training on isotropic data (Fig.
-9).
+\textbf{B3.} 
+We address this in the paper.
+The cubic region of interest is actually in nanometers, not voxels.
+We further discuss this parameter in the supplemental materials (Sec. 2.1). 
+In a future revision we will clarify this better.
 
-\textbf{B4.} We address this in the supplemental material. We can include a reference to the supplemental material in the future.
+From section 4.8, ``Since our CNN only takes as input a region of the label volume we can train on anisotropic data and test on isotropic data.'' 
+In the same section we show the results when training on isotropic data (Fig. 9).
 
-\textbf{B5.} Without the images, we avoid retraining for every new dataset that has different staining or resolution, which is every dataset that we receive from our biology collaborators.
-We will clarify this point in a revision.
+\textbf{B4.} 
+We address this in the supplemental material, and will reference it in the future.
 
-\textbf{B6.} This analysis is provided in Sec. 4.7 and Table 2.
+\textbf{B5.} 
+Without the images, we avoid retraining for every new dataset that has different staining or resolution.
+This reduces the amount of expert-labeled ground truth required for every new dataset.
+In our experience with our biological collaborators, every dataset has slightly different staining so this offers a large advantage.
+We will clarify our thinking.
 
-\textbf{B7.} We are not using ``lifted'' multicut but only the greedy-edge contraction method.
+\textbf{B6.} 
+This analysis is provided in Sec. 4.7 and Table 2.
+
+\textbf{B7.} 
+We are not using ``lifted'' multicut but only the greedy-edge contraction method.
 
@@
 
-\textbf{B9.} Here we reference the possibility for additional constraints using our new novel framework.
-Currently that enforces neurons to be acyclic but in the future can use other information.
-The important idea was that this framework allows domain-specific constraints.
+\textbf{B9.} 
+We reference the possibility for additional constraints using our new novel framework. 
+Currently we enforce neurons to be acyclic.
+This is a non-trivial constraint for massive datasets where neurons span the entire volume. 
+We can later extend our framework
 
@@
 For dense reconstruction, NeuroProof is state-of-the-art. 
-Variation of Information overcomes previous limitations of rand error and is more widely used by the community~\cite{lee2017superhuman,nunez2013machine}.
-The SNEMI3D dataset is considered outdated as concluded in~\cite{lee2017superhuman}.
+Variation of Information overcomes previous limitations of Rand error~\cite{lee2017superhuman,nunez2013machine}. 
+The SNEMI3D dataset is outdated~\cite{lee2017superhuman}.
 
-\textbf{C2.} Most of the current state-of-the-art methods are too slow to run on very large datasets.
+\textbf{C2.} Most of the current state-of-the-art methods are too slow to run on very large datasets, although we will consider other baselines in a future revision.
 

### 2018-01-25 papers/cvpr2018/rebuttal/egrebuttal.tex
added information on minimum spanning forest

@@
 
+\begin{figure}[h]
+	\begin{center}
+		\includegraphics[width=0.32\linewidth]{./figures/MSF.png}
+		\caption{Error with minimum spanning forest.}
+		\label{figure:msf}
+	\end{center}
+\end{figure}
+
 \textbf{Address acyclic nature of graph.}
 
-There are some polynomial time algorithms for finding the general minimum spanning forest on a general graph ($O(V^2 E)$).
-The multicut algorithm we use has a running time of $O(V^2 log(V))$, although provides an approximation to the optimal solution.
-Exploring both of these algorithms is reasonable in a future revision.
+Fig.~\ref{figure:msf} addresses one problem of using a minimum spanning forest where negative edges represent high affinities and positive edges represent low affinities. 
+With a multicut formulation, the edge between nodes 1 and 4 will keep the blue and green segments separate.
+In a minimum spanning forest nodes 1 and 4 will connect because of the moderate affinity between nodes 2 and 3.
 

### 2018-01-25 papers/cvpr2018/rebuttal/egrebuttal.tex
rebuttal: updated with HP comments and fit on one page

@@
 
-We would like to thank the reviewers for their time.
+We would like to thank the reviewers for their valuable feedback.
 
-\section*{Reviewer 1}
+\subsection*{Reviewer 1}
 
 \textbf{A1.} 
-We thank the reviewer for showing us these four recent papers, and we will cite them in the next revision. 
+We thank the reviewer for pointing out four recent papers, and we will cite them in the next revision.
 However, we believe that our work focuses on a slightly different problem.
 Our algorithm corrects the split errors generated by current segmentation algorithms.
-These papers show impressive results but are fundamentally pixel-based methods whereas our method explores higher level error correction. 
-We take issue with the statement that ``the paper does not adequately reflect prior art, rendering its own conclusions questionable.'' 
-In fact, reviewer 3 wrote ``the list of references is impressive, demonstrating comprehensive knowledge of both recent methods and the application domain.''
+These papers show impressive results but are fundamentally pixel-based methods, whereas our method explores higher level error correction.
+We take issue with the statement that ``the paper does not adequately reflect prior art, rendering its own conclusions questionable.'' In fact, reviewer 3 wrote ``the list of references is impressive, demonstrating comprehensive knowledge of both recent methods and the application domain.''
 
@@
 We will clarify this point in our revision.
-In \textit{Learning to Agglomerate Superpixel Hierarchies}, Jain et al. extract a graph from superpixels generated by a watershed algorithm. 
-We, on the other hand, would use the output of \textit{LASH} as input to our framework. 
-Then, We extract a graph from this input.
+In \textit{Learning to Agglomerate Superpixel Hierarchies}, Jain et al.
+extract a graph from superpixels generated by a watershed algorithm.
+We, on the other hand, use the output of \textit{LASH} as input to our framework.
 
 \textbf{A3.} 
-We do not agree with the assertion that these are ``drastic'' errors but rather honest mistakes. 
-In fact, citing reference [18] for the multicut algorithm is not a mistake at all. 
-We use the graph optimization library from Bjoern Andres' website\footnote{http://www.andres.sc/graph.html} which cites [18] (his own work) for the multicut package. 
+We do not agree with the statement that these are ``drastic'' errors, but rather honest mistakes.
+In fact, citing reference [18] for the multicut algorithm was done deliberately.
+We use the graph optimization library from Bjoern Andres' website\footnote{http://www.andres.sc/graph.html}, which cites [18] (his own work) for the multicut package.
 We will add an additional reference for U-Net that extends the original paper to 3D.
-We will update the reference to Funke et al.; this was an accidental LaTex citation omission.
+We will update the reference to Funke et al.
 
 \textbf{B1.} 
-We agree that the skeletonization algorithm can improve but our goal for this paper is to use an existing method and explore its application to new ideas.
-We chose this method with its corresponding default parameters because it has been used previously for neuron skeletonization.
+We agree that the skeletonization algorithm can be improved.
+Our goal for this paper was to use an existing method with its corresponding default parameters because it had been used previously for neuron skeletonization.
+We are currently working on an improved algorithm.
 
 \textbf{B2.} 
-The skeletons from the figures are actually from the anisotropic Kasthuri dataset.
+The skeletons shown are from an anisotropic dataset.
 
 \textbf{B3.} 
-We address this in the paper.
-The cubic region of interest is actually in nanometers, not voxels.
-We further discuss this parameter in the supplemental materials (Sec. 2.1). 
-In a future revision we will clarify this better.
-
-From section 4.8, ``Since our CNN only takes as input a region of the label volume we can train on anisotropic data and test on isotropic data.'' 
-In the same section we show the results when training on isotropic data (Fig. 9).
+The cubic region of interest is measured in nanometers, not voxels.
+We further discuss this parameter in the supplemental materials (Sec.
+2.1).
+From section 4.8, ``Since our CNN only takes as input a region of the label volume we can train on anisotropic data and test on isotropic data.'' In the same section we show the results when training on isotropic data (Fig.
+9).
+We will clarify this in the revision.
 
 \textbf{B4.} 
-We address this in the supplemental material, and will reference it in the future.
+We address this in the supplemental material, and we will reference it in the revision.
 
 \textbf{B5.} 
-Without the images, we avoid retraining for every new dataset that has different staining or resolution.
-This reduces the amount of expert-labeled ground truth required for every new dataset.
-In our experience with our biological collaborators, every dataset has slightly different staining so this offers a large advantage.
-We will clarify our thinking.
+Without relying on the raw images we avoid retraining for every new dataset that has different staining or resolution.
+This reduces the amount of expert-labeled ground truth required for training every new dataset.
+In our opinion this is a big advantage.
+We will clarify this in the revision.
 
@@
 \textbf{B7.} 
-We are not using ``lifted'' multicut but only the greedy-edge contraction method.
+We are not using the lifted multicut.
 
-\textbf{B8.
-Section 3.4 states that acyclic partitionings are enforced.
-Since acyclic regions are not an inherent outcome of the multicut algorithm, this requires a modified multicut, but the modification is unspecified.}
+\textbf{B8.}
+The multicut algorithm does not enforce acyclic graphs but rather closed-surfaces and consistent solutions.
+We will update this in the next revision.
+We are currently working on adding additional domain-specific constraints.
 
 \textbf{B9.} 
-We reference the possibility for additional constraints using our new novel framework. 
-Currently we enforce neurons to be acyclic.
-This is a non-trivial constraint for massive datasets where neurons span the entire volume. 
-We can later extend our framework
+We mention the possibility for adding additional constraints to our framework in the future. We will clarify this in the revision.
 
-\textbf{C1.} We use NeuroProof because it scales to terabyte datasets. 
-Flood filling networks provide better accuracy but are 25x slower and work on a single neuron at a time. 
+\textbf{C1.} 
+We use NeuroProof because it scales to terabyte datasets.
+Flood filling networks provide better accuracy but are much slower and work on a single neuron at a time.
 For dense reconstruction, NeuroProof is state-of-the-art.
 Variation of Information overcomes previous limitations of Rand error~\cite{lee2017superhuman,nunez2013machine}.
-The SNEMI3D dataset is outdated~\cite{lee2017superhuman}.
 
-\textbf{C2.} Most of the current state-of-the-art methods are too slow to run on very large datasets, although we will consider other baselines in a future revision.
+\textbf{C2.} 
+Most of the current state-of-the-art methods are too slow to run on very large datasets, although we will compare against other baselines in the revision.
 
-\section*{Reviewer 2}
+\subsection*{Reviewer 2}
 
-Unfortunately the challenge datasets (SNEMI3D, CREMI) are too small for meaningful improvement. The datasets presented in our paper are roughly ten times the size of these challenge datasets.
+The challenge datasets are generally too small for meaningful improvements.
+The datasets presented in our paper are ten times the size of these challenge datasets, and our method scales to much larger data.
+In a future revision, we will show the results of our network on these datasets.
 
-\section*{Reviewer 3}
+\subsection*{Reviewer 3}
 
-\begin{figure}[h]
 \begin{center}
-		\includegraphics[width=0.32\linewidth]{./figures/MSF.png}
-		\caption{Error with minimum spanning forest.}
-		\label{figure:msf}
+	\includegraphics[width=0.28\linewidth]{./figures/MSF.png}
 \end{center}
-\end{figure}
 
-\textbf{Address acyclic nature of graph.}
-
-Fig.~\ref{figure:msf} addresses one problem of using a minimum spanning forest where negative edges represent high affinities and positive edges represent low affinities. 
+The figure above addresses one problem of using a minimum spanning forest, where negative and positive edges represent high and low affinities respectively.
 With a multicut formulation, the edge between nodes 1 and 4 will keep the blue and green segments separate.
-In a minimum spanning forest nodes 1 and 4 will connect because of the moderate affinity between nodes 2 and 3.
+In a minimum spanning forest, nodes 1 and 4 will connect because of the moderate affinity between nodes 2 and 3.
 

### 2018-02-20 evaluation/comparestacks.pyx
evaluation: added my own faster evaluation metrics

@@ -1,0 +1,29 @@
+cimport cython
+cimport numpy as np
+import numpy as np
+import ctypes
+
+from ibex.transforms import seg2seg
+
+
+cdef extern from 'cpp-comparestacks.h':
+    void CppEvaluate(long *segmentation, long *gold, long resolution[3], unsigned char mask_ground_truth)
+
+def Evaluate(segmentation, gold, mask_ground_truth=True, filtersize=0):
+    # make sure these elements are the same size
+    assert (segmentation.shape == gold.shape)
+
+    # remove all small connected components
+    if filtersize > 0:
+        segmentation = seg2seg.RemoveSmallConnectedComponents(segmentation, filtersize)
+        gold = seg2seg.RemoveSmallConnectedComponents(gold, filtersize)
+
+    # convert to c++ arrays
+    cdef np.ndarray[long, ndim=3, mode='c'] cpp_segmentation
+    cpp_segmentation = np.ascontiguousarray(segmentation, dtype=ctypes.c_int64)
+
+    cdef np.ndarray[long, ndim=3, mode='c'] cpp_gold
+    cpp_gold = np.ascontiguousarray(gold, dtype=ctypes.c_int64)
+
+    zres, yres, xres = segmentation.shape
+    CppEvaluate(&(cpp_segmentation[0,0,0]), &(cpp_gold[0,0,0]), [zres, yres, xres], mask_ground_truth)

### 2018-02-20 evaluation/cpp-comparestacks.cpp

@@ -1,0 +1,147 @@
+#include <ctime>
+#include <math.h>
+#include <stdio.h>
+
+
+
+
+// constant variables
+
+static const int IB_Z = 0;
+static const int IB_Y = 1;
+static const int IB_X = 2;
+
+
+
+
+static long NChoose2(long N) 
+{
+    return N * (N - 1) / 2;
+}
+
+
+
+void CppEvaluate(long *segmentation, long *gold, long resolution[3], bool mask_ground_truth)
+{
+    // get convenient variables
+    long zres = resolution[IB_Z];
+    long yres = resolution[IB_Y];
+    long xres = resolution[IB_X];
+    long nentries = zres * yres * xres;
+    long nnonzero = nentries;
+
+    // start stopwatch
+    clock_t t1, t2;
+    t1 = clock();
+
+    // update the number of nonzero if mask is on 
+    for (long iv = 0; iv < nentries; ++iv) {
+        if (!gold[iv]) nnonzero--;
+    }
+
+    // get the maximum value for the segmentation and gold volumes
+    long max_segment = 0;
+    long max_gold = 0;
+    for (long iv = 0; iv < nentries; ++iv) {
+        if (segmentation[iv] > max_segment) max_segment = segmentation[iv] + 1;
+        if (gold[iv] > max_gold) max_gold = gold[iv] + 1;
+    }
+
+    // print lowest value of segment
+    long min_segment = max_segment;
+    for (long iv = 0; iv < nentries; ++iv) {
+        if (segmentation[iv] < min_segment) min_segment = segmentation[iv];
+    }
+
+    // populate values for joint sets
+    long **c = new long *[max_segment];
+    for (long is = 0; is < max_segment; ++is) {
+        c[is] = new long[max_gold];
+        for (long ig = 0; ig < max_gold; ++ig) {
+            c[is][ig] = 0;
+        }
+    }
+    for (long iv = 0; iv < nentries; ++iv) {
+        c[segmentation[iv]][gold[iv]]++;
+    }
+
+    // populate values for s and t sets
+    long *s = new long[max_segment];
+    for (long is = 0; is < max_segment; ++is) {
+        s[is] = 0;
+        for (long ig = mask_ground_truth; ig < max_gold; ++ig) {
+            s[is] += c[is][ig];
+        }
+    }
+    long *t = new long[max_gold];
[…]

### 2018-02-20 papers/eccv2018/paper.tex
updated paper to eccv format

--- 2017-11-28 papers/cvpr2018/paper.tex
@@
-\documentclass[10pt,twocolumn,letterpaper]{article}
+% last updated in April 2002 by Antje Endemann
+% Based on CVPR 07 and LNCS, with modifications by DAF, AZ and elle, 2008 and AA, 2010, and CC, 2011; TT, 2014; AAS, 2016
 
-\usepackage{cvpr}
+\documentclass[runningheads]{llncs}
+\usepackage{graphicx}
+\usepackage{amsmath,amssymb} % define this before the line numbering.
+\usepackage{ruler}
+\usepackage{color}
 \usepackage{subfig}
@@
 \usepackage{float}
+\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}
 
-% Include other packages here, before hyperref.
+\begin{document}
+% \renewcommand\thelinenumber{\color[rgb]{0.2,0.5,0.8}\normalfont\sffamily\scriptsize\arabic{linenumber}\color[rgb]{0,0,0}}
+% \renewcommand\makeLineNumber {\hss\thelinenumber\ \hspace{6mm} \rlap{\hskip\textwidth\ \hspace{6.5mm}\thelinenumber}}
+% \linenumbers
+\pagestyle{headings}
+\mainmatter
+\def\ECCV18SubNumber{***}  % Insert your submission number here
 
-% If you comment hyperref and then uncomment it, you should delete
-% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
-% run, let it finish, and you should be clear).
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
+\titlerunning{ECCV-18 submission ID \ECCV18SubNumber}
 
-% \cvprfinalcopy % *** Uncomment this line for the final submission
+\authorrunning{ECCV-18 submission ID \ECCV18SubNumber}
 
-\def\cvprPaperID{0446} % *** Enter the CVPR Paper ID here
-\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
-%
-\newcommand{\FIX}[1]{\textcolor{red}{#1}}
-\newcommand{\hp}[1]{\textcolor{red}{HP: #1}}
-\newcommand{\donglai}[1]{\textcolor{blue}{[Donglai: #1]}}
+\title{Graph-Based Neural Reconstruction from Skeletonized 3D Networks}
 
-%% Pages are numbered in submission mode, and unnumbered in camera-ready
-\ifcvprfinal\pagestyle{empty}\fi
-\begin{document}
-
-%%%%%%%%% TITLE
-\title{Graph-Based Neural Reconstruction from Skeletonized 3D Networks}
-% Neural Reconstruction Using Skeletonized 3D Networks
-% Neural Reconstruction with Top-Down Enhancements from Skeletonized 3D Networks
-% Graph-Based Neural Reconstruction from Morphological Skeletons
-%Robust Agglomeration using 3D Skeletonization of Labeled for Connectomics}
-
-%\author{Brian Matejek\\
-%Harvard University\\
-%Cambridge, MA 02138, USA\\
-%{\tt\small bmatejek@seas.harvard.edu}
-%% For a paper whose authors are all at the same institution,
-%% omit the following lines up until the closing ``}''.
-%% Additional authors and addresses can be added with ``\and'',
-%% just like the second author.
-%% To save space, use either the email address or home page, not both
-%%\and
-%%Second Author\\
-%%Institution2\\
-%%First line of institution2 address\\
-%%{\tt\small secondauthor@i2.org}
-%}
+\author{Anonymous ECCV submission}
+\institute{Paper ID \ECCV18SubNumber}
 
 \maketitle
-%\thispagestyle{empty}
-%
 
-%%%%%%%%% ABSTRACT
 \begin{abstract}
@@
 We demonstrate the performance of our approach on multiple real-world connectomics datasets with an average split variation of information improvement of 19.3\%.
-%The paper provides insights into learning shape features for top-down graph-based neuron reconstruction.
+\keywords{connectomics, skeletonization, deep learning}
 \end{abstract}
-%%%%%%%%	% BODY TEXT
 
@@
 
-{\small
-\bibliographystyle{ieee}
-\bibliography{paper}}
+\clearpage
+
+\bibliographystyle{splncs}
+\bibliography{egbib}
 

### 2018-03-01 papers/eccv2018/3_evaluation.tex
brief updates about what to add

--- 2017-11-16 papers/cvpr2018/3_evaluation.tex
@@
 The FlyEM dataset comes from the mushroom body of a 5-day old adult male \textit{Drosophila} fly imaged by a focused ion-beam milling scanning electron microscopy~\cite{takemura2017connectome}.
-The mushroom body in this species is the major site of associative learning.
+The mushroom body in this species is the primary site of associative learning.
 The original dataset contains a $\SI[product-units=single]{40 x 50 x 120}{\micro\meter}^3$ volume with a resolution of $\SI[product-units=single]{10 x 10 x 10}{\nano\meter}^3$ per voxel.
@@
 The segmentation of the Kasthuri dataset was computed by agglomerating 3D supervoxels produced by the z-watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}.
-A recent study by Funke et al.~\cite{schlegel2017learning} demonstrated superior performance of such methods over existing ones on anisotropic data.
+A recent study by Funke et al.~\cite{funke2017deep} demonstrated superior performance of such methods over existing ones on anisotropic data.
 We learn 3D affinities using MALIS loss with a U-net~\cite{ronneberger2015u,Turaga:2009}.
@@
 
+\paragraph{Data Augmentation.}
+
 %\subsection{Graph-based Strategies}

### 2018-03-02 cnns/skeleton/generate_features.py
updated training with starting epoch

@@ -10,7 +10,7 @@ from ibex.utilities import dataIO
 from ibex.transforms import seg2seg, seg2gold
 from ibex.cnns.skeleton.util import SkeletonCandidate
 from ibex.data_structures import unionfind
-from ibex.evaluation import comparestacks
+#from ibex.evaluation import comparestacks
 
 
 

### 2018-03-02 cnns/skeleton/train.py

@@ -95,7 +95,7 @@ class PlotLosses(keras.callbacks.Callback):
         plt.plot(self.x, self.val_losses, label="val_loss")
         plt.legend()
         plt.show();
-        plt.savefig('{}-training-curve.png'.format(self.model_prefix))
+        plt.savefig('{}-training-curve-update.png'.format(self.model_prefix))
         plt.gcf().clear()
 
 
@@ -279,7 +279,7 @@ def Train(prefix, model_prefix, threshold, maximum_distance, endpoint_distance, 
 
     history = model.fit_generator(SkeletonCandidateGenerator(prefix, network_distance, positive_candidates[:positive_cutoff], negative_candidates[:negative_cutoff], parameters, width),\
                     (examples_per_epoch / batch_size), epochs=2500, verbose=1, class_weight=weights, callbacks=callbacks,\
-                                  validation_data=SkeletonCandidateGenerator(prefix, network_distance, positive_candidates[positive_cutoff:], negative_candidates[negative_cutoff:], parameters, width), validation_steps=(examples_per_epoch / batch_size))
+                                  validation_data=SkeletonCandidateGenerator(prefix, network_distance, positive_candidates[positive_cutoff:], negative_candidates[negative_cutoff:], parameters, width), validation_steps=(examples_per_epoch / batch_size), initial_epoch=starting_epoch+1)
 
     # save the fully trained model
     model.save_weights('{}.h5'.format(model_prefix))

### 2018-03-02 papers/eccv2018/1_related_work.tex

--- 2017-11-16 papers/cvpr2018/1_related_work.tex
@@
 A large amount of connectomics research considers the problem of extracting segmentation information at the pixel (i.e., voxel) level from the raw EM images.
-Some early techniques apply computationally expensive graph partitioning algorithms with a single node per pixel~\cite{andres2012globally}.
+Some early techniques apply computationally expensive graph partitioning algorithms with a single node per pixel~\cite{andres2012globally} FIX (superpixels not pixels).
 However, these methods do not scale to terabyte datasets.
-More recent methods train classifiers to predict membrane probabilities per image slice either using 2D~\cite{ciresan2012deep,jain2010boundary,kaynig2015large,seymour2016rhoananet,amelio_segmentation} or 3D CNNs~\cite{lee2015recursive,ronneberger2015u,turaga2010convolutional}.
+More recent methods train classifiers to predict membrane probabilities per image slice either using 2D~\cite{ciresan2012deep,jain2010boundary,kaynig2015large,seymour2016rhoananet,amelio_segmentation,ronneberger2015u} or 3D CNNs~\cite{lee2015recursive,cciccek20163d,turaga2010convolutional}.
 
@@
 We use the method of Keuper et al.~\cite{keuper2015efficient} to partition the extracted 3D graph into the final neural reconstruction.
+
+Superhuman \cite{lee2017superhuman}
+Deep structured learning \cite{funke2017deep}
+Multicut brings \cite{beier2017multicut}
+DeepEM3D \cite{zeng2017deepem3d}

### 2018-03-02 cnns/skeleton/generate_features.py
merging conflicts in cnns

@@ -4,6 +4,7 @@ import random
 import struct
 from numba import jit
 import gc
+import time
 
 from ibex.utilities.constants import *
 from ibex.utilities import dataIO
@@ -72,6 +73,8 @@ def FindNeighboringCandidates(segmentation, centroid, candidates, maximum_distan
 
 # generate features for this prefix
 def GenerateFeatures(prefix, threshold, maximum_distance, network_distance, endpoint_distance, topology, training_data):
+    start_time = time.time()
+
     # read in the relevant information
     segmentation = dataIO.ReadSegmentationData(prefix)
     gold = dataIO.ReadGoldData(prefix)
@@ -79,10 +82,10 @@ def GenerateFeatures(prefix, threshold, maximum_distance, network_distance, endp
     zres, yres, xres = segmentation.shape
 
     # get the mapping from segmentation to gold
-    seg2gold_mapping = seg2gold.Mapping(segmentation, gold, low_threshold=0.50, high_threshold=0.80)
-    
+    seg2gold_mapping = seg2gold.Mapping(segmentation, gold, low_threshold=0.10, high_threshold=0.80)
+
     # remove small connceted components
-    segmentation = seg2seg.RemoveSmallConnectedComponents(segmentation, threshold=threshold).astype(np.int64)
+    thresholded_segmentation = seg2seg.RemoveSmallConnectedComponents(segmentation, threshold=threshold).astype(np.int64)
     max_label = np.amax(segmentation) + 1
     
     # get the grid size and the world resolution
@@ -94,41 +97,38 @@ def GenerateFeatures(prefix, threshold, maximum_distance, network_distance, endp
     network_radii = np.int64((network_distance / world_res[IB_Z], network_distance / world_res[IB_Y], network_distance / world_res[IB_X]))
     
     # get all of the skeletons
-    if topology: skeletons, endpoints = dataIO.ReadTopologySkeletons(prefix, segmentation)
-    else: skeletons, _, endpoints = dataIO.ReadSWCSkeletons(prefix, segmentation)
+    if topology: skeletons, endpoints = dataIO.ReadTopologySkeletons(prefix, thresholded_segmentation)
+    else: skeletons, _, endpoints = dataIO.ReadSWCSkeletons(prefix, thresholded_segmentation)
+
+    # get the set of all considered pairs
+    endpoint_candidates = [set() for _ in range(len(endpoints))]
+    for ie, endpoint in enumerate(endpoints):
[…]

### 2018-03-02 cnns/skeleton/train.py

@@ -238,7 +238,7 @@ def Train(prefix, model_prefix, threshold, maximum_distance, endpoint_distance, 
 
     # if the file exists do not continue
     if os.path.isfile(logfile) and starting_epoch == 1:
-        sys.stderr.write('Discovered {}, exiting'.format(logfile))
+        sys.stderr.write('Discovered {}, exiting\n'.format(logfile))
         sys.exit()
 
     # write out the network parameters to a file
@@ -276,10 +276,14 @@ def Train(prefix, model_prefix, threshold, maximum_distance, endpoint_distance, 
     
     if not starting_epoch == 1:
         model.load_weights('{}-{:03d}.h5'.format(model_prefix, starting_epoch))
+    # start with a better baseline (pre-trained LCylinder)
+    if 'CREMI' in model_prefix:
+        LCylinder_model_prefix = model_prefix.replace('-CREMI', '')
+        model.load_weights('{}-best-acc.h5'.format(LCylinder_model_prefix))
 
     history = model.fit_generator(SkeletonCandidateGenerator(prefix, network_distance, positive_candidates[:positive_cutoff], negative_candidates[:negative_cutoff], parameters, width),\
                     (examples_per_epoch / batch_size), epochs=2500, verbose=1, class_weight=weights, callbacks=callbacks,\
-                                  validation_data=SkeletonCandidateGenerator(prefix, network_distance, positive_candidates[positive_cutoff:], negative_candidates[negative_cutoff:], parameters, width), validation_steps=(examples_per_epoch / batch_size))
+                                  validation_data=SkeletonCandidateGenerator(prefix, network_distance, positive_candidates[positive_cutoff:], negative_candidates[negative_cutoff:], parameters, width), validation_steps=500 / batch_size)
 
     # save the fully trained model
     model.save_weights('{}.h5'.format(model_prefix))

### 2018-03-02 cnns/skeleton/generate_features.py
cnns/skeleton: removed difference between generating training and inference features

@@ -71,7 +71,7 @@ def FindNeighboringCandidates(segmentation, centroid, candidates, maximum_distan
 
 
 # generate features for this prefix
-def GenerateFeatures(prefix, threshold, maximum_distance, network_distance, endpoint_distance, topology, training_data):
+def GenerateFeatures(prefix, threshold, maximum_distance, network_distance, endpoint_distance, topology):
     start_time = time.time()
 
     # read in the relevant information

### 2018-03-02 cnns/skeleton/train.py
added support for loading pretrained model weights

@@ -209,7 +209,7 @@ def SkeletonCandidateGenerator(prefix, network_distance, positive_candidates, ne
 
 
 
-def Train(prefix, model_prefix, threshold, maximum_distance, endpoint_distance, network_distance, width, parameters):
+def Train(prefix, model_prefix, threshold, maximum_distance, endpoint_distance, network_distance, width, parameters, pretrained_model=''):
     # identify convenient variables
     nchannels = width[0]
     starting_epoch = parameters['starting_epoch']
@@ -277,9 +277,8 @@ def Train(prefix, model_prefix, threshold, maximum_distance, endpoint_distance, 
     if not starting_epoch == 1:
         model.load_weights('{}-{:03d}.h5'.format(model_prefix, starting_epoch))
     # start with a better baseline (pre-trained LCylinder)
-    if 'CREMI' in model_prefix:
-        LCylinder_model_prefix = model_prefix.replace('-CREMI', '')
-        model.load_weights('{}-best-acc.h5'.format(LCylinder_model_prefix))
+    if len(pretrained_model):
+        model.load_weights('{}-best-loss.h5'.format(pretrained_model))
 
     history = model.fit_generator(SkeletonCandidateGenerator(prefix, network_distance, positive_candidates[:positive_cutoff], negative_candidates[:negative_cutoff], parameters, width),\
                     (examples_per_epoch / batch_size), epochs=2500, verbose=1, class_weight=weights, callbacks=callbacks,\

### 2018-03-02 papers/eccv2018/2_method.tex
paper: added information on augmentations/lifted multicut

--- 2017-11-28 papers/cvpr2018/2_method.tex
@@
 	\centering
-	\includegraphics[width=0.82\linewidth]{./figures/skeleton1.png}
-	\includegraphics[width=0.82\linewidth]{./figures/skeleton2.png}
-	\includegraphics[width=0.82\linewidth]{./figures/skeleton3.png}
+	\includegraphics[width=0.32\linewidth]{./figures/skeleton1.png}
+	\includegraphics[width=0.32\linewidth]{./figures/skeleton2.png}
+	\includegraphics[width=0.32\linewidth]{./figures/skeleton3.png}
 	\caption{Example skeletons (in black) extracted from segments using the TEASER algorithm.}
@@
 	\centering
-	\includegraphics[width=0.92\linewidth]{./figures/split_error1.png}
-	\includegraphics[width=0.92\linewidth]{./figures/split_error2.png}		\includegraphics[width=0.85\linewidth]{./figures/merge_candidate2.png}
+	\includegraphics[width=0.32\linewidth]{./figures/split_error1.png}
+	\includegraphics[width=0.32\linewidth]{./figures/split_error2.png}		\includegraphics[width=0.32\linewidth]{./figures/merge_candidate2.png}
 	\caption{Three erroneously split segments.}
@@
 Using top-down graph partitioning allows us to apply biological constraints on the output. 
-Neuroscientists know that neuronal connectivity graphs in the brain are acyclic (i.e., the graphs have a genus of zero).
-We enforce this constraint by finding a multicut partition of the graph that generates a \textit{forest} of nodes, i.e., a set of trees where no segment has a cycle.
-To solve this constraing multicut problem we use the method by Keuper et al.~\cite{keuper2015efficient} that produces a feasible solution by greedy additive edge contraction.
+Formulating the problem as a multicut minimization problem allows us to guarantee \TODO{FIX} globally consistent solutions where every cycle of ``merge" edges is closed \TODO{CONFUSING}.
+To solve this constraining multicut problem we use the method by Keuper et al.~\cite{keuper2015efficient} that produces a feasible solution by greedy additive edge contraction.
+We extend the multicut formulation the ``lifted" version of the problem where non-adjacent nodes have edge weights corresponding to the probability of belonging to the same neuron \TODO{(CITE)}.
+We determine the lifted edge weights following the example of Keuper et al. \cite{keuper2015efficient}.
+\TODO{find better source and describe the process}

### 2018-03-02 papers/eccv2018/3_evaluation.tex
paper: added information on augmentations/lifted multicut

@@
 
-We use the left cylinder of the Kasthuri dataset for training and validation. We train on 80\% of the potential merge candidates for this volume.
+We use half of the Kasthuri dataset for training and validation. 
+We train on 80\% of the potential merge candidates for this volume.
 We validate the CNN classifier on the remaining 20\% of candidates.
-We apply data augmentation to the generated examples to increase the size of the training datasets.
-We consider all rotations of $90$ degrees along the $xy$-plane in addition to mirroring along the $x$ and $z$ axes.
-This produces 16 times more training data.
 
@@
 All the parameters are randomly initialized following the Xavier uniform distribution~\cite{glorot2010understanding}. 
-Training concluded after 34 epochs.
+Training concluded after \TODO{YYY} epochs.
 
@@
 
-\paragraph{Data Augmentation.}
+\paragraph{Training Augmentation.}
+
+Since our input is an existing segmentation of the EM images, there are very few training examples compared to per-pixel classifiers that a unique window for each voxel. 
+The Kasthuri dataset represents a region of brain over $\SI[product-units=single]{800}{\micro\meter}^3$ in volume and only yields \TODO{700} positive and \TODO{7000} negative examples.
+To avoid overfitting our deep networks, we apply the following augmentations on the example.
+During a single batch, we randomly select ten positive examples and ten negative examples. 
+With probability 0.5, the example is flipped across the $xy$-plane. 
+We then rotate the example by a random angle between $0$ and $360$ degrees using nearest neighbor interpolation. 
+The supplemental material contains experiments demonstrating that benefits of this augmentation strategy.
+We have 20,000 such examples per epoch.
 

### 2018-03-02 papers/eccv2018/4_results.tex
updated paper to eccv format
paper: added information on augmentations/lifted multicut

--- 2017-11-16 papers/cvpr2018/4_results.tex
@@
 
-Fig.~\ref{fig:positive-results} shows successful merges on the Kasthuri Vol. 2 dataset. Several of these examples combine multiple consecutive segments that span the volume.
+Fig.~\ref{fig:qualitative-results} shows successful merges on the Kasthuri Vol. 2 dataset. Several of these examples combine multiple consecutive segments that span the volume.
 In the third example we correct the over-segmentation of a dendrite and attached spine-necks.
-Fig.~\ref{fig:negative-results} shows typical failure cases of our method (red circles).
+Fig.~\ref{fig:qualitative-results} shows typical failure cases of our method (red circles).
 In two of these examples the algorithm correctly predicted several merges before a single error rendered the segment as wrong.
@@
 \begin{figure}[t]
+	\begin{minipage}{0.45\linewidth}
 		\centering
@@
 		\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-correct5.png}
-	\caption{Segments of neurons that were correctly merged by our method.}
-	\label{fig:positive-results}
-\end{figure}
-
-\begin{figure}[t]
+	\end{minipage}
+	\begin{minipage}{0.45\linewidth}
 		\centering
@@
 		\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-incorrect4.png}
-	\caption{Circles indicate areas of wrong merges by our method (red) or by the initial pixel-based segmentation (blue).}
-	\label{fig:negative-results}
+	\end{minipage}
+	\caption{(left) Segments of neurons that were correctly merged by our method. (right) Circles indicate areas of wrong merges by our method (red) or by the initial pixel-based segmentation (blue).}
+	\label{fig:qualitative-results}
 \end{figure}
@@
 
+\paragraph{Inference Augmentation.}
+
+When computing the probability to merge two segments, we input the initial segment into our CNN as well as \TODO{XX} randomly rotated and flipped examples (in the same manner as training augmentation).
+This produces some additional increase in overall accuracy (Table ~\ref{table:inference-augmentation}). 
+The supplemental material contains experiments showing the trade-offs between increased accuracy and runtime when using these augmentation strategies.
+
+\TODO{Add table for augmentation}
+
 Fig.~\ref{fig:receiver-operating-characteristic} shows the receiver operating characteristic (ROC) curve of our CNN classifier for all test datasets.
@@
 	\centering
+	\small
 	\begin{tabular}{c c c c} \hline
@@
 \end{table}
+
+\TODO{How does using lifted-multicut improve the results!}

### 2018-03-05 papers/eccv2018/0_introduction.tex
paper: major changes to abstract, intro, and related works

--- 2017-11-16 papers/cvpr2018/0_introduction.tex
@@
 	\caption{Example improvement of neural reconstruction.
-(a) We extract 3D skeletons from pixel-based segmentation algorithms to create a 3D graph representation.
-Edges with high segmentation error probabilities are indicated by the red arrows.
+(a) We extract 3D skeletons from pixel-based segmentation algorithms to create a graph representation.
+Red arrows highlight errors in the input segmentation.
 (b) We improve the segmentation accuracy using a graph partitioning algorithm, leveraging both local and global information.}
@@
 
-%\donglai{usually, top-down means split.. but we are also bottom-up, but with different representation}
 The field of connectomics is concerned with reconstructing the wiring diagram of the brain at nanometer resolutions to enable new insights into the workings of the brain~\cite{haehn2017scalable,kasthuri2015saturated}.
-Recent advancements in image acquisition using multi-beam serial-section electron microscopy (sSEM) have allowed researchers to produce terabytes of image data every hour~\cite{hildebrand2017whole}.
-It is not feasible for domain experts to manually reconstruct this vast amount of image data~\cite{haehn2014design}.
+Recent advancements in image acquisition using multi-beam serial-section electron microscopy (sSEM) allow researchers to produce terabytes of image data per hour~\cite{hildebrand2017whole}. 
+It is infeasible for domain experts to manually reconstruct this vast amount of image data~\cite{haehn2014design}. 
 State-of-the-art automatic reconstruction approaches use pixel-based segmentation with convolutional neural networks (CNNs) followed by agglomeration strategies~\cite{seymour2016rhoananet,lee2015recursive,nunez2014graph,parag2017anisotropic,ronneberger2015u,zlateski2015image}.
@@
 
-%\begin{figure*}[t]
-%	\centering
-%	\subfloat[]{
-%	\includegraphics[width=.24\linewidth]{./figures/pipeline/image.png}
-%	}
-%	\subfloat[]{
-%	\includegraphics[width=.24\linewidth]{./figures/pipeline/affinities.png}
-%	}
-%	\subfloat[]{
-%	\includegraphics[width=.24\linewidth]{./figures/pipeline/watershed.png}
-%	}
-%	\subfloat[]{
-%	\includegraphics[width=.24\linewidth]{./figures/pipeline/neuroproof.png}
-%	}
-%	\caption{An overview of a pixel-based connectomics segmentation pipeline.
-(a) Original EM image data (b) Output of a CNN predicting voxel affinities (c) Clustering of the affinities using a watershed algorithm (d) Agglomeration of the super-voxels into larger segments.}
-%	\label{fig:pipeline}
-%\end{figure*}
-
-%
-%\begin{figure*}[t!]
-%	\centering
-%	(a) \includegraphics[width=0.18\linewidth]{./figures/pipeline/image.png}
-%	\hspace{0.025\linewidth}
-%	(b) \includegraphics[width=0.18\linewidth]{./figures/pipeline/affinities.png}
-%	\hspace{0.025\linewidth}
-%	(c) \includegraphics[width=0.18\linewidth]{./figures/pipeline/watershed.png}
-%	\hspace{0.025\linewidth}
-%	(d) \includegraphics[width=0.18\linewidth]{./figures/pipeline/neuroproof.png}
-%	\caption{An overview of a pixel-based connectomics segmentation pipeline.
-(a) Original EM image data (b) Output of a CNN predicting voxel affinities (c) Clustering of the affinities using a watershed algorithm (d) Agglomeration of the super-voxels into larger segments.}
-%	\label{fig:pipeline}
-%\end{figure*}
-%
-%Researchers address the failures of these pixel-based algorithms by training random-forest classifiers to agglomerate an oversegmentation of voxels~\cite{nunez2014graph,10.1371/journal.pone.0125825}.
-%These classifiers take the output of the pixel-based algorithms as input and generate high-level statistics such as affinity distributions between regions.
-%Presently, these methods use hand-designed features despite the evidence that machine-learned features perform better~\cite{bogovic2013learned}.
-%These \textit{region-based} algorithms outperform the pixel-based algorithms but do not provide the accuracy needed for large scale reconstructions of the brain.
-
-%Here we introduce a scalable, top-down segmentation algorithm that also leverages local information.
-%Partitioning globally allows us to apply domain-specific constraints to the segmentation task.
-%We extract a graph representation from the input segmentation.
-%By simplifying the 3-D segments by their skeletons, we can quickly generate the graph nodes and edges.
-
-We present a \textit{top-down graph-based} method that builds on the outputs of bottom-up pixel-based segmentation approaches.
-We first extract 3D skeleton networks from the input segmentation and generate a simplified 3D graph (Fig.~\ref{fig:teaser}a).
-We train a CNN classifier on the agglomerated regions in the segmentation data to detect errors.
-We run the classifier to populate the graph edge weights with error probabilities.
-We then use a graph optimization algorithm to partition the graph into the final improved reconstruction by enforcing domain-specific global constraints from biology (Fig.~\ref{fig:teaser}b).
+We present a \textit{global\TODO{?} graph-based} method that builds on the outputs of bottom-up pixel-based segmentation approaches. 
+We first extract skeletons from labels in the input segmentation and generate a simplified graph (Fig.~\ref{fig:teaser}a). 
+Next, a trained CNN classifier detects split errors in the segmentation data. 
+Split errors correspond to neurons which are incorrectly segmented with multiple labels. 
+This classifier produces probabilities that two segments belong to the same neuron.
+These probabilities correspond to edge weights in our graph extracted from the input segmentation.
+We then use a graph optimization algorithm to partition the graph into a final improved reconstruction by enforcing domain-specific global constraints from biology (Fig.~\ref{fig:teaser}b).
 
@@
 Our method is independent of image resolution and acquisition parameters, enabling its application to isotropic and anisotropic image data without retraining.
-Using the 3D graph induced by the segmentation allows us to enforce global biological constraints on the reconstruction.
+Images generated by electron microscopes often differ in appearance because of variations in staining techniques \cite{briggman2012volume}.
+By removing the dependence of our algorithm on the input images, we greatly reduce the need for additional costly ground truth data for each new stack of images.
+Using the graph induced by the segmentation allows us to enforce global biological constraints on the reconstruction. 
 Our dual approach of assessing local decisions in a global context yields accuracy improvements over existing reconstruction methods.
 
-This work makes the following contributions: (1) a novel top-down method using  graphs from skeletonized 3D networks for improved neural reconstruction of connectomics data; (2) a region-based CNN classifier to detect errors using the 3D graph as global constraint; (3) an empirical evaluation of our method on several connectomics datasets; (4) our method yields improved performance over a state-of-the-art pixel-based reconstruction approach on average by 19.3\% without drastically increasing the running time.
+This work makes the following contributions: (1) a novel top-down\TODO{?} framework that extracts graphs from skeletonized 3D networks for improved neural reconstruction of connectomics data; (2) a region-based CNN classifier to detect errors; (3) an empirical evaluation of our method on several connectomics datasets; (4) improved performance over a state-of-the-art pixel-based reconstruction approach on average by \TODO{XX}\% with suitable running times.

### 2018-03-05 papers/eccv2018/1_related_work.tex
paper: major changes to abstract, intro, and related works

--- 2017-11-16 papers/cvpr2018/1_related_work.tex
@@
 
-We review some of the most successful segmentation methods that have been applied to large-scale EM images in connectomics.
-%Fig.~\ref{fig:pipeline} shows the results of a typical connectomics segmentation pipeline.
-
 \paragraph{Pixel-based methods.}
-A large amount of connectomics research considers the problem of extracting segmentation information at the pixel (i.e., voxel) level from the raw EM images.
-Some early techniques apply computationally expensive graph partitioning algorithms with a single node per pixel~\cite{andres2012globally}.
-However, these methods do not scale to terabyte datasets.
-More recent methods train classifiers to predict membrane probabilities per image slice either using 2D~\cite{ciresan2012deep,jain2010boundary,kaynig2015large,seymour2016rhoananet,amelio_segmentation} or 3D CNNs~\cite{lee2015recursive,ronneberger2015u,turaga2010convolutional}.
-
-Oftentimes these networks produce probabilities for the affinity between two voxels (i.e., the probability that adjacent voxels belong to the same neuron).
+A significant amount of connectomics research considers the problem of extracting segmentation information at the pixel (i.e., voxel) level from the raw EM images. 
+Some methods use a random forest populated with hand-designed features based on image characteristics around a given pixel to predict membrane probabilities~\cite{kaynig2015large}.
+Most recent advancements use convolutional neural networks since machine-learned features outperform hand-designed ones~\cite{bogovic2013learned}.
+Originally, networks predicted membrane probabilities per each image slice using 2D convolutions~\cite{seymour2016rhoananet,ronneberger2015u,ciresan2012deep,jain2010boundary,kaynig2015large,amelio_segmentation}.
+However, recent research extends these convolutions to include the z-dimension improving performance~\cite{lee2015recursive,parag2017anisotropic,cciccek20163d,turaga2010convolutional}.
+Many of these networks produce probabilities for the affinity between two voxels (i.e., the probability that adjacent voxels belong to the same neuron). 
 The MALIS cost function is specifically designed for generating affinities that produce good segmentations~\cite{briggman2009maximin}. 
@@
 These networks produce impressive accuracies but at a high computational cost.
+Data augmentation in both training and testing can increase the prediction accuracy in boundary detection~\cite{zeng2017deepem3d}.
+Lee et al. surpass the estimated human accuracy on the SNEMI3D dataset with a variant of the 3D U-Net architecture~\cite{lee2017superhuman}.
 
 \paragraph{Region-based methods.}
-%Lately, many recent advancements in segmentation use artificial neural networks since machine-learned features outperform hand-designed ones~\cite{bogovic2013learned}.
-%A significant amount of research focuses on the training and optimization of these deep neural networks~\cite{chatfield2014return,maas2013rectifier,nesterov1983method}.
+
+Some early techniques apply computationally expensive graph partitioning algorithms with a single node per superpixel~\cite{andres2012globally}. 
 Several pixel-based approaches generate probabilities that neighboring pixels belong to the same neuron.
 Often a watershed algorithm will then cluster pixels into super-pixels~\cite{zlateski2015image}.
-Many methods build on top of these region-based strategies and train random-forest classifiers to produce the final segmentations~\cite{seymour2016rhoananet,nunez2014graph,10.1371/journal.pone.0125825,parag2017anisotropic,zlateski2015image}.
+Many methods build on top of these region-based strategies and train random-forest classifiers to produce the final segmentations~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image,10.1371/journal.pone.0125825}.
+Some methods rely solely on the accuracy of the predicted affinities and agglomerate hierarchically based on the mean affinity between supervoxels~\cite{lee2017superhuman,funke2017deep}.
+Pape et al. present a scalable multicut algorithm to partition superpixels~\cite{beier2017multicut}.
 
 \paragraph{Error-correction methods.}
-Some recent research builds on top of these region-based methods to correct errors in the segmentation either using human proofreading~\cite{haehn2017guided,haehn2014design,mojo2} or fully automatically~\cite{rolnick2017morphological,error_correction_using_CNN}.
-However, to our knowledge, our method is the first to extract a 3D graph from pixel-based segmentations for a true top-down error correction approach.
+Additional research builds on top of these region-based methods to correct errors in the segmentation either using human proofreading~\cite{haehn2014design,haehn2017guided,mojo2} or automatic methods~\cite{rolnick2017morphological,error_correction_using_CNN}.
+However, to our knowledge, our method is the first to extract a 3D graph from an input segmentation for a true top-down\TODO{?} error correction approach. 
 This allows us to enforce domain-specific biology constraints and use efficient graph partitioning algorithms. 
@@
 Even though graph partitioning is an NP-Hard problem~\cite{demaine2006correlation} there are several useful multicut heuristics that provide good approximations with reasonable computational costs~\cite{horvnakova2017analysis}.
-We use the method of Keuper et al.~\cite{keuper2015efficient} to partition the extracted 3D graph into the final neural reconstruction.
+We use the method of Keuper et al.~\cite{keuper2015efficient} to partition the extracted graph into the final neural reconstruction.

### 2018-03-05 papers/eccv2018/2_method.tex
paper: major changes to abstract, intro, and related works

@@
 	\begin{center}
-		\includegraphics[width=0.24\linewidth]{./figures/methods/multicut_input.png}
-		\includegraphics[width=0.24\linewidth]{./figures/methods/pre-multicut.png}
-		\includegraphics[width=0.24\linewidth]{./figures/methods/multicut-graph.png}
-		\includegraphics[width=0.24\linewidth]{./figures/methods/post-multicut.png}
+		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/multicut_input.png}}
+		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/pre-multicut.png}}
+		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/multicut-graph.png}}
+		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/post-multicut.png}}
 	\end{center}
-	\caption{Outline of our approach, from left to right: result of the pixel-based segmentation and agglomeration algorithm; segments of several selected neurons from the initial segmentation; extracted skeletonized 3D network of those segments; improved 3D reconstruction of the selected segments after graph construction and partitioning with constraints.}
+	\caption{Outline of our approach, from left to right: result of the pixel-based segmentation and agglomeration algorithm; segments of several neurons from the initial segmentation; extracted skeletonized network of those segments; improved 3D reconstruction of the selected segments after graph construction and partitioning with constraints.}
 	\label{fig:overview}

### 2018-03-05 papers/eccv2018/paper.tex
paper: added information on augmentations/lifted multicut
paper: major changes to abstract, intro, and related works

@@
 \mainmatter
-\def\ECCV18SubNumber{***}  % Insert your submission number here
+\def\ECCV18SubNumber{534}  % Insert your submission number here
 
@@
 \authorrunning{ECCV-18 submission ID \ECCV18SubNumber}
-
 \title{Graph-Based Neural Reconstruction from Skeletonized 3D Networks}
@@
 
+\newcommand\TODO[1]{\textcolor{red}{#1}}
+
 \maketitle
@@
 \begin{abstract}
-Advancements in electron microscopy image acquisition have created massive connectomics datasets in the terabyte range that make manual reconstruction of neuronal structures infeasible.
-Current state-of-the-art automatic methods segment neural membranes at the pixel level followed by agglomeration methods to create full neuron reconstructions.
+Advancements in electron microscopy image acquisition have created connectomics datasets terabytes in size making manual reconstruction of neuronal structures infeasible.
+Current state-of-the-art automatic methods classify neural membranes at the pixel level followed by agglomeration methods to create full neuron reconstructions.
 However, these approaches widely neglect global geometric properties that are inherent in the graph structure of neural wiring diagrams.
-In this work, we follow bottom-up pixel-based reconstruction by a top-down graph-based method to more accurately approximate neural pathways.
+In this work, we follow pixel-based reconstruction by a global graph-based method to more accurately approximate neural pathways.
 We first generate skeletons in 3D from the neuron labels of the pixel-based segmentation.
-We then simplify this skeletonized 3D network into a 3D graph with nodes corresponding to labels from the segmentation and edges identifying potential locations of segmentation errors.
-We use a CNN classifier trained on ground truth data to generate edge weights on the 3D graph corresponding to error probabilities.
-We then apply a multicut algorithm to generate a partition on the graph that improves the final segmentation.
-Because the 3D graph is small and encodes top-down information our method is efficient and globally improves the neural reconstruction.
-We demonstrate the performance of our approach on multiple real-world connectomics datasets with an average split variation of information improvement of 19.3\%.
+Next, we simplify this skeletonized 3D network into a graph with nodes corresponding to labels from the segmentation and edges identifying potential locations of split errors.
+A CNN classifier produces edge weights for the graph corresponding to the probability of error. 
+We formulate the graph into a multicut partitioning problem to improve the final segmentation.
+Since the 3D graph is small and encodes top-down information our method is efficient and globally improves the neural reconstruction.
+We demonstrate the performance of our approach on multiple real-world connectomics datasets with an average split variation of information improvement of \TODO{XX}\%.
 \keywords{connectomics, skeletonization, deep learning}

### 2018-03-05 papers/eccv2018/2_method.tex
methods: major updates to skeletonization and neural networks

@@
 
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.32\linewidth]{./figures/skeleton1.png}
-	\includegraphics[width=0.32\linewidth]{./figures/skeleton2.png}
-	\includegraphics[width=0.32\linewidth]{./figures/skeleton3.png}
-	\caption{Example skeletons (in black) extracted from segments using the TEASER algorithm.}
-	\label{fig:skeletonization}
-\end{figure}
-
-There are two types of errors that can occur in connectomics segmentation.
-The first, called a split error, occurs when there are two segments that should have been merged.
-The second, called a merge error, happens when one segment should be split into two.
+There are two types of errors that can occur in connectomics segmentations: \textit{split errors} and \textit{merge errors}. 
+In a split error, two segments should have been merged into one neuronal process. 
+In a merge error, one segment corresponds to more than one neuron.
 Generally, it is much more difficult to correct merge errors than to correct split errors,
@@
 Thus, most reconstruction approaches are tuned towards over-segmentation with many more split than merge errors. 
-Our method takes as input over-segmentations of EM image volumes generated by state-of-the-art connectomics reconstruction pipelines (Sec.~\ref{sec:neuroproof}).
+Our method takes as input over-segmentations of EM image volumes generated by scalable, state-of-the-art connectomics reconstruction pipelines (Sec.~\ref{sec:neuroproof}). 
 Our goal is to identify locations of split errors and merge the corresponding segments automatically.
@@
 From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with weights $w_e$. 
-The nodes correspond to label segments from the segmentation with edges between segments considered for merging.
+The nodes correspond to labeled segments from the segmentation.
+There are edges between all nodes that we consider as merge candidates.
 Ideally, our graph has edges corresponding to all of the segments that were erroneously split. 
@@
 We then use a multicut algorithm to generate a partition on the graph where nodes in the same partition are assigned the same output label in the improved segmentation. 
-We will now discuss the three major components to our framework (graph creation, edge weights assignment, and graph partitioning) in more detail.
-
-%\subsection{Graph Creation}
-
-%We generate nodes $N$ and edges $E$ to apply a graph-based optimization strategy for segmentation.
-%In addition, these edges receive non-negative weights.
+We will now discuss the three major components to our framework (graph creation, edge weight assignment, and graph partitioning) in more detail.
 
@@
 It is difficult to extract useful shape features from these segments because of their small, often random, shape. 
-We prune these nodes from the graph by removing all segments with fewer than a threshold $t_{seg} = 20,000$ voxels.
-This removed on average 56\% of the segments in our  datasets (Sec.~\ref{sec:dataset}).
-Despite the large number of segments, these regions only take up 1.6\% of the total volume on average.
+We prune these nodes from the graph by removing all segments with fewer than a threshold $t_{seg} = 20,000$ voxels (\TODO{~XX\SI{}{\nano\meter^3}}). 
+This removed on average \TODO{XX}\% of the segments in our  datasets (Sec.~\ref{sec:dataset}).
+Despite the large number of segments, these regions only take up \TODO{XX}\% of the total volume on average.
 
 \subsection{Edge Generation}
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=0.32\linewidth]{./figures/skeleton1.png}
+	\includegraphics[width=0.32\linewidth]{./figures/skeleton2.png}
+	\includegraphics[width=0.32\linewidth]{./figures/skeleton3.png}
+	\caption{Example skeletons (in black) extracted from segments using a variant of the TEASER algorithm.}
+	\label{fig:skeletonization}
+\end{figure}
 
@@
 
-First, we extract a skeleton from each segment in the label volume using the TEASER algorithm~\cite{sato2000teasar,zhao2014automatic}.
-Fig.~\ref{fig:skeletonization} shows an example of three extracted skeletons (in black).
+First, we extract a skeleton from each segment in the label volume using a variant~\cite{zhao2014automatic} of the TEASER algorithm~\cite{sato2000teasar}. 
+This skeletonization algorithm repeatedly uses Dijkstra's algorithm to find the farthest voxel from a seed location. 
+Since this algorithm is non-linear in the number of voxels, we downsample the datasets so that there are voxel samples every $\SI{30}{\nano\meter}$ in each dimension.
+Empirically, this reduced the running time for skeletonization by $\TODO{XX\%}$, with minimal reduction in skeleton accuracy ($\TODO{XX\%}$ fewer branches). 
+Fig.~\ref{fig:skeletonization} shows three examples of extracted skeletons (in black). 
 These skeletons consist of a sequence of \textit{joints}, i.e., locations that are locally a maximum distance from the segment boundary, with line segments connecting successive joints. 
-We prune the joints that are within $t_{jnt} = 50$ voxels of each other to reduce unnecessary branching.
+We prune the joints that are within $t_{jnt} = \TODO{XX}\SI{}{\nano\meter}$ of each other to reduce unnecessary branching. 
 We refer to joints that have only one connected neighbor as \textit{endpoints}. 
@@
 If a segment $S^\prime \in \mathbb{S}_e^\prime$ has an endpoint within $t_{high}$ voxels of $e$, the segment $S$ and $S^\prime$ are considered for merging. 
-We store the midpoints between the two endpoints as the center of the potential merges in the set $\mathbb{S}_c$.
-This algorithm produces a set of segments to consider for merging.
-Only these pairs have a corresponding edge in the constructed graph.
+We store the midpoints between the two endpoints as the center of the potential merge in the set $\mathbb{S}_c$. 
+This algorithm produces a set of segments to consider for merging. Only these pairs have a corresponding edge in the constructed graph.
+
+\subsection{Edge Weights Assignment}
+We assign edge weights $w_e$ to each edge where the weight corresponds to the probability that two nodes belong to the same neuron.
+We train a 3D CNN classifier to learn from the manually labeled oversegmentation input volume (Sec.~\ref{sec:dataset}).
+If the probability that the nodes belong to the same neuron is $p_e$, the edge weight $w_e = \log{\frac{p_e}{1 - p_e}} + \log{\frac{1 - \beta}{\beta}}$, where $\beta$ is a tunable parameter that encourages over- or under-segmentation.
+
+\subsubsection{Classifier Input}
+
+We extract a cubic region of interest (ROI) around each endpoint $e$ in $\mathbb{S}_c$ as input to the CNN. 
+The CNN receives three input channels for every voxel in the ROI around segments $l_1$ and $l_2$. 
+The input in all of the channels is in the range $\{-0.5, 0.5\}$. 
+The first channel is $0.5$ only if the corresponding voxel has label $l_1$. 
+The second channel is $0.5$ only if the corresponding voxel has label $l_2$. 
+The third channel is $0.5$ if the corresponding voxel is either $l_1$ or $l_2$.
+We do not use the raw EM image information to avoid the need to retrain the network on datasets that have been stained differently or imaged at different resolution. 
+This significantly reduces the need for generating costly manually-labeled ground truth.
 
@@
 
-\subsection{Edge Weights Assignment}
-We assign edge weights $w_e$ to each edge where the weight corresponds to the probability that two nodes belong to the same neuron.
-Instead of using handcrafted features to compute the similarity between adjacent nodes, we train a 3D CNN classifier to learn from the manually labeled oversegmentation input volume (Sec.~\ref{sec:dataset}).
-If the probability that the nodes belong to the same neuron is $p_e$, the edge weight $w_e = \log{\frac{p_e}{1 - p_e}} + \log{\frac{1 - \beta}{\beta}}$, where $\beta$ is a tunable parameter that encourages over- or under-segmentation.
-%Our  edge weights  correspond to probabilities that two endpoints $e$ in $\mathbb{S}_c$ belong to the same neuron and should be merged. \hp{check}
-
-\subsubsection{Classifier Input}
-
-We extract a cubic region of interest (ROI) around each endpoint $e$ in $\mathbb{S}_c$ as input to the CNN.
-The CNN receives three input channels for every voxel in the ROI around segments $l_1$ and $l_2$.
-The input in all of the channels is in the range $\{-0.5, 0.5\}$.
-The first channel is $0.5$ only if the corresponding voxel has label $l_1$.
-The second channel is $0.5$ only if the corresponding voxel has label $l_2$.
-The third channel is $0.5$ if the corresponding voxel is either $l_1$ or $l_2$.
-
 \subsubsection{Network Architecture \& Training}
 
-%Fig.~\ref{fig:architecture} provides an overview of our CNN architecture.
-We use the CNN architecture by Chatfield et al.~\cite{chatfield2014return}.
-It consists of three layers of double convolutions followed by a max pooling step.
+We use \textit{VGG-style} blocks as presented by Chatfield et al.~\cite{chatfield2014return}. 
+Each blocks consists of two double convolutions with filter size $3\times3\times3$ followed by a max pooling step. 
+There are three layers of these blocks. 
 The first two max pooling layers are anisotropic with pooling only in the $x$ and $y$ dimensions. 
@@
 
-%\begin{figure*}[t]
-%	\centering
-%	\includegraphics[width=0.85\linewidth]{figures/architecture.png}
-%	\caption{The architecture for our classification CNN uses double convolutions followed by max pooling.
-The number of filters doubles each layer, with a final fully connected layer and sigmoid activation function.}
-%	\label{fig:architecture}
-%\end{figure*}
-
 \subsection{Graph Partitioning}
 
-After constructing the 3D graph we apply graph partitioning using multicut to compute the final segmentation. 
-Using top-down graph partitioning allows us to apply biological constraints on the output. 
-Formulating the problem as a multicut minimization problem allows us to guarantee \TODO{FIX} globally consistent solutions where every cycle of ``merge" edges is closed \TODO{CONFUSING}.
+After constructing the 3D graph we apply graph partitioning with a multicut formulation to compute the final segmentation. 
+Using this global graph partitioning allows us to apply biological constraints on the output. 
+The multicut minimization problem allows us to guarantee globally consistent solutions where every cycle is ``closed'' under merging.
 To solve this constraining multicut problem we use the method by Keuper et al.~\cite{keuper2015efficient} that produces a feasible solution by greedy additive edge contraction.
-We extend the multicut formulation the ``lifted" version of the problem where non-adjacent nodes have edge weights corresponding to the probability of belonging to the same neuron \TODO{(CITE)}.
-We determine the lifted edge weights following the example of Keuper et al. \cite{keuper2015efficient}.
-\TODO{find better source and describe the process}
+We extend the multicut formulation to the ``lifted'' version of the problem where non-adjacent nodes have ``lifted'' edges.
+These edges penalize or reward distance nodes for belonging to the same segment and produce benefits over traditional multicut. 
+We determine the lifted edge weights following the example of Beier et al~\cite{beier2017multicut}.
+We run the traditional multicut algorithm on our graph varying a bias parameter that encourages over- and under-segmentation. 
+\TODO{ADD ADDITIONAL FEATURES}

### 2018-03-05 papers/eccv2018/3_evaluation.tex
papers: added changes to evaluation, results and conclusions

@@
 The original dataset contains a $\SI[product-units=single]{40 x 50 x 120}{\micro\meter}^3$ volume with a resolution of $\SI[product-units=single]{10 x 10 x 10}{\nano\meter}^3$ per voxel. 
-We use two cubes (Vol.
-1 and Vol.
-2) of size $\SI[product-units=single]{10 x 10 x 10}{\micro\meter}^3$ or $1000 \times 1000 \times 1000$ voxels.
+We use two cubes (Vol. 1 and Vol. 2) of size $\SI[product-units=single]{10 x 10 x 10}{\micro\meter}^3$.
 
@@
 The two parameters for the graph pruning algorithm (Sec.~\ref{sec:skeletonization}) are $t_{low}$ and $t_{high}$. 
-Ideally, the merge candidates output by this algorithm will contain all possible positive examples with a very limited number of negative examples.
-After considering various thresholds, we find that $t_{low} = \SI{240}{\nano\meter}$ and $t_{high} = \SI{600}{\nano\meter}$ produce the best results considering this objective.
+Ideally, our graph will have an edge for every over-segmented pair of labels with few edges between correctly segments pairs. 
+After considering various thresholds, we find that $t_{low} = \SI{240}{\nano\meter}$ and $t_{high} = \SI{400}{\nano\meter}$ produce reasonable results on our training data considering this objective.
 
@@
 For example, the thresholds in voxels are $t_{low} = (40, 40, 8)$ and $t_{high} = (100, 100, 20)$ for the anisotropic Kasthuri dataset and $t_{low} = (24, 24, 24)$ and $t_{high} = (60, 60, 60)$ for the isotropic FlyEM dataset.
-
-%Table \ref{table:skeletonization} shows the overall success of our graph creation method with candidate pruning.
-\hp{not clear what this table is showing--explain.
-put this in the experiment section where you discuss the results}
 
@@
 Table~\ref{table:architecture} provides the parameters of the final network. 
-There are 7,294,705 learnable parameters in our final architecture. 
+There are \TODO{X,XXX,XXX} learnable parameters in our final architecture. 
 All the parameters are randomly initialized following the Xavier uniform distribution~\cite{glorot2010understanding}. 
-Training concluded after \TODO{YYY} epochs.
+Training concluded after \TODO{XXX} epochs.
 
@@
 		Momentum & 0.9 \\
-		Initial Learning Rate & 0.01 \\
+		Initial Learning Rate & 0.0001 \\
 		Decay Rate & $5 * 10^{-8}$ \\
@@
 
-Since our input is an existing segmentation of the EM images, there are very few training examples compared to per-pixel classifiers that a unique window for each voxel. 
-The Kasthuri dataset represents a region of brain over $\SI[product-units=single]{800}{\micro\meter}^3$ in volume and only yields \TODO{700} positive and \TODO{7000} negative examples.
-To avoid overfitting our deep networks, we apply the following augmentations on the example.
-During a single batch, we randomly select ten positive examples and ten negative examples. 
-With probability 0.5, the example is flipped across the $xy$-plane. 
+Since our input is an existing segmentation of the EM images, there are very few training examples compared to per-pixel classifiers that can train on a unique window for each voxel. 
+The Kasthuri dataset represents a region of brain over $\SI[product-units=single]{800}{\micro\meter}^3$ in volume and only yields \TODO{700} positive merge examples and \TODO{7000} negative ones.
+To avoid overfitting our deep networks, we apply the following augmentations on the training examples.
+During a single batch, we randomly select ten positive and negative examples. 
+With probability 0.5, the example is reflected across the $xy$-plane. 
 We then rotate the example by a random angle between $0$ and $360$ degrees using nearest neighbor interpolation. 
@@
 We have 20,000 such examples per epoch.
-
-%\subsection{Graph-based Strategies}
-
-%Applying a top-down globally optimal partitioning function allows us to enforce some domain-specific constraints on the reconstruction.
-%In connectomics, we want to enforce the topological restrictions that each partition in the graph has a genus of zero.
-%The greedy-additive heuristic solves the multicut graph partitioning problem by enforcing this constraint.
-%Previous agglomeration strategies at the per-region level consider neighboring superpixels in order of merge probability.
-%These superpixels are clustered hierarchically without concern for global constraints.
-%We compare the benefits of a top-down partitioning function versus the traditional bottom-up clustering methods.

### 2018-03-05 papers/eccv2018/4_results.tex
paper: major changes to abstract, intro, and related works
papers: added changes to evaluation, results and conclusions

@@
 
-%\section{Results}
-
 \subsection{Error Metric}
@@
 Given a ground truth labeling $GT$ and our automatically reconstructed segmentation $SG$, over- and under-segmentation are quantified by the conditional entropies $H(GT | SG)$ and $H(SG | GT)$, respectively.
-Since we are measuring the entropies between two clusterings, lower VI scores are better.
+Since we are measuring the entropy between two clusterings, lower VI scores are better.
 
@@
 
-Our algorithm improves the accuracy of the reconstruction for every dataset, reducing the VI split score on average by 19.3\% on the three testing datasets. 
+Our algorithm improves the accuracy of the reconstruction for every dataset, reducing the VI split score on average by \TODO{XX}\% on the three testing datasets. 
 Scores closer to the origin are better for this metric, and in every instance our results are below the green curve.
-We see significant improvements on the Kasthuri datasets (VI split reduction of 27.7\% and 24.8\% on the training and testing datasets respectively) and more modest improvements on the FlyEM datasets (reduction of 15.2\% and 18.0\%).
+We see significant improvements on the Kasthuri datasets (VI split reduction of \TODO{XX}\% and \TODO{XX}\% on the training and testing datasets respectively) and more modest improvements on the FlyEM datasets (reduction of \TODO{XX}\% and \TODO{XX}\%).
 This is because the baseline segmentation algorithm for the isotropic FlyEM data (Sec.~\ref{sec:neuroproof}) performs much better, reducing the potential for improvements. 
@@
 
-Fig.~\ref{fig:qualitative-results} shows successful merges on the Kasthuri Vol. 2 dataset. Several of these examples combine multiple consecutive segments that span the volume.
+Fig.~\ref{fig:qualitative-results} shows successful merges on the Kasthuri Vol. 2 dataset. 
+Several of these examples combine multiple consecutive segments that span the volume.
 In the third example we correct the over-segmentation of a dendrite and attached spine-necks.
@@
 The baseline algorithm considers all adjacent regions for merging. 
-Our method removes a significant portion of these candidates while maintaining a large number of the true merge locations (e.g., 753 compared to 763).
-Our pruning heuristic removes at least $6\times$ the number of edges on all datasets, achieving a maximum removal rate of $20\times$.
+Our method removes a significant portion of these candidates while maintaining a large number of the true merge locations (e.g., \TODO{XXX} compared to \TODO{XXX}). 
+Our pruning heuristic removes at least $\TODO{X}\times$ the number of edges on all datasets, achieving a maximum removal rate of $\TODO{XX}\times$.
+We present additional analysis of the skeletonization parameters in the supplemental material.
 
@@
 We still want to reconstruct these neurons despite the fact that the initial segmentation is non-continuous. 
-The second and fourth examples in Fig.~\ref{fig:positive-results} show correctly reconstructed neurons where two of the segments are non-adjacent. 
+The second and fourth examples in Fig.~\ref{fig:qualitative-results} show correctly reconstructed neurons where two of the segments are non-adjacent. 
 This is a large benefit over enforcing segment adjacency.
@@
 There are some pairs of segments which we do not consider for merging because of our reliance on the skeletons.
-Fig.~\ref{fig:skeleton-results} shows such a case. 
+Fig.~\ref{fig:skeleton-results} shows two such cases. 
 The endpoints of both segments are circled.
 In this example the small segment is carved from the larger segment in a location where there are no skeleton endpoints. 
+There are on average $\TODO{XX}$ such examples in our datasets, corresponding to $\TODO{XX}$ in the variation of information split score.
 
-\begin{figure}[h!]
+\begin{figure}[t!]
 	\centering
-	\includegraphics[width=0.85\linewidth]{./figures/merge_candidate1.png}
-	\caption{A false negative example of our method due to graph pruning. The distance between the endpoints (circled) of the two segments is too far to be flagged as a merge candidate.}
+	\includegraphics[width=0.45\linewidth]{./figures/merge_candidate1.png}		\includegraphics[width=0.45\linewidth]{./figures/merge_candidate1.png}
+	\caption{Two false negative example of our method due to graph pruning.
+The distance between the endpoints (circled) of the two segments is too far to be flagged as a merge candidate.
+\TODO{SECOND EXAMPLE}}
 	\label{fig:skeleton-results}
@@
 
+Data augmentation at test time can improve accuracy results~\cite{zeng2017deepem3d}.
 When computing the probability to merge two segments, we input the initial segment into our CNN as well as \TODO{XX} randomly rotated and flipped examples (in the same manner as training augmentation).
@@
 
-\TODO{Add table for augmentation}
+\begin{table}
+	\begin{center}
+		\begin{tabular}{c | c c c}
+			Dataset & Precision & Recall & Accuracy \\ \hline
+			Kasthuri & & & \\
+			FlyEM Vol. 1 & & & \\
+			FlyEM Vol. 2 & & & 
+		\end{tabular}
+		\caption{Data augmentation during test time increases the precision, recall, and accuracy of all three datasets.}
+		\label{table:inference-augmentation}
+	\end{center}
+\end{table}
 
@@
 	\centering
-	\includegraphics[width=0.95\linewidth]{./figures/receiver-operating-characteristic.jpg}
+	\includegraphics[width=0.45\linewidth]{./figures/receiver-operating-characteristic.jpg}
 	\caption{The receiver operating characteristic (ROC) curves of our classifier on three connectomics datasets.
@@
 Since it is more difficult to correct merge errors than split errors, it is often desirable to sacrifice recall for precision.
-Over the three testing datasets, applying a graph-based partitioning strategy reduced the number of merge errors by 36.1\%, 12.2\%, and 13.6\%, respectively.
+Over the three testing datasets, applying a graph-based partitioning strategy reduced the number of merge errors by \TODO{XX}\%, \TODO{XX}\% and \TODO{XX}\%, respectively.
 

### 2018-03-05 papers/eccv2018/5_conclusions.tex
updated paper to eccv format
papers: added changes to evaluation, results and conclusions

--- 2017-11-15 papers/cvpr2018/5_conclusions.tex
@@
 
-There is significant room for additional research and improvements.
+In the future, these methods can be adjusted to apply more specific domain constraints. 
 We can augment the graph with additional information from the image data, such as synaptic locations, cell morphology, locations of mitochondria, etc. 
-This would allow us to enforce additional biological constraints during graph partitioning.
+This would allow us to enforce more biological constraints during graph partitioning. 
 For example, we could then enforce the constraint that a given segment only has post- or pre-synaptic connections. 

### 2018-03-08 papers/eccv2018/supplemental/supplemental.tex
eccv2018: added template for supplemental material

--- 2018-03-05 papers/eccv2018/paper.tex
@@
 \usepackage{color}
-\usepackage{subfig}
-\usepackage{times}
-\usepackage{epsfig}
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{caption}
-%\usepackage{subcaption}
-\usepackage{booktabs}
-\usepackage{makecell}
-\usepackage{algorithm}
-\usepackage{algpseudocode}
-\usepackage{siunitx}
-\usepackage{float}
 \usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}
-
 \begin{document}
@@
 
-\titlerunning{ECCV-18 submission ID \ECCV18SubNumber}
+\title{Graph-Based Neural Reconstruction from Skeletonized 3D Networks\\~\\\textit{Supplemental Material}} % Replace with your title
+
+\titlerunning{Supplementary Material ID \ECCV18SubNumber}
 
 \authorrunning{ECCV-18 submission ID \ECCV18SubNumber}
-\title{Graph-Based Neural Reconstruction from Skeletonized 3D Networks}
 
@@
 
-\newcommand\TODO[1]{\textcolor{red}{#1}}
-
 \maketitle
-
-\begin{abstract}
-Advancements in electron microscopy image acquisition have created connectomics datasets terabytes in size making manual reconstruction of neuronal structures infeasible.
-Current state-of-the-art automatic methods classify neural membranes at the pixel level followed by agglomeration methods to create full neuron reconstructions.
-However, these approaches widely neglect global geometric properties that are inherent in the graph structure of neural wiring diagrams.
-In this work, we follow pixel-based reconstruction by a global graph-based method to more accurately approximate neural pathways.
-We first generate skeletons in 3D from the neuron labels of the pixel-based segmentation.
-Next, we simplify this skeletonized 3D network into a graph with nodes corresponding to labels from the segmentation and edges identifying potential locations of split errors.
-A CNN classifier produces edge weights for the graph corresponding to the probability of error. 
-We formulate the graph into a multicut partitioning problem to improve the final segmentation.
-Since the 3D graph is small and encodes top-down information our method is efficient and globally improves the neural reconstruction.
-We demonstrate the performance of our approach on multiple real-world connectomics datasets with an average split variation of information improvement of \TODO{XX}\%.
-\keywords{connectomics, skeletonization, deep learning}
-\end{abstract}
-
-\input{0_introduction}
-
-\input{1_related_work}
-
-\input{2_method}
-
-\input{3_evaluation}
-
-\input{4_results}
-
-\input{5_conclusions}
 
@@
 \bibliography{egbib}
-
 \end{document}

### 2018-03-09 papers/eccv2018/2_method.tex
papers: added comments from Daniel and create outline for supplemental materials

@@
 To find actual merges we run a classification CNN to generate edge weights corresponding to merge probabilities.
-We then use a multicut algorithm to generate a partition on the graph where nodes in the same partition are assigned the same output label in the improved segmentation. 
+We formulate our graph partitioning problem as a multicut problem to segment the nodes into correct neuronal processes. 
 We will now discuss the three major components to our framework (graph creation, edge weight assignment, and graph partitioning) in more detail.
@@
 The simplest node generation strategy creates one node for every unique segment label in the input volume. 
-However, some of the millions of labels in the volume correspond to very small structures that are likely the result of segmentation errors, typically in regions with noisy raw image data. 
+However, some of the labels in the volume correspond to very small structures that are likely the result of segmentation errors, typically in regions with noisy raw image data. 
 It is difficult to extract useful shape features from these segments because of their small, often random, shape. 
@@
 Despite the large number of segments, these regions only take up \TODO{XX}\% of the total volume on average.
+\TODO{How much does this change VI - should that matter?}
+\TODO{Picture of these examples}
 
@@
 We identify a smaller number of pairs of segments to consider as graph edges using the following approach.
+\TODO{address comment from that one reviewer}
 
@@
 We prune the joints that are within $t_{jnt} = \TODO{XX}\SI{}{\nano\meter}$ of each other to reduce unnecessary branching. 
+\TODO{why this value?}
 We refer to joints that have only one connected neighbor as \textit{endpoints}. 
 Many of the segments that are erroneously split have nearby endpoints  (Fig.~\ref{fig:merge_candidates}). 
+\TODO{Numbers for this?}
 We make use of this fact to find merge candidates with the following two-pass pruning algorithm.
@@
 This algorithm produces a set of segments to consider for merging. Only these pairs have a corresponding edge in the constructed graph.
+\TODO{From Daniel: this sounds like a double threshold to me.. imho 1-2 sentences without formulas is clearer?}
 
@@
 We do not use the raw EM image information to avoid the need to retrain the network on datasets that have been stained differently or imaged at different resolution. 
-This significantly reduces the need for generating costly manually-labeled ground truth.
+This reduces the need for generating costly manually-labeled ground truth.
 
@@
 
-After constructing the 3D graph we apply graph partitioning with a multicut formulation to compute the final segmentation. 
-Using this global graph partitioning allows us to apply biological constraints on the output. 
-The multicut minimization problem allows us to guarantee globally consistent solutions where every cycle is ``closed'' under merging.
-To solve this constraining multicut problem we use the method by Keuper et al.~\cite{keuper2015efficient} that produces a feasible solution by greedy additive edge contraction.
-We extend the multicut formulation to the ``lifted'' version of the problem where non-adjacent nodes have ``lifted'' edges.
-These edges penalize or reward distance nodes for belonging to the same segment and produce benefits over traditional multicut. 
-We determine the lifted edge weights following the example of Beier et al~\cite{beier2017multicut}.
-We run the traditional multicut algorithm on our graph varying a bias parameter that encourages over- and under-segmentation. 
-\TODO{ADD ADDITIONAL FEATURES}
+After constructing the 3D graph we seek to partition the graph into labels where every label corresponds to a neuronal process. 
+We formulate this graph partitioning problem as a multicut problem.
+There are two primary benefits to using a multicut formulation. 
+First, the number of segments in the final graph is not predetermined but depends on the input graph itself. 
+Second, this minimization produces globally consistent solutions (i.e. a boundary remains if and only if the two corresponding nodes belong to unique segments).
+
+We apply the algorithms of Keuper et al.~\cite{keuper2015efficient} to produce a feasible solution to the multicut problem using greedy additive edge contraction.
+Following their example, we employ the generalized ``lifted'' multicut formulation.
+Traditional multicut solutions only consider the probabilities that two adjacent nodes belong to the same segment. 
+In the ``lifted'' extension to the problem, we can penalize non-adjacent nodes that belong to different segments. 
+These penalties between non-adjacent nodes are called ``lifted'' edges. 
+Ideally these ``lifted'' weights represent the probability that two nodes belong to the same neuron given all such possible paths in the graph between the nodes.
+However, determining such probabilities is computationally expensive.
+We approximate these probabilities by finding the maximal probable path between any two nodes using Dijkstra's algorithm~\cite{keuper2015efficient}.
+Since our graphs are sufficiently small, we can generate ``lifted'' edges between all pairs of nodes.

### 2018-03-09 papers/eccv2018/3_evaluation.tex
papers: added comments from Daniel and create outline for supplemental materials

@@
 
-We evaluate our method by comparing it to a state-of-the-art pixel-based reconstruction approach using datasets from two different species.
+We evaluate our method by comparing it to a state-of-the-art pixel-based reconstruction approach using datasets from mouse and fly brains.
 
@@
 The original dataset contains a $\SI[product-units=single]{40 x 50 x 120}{\micro\meter}^3$ volume with a resolution of $\SI[product-units=single]{10 x 10 x 10}{\nano\meter}^3$ per voxel. 
-We use two cubes (Vol. 1 and Vol. 2) of size $\SI[product-units=single]{10 x 10 x 10}{\micro\meter}^3$.
+We use two cubes (Vol. 1 and Vol. 2) of size $\SI[product-units=single]{10 x 10 x 10}{\micro\meter}^3$ or $999 \times 999 \times 999$ voxels.
 
@@
 This segmentation framework learns voxel and supervoxel classifiers with an emphasis to minimize under-segmentation error. 
-At the same time this framework produces lower over-segmentation than standard algorithms. 
 The algorithm first computes multi-channel 3-D predictions for membranes, cell interiors, and mitochondria, among other cell features. 
@@
 The two parameters for the graph pruning algorithm (Sec.~\ref{sec:skeletonization}) are $t_{low}$ and $t_{high}$. 
-Ideally, our graph will have an edge for every over-segmented pair of labels with few edges between correctly segments pairs. 
-After considering various thresholds, we find that $t_{low} = \SI{240}{\nano\meter}$ and $t_{high} = \SI{400}{\nano\meter}$ produce reasonable results on our training data considering this objective.
+Ideally, our graph will have an edge for every over-segmented pair of labels with few edges between correctly segmented pairs. 
+After considering various thresholds, we find that $t_{low} = \SI{210}{\nano\meter}$ and $t_{high} = \SI{300}{\nano\meter}$ produce expressive graphs with a scalable number of nodes and edges.
+We explore these thresholds in greater detail in the supplemental material.
 
@@
 Using nanometers allows us to have uniform units across all of these datasets and calculate the thresholds in voxels at runtime.
-For example, the thresholds in voxels are $t_{low} = (40, 40, 8)$ and $t_{high} = (100, 100, 20)$ for the anisotropic Kasthuri dataset and $t_{low} = (24, 24, 24)$ and $t_{high} = (60, 60, 60)$ for the isotropic FlyEM dataset.
+Although the voxels vary between different datasets, the physical space remains constant.
 
@@
 We then rotate the example by a random angle between $0$ and $360$ degrees using nearest neighbor interpolation. 
-The supplemental material contains experiments demonstrating that benefits of this augmentation strategy.
+The supplemental material contains experiments demonstrating the benefits of this augmentation strategy.
 We have 20,000 such examples per epoch.

### 2018-03-09 papers/eccv2018/4_results.tex
papers: added comments from Daniel and create outline for supplemental materials

@@
 In Fig.~\ref{fig:variation-of-information}, we show the VI results of the pixel-based reconstructions of the Kasthuri and FlyEM data (Sec.~\ref{sec:neuroproof}) for varying thresholds of agglomeration (green).
-We use one of these segmentations (green circle) as out input dataset with an agglomeration threshold of 0.3 for all datasets. 
+We use one of these segmentations (green circle) as our input dataset with an agglomeration threshold of 0.3 for all datasets. 
 The results from our method are shown in red for varying the $\beta$ parameter. 
@@
 We see significant improvements on the Kasthuri datasets (VI split reduction of \TODO{XX}\% and \TODO{XX}\% on the training and testing datasets respectively) and more modest improvements on the FlyEM datasets (reduction of \TODO{XX}\% and \TODO{XX}\%).
-This is because the baseline segmentation algorithm for the isotropic FlyEM data (Sec.~\ref{sec:neuroproof}) performs much better, reducing the potential for improvements. 
-Isotropic datasets are easier to segment using state-of-the-art region-based methods than anisotropic ones~\cite{plaza2014annotating}.
+\TODO{FIX: This is because the baseline segmentation algorithm for the isotropic FlyEM data (Sec.~\ref{sec:neuroproof}) performs much better, reducing the potential for improvements. 
+Isotropic datasets are easier to segment using state-of-the-art region-based methods than anisotropic ones~\cite{plaza2014annotating}.}
 
-Fig.~\ref{fig:qualitative-results} shows successful merges on the Kasthuri Vol. 2 dataset. 
+Fig.~\ref{fig:qualitative-results} (left) shows successful merges on the Kasthuri Vol. 2 dataset. 
 Several of these examples combine multiple consecutive segments that span the volume.
-In the third example we correct the over-segmentation of a dendrite and attached spine-necks.
-Fig.~\ref{fig:qualitative-results} shows typical failure cases of our method (red circles).
+In the third example on the left we correct the over-segmentation of a dendrite and attached spine-necks.
+Fig.~\ref{fig:qualitative-results} (right) shows typical failure cases of our method (red circles).
 In two of these examples the algorithm correctly predicted several merges before a single error rendered the segment as wrong.
@@
 Our pruning heuristic removes at least $\TODO{X}\times$ the number of edges on all datasets, achieving a maximum removal rate of $\TODO{XX}\times$.
+However, there are some adjacent over-segmented labels which are considered. 
+Table~\ref{table:skeletonization} shows the results for our edge generation including the number of missed neighbors and potential penalty in VI score.
+\TODO{augment table}
 We present additional analysis of the skeletonization parameters in the supplemental material.
@@
 The second and fourth examples in Fig.~\ref{fig:qualitative-results} show correctly reconstructed neurons where two of the segments are non-adjacent. 
-This is a large benefit over enforcing segment adjacency.
+On average in our datasets we correctly merge \TODO{XX} number of non-adjacent segments.
 
@@
 Fig.~\ref{fig:receiver-operating-characteristic} shows the receiver operating characteristic (ROC) curve of our CNN classifier for all test datasets.
-%We train our CNN using one of the Kasthuri volumes and test using the other three datasets.
-Since our CNN only takes as input a region of the label volume we can train on  anisotropic data and test on isotropic data.
-This provides a major benefit given the time-intensive task of manually generating ground truth for each dataset at various resolutions.
-
-As shown by the ROC curve, the test results on the Kasthuri data are better than the results for FlyEM.
+\TODO{As shown by the ROC curve, the test results on the Kasthuri data are better than the results for FlyEM.
 We believe this is in part because of the differences in the datasets (i.e., isotropy and $xy$ resolution).
@@
 However, the improvement is minor, which led us to use the CNN trained on the anisotropic data for the rest of our experiments.
+-- FIX THIS, also AUC values}
 
@@
 
+\paragraph{Neural Network Transference.}
+
+Our neural network does not take as input the images or affinities to allow us to transfer network weights from one dataset to the next.
+Table~TODO{X} shows the result when training on the FlyEM data and inferring on the Kasthuri data and vice versa.
+The classification results are reasonable despite the fact that the datasets vary in resolution and even animal type.
+
 \subsection{Graph Optimization Results}
@@
 Table \ref{table:multicut} shows the changes in precision, recall, and accuracy for all four datasets compared to the CNN.
-The precision increases on each dataset, although the recall decreases on all but one of the datasets.
-Since it is more difficult to correct merge errors than split errors, it is often desirable to sacrifice recall for precision.
+The precision increases on each dataset, although the recall decreases on all but one of the datasets.Since it is more difficult to correct merge errors than split errors, it is often desirable to sacrifice recall for precision.
 Over the three testing datasets, applying a graph-based partitioning strategy reduced the number of merge errors by \TODO{XX}\%, \TODO{XX}\% and \TODO{XX}\%, respectively.

### 2018-03-09 papers/eccv2018/supplemental/classifier.tex
papers: added comments from Daniel and create outline for supplemental materials

\section{Merge Classification}

\subsection{Architecture}

\subsection{Training Augmentation}

\subsection{Testing Augmentation}

### 2018-03-11 papers/eccv2018/2_method.tex
eccv2018: updated figures

@@
 	\centering
-	\includegraphics[width=0.32\linewidth]{./figures/skeleton1.png}
-	\includegraphics[width=0.32\linewidth]{./figures/skeleton2.png}
-	\includegraphics[width=0.32\linewidth]{./figures/skeleton3.png}
+	\includegraphics[width=0.45\linewidth]{./figures/skeleton1.png}
+	\includegraphics[width=0.45\linewidth]{./figures/skeleton2.png}
+	\includegraphics[width=0.45\linewidth]{./figures/skeleton3.png}
+	\includegraphics[width=0.45\linewidth]{./figures/skeleton4.png}
 	\caption{Example skeletons (in black) extracted from segments using a variant of the TEASER algorithm.}
@@
 Since our graphs are sufficiently small, we can generate ``lifted'' edges between all pairs of nodes.
+
+\paragraph{Post-processing}
+
+By reformulating the segmentation problem as a graph partitioning one, we can enforce some global constraints on our result based on the underlying biology.
+Traditional hierarchical clustering algorithms do not rely on such constraints but consider local decisions independently.
+The multicut problems returns a series of ``collapsed'' edges between nodes that belong to the same neuron.
+We iterate over these edges in order of the probability of merge generated by our CNN. 
+\TODO{HOW DO WE ACCOMPLISH THIS}

### 2018-03-12 papers/eccv2018/3_evaluation.tex
method description in 4.2 + overall comments

@@
 \section{Experimental Results}
-
+\TODO{right now, too many subsections. shall we break it into "Setup" and "Results"}
 We evaluate our method by comparing it to a state-of-the-art pixel-based reconstruction approach using datasets from mouse and fly brains.
@@
 
-The segmentation of the Kasthuri dataset was computed by agglomerating 3D supervoxels produced by the z-watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}. 
-A recent study by Funke et al.~\cite{funke2017deep} demonstrated superior performance of such methods over existing ones on anisotropic data. 
-We learn 3D affinities using MALIS loss with a U-net~\cite{ronneberger2015u,Turaga:2009}. 
-We apply the z-watershed algorithm with suitable parameters to compute a 3D oversegmentation of the volume. 
-The resulting 3D oversegmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}.
+%The segmentation of the Kasthuri dataset was computed by agglomerating 3D supervoxels produced by the watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}. 
+%A recent study by Funke et al.~\cite{funke2017deep} demonstrated superior performance of such methods over existing ones on anisotropic data. 
+%We learn 3D affinities using MALIS loss with a U-net~\cite{ronneberger2015u,Turaga:2009}. 
+%We apply the z-watershed algorithm with suitable parameters to compute a 3D oversegmentation of the volume. 
+%The resulting 3D oversegmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}.
+For the Kasthuri dataset, we used the segmentation pipeline from Funke et al.~\cite{funke2017deep}. 
+We first trained a 3D affinity prediction U-Net model~\cite{ronneberger2015u} with Malis loss~\cite{Turaga:2009} and applied the watershed and agglomeration method~\cite{funke2017deep} to obtain the final segmentation result.
 
@@
 
+\TODO{we don't have space for the table for training parameters: move to supp}
 \begin{table}[h!]

### 2018-03-12 cnns/skeleton/forward.py
cnns: fixed bug in feature extraction

@@ -54,7 +54,7 @@ def Forward(prefix, model_prefix, threshold, maximum_distance, endpoint_distance
     # read in the trained model
     model = model_from_json(open('{}.json'.format(model_prefix), 'r').read())
     model.load_weights('{}-best-loss.h5'.format(model_prefix))
-    
+
     # get the candidate locations 
     positive_candidates = FindCandidates(prefix, threshold, maximum_distance, endpoint_distance, network_distance, 'positive')
     negative_candidates = FindCandidates(prefix, threshold, maximum_distance, endpoint_distance, network_distance, 'negative')

### 2018-03-12 cnns/skeleton/train.py

@@ -160,7 +160,6 @@ def WriteLogfiles(model, model_prefix, parameters):
 
 def SkeletonCandidateGenerator(prefix, network_distance, positive_candidates, negative_candidates, parameters, width):
     # get the number of channels for the data
-    nchannels = width[0]
 
     npositive_candidates = len(positive_candidates)
     nnegative_candidates = len(negative_candidates)

### 2018-03-12 cnns/skeleton/util.py

@@ -91,7 +91,8 @@ def ExtractFeature(segmentation, candidate, width, radii, augment=True):
     
     # perform a rotation
     angle = random.uniform(0, 360)
-    example = scipy.ndimage.interpolation.rotate(example, angle, axes=(IB_X + 2, IB_Y + 2), reshape=False, order=0)
+    # cvalue is -0.5 to match the background being -0.5
+    example = scipy.ndimage.interpolation.rotate(example, angle, axes=(IB_X + 2, IB_Y + 2), reshape=False, order=0, mode='constant', cval=-0.5)
 
     return example
 

### 2018-03-12 transforms/h52h5.py
transforms: added option to go from image stack to h5 file

@@ -25,6 +25,40 @@ def DownsampleData(data, ratio=(1, 2, 2)):
 
 
 
+@jit(nopython=True)
+def MaskAndCropSegmentation(data, labels):
+    # create a set of valid segments
+    ids = set()
+    for label in labels:
+        ids.add(label)
+
+    # get the shape of the data
+    zres, yres, xres = data.shape
+
+    zmin, ymin, xmin = data.shape
+    zmax, ymax, xmax = (0, 0, 0)
+
+    masked_data = np.zeros((zres, yres, xres), dtype=np.int64)
+
+    # go through the entire data set
+    for iz in range(zres):
+        for iy in range(yres):
+            for ix in range(xres):
+                # skip masked out values
+                if not data[iz,iy,ix] in ids: continue
+                
+                masked_data[iz,iy,ix] = data[iz,iy,ix]
+                if iz < zmin: zmin = iz
+                if iy < ymin: ymin = iy
+                if ix < xmin: xmin = ix
+                if iz > zmax: zmax = iz
+                if iy > ymax: ymax = iy
+                if ix > xmax: xmax = ix
+
+    return masked_data[zmin:zmax,ymin:ymax,xmin:xmax]
+
+
+
 # split the data to create training and validation data
 @jit(nopython=True)
 def SplitData(data, axis, threshold=0.5):

### 2018-03-12 utilities/dataIO.py
utilities: changed image reading

@@ -117,15 +117,7 @@ def ReadTopologySkeletons(prefix, data):
 
 
 def ReadImage(filename):
-    image = np.array(Image.open(filename)) / 255.0
-    # make into RGB image
-    if len(image.shape) == 2:
-        RGB_image = np.zeros((image.shape[0], image.shape[1], 3), dtype=np.float32)
-        RGB_image[:,:,0] = image
-        RGB_image[:,:,1] = image
-        RGB_image[:,:,2] = image
-        return RGB_image
-    
+    image = np.array(Image.open(filename))
     return image
 
 

### 2018-03-12 utilities/dataIO.py
updating dataIO

@@ -117,17 +117,7 @@ def ReadTopologySkeletons(prefix, data):
 
 
 def ReadImage(filename):
-    image = np.array(Image.open(filename)) / 255.0
-    # make into RGB image
-    if len(image.shape) == 2:
-        RGB_image = np.zeros((image.shape[0], image.shape[1], 3), dtype=np.float32)
-        RGB_image[:,:,0] = image
-        RGB_image[:,:,1] = image
-        RGB_image[:,:,2] = image
-        return RGB_image
-    
-    return image
-
+    return np.array(Image.open(filename))
 
 
 #def WriteImage(filename, image):

### 2018-03-12 papers/eccv2018/2_method.tex

@@
 Two segments $l_1$ and $l_2$ are considered adjacent if there is a pair of adjacent voxels with one labeled $l_1$ and the other labeled $l_2$.
+\TODO{maybe not mentioning neuroproof, but mean agglomeration and waterz}
 For example, pixel-based agglomeration methods such as NeuroProof~\cite{10.1371/journal.pone.0125825} and GALA~\cite{nunez2014graph} consider all pairs of adjacent segments for merging.
@@
 \subsection{Graph Partitioning}
-
+\TODO{the subsection name isn't intuitive for reviewers to link to reduce split error}
 After constructing the 3D graph we seek to partition the graph into labels where every label corresponds to a neuronal process. 

### 2018-03-12 papers/eccv2018/4_results.tex
eccv2018: updated figures

@@
 
-Data augmentation at test time can improve accuracy results~\cite{zeng2017deepem3d}.
+Data augmentation at test time can improve accuracy results~\cite{zeng2017deepem3d,lee2017superhuman}.
 When computing the probability to merge two segments, we input the initial segment into our CNN as well as \TODO{XX} randomly rotated and flipped examples (in the same manner as training augmentation).
@@
 \paragraph{Neural Network Transference.}
-
+\TODO{rename: Generalization to Other Dataset.}
 Our neural network does not take as input the images or affinities to allow us to transfer network weights from one dataset to the next.
@@
 \TODO{How does using lifted-multicut improve the results!}
+
+\TODO{What are the benefits of post processing?}

### 2018-03-12 papers/eccv2018/supplemental/classifier.tex

@@
 
-\subsection{Architecture}
+\subsection{Network Architecture}
+
+We tested various architectures before deciding on the one we present in the paper. 
+Each architecture uses VGG-style blocks (i.e. two convolutions of size $3\times3\times3$ followed by a max-pooling layer)~\cite{chatfield2014return}.
+For the first two layers the max-pooling is anisotropic with reduction only in the $x$ and $y$ dimensions. 
+The number of filters starts at 16 for the first block and doubles in each subsequent block.
+Our architectures vary in the input size and number of layers. 
+In all instances we extract a \SI{1200}{\nano\meter^3} region of interest and map the extracted voxels to the given input size. 
+These input sizes correspond to specific output sizes from the last VGG block.
+
+\begin{table}
+	\scriptsize
+	\centering
+	\begin{tabular}{c c c c c c c}
+		\hline
+		\textbf{Depth} & \textbf{Input Size} & \textbf{No. Parameters} & \textbf{Output Size} & \textbf{Accuracy} & \textbf{Precision} & \textbf{Recall} \\ \hline
+		      3        & (3, 18, 52, 52)     & 1,101,553               & (64, 3, 3, 3)        &                   &                    &  \\
+		      3        & (3, 20, 60, 60)     & 2,313,969               & (64, 4, 4, 4)        &                   &                    &  \\
+		      3        & (3, 22, 68, 68)     & 4,312,817               & (64, 5, 5, 5)        &                   &                    &  \\
+		      3        & (3, 24, 76, 76)     & 7,294,705               & (64, 6, 6, 6)        &                   &                    &  \\
+		      3        & (3, 26, 84, 84)     & 11,456,241              & (64, 7, 7, 8)        &                   &                    &  \\
+		      3        & (3, 28, 92, 92)     & 16,994,033              & (64, 8, 7, 8)        &                   &                    &  \\
+		      3        & (3, 30, 100, 100)   & 24,104,689              & (64, 9, 9, 9)        &                   &                    &  \\
+		      4        & (3, 28, 92, 92)     & 1,404,913               & (128, 2, 2, 2)       &                   &                    &  \\
+		      4        & (3, 32, 108, 108)   & 2,650,097               & (128, 3, 3, 3)       &                   &                    &  \\ \hline
+	\end{tabular}
+	\caption{The results of various network architectures trained on the Kasthuri data.}
+	\label{table:input-size}
+\end{table}
 

### 2018-03-12 papers/eccv2018/supplemental/skeletonization.tex

--- 2018-03-09 papers/eccv2018/2_method.tex
@@
-% !TEX root =  paper.tex
-\section{Method}
+\section{Skeletonization}
 
-\begin{figure*}[htbp]
-	\begin{center}
-		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/multicut_input.png}}
-		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/pre-multicut.png}}
-		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/multicut-graph.png}}
-		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/post-multicut.png}}
-	\end{center}
-	\caption{Outline of our approach, from left to right: result of the pixel-based segmentation and agglomeration algorithm; segments of several neurons from the initial segmentation; extracted skeletonized network of those segments; improved 3D reconstruction of the selected segments after graph construction and partitioning with constraints.}
-	\label{fig:overview}
-\end{figure*}
-
-There are two types of errors that can occur in connectomics segmentations: \textit{split errors} and \textit{merge errors}. 
-In a split error, two segments should have been merged into one neuronal process. 
-In a merge error, one segment corresponds to more than one neuron.
-Generally, it is much more difficult to correct merge errors than to correct split errors,
-as the space of possible split proposals grows quickly~\cite{parag2015properties}.
-Thus, most reconstruction approaches are tuned towards over-segmentation with many more split than merge errors. 
-Our method takes as input over-segmentations of EM image volumes generated by scalable, state-of-the-art connectomics reconstruction pipelines (Sec.~\ref{sec:neuroproof}). 
-Our goal is to identify locations of split errors and merge the corresponding segments automatically.
-
-From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with weights $w_e$. 
-The nodes correspond to labeled segments from the segmentation.
-There are edges between all nodes that we consider as merge candidates.
-Ideally, our graph has edges corresponding to all of the segments that were erroneously split. 
-To compute this graph we generate a skeleton for every segment in the pixel-based segmentation (Fig.~\ref{fig:overview}). 
-The skeletonized 3D network is a simplified representation of the overall branching structure of the neurons. 
-From these skeletons we identify potential merge locations and produce the corresponding edges for the graph. 
-To find actual merges we run a classification CNN to generate edge weights corresponding to merge probabilities.
-We formulate our graph partitioning problem as a multicut problem to segment the nodes into correct neuronal processes. 
-We will now discuss the three major components to our framework (graph creation, edge weight assignment, and graph partitioning) in more detail.
+\subsection{Volume Downsampling}
 
 \subsection{Node Generation}
-%\subsubsection{Node Generation}
-\label{sec:skeletonization}
-
-The simplest node generation strategy creates one node for every unique segment label in the input volume. 
-However, some of the labels in the volume correspond to very small structures that are likely the result of segmentation errors, typically in regions with noisy raw image data. 
-It is difficult to extract useful shape features from these segments because of their small, often random, shape. 
-We prune these nodes from the graph by removing all segments with fewer than a threshold $t_{seg} = 20,000$ voxels (\TODO{~XX\SI{}{\nano\meter^3}}). 
-This removed on average \TODO{XX}\% of the segments in our  datasets (Sec.~\ref{sec:dataset}).
-Despite the large number of segments, these regions only take up \TODO{XX}\% of the total volume on average.
-\TODO{How much does this change VI - should that matter?}
-\TODO{Picture of these examples}
 
 \subsection{Edge Generation}
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.32\linewidth]{./figures/skeleton1.png}
-	\includegraphics[width=0.32\linewidth]{./figures/skeleton2.png}
-	\includegraphics[width=0.32\linewidth]{./figures/skeleton3.png}
-	\caption{Example skeletons (in black) extracted from segments using a variant of the TEASER algorithm.}
-	\label{fig:skeletonization}
-\end{figure}
-
-A typical approach for generating edges produces one between all adjacent segments.
-Two segments $l_1$ and $l_2$ are considered adjacent if there is a pair of adjacent voxels with one labeled $l_1$ and the other labeled $l_2$.
-For example, pixel-based agglomeration methods such as NeuroProof~\cite{10.1371/journal.pone.0125825} and GALA~\cite{nunez2014graph} consider all pairs of adjacent segments for merging.
-However, this method produces too many edges in the graph for graph-based optimization approaches. 
-We identify a smaller number of pairs of segments to consider as graph edges using the following approach.
-\TODO{address comment from that one reviewer}
-
-First, we extract a skeleton from each segment in the label volume using a variant~\cite{zhao2014automatic} of the TEASER algorithm~\cite{sato2000teasar}. 
-This skeletonization algorithm repeatedly uses Dijkstra's algorithm to find the farthest voxel from a seed location. 
-Since this algorithm is non-linear in the number of voxels, we downsample the datasets so that there are voxel samples every $\SI{30}{\nano\meter}$ in each dimension.
-Empirically, this reduced the running time for skeletonization by $\TODO{XX\%}$, with minimal reduction in skeleton accuracy ($\TODO{XX\%}$ fewer branches). 
-Fig.~\ref{fig:skeletonization} shows three examples of extracted skeletons (in black). 
-These skeletons consist of a sequence of \textit{joints}, i.e., locations that are locally a maximum distance from the segment boundary, with line segments connecting successive joints. 
-We prune the joints that are within $t_{jnt} = \TODO{XX}\SI{}{\nano\meter}$ of each other to reduce unnecessary branching. 
-\TODO{why this value?}
-We refer to joints that have only one connected neighbor as \textit{endpoints}. 
-Many of the segments that are erroneously split have nearby endpoints  (Fig.~\ref{fig:merge_candidates}). 
-\TODO{Numbers for this?}
-We make use of this fact to find merge candidates with the following two-pass pruning algorithm.
-
-In the first pass, we iterate over all endpoints $e$ belonging to a segment $S$ and create a set of segments $\mathbb{S}_e^\prime$ that includes all labels that are within $t_{low}$ voxels from $e$.
-Elements of $\mathbb{S}_e^\prime$ are candidates for merging. 
-However, this first pass often leads to too many candidates, requiring an additional pass for further pruning. 
-In the second pass, we consider all of the segments in $\mathbb{S}_e^\prime$ for every endpoint $e$. 
-If a segment $S^\prime \in \mathbb{S}_e^\prime$ has an endpoint within $t_{high}$ voxels of $e$, the segment $S$ and $S^\prime$ are considered for merging. 
-We store the midpoints between the two endpoints as the center of the potential merge in the set $\mathbb{S}_c$. 
-This algorithm produces a set of segments to consider for merging. Only these pairs have a corresponding edge in the constructed graph.
-\TODO{From Daniel: this sounds like a double threshold to me.. imho 1-2 sentences without formulas is clearer?}
-
-\subsection{Edge Weights Assignment}
-We assign edge weights $w_e$ to each edge where the weight corresponds to the probability that two nodes belong to the same neuron.
-We train a 3D CNN classifier to learn from the manually labeled oversegmentation input volume (Sec.~\ref{sec:dataset}).
-If the probability that the nodes belong to the same neuron is $p_e$, the edge weight $w_e = \log{\frac{p_e}{1 - p_e}} + \log{\frac{1 - \beta}{\beta}}$, where $\beta$ is a tunable parameter that encourages over- or under-segmentation.
-
-\subsubsection{Classifier Input}
-
-We extract a cubic region of interest (ROI) around each endpoint $e$ in $\mathbb{S}_c$ as input to the CNN. 
-The CNN receives three input channels for every voxel in the ROI around segments $l_1$ and $l_2$. 
-The input in all of the channels is in the range $\{-0.5, 0.5\}$. 
-The first channel is $0.5$ only if the corresponding voxel has label $l_1$. 
-The second channel is $0.5$ only if the corresponding voxel has label $l_2$. 
-The third channel is $0.5$ if the corresponding voxel is either $l_1$ or $l_2$.
-We do not use the raw EM image information to avoid the need to retrain the network on datasets that have been stained differently or imaged at different resolution. 
-This reduces the need for generating costly manually-labeled ground truth.
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.32\linewidth]{./figures/split_error1.png}
-	\includegraphics[width=0.32\linewidth]{./figures/split_error2.png}		\includegraphics[width=0.32\linewidth]{./figures/merge_candidate2.png}
-	\caption{Three erroneously split segments.}
-	\label{fig:merge_candidates}
-\end{figure}
-
-\subsubsection{Network Architecture \& Training}
-
-We use \textit{VGG-style} blocks as presented by Chatfield et al.~\cite{chatfield2014return}. 
-Each blocks consists of two double convolutions with filter size $3\times3\times3$ followed by a max pooling step. 
-There are three layers of these blocks. 
-The first two max pooling layers are anisotropic with pooling only in the $x$ and $y$ dimensions. 
-The output of this final pooling step is flattened into a 1D vector that is input into two fully connected layers. 
-The final layer produces probabilities with a sigmoid activation function~\cite{funahashi1989approximate}. 
-All of the other activation functions are LeakyReLU~\cite{maas2013rectifier}.
-
-For training we use a stochastic gradient descent optimizer with Nesterov's accelerated gradient~\cite{nesterov1983method}. 
-We employ dropouts of $0.2$ after every pooling layer and the first dense layer, and a dropout of $0.5$ after the final dense layer to prevent overfitting. 
-We discuss all other network parameters in Sec.~\ref{sec:network-parameters}.
-
-\subsection{Graph Partitioning}
-
-After constructing the 3D graph we seek to partition the graph into labels where every label corresponds to a neuronal process. 
-We formulate this graph partitioning problem as a multicut problem.
-There are two primary benefits to using a multicut formulation. 
-First, the number of segments in the final graph is not predetermined but depends on the input graph itself. 
-Second, this minimization produces globally consistent solutions (i.e. a boundary remains if and only if the two corresponding nodes belong to unique segments).
-
-We apply the algorithms of Keuper et al.~\cite{keuper2015efficient} to produce a feasible solution to the multicut problem using greedy additive edge contraction.
-Following their example, we employ the generalized ``lifted'' multicut formulation.
-Traditional multicut solutions only consider the probabilities that two adjacent nodes belong to the same segment. 
-In the ``lifted'' extension to the problem, we can penalize non-adjacent nodes that belong to different segments. 
-These penalties between non-adjacent nodes are called ``lifted'' edges. 
-Ideally these ``lifted'' weights represent the probability that two nodes belong to the same neuron given all such possible paths in the graph between the nodes.
-However, determining such probabilities is computationally expensive.
-We approximate these probabilities by finding the maximal probable path between any two nodes using Dijkstra's algorithm~\cite{keuper2015efficient}.
-Since our graphs are sufficiently small, we can generate ``lifted'' edges between all pairs of nodes.

### 2018-03-12 papers/eccv2018/2_method.tex
papers: major updates to methods

--- 2018-03-11 papers/eccv2018/2_method.tex
@@
 It is difficult to extract useful shape features from these segments because of their small, often random, shape. 
-We prune these nodes from the graph by removing all segments with fewer than a threshold $t_{seg} = 20,000$ voxels (\TODO{~XX\SI{}{\nano\meter^3}}). 
-This removed on average \TODO{XX}\% of the segments in our  datasets (Sec.~\ref{sec:dataset}).
+We prune these nodes from the graph by removing all segments with fewer than a threshold $t_{seg} = 20,000$ voxels. 
+This removes on average \TODO{XX}\% of the segments in our  datasets (Sec.~\ref{sec:dataset}), leaving us with around $\TODO{XX}$ nodes per dataset (\TODO{X nodes per micrometer}). 
 Despite the large number of segments, these regions only take up \TODO{XX}\% of the total volume on average.
-\TODO{How much does this change VI - should that matter?}
-\TODO{Picture of these examples}
+We provide further analysis of this strategy in the supplemental material.
 
@@
 Two segments $l_1$ and $l_2$ are considered adjacent if there is a pair of adjacent voxels with one labeled $l_1$ and the other labeled $l_2$.
-For example, pixel-based agglomeration methods such as NeuroProof~\cite{10.1371/journal.pone.0125825} and GALA~\cite{nunez2014graph} consider all pairs of adjacent segments for merging.
+For example, pixel-based agglomeration methods such as mean agglomeration \TODO{CITE} or waterz \TODO{CITE} consider all pairs of adjacent segments for merging.
 However, this method produces too many edges in the graph for graph-based optimization approaches. 
 We identify a smaller number of pairs of segments to consider as graph edges using the following approach.
-\TODO{address comment from that one reviewer}
 
@@
 We prune the joints that are within $t_{jnt} = \TODO{XX}\SI{}{\nano\meter}$ of each other to reduce unnecessary branching.
-\TODO{why this value?}
+This value is small enough that the skeletons extend into the spines but large enough to keep branching does to a reasonable level.
+Additional analysis is available in the supplemental material.
 We refer to joints that have only one connected neighbor as \textit{endpoints}. 
-Many of the segments that are erroneously split have nearby endpoints  (Fig.~\ref{fig:merge_candidates}). 
-\TODO{Numbers for this?}
+We find that approximately \TODO{XX\%} of the segments that are erroneously split have nearby endpoints  (Fig.~\ref{fig:merge_candidates}). 
 We make use of this fact to find merge candidates with the following two-pass pruning algorithm.
@@
 This algorithm produces a set of segments to consider for merging. Only these pairs have a corresponding edge in the constructed graph.
-\TODO{From Daniel: this sounds like a double threshold to me.. imho 1-2 sentences without formulas is clearer?}
 
 \subsection{Edge Weights Assignment}
+\label{sec:edge-weights}
 We assign edge weights $w_e$ to each edge where the weight corresponds to the probability that two nodes belong to the same neuron.
@@
 
-\subsection{Graph Partitioning}
+\subsection{Graph Clustering}
 
@@
 Traditional hierarchical clustering algorithms do not rely on such constraints but consider local decisions independently.
+We enforce a global constraint that neurons are tree-structured and should not contain cycles. 
 The multicut problems returns a series of ``collapsed'' edges between nodes that belong to the same neuron.
 We iterate over these edges in order of the probability of merge generated by our CNN. 
-\TODO{HOW DO WE ACCOMPLISH THIS}
+We ``collapse'' the edge only if it does not create a cycle in the graph.

### 2018-03-12 papers/eccv2018/3_evaluation.tex
papers: major updates to methods

@@
 % !TEX root =  paper.tex
-\section{Experimental Results}
-\TODO{right now, too many subsections. shall we break it into "Setup" and "Results"}
+\section{Experiments}
+
 We evaluate our method by comparing it to a state-of-the-art pixel-based reconstruction approach using datasets from mouse and fly brains.
@@
 
+\paragraph{Fib-25.}
+The Fib-25 dataset comes from the visual system of a \textit{Drosophila} fly~\cite{takemura2015synaptic}.
+This sample is imaged at a resolution of $\SI[product-units=single]{8 x 8 x 8}{\nano\meter}^3$ and has $2588 \times 2108 \times 2876$ voxels representing a volume of $\SI[product-units=single]{23.0 x 16.9 x 23.0}{\micro\meter}^3$.
+There is currently a reconstruction challenge based on this sample.
+
 \subsection{Pixel-Based Segmentations}
@@
 For the Kasthuri dataset, we used the segmentation pipeline from Funke et al.~\cite{funke2017deep}. 
-We first trained a 3D affinity prediction U-Net model~\cite{ronneberger2015u} with Malis loss~\cite{Turaga:2009} and applied the watershed and agglomeration method~\cite{funke2017deep} to obtain the final segmentation result.
-
+We first trained a 3D affinity prediction U-Net model~\cite{ronneberger2015u} with MALIS loss~\cite{Turaga:2009} and applied the watershed and agglomeration method~\cite{funke2017deep} to obtain the final segmentation result.
 For the FlyEM data, based on the authors' suggestion~\cite{takemura2017connectome}, we applied a context-aware delayed agglomeration algorithm~\cite{10.1371/journal.pone.0125825} that shows improved performance on this dataset over the pipeline used in the original publication.
@@
 We used exactly the same parameters as the publicly available code for this algorithm.
+For the Fib-25 challenge dataset, we use the segmentation from Funke et al. as our input~\cite{funke2017deep}.
 
@@
 
-We use half of the Kasthuri dataset for training and validation. 
+We use half of the Kasthuri and FlyEM datasets\footnote{Since the FlyEM datasets have significantly fewer examples, we initialize the network with the weights from the Kasthuri training and have an initial learning rate of $10^{-4}$.} for training and validation.
 We train on 80\% of the potential merge candidates for this volume.
@@
 
-\TODO{we don't have space for the table for training parameters: move to supp}
 \begin{table}[h!]
@@
 We have 20,000 such examples per epoch.
+
+\subsection{Error Metric}
+\label{sec:variation-of-information}
+
+We evaluate the performance of the different methods using the split variation of information (VI)~\cite{meila2003comparing}.
+Given a ground truth labeling $GT$ and our automatically reconstructed segmentation $SG$, over- and under-segmentation are quantified by the conditional entropies $H(GT | SG)$ and $H(SG | GT)$, respectively.
+Since we are measuring the entropy between two clusterings, lower VI scores are better.

### 2018-03-12 papers/eccv2018/3_evaluation.tex

@@
 For the Kasthuri dataset, we used the segmentation pipeline from Funke et al.~\cite{funke2017deep}. 
-We first trained a 3D affinity prediction U-Net model~\cite{ronneberger2015u} with MALIS loss~\cite{Turaga:2009} and applied the watershed and agglomeration method~\cite{funke2017deep} to obtain the final segmentation result.
-For the FlyEM data, based on the authors' suggestion~\cite{takemura2017connectome}, we applied a context-aware delayed agglomeration algorithm~\cite{10.1371/journal.pone.0125825} that shows improved performance on this dataset over the pipeline used in the original publication.
+We first train a 3D affinity prediction U-Net model~\cite{ronneberger2015u} with MALIS loss~\cite{Turaga:2009} and apply the watershed and agglomeration method~\cite{funke2017deep} to obtain the final segmentation result.
+For the FlyEM data, based on the authors' suggestion~\cite{takemura2017connectome}, we apply a context-aware delayed agglomeration algorithm~\cite{10.1371/journal.pone.0125825} that shows improved performance on this dataset over the pipeline used in the original publication.
 This segmentation framework learns voxel and supervoxel classifiers with an emphasis to minimize under-segmentation error. 

### 2018-03-12 papers/eccv2018/4_results.tex

--- 2018-03-09 papers/eccv2018/4_results.tex
@@
 % !TEX root =  paper.tex
+\section{Results}
 
@@
 
-\subsection{Error Metric}
-\label{sec:variation-of-information}
-
-We evaluate the performance of the different methods using the split variation of information (VI)~\cite{meila2003comparing}.
-Given a ground truth labeling $GT$ and our automatically reconstructed segmentation $SG$, over- and under-segmentation are quantified by the conditional entropies $H(GT | SG)$ and $H(SG | GT)$, respectively.
-Since we are measuring the entropy between two clusterings, lower VI scores are better.
-
 \subsection{Variation of Information Results}
@@
 Scores closer to the origin are better for this metric, and in every instance our results are below the green curve.
-We see significant improvements on the Kasthuri datasets (VI split reduction of \TODO{XX}\% and \TODO{XX}\% on the training and testing datasets respectively) and more modest improvements on the FlyEM datasets (reduction of \TODO{XX}\% and \TODO{XX}\%).
-\TODO{FIX: This is because the baseline segmentation algorithm for the isotropic FlyEM data (Sec.~\ref{sec:neuroproof}) performs much better, reducing the potential for improvements. 
-Isotropic datasets are easier to segment using state-of-the-art region-based methods than anisotropic ones~\cite{plaza2014annotating}.}
+We see significant improvements on the Kasthuri datasets (VI split reduction of \TODO{XX}\%) and more modest improvements on the FlyEM dataset (reduction of \TODO{XX}\%) and Fib-25 dataset (reduction of \TODO{XX}\%).
 
-Fig.~\ref{fig:qualitative-results} (left) shows successful merges on the Kasthuri Vol. 2 dataset. 
+Fig.~\ref{fig:qualitative-results} (left) shows successful merges on the Kasthuri dataset. 
 Several of these examples combine multiple consecutive segments that span the volume.
@@
 Table~\ref{table:skeletonization} shows the results for our edge generation including the number of missed neighbors and potential penalty in VI score.
-\TODO{augment table}
 We present additional analysis of the skeletonization parameters in the supplemental material.
@@
 	\small
-	\begin{tabular}{c c c} \hline
-		\textbf{Dataset} & \textbf{Baseline} & \textbf{After Pruning} \\ \hline
-		Kasthuri Training & 763 / 21,242 & 753 / 3,459 \\
-		Kasthuri Vol. 2 & 1,010 / 26,073 & 904 / 4,327 \\
-		FlyEM Vol. 1 & 269 / 14,875 & 262 / 946 \\
-		FlyEM Vol. 2 & 270 / 16,808 & 285 / 768 \\ \hline
+	\begin{tabular}{c c c c} \hline
+		\textbf{Dataset} & \textbf{Segment Adjacency} & \textbf{Skeleton Pruning} & \textbf{Missed Split Errors} \\ \hline
+		Kasthuri Training & 763 / 21,242 & 753 / 3,459 & \\
+		Kasthuri Vol. 2 & 1,010 / 26,073 & 904 / 4,327 & \\
+		FlyEM Vol. 1 & 269 / 14,875 & 262 / 946 & \\
+		FlyEM Vol. 2 & 270 / 16,808 & 285 / 768 & \\ \hline
 		%		Kasthuri Vol. 1 & 763 / 21242 (3.47\%) & 753 / 3459 (17.88\%) \\
@@
 	\caption{The results of our graph pruning approach compared to the baseline graph with all adjacent regions.
-We show the number of true merge locations (e.g., 763) compared to total number of edges in the graph (e.g., 21,242) for each case.}
+We show the number of true merge locations (e.g., 763) compared to total number of edges in the graph (e.g., 21,242) for each case.
+The number of missed splits corresponds to the number of split errors that our method misses compared to an adjacency matrix.}
 	\label{table:skeletonization}
@@
 Fig.~\ref{fig:receiver-operating-characteristic} shows the receiver operating characteristic (ROC) curve of our CNN classifier for all test datasets.
-\TODO{As shown by the ROC curve, the test results on the Kasthuri data are better than the results for FlyEM.
+As shown by the ROC curve, the test results on the Kasthuri data are better than the results for FlyEM.
 We believe this is in part because of the differences in the datasets (i.e., isotropy and $xy$ resolution).
-To test this hypothesis, we also evaluate the performance of the FlyEM datasets when the network trains on FlyEM Vol.
-1 and infers on FlyEM Vol.
-2.\footnote{Since the FlyEM datasets have significantly fewer examples, we initialize the network with the weights from the Kasthuri training and have an initial learning rate of $10^{-4}$.}
-The blue dotted curve in the figure shows a slight performance increase in this case.
-However, the improvement is minor, which led us to use the CNN trained on the anisotropic data for the rest of our experiments.
--- FIX THIS, also AUC values}
 
@@
 
-\paragraph{Neural Network Transference.}
+\paragraph{Generalization to Other Datasets.}
 
 Our neural network does not take as input the images or affinities to allow us to transfer network weights from one dataset to the next.
-Table~TODO{X} shows the result when training on the FlyEM data and inferring on the Kasthuri data and vice versa.
+Table~\TODO{X} shows the result when training on the FlyEM data and inferring on the Kasthuri data and vice versa.
 The classification results are reasonable despite the fact that the datasets vary in resolution and even animal type.
@@
 The graph optimization strategy using multicut increases our accuracy over using just the CNN.
-Table \ref{table:multicut} shows the changes in precision, recall, and accuracy for all four datasets compared to the CNN.
-The precision increases on each dataset, although the recall decreases on all but one of the datasets.Since it is more difficult to correct merge errors than split errors, it is often desirable to sacrifice recall for precision.
+Table \ref{table:multicut} shows the changes in precision, recall, and accuracy for all four datasets compared to the CNN with both the multicut and ``lifted'' multicut formulations.
+These results correspond to $\beta = 0.5$ (Sec.~\ref{sec:edge-weights}). 
+The precision increases on each dataset, although the recall decreases on all but one of the datasets.
+The ``lifted'' variant further accentuates this trend of increasing precision and accuracy at the expense of recall. 
+Since it is more difficult to correct merge errors than split errors, it is often desirable to sacrifice recall for precision.
 Over the three testing datasets, applying a graph-based partitioning strategy reduced the number of merge errors by \TODO{XX}\%, \TODO{XX}\% and \TODO{XX}\%, respectively.
@@
 	\small
-	\begin{tabular}{c c c c} \hline
-		\textbf{Dataset} & $\Delta$ \textbf{Precision} & $\Delta$ \textbf{Recall} & $\Delta$ \textbf{Accuracy} \\ \hline
-		Kasthuri Training & +3.61\% & -0.53\% & +0.60\% \\
-		Kasthuri Vol. 2 & +7.59\% & -1.77\% & +1.38\% \\
-		FlyEM Vol. 1 & +2.68\% & +0.76\% & +0.66\% \\
-		FlyEM Vol. 2 & +2.22\% & -1.05\% & +0.29\% \\ \hline
+	\begin{tabular}{c c c c | c c c} \hline
+		& \multicolumn{3}{c}{\textbf{Multicut}} & \multicolumn{3}{c}{\textbf{Lifted Multicut}} \\ \hline
+		\textbf{Dataset} & $\Delta$ \textbf{Precision} & $\Delta$ \textbf{Recall} & $\Delta$ \textbf{Accuracy} & $\Delta$ \textbf{Precision} & $\Delta$ \textbf{Recall} & $\Delta$ \textbf{Accuracy} \\ \hline
+		Kasthuri Training & +3.61\% & -0.53\% & +0.60\% & +3.61\% & -0.53\% & +0.60\% \\
+		Kasthuri Vol. 2 & +7.59\% & -1.77\% & +1.38\%  & +7.59\% & -1.77\% & +1.38\% \\
+		FlyEM Vol. 1 & +2.68\% & +0.76\% & +0.66\% & +2.68\% & +0.76\% & +0.66\% \\
+		FlyEM Vol. 2 & +2.22\% & -1.05\% & +0.29\% & +2.22\% & -1.05\% & +0.29\% \\ \hline
 	\end{tabular}
@@
 
-\TODO{How does using lifted-multicut improve the results!}
+Our post-processing method to agglomerate segments while enforcing the acyclic nature of our graph additionally improves precision by $\TODO{XX}\%$ on average while only costing $\TODO{XX}\%$ in recall.
+Note that our post-processing strategy by design cannot increase the recall.

### 2018-03-12 transforms/cpp-seg2gold.cpp
seg2gold: improved memory constraints

@@ -3,7 +3,7 @@
 #include <map>
 
 
-long *CppMapping(long *segmentation, int *gold, long nentries, double low_threshold, double high_threshold)
+long *CppMapping(long *segmentation, int *gold, long nentries, double match_threshold, double nonzero_threshold)
 {
     // find the maximum segmentation value
     long max_segmentation_value = 0;
@@ -25,49 +25,68 @@ long *CppMapping(long *segmentation, int *gold, long nentries, double low_thresh
     unsigned long *nvoxels_per_segment = new unsigned long[max_segmentation_value];
     for (long iv = 0; iv < max_segmentation_value; ++iv)
         nvoxels_per_segment[iv] = 0;
+    for (long iv = 0; iv < nentries; ++iv)
+      nvoxels_per_segment[segmentation[iv]]++;
+
+    std::map<long, std::map<long, long> > seg2gold_overlap = std::map<long, std::map<long, long> >();	
+    for (long is = 0; is < max_segmentation_value; ++is) {
+      if (nvoxels_per_segment[is]) { seg2gold_overlap.insert(std::pair<long, std::map<long, long> >(is, std::map<long, long>())); }
+    }
+    
+    for (long iv = 0; iv < nentries; ++iv) {
+      seg2gold_overlap[segmentation[iv]][gold[iv]]++;
+    }
+    
+
 
     /* TODO way too memory expensive */
-    unsigned long **seg2gold_overlap = new unsigned long *[max_segmentation_value];
-    for (unsigned long is = 0; is < max_segmentation_value; ++is) {
-        seg2gold_overlap[is] = new unsigned long[max_gold_value];
-        for (unsigned long ig = 0; ig < max_gold_value; ++ig) {
-            seg2gold_overlap[is][ig] = 0;
+    long **seg2gold_overlap_old = new long *[max_segmentation_value];
+    for (long is = 0; is < max_segmentation_value; ++is) {
+        seg2gold_overlap_old[is] = new long[max_gold_value];
+        for (long ig = 0; ig < max_gold_value; ++ig) {
+            seg2gold_overlap_old[is][ig] = 0;
         }
     }
 
     // iterate over every voxel
     for (long iv = 0; iv < nentries; ++iv) {
-        nvoxels_per_segment[segmentation[iv]]++;
-        seg2gold_overlap[segmentation[iv]][gold[iv]]++;
+      seg2gold_overlap_old[segmentation[iv]][gold[iv]]++;
     }
 
[…]

### 2018-03-12 transforms/cpp-seg2gold.h

@@ -1,1 +1,1 @@
-long *CppMapping(long *segmentation, int *gold, long nentries, double low_threshold, double high_threshold);
+long *CppMapping(long *segmentation, int *gold, long nentries, double match_threshold, double nonzero_threshold);

### 2018-03-12 transforms/seg2gold.pyx

@@ -4,9 +4,9 @@ import numpy as np
 import ctypes
 
 cdef extern from 'cpp-seg2gold.h':
-    long *CppMapping(long *segmentation, int *gold, long nentries, double low_threshold, double high_threshold)
+    long *CppMapping(long *segmentation, int *gold, long nentries, double match_threshold, double nonzero_threshold)
 
-def Mapping(segmentation, gold, low_threshold=0.10, high_threshold=0.80):
+def Mapping(segmentation, gold, match_threshold=0.70, nonzero_threshold=0.40):
     cdef np.ndarray[long, ndim=3, mode='c'] cpp_segmentation
     cpp_segmentation = np.ascontiguousarray(segmentation, dtype=ctypes.c_int64)
     cdef np.ndarray[int, ndim=3, mode='c'] cpp_gold
@@ -14,7 +14,7 @@ def Mapping(segmentation, gold, low_threshold=0.10, high_threshold=0.80):
 
     max_segmentation = np.amax(segmentation) + 1
 
-    cdef long *mapping = CppMapping(&(cpp_segmentation[0,0,0]), &(cpp_gold[0,0,0]), segmentation.size, low_threshold, high_threshold)
+    cdef long *mapping = CppMapping(&(cpp_segmentation[0,0,0]), &(cpp_gold[0,0,0]), segmentation.size, match_threshold, nonzero_threshold)
 
     cdef long[:] tmp_mapping = <long[:max_segmentation]> mapping;
 

### 2018-03-12 cnns/skeleton/generate_features.py
skeleton: memory efficient generate features

@@ -122,8 +122,17 @@ def GenerateFeatures(prefix, threshold, maximum_distance, network_distance, endp
     endpoint_pairs = {}
 
     # find the smallest pair between endpoints
-    smallest_distances = (endpoint_distance + 1) * np.ones((max_label, max_label), dtype=np.float32)
-    midpoints = np.zeros((max_label, max_label, 3), dtype=np.int32)
+    smallest_distances = {}
+    midpoints = {}
+
+    #smallest_distances = (endpoint_distance + 1) * np.ones((max_label, max_label), dtype=np.float32)
+    #midpoints = np.zeros((max_label, max_label, 3), dtype=np.int32)
+
+    for ie, endpoint in enumerate(endpoints):
+        label = endpoint.label
+        for neighbor_label in endpoint_candidates[ie]:
+            smallest_distances[(label,neighbor_label)] = endpoint_distance + 1
+            smallest_distances[(neighbor_label,label)] = endpoint_distance + 1
 
     for ie, endpoint in enumerate(endpoints):
         # get the endpoint location
@@ -135,8 +144,8 @@ def GenerateFeatures(prefix, threshold, maximum_distance, network_distance, endp
                 # get the distance
                 deltas = endpoint.WorldPoint(world_res) - neighbor_endpoint.WorldPoint(world_res)
                 distance = math.sqrt(deltas[IB_Z] * deltas[IB_Z] + deltas[IB_Y] * deltas[IB_Y] + deltas[IB_X] * deltas[IB_X])
-
-                if distance < smallest_distances[label, neighbor_label]:
+                
+                if distance < smallest_distances[(label, neighbor_label)]:
                     midpoint = (endpoint.GridPoint() + neighbor_endpoint.GridPoint()) / 2
 
                     # make sure the bounding box fits
@@ -146,15 +155,15 @@ def GenerateFeatures(prefix, threshold, maximum_distance, network_distance, endp
                         if midpoint[dim]+network_radii[dim] > grid_size[dim]: valid_location = False
                     if not valid_location: continue
             
-                    smallest_distances[label,neighbor_label] = distance
-                    smallest_distances[neighbor_label,label] = distance
+                    smallest_distances[(label,neighbor_label)] = distance
+                    smallest_distances[(neighbor_label,label)] = distance
 
                     # add to the dictionary
[…]

### 2018-03-12 transforms/cpp-seg2gold.cpp
transforms: fixed major memory leak

@@ -37,31 +37,6 @@ long *CppMapping(long *segmentation, int *gold, long nentries, double match_thre
       seg2gold_overlap[segmentation[iv]][gold[iv]]++;
     }
     
-
-
-    /* TODO way too memory expensive */
-    long **seg2gold_overlap_old = new long *[max_segmentation_value];
-    for (long is = 0; is < max_segmentation_value; ++is) {
-        seg2gold_overlap_old[is] = new long[max_gold_value];
-        for (long ig = 0; ig < max_gold_value; ++ig) {
-            seg2gold_overlap_old[is][ig] = 0;
-        }
-    }
-
-    // iterate over every voxel
-    for (long iv = 0; iv < nentries; ++iv) {
-      seg2gold_overlap_old[segmentation[iv]][gold[iv]]++;
-    }
-
-    for (long is = 0; is < max_segmentation_value; ++is) {
-      for (long ig = 0; ig < max_gold_value; ++ig) {
-	if (seg2gold_overlap_old[is][ig]) 
-	  if (seg2gold_overlap[is][ig] != seg2gold_overlap_old[is][ig]) printf("NO!\n");
-      }
-    }
-	  
-
-    
     // create the mapping
     long *segmentation_to_gold = new long[max_segmentation_value];
     for (long is = 0; is < max_segmentation_value; ++is) {

### 2018-03-12 cnns/skeleton/generate_features.py
generate_features: updates from Odyssey

@@ -171,7 +171,7 @@ def GenerateFeatures(prefix, threshold, maximum_distance, network_distance, endp
     undetermined_candidates = []
 
     for ie, match in enumerate(endpoint_pairs):
-        if (ie % 100 == 0): print '{}/{}'.format(ie, len(endpoint_pairs))
+        if (ie % 1 == 0): print '{}/{}'.format(ie, len(endpoint_pairs))
         endpoint_one = endpoint_pairs[match][0]
         endpoint_two = endpoint_pairs[match][1]
 
@@ -214,17 +214,18 @@ def GenerateFeatures(prefix, threshold, maximum_distance, network_distance, endp
     # perform some tests to see how well this method can do
     max_value = np.amax(segmentation) + 1
     union_find = [unionfind.UnionFindElement(iv) for iv in range(max_value)]
-
+    print 'A'
     # iterate over all collapsed edges
     for candidate in positive_candidates:
         label_one, label_two = candidate.labels
         unionfind.Union(union_find[label_one], union_find[label_two])
-    
+    print 'B'
     # create a mapping for the labels
     mapping = np.zeros(max_value, dtype=np.int64)
     for iv in range(max_value):
         mapping[iv] = unionfind.Find(union_find[iv]).label
+    print 'C'
     segmentation = seg2seg.MapLabels(segmentation, mapping)
-
-    comparestacks.CremiEvaluate(segmentation, gold, dilate_ground_truth=1, mask_ground_truth=True, filtersize=0)
-
+    print 'D'
+    comparestacks.CremiEvaluate(segmentation, gold, dilate_ground_truth=1, mask_ground_truth=True, mask_segmentation=True, filtersize=0)
+    print 'E'

### 2018-03-12 papers/eccv2018/1_related_work.tex
papers: some updates based on HP comments

@@
 
-\paragraph{Pixel-based methods.}
+\subsubsection{Pixel-based methods}
 A significant amount of connectomics research considers the problem of extracting segmentation information at the pixel (i.e., voxel) level from the raw EM images. 
@@
 
-\paragraph{Region-based methods.}
+\subsubsection{Region-based methods}
 
@@
 
-\paragraph{Error-correction methods.}
+\subsubsection{Error-correction methods}
 Additional research builds on top of these region-based methods to correct errors in the segmentation either using human proofreading~\cite{haehn2014design,haehn2017guided,mojo2} or automatic methods~\cite{rolnick2017morphological,error_correction_using_CNN}.

### 2018-03-12 papers/eccv2018/4_results.tex
papers: some updates based on HP comments

@@
 	\centering
-	\includegraphics[width=0.45\linewidth]{./figures/variation_of_information-microns-train-600.png}
-	\includegraphics[width=0.45\linewidth]{./figures/variation_of_information-microns-test-600.png}
-	\includegraphics[width=0.45\linewidth]{./figures/variation_of_information-FlyEM-train-600.png}
-	\includegraphics[width=0.45\linewidth]{./figures/variation_of_information-FlyEM-test-600.png}
+	\includegraphics[width=0.32\linewidth]{./figures/variation_of_information-microns-test-600.png}
+	\includegraphics[width=0.32\linewidth]{./figures/variation_of_information-FlyEM-train-600.png}
+	\includegraphics[width=0.32\linewidth]{./figures/variation_of_information-FlyEM-test-600.png}
 	\caption{VI scores of our method (red) compared to the baseline segmentation (green) and an oracle (blue) that optimally partitions the graph based on ground truth.
@@
 	\end{minipage}
-	\caption{(left) Segments of neurons that were correctly merged by our method. (right) Circles indicate areas of wrong merges by our method (red) or by the initial pixel-based segmentation (blue).}
+	\caption{(left) Segments of neurons before they were correctly merged by our method.
+(right) Circles indicate areas of wrong merges by our method (red) or by the initial pixel-based segmentation (blue).}
 	\label{fig:qualitative-results}
@@
 
-\paragraph{Inference Augmentation.}
+\subsubsection{Inference Augmentation}
 
@@
 When computing the probability to merge two segments, we input the initial segment into our CNN as well as \TODO{XX} randomly rotated and flipped examples (in the same manner as training augmentation).
-This produces some additional increase in overall accuracy (Table ~\ref{table:inference-augmentation}). 
+This produces some additional increase in overall accuracy (Figure ~\ref{fig:receiver-operating-characteristic}).
 The supplemental material contains experiments showing the trade-offs between increased accuracy and runtime when using these augmentation strategies.
-
-\begin{table}
-	\begin{center}
-		\begin{tabular}{c | c c c}
-			Dataset & Precision & Recall & Accuracy \\ \hline
-			Kasthuri & & & \\
-			FlyEM Vol. 1 & & & \\
-			FlyEM Vol. 2 & & & 
-		\end{tabular}
-		\caption{Data augmentation during test time increases the precision, recall, and accuracy of all three datasets.}
-		\label{table:inference-augmentation}
-	\end{center}
-\end{table}
 
@@
 	\centering
-	\includegraphics[width=0.45\linewidth]{./figures/receiver-operating-characteristic.jpg}
+	\includegraphics[width=0.45\linewidth]{./figures/receiver-operating-characteristic.jpg}		\includegraphics[width=0.45\linewidth]{./figures/receiver-operating-characteristic.jpg}
 	\caption{The receiver operating characteristic (ROC) curves of our classifier on three connectomics datasets.
@@
 
-\paragraph{Generalization to Other Datasets.}
+\subsubsection{Generalization to Other Datasets}
 
@@
 Note that our post-processing strategy by design cannot increase the recall.
+
+\subsection{Computational Performance}

### 2018-03-12 papers/eccv2018/supplemental/classifier.tex
papers: some updates based on HP comments

@@
 
+\begin{table}[h!]
+	\centering
+	\begin{tabular}{l l} \hline
+		\textbf{Parameters} & \textbf{Values} \\ \hline
+		Loss Function & Mean Squared Error \\
+		Optimizer & SGD  with Nesterov Momentum \\
+		Momentum & 0.9 \\
+		Initial Learning Rate & 0.0001 \\
+		Decay Rate & $5 * 10^{-8}$ \\
+		Activation & LeakyReLU $(\alpha = 0.001)$ \\
+		Kernel Sizes & $3 \times 3 \times 3$ \\
+		Filter Sizes & $16 \to 32 \to 64$ \\ \hline
+	\end{tabular}
+	\caption{Training parameters.}
+	\label{table:architecture}
+\end{table}
+
 \subsection{Training Augmentation}

### 2018-03-12 papers/eccv2018/4_results.tex
trying different feature generation

@@
 \subsection{Computational Performance}
+
+\subsubsection{System} All performance experiments ran on an Intel Core i7-6800K CPU 3.40 GHz with a Titan X Pascal GPU.
+All code is written in Python and will be freely available upon paper decision.
+We use the Keras deep learning library for our neural networks with Theano backend and cuDNN 7 acceleration for CUDA 8.0.

### 2018-03-12 cnns/skeleton/generate_features.py

@@ -125,9 +125,6 @@ def GenerateFeatures(prefix, threshold, maximum_distance, network_distance, endp
     smallest_distances = {}
     midpoints = {}
 
-    #smallest_distances = (endpoint_distance + 1) * np.ones((max_label, max_label), dtype=np.float32)
-    #midpoints = np.zeros((max_label, max_label, 3), dtype=np.int32)
-
     for ie, endpoint in enumerate(endpoints):
         label = endpoint.label
         for neighbor_label in endpoint_candidates[ie]:
@@ -225,6 +222,9 @@ def GenerateFeatures(prefix, threshold, maximum_distance, network_distance, endp
     for iv in range(max_value):
         mapping[iv] = unionfind.Find(union_find[iv]).label
     segmentation = seg2seg.MapLabels(segmentation, mapping)
+
+    import gc
+    gc.collect()
 
     comparestacks.CremiEvaluate(segmentation, gold, dilate_ground_truth=1, mask_ground_truth=True, filtersize=0)
 

### 2018-03-13 papers/eccv2018/0_introduction.tex

@@
 
-We present a \textit{global\TODO{?} graph-based} method that builds on the outputs of bottom-up pixel-based segmentation approaches. 
+We present a \textit{top-down graph-based} method that builds on the outputs of bottom-up pixel-based segmentation approaches. 
 We first extract skeletons from labels in the input segmentation and generate a simplified graph (Fig.~\ref{fig:teaser}a). 
@@
 
-This work makes the following contributions: (1) a novel top-down\TODO{?} framework that extracts graphs from skeletonized 3D networks for improved neural reconstruction of connectomics data; (2) a region-based CNN classifier to detect errors; (3) an empirical evaluation of our method on several connectomics datasets; (4) improved performance over a state-of-the-art pixel-based reconstruction approach on average by \TODO{XX}\% with suitable running times.
+This work makes the following contributions: (1) a novel top-down framework that extracts graphs from skeletonized 3D networks for improved neural reconstruction of connectomics data; (2) a region-based CNN classifier to detect errors; (3) an empirical evaluation of our method on several connectomics datasets; (4) improved performance over a state-of-the-art pixel-based reconstruction approach on average by \TODO{XX}\% with suitable running times.

### 2018-03-13 papers/eccv2018/3_evaluation.tex

@@
 
-\paragraph{Kasthuri.}
+Our proposed method is designed for very large connectomics datasets. 
+Popular challenge datasets such as CREMI and SNEMI3D are simply too small for any noticeable change. 
+The following three datasets contain from 4 to 40 times more volume than the CREMI datasets.
+
+\subsubsection{Kasthuri}
 The Kasthuri dataset consists of scanning electron microscope images of the neocortex of a mouse brain~\cite{kasthuri2015saturated}. 
@@
 
-\paragraph{FlyEM.}
+\subsubsection{FlyEM}
 The FlyEM dataset comes from the mushroom body of a 5-day old adult male \textit{Drosophila} fly imaged by a focused ion-beam milling scanning electron microscopy~\cite{takemura2017connectome}.
@@
 
-\paragraph{Fib-25.}
+\subsubsection{Fib-25}
 The Fib-25 dataset comes from the visual system of a \textit{Drosophila} fly~\cite{takemura2015synaptic}.
@@
 The supplemental material includes information on the experiments that determined these final parameters. 
-Table~\ref{table:architecture} provides the parameters of the final network. 
+We provide all parameters of the final network in the supplemental material. 
 There are \TODO{X,XXX,XXX} learnable parameters in our final architecture. 
@@
 
-\begin{table}[h!]
-	\centering
-	\begin{tabular}{l l} \hline
-		\textbf{Parameters} & \textbf{Values} \\ \hline
-		Loss Function & Mean Squared Error \\
-		Optimizer & SGD  with Nesterov Momentum \\
-		Momentum & 0.9 \\
-		Initial Learning Rate & 0.0001 \\
-		Decay Rate & $5 * 10^{-8}$ \\
-		Activation & LeakyReLU $(\alpha = 0.001)$ \\
-		Kernel Sizes & $3 \times 3 \times 3$ \\
-		Filter Sizes & $16 \to 32 \to 64$ \\ \hline
-	\end{tabular}
-	\caption{Training parameters.}
-	\label{table:architecture}
-\end{table}
-
-\paragraph{Training Augmentation.}
+\subsubsection{Training Augmentation.}
 
@@
 
-\subsection{Error Metric}
+\subsection{Error Metrics}
 \label{sec:variation-of-information}
@@
 Since we are measuring the entropy between two clusterings, lower VI scores are better.
+
+We use both precision and recall to evaluate the convolutional neural network and multicut outputs. 
+Since our method attempts to only correct \textit{split errors}, we define a true positive as a pair of segments that are correctly merged together after our pipeline.

### 2018-03-13 cnns/skeleton/generate_features.py
removed garbage collection

@@ -221,10 +221,7 @@ def GenerateFeatures(prefix, threshold, maximum_distance, network_distance, endp
     mapping = np.zeros(max_value, dtype=np.int64)
     for iv in range(max_value):
         mapping[iv] = unionfind.Find(union_find[iv]).label
+   
     segmentation = seg2seg.MapLabels(segmentation, mapping)
-
-    import gc
-    gc.collect()
-
     comparestacks.CremiEvaluate(segmentation, gold, dilate_ground_truth=1, mask_ground_truth=True, filtersize=0)
 

### 2018-03-13 cnns/skeleton/generate_features.py
generate features: reverted to original method

@@ -175,8 +175,6 @@ def GenerateFeatures(prefix, threshold, maximum_distance, network_distance, endp
         label_one = endpoint_one.label
         label_two = endpoint_two.label
 
-        if (label_one > label_two): continue
-
         # extract a bounding box around this midpoint
         midz, midy, midx = midpoints[(label_one,label_two)]
 
@@ -184,6 +182,7 @@ def GenerateFeatures(prefix, threshold, maximum_distance, network_distance, endp
         extracted_gold = gold[midz-network_radii[IB_Z]:midz+network_radii[IB_Z],midy-network_radii[IB_Y]:midy+network_radii[IB_Y],midx-network_radii[IB_X]:midx+network_radii[IB_X]]
 
         extracted_seg2gold_mapping = seg2gold.Mapping(extracted_segmentation, extracted_gold, match_threshold=0.70, nonzero_threshold=0.40)
+
         gold_one = extracted_seg2gold_mapping[label_one]
         gold_two = extracted_seg2gold_mapping[label_two]
 
@@ -222,5 +221,5 @@ def GenerateFeatures(prefix, threshold, maximum_distance, network_distance, endp
     for iv in range(max_value):
         mapping[iv] = unionfind.Find(union_find[iv]).label
    
-    segmentation = seg2seg.MapLabels(segmentation, mapping)
-    comparestacks.CremiEvaluate(segmentation, gold, dilate_ground_truth=1, mask_ground_truth=True, filtersize=0)
+    # segmentation = seg2seg.MapLabels(segmentation, mapping)
+    # comparestacks.CremiEvaluate(segmentation, gold, dilate_ground_truth=1, mask_ground_truth=True, filtersize=0)

### 2018-03-13 cnns/skeleton/oracle.py

@@ -5,34 +5,11 @@ from ibex.utilities import dataIO
 from ibex.transforms import seg2seg, seg2gold
 from ibex.cnns.skeleton.util import FindCandidates
 from ibex.data_structures import unionfind
-from PixelPred2Seg import comparestacks
+from ibex.evaluation import comparestacks
 
 
 
 def Oracle(prefix, threshold, maximum_distance, network_distance):
-    segmentation = dataIO.ReadSegmentationData(prefix)
-    gold = dataIO.ReadGoldData(prefix)
-
-    seg2gold_mapping = seg2gold.Mapping(segmentation, gold, low_threshold=0.10, high_threshold=0.80)
-
-    # connect all segment that have the same gold label
-    max_segmentation = np.max(segmentation) + 1
-    mapping = np.zeros(max_segmentation, dtype=np.int64)
-
-    nzeros = 1
-    for iv in range(max_segmentation):
-        if not seg2gold_mapping[iv]:
-            mapping[iv] = max_segmentation + nzeros
-            nzeros += 1
-        else:
-            mapping[iv] = seg2gold_mapping[iv]
-
-    oracle_segmentation = seg2seg.MapLabels(segmentation, mapping)
-    comparestacks.Evaluate(oracle_segmentation, gold)
-
-    return
-
-
     # get all of the candidates
     candidates = FindCandidates(prefix, threshold, maximum_distance, network_distance, inference=True)  
     ncandidates = len(candidates)

### 2018-03-13 data_structures/skeleton_formats.py

@@ -215,25 +215,6 @@ class SWCSkeleton:
             if endpoints[ie]:
                 self.endpoints.append(self.joints[ie])
 
-        # go though all endpoints and add their parents
-        augmented_endpoints = []
-        for endpoint in self.endpoints:
-            if endpoint.parent_sample == -1: continue
-            augmented_endpoints.append(self.joints[endpoint.parent_sample - 1])
-
-        for joint in self.joints:
-            if joint.parent_sample == -1: continue
-            parent = self.joints[joint.parent_sample - 1]
-            for endpoint in self.endpoints:
-                if parent.sample_number == endpoint.sample_number:
-                    augmented_endpoints.append(joint)
-        self.endpoints = list(set(self.endpoints + augmented_endpoints))
-       
-        for ie1 in range(len(self.endpoints)):
-            for ie2 in range(ie1 + 1, len(self.endpoints)):
-                assert (self.endpoints[ie1].sample_number != self.endpoints[ie2].sample_number)
-
-
     # return the kth endpoint
     def EndPoint(self, k):
         assert (0 <= k and k < self.NEndPoints())

### 2018-03-13 algorithms/util.py
updated figures for the paper

@@ -17,7 +17,7 @@ def RetrieveCandidates(prefix, model_prefix, threshold, maximum_distance, endpoi
     ncandidates = len(candidates)
 
     # read the probabilities foor this candidate
-    probabilities_filename = '{}-{}-{}-{}nm.probabilities'.format(model_prefix, prefix, threshold, maximum_distance)
+    probabilities_filename = '{}-{}-{}-{}nm-{}nm-{}nm.probabilities'.format(model_prefix, prefix, threshold, maximum_distance, endpoint_distance, network_distance)
     with open(probabilities_filename, 'rb') as fd:
         nprobabilities, = struct.unpack('i', fd.read(4))
         assert (nprobabilities == ncandidates)

### 2018-03-13 papers/eccv2018/2_method.tex
papers: some updates based on HP comments
papers: added second error case

@@
 	\includegraphics[width=0.32\linewidth]{./figures/split_error1.png}
-	\includegraphics[width=0.32\linewidth]{./figures/split_error2.png}		\includegraphics[width=0.32\linewidth]{./figures/merge_candidate2.png}
+	\includegraphics[width=0.32\linewidth]{./figures/split_error2.png}		\includegraphics[width=0.32\linewidth]{./figures/split_error3.png}
 	\caption{Three erroneously split segments.}
@@
 
-\paragraph{Post-processing}
+\subsubsection{Post-processing}
 
@@
 We iterate over these edges in order of the probability of merge generated by our CNN. 
-We ``collapse'' the edge only if it does not create a cycle in the graph.
+We ``collapse'' an edge only if it does not create a cycle in the graph.

### 2018-03-13 papers/eccv2018/4_results.tex
papers: added second error case

@@
 	\centering
-	\includegraphics[width=0.45\linewidth]{./figures/merge_candidate1.png}		\includegraphics[width=0.45\linewidth]{./figures/merge_candidate1.png}
-	\caption{Two false negative example of our method due to graph pruning.
-The distance between the endpoints (circled) of the two segments is too far to be flagged as a merge candidate.
-\TODO{SECOND EXAMPLE}}
+	\includegraphics[width=0.45\linewidth]{./figures/merge_candidate1.png}		\includegraphics[width=0.45\linewidth]{./figures/merge_candidate2.png}
+	\caption{Two false negative example of our method due to graph pruning. The distance between the endpoints (circled) of the two segments is too far to be flagged as a merge candidate.}
 	\label{fig:skeleton-results}

### 2018-03-13 cnns/skeleton/oracle.py
oracle: updated with new util functions

@@ -9,10 +9,10 @@ from ibex.evaluation import comparestacks
 
 
 
-def Oracle(prefix, threshold, maximum_distance, network_distance):
+def Oracle(prefix, threshold, maximum_distance, endpoint_distance, network_distance, filtersize=0):
     # get all of the candidates
-    candidates = FindCandidates(prefix, threshold, maximum_distance, network_distance, inference=True)  
-    ncandidates = len(candidates)
+    positive_candidates = FindCandidates(prefix, threshold, maximum_distance, endpoint_distance, network_distance, 'positive')  
+    ncandidates = len(positive_candidates)
 
     # read in all relevant information
     segmentation = dataIO.ReadSegmentationData(prefix)
@@ -24,9 +24,7 @@ def Oracle(prefix, threshold, maximum_distance, network_distance):
     union_find = [unionfind.UnionFindElement(iv) for iv in range(max_value)]
 
     # iterate over all candidates and collapse edges
-    for candidate in candidates:
-        if not candidate.ground_truth: continue
-
+    for candidate in positive_candidates:
         label_one = candidate.labels[0]
         label_two = candidate.labels[1]
 
@@ -37,11 +35,4 @@ def Oracle(prefix, threshold, maximum_distance, network_distance):
     for iv in range(max_value):
         mapping[iv] = unionfind.Find(union_find[iv]).label
 
-    # output the mapping
-    with open('tmp.txt', 'w') as fd:
-        fd.write('{}\n'.format(max_value))
-        for iv in range(max_value):
-            fd.write('{}\n'.format(mapping[iv]))
-
-
-    #comparestacks.Evaluate(segmentation, gold, filtersize=threshold, anisotropic=anisotropy)
+    comparestacks.CremiEvaluate(segmentation, gold, dilate_ground_truth=1, mask_ground_truth=True, mask_segmentation=False, filtersize=filtersize)

### 2018-03-13 cnns/skeleton/oracle.py
added ROC curves to classification

@@ -35,4 +35,5 @@ def Oracle(prefix, threshold, maximum_distance, endpoint_distance, network_dista
     for iv in range(max_value):
         mapping[iv] = unionfind.Find(union_find[iv]).label
 
+    segmentation = seg2seg.MapLabels(segmentation, mapping)
     comparestacks.CremiEvaluate(segmentation, gold, dilate_ground_truth=1, mask_ground_truth=True, mask_segmentation=False, filtersize=filtersize)

### 2018-03-13 papers/eccv2018/2_method.tex
papers: updated figures and generated results

@@
 Two segments $l_1$ and $l_2$ are considered adjacent if there is a pair of adjacent voxels with one labeled $l_1$ and the other labeled $l_2$.
-For example, pixel-based agglomeration methods such as mean agglomeration \TODO{CITE} or waterz \TODO{CITE} consider all pairs of adjacent segments for merging.
+For example, pixel-based agglomeration methods such as mean agglomeration~\cite{lee2017superhuman} or waterz~\cite{funke2017deep} consider all pairs of adjacent segments for merging.
 However, this method produces too many edges in the graph for graph-based optimization approaches. 

### 2018-03-13 papers/eccv2018/3_evaluation.tex
papers: updated figures and generated results

@@
 We train on 80\% of the potential merge candidates for this volume.
-We validate the CNN classifier on the remaining 20\% of candidates.
+We validate the CNN classifier on the remaining 20\% of the candidates.
 
@@
 We provide all parameters of the final network in the supplemental material. 
-There are \TODO{X,XXX,XXX} learnable parameters in our final architecture. 
+There are 2,313,969 learnable parameters in our final architecture. 
 All the parameters are randomly initialized following the Xavier uniform distribution~\cite{glorot2010understanding}. 
-Training concluded after \TODO{XXX} epochs.
+Training concluded after 1000 epochs.
 
@@
 Since our input is an existing segmentation of the EM images, there are very few training examples compared to per-pixel classifiers that can train on a unique window for each voxel. 
-The Kasthuri dataset represents a region of brain over $\SI[product-units=single]{800}{\micro\meter}^3$ in volume and only yields \TODO{700} positive merge examples and \TODO{7000} negative ones.
+The Kasthuri dataset represents a region of brain over $\SI[product-units=single]{800}{\micro\meter}^3$ in volume and only yields 640 positive merge examples and 4821 negative ones.
 To avoid overfitting our deep networks, we apply the following augmentations on the training examples.

### 2018-03-13 papers/eccv2018/4_results.tex
papers: updated figures and generated results

@@
 	\small
+	\setlength{\tabcolsep}{0.75em}
 	\begin{tabular}{c c c c} \hline
 		\textbf{Dataset} & \textbf{Segment Adjacency} & \textbf{Skeleton Pruning} & \textbf{Missed Split Errors} \\ \hline
-		Kasthuri Training & 763 / 21,242 & 753 / 3,459 & \\
-		Kasthuri Vol. 2 & 1,010 / 26,073 & 904 / 4,327 & \\
-		FlyEM Vol. 1 & 269 / 14,875 & 262 / 946 & \\
-		FlyEM Vol. 2 & 270 / 16,808 & 285 / 768 & \\ \hline
-		%		Kasthuri Vol. 1 & 763 / 21242 (3.47\%) & 753 / 3459 (17.88\%) \\
-		%		Kasthuri Vol. 2 & 1010 / 26073 (3.73\%) & 904 / 4327 (17.28\%) \\
-		%		FlyEM Vol. 1 & 269 / 14875 (1.78\%) & 262 / 946 (21.69\%) \\
-		%		FlyEM Vol. 2 & 270 / 16808 (1.58\%) & 285 / 768 (27.07\%)\\ \hline
+		Kasthuri &  & & \\
+		FlyEM &  &  & \\
+		FIB-25 &  & & \\ \hline
 	\end{tabular}
 	\caption{The results of our graph pruning approach compared to the baseline graph with all adjacent regions.
-We show the number of true merge locations (e.g., 763) compared to total number of edges in the graph (e.g., 21,242) for each case.
+We show the number of true merge locations (e.g., \TODO{XXX}) compared to total number of edges in the graph (e.g., \TODO{XXXXX}) for each case.
 The number of missed splits corresponds to the number of split errors that our method misses compared to an adjacency matrix.}
@@
 	\includegraphics[width=0.45\linewidth]{./figures/merge_candidate1.png}		\includegraphics[width=0.45\linewidth]{./figures/merge_candidate2.png}
-	\caption{Two false negative example of our method due to graph pruning. The distance between the endpoints (circled) of the two segments is too far to be flagged as a merge candidate.}
+	\caption{Two example segment pairs that we incorrectly prune from our graph. The distances between the circled endpoints are greater than our thresholds.}
 	\label{fig:skeleton-results}
@@
 Data augmentation at test time can improve accuracy results~\cite{zeng2017deepem3d,lee2017superhuman}.
-When computing the probability to merge two segments, we input the initial segment into our CNN as well as \TODO{XX} randomly rotated and flipped examples (in the same manner as training augmentation).
+When computing the probability to merge two segments, we input the initial segment into our CNN as well as 3 randomly rotated and flipped examples (in the same manner as training augmentation).
 This produces some additional increase in overall accuracy (Figure ~\ref{fig:receiver-operating-characteristic}).
@@
 	\small
+	\setlength{\tabcolsep}{0.3em}
 	\begin{tabular}{c c c c | c c c} \hline

### 2018-03-13 evaluation/classification.py
classificaiton: switched to built in evaluation functions

@@ -1,6 +1,7 @@
 import numpy as np
 from numba import jit
 
+from sklearn.metrics import auc, average_precision_score, precision_recall_curve, roc_curve
 
 
 @jit(nopython=True)
@@ -16,56 +17,14 @@ def Prob2Pred(probabilities, threshold=0.5):
 
 
 def PrecisionAndRecallCurve(ground_truth, probabilities):
-    results = sorted(zip(probabilities, ground_truth), reverse=True)
+    precisions, recalls, _ = precision_recall_curve(ground_truth, probabilities)
+    return precisions, recalls, average_precision_score(ground_truth, probabilities)
 
-    precisions = []
-    recalls = []
-
-    TP = 0
-    FP = 0
-    FN = 0
-    TN = 0
-
-    for (probability, label) in results:
-        if probability > 0.5 and label: TP += 1
-        if probability > 0.5 and not label: FP += 1
-        if probability < 0.5 and label: FN += 1
-        if probability < 0.5 and not label: TN += 1
-
-        if TP + FP == 0 or TP + FN == 0: continue
-        precisions.append(TP / float(TP + FP))
-        recalls.append(TP / float(TP + FN))
-
-    return precisions, recalls
-        
-    
     
 
 def ReceiverOperatingCharacteristicCurve(ground_truth, probabilities):
-    results = sorted(zip(probabilities, ground_truth), reverse=True)
-
-    true_positive_rates = []
-    false_positive_rates = []
-
-    TP = 0
-    FP = 0
-    FN = 0
-    TN = 0
-    
-    for (probability, label) in results:
-        if probability > 0.5 and label: TP += 1
-        if probability > 0.5 and not label: FP += 1
-        if probability < 0.5 and label: FN += 1
-        if probability < 0.5 and not label: TN += 1
-
-        if TP + FN == 0 or TN + FP == 0: continue
-        true_positive_rates.append(TP / float(TP + FN))
-        false_positive_rates.append(1.0 - TN / float(TN + FP))
-
-    true_positive_rates.append(0)
-    false_positive_rates.append(0)
-        
-    return true_positive_rates, false_positive_rates
+    false_positive_rates, true_positive_rates, _ = roc_curve(ground_truth, probabilities)
+    return false_positive_rates, true_positive_rates, auc(false_positive_rates, true_positive_rates)
     
     
     

### 2018-03-13 papers/eccv2018/4_results.tex
papers: updated ROC and P&R curves

@@
 	\centering
-	\includegraphics[width=0.45\linewidth]{./figures/receiver-operating-characteristic.jpg}		\includegraphics[width=0.45\linewidth]{./figures/receiver-operating-characteristic.jpg}
+	\includegraphics[width=0.45\linewidth]{./figures/receiver-operating-characteristic.png}		\includegraphics[width=0.45\linewidth]{./figures/precision-and-recall.png}
 	\caption{The receiver operating characteristic (ROC) curves of our classifier on three connectomics datasets.

### 2018-03-13 papers/eccv2018/2_method.tex
papers: updated the methods and results section

@@
 These skeletons consist of a sequence of \textit{joints}, i.e., locations that are locally a maximum distance from the segment boundary, with line segments connecting successive joints. 
-We prune the joints that are within $t_{jnt} = \TODO{XX}\SI{}{\nano\meter}$ of each other to reduce unnecessary branching.
-This value is small enough that the skeletons extend into the spines but large enough to keep branching does to a reasonable level.
-Additional analysis is available in the supplemental material.
 We refer to joints that have only one connected neighbor as \textit{endpoints}. 

### 2018-03-13 papers/eccv2018/4_results.tex
papers: updated the methods and results section

@@
 Our pruning heuristic removes at least $\TODO{X}\times$ the number of edges on all datasets, achieving a maximum removal rate of $\TODO{XX}\times$.
-However, there are some adjacent over-segmented labels which are considered. 
+However, there are some adjacent over-segmented labels which are not considered. 
 Table~\ref{table:skeletonization} shows the results for our edge generation including the number of missed neighbors and potential penalty in VI score.
@@
 	\setlength{\tabcolsep}{0.75em}
-	\begin{tabular}{c c c c} \hline
-		\textbf{Dataset} & \textbf{Segment Adjacency} & \textbf{Skeleton Pruning} & \textbf{Missed Split Errors} \\ \hline
-		Kasthuri &  & & \\
-		FlyEM &  &  & \\
-		FIB-25 &  & & \\ \hline
+	\begin{tabular}{c c c c c} \hline
+		\textbf{Dataset} & \textbf{Segment Adjacency} & \textbf{Skeleton Pruning} & \textbf{Missed Splits} & \textbf{Gained Edges} \\ \hline
+		Kasthuri & 610 / 23506 & 556 / 4921 & 214 & 160 \\
+		FlyEM & 298 / 17614 & 197 / 4366 & 120 & 19 \\
+		FIB-25 &  & & & \\ \hline
 	\end{tabular}
 	\caption{The results of our graph pruning approach compared to the baseline graph with all adjacent regions.
-We show the number of true merge locations (e.g., \TODO{XXX}) compared to total number of edges in the graph (e.g., \TODO{XXXXX}) for each case.
+We show the number of true merge locations (e.g., 610) compared to total number of edges in the graph (e.g., 23506) for each case.
 The number of missed splits corresponds to the number of split errors that our method misses compared to an adjacency matrix.}
@@
 	\includegraphics[width=0.45\linewidth]{./figures/merge_candidate1.png}		\includegraphics[width=0.45\linewidth]{./figures/merge_candidate2.png}
-	\caption{Two example segment pairs that we incorrectly prune from our graph. The distances between the circled endpoints are greater than our thresholds.}
+	\includegraphics[width=0.45\linewidth]{./figures/merge_candidate2.png}
+	\includegraphics[width=0.45\linewidth]{./figures/merge_candidate2.png}
+	\caption{The top two examples correspond to segment pairs that we incorrectly prune from the graph.
+The distance between the circled endpoints is too great.
+The bottom two examples shows pairs of segments that belong to the same neuron but are not adjacent in the input segmentation.}
 	\label{fig:skeleton-results}
@@
 		\textbf{Dataset} & $\Delta$ \textbf{Precision} & $\Delta$ \textbf{Recall} & $\Delta$ \textbf{Accuracy} & $\Delta$ \textbf{Precision} & $\Delta$ \textbf{Recall} & $\Delta$ \textbf{Accuracy} \\ \hline
-		Kasthuri Training & +3.61\% & -0.53\% & +0.60\% & +3.61\% & -0.53\% & +0.60\% \\
-		Kasthuri Vol. 2 & +7.59\% & -1.77\% & +1.38\%  & +7.59\% & -1.77\% & +1.38\% \\
-		FlyEM Vol. 1 & +2.68\% & +0.76\% & +0.66\% & +2.68\% & +0.76\% & +0.66\% \\
-		FlyEM Vol. 2 & +2.22\% & -1.05\% & +0.29\% & +2.22\% & -1.05\% & +0.29\% \\ \hline
+		Kasthuri  &  &  & &  &  & \\
+		FlyEM &  & & &  &  &  \\
+		Fib-25&  & & & & & \\ \hline
 	\end{tabular}

### 2018-03-13 graphics/render.py
render: updated input to take number of labels

@@ -13,17 +13,12 @@ from ibex.transforms import h52h5
 
 
 # run the marching cube algorithm for these labels
-def MarchingCubes(data, resolution, downsample_rate, output_prefix):
+def MarchingCubes(data, labels, resolution, downsample_rate, output_prefix):
     # downsample the input data to a manageable size
     downsampled_data = h52h5.DownsampleData(data, downsample_rate)
 
     # get the new grid size
     zres, yres, xres = downsampled_data.shape
-
-    # go through all labels
-    labels = np.unique(downsampled_data)
-    # to make sure masking occurred (arbitrary value)
-    assert (len(labels) < 100)
 
     for label in labels:
         if not label: continue
@@ -38,7 +33,7 @@ def MarchingCubes(data, resolution, downsample_rate, output_prefix):
         nfaces = faces.shape[0]
 
         # center all of the vertices
-        scale_factor = 1000.0
+        scale_factor = 500.0
         for iv in range(nverts):
             # divide by 2.0 to center the vertices
             verts[iv,0] = resolution[IB_Z] * downsample_rate[IB_Z] * (verts[iv,IB_Z] - zres / 2.0) / scale_factor

### 2018-03-13 papers/eccv2018/0_introduction.tex
papers: added much more on biological constraints

@@
 
-\begin{figure}[t]
-	\subfloat[]{
-	\includegraphics[width=.47\linewidth]{figures/schema/pre-multicut-with-arrows.pdf}
-	}
-	\subfloat[]{
-	\includegraphics[width=.47\linewidth]{figures/schema/post-multicut.png}
-	}
-	\caption{Example improvement of neural reconstruction.
-(a) We extract 3D skeletons from pixel-based segmentation algorithms to create a graph representation.
-Red arrows highlight errors in the input segmentation.
-(b) We improve the segmentation accuracy using a graph partitioning algorithm, leveraging both local and global information.}
+\begin{figure}[t!]
+	\centering
+	\includegraphics[width=\linewidth]{./figures/teaser_v2.png}
+	\caption{Our proposed framework uses both local and global biological constraints to improve an input segmentation.}
 	\label{fig:teaser}
@@
 We present a \textit{top-down graph-based} method that builds on the outputs of bottom-up pixel-based segmentation approaches. 
+Our method imposes both local and global biological constraints onto the output segmentation to match the underlying structure of neuronal processes.
 We first extract skeletons from labels in the input segmentation and generate a simplified graph (Fig.~\ref{fig:teaser}a). 
-Next, a trained CNN classifier detects split errors in the segmentation data. 
-Split errors correspond to neurons which are incorrectly segmented with multiple labels. 
-This classifier produces probabilities that two segments belong to the same neuron.
+Next, we train a CNN classifier to learn biological constraints on the local structural shape of a neuron (Fig.~\ref{fig:teaser}b). 
+This classifier produces probabilities that two segments belong to the same neuron based on the input shapes of the segments.
 These probabilities correspond to edge weights in our graph extracted from the input segmentation.
-We then use a graph optimization algorithm to partition the graph into a final improved reconstruction by enforcing domain-specific global constraints from biology (Fig.~\ref{fig:teaser}b).
+We then use a graph optimization algorithm to partition the graph into a final improved reconstruction by enforcing domain-specific topological constraints from biology (Fig.~\ref{fig:teaser}c).
 
@@
 
-This work makes the following contributions: (1) a novel top-down framework that extracts graphs from skeletonized 3D networks for improved neural reconstruction of connectomics data; (2) a region-based CNN classifier to detect errors; (3) an empirical evaluation of our method on several connectomics datasets; (4) improved performance over a state-of-the-art pixel-based reconstruction approach on average by \TODO{XX}\% with suitable running times.
+This work makes the following contributions: (1) a novel top-down framework that extracts graphs from skeletonized 3D segmentations for improved neural reconstruction of connectomics data; (2) a region-based CNN classifier to detect errors; (3) an empirical evaluation of our method on several connectomics datasets; (4) improved performance over a state-of-the-art pixel-based reconstruction approach on average by \TODO{XX}\% with suitable running times.

### 2018-03-13 papers/eccv2018/1_related_work.tex
papers: added much more on biological constraints

@@
 \section{Related Work}
+
+\begin{figure}[t]
+	\subfloat[]{
+		\includegraphics[width=.47\linewidth]{figures/schema/pre-multicut-with-arrows.pdf}
+	}
+	\subfloat[]{
+		\includegraphics[width=.47\linewidth]{figures/schema/post-multicut.png}
+	}
+	\caption{Example improvement of neural reconstruction.
+(a) We extract 3D skeletons from pixel-based segmentation algorithms to create a graph representation.
+Red arrows highlight errors in the input segmentation.
+(b) We improve the segmentation accuracy using a graph partitioning algorithm, leveraging both local and global information.}
+	\label{fig:improved-reconstruction}
+\end{figure}
 
@@
 \subsubsection{Region-based methods}
-
 Some early techniques apply computationally expensive graph partitioning algorithms with a single node per superpixel~\cite{andres2012globally}. 

### 2018-03-13 papers/eccv2018/2_method.tex
eccv: fixed figures to be horizontally aligned
papers: added much more on biological constraints

@@
 
-\begin{figure*}[htbp]
+\begin{figure*}[t!]
 	\begin{center}
@@
 From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with weights $w_e$. 
-The nodes correspond to labeled segments from the segmentation.
-There are edges between all nodes that we consider as merge candidates.
-Ideally, our graph has edges corresponding to all of the segments that were erroneously split. 
-To compute this graph we generate a skeleton for every segment in the pixel-based segmentation (Fig.~\ref{fig:overview}). 
-The skeletonized 3D network is a simplified representation of the overall branching structure of the neurons. 
-From these skeletons we identify potential merge locations and produce the corresponding edges for the graph. 
-To find actual merges we run a classification CNN to generate edge weights corresponding to merge probabilities.
-We formulate our graph partitioning problem as a multicut problem to segment the nodes into correct neuronal processes. 
-We will now discuss the three major components to our framework (graph creation, edge weight assignment, and graph partitioning) in more detail.
+The nodes correspond to labeled segments from the input data with edges between merge candidates.
+We propose the following three steps to formulate and then partition the graph while obeying constraints from the underlying biology.
+First, we only consider merging segments based on a skeletonized representation of the input segmentation.
+This is enables us to reduce the number of nodes in the graph based on prior knowledge of the shape of neuronal processes.
+Second, we train a convolutional neural network that learns biological constraints based on the shapes of the input segmentation.
+This network generates probabilities that segments belong to the same neuron based only on the segmentations. 
+An example of one such learned constraint is that neurons have small turning radii (Fig.~\ref{fig:turn-radii}).
+Third, we partition the graph using a lifted multicut formulation with additional acyclic constraints to enforce global biological constraints.
+The lifted multicut solution is globally consistent which we then augment to produce a tree-structured graph (i.e., one with no cycles).
 
-\subsection{Node Generation}
+\subsection{Graph Creation}
 %\subsubsection{Node Generation}
 \label{sec:skeletonization}
+
+\begin{figure}[t]
+	\begin{minipage}{0.45\linewidth}
+		\includegraphics[width=\linewidth]{./figures/constraint_error.png}
+	\end{minipage}
+	\hfill
+	\begin{minipage}{0.45\linewidth}
+		\includegraphics[width=\linewidth]{./figures/constraint_success.png}
+	\end{minipage}
+	\caption{Two example candidates for merging. The two segments in the left example do not belong to the same neuron as evidenced by the sharp turning radius.}
+	\label{fig:turn-radii}
+\end{figure}
+
+\subsubsection{Node Generation}
 
@@
 Despite the large number of segments, these regions only take up \TODO{XX}\% of the total volume on average.
-We provide further analysis of this strategy in the supplemental material.
 
-\subsection{Edge Generation}
+\subsubsection{Edge Generation}
 
@@
 	\centering
-	\includegraphics[width=0.45\linewidth]{./figures/skeleton1.png}
-	\includegraphics[width=0.45\linewidth]{./figures/skeleton2.png}
-	\includegraphics[width=0.45\linewidth]{./figures/skeleton3.png}
-	\includegraphics[width=0.45\linewidth]{./figures/skeleton4.png}
+	\begin{minipage}{0.45\linewidth}
+		\includegraphics[width=\linewidth]{./figures/skeleton1.png}		
+	\end{minipage}
+	\hfill
+	\begin{minipage}{0.45\linewidth}
+		\includegraphics[width=\linewidth]{./figures/skeleton2.png}		
+	\end{minipage}
+	\begin{minipage}{0.45\linewidth}
+		\includegraphics[width=\linewidth]{./figures/skeleton3.png}		
+	\end{minipage}
+	\hfill
+	\begin{minipage}{0.45\linewidth}
+		\includegraphics[width=\linewidth]{./figures/skeleton4.png}		
+	\end{minipage}
 	\caption{Example skeletons (in black) extracted from segments using a variant of the TEASER algorithm.}
@@
 Empirically, this reduced the running time for skeletonization by $\TODO{XX\%}$, with minimal reduction in skeleton accuracy ($\TODO{XX\%}$ fewer branches). 
-Fig.~\ref{fig:skeletonization} shows three examples of extracted skeletons (in black). 
+Fig.~\ref{fig:skeletonization} shows four examples of extracted skeletons (in black). 
 These skeletons consist of a sequence of \textit{joints}, i.e., locations that are locally a maximum distance from the segment boundary, with line segments connecting successive joints. 
@@
 We find that approximately \TODO{XX\%} of the segments that are erroneously split have nearby endpoints (Fig.~\ref{fig:merge_candidates}).
-We make use of this fact to find merge candidates with the following two-pass pruning algorithm.
 
-In the first pass, we iterate over all endpoints $e$ belonging to a segment $S$ and create a set of segments $\mathbb{S}_e^\prime$ that includes all labels that are within $t_{low}$ voxels from $e$.
-Elements of $\mathbb{S}_e^\prime$ are candidates for merging. 
-However, this first pass often leads to too many candidates, requiring an additional pass for further pruning. 
-In the second pass, we consider all of the segments in $\mathbb{S}_e^\prime$ for every endpoint $e$. 
-If a segment $S^\prime \in \mathbb{S}_e^\prime$ has an endpoint within $t_{high}$ voxels of $e$, the segment $S$ and $S^\prime$ are considered for merging. 
+Two segments, $s_1$ and $s_2$, receive a corresponding edge if the two following conditions hold.
+First, a endpoint in either $s_1$ or $s_2$ is with $t_{low}$ nm of any voxel in the other segment.
+Second, there is an endpoint in $s_1$ and an endpoint in $s_2$ that are within $t_{high}$ nm of each other.
 We store the midpoints between the two endpoints as the center of the potential merge in the set $\mathbb{S}_c$. 
-This algorithm produces a set of segments to consider for merging. Only these pairs have a corresponding edge in the constructed graph.
+This algorithm produces a set of segments to consider for merging. 
+Only these pairs have a corresponding edge in the constructed graph.
 
@@
 We do not use the raw EM image information to avoid the need to retrain the network on datasets that have been stained differently or imaged at different resolution. 
-This reduces the need for generating costly manually-labeled ground truth.
+This reduces the needfor generating costly manually-labeled ground truth.
 
@@
 	\centering
-	\includegraphics[width=0.32\linewidth]{./figures/split_error1.png}
-	\includegraphics[width=0.32\linewidth]{./figures/split_error2.png}		\includegraphics[width=0.32\linewidth]{./figures/split_error3.png}
+	\begin{minipage}{0.32\linewidth}
+		\includegraphics[width=\linewidth]{./figures/split_error1.png}		
+	\end{minipage}
+	\hfill
+	\begin{minipage}{0.32\linewidth}
+		\includegraphics[width=\linewidth]{./figures/split_error2.png}				
+	\end{minipage}
+	\hfill
+	\begin{minipage}{0.32\linewidth}
+		\includegraphics[width=\linewidth]{./figures/split_error3.png}
+	\end{minipage}
 	\caption{Three erroneously split segments.}
@@
 
+\subsubsection{Lifted Multicut}
+
 After constructing the 3D graph we seek to partition the graph into labels where every label corresponds to a neuronal process. 
@@
 
-\subsubsection{Post-processing}
+\subsubsection{Topological Constraints}
 

### 2018-03-13 papers/eccv2018/paper.tex
methods: major updates to skeletonization and neural networks
papers: added much more on biological constraints

@@
 \authorrunning{ECCV-18 submission ID \ECCV18SubNumber}
-\title{Graph-Based Neural Reconstruction from Skeletonized 3D Networks}
+\title{Scalable Graph-Based Neural \\ Reconstruction for Connectomics}
 
@@
 Current state-of-the-art automatic methods classify neural membranes at the pixel level followed by agglomeration methods to create full neuron reconstructions.
-However, these approaches widely neglect global geometric properties that are inherent in the graph structure of neural wiring diagrams.
-In this work, we follow pixel-based reconstruction by a global graph-based method to more accurately approximate neural pathways.
+However, these approaches widely neglect global geometric properties and other biological constraints that are inherent in the graph structure of neural wiring diagrams.
+In this work, we follow pixel-based reconstruction by a biologically-constrained graph-based method to more accurately approximate neural pathways.
 We first generate skeletons in 3D from the neuron labels of the pixel-based segmentation.
@@
 A CNN classifier produces edge weights for the graph corresponding to the probability of error. 
-We formulate the graph into a multicut partitioning problem to improve the final segmentation.
-Since the 3D graph is small and encodes top-down information our method is efficient and globally improves the neural reconstruction.
+We formulate the graph into a lifted multicut partitioning problem to improve the final segmentation.
 We demonstrate the performance of our approach on multiple real-world connectomics datasets with an average split variation of information improvement of \TODO{XX}\%.
-\keywords{connectomics, skeletonization, deep learning}
+\keywords{connectomics, skeletonization, deep learning, multicut}
 \end{abstract}

### 2018-03-13 papers/eccv2018/2_method.tex
paper: added more biological constraint information

@@
 We do not use the raw EM image information to avoid the need to retrain the network on datasets that have been stained differently or imaged at different resolution. 
-This reduces the needfor generating costly manually-labeled ground truth.
+This reduces the need for generating costly manually-labeled ground truth.
 
@@
 First, the number of segments in the final graph is not predetermined but depends on the input graph itself. 
-Second, this minimization produces globally consistent solutions (i.e. a boundary remains if and only if the two corresponding nodes belong to unique segments).
+Second, this minimization produces globally consistent solutions (i.e. a boundary remains if and only if the two corresponding nodes belong to unique segments)~\cite{keuper2015efficient}.
 

### 2018-03-13 algorithms/cpp-lifted-multicut.cpp
multicut: save the results of multicut to output folder

@@ -43,10 +43,10 @@ unsigned char *CppLiftedMulticut(unsigned long nvertices, unsigned long nedges, 
     else if (heuristic == 1) andres::graph::multicut_lifted::greedyAdditiveEdgeContraction(original_graph, lifted_graph, weights, edge_labels);
 
     // turn vector into char array and return
-    unsigned char *collapsed_edges = new unsigned char[nedges];
+    unsigned char *maintain_edges = new unsigned char[nedges];
     for (unsigned long ie = 0; ie < nedges; ++ie) {
-        collapsed_edges[ie] = edge_labels[lifted_graph.findEdge(vertex_ones[ie], vertex_twos[ie]).second];
+        maintain_edges[ie] = edge_labels[lifted_graph.findEdge(vertex_ones[ie], vertex_twos[ie]).second];
     }
 
-    return collapsed_edges;
+    return maintain_edges;
 }

### 2018-03-13 algorithms/cpp-multicut.cpp

@@ -36,10 +36,10 @@ unsigned char *CppMulticut(unsigned long nvertices, unsigned long nedges, unsign
     else { fprintf(stderr, "Unrecognized heuristic: %u\n", heuristic); return NULL; }
     
     // turn vector into char array and return
-    unsigned char *collapsed_edges = new unsigned char[nedges];
+    unsigned char *maintain_edges = new unsigned char[nedges];
     for (unsigned long ie = 0; ie < nedges; ++ie) {
-        collapsed_edges[ie] = edge_labels[ie];
+        maintain_edges[ie] = edge_labels[ie];
     }
 
-    return collapsed_edges;
+    return maintain_edges;
 }

### 2018-03-13 algorithms/lifted_multicut.pyx

@@ -64,7 +64,7 @@ def LiftedMulticut(prefix, candidates, edge_weights, beta, threshold, heuristic)
     # run multicut algorithm
     cdef unsigned char *cpp_collapsed_edges = CppLiftedMulticut(nvertices, nedges, &(cpp_vertex_ones[0]), &(cpp_vertex_twos[0]), &(cpp_lifted_weights[0,0]), beta, heuristic)
     cdef unsigned char[:] tmp_collapsed_edges = <unsigned char[:nedges]> cpp_collapsed_edges
-    collapsed_edges = np.asarray(tmp_collapsed_edges).astype(dtype=np.bool)
+    maintain_edges = np.asarray(tmp_collapsed_edges).astype(dtype=np.bool)
     
     ncandidates = len(candidates)
     labels = np.zeros(ncandidates, dtype=np.uint8)
@@ -73,14 +73,12 @@ def LiftedMulticut(prefix, candidates, edge_weights, beta, threshold, heuristic)
 
     print 'After Multicut'
 
-    PrecisionAndRecall(labels, 1 - collapsed_edges)
+    PrecisionAndRecall(labels, 1 - maintain_edges)
 
     # collapse the edges returned from multicut
-    segmentation = CollapseGraph(segmentation, candidates, collapsed_edges, edge_weights)
+    output_filename = 'multicuts/{}-{}-lifted.results'.format(prefix, beta)
+    CollapseGraph(segmentation, candidates, maintain_edges, edge_weights, output_filename)
    
-    # evaluate before and after multicut
-    #comparestacks.CremiEvaluate(segmentation, gold, dilate_ground_truth=1, mask_ground_truth=True, filtersize=0)
-
 
 
 # function ro run multicut algorithm

### 2018-03-13 algorithms/multicut.pyx

@@ -48,7 +48,7 @@ def Multicut(prefix, candidates, edge_weights, beta, threshold, heuristic):
     # run multicut algorithm
     cdef unsigned char *cpp_collapsed_edges = CppMulticut(nvertices, nedges, &(cpp_vertex_ones[0]), &(cpp_vertex_twos[0]), &(cpp_edge_weights[0]), beta, heuristic)
     cdef unsigned char[:] tmp_collapsed_edges = <unsigned char[:nedges]> cpp_collapsed_edges
-    collapsed_edges = np.asarray(tmp_collapsed_edges).astype(dtype=np.bool)
+    maintain_edges = np.asarray(tmp_collapsed_edges).astype(dtype=np.bool)
     
     ncandidates = len(candidates)
     labels = np.zeros(ncandidates, dtype=np.uint8)
@@ -57,14 +57,13 @@ def Multicut(prefix, candidates, edge_weights, beta, threshold, heuristic):
 
     print '\nAfter Multicut\n'
 
-    PrecisionAndRecall(labels, 1 - collapsed_edges)
-
+    PrecisionAndRecall(labels, 1 - maintain_edges)
 
     # collapse the edges returned from multicut
-    segmentation = CollapseGraph(segmentation, candidates, collapsed_edges, edge_weights)
-   
-    # evaluate before and after multicut
-    #comparestacks.CremiEvaluate(segmentation, gold, dilate_ground_truth=1, mask_ground_truth=True, filtersize=0)
+    output_filename = 'multicuts/{}-{}.results'.format(prefix, beta)
+    CollapseGraph(segmentation, candidates, maintain_edges, edge_weights, output_filename)
+    
+
 
 
 

### 2018-03-13 algorithms/util.py

@@ -37,7 +37,7 @@ def RetrieveCandidates(prefix, model_prefix, threshold, maximum_distance, endpoi
 
 
 # collapse the edges from multicut
-def CollapseGraph(segmentation, candidates, collapsed_edges, probabilities):
+def CollapseGraph(segmentation, candidates, maintain_edges, probabilities, output_filename):
     ncandidates = len(candidates)
 
     # get the ground truth and the predictions
@@ -50,7 +50,7 @@ def CollapseGraph(segmentation, candidates, collapsed_edges, probabilities):
     union_find = [unionfind.UnionFindElement(iv) for iv in range(max_value)]
 
     # create adjacency sets for the elements in the segment
-    adjacency_sets = [set() for _ in range(ncandidates)]
+    adjacency_sets = [set() for _ in range(max_value)]
 
     for candidate in candidates:
         label_one = candidate.labels[0]
@@ -64,7 +64,7 @@ def CollapseGraph(segmentation, candidates, collapsed_edges, probabilities):
 
     for probability, ie in sorted(zipped, reverse=True):
         # skip if the edge is not collapsed
-        if collapsed_edges[ie]: continue
+        if maintain_edges[ie]: continue
         # skip if this creates a cycle
         label_one, label_two = candidates[ie].labels
 
@@ -76,21 +76,17 @@ def CollapseGraph(segmentation, candidates, collapsed_edges, probabilities):
             if neighbor_label == label_two: continue
 
             if unionfind.Find(union_find[neighbor_label]).label == label_two_union_find: 
-                collapsed_edges[ie] = True
+                maintain_edges[ie] = True
 
         # skip if the edge is no longer collapsed
-        if collapsed_edges[ie]: continue
+        if maintain_edges[ie]: continue
         unionfind.Union(union_find[label_one], union_find[label_two])
 
     print '\nBorder Constraints\n'
-    PrecisionAndRecall(labels, 1 - collapsed_edges)
+    PrecisionAndRecall(labels, 1 - maintain_edges)
 
-
-    # create a mapping for the labels
-    mapping = np.zeros(max_value, dtype=np.int64)
-    for iv in range(max_value):
-        mapping[iv] = unionfind.Find(union_find[iv]).label
-
-    segmentation = seg2seg.MapLabels(segmentation, mapping)
-
-    return segmentation
+    # for every edge, save if the edge is collapsed
+    with open(output_filename, 'wb') as fd:
[…]

### 2018-03-13 algorithms/lifted_multicut.pyx
oracle: updated method for determining oracle

@@ -76,7 +76,7 @@ def LiftedMulticut(prefix, candidates, edge_weights, beta, threshold, heuristic)
     PrecisionAndRecall(labels, 1 - maintain_edges)
 
     # collapse the edges returned from multicut
-    output_filename = 'multicuts/{}-{}-lifted.results'.format(prefix, beta)
+    output_filename = 'multicuts/{}-{:0.2f}-lifted.results'.format(prefix, beta)
     CollapseGraph(segmentation, candidates, maintain_edges, edge_weights, output_filename)
    
 

### 2018-03-13 algorithms/multicut.pyx

@@ -60,7 +60,7 @@ def Multicut(prefix, candidates, edge_weights, beta, threshold, heuristic):
     PrecisionAndRecall(labels, 1 - maintain_edges)
 
     # collapse the edges returned from multicut
-    output_filename = 'multicuts/{}-{}.results'.format(prefix, beta)
+    output_filename = 'multicuts/{}-{:0.2f}.results'.format(prefix, beta)
     CollapseGraph(segmentation, candidates, maintain_edges, edge_weights, output_filename)
     
 

### 2018-03-13 cnns/analysis.py

@@ -63,7 +63,7 @@ class Architecture:
 
 
 def ParseResults(filename):
-    prefix = filename.split('/')[-1].split('.')[0].strip('skeleton')[1:-12]
+    prefix = filename.split('/')[-1].split('.')[0].strip('skeleton')[1:-24]
 
     # open the results filename
     with open(filename, 'r') as fd:

### 2018-03-13 cnns/skeleton/oracle.py

@@ -6,29 +6,35 @@ from ibex.transforms import seg2seg, seg2gold
 from ibex.cnns.skeleton.util import FindCandidates
 from ibex.data_structures import unionfind
 from ibex.evaluation import comparestacks
+from ibex.transforms import seg2gold
 
 
 
 def Oracle(prefix, threshold, maximum_distance, endpoint_distance, network_distance, filtersize=0):
     # get all of the candidates
     positive_candidates = FindCandidates(prefix, threshold, maximum_distance, endpoint_distance, network_distance, 'positive')  
-    ncandidates = len(positive_candidates)
+    negative_candidates = FindCandidates(prefix, threshold, maximum_distance, endpoint_distance, network_distance, 'negative')
+    candidates = positive_candidates + negative_candidates
 
     # read in all relevant information
     segmentation = dataIO.ReadSegmentationData(prefix)
     segmentation = seg2seg.RemoveSmallConnectedComponents(segmentation, threshold=threshold)
     gold = dataIO.ReadGoldData(prefix)
 
+    seg2gold_mapping = seg2gold.Mapping(segmentation, gold)
+
     # create the union find data structure
     max_value = np.amax(segmentation) + 1
     union_find = [unionfind.UnionFindElement(iv) for iv in range(max_value)]
 
     # iterate over all candidates and collapse edges
-    for candidate in positive_candidates:
+    for candidate in candidates:
         label_one = candidate.labels[0]
         label_two = candidate.labels[1]
 
-        unionfind.Union(union_find[label_one], union_find[label_two])
+        if not seg2gold_mapping[label_one] or not seg2gold_mapping[label_two]: continue
+        if (seg2gold_mapping[label_one] == seg2gold_mapping[label_two]):
+            unionfind.Union(union_find[label_one], union_find[label_two])
 
     # create a mapping for the labels
     mapping = np.zeros(max_value, dtype=np.int64)

### 2018-03-14 papers/eccv2018/0_introduction.tex
donglai's pass on abstract-intro-related

@@
 
-\begin{figure}[t!]
+% \begin{figure}[t!]
+% 	\centering
+% 	\includegraphics[width=\linewidth]{./figures/teaser_v2.png}
+% 	\caption{Our proposed framework uses both local and global biological constraints to improve an input segmentation.}
+% 	\label{fig:teaser}
+% \end{figure}
+\begin{figure}[t]
 	\centering
-	\includegraphics[width=\linewidth]{./figures/teaser_v2.png}
-	\caption{Our proposed framework uses both local and global biological constraints to improve an input segmentation.}
-	\label{fig:teaser}
+	\includegraphics[width=\linewidth]{./figures/bc/teaser_bc_v2.pdf}
+	\caption{Biological constraints for 3D segments in Connectomics.}
+	\label{fig:bc}
 \end{figure}
 
-The field of connectomics is concerned with reconstructing the wiring diagram of the brain at nanometer resolutions to enable new insights into the workings of the brain~\cite{haehn2017scalable,kasthuri2015saturated}.
-Recent advancements in image acquisition using multi-beam serial-section electron microscopy (sSEM) allow researchers to produce terabytes of image data per hour~\cite{hildebrand2017whole}. 
-It is infeasible for domain experts to manually reconstruct this vast amount of image data~\cite{haehn2014design}. 
-State-of-the-art automatic reconstruction approaches use pixel-based segmentation with convolutional neural networks (CNNs) followed by agglomeration strategies~\cite{seymour2016rhoananet,lee2015recursive,nunez2014graph,parag2017anisotropic,ronneberger2015u,zlateski2015image}.
-These \textit{bottom-up pixel-based} methods produce excellent results but still fall short of acceptable error rates for large volumes.
+The field of connectomics is concerned about reconstructing the wiring diagram of the brain at nanometer resolutions to enable new insights into the workings of the brain~\cite{haehn2017scalable,kasthuri2015saturated}.
+%Recent advancements in image acquisition using multi-beam serial-section electron microscopy (sSEM) allow researchers to produce terabytes of image data per hour~\cite{hildebrand2017whole}. 
+%It is infeasible for domain experts to manually reconstruct this vast amount of image data~\cite{haehn2014design}. 
+State-of-the-art automatic 3D reconstruction approaches use voxel-based convolutional neural networks (CNNs) and watershed transform to generate initial segmentation, followed by agglomeration steps~\cite{seymour2016rhoananet,lee2015recursive,nunez2014graph,parag2017anisotropic,ronneberger2015u,zlateski2015image}.
+%These \textit{bottom-up pixel-based} methods produce excellent results but still fall short of acceptable error rates for large volumes.
+For the agglomeration, most methods do not make use of the biological knowledge of the 3D shape of neural structures.
+Reported on small-sized volumes, a simple threshold-based mean agglomeration method can achieve superhuman result~\cite{lee2017superhuman}.
+However, it is unclear if it is the case for larger volumes.
 
-We present a \textit{top-down graph-based} method that builds on the outputs of bottom-up pixel-based segmentation approaches. 
-Our method imposes both local and global biological constraints onto the output segmentation to match the underlying structure of neuronal processes.
+%\TODO{the selling point is to add biological constraint}
+%We present a \textit{top-down graph-based} method that builds on the outputs of bottom-up pixel-based segmentation approaches. 
+We here present a new agglomeration method that imposes both local and global biological constraints onto the output segmentation to match the underlying structure of neuronal processes.
 We first extract skeletons from labels in the input segmentation and generate a simplified graph (Fig.~\ref{fig:teaser}a). 
@@
 
-Our approach operates at a level of abstraction above existing pixel-based methods. 
-This allows us to leverage both local and global information to produce more accurate reconstructions. 
+%Our approach operates at a level of abstraction above existing pixel-based methods. 
+%This allows us to leverage both local and global information to produce more accurate reconstructions. 
+With the biological constraints, we can make use of both geometric and topological prior information to produce more accurate reconstructions.
+\TODO{refer to figure 1}
 Our method is independent of image resolution and acquisition parameters, enabling its application to isotropic and anisotropic image data without retraining.
@@
 
-This work makes the following contributions: (1) a novel top-down framework that extracts graphs from skeletonized 3D segmentations for improved neural reconstruction of connectomics data; (2) a region-based CNN classifier to detect errors; (3) an empirical evaluation of our method on several connectomics datasets; (4) improved performance over a state-of-the-art pixel-based reconstruction approach on average by \TODO{XX}\% with suitable running times.
+This work makes three contributions.
+First, a novel top-down framework that extracts graphs from skeletonized 3D segmentations for improved neural reconstruction of connectomics data; 
+Then, a region-based CNN classifier to detect errors; 
+%(3) an empirical evaluation of our method on several connectomics datasets;  % this is not contribution
+Last, improved performance over a state-of-the-art pixel-based reconstruction approach on average by \TODO{XX}\% with suitable running times.

### 2018-03-14 papers/eccv2018/1_related_work.tex
donglai's pass on abstract-intro-related

--- 2018-03-05 papers/eccv2018/1_related_work.tex
@@
 
-\paragraph{Pixel-based methods.}
-A significant amount of connectomics research considers the problem of extracting segmentation information at the pixel (i.e., voxel) level from the raw EM images. 
+% \begin{figure}[t]
+% 	\subfloat[]{
+% 		\includegraphics[width=.47\linewidth]{figures/schema/pre-multicut-with-arrows.pdf}
+% 	}
+% 	\subfloat[]{
+% 		\includegraphics[width=.47\linewidth]{figures/schema/post-multicut.png}
+% 	}
+% 	\caption{Example improvement of neural reconstruction.
+(a) We extract 3D skeletons from pixel-based segmentation algorithms to create a graph representation.
+Red arrows highlight errors in the input segmentation.
+(b) We improve the segmentation accuracy using a graph partitioning algorithm, leveraging both local and global information.}
+% 	\label{fig:improved-reconstruction}
+% \end{figure}
+
+\subsubsection{Initial Segmentation}
+A significant amount of connectomics research considers the problem of extracting segmentation information at the voxel level from raw EM images.
+
+First, intermediate representations like boundary or affinity maps are generated.
 Some methods use a random forest populated with hand-designed features based on image characteristics around a given pixel to predict membrane probabilities~\cite{kaynig2015large}.
@@
 
-\paragraph{Region-based methods.}
-
+Then, these intermediate representations are transformed into segmentation.
 Some early techniques apply computationally expensive graph partitioning algorithms with a single node per superpixel~\cite{andres2012globally}.
@@
 Often a watershed algorithm will then cluster pixels into super-pixels~\cite{zlateski2015image}.
-Many methods build on top of these region-based strategies and train random-forest classifiers to produce the final segmentations~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image,10.1371/journal.pone.0125825}.
+
+\subsubsection{Agglomeration}
+Given the initial segmentation, some methods train random-forest classifiers to produce the final segmentations~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image,10.1371/journal.pone.0125825}.
 Some methods rely solely on the accuracy of the predicted affinities and agglomerate hierarchically based on the mean affinity between supervoxels~\cite{lee2017superhuman,funke2017deep}.
 Pape et al. present a scalable multicut algorithm to partition superpixels~\cite{beier2017multicut}.
-
-\paragraph{Error-correction methods.}
-Additional research builds on top of these region-based methods to correct errors in the segmentation either using human proofreading~\cite{haehn2014design,haehn2017guided,mojo2} or automatic methods~\cite{rolnick2017morphological,error_correction_using_CNN}.
-However, to our knowledge, our method is the first to extract a 3D graph from an input segmentation for a true top-down\TODO{?} error correction approach. 
-This allows us to enforce domain-specific biology constraints and use efficient graph partitioning algorithms. 
-Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for traditional image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}.
-Even though graph partitioning is an NP-Hard problem~\cite{demaine2006correlation} there are several useful multicut heuristics that provide good approximations with reasonable computational costs~\cite{horvnakova2017analysis}.
-We use the method of Keuper et al.~\cite{keuper2015efficient} to partition the extracted graph into the final neural reconstruction.
+\TODO{add learning-based algorithm} ~\cite{jain2011learning,bogovic2013learned}
+%\subsubsection{Error-correction methods}
+%Additional research builds on top of these region-based methods to correct errors in the segmentation either using human proofreading~\cite{haehn2014design,haehn2017guided,mojo2} or automatic methods~\cite{rolnick2017morphological,error_correction_using_CNN}.
+%However, to our knowledge, our method is the first to extract a 3D graph from an input segmentation for a true top-down\TODO{?} error correction approach. 
+%This allows us to enforce domain-specific biology constraints and use efficient graph partitioning algorithms. 
+% Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for traditional image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}.
+% Even though graph partitioning is an NP-Hard problem~\cite{demaine2006correlation} there are several useful multicut heuristics that provide good approximations with reasonable computational costs~\cite{horvnakova2017analysis}.
+%We use the method of Keuper et al.~\cite{keuper2015efficient} to partition the extracted graph into the final neural reconstruction.

### 2018-03-14 papers/eccv2018/2_method.tex
donglai's pass on abstract-intro-related

@@
 
-\begin{figure*}[t!]
-	\begin{center}
-		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/multicut_input.png}}
-		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/pre-multicut.png}}
-		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/multicut-graph.png}}
-		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/post-multicut.png}}
-	\end{center}
-	\caption{Outline of our approach, from left to right: result of the pixel-based segmentation and agglomeration algorithm; segments of several neurons from the initial segmentation; extracted skeletonized network of those segments; improved 3D reconstruction of the selected segments after graph construction and partitioning with constraints.}
-	\label{fig:overview}
-\end{figure*}
+\begin{figure}[t!]
+	\centering
+	\includegraphics[width=\linewidth]{./figures/teaser_v2.png}
+	\caption{Our proposed framework uses both local and global biological constraints to improve an input segmentation.}
+	\label{fig:teaser}
+\end{figure}
+% \begin{figure*}[t!]
+% 	\begin{center}
+% 		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/multicut_input.png}}
+% 		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/pre-multicut.png}}
+% 		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/multicut-graph.png}}
+% 		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/post-multicut.png}}
+% 	\end{center}
+% 	\caption{Outline of our approach, from left to right: result of the pixel-based segmentation and agglomeration algorithm; segments of several neurons from the initial segmentation; extracted skeletonized network of those segments; improved 3D reconstruction of the selected segments after graph construction and partitioning with constraints.}
+% 	\label{fig:overview}
+% \end{figure*}
 
-There are two types of errors that can occur in connectomics segmentations: \textit{split errors} and \textit{merge errors}. 
-In a split error, two segments should have been merged into one neuronal process. 
-In a merge error, one segment corresponds to more than one neuron.
-Generally, it is much more difficult to correct merge errors than to correct split errors,
-as the space of possible split proposals grows quickly~\cite{parag2015properties}.
-Thus, most reconstruction approaches are tuned towards over-segmentation with many more split than merge errors. 
+%There are two types of errors that can occur in connectomics segmentations: \textit{split errors} and \textit{merge errors}. 
+%In a split error, two segments should have been merged into one neuronal process. 
+%In a merge error, one segment corresponds to more than one neuron.
+%Generally, it is much more difficult to correct merge errors than to correct split errors, as the space of possible split proposals grows quickly~\cite{parag2015properties}.
+%Thus, most reconstruction approaches are tuned towards over-segmentation with many more split than merge errors. 
 Our method takes as input over-segmentations of EM image volumes generated by scalable, state-of-the-art connectomics reconstruction pipelines (Sec.~\ref{sec:neuroproof}). 
@@
 \label{sec:skeletonization}
-
-\begin{figure}[t]
-	\begin{minipage}{0.45\linewidth}
-		\includegraphics[width=\linewidth]{./figures/constraint_error.png}
-	\end{minipage}
-	\hfill
-	\begin{minipage}{0.45\linewidth}
-		\includegraphics[width=\linewidth]{./figures/constraint_success.png}
-	\end{minipage}
-	\caption{Two example candidates for merging. The two segments in the left example do not belong to the same neuron as evidenced by the sharp turning radius.}
-	\label{fig:turn-radii}
-\end{figure}
 
@@
 
+\begin{figure}[t]
+	\begin{minipage}{0.45\linewidth}
+		\includegraphics[width=\linewidth]{./figures/constraint_error.png}
+	\end{minipage}
+	\hfill
+	\begin{minipage}{0.45\linewidth}
+		\includegraphics[width=\linewidth]{./figures/constraint_success.png}
+	\end{minipage}
+	\caption{Two example candidates for merging. The two segments in the left example do not belong to the same neuron as evidenced by the sharp turning radius.}
+	\label{fig:turn-radii}
+\end{figure}
 \subsection{Edge Weights Assignment}
@@
 
+\subsubsection{Network Architecture \& Training}
+
+We use \textit{VGG-style} blocks as presented by Chatfield et al.~\cite{chatfield2014return}. 
+Each blocks consists of two double convolutions with filter size $3\times3\times3$ followed by a max pooling step. 
+There are three layers of these blocks. 
+The first two max pooling layers are anisotropic with pooling only in the $x$ and $y$ dimensions. 
+The output of this final pooling step is flattened into a 1D vector that is input into two fully connected layers. 
+The final layer produces probabilities with a sigmoid activation function~\cite{funahashi1989approximate}. 
+All of the other activation functions are LeakyReLU~\cite{maas2013rectifier}.
+
+For training we use a stochastic gradient descent optimizer with Nesterov's accelerated gradient~\cite{nesterov1983method}. 
+We employ dropouts of $0.2$ after every pooling layer and the first dense layer, and a dropout of $0.5$ after the final dense layer to prevent overfitting. 
+We discuss all other network parameters in Sec.~\ref{sec:network-parameters}.
+
+\subsection{Graph Clustering}
+
 \begin{figure}[t]
@@
 \end{figure}
-
-\subsubsection{Network Architecture \& Training}
-
-We use \textit{VGG-style} blocks as presented by Chatfield et al.~\cite{chatfield2014return}. 
-Each blocks consists of two double convolutions with filter size $3\times3\times3$ followed by a max pooling step. 
-There are three layers of these blocks. 
-The first two max pooling layers are anisotropic with pooling only in the $x$ and $y$ dimensions. 
-The output of this final pooling step is flattened into a 1D vector that is input into two fully connected layers. 
-The final layer produces probabilities with a sigmoid activation function~\cite{funahashi1989approximate}. 
-All of the other activation functions are LeakyReLU~\cite{maas2013rectifier}.
-
-For training we use a stochastic gradient descent optimizer with Nesterov's accelerated gradient~\cite{nesterov1983method}. 
-We employ dropouts of $0.2$ after every pooling layer and the first dense layer, and a dropout of $0.5$ after the final dense layer to prevent overfitting. 
-We discuss all other network parameters in Sec.~\ref{sec:network-parameters}.
-
-\subsection{Graph Clustering}
-
 \subsubsection{Lifted Multicut}

### 2018-03-14 papers/eccv2018/paper.tex
donglai's pass on abstract-intro-related

@@
 \authorrunning{ECCV-18 submission ID \ECCV18SubNumber}
-\title{Scalable Graph-Based Neural \\ Reconstruction for Connectomics}
+%\title{Scalable Graph-Based Neural \\ Reconstruction for Connectomics}
+\title{Biologically-Constrained 3D Agglomeration for Connectome Reconstruction}
 
@@
 \begin{abstract}
-Advancements in electron microscopy image acquisition have created connectomics datasets terabytes in size making manual reconstruction of neuronal structures infeasible.
-Current state-of-the-art automatic methods classify neural membranes at the pixel level followed by agglomeration methods to create full neuron reconstructions.
-However, these approaches widely neglect global geometric properties and other biological constraints that are inherent in the graph structure of neural wiring diagrams.
-In this work, we follow pixel-based reconstruction by a biologically-constrained graph-based method to more accurately approximate neural pathways.
-We first generate skeletons in 3D from the neuron labels of the pixel-based segmentation.
-Next, we simplify this skeletonized 3D network into a graph with nodes corresponding to labels from the segmentation and edges identifying potential locations of split errors.
-A CNN classifier produces edge weights for the graph corresponding to the probability of error. 
-We formulate the graph into a lifted multicut partitioning problem to improve the final segmentation.
+% maybe better to cut to the point
+%Advancements in electron microscopy image acquisition have created connectomics datasets terabytes in size making manual reconstruction of neuronal structures infeasible.
+%In the past decade in Connectomics, much progress has been made to classify neural membranes or affinities from the raw pixel and to watershed transform them into initial segments.
+%Current state-of-the-art automatic methods classify neural membranes or affinities from the raw pixel followed by agglomeration methods to create full neuron reconstructions.
+%An agglomerative segmentation algorithm merges initial pair of clusters.
+Current state-of-the-art connectome reconstruction pipelines have three major steps: affinity prediction from raw voxels, initial segmentation with watershed transform and refined segmentation with agglomeration.
+%In the past deTraditionally, neuron segmentation from 3D electron microscopy (EM)
+For the agglomeration, most methods neglect geometric and topological constraints that are inherent in the graph structure of neural wiring diagrams.
+
+In this work, we use a biologically-constrained graph-based method to better reconstruct neural pathways.
+Given the initial segmentation, we first create a graph with nodes corresponding to segment labels and edges identifying potential locations of split errors based on the skeleton structure of the segmentation.
+Next, we train a convolutional neural network to capture the geometric properties of segment connections and produce edge weights as the probability of merging two nodes.
+Finally, we formulate the agglomeration as a lifted multicut partitioning problem with topological constraints to avoid cycles.
 We demonstrate the performance of our approach on multiple real-world connectomics datasets with an average split variation of information improvement of \TODO{XX}\%.
-\keywords{connectomics, skeletonization, deep learning, multicut}
+\keywords{connectomics, biological constraints, agglomeration, skeletonization, deep learning, lifted multicut}
 \end{abstract}

### 2018-03-14 papers/eccv2018/1_related_work.tex
related work: categorize agglomeration

@@
 \subsubsection{Agglomeration}
-Given the initial segmentation, some methods train random-forest classifiers to produce the final segmentations~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image,10.1371/journal.pone.0125825}.
+\TODO{rule-based method}
 Some methods rely solely on the accuracy of the predicted affinities and agglomerate hierarchically based on the mean affinity between supervoxels~\cite{lee2017superhuman,funke2017deep}.
+
+\TODO{classification-based method}
+Given the initial segmentation, some methods train random-forest classifiers to produce the final segmentations~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image,10.1371/journal.pone.0125825}
+extract different features
+~\cite{jain2011learning,bogovic2013learned}.
+
+\TODO{optimization-based method}
 Pape et al. present a scalable multicut algorithm to partition superpixels~\cite{beier2017multicut}.
-\TODO{add learning-based algorithm} ~\cite{jain2011learning,bogovic2013learned}
+
+In our work, we combine classification and optimization.
 %\subsubsection{Error-correction methods}

### 2018-03-14 papers/eccv2018/0_introduction.tex
pass on exp and result

@@
 %It is infeasible for domain experts to manually reconstruct this vast amount of image data~\cite{haehn2014design}. 
-State-of-the-art automatic 3D reconstruction approaches use voxel-based convolutional neural networks (CNNs) and watershed transform to generate initial segmentation, followed by agglomeration steps~\cite{seymour2016rhoananet,lee2015recursive,nunez2014graph,parag2017anisotropic,ronneberger2015u,zlateski2015image}.
+State-of-the-art automatic 3D reconstruction approaches use pixel-based convolutional neural networks (CNNs) and watershed transform to generate initial segmentation, followed by agglomeration steps~\cite{seymour2016rhoananet,lee2015recursive,nunez2014graph,parag2017anisotropic,ronneberger2015u,zlateski2015image}.
 %These \textit{bottom-up pixel-based} methods produce excellent results but still fall short of acceptable error rates for large volumes.

### 2018-03-14 papers/eccv2018/1_related_work.tex
pass on exp and result

@@
 
-\subsubsection{Initial Segmentation}
+\subsubsection{Pixel-Based Segmentation}
 A significant amount of connectomics research considers the problem of extracting segmentation information at the voxel level from raw EM images.
@@
 \subsubsection{Agglomeration}
-\TODO{rule-based method}
+\TODO{rule-based}
 Some methods rely solely on the accuracy of the predicted affinities and agglomerate hierarchically based on the mean affinity between supervoxels~\cite{lee2017superhuman,funke2017deep}.
 
-\TODO{classification-based method}
+\TODO{classification-based}
 Given the initial segmentation, some methods train random-forest classifiers to produce the final segmentations~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image,10.1371/journal.pone.0125825}
@@
 
-\TODO{optimization-based method}
+\TODO{optimization-based}
 Pape et al. present a scalable multicut algorithm to partition superpixels~\cite{beier2017multicut}.

### 2018-03-14 papers/eccv2018/2_method.tex
pass on exp and result

@@
 	\caption{Our proposed framework uses both local and global biological constraints to improve an input segmentation.}
-	\label{fig:teaser}
+	\label{fig:teaser_pipeline}
 \end{figure}
@@
 %Thus, most reconstruction approaches are tuned towards over-segmentation with many more split than merge errors. 
-Our method takes as input over-segmentations of EM image volumes generated by scalable, state-of-the-art connectomics reconstruction pipelines (Sec.~\ref{sec:neuroproof}). 
-Our goal is to identify locations of split errors and merge the corresponding segments automatically.
+The input of our method is the over-segmentation of EM image volumes from state-of-the-art pipelines.
+Our pipeline is illustrated in Fig.~\ref{fig:teaser_pipeline}.
+%Our goal is to identify locations of split errors and merge the corresponding segments automatically.
 
+\TODO{[refer to teaser figure of the pipeline]}
+\TODO{[need to be concise here]}
+\TODO{[we use biological constraints]}
 From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with weights $w_e$. 
@@
 
-\subsection{Graph Creation}
+\subsection{Skeleton-Based Graph Generation}
 %\subsubsection{Node Generation}
 \label{sec:skeletonization}
+Most agglomeration methods create the region graph by removing small-sized segments and linking each pair of adjacent segments, which can still lead to a large graph size due to the irregular shape of neural structures.
+We here use the skeleton representation of the segmenation and reduce the graph size with the geometric constraints on the connectivity of two adjacent segments to prune edges.
+% a bit trivial, as everyone is doing this. maybe no need to mention
+% \subsubsection{Node Pruning}
+% %The simplest node generation strategy creates one node for every unique segment label in the input volume. 
+% Some labels in the volume correspond to very small structures that are likely the result of segmentation errors, typically in regions with noisy raw image data. 
+% It is difficult to extract useful shape features from these segments because of their small, often random, shape. 
+% We prune these nodes from the graph by removing all segments with fewer than a empirical threshold $t_{seg} = 20,000$ voxels. 
+% This removes on average \TODO{XX}\% of the segments in our  datasets (Sec.~\ref{sec:dataset}), leaving us with around $\TODO{XX}$ nodes per dataset (\TODO{X nodes per micrometer}). 
+% Despite the large number of segments, these regions only take up \TODO{XX}\% of the total volume on average.
 
-\subsubsection{Node Generation}
-
-The simplest node generation strategy creates one node for every unique segment label in the input volume. 
-However, some of the labels in the volume correspond to very small structures that are likely the result of segmentation errors, typically in regions with noisy raw image data. 
-It is difficult to extract useful shape features from these segments because of their small, often random, shape. 
-We prune these nodes from the graph by removing all segments with fewer than a threshold $t_{seg} = 20,000$ voxels. 
-This removes on average \TODO{XX}\% of the segments in our  datasets (Sec.~\ref{sec:dataset}), leaving us with around $\TODO{XX}$ nodes per dataset (\TODO{X nodes per micrometer}). 
-Despite the large number of segments, these regions only take up \TODO{XX}\% of the total volume on average.
-
-\subsubsection{Edge Generation}
+% \subsubsection{Edge Pruning}
 
@@
 
-A typical approach for generating edges produces one between all adjacent segments. 
-Two segments $l_1$ and $l_2$ are considered adjacent if there is a pair of adjacent voxels with one labeled $l_1$ and the other labeled $l_2$.
-For example, pixel-based agglomeration methods such as mean agglomeration~\cite{lee2017superhuman} or waterz~\cite{funke2017deep} consider all pairs of adjacent segments for merging.
-However, this method produces too many edges in the graph for graph-based optimization approaches. 
-We identify a smaller number of pairs of segments to consider as graph edges using the following approach.
+%A typical approach for generating edges produces one between all adjacent segments. 
+%Two segments $l_1$ and $l_2$ are considered adjacent if there is a pair of adjacent voxels with one labeled $l_1$ and the other labeled $l_2$.
+%For example, pixel-based agglomeration methods such as mean agglomeration~\cite{lee2017superhuman} or waterz~\cite{funke2017deep} consider all pairs of adjacent segments for merging.
+%However, this method produces too many edges in the graph for graph-based optimization approaches. 
+Our key observation is that if two segments belong to the same neural structure, their skeleton end points should satisfy certain geomtry constraints.
+%We identify a smaller number of pairs of segments to consider as graph edges using the following approach.
 
-First, we extract a skeleton from each segment in the label volume using a variant~\cite{zhao2014automatic} of the TEASER algorithm~\cite{sato2000teasar}. 
+To extract the skeleton from each segment, we use a variant~\cite{zhao2014automatic} of the TEASER algorithm~\cite{sato2000teasar}. 
 This skeletonization algorithm repeatedly uses Dijkstra's algorithm to find the farthest voxel from a seed location. 
@@
 
-Two segments, $s_1$ and $s_2$, receive a corresponding edge if the two following conditions hold.
+\TODO{maybe good to have equation, to make the biological constraints stand out more}
+Two segments, $s_1$ and $s_2$, receive a corresponding edge if the two following conditions hold. \TODO{what's the intuition}
 First, a endpoint in either $s_1$ or $s_2$ is with $t_{low}$ nm of any voxel in the other segment.
@@
 \end{figure}
-\subsection{Edge Weights Assignment}
+\subsection{Learning-based Edge Weight}
 \label{sec:edge-weights}
-We assign edge weights $w_e$ to each edge where the weight corresponds to the probability that two nodes belong to the same neuron.
-We train a 3D CNN classifier to learn from the manually labeled oversegmentation input volume (Sec.~\ref{sec:dataset}).
-If the probability that the nodes belong to the same neuron is $p_e$, the edge weight $w_e = \log{\frac{p_e}{1 - p_e}} + \log{\frac{1 - \beta}{\beta}}$, where $\beta$ is a tunable parameter that encourages over- or under-segmentation.
+We aim to assign edge weights $w_e$ to each edge corresponding to the possibility of two nodes belonging to the same neural structure.
+W, we train a 3D CNN model to learn these geometric contraints for valid connection between two segments from labeled volume.
 
-\subsubsection{Classifier Input}
+\noindent\textbf{Edge Probability}
+As it's hard to manually design the weight
+Below, we describe the network we trained to predict $p_e$.
 
-We extract a cubic region of interest (ROI) around each endpoint $e$ in $\mathbb{S}_c$ as input to the CNN. 
+%\subsubsection{Network Architecture}
+Our network is a feedforward convolutional network with three \textit{VGG-style} convolution blocks~\cite{chatfield2014return} and two fully connected layers before the final sigmoid activation. 
+Each \textit{VGG-style} convolution block consists of two double convolutions with filter size $3\times3\times3$ and LeakyReLU(0.0005), followed by a max pooling with filter size \TODO{xx}.
+
+For the input of the network, we extract a cubic region of interest (ROI) around each endpoint $e$ in $\mathbb{S}_c$ as input to the CNN. 
 The CNN receives three input channels for every voxel in the ROI around segments $l_1$ and $l_2$. 
@@
 
-\subsubsection{Network Architecture \& Training}
+\noindent\textbf{Edge Weight}
+To add more control.. \TODO{what's the intuition}
+Given the probability that the nodes belong to the same neuron is $p_e$, the edge weight $w_e$ is defined as
+%p_e &=\mbox{CNN}(x_1, x_2) \\
+\begin{align}
+w_e = \log{\frac{p_e}{1 - p_e}} + \log{\frac{1 - \beta}{\beta}}
+\end{align}
+, where $\beta$ is a tunable parameter that encourages over- or under-segmentation. 
+%The first two max pooling layers are anisotropic with pooling only in the $x$ and $y$ dimensions. 
+%The output of this final pooling step is flattened into a 1D vector that is input into . 
+%The final layer produces probabilities with a sigmoid activation function~\cite{funahashi1989approximate}. 
+%All of the other activation functions are .
 
-We use \textit{VGG-style} blocks as presented by Chatfield et al.~\cite{chatfield2014return}. 
-Each blocks consists of two double convolutions with filter size $3\times3\times3$ followed by a max pooling step. 
-There are three layers of these blocks. 
-The first two max pooling layers are anisotropic with pooling only in the $x$ and $y$ dimensions. 
-The output of this final pooling step is flattened into a 1D vector that is input into two fully connected layers. 
-The final layer produces probabilities with a sigmoid activation function~\cite{funahashi1989approximate}. 
-All of the other activation functions are LeakyReLU~\cite{maas2013rectifier}.
-
-For training we use a stochastic gradient descent optimizer with Nesterov's accelerated gradient~\cite{nesterov1983method}. 
-We employ dropouts of $0.2$ after every pooling layer and the first dense layer, and a dropout of $0.5$ after the final dense layer to prevent overfitting. 
-We discuss all other network parameters in Sec.~\ref{sec:network-parameters}.
-
-\subsection{Graph Clustering}
+% covered in the experiment
+%For training we use a stochastic gradient descent optimizer with Nesterov's accelerated gradient~\cite{nesterov1983method}. 
+%We employ dropouts of $0.2$ after every pooling layer and the first dense layer, and a dropout of $0.5$ after the final dense layer to prevent overfitting. 
+%We discuss all other network parameters in Sec.~\ref{sec:network-parameters}.
 
@@
 \end{figure}
-\subsubsection{Lifted Multicut}
+\subsection{Optimization-Based Graph Partition}
+intro: blah,blah. \TODO{can we have a formula here?}
 
+%\subsubsection{Lifted Multicut}
+\noindent\textbf{Lifted Multicut}
 After constructing the 3D graph we seek to partition the graph into labels where every label corresponds to a neuronal process. 
@@
 
-\subsubsection{Topological Constraints}
-
+%\subsubsection{Topological Constraints}
+\noindent\textbf{Topological Constraints}
 By reformulating the segmentation problem as a graph partitioning one, we can enforce some global constraints on our result based on the underlying biology.

### 2018-03-14 papers/eccv2018/3_evaluation.tex
pass on exp and result

@@
 
-\subsubsection{Kasthuri}
+%\subsubsection{Kasthuri}
+\noindent\textbf{Kasthuri}
 The Kasthuri dataset consists of scanning electron microscope images of the neocortex of a mouse brain~\cite{kasthuri2015saturated}. 
@@
 
-\subsubsection{FlyEM}
+%\subsubsection{FlyEM}
+\noindent\textbf{FlyEM}
 The FlyEM dataset comes from the mushroom body of a 5-day old adult male \textit{Drosophila} fly imaged by a focused ion-beam milling scanning electron microscopy~\cite{takemura2017connectome}.
@@
 
-\subsubsection{Fib-25}
+%\subsubsection{Fib-25}
+\noindent\textbf{Fib-25}
 The Fib-25 dataset comes from the visual system of a \textit{Drosophila} fly~\cite{takemura2015synaptic}.
@@
 
-\subsection{Pixel-Based Segmentations}
-\label{sec:neuroproof}
-
+\subsection{Method Configuration}
+\noindent\textbf{Initial Segmentation}
+%\label{sec:neuroproof}
 %The segmentation of the Kasthuri dataset was computed by agglomerating 3D supervoxels produced by the watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}. 
@@
 
-\subsection{Graph Pruning Parameters}
-
+\noindent\textbf{Graph Generation}
 The two parameters for the graph pruning algorithm (Sec.~\ref{sec:skeletonization}) are $t_{low}$ and $t_{high}$. 
@@
 We explore these thresholds in greater detail in the supplemental material.
+During implementation, we use nanometers instead of voxels for these thresholds to have uniform units across all datasets.
+% Connectomics datasets often have lower sample resolutions in $z$ because of limitations during sample preparation. 
+% Using nanometers allows us to have uniform units across all of these datasets and calculate the thresholds in voxels at runtime.
+% Although the voxels vary between different datasets, the physical space remains constant.
 
-In our implementation we use nanometers for these thresholds and not voxels. 
-Connectomics datasets often have lower sample resolutions in $z$ because of limitations during sample preparation. 
-Using nanometers allows us to have uniform units across all of these datasets and calculate the thresholds in voxels at runtime.
-Although the voxels vary between different datasets, the physical space remains constant.
-
-\subsection{Classifier Training}
+\noindent\textbf{Edge Weight Learning}
 \label{sec:network-parameters}
-
 We use half of the Kasthuri and FlyEM datasets\footnote{Since the FlyEM datasets have significantly fewer examples, we initialize the network with the weights from the Kasthuri training and have an initial learning rate of $10^{-4}$.} for training and validation.
@@
 
-\subsubsection{Training Augmentation.}
-
+%\noindent\textbf{Training Augmentation.}
 Since our input is an existing segmentation of the EM images, there are very few training examples compared to per-pixel classifiers that can train on a unique window for each voxel. 
@@
 
+\noindent\textbf{Graph Partition} \TODO{parameters?}
+
 \subsection{Error Metrics}
 \label{sec:variation-of-information}
-
 We evaluate the performance of the different methods using the split variation of information (VI)~\cite{meila2003comparing}.

### 2018-03-14 papers/eccv2018/4_results.tex
eccv: fixed figures to be horizontally aligned
pass on exp and result

@@
 
-\subsection{Variation of Information Results}
-
+\subsection{Connectomics Benchmark}
 In Fig.~\ref{fig:variation-of-information}, we show the VI results of the pixel-based reconstructions of the Kasthuri and FlyEM data (Sec.~\ref{sec:neuroproof}) for varying thresholds of agglomeration (green).
@@
 
-\subsection{Graph Pruning Results}
+\subsection{Empirical Ablation Studies}
+Below, we analyze various design choiceswe for each step of our pipeline.
 
+\noindent\textbf{Graph Generation.}
 Table \ref{table:skeletonization} shows the results of pruning the skeleton graph using the algorithm discussed in Sec.~\ref{sec:skeletonization}. 
@@
 	\centering
-	\includegraphics[width=0.45\linewidth]{./figures/merge_candidate1.png}		\includegraphics[width=0.45\linewidth]{./figures/merge_candidate2.png}
-	\includegraphics[width=0.45\linewidth]{./figures/merge_candidate2.png}
-	\includegraphics[width=0.45\linewidth]{./figures/merge_candidate2.png}
+	\begin{minipage}{0.45\linewidth}
+		\includegraphics[width=\linewidth]{./figures/merge_candidate1.png}	
+	\end{minipage}
+	\hfill
+	\begin{minipage}{0.45\linewidth}	
+		\includegraphics[width=\linewidth]{./figures/merge_candidate2.png}
+	\end{minipage}
+	\begin{minipage}{0.45\linewidth}
+		\includegraphics[width=\linewidth]{./figures/merge_candidate3.png}
+	\end{minipage}
+	\begin{minipage}{0.45\linewidth}
+		\includegraphics[width=\linewidth]{./figures/merge_candidate4.png}
+	\end{minipage}
 	\caption{The top two examples correspond to segment pairs that we incorrectly prune from the graph.
@@
 
-\subsection{CNN Classification Results}
-
-\subsubsection{Inference Augmentation}
-
+%\subsection{CNN Classification Results}
+\noindent\textbf{Edge Weight Learning}
+We first evaluate the effectiveness of inference augmentation.
+%\subsubsection{Inference Augmentation}
+%\noindent\textbf{Inference Augmentation.}
 Data augmentation at test time can improve accuracy results~\cite{zeng2017deepem3d,lee2017superhuman}.
@@
 
-\subsubsection{Generalization to Other Datasets}
-
+%\subsubsection{Generalization to Other Datasets}
+%\noindent\textbf{Generalization to Other Datasets.}
+We also evaluate the generalization to other datasets.
 Our neural network does not take as input the images or affinities to allow us to transfer network weights from one dataset to the next.
@@
 
-\subsection{Graph Optimization Results}
-
+%\subsection{Graph Optimization Results}
+\noindent\textbf{Graph Partition}
 The graph optimization strategy using multicut increases our accuracy over using just the CNN.
@@
 \subsection{Computational Performance}
-
-\subsubsection{System} All performance experiments ran on an Intel Core i7-6800K CPU 3.40 GHz with a Titan X Pascal GPU.
+%\subsubsection{System} 
+\noindent\textbf{System}
+All performance experiments ran on an Intel Core i7-6800K CPU 3.40 GHz with a Titan X Pascal GPU.
 All code is written in Python and will be freely available upon paper decision.

### 2018-03-14 papers/eccv2018/paper.tex
pass on exp and result

@@
 %An agglomerative segmentation algorithm merges initial pair of clusters.
-Current state-of-the-art connectome reconstruction pipelines have three major steps: affinity prediction from raw voxels, initial segmentation with watershed transform and refined segmentation with agglomeration.
+Current state-of-the-art connectome reconstruction pipelines have two major steps: initial pixel-based segmentation with affinity prediction and watershed transform, and refined segmentation with agglomeration.
 %In the past deTraditionally, neuron segmentation from 3D electron microscopy (EM)

### 2018-03-14 papers/eccv2018/0_introduction.tex
paper: major updates

@@
 	\caption{Biological constraints for 3D segments in Connectomics.}
-	\label{fig:bc}
+	\label{fig:biological_constraints}
 \end{figure}
 
-The field of connectomics is concerned about reconstructing the wiring diagram of the brain at nanometer resolutions to enable new insights into the workings of the brain~\cite{haehn2017scalable,kasthuri2015saturated}.
+The field of connectomics considers the problem of reconstructing the wiring diagram of the brain at nanometer resolutions to enable new insights into the workings of the brain~\cite{haehn2017scalable,kasthuri2015saturated}.
 %Recent advancements in image acquisition using multi-beam serial-section electron microscopy (sSEM) allow researchers to produce terabytes of image data per hour~\cite{hildebrand2017whole}. 
 %It is infeasible for domain experts to manually reconstruct this vast amount of image data~\cite{haehn2014design}. 
-State-of-the-art automatic 3D reconstruction approaches use pixel-based convolutional neural networks (CNNs) and watershed transform to generate initial segmentation, followed by agglomeration steps~\cite{seymour2016rhoananet,lee2015recursive,nunez2014graph,parag2017anisotropic,ronneberger2015u,zlateski2015image}.
-%These \textit{bottom-up pixel-based} methods produce excellent results but still fall short of acceptable error rates for large volumes.
-For the agglomeration, most methods do not make use of the biological knowledge of the 3D shape of neural structures.
+State-of-the-art automatic 3D reconstruction approaches use pixel-based convolutional neural networks (CNNs) and watershed transforms to generate initial segmentation, followed by agglomeration steps~\cite{seymour2016rhoananet,lee2015recursive,nunez2014graph,parag2017anisotropic,ronneberger2015u,zlateski2015image}.
+For the agglomeration, most methods do not use prior biological knowledge of the 3D shape of neural structures.
 Reported on small-sized volumes, a simple threshold-based mean agglomeration method can achieve superhuman result~\cite{lee2017superhuman}.
-However, it is unclear if it is the case for larger volumes.
+However, it is unclear if that is the case for larger volumes.
 
@@
 %We present a \textit{top-down graph-based} method that builds on the outputs of bottom-up pixel-based segmentation approaches. 
-We here present a new agglomeration method that imposes both local and global biological constraints onto the output segmentation to match the underlying structure of neuronal processes.
-We first extract skeletons from labels in the input segmentation and generate a simplified graph (Fig.~\ref{fig:teaser}a). 
-Next, we train a CNN classifier to learn biological constraints on the local structural shape of a neuron (Fig.~\ref{fig:teaser}b). 
+We present a new agglomeration framework that imposes both local and global biological constraints onto the output segmentation to match the underlying structure of neuronal processes.
+We first extract skeletons from labels in the input segmentation and generate a simplified graph (Fig.~\ref{fig:teaser_pipeline}a). 
+Next, we train a CNN classifier to learn biological constraints on the local structural shape of a neuron (Fig.~\ref{fig:teaser_pipeline}b). 
 This classifier produces probabilities that two segments belong to the same neuron based on the input shapes of the segments.
 These probabilities correspond to edge weights in our graph extracted from the input segmentation.
-We then use a graph optimization algorithm to partition the graph into a final improved reconstruction by enforcing domain-specific topological constraints from biology (Fig.~\ref{fig:teaser}c).
+We then use a graph optimization algorithm to partition the graph into a final improved reconstruction by enforcing domain-specific topological constraints from biology (Fig.~\ref{fig:teaser_pipeline}c).
 
@@
 %This allows us to leverage both local and global information to produce more accurate reconstructions. 
-With the biological constraints, we can make use of both geometric and topological prior information to produce more accurate reconstructions.
-\TODO{refer to figure 1}
+With the biological constraints, we can make use of both geometric and topological prior information to produce more accurate reconstructions (Fig.~\ref{fig:biological_constraints}).
 Our method is independent of image resolution and acquisition parameters, enabling its application to isotropic and anisotropic image data without retraining.
@@
 
-This work makes three contributions.
-First, a novel top-down framework that extracts graphs from skeletonized 3D segmentations for improved neural reconstruction of connectomics data; 
-Then, a region-based CNN classifier to detect errors; 
+This work makes three contributions:
+first, a novel top-down framework that extracts graphs from skeletonized 3D segmentations for improved neural reconstruction of connectomics data; 
+next, a region-based CNN classifier to detect errors; 
 %(3) an empirical evaluation of our method on several connectomics datasets;  % this is not contribution
-Last, improved performance over a state-of-the-art pixel-based reconstruction approach on average by \TODO{XX}\% with suitable running times.
+last, improved performance over a state-of-the-art pixel-based reconstruction approach on average by \TODO{XX}\% with suitable running times.

### 2018-03-14 papers/eccv2018/2_method.tex
paper: major updates

@@
 	\centering
-	\includegraphics[width=\linewidth]{./figures/teaser_v2.png}
+	\includegraphics[width=\linewidth]{./figures/teaser-image.png}
 	\caption{Our proposed framework uses both local and global biological constraints to improve an input segmentation.}
@@
 \end{figure}
-% \begin{figure*}[t!]
+%\begin{figure*}[t!]
 %	\begin{center}
@@
 
-%There are two types of errors that can occur in connectomics segmentations: \textit{split errors} and \textit{merge errors}. 
-%In a split error, two segments should have been merged into one neuronal process. 
-%In a merge error, one segment corresponds to more than one neuron.
-%Generally, it is much more difficult to correct merge errors than to correct split errors, as the space of possible split proposals grows quickly~\cite{parag2015properties}.
-%Thus, most reconstruction approaches are tuned towards over-segmentation with many more split than merge errors. 
+There are two types of errors that can occur in connectomics segmentations: \textit{split errors} and \textit{merge errors}. 
+In a split error, two segments should have been merged into one neuronal process (Fig.~\ref{fig:improved-reconstruction}). 
+In a merge error, one segment corresponds to more than one neuron.
+Generally, it is much more difficult to correct merge errors than to correct split errors, as the space of possible split proposals grows quickly~\cite{parag2015properties}.
+Thus, most reconstruction approaches are tuned towards over-segmentation with many more split than merge errors. 
 The input of our method is the over-segmentation of EM image volumes from state-of-the-art pipelines.
+
 Our pipeline is illustrated in Fig.~\ref{fig:teaser_pipeline}.
-%Our goal is to identify locations of split errors and merge the corresponding segments automatically.
-
-\TODO{[refer to teaser figure of the pipeline]}
-\TODO{[need to be concise here]}
-\TODO{[we use biological constraints]}
 From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with weights $w_e$. 
@@
 We propose the following three steps to formulate and then partition the graph while obeying constraints from the underlying biology.
-First, we only consider merging segments based on a skeletonized representation of the input segmentation.
+First, we only consider merging segments based on a skeletonized representation of the input segmentation (Fig.~\ref{fig:teaser_pipeline}a).
 This is enables us to reduce the number of nodes in the graph based on prior knowledge of the shape of neuronal processes.
-Second, we train a convolutional neural network that learns biological constraints based on the shapes of the input segmentation.
+Second, we train a convolutional neural network that learns biological constraints based on the shapes of the input segmentation (Fig.~\ref{fig:teaser_pipeline}b).
 This network generates probabilities that segments belong to the same neuron based only on the segmentations. 
 An example of one such learned constraint is that neurons have small turning radii (Fig.~\ref{fig:turn-radii}).
-Third, we partition the graph using a lifted multicut formulation with additional acyclic constraints to enforce global biological constraints.
+Third, we partition the graph using a lifted multicut formulation with additional acyclic constraints to enforce global biological constraints (Fig.~\ref{fig:teaser_pipeline}c).
 The lifted multicut solution is globally consistent which we then augment to produce a tree-structured graph (i.e., one with no cycles).
@@
 Most agglomeration methods create the region graph by removing small-sized segments and linking each pair of adjacent segments, which can still lead to a large graph size due to the irregular shape of neural structures.
-We here use the skeleton representation of the segmenation and reduce the graph size with the geometric constraints on the connectivity of two adjacent segments to prune edges.
+We here use the skeleton representation of the segmentation and reduce the graph size with the geometric constraints on the connectivity of two adjacent segments to prune edges.
 % a bit trivial, as everyone is doing this. maybe no need to mention
@@
 %However, this method produces too many edges in the graph for graph-based optimization approaches. 
-Our key observation is that if two segments belong to the same neural structure, their skeleton end points should satisfy certain geomtry constraints.
-%We identify a smaller number of pairs of segments to consider as graph edges using the following approach.
-
+Our key observation is that if two segments belong to the same neuronal process, their skeleton end points should satisfy certain geometric constraints.
 To extract the skeleton from each segment, we use a variant~\cite{zhao2014automatic} of the TEASER algorithm~\cite{sato2000teasar}. 
@@
 Since this algorithm is non-linear in the number of voxels, we downsample the datasets so that there are voxel samples every $\SI{30}{\nano\meter}$ in each dimension.
-Empirically, this reduced the running time for skeletonization by $\TODO{XX\%}$, with minimal reduction in skeleton accuracy ($\TODO{XX\%}$ fewer branches). 
+Empirically, this reduced the running time for skeletonization by $30\times$, with minimal reduction in skeleton accuracy (${\sim}5\%$ fewer branches). 
 Fig.~\ref{fig:skeletonization} shows four examples of extracted skeletons (in black). 
-These skeletons consist of a sequence of \textit{joints}, i.e., locations that are locally a maximum distance from the segment boundary, with line segments connecting successive joints. 
+These skeletons consist of a sequence of \textit{joints}, locations that are locally a maximum distance from the segment boundary, with line segments connecting successive joints. 
 We refer to joints that have only one connected neighbor as \textit{endpoints}. 
-We find that approximately \TODO{XX\%} of the segments that are erroneously split have nearby endpoints (Fig.~\ref{fig:merge_candidates}).
+We find that approximately 70\% of the segments that are erroneously split have nearby endpoints (Fig.~\ref{fig:merge_candidates}).
 
-\TODO{maybe good to have equation, to make the biological constraints stand out more}
-Two segments, $s_1$ and $s_2$, receive a corresponding edge if the two following conditions hold. \TODO{what's the intuition}
+Two segments, $s_1$ and $s_2$, receive a corresponding edge if the two following conditions hold.
 First, a endpoint in either $s_1$ or $s_2$ is with $t_{low}$ nm of any voxel in the other segment.
@@
 Only these pairs have a corresponding edge in the constructed graph.
+These parameters follow empirically from noise in the skeleton generation process. 
+There are occasionally spurious branches and other artifacts and these thresholds mitigate the influence of these degenerate locations.
+We provide a fuller analysis in the supplemental materials.
 
@@
 \label{sec:edge-weights}
-We aim to assign edge weights $w_e$ to each edge corresponding to the possibility of two nodes belonging to the same neural structure.
-W, we train a 3D CNN model to learn these geometric contraints for valid connection between two segments from labeled volume.
+We assign an edge weight $w_e$ to each edge corresponding to the probability that two nodes belong to the same neuronal process.
+We train a 3D CNN model to learn these geometric constraints for valid connection between two segments from labeled volume.
 
 \noindent\textbf{Edge Probability}
-As it's hard to manually design the weight
-Below, we describe the network we trained to predict $p_e$.
-
-%\subsubsection{Network Architecture}
-Our network is a feedforward convolutional network with three \textit{VGG-style} convolution blocks~\cite{chatfield2014return} and two fully connected layers before the final sigmoid activation. 
-Each \textit{VGG-style} convolution block consists of two double convolutions with filter size $3\times3\times3$ and LeakyReLU(0.0005), followed by a max pooling with filter size \TODO{xx}.
+To predict the probabilities that two segments belong to the same neuron, we train a feed-forward convolutional network with three \textit{VGG-style} convolution blocks~\cite{chatfield2014return} and two fully connected layers before the final sigmoid activation.
+Each \textit{VGG-style} convolution block consists of two double convolutions with filter size $3\times3\times3$ and LeakyReLU(0.0005), followed by a max pooling with filter size $2\times2\times1$ in the first two blocks and $2\times2\times2$ in the third.
 
@@
 \noindent\textbf{Edge Weight}
-To add more control.. \TODO{what's the intuition}
+
 Given the probability that the nodes belong to the same neuron is $p_e$, the edge weight $w_e$ is defined as
@@
 , where $\beta$ is a tunable parameter that encourages over- or under-segmentation. 
+This particular weighting scheme allows us to optimize for a Bayesian network defined on the graph~\cite{keuper2015efficient,andres2011probabilistic}.
+
 %The first two max pooling layers are anisotropic with pooling only in the $x$ and $y$ dimensions. 
@@
 \subsection{Optimization-Based Graph Partition}
-intro: blah,blah. \TODO{can we have a formula here?}
+
+After graph construction, we segment the graph into a globally consistent manner while enforcing topological constraints on the output.
 
@@
 \noindent\textbf{Lifted Multicut}
-After constructing the 3D graph we seek to partition the graph into labels where every label corresponds to a neuronal process. 
+After constructing the graph we seek to partition it into labels where every label corresponds to a neuronal process. 
 We formulate this graph partitioning problem as a multicut problem.
 There are two primary benefits to using a multicut formulation. 
-First, the number of segments in the final graph is not predetermined but depends on the input graph itself. 
-Second, this minimization produces globally consistent solutions (i.e. a boundary remains if and only if the two corresponding nodes belong to unique segments)~\cite{keuper2015efficient}.
+First, the number of segments in the final graph is not predetermined but depends on the input. 
+Second, this minimization produces globally consistent solutions (i.e. a boundary remains only if the two corresponding nodes belong to unique segments)~\cite{keuper2015efficient}.
 
@@
 These penalties between non-adjacent nodes are called ``lifted'' edges. 
-Ideally these ``lifted'' weights represent the probability that two nodes belong to the same neuron given all such possible paths in the graph between the nodes.
+Ideally these ``lifted'' weights represent the probability that two nodes belong to the same neuron.
 However, determining such probabilities is computationally expensive.
 We approximate these probabilities by finding the maximal probable path between any two nodes using Dijkstra's algorithm~\cite{keuper2015efficient}.
+This is an underestimate of the probability that two nodes belong to the same neuron since it does not consider all possible paths.
 Since our graphs are sufficiently small, we can generate ``lifted'' edges between all pairs of nodes.

### 2018-03-14 papers/eccv2018/3_evaluation.tex
paper: major updates

@@
 Popular challenge datasets such as CREMI and SNEMI3D are simply too small for any noticeable change. 
-The following three datasets contain from 4 to 40 times more volume than the CREMI datasets.
+The following datasets contain 4 times more volume than the CREMI datasets.
 
@@
 %\subsubsection{Fib-25}
-\noindent\textbf{Fib-25}
-The Fib-25 dataset comes from the visual system of a \textit{Drosophila} fly~\cite{takemura2015synaptic}.
-This sample is imaged at a resolution of $\SI[product-units=single]{8 x 8 x 8}{\nano\meter}^3$ and has $2588 \times 2108 \times 2876$ voxels representing a volume of $\SI[product-units=single]{23.0 x 16.9 x 23.0}{\micro\meter}^3$.
-There is currently a reconstruction challenge based on this sample.
+%\noindent\textbf{Fib-25}
+%The Fib-25 dataset comes from the visual system of a \textit{Drosophila} fly~\cite{takemura2015synaptic}.
+This sample is %imaged at a resolution of $\SI[product-units=single]{8 x 8 x 8}{\nano\meter}^3$ and has $2588 \times 2108 \times 2876$ %voxels representing a volume of $\SI[product-units=single]{23.0 x 16.9 x 23.0}{\micro\meter}^3$.
+%There is currently a reconstruction challenge based on this sample.
 
@@
 We used exactly the same parameters as the publicly available code for this algorithm.
-For the Fib-25 challenge dataset, we use the segmentation from Funke et al. as our input~\cite{funke2017deep}.
+%For the Fib-25 challenge dataset, we use the segmentation from Funke et al. as our input~\cite{funke2017deep}.
 
@@
 \label{sec:network-parameters}
-We use half of the Kasthuri and FlyEM datasets\footnote{Since the FlyEM datasets have significantly fewer examples, we initialize the network with the weights from the Kasthuri training and have an initial learning rate of $10^{-4}$.} for training and validation.
+We use half of the Kasthuri dataset for training and validation. 
 We train on 80\% of the potential merge candidates for this volume.
 We validate the CNN classifier on the remaining 20\% of the candidates. 
+Since our input does not require the image data, we can train on the anisotropic Kasthuri data and test on the isotropic FlyEM data.
 
@@
 
-\noindent\textbf{Graph Partition} \TODO{parameters?}
+\noindent\textbf{Graph Partition}
+We assign the edges in our graph a weight $w_e = \log{\frac{p_e}{1 - p_e}} + \log{\frac{1 - \beta}{\beta}}$ where $\beta$ is a tunable parameter. 
+Higher values of $\beta$ encourage over-segmentation.
+Figure~\ref{fig:variation-of-information} shows our results for variables $\beta \in [0.5, 0.9]$. 
+For our multicut analysis we consider $\beta = 0.5$.
 
@@
 
-We use both precision and recall to evaluate the convolutional neural network and multicut outputs. 
+We use precision and recall to evaluate the convolutional neural network and multicut outputs. 
 Since our method attempts to only correct \textit{split errors}, we define a true positive as a pair of segments that are correctly merged together after our pipeline.

### 2018-03-14 papers/eccv2018/3_evaluation.tex
merging evaluation

--- 2018-03-13 papers/eccv2018/3_evaluation.tex
@@
 
-\subsubsection{Fib-25}
-The Fib-25 dataset comes from the visual system of a \textit{Drosophila} fly~\cite{takemura2015synaptic}.
+%\subsubsection{Fib-25}
+%The Fib-25 dataset comes from the visual system of a \textit{Drosophila} fly~\cite{takemura2015synaptic}.
 This sample is imaged at a resolution of $\SI[product-units=single]{8 x 8 x 8}{\nano\meter}^3$ and has $2588 \times 2108 \times 2876$ voxels representing a volume of $\SI[product-units=single]{23.0 x 16.9 x 23.0}{\micro\meter}^3$.
-There is currently a reconstruction challenge based on this sample.
+%There is currently a reconstruction challenge based on this sample.
 

### 2018-03-14 papers/eccv2018/1_related_work.tex

--- 2018-03-14 papers/eccv2018/1_related_work.tex
@@
 
-% \begin{figure}[t]
-% 	\subfloat[]{
-% 		\includegraphics[width=.47\linewidth]{figures/schema/pre-multicut-with-arrows.pdf}
-% 	}
-% 	\subfloat[]{
-% 		\includegraphics[width=.47\linewidth]{figures/schema/post-multicut.png}
-% 	}
-% 	\caption{Example improvement of neural reconstruction.
+\begin{figure}[t]
+ 	\subfloat[]{
+ 		\includegraphics[width=.47\linewidth]{figures/schema/pre-multicut-with-arrows.pdf}
+ 	}
+ 	\subfloat[]{
+ 		\includegraphics[width=.47\linewidth]{figures/schema/post-multicut.png}
+ 	}
+ 	\caption{Example improvement of neural reconstruction.
 (a) We extract 3D skeletons from pixel-based segmentation algorithms to create a graph representation.
@@
 (b) We improve the segmentation accuracy using a graph partitioning algorithm, leveraging both local and global information.}
-% 	\label{fig:improved-reconstruction}
-% \end{figure}
+ 	\label{fig:improved-reconstruction}
+\end{figure}
 
-\subsubsection{Initial Segmentation}
+\subsubsection{Pixel-Based Segmentation}
 A significant amount of connectomics research considers the problem of extracting segmentation information at the voxel level from raw EM images.
-
 First, intermediate representations like boundary or affinity maps are generated.
@@
 Most recent advancements use convolutional neural networks since machine-learned features outperform hand-designed ones~\cite{bogovic2013learned}.
-Originally, networks predicted membrane probabilities per each image slice using 2D convolutions~\cite{seymour2016rhoananet,ronneberger2015u,ciresan2012deep,jain2010boundary,kaynig2015large,amelio_segmentation}.
-However, recent research extends these convolutions to include the z-dimension improving performance~\cite{lee2015recursive,parag2017anisotropic,cciccek20163d,turaga2010convolutional}.
+Originally, networks predicted membrane probabilities per each image slice using 2D convolutions~\cite{seymour2016rhoananet,ronneberger2015u,kaynig2015large,ciresan2012deep,jain2010boundary,amelio_segmentation}.
+More recent research extends these convolutions to include the z-dimension improving performance~\cite{lee2015recursive,parag2017anisotropic,cciccek20163d,turaga2010convolutional}.
 Many of these networks produce probabilities for the affinity between two voxels (i.e., the probability that adjacent voxels belong to the same neuron). 
@@
 
-Then, these intermediate representations are transformed into segmentation.
+\subsubsection{Region Agglomeration}
+Next, agglomeration techniques transform these intermediate representations into segmentations.
 Some early techniques apply computationally expensive graph partitioning algorithms with a single node per superpixel~\cite{andres2012globally}.
 Several pixel-based approaches generate probabilities that neighboring pixels belong to the same neuron.
-Often a watershed algorithm will then cluster pixels into super-pixels~\cite{zlateski2015image}.
+Often a watershed algorithm will then cluster these pixels into super-pixels~\cite{zlateski2015image}.
+Some methods rely solely on the accuracy of the predicted affinities and agglomerate hierarchically based on the mean affinity between supervoxels~\cite{lee2017superhuman,funke2017deep}.
+Given the initial segmentation, others train random-forest classifiers to produce the final segmentations~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image,10.1371/journal.pone.0125825}
+extract different features~\cite{bogovic2013learned,jain2011learning}.
+Pape et al. present a scalable multicut algorithm to partition superpixels~\cite{beier2017multicut}.
+In our work, we combine these last two strategies of classification and optimization.
 
-\subsubsection{Agglomeration}
-Given the initial segmentation, some methods train random-forest classifiers to produce the final segmentations~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image,10.1371/journal.pone.0125825}.
-Some methods rely solely on the accuracy of the predicted affinities and agglomerate hierarchically based on the mean affinity between supervoxels~\cite{lee2017superhuman,funke2017deep}.
-Pape et al. present a scalable multicut algorithm to partition superpixels~\cite{beier2017multicut}.
-\TODO{add learning-based algorithm} ~\cite{jain2011learning,bogovic2013learned}
+\subsubsection{Error-correction methods}
+Additional research builds on top of these region-based methods to correct errors in the segmentation either using human proofreading~\cite{haehn2014design,haehn2017guided,mojo2} or automatic methods~\cite{rolnick2017morphological,error_correction_using_CNN}.
+Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for traditional image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}.
+Even though graph partitioning is an NP-Hard problem~\cite{demaine2006correlation} there are several useful multicut heuristics that provide good approximations with reasonable computational costs~\cite{horvnakova2017analysis}.
+We extract a 3D graph from an input segmentation for a true top-down error correction approach. 
+This allows us to enforce domain-specific biological constraints while using graph partitioning algorithms. 
+We use the method of Keuper et al.~\cite{keuper2015efficient} to partition the extracted graph into the final neural reconstruction.
+
 %\subsubsection{Error-correction methods}

### 2018-03-14 papers/eccv2018/4_results.tex

@@
 \subsection{Connectomics Benchmark}
-In Fig.~\ref{fig:variation-of-information}, we show the VI results of the pixel-based reconstructions of the Kasthuri and FlyEM data (Sec.~\ref{sec:neuroproof}) for varying thresholds of agglomeration (green).
+
+In Fig.~\ref{fig:variation-of-information}, we show the VI results of the pixel-based reconstructions of the Kasthuri and FlyEM data (Sec.~\ref{sec:dataset}) for varying thresholds of agglomeration (green).
 We use one of these segmentations (green circle) as our input dataset with an agglomeration threshold of 0.3 for all datasets. 
@@
 Scores closer to the origin are better for this metric, and in every instance our results are below the green curve.
-We see significant improvements on the Kasthuri datasets (VI split reduction of \TODO{XX}\%) and more modest improvements on the FlyEM dataset (reduction of \TODO{XX}\%) and Fib-25 dataset (reduction of \TODO{XX}\%).
+We see significant improvements on the Kasthuri datasets (VI split reduction of \TODO{XX}\%) and more modest improvements on the FlyEM datasets (reduction of \TODO{XX}\% and \TODO{XX}\%).
 
@@
 \subsection{Empirical Ablation Studies}
-Below, we analyze various design choiceswe for each step of our pipeline.
 
@@
 Table \ref{table:skeletonization} shows the results of pruning the skeleton graph using the algorithm discussed in Sec.~\ref{sec:skeletonization}. 
-This edge pruning is essential for the graph partitioning algorithm, which has a computational complexity dependence on the number of edges. 
+This edge pruning is essential for the graph partitioning algorithm, which has a non-linear computational complexity dependence on the number of edges. 
 The baseline algorithm considers all adjacent regions for merging. 
-Our method removes a significant portion of these candidates while maintaining a large number of the true merge locations (e.g., \TODO{XXX} compared to \TODO{XXX}). 
-Our pruning heuristic removes at least $\TODO{X}\times$ the number of edges on all datasets, achieving a maximum removal rate of $\TODO{XX}\times$.
+Our method removes a significant portion of these candidates while maintaining a large number of the true merge locations (e.g., 556 compared to 610). 
+Our pruning heuristic removes at least $3.5\times$ the number of edges on all datasets, achieving a maximum removal rate of $4.8\times$.
 However, there are some adjacent over-segmented labels which are not considered.
-Table~\ref{table:skeletonization} shows the results for our edge generation including the number of missed neighbors and potential penalty in VI score.
-We present additional analysis of the skeletonization parameters in the supplemental material.
 
@@
 		Kasthuri & 610 / 23506 & 556 / 4921 & 214 & 160 \\
-		FlyEM & 298 / 17614 & 197 / 4366 & 120 & 19 \\
-		FIB-25 &  & & & \\ \hline
+		FlyEM Vol. 1 & 304 / 15949 & 212 / 4578 & 105 & 13 \\
+		FlyEM Vol. 2 &  298 / 17614 & 197 / 4366 & 120 & 19 \\ \hline
 	\end{tabular}
@@
 The second and fourth examples in Fig.~\ref{fig:qualitative-results} show correctly reconstructed neurons where two of the segments are non-adjacent. 
-On average in our datasets we correctly merge \TODO{XX} number of non-adjacent segments.
+On average in our datasets we correctly merge \TODO{XX} of the non-adjacent segments.
 
@@
 In this example the small segment is carved from the larger segment in a location where there are no skeleton endpoints. 
-There are on average $\TODO{XX}$ such examples in our datasets, corresponding to $\TODO{XX}$ in the variation of information split score.
+There are on average 146 such examples in our datasets.
 
@@
 	\includegraphics[width=0.45\linewidth]{./figures/receiver-operating-characteristic.png}		\includegraphics[width=0.45\linewidth]{./figures/precision-and-recall.png}
-	\caption{The receiver operating characteristic (ROC) curves of our classifier on three connectomics datasets.
-The classifier works best on previously unseen data of the Kasthuri volume.
-The dashed blue line indicates better performance on the FlyEM datasets with retraining compared to without (solid blue).}
+	\caption{The receiver operating characteristic (ROC) curves of our classifier on three connectomics datasets. The classifier works best on previously unseen data of the Kasthuri volume.}
 	\label{fig:receiver-operating-characteristic}
@@
 %\noindent\textbf{Generalization to Other Datasets.}
-We also evaluate the generalization to other datasets.
-Our neural network does not take as input the images or affinities to allow us to transfer network weights from one dataset to the next.
-Table~\TODO{X} shows the result when training on the FlyEM data and inferring on the Kasthuri data and vice versa.
-The classification results are reasonable despite the fact that the datasets vary in resolution and even animal type.
+Our neural network does not take as input the images or affinities so we can transfer network weights from one dataset to the next.
+The classification results are reasonable on the FlyEM datasets despite the fact that the data varies in resolution and even animal type from the training set.
 
@@
 		\textbf{Dataset} & $\Delta$ \textbf{Precision} & $\Delta$ \textbf{Recall} & $\Delta$ \textbf{Accuracy} & $\Delta$ \textbf{Precision} & $\Delta$ \textbf{Recall} & $\Delta$ \textbf{Accuracy} \\ \hline
-		Kasthuri  &  &  & &  &  & \\
-		FlyEM &  & & &  &  &  \\
-		Fib-25&  & & & & & \\ \hline
+		Kasthuri  & 7.56\% & -3.83\% & 0.89\% & -5.67\% & -2.15\% & -1.03\% \\
+		FlyEM Vol. 1 & 4.50\% & -4.24\% & 0.26\% & -1.52\% & -2.97\% & -0.16\%  \\
+		FlyEM Vol. 2 & 5.54\% & -1.38\% & 0.26\% & -8.65\% & -2.75\% & -0.54\%\\ \hline
 	\end{tabular}
@@
 
-Our post-processing method to agglomerate segments while enforcing the acyclic nature of our graph additionally improves precision by $\TODO{XX}\%$ on average while only costing $\TODO{XX}\%$ in recall.
+Our post-processing method to agglomerate segments while enforcing the acyclic nature of our graph additionally improves precision by $6.6\%$ on average while only costing $-1.16\%$ in recall. 
 Note that our post-processing strategy by design cannot increase the recall.
@@
 We use the Keras deep learning library for our neural networks with Theano backend and cuDNN 7 acceleration for CUDA 8.0.
+
+Every step in our framework is fast enough on large connectomics datasets. 
+After downsampling, skeletonization takes less than 1 second per segment on average. 
+On average, each segment was skeletonized in 0.56 seconds on the training half of the Kasthuri data set. 
+There are 4451 such segments resulting in a total running time of 2,492 seconds on an 800 megavoxel volume. 
+From here, it took just over 31 seconds to generate the edges for our graph by considering nearby skeleton endpoints.
+On our hardware, inference on the neural network had a throughput of 30 examples per second. 
+Lastly, on this dataset the multicut algorithm ran for \TODO{XX} seconds while the lifted multicut variant spent \TODO{XX} seconds.

### 2018-03-14 algorithms/util.py
small updates

@@ -75,8 +75,8 @@ def CollapseGraph(segmentation, candidates, maintain_edges, probabilities, outpu
         for neighbor_label in adjacency_sets[label_one]:
             if neighbor_label == label_two: continue
 
-            if unionfind.Find(union_find[neighbor_label]).label == label_two_union_find: 
-                maintain_edges[ie] = True
+        if unionfind.Find(union_find[neighbor_label]).label == label_two_union_find: 
+            maintain_edges[ie] = True
 
         # skip if the edge is no longer collapsed
         if maintain_edges[ie]: continue

### 2018-03-14 cnns/skeleton/forward.py

@@ -60,7 +60,7 @@ def Forward(prefix, model_prefix, threshold, maximum_distance, endpoint_distance
     negative_candidates = FindCandidates(prefix, threshold, maximum_distance, endpoint_distance, network_distance, 'negative')
     candidates = positive_candidates + negative_candidates
     ncandidates = len(candidates)
-
+    
     # compute augmentations
     probabilities = np.zeros((ncandidates, 1), dtype=np.float64)
     for _ in range(naugmentations):

### 2018-03-14 cnns/skeleton/generate_features.py

@@ -95,7 +95,7 @@ def GenerateFeatures(prefix, threshold, maximum_distance, network_distance, endp
     # get all of the skeletons
     if topology: skeletons, endpoints = dataIO.ReadTopologySkeletons(prefix, thresholded_segmentation)
     else: skeletons, _, endpoints = dataIO.ReadSWCSkeletons(prefix, thresholded_segmentation)
-
+    
     # get the set of all considered pairs
     endpoint_candidates = [set() for _ in range(len(endpoints))]
     for ie, endpoint in enumerate(endpoints):
@@ -161,6 +161,7 @@ def GenerateFeatures(prefix, threshold, maximum_distance, network_distance, endp
 
                     midpoints[(label,neighbor_label)] = midpoint
                     midpoints[(neighbor_label,label)] = midpoint
+
 
     # create list of candidates
     positive_candidates = []

### 2018-03-14 data_structures/skeleton_formats.py

@@ -176,7 +176,7 @@ class SWCSkeleton:
 
         # get the skeleton filename
         filename = 'skeletons/NeuTu/{}/tree_{}.swc'.format(prefix, label)
-
+        
         # open the file and read all of the swc entries
         with open(filename, 'r') as fd:
             for joint in fd.readlines():

### 2018-03-14 evaluation/comparestacks.pyx
evaluation: removed some options for deadline

@@ -45,16 +45,9 @@ def CremiEvaluate(segmentation, gold, dilate_ground_truth=1, mask_ground_truth=T
     if dilate_ground_truth > 0:
         masked_gold = np.zeros(gold.shape, dtype=gold.dtype)
         border_mask.create_border_mask(gold, masked_gold, dilate_ground_truth, 0)
-    else:
-        masked_gold = np.copy(gold)
+        gold = np.copy(masked_gold)
 
-    # run the cremi variation of information algorithm
-    if mask_ground_truth: gold_mask = [0]
-    else: gold_mask = []
-    if mask_segmentation: segment_mask = [0]
-    else: segment_mask = []
-
-    vi_split, vi_merge = voi(segmentation, masked_gold, segment_mask, gold_mask)
+    vi_split, vi_merge = voi(segmentation, gold)
     print 'Variation of Information Full: {}'.format(vi_split + vi_merge)
     print 'Variation of Information Merge: {}'.format(vi_merge)
     print 'Variation of Information Split: {}'.format(vi_split)

### 2018-03-14 transforms/cpp-seg2seg.cpp
seg2seg: eased memory requirements

@@ -5,15 +5,11 @@
 
 
 
-long *CppMapLabels(long *segmentation, long *mapping, unsigned long nentries)
+void CppMapLabels(long *segmentation, long *mapping, unsigned long nentries)
 {
-  long *updated_segmentation = new long[nentries];
-  
   for (unsigned long iv = 0; iv < nentries; ++iv) {
-    updated_segmentation[iv] = mapping[segmentation[iv]];
+    segmentation[iv] = mapping[segmentation[iv]];
   }
-
-  return updated_segmentation;
 }
 
 

### 2018-03-14 transforms/cpp-seg2seg.h

@@ -1,3 +1,3 @@
-long *CppMapLabels(long *segmentation, long *mapping, unsigned long nentries);
+void CppMapLabels(long *segmentation, long *mapping, unsigned long nentries);
 long *CppRemoveSmallConnectedComponents(long *segmentation, int threshold, unsigned long nentries);
 long *CppForceConnectivity(long *segmentation, long zres, long yres, long xres);

### 2018-03-14 transforms/seg2seg.pyx

@@ -7,7 +7,7 @@ import scipy.ndimage
 
 
 cdef extern from 'cpp-seg2seg.h':
-    long *CppMapLabels(long *segmentation, long *mapping, unsigned long nentries)
+    void CppMapLabels(long *segmentation, long *mapping, unsigned long nentries)
     long *CppRemoveSmallConnectedComponents(long *segmentation, int threshold, unsigned long nentries)
     long *CppForceConnectivity(long *segmentation, long zres, long yres, long xres)
 
@@ -23,11 +23,9 @@ def MapLabels(segmentation, mapping):
     cdef np.ndarray[long, ndim=1, mode='c'] cpp_mapping
     cpp_mapping = np.ascontiguousarray(mapping, dtype=ctypes.c_int64)
 
-    cdef long *mapped_segmentation = CppMapLabels(&(cpp_segmentation[0,0,0]), &(cpp_mapping[0]), nentries)
+    CppMapLabels(&(cpp_segmentation[0,0,0]), &(cpp_mapping[0]), nentries)
 
-    cdef long[:] tmp_segmentation = <long[:segmentation.size]> mapped_segmentation
-
-    return np.reshape(np.asarray(tmp_segmentation), (zres, yres, xres))
+    return segmentation
 
 
 

### 2018-03-14 papers/eccv2018/0_introduction.tex
First pass of fixes.

@@
 We first extract skeletons from labels in the input segmentation and generate a simplified graph (Fig.~\ref{fig:teaser_pipeline}a). 
-Next, we train a CNN classifier to learn biological constraints on the local structural shape of a neuron (Fig.~\ref{fig:teaser_pipeline}b). 
+Next, we train a CNN classifier to learn biological constraints on the local structural shape of a neuron (Fig.~\ref{fig:teaser_pipeline}b). \TODO{The teaser is so far back - should be close by.}
 This classifier produces probabilities that two segments belong to the same neuron based on the input shapes of the segments.

### 2018-03-14 papers/eccv2018/2_method.tex
First pass of fixes.

@@
 	\includegraphics[width=\linewidth]{./figures/teaser-image.png}
-	\caption{Our proposed framework uses both local and global biological constraints to improve an input segmentation.}
+	\caption{Our proposed framework uses both local and global biological constraints to improve an input segmentation.
+We generate a simplified graph from an input segmentation (a), train a classifier to learn neuron shape constraints locally (b), and perform graph partitioning to enforce domain-specific properties globally.\TODO{Is it possible to have the weights next to the lines?}}
 	\label{fig:teaser_pipeline}

### 2018-03-14 papers/eccv2018/0_introduction.tex
pass on related work, use region merging instead of agglomeration

--- 2018-03-14 papers/eccv2018/0_introduction.tex
@@
 %It is infeasible for domain experts to manually reconstruct this vast amount of image data~\cite{haehn2014design}. 
-State-of-the-art automatic 3D reconstruction approaches use pixel-based convolutional neural networks (CNNs) and watershed transforms to generate initial segmentation, followed by agglomeration steps~\cite{seymour2016rhoananet,lee2015recursive,nunez2014graph,parag2017anisotropic,ronneberger2015u,zlateski2015image}.
-For the agglomeration, most methods do not use prior biological knowledge of the 3D shape of neural structures.
+State-of-the-art automatic 3D reconstruction approaches use pixel-based convolutional neural networks (CNNs) and watershed transforms to generate initial over-segmentation, followed by region merging steps~\cite{seymour2016rhoananet,lee2015recursive,nunez2014graph,parag2017anisotropic,ronneberger2015u,zlateski2015image}.
+For the region merging, most methods do not use prior biological knowledge of the 3D shape of neural structures.
 Reported on small-sized volumes, a simple threshold-based mean agglomeration method can achieve superhuman result~\cite{lee2017superhuman}.
 However, it is unclear if that is the case for larger volumes.
+\TODO{sth. about figure 1.}
 
@@
 %We present a \textit{top-down graph-based} method that builds on the outputs of bottom-up pixel-based segmentation approaches. 
-We present a new agglomeration framework that imposes both local and global biological constraints onto the output segmentation to match the underlying structure of neuronal processes.
+We present a new region merging framework that imposes both local and global biological constraints onto the output segmentation to match the underlying structure of neuronal processes.
 We first extract skeletons from labels in the input segmentation and generate a simplified graph (Fig.~\ref{fig:teaser_pipeline}a). 

### 2018-03-14 papers/eccv2018/1_related_work.tex
pass on related work, use region merging instead of agglomeration

--- 2018-03-14 papers/eccv2018/1_related_work.tex
@@
 
+%\noindent\textbf{Pixel-Based Segmentation}
 \subsubsection{Pixel-Based Segmentation}
-A significant amount of connectomics research considers the problem of extracting segmentation information at the voxel level from raw EM images.
+A significant amount of connectomics research considers the problem of extracting segmentation information at the voxel level of EM images.
+First, intermediate representations like boundary, affinity or binary segmentation maps are generated from voxels.
+For the boundary probabilities, random forest with hand-designed features~\cite{kaynig2015large}, 2D and 3D convolution networks ~\cite{bogovic2013learned,seymour2016rhoananet,ronneberger2015u,ciresan2012deep,jain2010boundary,amelio_segmentation}.
+Later, the affinity between each voxel and its six neighors are widely used~\cite{lee2015recursive,parag2017anisotropic,cciccek20163d,turaga2010convolutional,lee2017superhuman}.
+3D U-Net architecture becomes popular~\cite{cciccek20163d} and MALIS cost function is designed to re-weight affinity prediction by their contribution to the segmentation error~\cite{briggman2009maximin}.
+More recently, flood-filling networks~\cite{januszewski2016flood} produce binary segmentations from raw pixels with a recurrent convolution network at a high computational cost.
+Orthogonal to the representation, model averaging~\cite{zeng2017deepem3d} and data augmentation~\cite{lee2017superhuman} methods can further improve the performance, where Lee et al.~\cite{lee2017superhuman} surpass the estimated human accuracy on the SNEMI3D dataset.
 
-First, intermediate representations like boundary or affinity maps are generated.
-Some methods use a random forest populated with hand-designed features based on image characteristics around a given pixel to predict membrane probabilities~\cite{kaynig2015large}.
-Most recent advancements use convolutional neural networks since machine-learned features outperform hand-designed ones~\cite{bogovic2013learned}.
-Originally, networks predicted membrane probabilities per each image slice using 2D convolutions~\cite{seymour2016rhoananet,ronneberger2015u,ciresan2012deep,jain2010boundary,kaynig2015large,amelio_segmentation}.
-However, recent research extends these convolutions to include the z-dimension improving performance~\cite{lee2015recursive,parag2017anisotropic,cciccek20163d,turaga2010convolutional}.
-Many of these networks produce probabilities for the affinity between two voxels (i.e., the probability that adjacent voxels belong to the same neuron). 
-The MALIS cost function is specifically designed for generating affinities that produce good segmentations~\cite{briggman2009maximin}. 
-More recently, flood-filling networks produce segmentations by training an end-to-end neural network that goes from EM images directly to label volumes~\cite{januszewski2016flood}. 
-These networks produce impressive accuracies but at a high computational cost.
-Data augmentation in both training and testing can increase the prediction accuracy in boundary detection~\cite{zeng2017deepem3d}.
-Lee et al. surpass the estimated human accuracy on the SNEMI3D dataset with a variant of the 3D U-Net architecture~\cite{lee2017superhuman}.
-
-Then, these intermediate representations are transformed into segmentation.
+Then, clustering techniques transform these intermediate representations into segmentations.
 Some early techniques apply computationally expensive graph partitioning algorithms with a single node per superpixel~\cite{andres2012globally}.
 Several pixel-based approaches generate probabilities that neighboring pixels belong to the same neuron.
-Often a watershed algorithm will then cluster pixels into super-pixels~\cite{zlateski2015image}.
+Often a watershed algorithm will then cluster these pixels into super-pixels~\cite{zlateski2015image}.
 
-\subsubsection{Agglomeration}
-\TODO{rule-based}
-Some methods rely solely on the accuracy of the predicted affinities and agglomerate hierarchically based on the mean affinity between supervoxels~\cite{lee2017superhuman,funke2017deep}.
+%\noindent\textbf{Region Merging}
+\subsubsection{Region Merging}
+Region merging methods can be categorized by the similairity metric between adjacent segments and the merging strategy.
+For the similarity metric, Lee et al.
+and Funke et al.
+rely solely on the accuracy of the predicted affinities and define the metric as the mean affinity between segments~\cite{lee2017superhuman,funke2017deep}.
+Classification-based method predicts the probability to merge two segments from handcrafted~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image,10.1371/journal.pone.0125825,jain2011learning} and learned features~\cite{bogovic2013learned}.
 
-\TODO{classification-based}
-Given the initial segmentation, some methods train random-forest classifiers to produce the final segmentations~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image,10.1371/journal.pone.0125825}
-extract different features
-~\cite{jain2011learning,bogovic2013learned}.
+For the merging stategy, most methods use variants of hierarchical agglomeration methods~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image,10.1371/journal.pone.0125825,bogovic2013learned} to greedily merge a pair of regions at a time.
+Jain et al.
+formulates the agglomeration as a reinforecement learning problem ~\cite{jain2011learning} and Pape et al.
+present a scalable multicut algorithm to partition superpixels with global optimization~\cite{beier2017multicut}.
 
-\TODO{optimization-based}
-Pape et al. present a scalable multicut algorithm to partition superpixels~\cite{beier2017multicut}.
+% \subsubsection{Error-correction methods}
+% Additional research builds on top of these region-based methods to correct errors in the segmentation either using human proofreading~\cite{haehn2014design,haehn2017guided,mojo2} or automatic methods~\cite{rolnick2017morphological,error_correction_using_CNN}.
+% Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for traditional image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}.
+% Even though graph partitioning is an NP-Hard problem~\cite{demaine2006correlation} there are several useful multicut heuristics that provide good approximations with reasonable computational costs~\cite{horvnakova2017analysis}.
+%We extract a 3D graph from an input segmentation for a true top-down error correction approach. 
+%This allows us to enforce domain-specific biological constraints while using graph partitioning algorithms. 
+%We use the method of Keuper et al.~\cite{keuper2015efficient} to partition the extracted graph into the final neural reconstruction.
 
-In our work, we combine classification and optimization.
 %\subsubsection{Error-correction methods}

### 2018-03-14 papers/eccv2018/2_method.tex
pass on related work, use region merging instead of agglomeration

@@
 % !TEX root =  paper.tex
-\section{Method}
-
 \begin{figure}[t!]
@@
 \end{figure}
+\section{Method}
 %\begin{figure*}[t!]
@@
 
-There are two types of errors that can occur in connectomics segmentations: \textit{split errors} and \textit{merge errors}. 
-In a split error, two segments should have been merged into one neuronal process (Fig.~\ref{fig:improved-reconstruction}). 
-In a merge error, one segment corresponds to more than one neuron.
-Generally, it is much more difficult to correct merge errors than to correct split errors, as the space of possible split proposals grows quickly~\cite{parag2015properties}.
-Thus, most reconstruction approaches are tuned towards over-segmentation with many more split than merge errors. 
-The input of our method is the over-segmentation of EM image volumes from state-of-the-art pipelines.
+%There are two types of errors that can occur in connectomics segmentations: \textit{split errors} and \textit{merge errors}. 
+%In a split error, two segments should have been merged into one neuronal process (Fig.~\ref{fig:improved-reconstruction}). 
+%In a merge error, one segment corresponds to more than one neuron.
+%Generally, it is much more difficult to correct merge errors than to correct split errors, as the space of possible split proposals grows quickly~\cite{parag2015properties}.
+%Thus, most reconstruction approaches are tuned towards over-segmentation with many more split than merge errors. 
+%The input of our method is the over-segmentation of EM image volumes from state-of-the-art pipelines.
 

### 2018-03-14 papers/eccv2018/paper.tex
First pass of fixes.
pass on related work, use region merging instead of agglomeration

@@
 %\title{Scalable Graph-Based Neural \\ Reconstruction for Connectomics}
-\title{Biologically-Constrained 3D Agglomeration for Connectome Reconstruction}
+%\title{Biologically-Constrained 3D Agglomeration for Connectome Reconstruction}
+\title{Biologically-Constrained Region Merging for Connectome Reconstruction}
 
@@
 %An agglomerative segmentation algorithm merges initial pair of clusters.
-Current state-of-the-art connectome reconstruction pipelines have two major steps: initial pixel-based segmentation with affinity prediction and watershed transform, and refined segmentation with agglomeration.
+Current state-of-the-art connectome reconstruction pipelines have two major steps: initial pixel-based segmentation with affinity prediction and watershed transform, and refined segmentation by merging oversegmented regions.
 %In the past deTraditionally, neuron segmentation from 3D electron microscopy (EM)
-For the agglomeration, most methods neglect geometric and topological constraints that are inherent in the graph structure of neural wiring diagrams.
-
+For the region merging, most methods neglect geometric and topological constraints that are inherent in the graph structure of neural wiring diagrams.
 In this work, we use a biologically-constrained graph-based method to better reconstruct neural pathways.
@@
 Next, we train a convolutional neural network to capture the geometric properties of segment connections and produce edge weights as the probability of merging two nodes.
-Finally, we formulate the agglomeration as a lifted multicut partitioning problem with topological constraints to avoid cycles.
+Finally, we formulate the region merging as a lifted multicut partitioning problem with topological constraints to avoid cycles.
 We demonstrate the performance of our approach on multiple real-world connectomics datasets with an average split variation of information improvement of \TODO{XX}\%.
-\keywords{connectomics, biological constraints, agglomeration, skeletonization, deep learning, lifted multicut}
+\keywords{connectomics, biological constraints, region merge, skeletonization, deep learning, lifted multicut}
 \end{abstract}

### 2018-03-14 papers/eccv2018/2_method.tex
Updates.

@@
 We train a 3D CNN model to learn these geometric constraints for valid connection between two segments from labeled volume.
-
+\\~\\
 \noindent\textbf{Edge Probability}
 To predict the probabilities that two segments belong to the same neuron, we train a feed-forward convolutional network with three \textit{VGG-style} convolution blocks~\cite{chatfield2014return} and two fully connected layers before the final sigmoid activation.
-Each \textit{VGG-style} convolution block consists of two double convolutions with filter size $3\times3\times3$ and LeakyReLU(0.0005), followed by a max pooling with filter size $2\times2\times1$ in the first two blocks and $2\times2\times2$ in the third.
 
@@
 This reduces the need for generating costly manually-labeled ground truth. 
-
-\noindent\textbf{Edge Weight}
-
-Given the probability that the nodes belong to the same neuron is $p_e$, the edge weight $w_e$ is defined as
+\\~\\
+\noindent\textbf{Edge Weight} Given the probability that the nodes belong to the same neuron is $p_e$, the edge weight $w_e$ is defined as
 %p_e &=\mbox{CNN}(x_1, x_2) \\
 \begin{align}
-w_e = \log{\frac{p_e}{1 - p_e}} + \log{\frac{1 - \beta}{\beta}}
+w_e = \log{\frac{p_e}{1 - p_e}} + \log{\frac{1 - \beta}{\beta}},
 \end{align}
-, where $\beta$ is a tunable parameter that encourages over- or under-segmentation. 
+where $\beta$ is a tunable parameter that encourages over- or under-segmentation. 
 This particular weighting scheme allows us to optimize for a Bayesian network defined on the graph~\cite{keuper2015efficient,andres2011probabilistic}.
@@
 After graph construction, we segment the graph into a globally consistent manner while enforcing topological constraints on the output.
-
+\\~\\
 %\subsubsection{Lifted Multicut}
@@
 Since our graphs are sufficiently small, we can generate ``lifted'' edges between all pairs of nodes. 
-
+\\~\\
 %\subsubsection{Topological Constraints}

### 2018-03-14 papers/eccv2018/2_method.tex
fix figure 1 and 2

--- 2018-03-14 papers/eccv2018/2_method.tex
@@
 \label{sec:skeletonization}
-Most agglomeration methods create the region graph by removing small-sized segments and linking each pair of adjacent segments, which can still lead to a large graph size due to the irregular shape of neural structures.
+Most region merging methods create the region graph by removing small-sized segments and linking each pair of adjacent segments, which can still lead to a large graph size due to the irregular shape of neural structures.
 We here use the skeleton representation of the segmentation and reduce the graph size with the geometric constraints on the connectivity of two adjacent segments to prune edges.

### 2018-03-14 papers/eccv2018/4_results.tex
First pass of fixes.
Fix the other table.

@@
 \begin{table}
-	\centering
-	\small
-	\setlength{\tabcolsep}{0.75em}
+	\caption{The results of our graph pruning approach compared to the baseline graph with all adjacent regions.
+We show the number of true merge locations (e.g., 610) compared to total number of edges in the graph (e.g., 23506) for each case.
+The number of missed splits corresponds to the number of split errors that our method misses compared to an adjacency matrix.}
+\resizebox{\linewidth}{!}{
 	\begin{tabular}{c c c c c} \hline
@@
 	\end{tabular}
-	\caption{The results of our graph pruning approach compared to the baseline graph with all adjacent regions.
-We show the number of true merge locations (e.g., 610) compared to total number of edges in the graph (e.g., 23506) for each case.
-The number of missed splits corresponds to the number of split errors that our method misses compared to an adjacency matrix.}
+}
+	\centering
 	\label{table:skeletonization}
@@
 On average in our datasets we correctly merge \TODO{XX} of the non-adjacent segments. 
-
-There are some pairs of segments which we do not consider for merging because of our reliance on the skeletons.
-Fig.~\ref{fig:skeleton-results} shows two such cases. 
-The endpoints of both segments are circled.
-In this example the small segment is carved from the larger segment in a location where there are no skeleton endpoints. 
-There are on average 146 such examples in our datasets.
-
 \begin{figure}[t!]
@@
 \end{figure}
-
-%\subsection{CNN Classification Results}
+There are some pairs of segments which we do not consider for merging because of our reliance on the skeletons.
+Fig.~\ref{fig:skeleton-results} shows two such cases. 
+The endpoints of both segments are circled.
+In this example the small segment is carved from the larger segment in a location where there are no skeleton endpoints. 
+There are on average 146 such examples in our datasets.
+\\~\\
 \noindent\textbf{Edge Weight Learning}
@@
 The classification results are reasonable on the FlyEM datasets despite the fact that the data varies in resolution and even animal type from the training set.
-
+\\~\\
 %\subsection{Graph Optimization Results}
@@
 \begin{table}[h]
+	\caption{Precision, recall, and accuracy changes between CNN only and CNN paired with graph-optimized reconstructions for the training and three test datasets.
+The combined method results in better precision and accuracy.}
 	\centering
-	\small
-	\setlength{\tabcolsep}{0.3em}
+\resizebox{\linewidth}{!}{
 	\begin{tabular}{c c c c | c c c} \hline
@@
 	\end{tabular}
-	\caption{Precision, recall, and accuracy changes between CNN only and CNN paired with graph-optimized reconstructions for the training and three test datasets.
-The combined method results in better precision and accuracy.}
+}
 	\label{table:multicut}
@@
 All performance experiments ran on an Intel Core i7-6800K CPU 3.40 GHz with a Titan X Pascal GPU.
-All code is written in Python and will be freely available upon paper decision.
+All code is written in Python and is freely available (link omitted for review).
 We use the Keras deep learning library for our neural networks with Theano backend and cuDNN 7 acceleration for CUDA 8.0.

### 2018-03-14 papers/eccv2018/5_conclusions.tex

--- 2017-11-15 papers/cvpr2018/5_conclusions.tex
@@
 
-There is significant room for additional research and improvements.
-We can augment the graph with additional information from the image data, such as synaptic locations, cell morphology, locations of mitochondria, etc.
-This would allow us to enforce additional biological constraints during graph partitioning.
+In the future, these methods can be adjusted to apply additional domain constraints. 
+We can augment the graph with more information from the image data, such as synaptic locations, cell morphology, locations of mitochondria, etc. 
+This would allow us to match other biological constraints during graph partitioning. 
 For example, we could then enforce the constraint that a given segment only has post- or pre-synaptic connections. 

### 2018-03-14 papers/eccv2018/1_related_work.tex
More updates.

@@
 \section{Related Work}
-
 % \begin{figure}[t]
@@
 % \end{figure}
-
-%\noindent\textbf{Pixel-Based Segmentation}
-\subsubsection{Pixel-Based Segmentation}
+%\\~\\
+\noindent\textbf{Pixel-Based Segmentation}
+%\subsubsection{Pixel-Based Segmentation}
 A significant amount of connectomics research considers the problem of extracting segmentation information at the voxel level of EM images.
@@
 Often a watershed algorithm will then cluster these pixels into super-pixels~\cite{zlateski2015image}.
-
-%\noindent\textbf{Region Merging}
-\subsubsection{Region Merging}
-Region merging methods can be categorized by the similairity metric between adjacent segments and the merging strategy.
+\\~\\
+\noindent\textbf{Region Merging}
+%\subsubsection{Region Merging}
+Region merging methods can be categorized by the similarity metric between adjacent segments and the merging strategy.
 For the similarity metric, Lee et al.
@@
 
-For the merging stategy, most methods use variants of hierarchical agglomeration methods~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image,10.1371/journal.pone.0125825,bogovic2013learned} to greedily merge a pair of regions at a time.
+For the merging stategy, most methods use variants of hierarchical agglomeration methods~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image,10.1371/journal.pone.0125825} to greedily merge a pair of regions at a time.
 Jain et al.
-formulates the agglomeration as a reinforecement learning problem ~\cite{jain2011learning} and Pape et al.
+formulates the agglomeration as a reinforcement learning problem ~\cite{jain2011learning} and Pape et al.
 present a scalable multicut algorithm to partition superpixels with global optimization~\cite{beier2017multicut}.
+\\~\\
+\noindent\textbf{Error-correction Methods}
+ Additional research builds on top of these region-based methods to correct errors in the segmentation.
+This can be done either using human proofreading~\cite{haehn2014design,haehn2017guided,mojo2} or automatically~\cite{rolnick2017morphological,error_correction_using_CNN}.
+In both cases, available methods are pixel-based and do not include global biological constraints into the decision making process.
+Our method can be used as input to any existing error correction framework.
+% Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for traditional image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}.
 
-% \subsubsection{Error-correction methods}
-% Additional research builds on top of these region-based methods to correct errors in the segmentation either using human proofreading~\cite{haehn2014design,haehn2017guided,mojo2} or automatic methods~\cite{rolnick2017morphological,error_correction_using_CNN}.
-% Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for traditional image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}.
 % Even though graph partitioning is an NP-Hard problem~\cite{demaine2006correlation} there are several useful multicut heuristics that provide good approximations with reasonable computational costs~\cite{horvnakova2017analysis}.

### 2018-03-14 papers/eccv2018/2_method.tex
More updates.

--- 2018-03-14 papers/eccv2018/2_method.tex
@@
 	\caption{Our proposed framework uses both local and global biological constraints to improve an input segmentation.
-We generate a simplified graph from an input segmentation (a), train a classifier to learn neuron shape constraints locally (b), and perform graph partitioning to enforce domain-specific properties globally.\TODO{Is it possible to have the weights next to the lines?}}
+We generate a simplified graph from an input segmentation (a), train a classifier to learn neuron shape constraints locally (b), and perform graph partitioning to enforce domain-specific properties globally.}
 	\label{fig:teaser_pipeline}

### 2018-03-14 papers/eccv2018/2_method.tex
fix figure 1 and 2

--- 2018-03-14 papers/eccv2018/2_method.tex
@@
 	\centering
-	\includegraphics[width=\linewidth]{./figures/teaser-image.png}
+	\includegraphics[width=\linewidth]{./figures/teaser_v4.png}
 	\caption{Our proposed framework uses both local and global biological constraints to improve an input segmentation.
-We generate a simplified graph from an input segmentation (a), train a classifier to learn neuron shape constraints locally (b), and perform graph partitioning to enforce domain-specific properties globally.\TODO{Is it possible to have the weights next to the lines?}}
+We generate a simplified graph from an input segmentation (a), train a classifier to learn neuron shape constraints locally (b), and perform graph partitioning to enforce domain-specific properties globally.}
 	\label{fig:teaser_pipeline}

### 2018-03-14 papers/eccv2018/0_introduction.tex
fix figure 1 and 2
changes to some figures

@@
 	\centering
-	\includegraphics[width=\linewidth]{./figures/bc/teaser_bc_v2.pdf}
+	\includegraphics[width=\linewidth]{./figures/bc/teaser_bc_v3.png}
 	\caption{Biological constraints for 3D segments in Connectomics.}
@@
 However, it is unclear if that is the case for larger volumes.
-\TODO{sth. about figure 1.}
 
@@
 %We present a \textit{top-down graph-based} method that builds on the outputs of bottom-up pixel-based segmentation approaches. 
-We present a new region merging framework that imposes both local and global biological constraints onto the output segmentation to match the underlying structure of neuronal processes.
+We present a new region merging framework that imposes both local and global biological constraints onto the output segmentation to match the underlying structure of neuronal processes (Fig.~\ref{fig:biological_constraints}).
 We first extract skeletons from labels in the input segmentation and generate a simplified graph (Fig.~\ref{fig:teaser_pipeline}a). 

### 2018-03-14 papers/eccv2018/4_results.tex
changes to some figures

@@
 	\includegraphics[width=0.32\linewidth]{./figures/variation_of_information-microns-test-600.png}
-	\includegraphics[width=0.32\linewidth]{./figures/variation_of_information-FlyEM-train-600.png}
-	\includegraphics[width=0.32\linewidth]{./figures/variation_of_information-FlyEM-test-600.png}
+	\includegraphics[width=0.32\linewidth]{./figures/voi-FlyEM-Vol--1.png}
+	\includegraphics[width=0.32\linewidth]{./figures/voi-FlyEM-Vol--2.png}
 	\caption{VI scores of our method (red) compared to the baseline segmentation (green) and an oracle (blue) that optimally partitions the graph based on ground truth.
@@
 	\centering
-	\includegraphics[width=0.45\linewidth]{./figures/receiver-operating-characteristic.png}		\includegraphics[width=0.45\linewidth]{./figures/precision-and-recall.png}
+	\includegraphics[width=0.45\linewidth]{./figures/receiver-operating-characteristic.png}
 	\caption{The receiver operating characteristic (ROC) curves of our classifier on three connectomics datasets. The classifier works best on previously unseen data of the Kasthuri volume.}

### 2018-03-14 papers/eccv2018/0_introduction.tex
caption for figure 1,2

@@
 	\includegraphics[width=\linewidth]{./figures/bc/teaser_bc_v3.png}
-	\caption{Biological constraints for 3D segments in Connectomics.}
+	\caption{Biological constraints for 3D segments in Connectomics.
+(a) Unlike daily objects, e.g.
+tables, neural structures tend to have diversified 3D shapes which are hard to model directly.
+(b) However, due to its biological nature, there are geometric and togological constraints for the 3D shapes.
+For example, L-juctions and Arrow-junctions are rare and neural segments do not form cycles.}
 	\label{fig:biological_constraints}

### 2018-03-14 papers/eccv2018/2_method.tex
caption for figure 1,2

@@
 	\includegraphics[width=\linewidth]{./figures/teaser_v4.png}
-	\caption{Our proposed framework uses both local and global biological constraints to improve an input segmentation.
-We generate a simplified graph from an input segmentation (a), train a classifier to learn neuron shape constraints locally (b), and perform graph partitioning to enforce domain-specific properties globally.}
+	\caption{Our proposed framework uses both geometric and topological biological constraints for region merging.
+We (a) generate a simplified graph from the skeleton representation of the input segmentation, (b) train a classifier to learn the edge weight based on the shape of the segment connection, and (c) perform graph partitioning with acyclic contraints.}
 	\label{fig:teaser_pipeline}

### 2018-03-14 papers/eccv2018/3_evaluation.tex
pass on related work, use region merging instead of agglomeration
changes to some figures

--- 2018-03-14 papers/eccv2018/3_evaluation.tex
@@
 The following datasets contain 4 times more volume than the CREMI datasets. 
-
+\\~\\
 %\subsubsection{Kasthuri}
@@
 2) along the $x$ dimension, where each volume is $\SI[product-units=single]{8.0 x 10.9 x 10.1}{\micro\meter}^3$ or $1335 \times 1809 \times 338$ voxels.
-
+\\~\\
 %\subsubsection{FlyEM}
@@
 %For the Fib-25 challenge dataset, we use the segmentation from Funke et al. as our input~\cite{funke2017deep}.
-
+\\~\\
 \noindent\textbf{Graph Generation}
@@
 % Although the voxels vary between different datasets, the physical space remains constant. 
-
+\\~\\
 \noindent\textbf{Edge Weight Learning}
@@
 We provide all parameters of the final network in the supplemental material. 
-There are 2,313,969 learnable parameters in our final architecture. 
+There are $11,456,241$ learnable parameters in our final architecture. 
 All the parameters are randomly initialized following the Xavier uniform distribution~\cite{glorot2010understanding}. 
-Training concluded after 1000 epochs.
+Training concluded after 330 epochs.
 
@@
 We have 20,000 such examples per epoch.
-
+\\~\\
 \noindent\textbf{Graph Partition}
-We assign the edges in our graph a weight $w_e = \log{\frac{p_e}{1 - p_e}} + \log{\frac{1 - \beta}{\beta}}$ where $\beta$ is a tunable parameter. 
-Higher values of $\beta$ encourage over-segmentation.
+%We assign the edges in our graph a weight $w_e = \log{\frac{p_e}{1 - p_e}} + \log{\frac{1 - \beta}{\beta}}$ where $\beta$ is a tunable parameter. 
+%Higher values of $\beta$ encourage over-segmentation.
 Figure~\ref{fig:variation-of-information} shows our results for variables $\beta \in [0.5, 0.9]$. 

### 2018-03-14 papers/eccv2018/4_results.tex

@@
 	\centering
-	\includegraphics[width=0.32\linewidth]{./figures/variation_of_information-microns-test-600.png}
+	\includegraphics[width=0.32\linewidth]{./figures/voi-Kasthuri-Luigi-Test.png}
 	\includegraphics[width=0.32\linewidth]{./figures/voi-FlyEM-Vol--1.png}
@@
 Fig.~\ref{fig:receiver-operating-characteristic} shows the receiver operating characteristic (ROC) curve of our CNN classifier for all test datasets.
-As shown by the ROC curve, the test results on the Kasthuri data are better than the results for FlyEM.
-We believe this is in part because of the differences in the datasets (i.e., isotropy and $xy$ resolution).
+As shown by the ROC curve, the test results on the FlyEM data are better than the results for Kasthuri.
+In part this comes from the disparity in the number of positive to negative merge candidates in the two graphs. 
+The network easily classifies most of the negative examples leaving only a few difficult examples to predict.
+Since there are more negative examples in relation to the positive examples in the FlyEM data, the ROC curve is greater.
 
@@
 Our neural network does not take as input the images or affinities so we can transfer network weights from one dataset to the next.
-The classification results are reasonable on the FlyEM datasets despite the fact that the data varies in resolution and even animal type from the training set.
+The classification results are comparable on the FlyEM datasets despite the fact that the data varies in resolution and even animal type from the training set.
 \\~\\

### 2018-03-14 papers/eccv2018/2_method.tex
fix typos

@@
 	\caption{Our proposed framework uses both geometric and topological biological constraints for region merging.
-We (a) generate a simplified graph from the skeleton representation of the input segmentation, (b) train a classifier to learn the edge weight based on the shape of the segment connection, and (c) perform graph partitioning with acyclic contraints.}
+We (a) generate a simplified graph from the skeleton representation of the input segmentation, (b) train a classifier to learn the edge weight based on the shape of the segment connection, and (c) perform graph partitioning with acyclic constraints.}
 	\label{fig:teaser_pipeline}

### 2018-03-14 papers/eccv2018/0_introduction.tex
fix typos
added HP comments

--- 2018-03-14 papers/eccv2018/0_introduction.tex
@@
 % \end{figure}
-\begin{figure}[t]
+\begin{figure}[t!]
 	\centering
-	\includegraphics[width=\linewidth]{./figures/bc/teaser_bc_v2.pdf}
-	\caption{Biological constraints for 3D segments in Connectomics.}
-	\label{fig:biological_constraints}
+	\includegraphics[width=\linewidth]{./figures/teaser_v4.png}
+	\caption{Our framework uses both geometric and topological biological constraints for region merging.
+We (a) generate a simplified graph from the skeleton representation of the input segmentation, (b) train a classifier to learn the edge weight based on the shape of the segment connection, and (c) perform graph partitioning with acyclic constraints.}
+	\label{fig:teaser_pipeline}
 \end{figure}
@@
 State-of-the-art automatic 3D reconstruction approaches use pixel-based convolutional neural networks (CNNs) and watershed transforms to generate initial over-segmentation, followed by region merging steps~\cite{seymour2016rhoananet,lee2015recursive,nunez2014graph,parag2017anisotropic,ronneberger2015u,zlateski2015image}.
-For the region merging, most methods do not use prior biological knowledge of the 3D shape of neural structures.
-Reported on small-sized volumes, a simple threshold-based mean agglomeration method can achieve superhuman result~\cite{lee2017superhuman}.
-However, it is unclear if that is the case for larger volumes.
-\TODO{sth. about figure 1.}
+For region merging, most methods do not use prior biological knowledge of the 3D shape of neural structures.
+Simple threshold-based mean agglomeration methods can achieve superhuman resolution  small-sized volumes~\cite{lee2017superhuman}.
 
@@
 %We present a \textit{top-down graph-based} method that builds on the outputs of bottom-up pixel-based segmentation approaches. 
+There are two types of errors in connectomics segmentations.
+In a \textit{split error}, multiple segments compose a single neuronal process. 
+In a \textit{merge error}, two neurons incorrectly merge to form a single segment. 
+Generally, it is much more difficult to correct merge errors than to correct split errors, as the space of possible split proposals grows quickly~\cite{parag2015properties}.
+Thus, most reconstruction approaches are tuned towards over-segmentation with many more split than merge errors.
+We focus on correcting these split errors in the input segmentation.
+
 We present a new region merging framework that imposes both local and global biological constraints onto the output segmentation to match the underlying structure of neuronal processes.
@@
 This work makes three contributions:
-first, a novel top-down framework that extracts graphs from skeletonized 3D segmentations for improved neural reconstruction of connectomics data; 
-next, a region-based CNN classifier to detect errors; 
+first, a novel top-down framework that extracts graphs from skeletonized 3D segmentations for improved region merging for neural reconstruction of connectomics data; 
+next, a region-based CNN classifier to detect split errors; 
 %(3) an empirical evaluation of our method on several connectomics datasets;  % this is not contribution
-last, improved performance over a state-of-the-art pixel-based reconstruction approach on average by \TODO{XX}\% with suitable running times.
+last, improved performance over a state-of-the-art pixel-based reconstruction approach on average by \TODO{XX}\% while maintaining scalable runtimes for large volumes.

### 2018-03-14 papers/eccv2018/2_method.tex
added HP comments

--- 2018-03-14 papers/eccv2018/2_method.tex
@@
 % !TEX root =  paper.tex
-\begin{figure}[t!]
-	\centering
-	\includegraphics[width=\linewidth]{./figures/teaser_v4.png}
-	\caption{Our proposed framework uses both local and global biological constraints to improve an input segmentation.
-We generate a simplified graph from an input segmentation (a), train a classifier to learn neuron shape constraints locally (b), and perform graph partitioning to enforce domain-specific properties globally.}
-	\label{fig:teaser_pipeline}
-\end{figure}
+
 \section{Method}
@@
 
-Our pipeline is illustrated in Fig.~\ref{fig:teaser_pipeline}.
+Our method is illustrated in Fig.~\ref{fig:teaser_pipeline}.
 From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with weights $w_e$. 
@@
 	\end{minipage}
-	\caption{Example skeletons (in black) extracted from segments using a variant of the TEASER algorithm.}
+	\caption{Example skeletons (in black) extracted from segments using a variant of the TEASER algorithm~\cite{sato2000teasar}.}
 	\label{fig:skeletonization}
@@
 Since this algorithm is non-linear in the number of voxels, we downsample the datasets so that there are voxel samples every $\SI{30}{\nano\meter}$ in each dimension.
-Empirically, this reduced the running time for skeletonization by $30\times$, with minimal reduction in skeleton accuracy (${\sim}5\%$ fewer branches). 
+Empirically, this reduced the running time for skeletonization by $30\times$ with minimal reduction in skeleton accuracy (${\sim}5\%$ fewer branches). 
 Fig.~\ref{fig:skeletonization} shows four examples of extracted skeletons (in black). 
@@
 Two segments, $s_1$ and $s_2$, receive a corresponding edge if the two following conditions hold.
-First, a endpoint in either $s_1$ or $s_2$ is with $t_{low}$ nm of any voxel in the other segment.
-Second, there is an endpoint in $s_1$ and an endpoint in $s_2$ that are within $t_{high}$ nm of each other.
+First, endpoints in either $s_1$ or $s_2$ are within $t_{low}$ nm of any voxel in the other segment.
+Second, there are endpoints in $s_1$ and in $s_2$ that are within $t_{high}$ nm of each other.
 We store the midpoints between the two endpoints as the center of the potential merge in the set $\mathbb{S}_c$. 
@@
 Only these pairs have a corresponding edge in the constructed graph.
-These parameters follow empirically from noise in the skeleton generation process. 
-There are occasionally spurious branches and other artifacts and these thresholds mitigate the influence of these degenerate locations.
-We provide a fuller analysis in the supplemental materials.
+We provide an empirical analysis of these parameters on the structure of the graph in the supplemental materials.
 
 \begin{figure}[t]
-	\begin{minipage}{0.45\linewidth}
+	\begin{minipage}{0.4\linewidth}
 		\includegraphics[width=\linewidth]{./figures/constraint_error.png}
@@
 	\hfill
-	\begin{minipage}{0.45\linewidth}
+	\begin{minipage}{0.55\linewidth}
 		\includegraphics[width=\linewidth]{./figures/constraint_success.png}
 	\end{minipage}
-	\caption{Two example candidates for merging. The two segments in the left example do not belong to the same neuron as evidenced by the sharp turning radius.}
+	\caption{Two example candidates for merging. The two segments in the left example do not belong to the same neuron as evidenced by the sharp turning radius indicated by the arrow.}
 	\label{fig:turn-radii}
@@
 This reduces the need for generating costly manually-labeled ground truth.
-\\~\\
-\noindent\textbf{Edge Weight} Given the probability that the nodes belong to the same neuron is $p_e$, the edge weight $w_e$ is defined as
-%p_e &=\mbox{CNN}(x_1, x_2) \\
-\begin{align}
-w_e = \log{\frac{p_e}{1 - p_e}} + \log{\frac{1 - \beta}{\beta}},
-\end{align}
-where $\beta$ is a tunable parameter that encourages over- or under-segmentation. 
-This particular weighting scheme allows us to optimize for a Bayesian network defined on the graph~\cite{keuper2015efficient,andres2011probabilistic}.
 
@@
 
-After graph construction, we segment the graph into a globally consistent manner while enforcing topological constraints on the output.
+After graph construction, we segment the graph in a globally consistent manner while enforcing topological constraints on the output.
 \\~\\
@@
 First, the number of segments in the final graph is not predetermined but depends on the input. 
-Second, this minimization produces globally consistent solutions (i.e. a boundary remains only if the two corresponding nodes belong to unique segments)~\cite{keuper2015efficient}.
+Second, this minimization produces globally consistent solutions (i.e., a boundary remains only if the two corresponding nodes belong to unique segments)~\cite{keuper2015efficient}.
 
 We apply the algorithms of Keuper et al.~\cite{keuper2015efficient} to produce a feasible solution to the multicut problem using greedy additive edge contraction.
-Following their example, we employ the generalized ``lifted'' multicut formulation.
+Following their example, we employ the generalized lifted multicut formulation.
 Traditional multicut solutions only consider the probabilities that two adjacent nodes belong to the same segment. 
-In the ``lifted'' extension to the problem, we can penalize non-adjacent nodes that belong to different segments. 
-These penalties between non-adjacent nodes are called ``lifted'' edges. 
-Ideally these ``lifted'' weights represent the probability that two nodes belong to the same neuron.
+In the lifted extension to the problem, we can penalize non-adjacent nodes that belong to different segments. 
+These penalties between non-adjacent nodes are called lifted edges. 
+Ideally these lifted weights represent the probability that two nodes belong to the same neuron.
 However, determining such probabilities is computationally expensive.
@@
 This is an underestimate of the probability that two nodes belong to the same neuron since it does not consider all possible paths.
-Since our graphs are sufficiently small, we can generate ``lifted'' edges between all pairs of nodes. 
+Since our graphs are sufficiently small, we can generate lifted edges between all pairs of nodes. 
+\\~\\
+\noindent\textbf{Edge Weight} 
+We need to convert the probabilities into the following weighting scheme to solve the multicut problem with this heuristic~\cite{keuper2015efficient,andres2011probabilistic}.
+Given the probability that the nodes belong to the same neuron is $p_e$, the edge weight $w_e$ is defined as
+%p_e &=\mbox{CNN}(x_1, x_2) \\
+\begin{align}
+w_e = \log{\frac{p_e}{1 - p_e}} + \log{\frac{1 - \beta}{\beta}},
+\end{align}
+where $\beta$ is a tunable parameter that encourages over- or under-segmentation. 
 \\~\\

### 2018-03-14 papers/eccv2018/3_evaluation.tex
added HP comments

@@
 Figure~\ref{fig:variation-of-information} shows our results for variables $\beta \in [0.5, 0.9]$. 
-For our multicut analysis we consider $\beta = 0.5$.
+For our multicut analysis we use $\beta = 0.5$. There are many more lifted edges than adjacent edges. 
+To prevent the lifted weights from dominating the objective function we weight each set of edges~\cite{beier2017multicut}.
 
@@
 We use precision and recall to evaluate the convolutional neural network and multicut outputs. 
-Since our method attempts to only correct \textit{split errors}, we define a true positive as a pair of segments that are correctly merged together after our pipeline.
+Since our method only corrects \textit{split errors}, we define a true positive as a pair of segments that are correctly merged together after our pipeline.

### 2018-03-14 papers/eccv2018/4_results.tex
added HP comments

@@
 \end{figure*}
-
-\subsection{Connectomics Benchmark}
 
@@
 	\caption{The results of our graph pruning approach compared to the baseline graph with all adjacent regions.
-We show the number of true merge locations (e.g., 610) compared to total number of edges in the graph (e.g., 23506) for each case.
+We show the number of true merge locations (e.g., 610) compared to total number of edges in the graph (e.g., 23,506) for each case.
 The number of missed splits corresponds to the number of split errors that our method misses compared to an adjacency matrix.}
@@
 		\textbf{Dataset} & \textbf{Segment Adjacency} & \textbf{Skeleton Pruning} & \textbf{Missed Splits} & \textbf{Gained Edges} \\ \hline
-		Kasthuri & 610 / 23506 & 556 / 4921 & 214 & 160 \\
-		FlyEM Vol. 1 & 304 / 15949 & 212 / 4578 & 105 & 13 \\
-		FlyEM Vol. 2 &  298 / 17614 & 197 / 4366 & 120 & 19 \\ \hline
+		Kasthuri & 610 / 23,506 & 556 / 4,921 & 214 & 160 \\
+		FlyEM Vol. 1 & 304 / 15,949 & 212 / 4,578 & 105 & 13 \\
+		FlyEM Vol. 2 &  298 / 17,614 & 197 / 4,366 & 120 & 19 \\ \hline
 	\end{tabular}
@@
 On average in our datasets we correctly merge \TODO{XX} of the non-adjacent segments. 
+\\~\\
+\noindent\textbf{Failure Cases}
+There are some pairs of segments which we do not consider for merging because of our reliance on the skeletons.
+Fig.~\ref{fig:skeleton-results} shows two such cases. 
+The endpoints of both segments are circled.
+In this example the small segment is carved from the larger segment in a location where there are no skeleton endpoints. 
+There are on average 146 such examples in our datasets.
+\\~\\
+\noindent\textbf{Edge Weight Learning}
+We first evaluate the effectiveness of inference augmentation.
+%\subsubsection{Inference Augmentation}
+%\noindent\textbf{Inference Augmentation.}
+Data augmentation at test time can improve accuracy results~\cite{zeng2017deepem3d,lee2017superhuman}.
+When computing the probability to merge two segments, we input the initial segment into our CNN as well as 3 randomly rotated and flipped examples (in the same manner as training augmentation).
+This produces some additional increase in overall accuracy (Figure ~\ref{fig:receiver-operating-characteristic}).
+The supplemental material contains experiments showing the trade-offs between increased accuracy and runtime when using these augmentation strategies.
+
 \begin{figure}[t!]
@@
 	\end{minipage}
-	\caption{The top two examples correspond to segment pairs that we incorrectly prune from the graph.
+	\caption{\textit{Failure cases.} The top two examples correspond to segment pairs that we incorrectly prune from the graph.
 The distance between the circled endpoints is too great.
@@
 \end{figure}
-There are some pairs of segments which we do not consider for merging because of our reliance on the skeletons.
-Fig.~\ref{fig:skeleton-results} shows two such cases. 
-The endpoints of both segments are circled.
-In this example the small segment is carved from the larger segment in a location where there are no skeleton endpoints. 
-There are on average 146 such examples in our datasets.
-\\~\\
-\noindent\textbf{Edge Weight Learning}
-We first evaluate the effectiveness of inference augmentation.
-%\subsubsection{Inference Augmentation}
-%\noindent\textbf{Inference Augmentation.}
-Data augmentation at test time can improve accuracy results~\cite{zeng2017deepem3d,lee2017superhuman}.
-When computing the probability to merge two segments, we input the initial segment into our CNN as well as 3 randomly rotated and flipped examples (in the same manner as training augmentation).
-This produces some additional increase in overall accuracy (Figure ~\ref{fig:receiver-operating-characteristic}).
-The supplemental material contains experiments showing the trade-offs between increased accuracy and runtime when using these augmentation strategies.
-
 Fig.~\ref{fig:receiver-operating-characteristic} shows the receiver operating characteristic (ROC) curve of our CNN classifier for all test datasets.

### 2018-03-14 papers/eccv2018/0_introduction.tex
removing red valuesgit add -v papers/eccv2018/*

@@
 %(3) an empirical evaluation of our method on several connectomics datasets;  % this is not contribution
-last, improved performance over a state-of-the-art pixel-based reconstruction approach on average by \TODO{XX}\% while maintaining scalable runtimes for large volumes.
+last, improved performance over a state-of-the-art pixel-based reconstruction approach on average by $19.7\%$ while maintaining scalable runtimes for large volumes.

### 2018-03-14 papers/eccv2018/paper.tex
removing red valuesgit add -v papers/eccv2018/*

@@
 Finally, we formulate the region merging as a lifted multicut partitioning problem with topological constraints to avoid cycles.
-We demonstrate the performance of our approach on multiple real-world connectomics datasets with an average split variation of information improvement of \TODO{XX}\%.
+We demonstrate the performance of our approach on multiple real-world connectomics datasets with an average variation of information improvement of 19.7\%.
 \keywords{connectomics, biological constraints, region merge, skeletonization, deep learning, lifted multicut}

### 2018-03-14 papers/eccv2018/0_introduction.tex
updated red Xs

@@
 %This allows us to leverage both local and global information to produce more accurate reconstructions. 
-With the biological constraints, we can make use of both geometric and topological prior information to produce more accurate reconstructions (Fig.~\ref{fig:biological_constraints}).
+With the biological constraints, we can make use of both geometric and topological prior information to produce more accurate reconstructions (Fig.~\ref{fig:teaser_pipeline}).
 Our method is independent of image resolution and acquisition parameters, enabling its application to isotropic and anisotropic image data without retraining.
@@
 %(3) an empirical evaluation of our method on several connectomics datasets;  % this is not contribution
-last, improved performance over a state-of-the-art pixel-based reconstruction approach on average by $19.7\%$ while maintaining scalable runtimes for large volumes.
+last, improved performance over a state-of-the-art pixel-based reconstruction approach on average by $8.2\%$ while maintaining scalable runtimes for large volumes.

### 2018-03-14 papers/eccv2018/paper.tex
updated red Xs

@@
 Finally, we formulate the region merging as a lifted multicut partitioning problem with topological constraints to avoid cycles.
-We demonstrate the performance of our approach on multiple real-world connectomics datasets with an average variation of information improvement of 19.7\%.
+We demonstrate the performance of our approach on multiple real-world connectomics datasets with an average variation of information improvement of 8.2\%.
 \keywords{connectomics, biological constraints, region merge, skeletonization, deep learning, lifted multicut}

### 2018-03-14 papers/eccv2018/0_introduction.tex
minor edits to first few sections, removed all red Xs

@@
 For region merging, most methods do not use prior biological knowledge of the 3D shape of neural structures.
-Simple threshold-based mean agglomeration methods can achieve superhuman resolution  small-sized volumes~\cite{lee2017superhuman}.
 
@@
 
+We can make use of both geometric and topological prior information to produce more accurate reconstructions matching the underlying biology (Fig.~\ref{fig:teaser_pipeline}).
+
 We present a new region merging framework that imposes both local and global biological constraints onto the output segmentation to match the underlying structure of neuronal processes.
@@
 %This allows us to leverage both local and global information to produce more accurate reconstructions.
-With the biological constraints, we can make use of both geometric and topological prior information to produce more accurate reconstructions (Fig.~\ref{fig:teaser_pipeline}).
+
 Our method is independent of image resolution and acquisition parameters, enabling its application to isotropic and anisotropic image data without retraining.
@@
 %(3) an empirical evaluation of our method on several connectomics datasets;  % this is not contribution
-last, improved performance over a state-of-the-art pixel-based reconstruction approach on average by $8.2\%$ while maintaining scalable runtimes for large volumes.
+last, improved variation of information performance over a state-of-the-art pixel-based reconstruction approach on average by $8.2\%$ while maintaining scalable runtimes for large volumes.

### 2018-03-14 papers/eccv2018/2_method.tex
minor edits to first few sections, removed all red Xs

@@
 First, we only consider merging segments based on a skeletonized representation of the input segmentation (Fig.~\ref{fig:teaser_pipeline}a).
-This is enables us to reduce the number of nodes in the graph based on prior knowledge of the shape of neuronal processes.
+This enables us to reduce the number of nodes in the graph based on prior knowledge on the shape of neuronal processes.
 Second, we train a convolutional neural network that learns biological constraints based on the shapes of the input segmentation (Fig.~\ref{fig:teaser_pipeline}b).
@@
 \label{sec:skeletonization}
-Most region merging methods create the region graph by removing small-sized segments and linking each pair of adjacent segments, which can still lead to a large graph size due to the irregular shape of neural structures.
-We here use the skeleton representation of the segmentation and reduce the graph size with the geometric constraints on the connectivity of two adjacent segments to prune edges.
+Most region merging methods create a region graph by removing small-sized segments and linking each pair of adjacent segments, which can still lead to a large graph size due to the irregular shape of neural structures.
+We use a skeleton representation of the segmentation to reduce the graph size with the geometric constraints on the connectivity of two adjacent segments to prune edges.
 % a bit trivial, as everyone is doing this. maybe no need to mention
@@
 The CNN receives three input channels for every voxel in the ROI around segments $l_1$ and $l_2$. 
-The input in all of the channels is in the range $\{-0.5, 0.5\}$. 
+The input in all of the channels is in the set $\{-0.5, 0.5\}$. 
 The first channel is $0.5$ only if the corresponding voxel has label $l_1$. 
@@
 \subsection{Optimization-Based Graph Partition}
-
+\label{sec:optimization}
 After graph construction, we segment the graph in a globally consistent manner while enforcing topological constraints on the output.
@@
 where $\beta$ is a tunable parameter that encourages over- or under-segmentation. 
+Since, there are many more lifted edges than adjacent edges, we scale down the lifted weights proportionally to their total number.  
+~\cite{beier2017multicut}.
 \\~\\

### 2018-03-14 papers/eccv2018/3_evaluation.tex
updated red Xs
minor edits to first few sections, removed all red Xs

@@
 %The resulting 3D oversegmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}.
-For the Kasthuri dataset, we used the segmentation pipeline from Funke et al.~\cite{funke2017deep}. 
-We first train a 3D affinity prediction U-Net model~\cite{ronneberger2015u} with MALIS loss~\cite{Turaga:2009} and apply the watershed and agglomeration method~\cite{funke2017deep} to obtain the final segmentation result.
+The segmentation of the Kasthuri dataset was computed by agglomerating 3D supervoxels produced by the z-watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}. 
+A recent study by Funke et al.~\cite{funke2017deep} demonstrated superior performance of such methods over existing ones on anisotropic data. 
+We learn 3D affinities using MALIS loss with a U-net~\cite{ronneberger2015u,Turaga:2009}. 
+We apply the z-watershed algorithm with suitable parameters to compute a 3D over-segmentation of the volume. 
+The resulting 3D over-segmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}.
 For the FlyEM data, based on the authors' suggestion~\cite{takemura2017connectome}, we apply a context-aware delayed agglomeration algorithm~\cite{10.1371/journal.pone.0125825} that shows improved performance on this dataset over the pipeline used in the original publication.
@@
 %Higher values of $\beta$ encourage over-segmentation.
-Figure~\ref{fig:variation-of-information} shows our results for variables $\beta \in [0.5, 0.9]$. 
-For our multicut analysis we use $\beta = 0.5$. There are many more lifted edges than adjacent edges. 
-To prevent the lifted weights from dominating the objective function we weight each set of edges~\cite{beier2017multicut}.
+Figure~\ref{fig:variation-of-information} shows our results for variables $\beta \in [0.5, 0.99]$. 
+For our multicut analysis we use $\beta = 0.95$ (Sec.~\ref{sec:optimization}).
 
@@
 Since we are measuring the entropy between two clusterings, lower VI scores are better.
+The sum of these conditional entropies gives the total variation of information.
 

### 2018-03-14 papers/eccv2018/4_results.tex
minor edits to first few sections, removed all red Xs

@@
 
-Our algorithm improves the accuracy of the reconstruction for every dataset, reducing the VI split score on average by \TODO{XX}\% on the three testing datasets. 
 Scores closer to the origin are better for this metric, and in every instance our results are below the green curve.
-We see significant improvements on the Kasthuri datasets (VI split reduction of \TODO{XX}\%) and more modest improvements on the FlyEM datasets (reduction of \TODO{XX}\% and \TODO{XX}\%).
+We see improvements on each data with a reduction in total VI score of $10.4\%$ on the Kasthuri data and $8.9\%$ and $5.4\%$ on the FlyEM datasets.
 
@@
 The baseline algorithm considers all adjacent regions for merging. 
-Our method removes a significant portion of these candidates while maintaining a large number of the true merge locations (e.g., 556 compared to 610). 
-Our pruning heuristic removes at least $3.5\times$ the number of edges on all datasets, achieving a maximum removal rate of $4.8\times$.
+Our method removes a significant portion of these candidates while maintaining a large number of the true merge locations (e.g., 764 compared to 974). 
+Our pruning heuristic removes at least $3.5\times$ the number of edges on all datasets, achieving a maximum removal rate of $4.15\times$.
 However, there are some adjacent over-segmented labels which are not considered.
@@
 	\caption{The results of our graph pruning approach compared to the baseline graph with all adjacent regions.
-We show the number of true merge locations (e.g., 610) compared to total number of edges in the graph (e.g., 23,506) for each case.
+We show the number of true merge locations (e.g., 974) compared to total number of edges in the graph (e.g., 25,798) for each case.
 The number of missed splits corresponds to the number of split errors that our method misses compared to an adjacency matrix.}
@@
 		\textbf{Dataset} & \textbf{Segment Adjacency} & \textbf{Skeleton Pruning} & \textbf{Missed Splits} & \textbf{Gained Edges} \\ \hline
-		Kasthuri & 610 / 23,506 & 556 / 4,921 & 214 & 160 \\
+		Kasthuri & 974 / 25,798 & 764 / 6,218 & 307 & 97 \\
 		FlyEM Vol. 1 & 304 / 15,949 & 212 / 4,578 & 105 & 13 \\
@@
 The second and fourth examples in Fig.~\ref{fig:qualitative-results} show correctly reconstructed neurons where two of the segments are non-adjacent. 
-On average in our datasets we correctly merge \TODO{XX} of the non-adjacent segments. 
 \\~\\
@@
 In this example the small segment is carved from the larger segment in a location where there are no skeleton endpoints. 
-There are on average 146 such examples in our datasets.
+There are on average 177 such examples in our datasets.
 \\~\\
@@
 Data augmentation at test time can improve accuracy results~\cite{zeng2017deepem3d,lee2017superhuman}.
-When computing the probability to merge two segments, we input the initial segment into our CNN as well as 3 randomly rotated and flipped examples (in the same manner as training augmentation).
+When computing the probability to merge two segments, we randomly rotate and flip the examples three times (in the same fashion as training augmentation).
 This produces some additional increase in overall accuracy (Figure ~\ref{fig:receiver-operating-characteristic}).
@@
 Table \ref{table:multicut} shows the changes in precision, recall, and accuracy for all four datasets compared to the CNN with both the multicut and ``lifted'' multicut formulations.
-These results correspond to $\beta = 0.5$ (Sec.~\ref{sec:edge-weights}). 
+These results correspond to $\beta = 0.95$ (Sec.~\ref{sec:edge-weights}). 
 The precision increases on each dataset, although the recall decreases on all but one of the datasets.
@@
 Since it is more difficult to correct merge errors than split errors, it is often desirable to sacrifice recall for precision.
-Over the three testing datasets, applying a graph-based partitioning strategy reduced the number of merge errors by \TODO{XX}\%, \TODO{XX}\% and \TODO{XX}\%, respectively.
+Over the three testing datasets, applying a graph-based partitioning strategy increased the precision by $31.9\%$, $40.9\%$, and $27.8\%$ respectively.
 
@@
 	\caption{Precision, recall, and accuracy changes between CNN only and CNN paired with graph-optimized reconstructions for the training and three test datasets.
-The combined method results in better precision and accuracy.}
+The combined method results in better precision and accuracy.
+The lifted multicut extension provides very slight improvements in recall and accuracy over these three datasets.}
 	\centering
@@
 		\textbf{Dataset} & $\Delta$ \textbf{Precision} & $\Delta$ \textbf{Recall} & $\Delta$ \textbf{Accuracy} & $\Delta$ \textbf{Precision} & $\Delta$ \textbf{Recall} & $\Delta$ \textbf{Accuracy} \\ \hline
-		Kasthuri  & 7.56\% & -3.83\% & 0.89\% & -5.67\% & -2.15\% & -1.03\% \\
-		FlyEM Vol. 1 & 4.50\% & -4.24\% & 0.26\% & -1.52\% & -2.97\% & -0.16\%  \\
-		FlyEM Vol. 2 & 5.54\% & -1.38\% & 0.26\% & -8.65\% & -2.75\% & -0.54\%\\ \hline
+		Kasthuri  & 31.94\% & -36.24\% & 0.71\% & -1.01\% & 0.60\% & 0.02\% \\
+		FlyEM Vol. 1 & 40.87\% & -42.37\% & 1.26\% & 0.35\% & 0.85\% & 0.04\%  \\
+		FlyEM Vol. 2 & 27.80\% & -44.95\% & 0.33\% & 0.54\% & 0.92\% & 0.04\% \\ \hline
 	\end{tabular}
@@
 \end{table}
-
-Our post-processing method to agglomerate segments while enforcing the acyclic nature of our graph additionally improves precision by $6.6\%$ on average while only costing $-1.16\%$ in recall. 
-Note that our post-processing strategy by design cannot increase the recall.
 
@@
 On our hardware, inference on the neural network had a throughput of 30 examples per second. 
-Lastly, on this dataset the multicut algorithm ran for \TODO{XX} seconds while the lifted multicut variant spent \TODO{XX} seconds.
+Lastly, on this dataset the multicut algorithm ran for 25.28 seconds while the lifted multicut variant took 36.5 seconds.

### 2018-03-14 papers/eccv2018/5_conclusions.tex
minor edits to first few sections, removed all red Xs

@@
 In the future, these methods can be adjusted to apply additional domain constraints. 
-We can augment the graph with more information from the image data, such as synaptic locations, cell morphology, locations of mitochondria, etc. 
+We can augment the graph with more information from the image data, such as synaptic connections, cell morphology, and locations of mitochondria. 
 This would allow us to match other biological constraints during graph partitioning. 
 For example, we could then enforce the constraint that a given segment only has post- or pre-synaptic connections.
+
 An augmented graph would also be helpful for splitting improperly merged segments by adding additional terms to the partitioning cost function. 
+Using skeletons we can apply biological constraints on the topology for neurons that are improperly merged.
 Finally, we believe that the benefits of top-down enhancements from graph optimization can extend beyond connectomics to other domains, such as medical image segmentation.

### 2018-03-14 papers/eccv2018/4_results.tex
benchmark figure

@@
 	\centering
-	\includegraphics[width=0.32\linewidth]{./figures/voi-Kasthuri-Luigi-Test.png}
-	\includegraphics[width=0.32\linewidth]{./figures/voi-FlyEM-Vol--1.png}
-	\includegraphics[width=0.32\linewidth]{./figures/voi-FlyEM-Vol--2.png}
+	\includegraphics[width=0.32\linewidth]{./figures/benchmark/voi-Kasthuri-Luigi-Test.pdf}
+	\includegraphics[width=0.32\linewidth]{./figures/benchmark/voi-FlyEM-Vol--1.pdf}
+	\includegraphics[width=0.32\linewidth]{./figures/benchmark/voi-FlyEM-Vol--2.pdf}
 	\caption{VI scores of our method (red) compared to the baseline segmentation (green) and an oracle (blue) that optimally partitions the graph based on ground truth.

### 2018-03-14 papers/eccv2018/0_introduction.tex
add intro: biological constraints

@@
 State-of-the-art automatic 3D reconstruction approaches use pixel-based convolutional neural networks (CNNs) and watershed transforms to generate initial over-segmentation, followed by region merging steps~\cite{seymour2016rhoananet,lee2015recursive,nunez2014graph,parag2017anisotropic,ronneberger2015u,zlateski2015image}.
-For region merging, most methods do not use prior biological knowledge of the 3D shape of neural structures.
+%For region merging, most methods do not use prior biological knowledge of the 3D shape of neural structures.
 
@@
 
-We can make use of both geometric and topological prior information to produce more accurate reconstructions matching the underlying biology (Fig.~\ref{fig:teaser_pipeline}).
+Due to their biological nature, these over-segmented regions are connected with specific geomtric and topological properties.
+For example, L-shape juctions and Arrow-shape junctions are rare in neural structures and these regions do not form cycles.
+Thus, we can make use and learn these shape prior information to produce more accurate region merging to match the underlying biology (Fig.~\ref{fig:teaser_pipeline}).
 

### 2018-03-14 papers/eccv2018/3_evaluation.tex
papers: last updates

@@
 %The resulting 3D oversegmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}.
-The segmentation of the Kasthuri dataset was computed by agglomerating 3D supervoxels produced by the z-watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}. 
-A recent study by Funke et al.~\cite{funke2017deep} demonstrated superior performance of such methods over existing ones on anisotropic data. 
-We learn 3D affinities using MALIS loss with a U-net~\cite{ronneberger2015u,Turaga:2009}. 
+The segmentation of the Kasthuri dataset is computed by agglomerating 3D supervoxels produced by the z-watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}. 
+A recent study by Funke et al.~\cite{funke2017deep} demonstrates superior performance of such methods over existing ones on anisotropic data. 
+We learn 3D affinities using MALIS loss with a U-Net~\cite{ronneberger2015u,Turaga:2009}. 
 We apply the z-watershed algorithm with suitable parameters to compute a 3D over-segmentation of the volume. 
@@
 %\noindent\textbf{Training Augmentation.}
-Since our input is an existing segmentation of the EM images, there are very few training examples compared to per-pixel classifiers that can train on a unique window for each voxel. 
+Since our input is an existing segmentation of the EM images, there are very few training examples compared to per-pixel classifiers that train on a unique window for each voxel. 
 The Kasthuri dataset represents a region of brain over $\SI[product-units=single]{800}{\micro\meter}^3$ in volume and only yields 640 positive merge examples and 4821 negative ones.
 To avoid overfitting our deep networks, we apply the following augmentations on the training examples.
-During a single batch, we randomly select ten positive and negative examples. 
-With probability 0.5, the example is reflected across the $xy$-plane. 
-We then rotate the example by a random angle between $0$ and $360$ degrees using nearest neighbor interpolation. 
+During a single batch, we randomly select ten positive and ten negative examples. 
+With probability 0.5, an example is reflected across the $xy$-plane. 
+We then rotate each example by a random angle between $0$ and $360$ degrees using nearest neighbor interpolation. 
 The supplemental material contains experiments demonstrating the benefits of this augmentation strategy.

### 2018-03-14 papers/eccv2018/4_results.tex
papers: last updates

@@
 Fig.~\ref{fig:qualitative-results} (right) shows typical failure cases of our method (red circles).
-In two of these examples the algorithm correctly predicted several merges before a single error rendered the segment as wrong.
-In the third example (blue circle) a merge error in the initial segmentation propagated to our output.
+In two of these examples the algorithm correctly predicts several merges before a single error renders the segment as wrong.
+In the third example (blue circle) a merge error in the initial segmentation propagates to our output.
 We now analyze how each major component of our method contributes to this final result.
@@
 There are some pairs of segments which we do not consider for merging because of our reliance on the skeletons.
-Fig.~\ref{fig:skeleton-results} shows two such cases. 
-The endpoints of both segments are circled.
-In this example the small segment is carved from the larger segment in a location where there are no skeleton endpoints. 
+Fig.~\ref{fig:skeleton-results} shows two such cases with the closest endpoints circled. 
+In the right example the small segment is carved from the larger segment in a location where there are no skeleton endpoints. 
 There are on average 177 such examples in our datasets.
@@
 \noindent\textbf{Edge Weight Learning}
-We first evaluate the effectiveness of inference augmentation.
 %\subsubsection{Inference Augmentation}
 %\noindent\textbf{Inference Augmentation.}
-Data augmentation at test time can improve accuracy results~\cite{zeng2017deepem3d,lee2017superhuman}.
+Data augmentation at test time can improve accuracy results~\cite{lee2017superhuman,zeng2017deepem3d}.
 When computing the probability to merge two segments, we randomly rotate and flip the examples three times (in the same fashion as training augmentation).
-This produces some additional increase in overall accuracy (Figure ~\ref{fig:receiver-operating-characteristic}).
 The supplemental material contains experiments showing the trade-offs between increased accuracy and runtime when using these augmentation strategies.
@@
 	\end{minipage}
-	\caption{\textit{Failure cases.} The top two examples correspond to segment pairs that we incorrectly prune from the graph.
+	\caption{The top two examples correspond to segment pairs that we incorrectly prune from the graph.
 The distance between the circled endpoints is too great.
-The bottom two examples shows pairs of segments that belong to the same neuron but are not adjacent in the input segmentation.}
+The bottom two examples show pairs of segments that belong to the same neuron but are not adjacent in the input segmentation.
+However, we correctly merge these pairs.}
 	\label{fig:skeleton-results}

### 2018-03-14 papers/eccv2018/4_results.tex
small changes to performance

@@
 \noindent\textbf{Graph Partition}
-The graph optimization strategy using multicut increases our accuracy over using just the CNN.
-Table \ref{table:multicut} shows the changes in precision, recall, and accuracy for all four datasets compared to the CNN with both the multicut and ``lifted'' multicut formulations.
+The graph optimization strategy using multicut increases accuracy over using just the CNN.
+Table \ref{table:multicut} shows the changes in precision, recall, and accuracy for all four datasets compared to the CNN with both the multicut and lifted multicut formulations.
 These results correspond to $\beta = 0.95$ (Sec.~\ref{sec:edge-weights}). 
-The precision increases on each dataset, although the recall decreases on all but one of the datasets.
-The ``lifted'' variant further accentuates this trend of increasing precision and accuracy at the expense of recall. 
+The precision increases on each dataset, although the recall decreases on each datasets.
 Since it is more difficult to correct merge errors than split errors, it is often desirable to sacrifice recall for precision.
@@
 
-Every step in our framework is fast enough on large connectomics datasets. 
-After downsampling, skeletonization takes less than 1 second per segment on average. 
-On average, each segment was skeletonized in 0.56 seconds on the training half of the Kasthuri data set. 
+Every step in our framework is fast enough for large connectomics datasets. 
+On our training data, after downsampling, each segment was skeletonized in 0.56 seconds on average.
 There are 4451 such segments resulting in a total running time of 2,492 seconds on an 800 megavoxel volume. 
-From here, it took just over 31 seconds to generate the edges for our graph by considering nearby skeleton endpoints.
-On our hardware, inference on the neural network had a throughput of 30 examples per second. 
-Lastly, on this dataset the multicut algorithm ran for 25.28 seconds while the lifted multicut variant took 36.5 seconds.
+From here, it took just over 31 seconds to generate the edges for our graph.
+On our hardware, inference on the neural network has a throughput of 30 examples per second. 
+Lastly, the multicut algorithm ran for 25.28 seconds while the lifted multicut variant took 36.5 seconds on the graph from this dataset.

### 2018-03-14 papers/eccv2018/2_method.tex
papers: last updates
figure caption

@@
 	\end{minipage}
-	\caption{Example skeletons (in black) extracted from segments using a variant of the TEASER algorithm~\cite{sato2000teasar}.}
+	\caption{Example skeletons (in black) extracted from segments using a variant of the TEASER algorithm~\cite{sato2000teasar}.
+These skeletons not only well-capture the shape of the segmentation, but also provide end-points useful for region merging proposals.}
 	\label{fig:skeletonization}
@@
 	\end{minipage}
-	\caption{Two example candidates for merging. The two segments in the left example do not belong to the same neuron as evidenced by the sharp turning radius indicated by the arrow.}
+	\caption{Geometric constraints for region merging.
+We show two region merging proposals.
+On the left, the segments do not belong to the same neuron, as evidenced by the sharp turning radius; while on the right, the segments should be merged due to the continuity of the 3D shape.
+Instead of using handcrafted geometric features, we train a convolutional neural networks to automatically learn them from the ground truth labels.}
 	\label{fig:turn-radii}
@@
 where $\beta$ is a tunable parameter that encourages over- or under-segmentation. 
-Since, there are many more lifted edges than adjacent edges, we scale down the lifted weights proportionally to their total number.  
+Since, there are many more lifted edges than adjacent edges, we scale down the lifted weights proportionally to their total number  
 ~\cite{beier2017multicut}.

### 2018-03-14 papers/eccv2018/4_results.tex
figure caption

--- 2018-03-14 papers/eccv2018/4_results.tex
@@
 	\includegraphics[width=0.32\linewidth]{./figures/benchmark/voi-FlyEM-Vol--2.pdf}
-	\caption{VI scores of our method (red) compared to the baseline segmentation (green) and an oracle (blue) that optimally partitions the graph based on ground truth.
-Lower scores are better.
-Our method improves the accuracy of the segmentation in all cases.}
+	\caption{Benchmark results on two datasets.
+We compare our method (red) to the baseline segmentation (green) and an oracle (blue) that optimally partitions our constructed graph as the upper-bound for our method.
+Lower VI scores are better.
+Our method improves the segmentation accuracy over the baseline in all cases.
+	Note that our model is only trained on Kasthuri dataset and it generalizes well on the FlyEM dataset.}
 	\label{fig:variation-of-information}

### 2018-03-19 papers/eccv2018/2_method.tex
papers: updated with final draft

@@
 	\caption{Example skeletons (in black) extracted from segments using a variant of the TEASER algorithm~\cite{sato2000teasar}.
-These skeletons not only well-capture the shape of the segmentation, but also provide end-points useful for region merging proposals.}
+These skeletons not only capture the shape of the segmentation, but also provide endpoints useful for region merging proposals.}
 	\label{fig:skeletonization}
@@
 We show two region merging proposals.
-On the left, the segments do not belong to the same neuron, as evidenced by the sharp turning radius; while on the right, the segments should be merged due to the continuity of the 3D shape.
+On the left, the segments do not belong to the same neuron, as evidenced by the sharp turning radius indicated by the arrow; while on the right, the segments should be merged due to the continuity of the 3D shape.
 Instead of using handcrafted geometric features, we train a convolutional neural networks to automatically learn them from the ground truth labels.}

### 2018-03-19 algorithms/cpp-lifted-multicut.cpp
fixed lifted multicut

@@ -27,13 +27,19 @@ unsigned char *CppLiftedMulticut(unsigned long nvertices, unsigned long nedges, 
     andres::graph::CompleteGraph<> lifted_graph(nvertices); 
     std::vector<double> weights(lifted_graph.numberOfEdges());
 
+    double downsample_rate = nedges / (double)(nvertices * nvertices);
+
     for (unsigned long iv1 = 0; iv1 < nvertices; ++iv1) {
         for (unsigned long iv2 = iv1 + 1; iv2 < nvertices; ++iv2) {
             double probability = lifted_weights[iv1 * nvertices + iv2];
-            if (probability < 0.0001) probability = 0.0001;
-            if (probability > 0.9999) probability = 0.9999;
-            else weights[lifted_graph.findEdge(iv1, iv2).second] = log(probability / (1.0 - probability)) + log((1.0 - beta) / beta);
+            weights[lifted_graph.findEdge(iv1, iv2).second] = nedges * (log(probability / (1.0 - probability)) + log((1.0 - beta) / beta));
         }
+    }
+    for (unsigned long ie = 0; ie < nedges; ++ie) {
+        unsigned long vertex_one = vertex_ones[ie];
+        unsigned long vertex_two = vertex_twos[ie];
+        double probability = lifted_weights[vertex_one * nvertices + vertex_two];
+        weights[lifted_graph.findEdge(vertex_one, vertex_two).second] = nvertices * (nvertices - 1) / 2 * (log(probability / (1.0 - probability)) + log((1.0 - beta) / beta));
     }
 
     // create empty edge labels

### 2018-03-19 cnns/skeleton/generate_features.py

@@ -186,8 +186,8 @@ def GenerateFeatures(prefix, threshold, maximum_distance, network_distance, endp
 
         extracted_seg2gold_mapping = seg2gold.Mapping(extracted_segmentation, extracted_gold, match_threshold=0.70, nonzero_threshold=0.40)
 
-        gold_one = extracted_seg2gold_mapping[label_one]
-        gold_two = extracted_seg2gold_mapping[label_two]
+        gold_one = seg2gold_mapping[label_one]
+        gold_two = seg2gold_mapping[label_two]
 
         ground_truth = (gold_one == gold_two)
 

### 2018-03-19 papers/eccv2018/supplemental/classifier.tex

--- 2018-03-12 papers/eccv2018/supplemental/classifier.tex
@@
 
-\subsection{Network Architecture}
+After generating the list of potential merge locations we extract a cubic region of interest around each.
+We experimented with three different cube side lengths: $800 \textrm{nm}$, $1200 \textrm{nm}$, and $1600 \textrm{nm}$. 
+Side lengths of $1200 \textrm{nm}$ performed better on the training and validation data on our network.
 
+\vspace{1cm}
+
+\noindent
+\textbf{Network Architecture}
 We tested various architectures before deciding on the one we present in the paper. 
@@
 These input sizes correspond to specific output sizes from the last VGG block.
+For training we use the mean squared error loss function and optimize with SGD with Nesterov momentum.
 
@@
 		\textbf{Depth} & \textbf{Input Size} & \textbf{No. Parameters} & \textbf{Output Size} & \textbf{Accuracy} & \textbf{Precision} & \textbf{Recall} \\ \hline
-		      3        & (3, 18, 52, 52)     & 1,101,553               & (64, 3, 3, 3)        &                   &                    &  \\
-		      3        & (3, 20, 60, 60)     & 2,313,969               & (64, 4, 4, 4)        &                   &                    &  \\
-		      3        & (3, 22, 68, 68)     & 4,312,817               & (64, 5, 5, 5)        &                   &                    &  \\
-		      3        & (3, 24, 76, 76)     & 7,294,705               & (64, 6, 6, 6)        &                   &                    &  \\
-		      3        & (3, 26, 84, 84)     & 11,456,241              & (64, 7, 7, 8)        &                   &                    &  \\
-		      3        & (3, 28, 92, 92)     & 16,994,033              & (64, 8, 7, 8)        &                   &                    &  \\
-		      3        & (3, 30, 100, 100)   & 24,104,689              & (64, 9, 9, 9)        &                   &                    &  \\
-		      4        & (3, 28, 92, 92)     & 1,404,913               & (128, 2, 2, 2)       &                   &                    &  \\
-		      4        & (3, 32, 108, 108)   & 2,650,097               & (128, 3, 3, 3)       &                   &                    &  \\ \hline
+		      3        & (3, 18, 52, 52)     & 1,101,553               & (64, 3, 3, 3)        & 91.30             & 58.06              & 92.81 \\
+		      3        & (3, 20, 60, 60)     & 2,313,969               & (64, 4, 4, 4)        & 92.41             & 61.70              & 92.41 \\
+		      3        & (3, 22, 68, 68)     & 4,312,817               & (64, 5, 5, 5)        & 92.33             & 61.49              & 92.34 \\
+		      3        & (3, 24, 76, 76)     & 7,294,705               & (64, 6, 6, 6)        & 93.51             & 65.78              & 93.13 \\
+		      \textbf{3}        & \textbf{(3, 26, 84, 84)}     & \textbf{11,456,241}              & \textbf{(64, 7, 7, 8)}        & \textbf{95.38}             & \textbf{74.43}              & \textbf{92.34} \\
+		      3        & (3, 28, 92, 92)     & 16,994,033              & (64, 8, 7, 8)        & 91.87             & 59.70              & 94.22 \\
+		      3        & (3, 30, 100, 100)   & 24,104,689              & (64, 9, 9, 9)        & 92.01             & 60.24              & 93.75 \\
+		      4        & (3, 28, 92, 92)     & 1,404,913               & (128, 2, 2, 2)       & 91.70             & 60.24             & 85.94 \\
+		      4        & (3, 32, 108, 108)   & 2,650,097               & (128, 3, 3, 3)       & 92.80             & 64.28              & 86.88 \\\hline
 	\end{tabular}
@@
 
-\subsection{Training Augmentation}
+\noindent
+\textbf{Inference Augmentation}
+Augmenting the data for inference increases the precision by 3.79\% and the accuracy by 0.64\%. 
+Figure~\ref{fig:test-augmentation} shows the changes in the number of true positives, false positives, and false negatives as a function of the number of augmentations on the Kasthuri dataset.
+The number of false positives decreases at first, falling below 200 after a second augmentation.
+The gains become more gradual with the number of augmentations, leveling out around 175 false positives after 5 augmentations.
 
-\subsection{Testing Augmentation}
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=0.45\linewidth]{./figures/Kasthuri-test-augmentation.png}
+	\caption{The number of false positives decreases with our data augmentation scheme. The benefit of augmentation gradually decreases with the number of random examples.}
+	\label{fig:test-augmentation}
+\end{figure}

### 2018-03-19 papers/eccv2018/supplemental/skeletonization.tex

@@
 
-\subsection{Volume Downsampling}
+\noindent
+\textbf{Volume Downsampling}
+We downsample the segmentation data to a resolution of $30$ nm in each direction. 
+The skeletonization algorithm that we use takes as a parameter the minimum distance between joints in the skeleton~\cite{zhao2014automatic}.
+When we downsample, we also reduce this minimum distance by the same rate.
+We find that this produces expressive skeletons at a fraction of the computational cost. 
+Table~\ref{table:skeleton} shows statistics comparing the skeletonization algorithm on 200 randomly chosen labels.
 
-\subsection{Node Generation}
+\begin{table}
+	\scriptsize
+	\begin{center}
+		\begin{tabular}{c c c c c} \hline
+			& \textbf{Average Time} &  \textbf{Skeleton Length} & \textbf{No. Branches} & \textbf{No. Endpoints} \\ \hline
+			Full Resolution & 16.35s & 1,352,157nm & 9,858 & 1,068 \\
+			Downsampled & 0.56s & 1,671,138nm & 9,359  & 1,824 \\ \hline
+		\end{tabular}
+	\caption{The results of the skeletonization algorithm on both the full resolution and the downsampled data.
+Downsampling the data provides expressive skeletons at a fraction of the computational cost.}
+	\label{table:skeleton}
+	\end{center}
+\end{table}
 
-\subsection{Edge Generation}
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=0.45\linewidth]{./figures/node-threshold.png}
+		\caption{The number of remaining nodes after increasing the threshold (blue) and the number of voxels excluded as a percent of the total volume (green).}
+		\label{fig:node-pruning}
+	\end{center}
+\end{figure}
+
+\noindent
+\textbf{Node Generation}
+We remove all nodes from the graph corresponding to labels with fewer than $t_{seg}$ voxels.
+Figure \ref{fig:node-pruning} shows the results of varying $t_{seg}$ on two different quantities for the Kasthuri training volume. 
+The blue line indicates the number of nodes remaining in the graph.
+The rate of node reduction decreases for larger thresholds since there are fewer labels of larger size. 
+The green line shows the percent of voxels with a label pruned from the graph.
+Ideally this number is low since we want to remove small segments which do not contribute much to the overall volume.
+This ``volume lost" grows at an increasing rate as the larger segments are removed. 
+Based on these curves we set $t_{seg} = 20,000$ voxels.
+With this threshold, we prune over half of the labels and only lose $1.5\%$ of the total volume.

### 2018-04-18 papers/quals2018/1_related_work.tex
quals: added first draft for qualifying exam proposals

--- 2018-03-14 papers/eccv2018/1_related_work.tex
@@
 A significant amount of connectomics research considers the problem of extracting segmentation information at the voxel level of EM images.
-First, intermediate representations like boundary, affinity or binary segmentation maps are generated from voxels.
-For the boundary probabilities, random forest with hand-designed features~\cite{kaynig2015large}, 2D and 3D convolution networks ~\cite{bogovic2013learned,seymour2016rhoananet,ronneberger2015u,ciresan2012deep,jain2010boundary,amelio_segmentation}.
-Later, the affinity between each voxel and its six neighors are widely used~\cite{lee2015recursive,parag2017anisotropic,cciccek20163d,turaga2010convolutional,lee2017superhuman}.
-3D U-Net architecture becomes popular~\cite{cciccek20163d} and MALIS cost function is designed to re-weight affinity prediction by their contribution to the segmentation error~\cite{briggman2009maximin}.
-More recently, flood-filling networks~\cite{januszewski2016flood} produce binary segmentations from raw pixels with a recurrent convolution network at a high computational cost.
+First, intermediate representations like boundary, affinity or binary segmentation maps are generated from the voxels.
+Random forests with hand-designed features~\cite{kaynig2015large}, or 2D and 3D convolutional networks produce boundary probabilities.
+~\cite{seymour2016rhoananet,ronneberger2015u,bogovic2013learned,ciresan2012deep,jain2010boundary,amelio_segmentation}.
+Often, the affinity between each voxel and its six neighbors are used~\cite{lee2015recursive,parag2017anisotropic,lee2017superhuman,cciccek20163d,turaga2010convolutional}. 
+The 3D U-Net architecture has become popular~\cite{cciccek20163d} and the MALIS cost function is specifically designed to re-weight affinity predictions by their contribution to the segmentation error~\cite{briggman2009maximin}.
+More recently, flood-filling networks~\cite{januszewski2016flood} produce binary segmentations from raw pixels with a recurrent convolutional network at a high computational cost.
 Orthogonal to the representation, model averaging~\cite{zeng2017deepem3d} and data augmentation~\cite{lee2017superhuman} methods can further improve the performance, where Lee et al.~\cite{lee2017superhuman} surpass the estimated human accuracy on the SNEMI3D dataset.
 
-Then, clustering techniques transform these intermediate representations into segmentations.
-Some early techniques apply computationally expensive graph partitioning algorithms with a single node per superpixel~\cite{andres2012globally}.
+Clustering techniques transform these intermediate representations into segmentations.
+Some early methods apply computationally expensive graph partitioning algorithms with a single node per superpixel~\cite{andres2012globally}.
 Several pixel-based approaches generate probabilities that neighboring pixels belong to the same neuron.
@@
 rely solely on the accuracy of the predicted affinities and define the metric as the mean affinity between segments~\cite{lee2017superhuman,funke2017deep}.
-Classification-based method predicts the probability to merge two segments from handcrafted~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image,10.1371/journal.pone.0125825,jain2011learning} and learned features~\cite{bogovic2013learned}.
-
-For the merging stategy, most methods use variants of hierarchical agglomeration methods~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image,10.1371/journal.pone.0125825} to greedily merge a pair of regions at a time.
+Classification-based methods generate the probability to merge two segments from handcrafted~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image,10.1371/journal.pone.0125825,jain2011learning} and learned features~\cite{bogovic2013learned}.
+For the merging strategy, most methods use variants of hierarchical agglomeration ~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image,10.1371/journal.pone.0125825} to greedily merge a pair of regions at a time.
 Jain et al.
-formulates the agglomeration as a reinforcement learning problem ~\cite{jain2011learning} and Pape et al.
+formulates the agglomeration problem as a reinforcement learning problem ~\cite{jain2011learning} and Pape et al.
 present a scalable multicut algorithm to partition superpixels with global optimization~\cite{beier2017multicut}.

### 2018-04-18 papers/quals2018/4_results.tex
quals: added first draft for qualifying exam proposals

--- 2018-03-14 papers/eccv2018/4_results.tex
@@
 	\includegraphics[width=0.32\linewidth]{./figures/benchmark/voi-FlyEM-Vol--2.pdf}
-	\caption{Benchmark results on two datasets.
-We compare our method (red) to the baseline segmentation (green) and an oracle (blue) that optimally partitions our constructed graph as the upper-bound for our method.
+	\caption{Segmentation benchmark results on three volumes.
+We compare our method (red) to the baseline segmentation (green) and an oracle (blue) that optimally partitions our constructed graph from our method.
 Lower VI scores are better.
 Our method improves the segmentation accuracy over the baseline in all cases.
-	Note that our model is only trained on Kasthuri dataset and it generalizes well on the FlyEM dataset.}
+	Note that our model is only trained on the Kasthuri training volume and it generalizes well to the FlyEM dataset.}
 	\label{fig:variation-of-information}

### 2018-04-18 papers/quals2018/paper.tex
quals: added first draft for qualifying exam proposals

--- 2017-11-15 papers/cvpr2018/paper.tex
@@
 %
-\newcommand{\FIX}[1]{\textcolor{red}{#1}}
-\newcommand{\hp}[1]{\textcolor{red}{HP: #1}}
-\newcommand{\donglai}[1]{\textcolor{blue}{[Donglai: #1]}}
+
+\cvprfinalcopy
 
@@
 	%%%%%%%%% TITLE
-\title{Graph-Based Neural Reconstruction from Morphological Skeletons}
+	\title{Biologically-Constrained Error Correction for Connectome Reconstruction}
 
-%Robust Agglomeration using 3D Skeletonization of Labeled for Connectomics}
-
-%\author{Brian Matejek\\
-%Harvard University\\
-%Cambridge, MA 02138, USA\\
-%{\tt\small bmatejek@seas.harvard.edu}
+	\author{Brian Matejek\\
+	Harvard University\\
+	Cambridge, MA 02138, USA\\
+	{\tt\small bmatejek@seas.harvard.edu}
 	%% For a paper whose authors are all at the same institution,
@@
 	%%{\tt\small secondauthor@i2.org}
-%}
+	}
 
@@
 	\begin{abstract}
-Advancements in electron microscopy image acquisition have created massive connectomics datasets in the terabyte range that make manual reconstruction of neuronal structures infeasible. 
-Current state-of-the-art automatic methods segment neural membranes at the pixel level followed by agglomeration methods to create full neuron reconstructions. 
-However, these approaches widely neglect global geometric properties that are inherent in the graph structure of neural wiring diagrams.
-In this work, we follow bottom-up pixel-based reconstruction by a top-down graph-based method to more accurately approximate neural pathways. 
-Using the membrane labels of the pixel-based segmentation we first generate skeletons in 3D.
-Using this 3D graph we train automatic classifiers for shape description to detect impossible neural pathways by looking at geometric properties.
-We then apply efficient graph-based optimization strategies to improve the segmentation labels.
-We demonstrate the performance of our approach on multiple real-world connectomics datasets with an average variation of information improvement of \FIX{$X\times$}.
-%The paper provides insights into learning shape features for top-down graph-based neuron reconstruction.
+Current state-of-the-art connectome reconstruction pipelines have two major steps: initial pixel-based segmentation with affinity prediction and watershed transform, and refined segmentation by merging oversegmented regions.
+For the region merging, most methods neglect geometric and topological constraints that are inherent in the graph structure of neural wiring diagrams.
+In this work, we use a biologically-constrained graph-based method to better reconstruct neural pathways.
+Given the initial segmentation, we first create a graph with nodes corresponding to segment labels and edges identifying potential locations of split errors based on the skeleton structure of the segmentation.
+Next, we train a convolutional neural network to capture the geometric properties of segment connections and produce edge weights as the probability of merging two nodes.
+Finally, we formulate the region merging as a lifted multicut partitioning problem with topological constraints to avoid cycles.
+We demonstrate the performance of our approach on multiple real-world connectomics datasets with an average variation of information improvement of 8.2\%.
 	\end{abstract}

### 2018-04-27 papers/quals2018/paper.tex
Changed format and removed old text

@@
 	%%%%%%%%% TITLE
-	\title{Biologically-Constrained Error Correction for Connectome Reconstruction}
+	\title{Segmentation of Electron Microscopy Images for Connectomics}
 
 	\author{Brian Matejek\\
+		Advisor: Hanspeter Pfister \\
 	Harvard University\\
-	Cambridge, MA 02138, USA\\
 	{\tt\small bmatejek@seas.harvard.edu}
@@
 
-	%%%%%%%%% ABSTRACT
-	\begin{abstract}
-Current state-of-the-art connectome reconstruction pipelines have two major steps: initial pixel-based segmentation with affinity prediction and watershed transform, and refined segmentation by merging oversegmented regions.
-For the region merging, most methods neglect geometric and topological constraints that are inherent in the graph structure of neural wiring diagrams.
-In this work, we use a biologically-constrained graph-based method to better reconstruct neural pathways.
-Given the initial segmentation, we first create a graph with nodes corresponding to segment labels and edges identifying potential locations of split errors based on the skeleton structure of the segmentation.
-Next, we train a convolutional neural network to capture the geometric properties of segment connections and produce edge weights as the probability of merging two nodes.
-Finally, we formulate the region merging as a lifted multicut partitioning problem with topological constraints to avoid cycles.
-We demonstrate the performance of our approach on multiple real-world connectomics datasets with an average variation of information improvement of 8.2\%.
-	\end{abstract}
-	%%%%%%%%	% BODY TEXT
-
 	\input{0_introduction}
@@
 
-	\input{3_evaluation}
+	\input{3_results}
 
-	\input{4_results}
+	\input{4_proposed}
 

### 2018-04-27 papers/miccai2017/sections/abstract.tex
papers: added final version of compresso

Recent advances in segmentation methods for connectomics and biomedical imaging produce very large datasets with labels that assign object classes to image pixels. The resulting label volumes are bigger than the raw image data and need compression for efficient storage and transfer. General-purpose compression methods are less effective because the label data consists of large low-frequency regions with structured boundaries unlike natural image data. We present \appName, a new compression scheme for label data that outperforms existing approaches by using a sliding window to exploit redundancy across border regions in 2D and 3D. We compare our method to existing compression schemes and provide a detailed evaluation on eleven biomedical and image segmentation datasets. Our method provides a factor of 600-2200x compression for label volumes, with running times suitable for practice.

### 2018-04-27 papers/miccai2017/sections/appendix.tex
papers: added final version of compresso

\section{Appendix} \label{sec:appendix}

Additional Math:

TEMPORARY:

For example, we analyzed the proportion of windows encoded as a function of the $x$ most frequent values on the AC3 dataset with a window size of $8 \times 8 \times 1$. The most common $V_w$---corresponding to zero boundary pixels---accounts for nearly 75\% of all windows. The top 2,500 and 13,000 most common $V_w$ values include 90\% and 95\% of all windows respectively. If there are $|W|$ windows with $n$ bits each the expected number of unique values for a completely random boundary map (i.e. a pixel $p = 1$ with probability 0.5) is:

CONNECTED COMPONENT RESULTS:

For every image slice, the encoding uses a deterministic connected component algorithm. 
We define $M$ as the number of connected components $m \in [0, M)$. 
The identifier values themselves are not confined to this range but rather from $[0, 2^{64})$. 
We construct a function $g_z(m) \to [0, 2^{64})$ for every slice $z$ that maps a connected component index to its per-pixel identifier. 
Under this scheme, we transmit $64 * M$ bits per image slice to encode all of the per-pixel identifiers. 
In run-length encoding, an identifier is transmitted at least once for every x-scanline intersecting a given segment. 
On the AC3 dataset, using connected components instead of run-length encoding reduced the number of identifiers transmitted from 1,524,280 to 27,280 over 75 slices---a reduction of nearly 5,500\%.

\begin{equation}
2^{n}\left[1 - \left(\frac{2^{n} - 1}{2^{n}}\right)^{|W|}\right]
\end{equation}

Here we present additional plots for the CREMI, AC3 and MRI datasets.

%
%
%
\begin{figure}[h]
\includegraphics[width=0.5\textwidth]{gfx/cremi_enconly_bytes.pdf}%
\includegraphics[width=0.5\textwidth]{gfx/cremi_enconly_ratio.pdf}%
\\
\includegraphics[width=0.5\textwidth]{gfx/cremi_enconly_encodingspeed.pdf}%
\includegraphics[width=0.5\textwidth]{gfx/cremi_enconly_decodingspeed.pdf}%
\caption{Evaluation of encoding methods on the \textbf{CREMI} dataset. The Bockwurst encoding scheme (black) outperforms Neuroglancer and run-length encoding (RLE) in terms of compression ratio (top right) but decodes much slower (bottom right).}
\label{fig:cremi_encoding_results}
\end{figure}

\begin{figure}[h]
\includegraphics[width=0.5\textwidth]{gfx/cremi_compression_bytes.pdf}%
\includegraphics[width=0.5\textwidth]{gfx/cremi_compression_ratios.pdf}%
\\
\includegraphics[width=0.5\textwidth]{gfx/cremi_compression_total_comp_speed.pdf}%
\includegraphics[width=0.5\textwidth]{gfx/cremi_compression_total_decomp_speed.pdf}%
\caption{General-purpose compression methods with different encoding schemes on the \textbf{CREMI} segmentation data. A combination of Bockwurst encoding (red) and LZ78 yields the best performance (top right)---over $2\times$ higher compression ratio than any other method and $1600\times$ smaller than the uncompressed data.}
\label{fig:cremi_compression_results}
\end{figure}

%
%
%
\begin{figure}[h]
\includegraphics[width=0.5\textwidth]{gfx/ac3_enconly_bytes.pdf}%
\includegraphics[width=0.5\textwidth]{gfx/ac3_enconly_ratio.pdf}%
\\
\includegraphics[width=0.5\textwidth]{gfx/ac3_enconly_encodingspeed.pdf}%
\includegraphics[width=0.5\textwidth]{gfx/ac3_enconly_decodingspeed.pdf}%
\caption{Bockwurst performs best among the tested encoding methods on \textbf{AC3} which is also our training dataset (top right). While Bockwurst provides also a reasonable encoding speed (bottom left), the decoding performance is poor (bottom right).}
\label{fig:ac3_encoding_results}
\end{figure}

\begin{figure}[h]
\includegraphics[width=0.5\textwidth]{gfx/ac3_compression_bytes.pdf}%
\includegraphics[width=0.5\textwidth]{gfx/ac3_compression_ratios.pdf}%
\\
\includegraphics[width=0.5\textwidth]{gfx/ac3_compression_total_comp_speed.pdf}%
\includegraphics[width=0.5\textwidth]{gfx/ac3_compression_total_decomp_speed.pdf}%
\caption{Performance of general-purpose compression methods combined with run-length encoding (RLE), Neuroglancer and Bockwurst on the \textbf{AC3} connectomics dataset. Bockwurst encoding (red) with LZ78 results in a compression ratio of over $1400\times$. This is better than all other methods but the compression and decompression speeds leave room for optimization.}
\label{fig:ac3_compression_results}
\end{figure}

\begin{figure}[h]
\center
\includegraphics[width=0.5\textwidth]{gfx/mri.png}%
\caption{One slice of the \textbf{brain MRI} segmentation data with different anatomical parts labeled by a unique identifier and colored using a lookup table.}
\label{fig:mridata}
\end{figure}

%
% 
%
\begin{figure}[h]
\includegraphics[width=0.5\textwidth]{gfx/mri_enconly_bytes.pdf}%
\includegraphics[width=0.5\textwidth]{gfx/mri_enconly_ratio.pdf}%
\\
\includegraphics[width=0.5\textwidth]{gfx/mri_enconly_encodingspeed.pdf}%
\includegraphics[width=0.5\textwidth]{gfx/mri_enconly_decodingspeed.pdf}%
\caption{Evaluation of encoding methods on the labeled \textbf{brain MRI} dataset. Bockwurst encoding (black) yields less encoding performance than Neuroglancer but outperforms run-length encoding (RLE). The MRI data size is approximately 130 MB, resulting in 1-2 seconds encoding time using all methods. Bockwurst, however, is much slower in decoding.}
\label{fig:mri_encoding_results}
\end{figure}

\begin{figure}[h]
\includegraphics[width=0.5\textwidth]{gfx/mri_compression_bytes.pdf}%
\includegraphics[width=0.5\textwidth]{gfx/mri_compression_ratios.pdf}%
\\
\includegraphics[width=0.5\textwidth]{gfx/mri_compression_total_comp_speed.pdf}%
\includegraphics[width=0.5\textwidth]{gfx/mri_compression_total_decomp_speed.pdf}%
\caption{General-purpose compression methods with different encoding schemes on the labeled \textbf{brain MRI} data. A combination of Bockwurst encoding (red) and LZ78 yields the best performance.}
\label{fig:mri_compression_results}
\end{figure}

### 2018-04-27 papers/miccai2017/sections/conclusions.tex
papers: added final version of compresso

\section{Conclusions} \label{sec:c}
% Things we learned during this project, such as:
% - LZMA is black magic
% - Certain encodings do not necessarily lead to better results after compression but can significantly improve other properties such as compression speed or before compression space consumption
% - Mitzenmacher is a cool guy
% - etc.
%In this paper, we study and evaluate encoding and compression methods for segmentation data with focus on connectomics.
%
%%% Summary
%In this paper, we study and evaluate compression of segmentation data for connectomics and introduce \appName---an efficient compression tool that outperforms existing solutions.
%Interestingly, we have learned that simple encoding schemes (e.g., RLE) can perform existing methods already and that complexity does not always proof beneficial. \cf{Since we have removed RLE from the plot we need to make sure to name it somewhere briefly in the results!}
%
%%% Future work
%Besides connectomics datasets, we show that \appName efficiently compresses labeled brain MRI data and we believe it generalizes well on any kind of labeled segmentation data.
%In the future we plan to improve random access to lower memory requirements for online viewers and focus on more efficient compression of the metadata (Sec. ~\ref{sec:m}).
%Also, we will integrate \appName into our analysis pipeline and provide wrappers for various other clients.
%
%%% Promotion
%To encourage testing of our tool, replication of our experiments, and adoption in the community, we provide \appName and results as free and open research at (link omitted for review).%\appUrl.
We have introduced \appName, an efficient compression tool for segmentation data that outperforms existing solutions on connectomics, MRI, and other segmentation data. 
%We believe our approach will generalize well to other kinds of label data. 
In the future we plan to improve random access to lower memory requirements for online viewers and enhance compression of the metadata.
Also, we will integrate \appName into our analysis pipeline and various end-user applications. 
To encourage testing of our tool, replication of our experiments, and adoption in the community, we release \appName and our results as free and open research at \href{github.com/rhoana/Compresso}{github.com/rhoana/Compresso}. 
%{\color{White} B to the Ockwurst!}

\smallskip

{\small M. Mitzenmacher is supported in part by NSF grants CNS-1228598, CCF-1320231, CCF-1535795, and CCF-1563710. H. Pfister is supported in part by NSF grants IIS-1447344 and IIS-1607800, by the Intelligence Advanced Research Projects Activity (IARPA) via Department of Interior/Interior Business Center (DoI/IBC) contract number D16PC00002, and by the King Abdullah University of Science and Technology (KAUST) under Award No. OSR-2015-CCF-2533-01.}

### 2018-04-27 papers/miccai2017/sections/evaluation.tex
papers: added final version of compresso

\section{Evaluation and Results} \label{sec:results}

%
%\paragraph{AC3 Subvolume.} For development and parameter exploration, we use the publicly-available dataset of mouse cortex known in the community as AC3. The dataset size is $1024\times1024\times75$ voxels and the resolution is $6\times6\times30~\text{nm}^3\text{/voxel}$. AC3 was acquired using serial section transmission electron microscopy (ssTEM).
%
%\paragraph{L. Cylinder.} We use the left part of the 3-cylinder mouse cortex volume of Kasthuri et al.~\cite{kasthuri2015saturated} ($2048\times2048\times50$ voxels). The tissue is dense mammalian neuropil from layers 4 and 5 of the S1 primary somatosensory cortex, acquired using serial section electron microscopy (ssEM). The dataset resolution is $3\times3\times30~\text{nm}^3\text{/voxel}$. Image data and a manually-labeled expert `ground truth' segmentation is publicly available\footnote{\scriptsize{\url{https://software.rc.fas.harvard.edu/lichtman/vast/}}}.
%
%\paragraph{CREMI.} As part of the MICCAI 2016 challenge on circuit reconstruction from electron microscopy images (CREMI), six ssTEM datasets were made publicly available\footnote{\scriptsize{\url{http://www.cremi.org}}},  each $1250\times1250\times125$ voxels. The volumes are part of an adult fruit fly (Drosophila melanogaster) brain. The resolution of all three datasets is $4\times4\times40~\text{nm}^3\text{/voxel}$. We include the CREMI A dataset for our evaluation.
%\\~\\
%We use a state-of-the-art method to create a dense automatic segmentation of the datasets.
%Membrane probabilities are generated using a convolutional neural network based on the U-net architecture~\cite{RonnebergerFB15}.
%The probabilities are used to seed watershed and generate an oversegmentation using superpixels.
%Agglomeration is then performed by the GALA active learning classifier~\cite{nunez2014graph}.
%The output of the agglomeration is shown in Fig.~\ref{fig:data}.
%
%\paragraph{MRI.} We include a label map of a T1-weighted brain MRI scan to evaluate compression on non-connectomics data. The dataset dimensions are $250\times250\times250$ voxels with a resolution of $1\times1\times1~\text{mm}^3\text{/voxel}$. This dataset is isotropic. The segmentation was obtained using the publicly available tool FreeSurfer\footnote{\scriptsize{FreeSurfer is available at \url{https://surfer.nmr.mgh.harvard.edu/}.}}.

%\subsection{Parameter Estimation}
%\paragraph{Varying Window Size.}
%\begin{figure}
%	\begin{center}
%		\includegraphics[width=0.7\textwidth]{./gfx/bockwurst_window_size.png}
%		\caption{The above plots show the effect of window size on the compression ratio. The left subplot shows the variation with window sizes $(n, n, 1)$ for $n$ ranging between $1$ and $720$. The right subplot shows the results where $z$ is no longer constrained to equal 1.}
%		\label{fig:bockwurst-window-size}
%	\end{center}
%\end{figure}
%Figure \ref{fig:bockwurst-window-size} shows the compression results of \appName on several connectomics datasets. There is a trade-off between the number of windows and the number of unique window values when varying the window size. The compression ratio generally peaks around the same window sizes across several different data sets.

We consider the following compression schemes: Compresso, Neuroglancer, Brotli, BZip2, Zlib, LZ78, LZF, LZMA, LZO, LZW, Zopfli, Zstandard, PNG, JPEG2000, and X.264. 
In addition to these stand-alone compression schemes we consider all pairs with a first stage encoding using either Compresso or Neuroglancer and a second stage using one of the general-purpose algorithms. 
Both \appName and Neuroglancer leave some redundancies that a general-purpose compressor can easily reduce; such multi-stage schemes are common in image compression. 
Table~\ref{tab:datasets} presents six connectomics, three MRI, and two image segmentation datasets used for evaluation. 
Compresso works for any arbitrary 2-D and 3-D window dimensions. We achieve the results in this section using an 8x8x1 window.

%We consider the following compression schemes: \appName, Neuroglancer, Run-Length Encoding (RLE), Brotli, BZip2, Zlib, LZ78, LZF, LZMA, LZO, LZW, Zopfli, Zstandard, PNG, JPEG2000, and X.264. In addition to these stand-alone compression schemes we consider all pairs between \appName, Neuroglancer, RLE, and the following general-purpose algorithms: Brotli, BZip2, ZLIB, LZ78, LZF, LZMA, LZO, LZW, Zopfli, Zstandard.

The combination of \appName and LZMA provides superior compression on all connectomics datasets (Tab.~\ref{tab:datasets}). Figure~\ref{fig:compression_ratios} shows the compression ratios for every compressor on segmentation data. For example, \appName achieves a compression ratio of over 950x on $L. Cylinder$ reducing the 10 gigabyte volume to 10.5 megabytes. LZMA performs very well by itself and paired with any encoding strategy. X.264 performs surprisingly poorly on these datasets, in part because

\begin{table}[!th]
\begin{minipage}{\textwidth}
\small
\caption{For evaluation, we use the following publicly available datasets. Segmentations were obtained using a combination of U-net~\cite{ronneberger2015u} and watershed, semi-automatic, or manually. Compresso paired with LZMA yields the best compression ratio on all datasets indicated by an asterisk (\textbf{*}). Neuroglancer paired with LZMA achieved the best compression ratio only for the SPL Brain Atlas (724x).}%While the training of our classifier is more expensive, testing accuracy is superior. }
\resizebox{\linewidth}{!}{
\begin{tabular}{l@{\hskip .1in}l@{\hskip .1in}l@{\hskip .2in}l@{\hskip .2in}l}
\toprule
Dataset & Size & Segmentation &  \multicolumn{2}{c}{\makecell{\textbf{Compresso} + \textbf{LZMA}\\Speed (Com./Dec.)~~~~~Compression Ratio}}\\
\midrule
\makecell[l]{\emph{AC3 Subvolume\footnotemark}\\~~mouse cortex, EM} & \makecell[l]{$1024\times1024\times150$ vx\\($6\times6\times30~\text{nm}^3\text{/vx}$)} & U-net & \makecell[l]{100 / 209 MB/s} & 814x \textbf{*}\\
\makecell[l]{\emph{AC4 Subvolume}\\~~mouse cortex, EM} & \makecell[l]{$1024\times1024\times100$ vx\\($6\times6\times30~\text{nm}^3\text{/vx}$)} & U-net & \makecell[l]{105 / 218 MB/s} & 701x \textbf{*}\\
\makecell[l]{\emph{L. Cylinder\footnotemark}~\cite{kasthuri2015saturated}\\~~mouse cortex, EM} & \makecell[l]{$2048\times2048\times300$ vx\\($3\times3\times30~\text{nm}^3\text{/vx}$)} & U-net & \makecell[l]{103 / 180 MB/s} & 952x \textbf{*}\\
\makecell[l]{\emph{CREMI A, B, C\footnotemark}\\~~drosophila brain, EM} & \makecell[l]{$1250\times1250\times125$ vx\\($4\times4\times40~\text{nm}^3\text{/vx}$)} & U-net & \makecell[l]{110 / 218, 118 / 243, \\ 110 / 219 MB/s} & \makecell[l]{857x \textbf{*}, 1239x \textbf{*}\\960x \textbf{*}}\\
\makecell[l]{\emph{SPL Brain Atlas\footnotemark}\\~~T1/T2-weighted MRIs} & \makecell[l]{$256\times256\times256$ vx\\($1\times1\times1~\text{mm}^3\text{/vx}$)} & Semi-autom. & \makecell[l]{85 / 254 MB/s} & 636x\\
\makecell[l]{\emph{SPL Knee Atlas\footnotemark}\\~~
MRI} & \makecell[l]{$512\times512\times119$ vx\\($0.277\times0.277\times1~\text{mm}^3\text{/vx}$)} & Semi-autom. & \makecell[l]{136 / 244 MB/s} & 1553x \textbf{*}\\
\makecell[l]{\emph{SPL Abdominal Atlas\footnotemark}\\~~CT} & \makecell[l]{$256\times256\times113$ vx\\($0.9375\times0.9375\times1.5~\text{mm}^3\text{/vx}$)} & Semi-autom. & \makecell[l]{91 / 254 MB/s} & 480x \textbf{*}\\
\makecell[l]{\emph{BSD500\footnotemark}\\~~Segmentation Challenge} & $321\times481$, 2696 images & Manual & \makecell[l]{110 / 187 MB/s} & 1188x \textbf{*}\\
\makecell[l]{\emph{PASCAL VOC\footnotemark}\\~~2012 Challenge } & Varying, 2913 images & Manual & \makecell[l]{146 / 222 MB/s} & 2217x \textbf{*}\\
\bottomrule
\end{tabular}
}
\label{tab:datasets}
\end{minipage}
\end{table}
\addtocounter{footnote}{-8} %3=n
\stepcounter{footnote}\footnotetext{\scriptsize{AC3+AC4 Subvolumes: \url{http://openconnecto.me/catmaid/?dataview=13}}}
\stepcounter{footnote}\footnotetext{\scriptsize{L. Cylinder: \url{https://software.rc.fas.harvard.edu/lichtman/vast/}}}
\stepcounter{footnote}\footnotetext{\scriptsize{CREMI A+B+C: \url{http://www.cremi.org}}}
\stepcounter{footnote}\footnotetext{\scriptsize{SPL Brain Atlas: \url{http://www.spl.harvard.edu/publications/item/view/2037}}}
\stepcounter{footnote}\footnotetext{\scriptsize{SPL Knee Atlas: \url{http://www.spl.harvard.edu/publications/item/view/1953}}}
\stepcounter{footnote}\footnotetext{\scriptsize{SPL Abdominal Atlas: \url{http://www.spl.harvard.edu/publications/item/view/1918}}}
\stepcounter{footnote}\footnotetext{\scriptsize{BSD500: \url{https://www.eecs.berkeley.edu/Research/Projects/CS/vision/grouping/resources.html}}}
\stepcounter{footnote}\footnotetext{\scriptsize{VOC2012: \url{http://host.robots.ox.ac.uk/pascal/VOC/voc2012/}}}

%\stepcounter{footnote}\footnotetext{\scriptsize{FreeSurfer is available at \url{https://surfer.nmr.mgh.harvard.edu/}.}}

\begin{figure}[h]
	\begin{center}
		\includegraphics[width=0.5\textwidth]{gfx/LCylinder+ac3+ac4+cremiA+cremiB+cremiC_rhoana_compression_ratios.pdf}%
		\includegraphics[width=0.5\textwidth]{gfx/VOC+mri1+mri2+mri3+BSD_gold_compression_ratios.pdf}%
		\caption{Compression ratios of general-purpose compression methods combined with \appName and Neuroglancer. % on all connectomics datasets (left) and on the other datasets (right).
%		the average on the remaining five connectomics datasets (right).
		\appName paired with LZMA yields the best compression ratios for all connectomics datasets and in average (four out of five) for the others.}
		\label{fig:compression_ratios}
	\end{center}
	\vspace{-18pt}
\end{figure}

%\vspace{-0.2cm}

\noindent of our requirement of lossless compression. It performs better when information loss is tolerated, however, even then it does not surpass the more specialized encoding schemes. These observations also hold for JPEG2000 and PNG. \appName with LZMA outperforms all other existing methods on connectomics datasets by 80\%.

The fundamental principles guiding \appName are valid for a diverse set of segmentation datasets (Fig.~\ref{fig:compression_ratios}, right). We evaluate the performance of our compression scheme on three MRI and two image segmentation datasets to demonstrate additional potential use cases. \appName followed by LZMA compresses the MRI datasets reasonably well, particularly on the SPL Knee Atlas which contains highly redundant boundary segments.
%\appName followed by LZMA compresses the SPL Brain Atlas data by nearly a factor of 640x. 
The Berkeley Segmentation and PASCAL Visual Object Class datasets are two very common benchmarks in image segmentation~\cite{MartinFTM01,pascal-voc-2012}. Currently these datasets use GZIP and PNG compression but \appName with LZMA can improve on them by a factor of over 10x and 5x respectively.

In terms of speed, \appName is on par with Neuroglancer across all datasets and achieves throughput of 112.16 megabytes per second ($SD = 18.62$ MB/s) for compression and 222.85 megabytes per second ($SD = 32.14$ MB/s) for decompression. All experiments ran on a single core of a Intel Xeon 2.3GHz CPU.

%Compared to all other methods, X.264 performs surprisingly poor on these datasets. Our requirement of lossless compression prevents this method from eliminating high frequencies between successive frames. We found that the video compression performs much better when information loss is tolerated. However, even then, the technique does not surpass the specialized encoding schemes discussed. These observations are also valid for JPEG2000 and PNG because of similar data assumptions.
 %The decompression speed for \appName was worse than the other encoding algorithms. However, there is significant room for optimization.

### 2018-04-27 papers/miccai2017/sections/introduction.tex
papers: added final version of compresso

\section{Introduction} \label{sec:i}

Connectomics---reconstructing the wiring diagram of a mammalian brain at nanometer resolution---results in datasets at the scale of petabytes~\cite{suissapeleg2016,haehn_dojo_2014}. Machine learning methods find cell membranes and create cell body labelings for every neuron~\cite{ronneberger2015u,liu2014modular,GALA2014} (Fig.~\ref{fig:data}).
%aims to reconstruct the wiring diagram of a mammalian brain at nanometer resolution. This results in datasets at the scale of petabytes~\cite{suissapeleg2016}. 
%These shear amounts of data require sophisticated methods of compression to enable efficient storage and transfer. 
These segmentations are stored as label volumes that are typically encoded in 32 bits or 64 bits per voxel to support labeling of millions of different nerve cells (neurons).  Storing such data is expensive and transferring the data is slow. To cut costs and delays, we need compression methods to reduce data sizes.

%Our work stems from a collaboration between computer scientists and neuroscientists in the field of connectomics. 
%Connectomics aims to reconstruct the wiring diagram of a mammalian brain at nanometer resolution, comprising millions of nerve cells (neurons) and their interconnections. 
%By deciphering this vast network and analyzing its underlying properties, scientists hope to better understand mental illnesses, learning disorders, and neural pathologies.

\begin{figure}[h]
	\begin{center}
		\includegraphics[width=0.38\textwidth]{gfx/ac3.png}%
		\hspace{0.12\textwidth}
		\includegraphics[width=0.38\textwidth]{gfx/cyl.png}%
	\end{center}
\caption{Examples of connectomics segmentation data with a different color per cell.}
\label{fig:data}
\end{figure}

%To analyze neuronal connectivity at the level of individual connections of neurons, we acquire and process high-resolution electron microscopy (EM) image stacks. 
%Recent progress in automatic sample preparation and EM acquisition techniques increases these datasets to petabytes in size~\cite{suissapeleg2016}.
%Machine learning methods find cell membranes and create cell body labelings for every neuron~\cite{ronneberger2015u,liu2014modular,GALA2014} (Fig.~\ref{fig:data}). 
%These segmentations are stored as label volumes, which are typically encoded in 32 bits or 64 bits per voxel to support millions of unique labels. 
%Storing such data is costly, and transferring the data is slow. To cut costs and delays, we need compression methods to reduce data sizes.

%One approach to allow data analysis of these volumes is to pre-process the segmentation data and store it uncompressed as a tiled quadtree data structure on a network filesystem.
%Researchers then access the segmentation data with thin clients, e.g., web-based applications like Dojo~\cite{haehn_dojo_2014}.
%The quadtree structure represents different pre-computed zoom levels of the data and enables loading and exploration of downsampled images.
%This scenario imposes three problems: offline storage, data transmission, and random access.
%Currently, the complete dataset is stored on disk and only a subset is transferred depending on individual use cases. This works well; however, recent progress in automatic sample preparation and EM acquisition techniques increases connectomics data to terabytes in size~\cite{RonnebergerFB15,GALA2014}. Storage and transmission of such massive datasets is hard and expensive, and access can be slow. Therefore, we need compression methods to reduce data sizes.

The literature currently lacks efficient compression of label volumes. 
General-purpose compression schemes~\cite{deutsch1996zlib,ziv1978compression,lehmann2016liblzf,oberhumer2005lzo,welch1984technique,seward1998bzip2,pavlov2007lzma,vandevenne2016zopfli,google2016brotli,collet2016smaller} are not optimized for this data.
In this paper, we exploit the typical characteristics of label volumes such as large invariant regions without natural relationship between label values. 
These properties render 2D image compression schemes inadequate since they rely on frequency reduction (using e.g., wavelet or discrete cosine transform) and value prediction of pixels based on local context (differential pulse-code modulation)~\cite{roelofs1999png,skodras2001jpeg}. 
Color space optimization strategies in video codecs~\cite{aimar2005x264} also have no effect on label volumes, even though the spatial properties of a segmentation stack (\textit{z}-axis) are similar to the temporal properties of video data (time-axis). 
A compression scheme designed specifically for label volumes is part of the visualization software Neuroglancer~\cite{google2016compressed}. 
This method exploits segmentation homogeneity by creating small blocks with $N$ labels and reducing local entropy to $\log_2{N}$ per pixel. 
Lookup tables then decode the values $[0,N)$ to the original 64-bit labels. We compare the Neuroglancer scheme with our method.
%The most relevant current compression tool is Neuroglancer~\cite{google2016compressed}---a web-based 3D segmentation viewer that provides a compression scheme for segmentation data.
%
%The assumption behind this scheme is that, on average, small local areas will contain very few unique labels with high probability. Based on this assumption, Neuroglancer divides the segmentation data into several small blocks. Pixels inside a block with $N$ distinct labels only require $\log_2{N}$ bits of information to encode.
%
%A lookup table for each block maps the values $[0, N)$ to the original 64-bit label. We compare the performance of Neuroglancer with our scheme in Sec.~\ref{sec:results}.
%
%A compression scheme for labeled volumes is part of the 3D segmentation viewer Neuroglancer~\cite{google2016compressed}. This method exploits segmentation homogeneity by creating small blocks with $N$ labels, reducing entropy to $\log_2{N}$. Lookup tables map the values $[0,N)$ to the original 64-bit labels. We compare the performance of Neuroglancer with our scheme in Sec.~\ref{sec:results}.
%
%and therefor reduces the
%to exploit homogeneity
%
%The most relevant current compression is

We explore the lossless compression of gigavoxel neuron segmentation volumes with high bit-encodings. 
We study and evaluate the performance of existing lossless compression methods, and their combinations, on multiple connectomics, magnetic resonance imaging (MRI) and general segmentation datasets.
As our main contribution, we present \appName---a novel compression method designed for label volumes using windowed feature extraction. 
\appName yields compression ratios on label volumes 80\% higher than the current best tools (Sec.~\ref{sec:results}).
We release an open-source C++ implementation of our method including a Python interface.

### 2018-04-27 papers/miccai2017/sections/methods.tex
papers: added final version of compresso

\section{The \appName Scheme} \label{sec:m}

\subsection{Encoding}

\paragraph{Overview.}

Segmentation datasets contain two important pieces of information across the image stack: per-segment shape and per-pixel label. 
Decoupling these two components allows for better compression on each.

\paragraph{Boundary Encoding.}
\label{sec:boundary-map}

To encode the segment shapes, we consider the boundary pixels between two segments. 
Removing the per-pixel labels, we produce a boundary map for each slice where a pixel $(x, y, z)$ is 1 if either pixel at $(x + 1, y, z)$ or $(x, y + 1, z)$ belongs to a different segment. 
The boundary map is divided into non-overlapping congruent 3D windows. If there are $n$ pixels per window, each window $w$ is assigned an integer $V_w \in [0, 2^n)$ where $V_w$ is defined as:

\begin{equation}
V_w = \sum_{i = 0}^{n - 1} \mathbb{I}(i) 2^i,
\end{equation}

\noindent
and $\mathbb{I}(i)$ is 1 if pixel $i$ is on a boundary and 0 otherwise. 
Figure~\ref{fig:bockwurst-encoding} shows an example segmentation with a window size of $4 \times 4 \times 1$.

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.7\textwidth]{gfx/encoding_diagram_opt.pdf}
  \end{center}
  \caption{A $4 \times 4 \times 1$ pixel window where three unique labels meet (left). The boundary map for the same window, where dark pixels represent the boundary (center). This window has an encoded value of 50,978 $(2^1 + 2^5 + 2^8 + 2^9 + 2^{10} + 2^{14} + 2^{15})$. A boundary pixel $i$ that is indeterminate and requires additional decoding information (right).}
  \label{fig:bockwurst-encoding}
\end{figure}

A priori, each window could take any of $2^n$ distinct values, and therefore require $n$ bits to encode without further manipulation. 
However, boundaries in segmentation images are not random, and many of these values never appear. 
Indeed, we find that a small subset of high-frequency $V_w$ values accounts for most windows, allowing for significant compression. 
Figure~\ref{fig:bockwurst-frequency} shows the 100 most common windows for a representative connectomics dataset. 
These 100 frequently occurring windows account for approximately 82\% of the over 1.2 million $V_w$ values in this dataset.
Nearly all of these windows correspond to simple lines traversing through the window. 
For contrast, we also provide 5 randomly generated windows that never occur in the dataset.

We define $N$ as the number of distinct $V_w$ representing all of the windows in an image stack. 
We construct an invertible function $f(V_w) \to [0, N)$ to transform the window values into a smaller set of integers. 
For all real-world segmentations $N \ll 2^n$; however, we assume no constraint on $N$ in order to guarantee lossless compression. 
With this function, each $V_w$ requires $\log_2{N}$ bits of information to encode. 
This is fewer than the initial number of bits so long as $N \leq 2^{n - 1}$.  
We create two arrays that store the per-segment shape encoding: $\texttt{WindowValues[]}$ contains the value $f(V_w)$ for every window $w$ and $\texttt{ValueMapping[]}$ contains the reverse mapping from $[0, N) \to [0, 2^n)$ based on the function $f$. 
Long sequences of $0$s in $\texttt{WindowValues[]}$ are reduced using run-length encoding.
%\vspace{-1mm}
\paragraph{Per-Pixel Label Compression.}

So far we have focused exclusively on transforming the boundary map of an image segmentation. 
However, the per-pixel labels themselves are equally important. 
The boundary map divides each image slice into different segments. 
By design, all pixels in the same segment have the same label so we store only one label per segment for each slice. 
We use a connected-component labeling algorithm to store one label per segment \cite{he2009fast}. 
The algorithm labels all pixels clustered within a component $m$ from $M$ section labels.
We store the original label for a segment $m$ in slice $z$ in $\texttt{Labels}_z\texttt{[m]}$. 
We concatenate these arrays for every image slice to create a variable $\texttt{Labels[]}$.
%\vspace{-1mm}
\paragraph{Exceptions.}

\begin{figure}
  \begin{center}
    \begin{minipage}{.8\linewidth}
      \includegraphics[width=\linewidth]{./gfx/window_values.pdf}
    \end{minipage}
  \end{center}
  \caption{The 100 most frequent windows accounting for approximately 82\% of the over 1.2 million $V_w$ values on a representative connectomics dataset contrasted with 5 randomly generated windows. Each box represents an 8 x 8 x 1 window where black pixels are boundary and white pixels are non-boundary.}
  \label{fig:bockwurst-frequency}
\end{figure}

Thus far, we have assumed the boundaries described in Section~\ref{sec:boundary-map} provide enough information to reconstruct the entire segmentation.
Pixels not on a segment boundary are easily relabeled using the $\texttt{Labels[]}$ array. 
However, more care is needed for pixels on the segment boundaries. 
Consider Figure~\ref{fig:bockwurst-encoding}, which depicts a difficult boundary to decode. 
If a boundary pixel has a non-boundary neighbor to the left or above, then that pixel merely takes on the value of that neighbor. 
However, the pixel $i$ requires more care since its relevant neighbors are both boundary pixels. 
If a non-boundary neighbor pixel shares a label with the undetermined pixel, we add the offset to that neighbor to an array \texttt{IndeterminateValues[]}. 
Otherwise we add that per-pixel label.
%\vspace{-1mm}
\paragraph{Metadata.}

We construct a data structure containing the two per-segment shape and two per-pixel label arrays. The last component of the data structure is the \texttt{Header}, which contains the dimensions of the original data, the window size, and the size of the arrays. \appName could be improved by further compressing the individual components of the encoding (e.g., Huffman encoding the $V_w$ values). We achieve strong overall compression by using a second-stage general compression scheme such as LZMA~(Sec.~\ref{sec:results}).

\subsection{Decoding}

The first step in decoding the data is to reconstruct the boundary map. We iterate over every pixel, determine the corresponding window $w$, and retrieve the encoded window value $f(V_w)$ from the $\texttt{WindowValues[]}$ array. These values range from $0$ to $N - 1$ and correspond to an index in $\texttt{ValueMapping[]}$ that contains the original $V_w$ value. After decoding $V_w$, the value of pixel $i$ in window $w$ equals $V_w \land 2^i$.

After reproducing the boundary map, we execute the same deterministic connected-components algorithm per slice as when encoding. Each component in the boundary map receives a label between $0$ and $M - 1$. Using the $\texttt{Labels[]}$ array, we can easily translate these component labels into the original per-pixel labels for every slice. To determine the per-pixel labels for every boundary pixel, we iterate over the entire dataset in raster order. Any boundary pixel $(x, y, z)$ with a non-boundary neighbor at $(x - 1, y, z)$ or $(x, y - 1, z)$ shares the same per-pixel label. If both relevant neighbors are boundaries we consider the next unused value in the $\texttt{IndeterminateValues[]}$ array and update this pixel's label.

\subsection{Complexity}

In what follows, $P$ is the number of input pixels; $N$ is the number of distinct window values; $X$, $Y$ and $Z$ are the size of the $x$, $y$, and $z$ dimensions of the input data;  and $\alpha$ is the inverse Ackermann function~\cite{fredman1989cell}.
%\vspace{-5mm}
\paragraph{Encoding.}

Extracting the boundaries from the segmentation, generating the $V_w$ values, and populating the $\texttt{IndeterminateValues[]}$ array are all linear work in $P$. The $N$ unique window values are sorted to create the $\texttt{ValueMapping}$ variable. Generating the $\texttt{Labels[]}$ array requires running a connected-component labeling algorithm over each $z$ slice; we use a union-find data structure with union by rank and path compression optimizations.  The overall complexity of the compression scheme is therefore $O\left({P(1 + \alpha(XY)) + N\log{N}}\right)$.
%\vspace{-5mm}
\paragraph{Decoding.}

Decoding the window values, reconstructing the boundary map, and applying the correct per-pixel labels for all boundary pixels using the array \texttt{IndeterminateValues[]} are all linear work in $P$.  Reconstructing the per-pixel labels requires running the connected-component labeling algorithm over every image slice. The overall complexity of the decompression scheme is therefore $O\left({P(1 + \alpha(XY))}\right)$.

%\subsection{Complexity}
%
%\paragraph{Encoding.}
%
%Extracting the boundaries from the segmentation and generating the $V_w$ values is linear in the number of input pixels $P$. The $N$ unique window values are sorted to create the $\texttt{ValueMapping}$ variable. Generating the $\texttt{IDs}$ array requires running a connected-component labeling algorithm over each $z$ slice. The algorithm uses a union-find data structure with union by rank and path compression optimizations. Populating the $\texttt{IndeterminateValues}$ array is linear in the number of pixels. With $X$, $Y$ and $Z$ as the size of the $x$, $y$, and $z$ dimensions of the input data, $N$ as the number of unique window values, and $P$ as the number of pixels, the complexity of the compression scheme is $O\left({P(1 + \alpha(XY)) + N\log{N}}\right)$, where $\alpha$ is the inverse Ackermann function\cite{Fredman:1989:CPC:73007.73040}.
%
%\paragraph{Decoding.}
%
%Decoding the window values and reconstructing the boundary map is linear in the number of input pixels $P$. Reconstructing the per-pixel labels requires running the connected-component labeling algorithm over every image slice. Applying the correct per-pixel labels for all boundary pixels using $\texttt{IndeterminateValues}$ is linear in the number of input pixels. With $X$ and $Y$ as the size of the $x$ and $y$ dimensions, and $P$ as the number of pixels, the complexity of the decompression scheme is $O\left({P(1 + \alpha(XY))}\right)$.

### 2018-04-27 papers/miccai2017/sections/related-work.tex
papers: added final version of compresso

\section{Related Work} \label{sec:rl}
%
%\paragraph{Data Storage.}
%For data storage we are mostly interested in compression tools with compression rates.
%There are many studies~\cite{alakuijala2015comparison,squash2016squash,mahoney2016large,lzturbo2016lzturbo,turbobench2016turbobench} evaluating general compression tools in regards to their compression rate, compression speed, and decompression speed.
%Classic encoders are zlib~\cite{deutsch1996zlib} (which utilizes LZ77~\cite{ziv1977universal}, LZ78~\cite{ziv1978compression}, LZF~\cite{lehmann2016liblzf}, LZO~\cite{oberhumer2005lzo}, LZW~\cite{welch1984technique}, and Huffmann codes~\cite{huffman1952method}), bzip2 (using run-length encoding, the Burrows-Wheeler transformation~\cite{burrows1994block}, move-to-front encoding, and delta encoding), and LZMA; LZMA is usually reported to provide best compression rates.
%
%\paragraph{Data Transmission.}
%
%Since major browsers natively support Zlib-based decompression, this method is predominantly used for concise data transmission from server to client. All major 
%
%Generally, there are two important aspects for data transmission: the size of the data being transferred and the time it takes to decompress that data.
%
%The first aspected is important as outwards traffic is expensive while the second aspect takes the overall response time into account.
%Zopfli~\cite{vandevenne2016zopfli} provides zlib compatible data streams with a slightly higher compression rate at the expense of a dramatically increased compression time.
%Another tool, recently published by Google, is Brotli~\cite{google2016brotli}---an LZ77-based compression tools that provides comparable compression rates to bzip2 at slow compression speed but high decompression speed.
%Finally, Facebook released Zstandard~\cite{collet2016smaller}, which claims to provide faster speeds and higher ratios.

\paragraph{General-purpose Compression.} Compression tools are well studied and compared in regards to their compression rate, compression speed, and decompression speed~\cite{alakuijala2015comparison,squash2016squash,mahoney2016large,lzturbo2016lzturbo,turbobench2016turbobench}. Classic encoders are zlib~\cite{deutsch1996zlib} (which utilizes LZ77~\cite{ziv1977universal} and Huffmann codes~\cite{huffman1952method}), LZ78~\cite{ziv1978compression}, LZF~\cite{lehmann2016liblzf}, LZO~\cite{oberhumer2005lzo}, LZW~\cite{welch1984technique}, bzip2~\cite{alakuijala2015comparison},
% (using run-length encoding, the Burrows-Wheeler transformation~\cite{burrows1994block}, move-to-front encoding, and delta encoding), 
and LZMA; LZMA is usually reported to provide very high compression rates.% which we observe also in our experiments. 
Recent efforts to optimize these approaches include Zopfli~\cite{vandevenne2016zopfli}, Brotli~\cite{google2016brotli}, and Zstandard~\cite{collet2016smaller}.

% Several efforts tried to optimize these approaches, such as Zopfli~\cite{vandevenne2016zopfli}, which provides zlib compatible data streams with a slightly higher compression rate at the expense of an increased compression time. Another optimization, recently published by Google, is Brotli~\cite{google2016brotli}---an LZ77-based compression tools that provides comparable compression rates to bzip2 with high decompression speed. Finally, Facebook released Zstandard~\cite{collet2016smaller}, which claims to provide faster speeds and higher ratios.

All general-purpose methods are targeted towards handling any kind of data and we evaluate a variety on our datasets, resulting in compression without exploiting the typical characteristics of segmentation data. In addition, some methods are not able to handle the size of our datasets (Sec. \ref{sec:results}).

\paragraph{Image Compression.}
Many compression schemes for 2D images exist. The two most prominent lossless compression methods are PNG and JPEG2000 --- optimized for photographs. These techniques rely on frequency reduction (using e.g., wavelet or discrete cosine transform) and value prediction of images based on local context (differential pulse-code modulation). In contrast to photographs, segmentation data consists of large invariant regions and no natural relationship between their identifiers.

The typical frequency reductions and value predictions can not be applied to segmentation data. Therefore, off-the-shelf image compression techniques are not optimized and provide lower compression ratios. We still include PNG and JPEG2000 for evaluation.

\paragraph{Video Compression.} 
The \textit{z}-axis of a segmentation stack can be mapped to the time axis of video data. This relates video compression to segmentation compression. In practice, the change between slices in connectomics segmentation data is limited given natural constraints of the shape of cell bodies and restrictions in between-slice resolution. 
%There is a variety of different lossless compression tools for videos.

The currently most widespread video compression is x264 which provides lossless encoding when quantization is disabled. Intuitively, this does not yield the best performance on segmentation data, since any possible color space optimization is not applicable. 
Nevertheless, we include x264 for evaluation in Sec.~\ref{sec:results}.

\paragraph{Neuroglancer.} 
% \subsection{Neuroglancer} \label{sec:rl:neuroglancer}
The closest current compression tool is Neuroglancer~\cite{google2016compressed}---a web-based 3D segmentation viewer that provides a compression scheme for segmentation data. 
The assumption behind the compression scheme is that, on average, small local areas will contain very few distinct segment identifiers with high probability. 
Based on this assumption, Neuroglancer divides the segmentation data into several small blocks. 
Consider an arbitrary block $b$ with $N$ distinct segment identifiers.
Neuroglancer maps the identifier for each pixel into $[0, N)$ and stores a lookup table for $[0, N)$ to the original value. 
This reduces the number of bits needed to encode a pixel in a given block to $\log_2{N}$. 
The lookup table requires $64 * N$ bits of information to reconstruct the original data. 
In order to allow random access, Neuroglancer creates a header that stores the byte offset to the lookup table and encoded values for each block.
We compare the performance of Neuroglancer with our scheme in Sec. \ref{sec:results}.

### 2018-04-27 papers/quals2018/0_introduction.tex
updated proposal

\section{Introduction}

The field of connectomics is concerned with the reconstruction of the wiring diagram of the mammalian brain.
In order to achieve this ambitious goal, we need images at nanometer resolution to see the structure of the neurons and the synaptic connections between them.
Recent advances in electron microscopy acquisition techniques enable a throughput of a terabyte of image data every hour~\cite{richard2016imaging}.
Manual reconstruction of this image data is simply infeasible and requires automatic segmentation methods.
These automatic methods label every voxel of the image with a 64-bit integer value where two voxels have the same label only if they belong to the same neuron.
As the field progresses, our goal is to reconstruct a cubic millimeter of brain which will result in over 18 petabytes of segmentation data alone~\cite{suissa2016automatic}.

Three major challenges arise as the image datasets scale to a petabyte and more. 
First, the segmentation methods must be accurate enough to extract the proper connections between neurons.
In particular, the dendritic spines \TODO{check,CITE} which contain the postsynaptic density can be only \TODO{XX} nanometers thick.
Second, automatic segmentation must be fast -- ideally matching the throughput of the electron microscope~\cite{haehn2017scalable}.
The current state-of-the-art automatic reconstruction pipelines are either too slow for such large datasets or too inaccurate at scale.
Third, the label volumes require $8\times$ the number of bytes as the already massive image volumes.
Storing such data is expensive and transferring the data is slow. 
To cut costs and delays, we need compression methods to reduce data sizes.

### 2018-04-27 papers/quals2018/1_related_work.tex
updated proposal

@@
-% !TEX root =  paper.tex
+\section{Related Work}
 
-\section{Related Work}
-% \begin{figure}[t]
-%  	\subfloat[]{
-%  		\includegraphics[width=.47\linewidth]{figures/schema/pre-multicut-with-arrows.pdf}
-%  	}
-%  	\subfloat[]{
-%  		\includegraphics[width=.47\linewidth]{figures/schema/post-multicut.png}
-%  	}
-%  	\caption{Example improvement of neural reconstruction.
-(a) We extract 3D skeletons from pixel-based segmentation algorithms to create a graph representation.
-Red arrows highlight errors in the input segmentation.
-(b) We improve the segmentation accuracy using a graph partitioning algorithm, leveraging both local and global information.}
-%  	\label{fig:improved-reconstruction}
-% \end{figure}
-%\\~\\
-\noindent\textbf{Pixel-Based Segmentation}
-%\subsubsection{Pixel-Based Segmentation}
+\paragraph{Automatic Segmentation.}
 A significant amount of connectomics research considers the problem of extracting segmentation information at the voxel level of EM images.
 First, intermediate representations like boundary, affinity or binary segmentation maps are generated from the voxels.
-Random forests with hand-designed features~\cite{kaynig2015large}, or 2D and 3D convolutional networks produce boundary probabilities.
-~\cite{seymour2016rhoananet,ronneberger2015u,bogovic2013learned,ciresan2012deep,jain2010boundary,amelio_segmentation}.
+Random forests with hand-designed features~\cite{kaynig2015large}, or 2D and 3D convolutional networks produce boundary probabilities~\cite{seymour2016rhoananet,ronneberger2015u,bogovic2013learned,ciresan2012deep,jain2010boundary,amelio_segmentation}.
 Often, the affinity between each voxel and its six neighbors are used~\cite{lee2015recursive,parag2017anisotropic,lee2017superhuman,cciccek20163d,turaga2010convolutional}. 
@@
 Often a watershed algorithm will then cluster these pixels into super-pixels~\cite{zlateski2015image}.
-\\~\\
-\noindent\textbf{Region Merging}
-%\subsubsection{Region Merging}
+
 Region merging methods can be categorized by the similarity metric between adjacent segments and the merging strategy.
@@
 present a scalable multicut algorithm to partition superpixels with global optimization~\cite{beier2017multicut}.
-\\~\\
-\noindent\textbf{Error-correction Methods}
+
 Additional research builds on top of these region-based methods to correct errors in the segmentation.
@@
 Our method can be used as input to any existing error correction framework.
-% Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for traditional image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}.
 
-% Even though graph partitioning is an NP-Hard problem~\cite{demaine2006correlation} there are several useful multicut heuristics that provide good approximations with reasonable computational costs~\cite{horvnakova2017analysis}.
-%We extract a 3D graph from an input segmentation for a true top-down error correction approach. 
-%This allows us to enforce domain-specific biological constraints while using graph partitioning algorithms. 
-%We use the method of Keuper et al.~\cite{keuper2015efficient} to partition the extracted graph into the final neural reconstruction.
+\paragraph{Compression.}
 
-%\subsubsection{Error-correction methods}
-%Additional research builds on top of these region-based methods to correct errors in the segmentation either using human proofreading~\cite{haehn2014design,haehn2017guided,mojo2} or automatic methods~\cite{rolnick2017morphological,error_correction_using_CNN}.
-%However, to our knowledge, our method is the first to extract a 3D graph from an input segmentation for a true top-down\TODO{?} error correction approach. 
-%This allows us to enforce domain-specific biology constraints and use efficient graph partitioning algorithms. 
-% Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for traditional image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}.
-% Even though graph partitioning is an NP-Hard problem~\cite{demaine2006correlation} there are several useful multicut heuristics that provide good approximations with reasonable computational costs~\cite{horvnakova2017analysis}.
-%We use the method of Keuper et al.~\cite{keuper2015efficient} to partition the extracted graph into the final neural reconstruction.
+The literature currently lacks efficient compression of label volumes. 
+General-purpose compression schemes~\cite{deutsch1996zlib,ziv1978compression,lehmann2016liblzf,oberhumer2005lzo,welch1984technique,seward1998bzip2,pavlov2007lzma,vandevenne2016zopfli,google2016brotli,collet2016smaller} are not optimized for this data.
+In this paper, we exploit the typical characteristics of label volumes such as large invariant regions without natural relationship between label values. 
+These properties render 2D image compression schemes inadequate since they rely on frequency reduction (using e.g., wavelet or discrete cosine transform) and value prediction of pixels based on local context (differential pulse-code modulation)~\cite{roelofs1999png,skodras2001jpeg}.
+Color space optimization strategies in video codecs~\cite{aimar2005x264} also have no effect on label volumes, even though the spatial properties of a segmentation stack (\textit{z}-axis) are similar to the temporal properties of video data (time-axis).
+A compression scheme designed specifically for label volumes is part of the visualization software Neuroglancer~\cite{google2016compressed}. 
+This method exploits segmentation homogeneity by creating small blocks with $N$ labels and reducing local entropy to $\log_2{N}$ per pixel. 
+Lookup tables then decode the values $[0,N)$ to the original 64-bit labels. We compare the Neuroglancer scheme with our method.

### 2018-04-27 papers/quals2018/2_method.tex
updated proposal

--- 2018-03-19 papers/eccv2018/2_method.tex
@@
-% !TEX root =  paper.tex
+\section{Preliminary Methods}
+\begin{figure}[t!]
+	\centering
+	\includegraphics[width=\linewidth]{./figures/teaser_v4.png}
+	\caption{Our framework uses both geometric and topological biological constraints for region merging.
+We (a) generate a simplified graph from the skeleton representation of the input segmentation, (b) train a classifier to learn the edge weight based on the shape of the segment connection, and (c) perform graph partitioning with acyclic constraints.}
+	\label{fig:teaser_pipeline}
+\end{figure}
 
-\section{Method}
-%\begin{figure*}[t!]
-%	\begin{center}
-%		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/multicut_input.png}}
-%		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/pre-multicut.png}}
-% 		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/multicut-graph.png}}
-% 		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/post-multicut.png}}
-% 	\end{center}
-% 	\caption{Outline of our approach, from left to right: result of the pixel-based segmentation and agglomeration algorithm; segments of several neurons from the initial segmentation; extracted skeletonized network of those segments; improved 3D reconstruction of the selected segments after graph construction and partitioning with constraints.}
-% 	\label{fig:overview}
-% \end{figure*}
-
-%There are two types of errors that can occur in connectomics segmentations: \textit{split errors} and \textit{merge errors}. 
-%In a split error, two segments should have been merged into one neuronal process (Fig.~\ref{fig:improved-reconstruction}). 
-%In a merge error, one segment corresponds to more than one neuron.
-%Generally, it is much more difficult to correct merge errors than to correct split errors, as the space of possible split proposals grows quickly~\cite{parag2015properties}.
-%Thus, most reconstruction approaches are tuned towards over-segmentation with many more split than merge errors. 
-%The input of our method is the over-segmentation of EM image volumes from state-of-the-art pipelines.
+\paragraph{Biologically-Constrained Error Correction}
 
@@
 We use a skeleton representation of the segmentation to reduce the graph size with the geometric constraints on the connectivity of two adjacent segments to prune edges.
-% a bit trivial, as everyone is doing this. maybe no need to mention
-% \subsubsection{Node Pruning}
-% %The simplest node generation strategy creates one node for every unique segment label in the input volume. 
-% Some labels in the volume correspond to very small structures that are likely the result of segmentation errors, typically in regions with noisy raw image data. 
-% It is difficult to extract useful shape features from these segments because of their small, often random, shape. 
-% We prune these nodes from the graph by removing all segments with fewer than a empirical threshold $t_{seg} = 20,000$ voxels. 
-% This removes on average \TODO{XX}\% of the segments in our  datasets (Sec.~\ref{sec:dataset}), leaving us with around $\TODO{XX}$ nodes per dataset (\TODO{X nodes per micrometer}). 
-% Despite the large number of segments, these regions only take up \TODO{XX}\% of the total volume on average.
-
-% \subsubsection{Edge Pruning}
 
@@
 
-%A typical approach for generating edges produces one between all adjacent segments. 
-%Two segments $l_1$ and $l_2$ are considered adjacent if there is a pair of adjacent voxels with one labeled $l_1$ and the other labeled $l_2$.
-%For example, pixel-based agglomeration methods such as mean agglomeration~\cite{lee2017superhuman} or waterz~\cite{funke2017deep} consider all pairs of adjacent segments for merging.
-%However, this method produces too many edges in the graph for graph-based optimization approaches. 
 Our key observation is that if two segments belong to the same neuronal process, their skeleton end points should satisfy certain geometric constraints.
@@
 This reduces the need for generating costly manually-labeled ground truth.
-
-%The first two max pooling layers are anisotropic with pooling only in the $x$ and $y$ dimensions. 
-%The output of this final pooling step is flattened into a 1D vector that is input into . 
-%The final layer produces probabilities with a sigmoid activation function~\cite{funahashi1989approximate}. 
-%All of the other activation functions are .
-
-% covered in the experiment
-%For training we use a stochastic gradient descent optimizer with Nesterov's accelerated gradient~\cite{nesterov1983method}. 
-%We employ dropouts of $0.2$ after every pooling layer and the first dense layer, and a dropout of $0.5$ after the final dense layer to prevent overfitting. 
-%We discuss all other network parameters in Sec.~\ref{sec:network-parameters}.
 
@@
 We ``collapse'' an edge only if it does not create a cycle in the graph.
+
+\paragraph{Compression}
+
+\begin{figure*}[t]
+	\begin{center}
+		\includegraphics[width=0.45\linewidth]{./figures/encoding_diagram_opt.pdf}
+		\hspace{0.08\linewidth}
+		\includegraphics[width=0.45\linewidth]{./figures/window_values.pdf}
+	\end{center}	
+	\caption{Compresso works by dividing up the segmentation data into small blocks.
+On the left we show the intersection of three segments in a $4\times4\times1$ window.
+We extract a boundary map from this segmentation to transform the window into an integral value between $0$ and $2^{16} - 1$.
+The location $i$ requires some additional bookkeeping.
+On the right are the $100$ most common $8 \times 8 \times 1$ windows accounting for $\sim82\%$ of the volume on a representative dataset.}
+	\label{fig:compression}
+\end{figure*}
+
+Segmentation datasets contain two important pieces of information across the image stack: per-segment shape and per-pixel label. 
+Decoupling these two components allows for better compression on each.
+
+\paragraph{Boundary Encoding.}
+\label{sec:boundary-map}
+
+To encode the segment shapes, we consider the boundary pixels between two segments. 
+Removing the per-pixel labels, we produce a boundary map for each slice where a pixel $(x, y, z)$ is 1 if either pixel at $(x + 1, y, z)$ or $(x, y + 1, z)$ belongs to a different segment. 
+The boundary map is divided into non-overlapping congruent 3D windows. If there are $n$ pixels per window, each window $w$ is assigned an integer $V_w \in [0, 2^n)$ where $V_w$ is defined as:
+
+\begin{equation}
+V_w = \sum_{i = 0}^{n - 1} \mathbb{I}(i) 2^i,
+\end{equation}
+
+\noindent
+and $\mathbb{I}(i)$ is 1 if pixel $i$ is on a boundary and 0 otherwise. 
+Figure~\ref{fig:bockwurst-encoding} shows an example segmentation with a window size of $4 \times 4 \times 1$.
+
+A priori, each window could take any of $2^n$ distinct values, and therefore require $n$ bits to encode without further manipulation. 
+However, boundaries in segmentation images are not random, and many of these values never appear. 
+Indeed, we find that a small subset of high-frequency $V_w$ values accounts for most windows, allowing for significant compression. 
+Figure~\ref{fig:bockwurst-frequency} shows the 100 most common windows for a representative connectomics dataset. 
+These 100 frequently occurring windows account for approximately 82\% of the over 1.2 million $V_w$ values in this dataset.
+Nearly all of these windows correspond to simple lines traversing through the window. 
+For contrast, we also provide 5 randomly generated windows that never occur in the dataset.
+
+We define $N$ as the number of distinct $V_w$ representing all of the windows in an image stack. 
+We construct an invertible function $f(V_w) \to [0, N)$ to transform the window values into a smaller set of integers. 
+For all real-world segmentations $N \ll 2^n$; however, we assume no constraint on $N$ in order to guarantee lossless compression. 
+With this function, each $V_w$ requires $\log_2{N}$ bits of information to encode. 
+This is fewer than the initial number of bits so long as $N \leq 2^{n - 1}$.  
+We create two arrays that store the per-segment shape encoding: $\texttt{WindowValues[]}$ contains the value $f(V_w)$ for every window $w$ and $\texttt{ValueMapping[]}$ contains the reverse mapping from $[0, N) \to [0, 2^n)$ based on the function $f$.
+Long sequences of $0$s in $\texttt{WindowValues[]}$ are reduced using run-length encoding.
+
+\paragraph{Per-Pixel Label Compression.}
+
+So far we have focused exclusively on transforming the boundary map of an image segmentation. 
+However, the per-pixel labels themselves are equally important. 
+The boundary map divides each image slice into different segments. 
+By design, all pixels in the same segment have the same label so we store only one label per segment for each slice. 
+We use a connected-component labeling algorithm to store one label per segment \cite{he2009fast}. 
+The algorithm labels all pixels clustered within a component $m$ from $M$ section labels.
+We store the original label for a segment $m$ in slice $z$ in $\texttt{Labels}_z\texttt{[m]}$. 
+We concatenate these arrays for every image slice to create a variable $\texttt{Labels[]}$.
+
+\paragraph{Exceptions.}
+
+Thus far, we have assumed the boundaries described in Section~\ref{sec:boundary-map} provide enough information to reconstruct the entire segmentation.
+Pixels not on a segment boundary are easily relabeled using the $\texttt{Labels[]}$ array. 
+However, more care is needed for pixels on the segment boundaries. 
+Consider Figure~\ref{fig:bockwurst-encoding}, which depicts a difficult boundary to decode. 
+If a boundary pixel has a non-boundary neighbor to the left or above, then that pixel merely takes on the value of that neighbor. 
+However, the pixel $i$ requires more care since its relevant neighbors are both boundary pixels. 
+If a non-boundary neighbor pixel shares a label with the undetermined pixel, we add the offset to that neighbor to an array \texttt{IndeterminateValues[]}. 
+Otherwise we add that per-pixel label.
+
+\paragraph{Metadata.}
+
+We construct a data structure containing the two per-segment shape and two per-pixel label arrays.
+The last component of the data structure is the \texttt{Header}, which contains the dimensions of the original data, the window size, and the size of the arrays.
+Compresso could be improved by further compressing the individual components of the encoding (e.g., Huffman encoding the $V_w$ values).
+We achieve strong overall compression by using a second-stage general compression scheme such as LZMA~(Sec.~\ref{sec:results}).
+
+\subsection{Decoding}
+
+The first step in decoding the data is to reconstruct the boundary map.
+We iterate over every pixel, determine the corresponding window $w$, and retrieve the encoded window value $f(V_w)$ from the $\texttt{WindowValues[]}$ array.
+These values range from $0$ to $N - 1$ and correspond to an index in $\texttt{ValueMapping[]}$ that contains the original $V_w$ value.
+After decoding $V_w$, the value of pixel $i$ in window $w$ equals $V_w \land 2^i$.
+
+After reproducing the boundary map, we execute the same deterministic connected-components algorithm per slice as when encoding.
+Each component in the boundary map receives a label between $0$ and $M - 1$.
+Using the $\texttt{Labels[]}$ array, we can easily translate these component labels into the original per-pixel labels for every slice.
+To determine the per-pixel labels for every boundary pixel, we iterate over the entire dataset in raster order.
+Any boundary pixel $(x, y, z)$ with a non-boundary neighbor at $(x - 1, y, z)$ or $(x, y - 1, z)$ shares the same per-pixel label.
+If both relevant neighbors are boundaries we consider the next unused value in the $\texttt{IndeterminateValues[]}$ array and update this pixel's label.

### 2018-05-01 papers/quals2018/0_introduction.tex
quals: added method and evaluation from eccv submission

@@
 
-The field of connectomics is concerned with the reconstruction of the wiring diagram of the mammalian brain.
-In order to achieve this ambitious goal, we need images at nanometer resolution to see the structure of the neurons and the synaptic connections between them.
-Recent advances in electron microscopy acquisition techniques enable a throughput of a terabyte of image data every hour~\cite{richard2016imaging}.
-Manual reconstruction of this image data is simply infeasible and requires automatic segmentation methods.
-These automatic methods label every voxel of the image with a 64-bit integer value where two voxels have the same label only if they belong to the same neuron.
-As the field progresses, our goal is to reconstruct a cubic millimeter of brain which will result in over 18 petabytes of segmentation data alone~\cite{suissa2016automatic}.
+One of the critical components of connectomics--the field concerned with reconstructing the wiring diagram of the brain at nanometer resolution--is automatic segmentation of electron microscopy (EM) images of the brain.
+With recent advances in EM acquisition techniques, neuroscientists can now generate a terabyte of EM image data every hour~\cite{richard2016imaging}.
+These images are typically anisotropic with $4$nm resolution in the $xy$ plane with $30-40$nm between slices. 
+At this resolution, we can see all of the axon terminals and dendritic spines, and the synaptic connections between them.
+Accurate reconstruction of every neuron paired with synapse detection will enable us create a true graphical representation of the brain and further our understanding of the underlying circuitry.
+These segmentation, or label, volumes assign an integer label to every voxel where voxels have the same label only if they belong to the same neuron.
 
-Three major challenges arise as the image datasets scale to a petabyte and more. 
-First, the segmentation methods must be accurate enough to extract the proper connections between neurons.
-In particular, the dendritic spines \TODO{check,CITE} which contain the postsynaptic density can be only \TODO{XX} nanometers thick.
-Second, automatic segmentation must be fast -- ideally matching the throughput of the electron microscope~\cite{haehn2017scalable}.
-The current state-of-the-art automatic reconstruction pipelines are either too slow for such large datasets or too inaccurate at scale.
-Third, the label volumes require $8\times$ the number of bytes as the already massive image volumes.
-Storing such data is expensive and transferring the data is slow. 
-To cut costs and delays, we need compression methods to reduce data sizes.
+The first complete reconstruction of animal brain occurred in the 1980s with an ambitious manual effort of the C. elegans worm\TODO{CITE}. 
+This species has \TODO{300} neurons and manual labeling required \TODO{13} years of intensive work.
+More recent research focuses on Drosophila flies~\cite{jovanic2016competitive}\TODO{CITE JANELIA}, rodents~\cite{richard2016imaging,suissa2016automatic}, and even humans\TODO{CITE}. 
+With an EM throughput of one terabyte per hour, neuroscientists can image a cubic millimeter of data (one petabyte) in six months. 
+At this scale, the manual reconstruction efforts of the 80s are simply infeasible.
+Thus, researchers have turned to the deep learning revolution to provide automatic solutions to the segmentation problem.
+
+Automatic reconstruction techniques need to be fast, scalable, and accurate.
+Ideally, image acquisition is the bottleneck of the connectomics pipeline which requires reconstruction efforts of a terabyte per hour~\cite{haehn2017scalable}.
+We can achieve this throughput with parallelization among several GPUs with fast reconstruction techniques~\cite{funke2017deep,parag2017anisotropic}.
+One of the issues with these automatic techniques is that they use only local context in decision making and are agnostic about the underlying biological system.
+Thus, these methods make errors at scale and currently require human proofreading and other bulky error correction techniques~\cite{haehn2017guided,error_correction_using_CNN}.
+
+We propose a novel region merging framework that takes as input and oversegmentation of an EM volume.
+Our method imposes both local and global biological constrains onto the output segmentation to more close match the underlying structure of neuronal processes.
+Additionally, our method is independent of image resolution and acquisition parameters, enabling its application to isotropic and anisotropic data without retraining.
+Images generated by electron microscopes often differ in appearance because of variations in staining techniques~\cite{briggman2012volume}.
+By removing the dependence of our algorithm on the input images, we greatly reduce the need for additional costly ground truth data for each new stack of images.

### 2018-05-01 papers/quals2018/1_related_work.tex
quals: added method and evaluation from eccv submission

@@
 
-\paragraph{Automatic Segmentation.}
+\begin{figure*}[t!]
+	\centering
+	\includegraphics[width=0.75\linewidth]{./figures/teaser_v4.png}
+	\caption{Our framework uses both geometric and topological biological constraints for region merging.
+We (a) generate a simplified graph from the skeleton representation of the input segmentation, (b) train a classifier to learn the edge weight based on the shape of the segment connection, and (c) perform graph partitioning with acyclic constraints.}
+	\label{fig:teaser_pipeline}
+\end{figure*}
+
 A significant amount of connectomics research considers the problem of extracting segmentation information at the voxel level of EM images.
@@
 and Funke et al.
-rely solely on the accuracy of the predicted affinities and define the metric as the mean affinity between segments~\cite{lee2017superhuman,funke2017deep}.
-Classification-based methods generate the probability to merge two segments from handcrafted~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image,10.1371/journal.pone.0125825,jain2011learning} and learned features~\cite{bogovic2013learned}.
-For the merging strategy, most methods use variants of hierarchical agglomeration ~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image,10.1371/journal.pone.0125825} to greedily merge a pair of regions at a time.
+rely solely on the accuracy of the predicted affinities and define the metric as the mean affinity between segments~\cite{funke2017deep,lee2017superhuman}.
+Classification-based methods generate the probability to merge two segments from handcrafted~\cite{jain2011learning,seymour2016rhoananet,nunez2014graph,10.1371/journal.pone.0125825,parag2017anisotropic,zlateski2015image} and learned features~\cite{bogovic2013learned}.
+For the merging strategy, most methods use variants of hierarchical agglomeration ~\cite{seymour2016rhoananet,nunez2014graph,10.1371/journal.pone.0125825,parag2017anisotropic,zlateski2015image} to greedily merge a pair of regions at a time.
 Jain et al.
@@
 Additional research builds on top of these region-based methods to correct errors in the segmentation.
-This can be done either using human proofreading~\cite{haehn2014design,haehn2017guided,mojo2} or automatically~\cite{rolnick2017morphological,error_correction_using_CNN}.
+This can be done either using human proofreading~\cite{haehn2017guided,haehn2014design,mojo2} or automatically~\cite{rolnick2017morphological,error_correction_using_CNN}.
 In both cases, available methods are pixel-based and do not include global biological constraints into the decision making process.
 Our method can be used as input to any existing error correction framework.
-
-\paragraph{Compression.}
-
-The literature currently lacks efficient compression of label volumes. 
-General-purpose compression schemes~\cite{deutsch1996zlib,ziv1978compression,lehmann2016liblzf,oberhumer2005lzo,welch1984technique,seward1998bzip2,pavlov2007lzma,vandevenne2016zopfli,google2016brotli,collet2016smaller} are not optimized for this data.
-In this paper, we exploit the typical characteristics of label volumes such as large invariant regions without natural relationship between label values. 
-These properties render 2D image compression schemes inadequate since they rely on frequency reduction (using e.g., wavelet or discrete cosine transform) and value prediction of pixels based on local context (differential pulse-code modulation)~\cite{roelofs1999png,skodras2001jpeg}.
-Color space optimization strategies in video codecs~\cite{aimar2005x264} also have no effect on label volumes, even though the spatial properties of a segmentation stack (\textit{z}-axis) are similar to the temporal properties of video data (time-axis).
-A compression scheme designed specifically for label volumes is part of the visualization software Neuroglancer~\cite{google2016compressed}. 
-This method exploits segmentation homogeneity by creating small blocks with $N$ labels and reducing local entropy to $\log_2{N}$ per pixel. 
-Lookup tables then decode the values $[0,N)$ to the original 64-bit labels. We compare the Neuroglancer scheme with our method.

### 2018-05-01 papers/quals2018/5_proposed.tex
quals: added method and evaluation from eccv submission

\section{Proposed Work}

There are significantly more biological constraints that we plan to use in the future.
Once we improve our synaptic classifiers, we can ensure that we do not merge dendritic spines with axons. 
By stipulating that a segment on one side of the cell body can only have either pre- or post-synaptic connections, we will prevent undersegmentation that merges multiple neurons together.
Additionally, once we have a classifier to label each neuron as inhibitory or excitatory, we can prevent the merging of two different types of neurons.
Both of these additional constraints will help with the current problem associated with large-scale reconstruction.
Namely, that a small percentage of merge errors results in a tangled mess of multiple neurons per segment.

To further prevent this problem, we will augment our work to correct split errors as well.
We will generate locations from splits with the following algorithm.
First, we will locate places where a single skeleton joint has three immediate neighbors (Fig~\ref{fig:split_errors}).
We will choose two of the neighbors as seed locations for a watershed algorithm that will run on the affinities constrained to the segment.
This will generate a potential split location between the two seeds.
We will then extract a region of interest around this split and use that cube as input into our previously trained merge classifier.
If the classifier says that the two segments should not merge, we will accept the split as is and divide the segment.
Otherwise we will ignore this split candidate and keep the segment intact.

A benefit of this approach is that we will have one CNN to determine both merge and split decisions.
This allows us to better tune our parameters with the scarce number of training examples from error correction.
Figure~\ref{fig:proposed-pipeline} shows our proposed framework that corrects both merge and split errors.

### 2018-05-01 papers/quals2018/6_compression.tex
quals: added method and evaluation from eccv submission

\section{Compression}

\begin{figure*}[t]
	\begin{center}
		\includegraphics[width=0.45\linewidth]{./figures/encoding_diagram_opt.pdf}
		\hspace{0.08\linewidth}
		\includegraphics[width=0.45\linewidth]{./figures/window_values.pdf}
	\end{center}	
	\caption{Compresso works by dividing up the segmentation data into small blocks. On the left we show the intersection of three segments in a $4\times4\times1$ window. We extract a boundary map from this segmentation to transform the window into an integral value between $0$ and $2^{16} - 1$. The location $i$ requires some additional bookkeeping. On the right are the $100$ most common $8 \times 8 \times 1$ windows accounting for $\sim82\%$ of the volume on a representative dataset.}
	\label{fig:compression}
\end{figure*}

An often overlooked aspect of these segmentation datasets is how to efficiently store the label volumes.
These label volumes are often 32- or 64-bit to account for the massive number of neurons that interweave through a cubic millimeter.
Uncompressed, a cubic millimeter of segmentation data is nearly 20 petabytes and oftentimes there are a series of saved interim segmentations.
Simply put, compression techniques are needed for fast transmission and cost-efficient storage.

General-purpose compression schemes~\cite{collet2016smaller,deutsch1996zlib,google2016brotli,lehmann2016liblzf,oberhumer2005lzo,pavlov2007lzma,seward1998bzip2,vandevenne2016zopfli,welch1984technique,ziv1978compression} are not optimized for this data.
With Compresso, an algorithm published in MICCAI 2017, we exploit the typical characteristics of label volumes such as large invariant regions without natural relationship between label values. 
These properties render 2D image compression schemes inadequate since they rely on frequency reduction (using e.g., wavelet or discrete cosine transform) and value prediction of pixels based on local context (differential pulse-code modulation)~\cite{roelofs1999png,skodras2001jpeg}. 
Color space optimization strategies in video codecs~\cite{aimar2005x264} also have no effect on label volumes, even though the spatial properties of a segmentation stack (\textit{z}-axis) are similar to the temporal properties of video data (time-axis). 
A compression scheme designed specifically for label volumes is part of the visualization software Neuroglancer~\cite{google2016compressed}. 
This method exploits segmentation homogeneity by creating small blocks with $N$ labels and reducing local entropy to $\log_2{N}$ per pixel. 
Lookup tables then decode the values $[0,N)$ to the original 64-bit labels.

Compresso works by decoupling the two important components across the image stack: per-segment shape and per-pixel label.
To encode the segment shapes, we consider the boundary pixels between two segments. 
Removing the per-pixel labels, we produce a boundary map for each slice where a pixel $(x, y, z)$ is 1 if either pixel at $(x + 1, y, z)$ or $(x, y + 1, z)$ belongs to a different segment (Fig~\ref{fig:compression}, left). 
The boundary map is divided into non-overlapping congruent 3D windows. If there are $n$ pixels per window, each window $w$ is assigned an integer $V_w \in [0, 2^n)$ where $V_w$ is defined as:

\begin{equation}
V_w = \sum_{i = 0}^{n - 1} \mathbb{I}(i) 2^i,
\end{equation}

\noindent
and $\mathbb{I}(i)$ is 1 if pixel $i$ is on a boundary and 0 otherwise. 
Figure~\ref{fig:compression}, left, shows an example segmentation with a window size of $4 \times 4 \times 1$.

A priori, each window could take any of $2^n$ distinct values, and therefore require $n$ bits to encode without further manipulation. 
However, boundaries in segmentation images are not random, and many of these values never appear. 
Indeed, we find that a small subset of high-frequency $V_w$ values accounts for most windows, allowing for significant compression. 
Figure~\ref{fig:compression}, right, shows the 100 most common windows for a representative connectomics dataset. 
These 100 frequently occurring windows account for approximately 82\% of the over 1.2 million $V_w$ values in this dataset.
Nearly all of these windows correspond to simple lines traversing through the window. 
For contrast, we also provide 5 randomly generated windows that never occur in the dataset.

We define $N$ as the number of distinct $V_w$ representing all of the windows in an image stack. 
We construct an invertible function $f(V_w) \to [0, N)$ to transform the window values into a smaller set of integers. 
For all real-world segmentations $N \ll 2^n$; however, we assume no constraint on $N$ in order to guarantee lossless compression. 
With this function, each $V_w$ requires $\log_2{N}$ bits of information to encode. 
This is fewer than the initial number of bits so long as $N \leq 2^{n - 1}$.

So far we have focused exclusively on transforming the boundary map of an image segmentation. 
However, the per-pixel labels themselves are equally important. 
The boundary map divides each image slice into different segments. 
By design, all pixels in the same segment have the same label so we store only one label per segment for each slice. 
We use a connected-component labeling algorithm to store one label per segment \cite{he2009fast}. 
The algorithm labels all pixels clustered within a component $m$ from $M$ section labels.

Thus far, we have assumed the boundaries provide enough information to reconstruct the entire segmentation.
Pixels not on a segment boundary are easily relabeled.
However, more care is needed for pixels on the segment boundaries. 
Consider Figure~\ref{fig:compression}, left, which depicts a difficult boundary to decode. 
If a boundary pixel has a non-boundary neighbor to the left or above, then that pixel merely takes on the value of that neighbor. 
However, pixel $i$ requires more care since its relevant neighbors are both boundary pixels. 
We simply just store the label values for indeterminate pixels like $i$.

To decompress the data, we first reconstruct the boundary map from the windows that we extracted.
From there, we can run the same deterministic connected-components algorithm per slice.
We can traverse through the saved labels to fill in all non-boundary labels.
To determine the per-pixel labels for every boundary pixel, we iterate over the entire dataset in raster order. 
Any boundary pixel $(x, y, z)$ with a non-boundary neighbor at $(x - 1, y, z)$ or $(x, y - 1, z)$ shares the same per-pixel label. 
If both relevant neighbors are boundaries (i.e., like pixel $i$ in Fig.~\ref{fig:compression}) we extract the value we had stored.

Our compression scheme outperforms all existing methods.
We follow our scheme with LZMA which uses sophisticated probabilistic bit prediction strategies and achieve ratios of $700\times$ on average.
We compressed an 18 terabyte label volume of 100 microns cubed to 26.2 gigabytes, a ratio of $\sim670\times$.

### 2018-05-01 papers/quals2018/0_introduction.tex
quals: major updates to structure

--- 2018-04-27 papers/quals2018/0_introduction.tex
@@
+% !TEX root =  paper.tex
 \section{Introduction}
 
-The field of connectomics is concerned with the reconstruction of the wiring diagram of the mammalian brain.
-In order to achieve this ambitious goal, we need images at nanometer resolution to see the structure of the neurons and the synaptic connections between them.
-Recent advances in electron microscopy acquisition techniques enable a throughput of a terabyte of image data every hour~\cite{richard2016imaging}.
-Manual reconstruction of this image data is simply infeasible and requires automatic segmentation methods.
-These automatic methods label every voxel of the image with a 64-bit integer value where two voxels have the same label only if they belong to the same neuron.
-As the field progresses, our goal is to reconstruct a cubic millimeter of brain which will result in over 18 petabytes of segmentation data alone~\cite{suissa2016automatic}.
+One of the critical components of connectomics---the field concerned with reconstructing the wiring diagram of the brain at nanometer resolution---is automatic segmentation of electron microscopy (EM) images of the brain.
+With recent advances in EM acquisition techniques, neuroscientists can now generate a terabyte of image data every hour~\cite{richard2016imaging}.
+These images are typically anisotropic with $4$nm resolution in the $xy$ plane and \numrange{30}{40}nm between slices. 
+At this resolution, we can see the axon terminals and dendritic spines, and the synaptic connections between them.
+Accurate reconstruction of every neuron paired with synapse detection will allow us to create a true graphical representation of the brain and further our understanding of the underlying circuitry.
+These segmentation, or label, volumes assign a 32- or 64-bit integer label to every voxel where voxels have the same label only if they belong to the same neuron.
 
-Three major challenges arise as the image datasets scale to a petabyte and more. 
-First, the segmentation methods must be accurate enough to extract the proper connections between neurons.
-In particular, the dendritic spines \TODO{check,CITE} which contain the postsynaptic density can be only \TODO{XX} nanometers thick.
-Second, automatic segmentation must be fast -- ideally matching the throughput of the electron microscope~\cite{haehn2017scalable}.
-The current state-of-the-art automatic reconstruction pipelines are either too slow for such large datasets or too inaccurate at scale.
-Third, the label volumes require $8\times$ the number of bytes as the already massive image volumes.
-Storing such data is expensive and transferring the data is slow. 
-To cut costs and delays, we need compression methods to reduce data sizes.
+An ambitious manual reconstruction effort in the 1980s resulted in the first complete connectome of any animal, the \textit{Caenorhabditis elegans} worm~\cite{white1986structure}. 
+This species has 302 neurons and manual labeling required several years.
+More recent studies focus on \textit{Drosophila} flies~\cite{jovanic2016competitive,takemura2015synaptic},  rodents~\cite{richard2016imaging}, and even humans~\cite{sporns2005human}. 
+With an EM throughput of one terabyte per hour, neuroscientists can image a cubic millimeter of data (two petabytes) in six months~\cite{suissa2016automatic}. 
+At this scale, the manual reconstruction techniques of the 80s are simply infeasible.
+Thus, researchers rely on deep learning methods to segment these massive datasets.
+
+Automatic reconstruction produces label volumes that, uncompressed, are much larger in size than the already massive image datasets.
+In our paper published in \textit{MICCAI 2017}, we explore the effectiveness of existing general-purpose, image, and video compression techniques on the segmentation datasets.
+We find that these existing techniques fail to adequately exploit the typical properties of our label volumes.
+Thus, we propose \textit{Compresso}, a new compression algorithm specifically tailored for large label volumes that far exceeds existing strategies.
+
+Automatic reconstruction techniques need to be fast, scalable, and accurate.
+Ideally, image acquisition is the bottleneck of the connectomics pipeline so reconstruction occurs at a rate of one terabyte per hour~\cite{haehn2017scalable}.
+We can achieve this throughput with parallelization among several GPUs with existing techniques~\cite{funke2017deep,parag2017anisotropic}.
+However, these automatic methods typically only rely on local context for decision making and are agnostic about the underlying biological systems.
+Thus, they often make errors at scale and currently require human proofreading or other error correction techniques~\cite{haehn2017guided,error_correction_using_CNN}.
+
+We propose a novel region merging framework that takes as input an oversegmentation of an EM volume (under review, \textit{ECCV 2018}).
+Our method imposes both local and global biological constraints onto the output segmentation to more closely match the underlying structure of neuronal processes.
+Additionally, our method is independent of image resolution and acquisition parameters, enabling its application to isotropic and anisotropic data without retraining.
+Images generated by electron microscopes often differ in appearance because of variations in staining techniques~\cite{briggman2012volume}.
+By removing the dependence of our algorithm on the input images, we greatly reduce the need for additional costly ground truth data for each new stack of images.

### 2018-05-01 papers/quals2018/1_related_work.tex
quals: major updates to structure

@@
+% !TEX root =  paper.tex
 \section{Related Work}
 
-\begin{figure*}[t!]
-	\centering
-	\includegraphics[width=0.75\linewidth]{./figures/teaser_v4.png}
-	\caption{Our framework uses both geometric and topological biological constraints for region merging.
-We (a) generate a simplified graph from the skeleton representation of the input segmentation, (b) train a classifier to learn the edge weight based on the shape of the segment connection, and (c) perform graph partitioning with acyclic constraints.}
-	\label{fig:teaser_pipeline}
+\begin{figure*}[t]
+	\begin{center}
+		\includegraphics[width=0.45\linewidth]{./figures/encoding_diagram_opt.pdf}
+		\hspace{0.08\linewidth}
+		\includegraphics[width=0.45\linewidth]{./figures/window_values.pdf}
+	\end{center}	
+	\caption{Compresso works by dividing up the segmentation data into small blocks.
+On the left we show the intersection of three segments in a $4\times4\times1$ window.
+We extract a boundary map from this segmentation to transform the window into an integral value between $0$ and $2^{16} - 1$.
+The location $i$ requires some additional bookkeeping.
+On the right are the $100$ most common $8 \times 8 \times 1$ windows accounting for $\sim82\%$ of the volume on a representative dataset.}
+	\label{fig:compression}
 \end{figure*}
+
+General-purpose compression schemes~\cite{collet2016smaller,deutsch1996zlib,google2016brotli,lehmann2016liblzf,oberhumer2005lzo,pavlov2007lzma,seward1998bzip2,vandevenne2016zopfli,welch1984technique,ziv1978compression} are not optimized for this data.
+With Compresso, an algorithm published in MICCAI 2017, we exploit the typical characteristics of label volumes such as large invariant regions without natural relationship between label values. 
+These properties render 2D image compression schemes inadequate since they rely on frequency reduction (using e.g., wavelet or discrete cosine transform) and value prediction of pixels based on local context (differential pulse-code modulation)~\cite{roelofs1999png,skodras2001jpeg}.
+Color space optimization strategies in video codecs~\cite{aimar2005x264} also have no effect on label volumes, even though the spatial properties of a segmentation stack (\textit{z}-axis) are similar to the temporal properties of video data (time-axis).
+A compression scheme designed specifically for label volumes is part of the visualization software Neuroglancer~\cite{google2016compressed}. 
+This method exploits segmentation homogeneity by creating small blocks with $N$ labels and reducing local entropy to $\log_2{N}$ per pixel. 
+Lookup tables then decode the values $[0,N)$ to the original 64-bit labels.
 
@@
 First, intermediate representations like boundary, affinity or binary segmentation maps are generated from the voxels.
-Random forests with hand-designed features~\cite{kaynig2015large}, or 2D and 3D convolutional networks produce boundary probabilities~\cite{seymour2016rhoananet,ronneberger2015u,bogovic2013learned,ciresan2012deep,jain2010boundary,amelio_segmentation}.
-Often, the affinity between each voxel and its six neighbors are used~\cite{lee2015recursive,parag2017anisotropic,lee2017superhuman,cciccek20163d,turaga2010convolutional}. 
+Random forests with hand-designed features~\cite{kaynig2015large}, or 2D and 3D convolutional networks produce boundary probabilities~\cite{bogovic2013learned,ciresan2012deep,jain2010boundary,seymour2016rhoananet,ronneberger2015u,amelio_segmentation}.
+Often, the affinity between each voxel and its six neighbors are used~\cite{cciccek20163d,lee2015recursive,lee2017superhuman,parag2017anisotropic,turaga2010convolutional}. 
 The 3D U-Net architecture has become popular~\cite{cciccek20163d} and the MALIS cost function is specifically designed to re-weight affinity predictions by their contribution to the segmentation error~\cite{briggman2009maximin}.
@@
 In both cases, available methods are pixel-based and do not include global biological constraints into the decision making process. 
-Our method can be used as input to any existing error correction framework.
+Our method can take as input any existing segmentation pipeline.

### 2018-05-01 papers/quals2018/2_method.tex
quals: added method and evaluation from eccv submission
quals: major updates to structure

--- 2018-03-14 papers/eccv2018/2_method.tex
@@
 % !TEX root =  paper.tex
+\section{Biologically-Constrained Error Correction}
 
-\section{Method}
-%\begin{figure*}[t!]
-%	\begin{center}
-%		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/multicut_input.png}}
-%		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/pre-multicut.png}}
-% 		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/multicut-graph.png}}
-% 		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/post-multicut.png}}
-% 	\end{center}
-% 	\caption{Outline of our approach, from left to right: result of the pixel-based segmentation and agglomeration algorithm; segments of several neurons from the initial segmentation; extracted skeletonized network of those segments; improved 3D reconstruction of the selected segments after graph construction and partitioning with constraints.}
-% 	\label{fig:overview}
-% \end{figure*}
-
-%There are two types of errors that can occur in connectomics segmentations: \textit{split errors} and \textit{merge errors}. 
-%In a split error, two segments should have been merged into one neuronal process (Fig.~\ref{fig:improved-reconstruction}). 
-%In a merge error, one segment corresponds to more than one neuron.
-%Generally, it is much more difficult to correct merge errors than to correct split errors, as the space of possible split proposals grows quickly~\cite{parag2015properties}.
-%Thus, most reconstruction approaches are tuned towards over-segmentation with many more split than merge errors. 
-%The input of our method is the over-segmentation of EM image volumes from state-of-the-art pipelines.
+\begin{figure*}[t!]
+	\centering
+	\includegraphics[width=0.75\linewidth]{./figures/teaser_v4.png}
+	\caption{Our framework uses both geometric and topological biological constraints for region merging.
+We (a) generate a simplified graph from the skeleton representation of the input segmentation, (b) train a classifier to learn the edge weight based on the shape of the segment connection, and (c) perform graph partitioning with acyclic constraints.}
+	\label{fig:teaser_pipeline}
+\end{figure*}
 
@@
 First, we only consider merging segments based on a skeletonized representation of the input segmentation (Fig.~\ref{fig:teaser_pipeline}a).
-This enables us to reduce the number of nodes in the graph based on prior knowledge on the shape of neuronal processes.
+This enables us to reduce the number of edges in the graph based on prior knowledge on the shape of neuronal processes.
 Second, we train a convolutional neural network that learns biological constraints based on the shapes of the input segmentation (Fig.~\ref{fig:teaser_pipeline}b).
@@
 Third, we partition the graph using a lifted multicut formulation with additional acyclic constraints to enforce global biological constraints (Fig.~\ref{fig:teaser_pipeline}c).
-The lifted multicut solution is globally consistent which we then augment to produce a tree-structured graph (i.e., one with no cycles).
+The lifted multicut solution is globally consistent which we then augment to produce a tree-structured graph.
 
 \subsection{Skeleton-Based Graph Generation}
-%\subsubsection{Node Generation}
 \label{sec:skeletonization}
 Most region merging methods create a region graph by removing small-sized segments and linking each pair of adjacent segments, which can still lead to a large graph size due to the irregular shape of neural structures.
-We use a skeleton representation of the segmentation to reduce the graph size with the geometric constraints on the connectivity of two adjacent segments to prune edges.
-% a bit trivial, as everyone is doing this. maybe no need to mention
-% \subsubsection{Node Pruning}
-% %The simplest node generation strategy creates one node for every unique segment label in the input volume. 
-% Some labels in the volume correspond to very small structures that are likely the result of segmentation errors, typically in regions with noisy raw image data. 
-% It is difficult to extract useful shape features from these segments because of their small, often random, shape. 
-% We prune these nodes from the graph by removing all segments with fewer than a empirical threshold $t_{seg} = 20,000$ voxels. 
-% This removes on average \TODO{XX}\% of the segments in our  datasets (Sec.~\ref{sec:dataset}), leaving us with around $\TODO{XX}$ nodes per dataset (\TODO{X nodes per micrometer}). 
-% Despite the large number of segments, these regions only take up \TODO{XX}\% of the total volume on average.
+We use a skeleton representation of the segmentation to reduce the graph size with geometric constraints on the connectivity of two adjacent segments to prune edges.
 
-% \subsubsection{Edge Pruning}
-
-\begin{figure}[t]
-	\centering
-	\begin{minipage}{0.45\linewidth}
-		\includegraphics[width=\linewidth]{./figures/skeleton1.png}		
-	\end{minipage}
-	\hfill
-	\begin{minipage}{0.45\linewidth}
-		\includegraphics[width=\linewidth]{./figures/skeleton2.png}		
-	\end{minipage}
-	\begin{minipage}{0.45\linewidth}
-		\includegraphics[width=\linewidth]{./figures/skeleton3.png}		
-	\end{minipage}
-	\hfill
-	\begin{minipage}{0.45\linewidth}
-		\includegraphics[width=\linewidth]{./figures/skeleton4.png}		
-	\end{minipage}
-	\caption{Example skeletons (in black) extracted from segments using a variant of the TEASER algorithm~\cite{sato2000teasar}.
-These skeletons not only well-capture the shape of the segmentation, but also provide end-points useful for region merging proposals.}
-	\label{fig:skeletonization}
-\end{figure}
-
-%A typical approach for generating edges produces one between all adjacent segments. 
-%Two segments $l_1$ and $l_2$ are considered adjacent if there is a pair of adjacent voxels with one labeled $l_1$ and the other labeled $l_2$.
-%For example, pixel-based agglomeration methods such as mean agglomeration~\cite{lee2017superhuman} or waterz~\cite{funke2017deep} consider all pairs of adjacent segments for merging.
-%However, this method produces too many edges in the graph for graph-based optimization approaches. 
 Our key observation is that if two segments belong to the same neuronal process, their skeleton end points should satisfy certain geometric constraints.
 To extract the skeleton from each segment, we use a variant~\cite{zhao2014automatic} of the TEASER algorithm~\cite{sato2000teasar}. 
-This skeletonization algorithm repeatedly uses Dijkstra's algorithm to find the farthest voxel from a seed location. 
-Since this algorithm is non-linear in the number of voxels, we downsample the datasets so that there are voxel samples every $\SI{30}{\nano\meter}$ in each dimension.
-Empirically, this reduced the running time for skeletonization by $30\times$ with minimal reduction in skeleton accuracy (${\sim}5\%$ fewer branches). 
 Fig.~\ref{fig:skeletonization} shows four examples of extracted skeletons (in black). 
@@
 Only these pairs have a corresponding edge in the constructed graph.
-We provide an empirical analysis of these parameters on the structure of the graph in the supplemental materials.
 
-\begin{figure}[t]
-	\begin{minipage}{0.4\linewidth}
-		\includegraphics[width=\linewidth]{./figures/constraint_error.png}
-	\end{minipage}
-	\hfill
-	\begin{minipage}{0.55\linewidth}
-		\includegraphics[width=\linewidth]{./figures/constraint_success.png}
-	\end{minipage}
-	\caption{Geometric constraints for region merging.
-We show two region merging proposals.
-On the left, the segments do not belong to the same neuron, as evidenced by the sharp turning radius; while on the right, the segments should be merged due to the continuity of the 3D shape.
-Instead of using handcrafted geometric features, we train a convolutional neural networks to automatically learn them from the ground truth labels.}
-	\label{fig:turn-radii}
-\end{figure}
 \subsection{Learning-based Edge Weight}
 \label{sec:edge-weights}
-We assign an edge weight $w_e$ to each edge corresponding to the probability that two nodes belong to the same neuronal process.
-We train a 3D CNN model to learn these geometric constraints for valid connection between two segments from labeled volume.
-\\~\\
-\noindent\textbf{Edge Probability}
+
 To predict the probabilities that two segments belong to the same neuron, we train a feed-forward convolutional network with three \textit{VGG-style} convolution blocks~\cite{chatfield2014return} and two fully connected layers before the final sigmoid activation.
-
 For the input of the network, we extract a cubic region of interest (ROI) around each endpoint $e$ in $\mathbb{S}_c$ as input to the CNN. 
-The CNN receives three input channels for every voxel in the ROI around segments $l_1$ and $l_2$. 
-The input in all of the channels is in the set $\{-0.5, 0.5\}$. 
-The first channel is $0.5$ only if the corresponding voxel has label $l_1$. 
-The second channel is $0.5$ only if the corresponding voxel has label $l_2$. 
-The third channel is $0.5$ if the corresponding voxel is either $l_1$ or $l_2$.
+There are three channels corresponding to voxels belonging to label one, label two, or either label.
 We do not use the raw EM image information to avoid the need to retrain the network on datasets that have been stained differently or imaged at different resolution. 
@@
 
-%The first two max pooling layers are anisotropic with pooling only in the $x$ and $y$ dimensions. 
-%The output of this final pooling step is flattened into a 1D vector that is input into . 
-%The final layer produces probabilities with a sigmoid activation function~\cite{funahashi1989approximate}. 
-%All of the other activation functions are .
+\subsection{Optimization-Based Graph Partition}
 
-% covered in the experiment
-%For training we use a stochastic gradient descent optimizer with Nesterov's accelerated gradient~\cite{nesterov1983method}. 
-%We employ dropouts of $0.2$ after every pooling layer and the first dense layer, and a dropout of $0.5$ after the final dense layer to prevent overfitting. 
-%We discuss all other network parameters in Sec.~\ref{sec:network-parameters}.
+\label{sec:optimization}
 
-\begin{figure}[t]
-	\centering
-	\begin{minipage}{0.32\linewidth}
-		\includegraphics[width=\linewidth]{./figures/split_error1.png}		
-	\end{minipage}
-	\hfill
-	\begin{minipage}{0.32\linewidth}
-		\includegraphics[width=\linewidth]{./figures/split_error2.png}				
-	\end{minipage}
-	\hfill
-	\begin{minipage}{0.32\linewidth}
-		\includegraphics[width=\linewidth]{./figures/split_error3.png}
-	\end{minipage}
-	\caption{Three erroneously split segments.}
-	\label{fig:merge_candidates}
-\end{figure}
-\subsection{Optimization-Based Graph Partition}
-\label{sec:optimization}
-After graph construction, we segment the graph in a globally consistent manner while enforcing topological constraints on the output.
-\\~\\
-%\subsubsection{Lifted Multicut}
-\noindent\textbf{Lifted Multicut}
 After constructing the graph we seek to partition it into labels where every label corresponds to a neuronal process. 
@@
 Since our graphs are sufficiently small, we can generate lifted edges between all pairs of nodes.
-\\~\\
-\noindent\textbf{Edge Weight} 
-We need to convert the probabilities into the following weighting scheme to solve the multicut problem with this heuristic~\cite{keuper2015efficient,andres2011probabilistic}.
+
+We need to convert the probabilities into the following weighting scheme to solve the multicut problem with this heuristic~\cite{andres2011probabilistic,keuper2015efficient}.
 Given the probability that the nodes belong to the same neuron is $p_e$, the edge weight $w_e$ is defined as
@@
 ~\cite{beier2017multicut}.
-\\~\\
-%\subsubsection{Topological Constraints}
-\noindent\textbf{Topological Constraints}
+
 By reformulating the segmentation problem as a graph partitioning one, we can enforce some global constraints on our result based on the underlying biology.

### 2018-05-01 papers/quals2018/3_evaluation.tex
quals: added method and evaluation from eccv submission
quals: major updates to structure

--- 2018-03-14 papers/eccv2018/3_evaluation.tex
@@
 \section{Experiments}
+
+\begin{figure}[t]
+	\centering
+	\begin{minipage}{0.45\linewidth}
+		\includegraphics[width=\linewidth]{./figures/skeleton1.png}		
+	\end{minipage}
+	\hfill
+	\begin{minipage}{0.45\linewidth}
+		\includegraphics[width=\linewidth]{./figures/skeleton2.png}		
+	\end{minipage}
+	\begin{minipage}{0.45\linewidth}
+		\includegraphics[width=\linewidth]{./figures/skeleton3.png}		
+	\end{minipage}
+	\hfill
+	\begin{minipage}{0.45\linewidth}
+		\includegraphics[width=\linewidth]{./figures/skeleton4.png}		
+	\end{minipage}
+	\caption{Example skeletons (in black) extracted from segments using a variant of the TEASER algorithm~\cite{sato2000teasar}.
+These skeletons not only capture the shape of the segmentation, but also provide endpoints useful for region merging proposals.}
+	\label{fig:skeletonization}
+\end{figure}
+
+\begin{figure}[t]
+	\begin{minipage}{0.4\linewidth}
+		\includegraphics[width=\linewidth]{./figures/constraint_error.png}
+	\end{minipage}
+	\hfill
+	\begin{minipage}{0.55\linewidth}
+		\includegraphics[width=\linewidth]{./figures/constraint_success.png}
+	\end{minipage}
+	\caption{Geometric constraints for region merging.
+We show two region merging proposals.
+On the left, the segments do not belong to the same neuron, as evidenced by the sharp turning radius indicated by the arrow; while on the right, the segments should be merged due to the continuity of the 3D shape.
+Instead of using handcrafted geometric features, we train a convolutional neural networks to automatically learn them from the ground truth labels.}
+	\label{fig:turn-radii}
+\end{figure}
+
+\begin{figure}[t]
+	\centering
+	\begin{minipage}{0.32\linewidth}
+		\includegraphics[width=\linewidth]{./figures/split_error1.png}		
+	\end{minipage}
+	\hfill
+	\begin{minipage}{0.32\linewidth}
+		\includegraphics[width=\linewidth]{./figures/split_error2.png}				
+	\end{minipage}
+	\hfill
+	\begin{minipage}{0.32\linewidth}
+		\includegraphics[width=\linewidth]{./figures/split_error3.png}
+	\end{minipage}
+	\caption{Three erroneously split segments.}
+	\label{fig:merge_candidates}
+\end{figure}
 
@@
 The following datasets contain 4 times more volume than the CREMI datasets. 
-\\~\\
-%\subsubsection{Kasthuri}
-\noindent\textbf{Kasthuri}
-The Kasthuri dataset consists of scanning electron microscope images of the neocortex of a mouse brain~\cite{kasthuri2015saturated}. 
+The first, which we call the Kasthuri dataset, consists of scanning electron microscope images of the neocortex of a mouse brain~\cite{kasthuri2015saturated}. 
 This dataset is $5342 \times 3618 \times 338$ voxels in size. 
 The resolution of the dataset is $\SI[product-units=single]{3 x 3 x 30}{\nano\meter}^3$ per voxel. 
-We evaluate our methods using the left cylinder of this 3-cylinder dataset. 
-We downsample the dataset in the $x$ and $y$ dimensions to give a final resolution of $\SI[product-units=single]{6 x 6 x 30}{\nano\meter}^3$ per voxel. 
-We divide the dataset into two volumes (Vol.
-1 and Vol.
-2) along the $x$ dimension, where each volume is $\SI[product-units=single]{8.0 x 10.9 x 10.1}{\micro\meter}^3$ or $1335 \times 1809 \times 338$ voxels.
-\\~\\
-%\subsubsection{FlyEM}
-\noindent\textbf{FlyEM}
-The FlyEM dataset comes from the mushroom body of a 5-day old adult male \textit{Drosophila} fly imaged by a focused ion-beam milling scanning electron microscopy~\cite{takemura2017connectome}.
-The mushroom body in this species is the primary site of associative learning. 
+We divide the dataset into two volumes (Vol. 1 and Vol. 2) along the $x$ dimension, where each volume is $\SI[product-units=single]{8.0 x 10.9 x 10.1}{\micro\meter}^3$.
+We train one of these halves and test on the other.
+Our second dataset, called FlyEM, comes from the mushroom body of a 5-day old adult male \textit{Drosophila} fly imaged by a focused ion-beam milling scanning electron microscopy~\cite{takemura2017connectome}.
 The original dataset contains a $\SI[product-units=single]{40 x 50 x 120}{\micro\meter}^3$ volume with a resolution of $\SI[product-units=single]{10 x 10 x 10}{\nano\meter}^3$ per voxel. 
-We use two cubes (Vol. 1 and Vol. 2) of size $\SI[product-units=single]{10 x 10 x 10}{\micro\meter}^3$ or $999 \times 999 \times 999$ voxels.
-
-%\subsubsection{Fib-25}
-%\noindent\textbf{Fib-25}
-%The Fib-25 dataset comes from the visual system of a \textit{Drosophila} fly~\cite{takemura2015synaptic}.
-This sample is %imaged at a resolution of $\SI[product-units=single]{8 x 8 x 8}{\nano\meter}^3$ and has $2588 \times 2108 \times 2876$ %voxels representing a volume of $\SI[product-units=single]{23.0 x 16.9 x 23.0}{\micro\meter}^3$.
-%There is currently a reconstruction challenge based on this sample.
+We use two cubes (Vol. 1 and Vol. 2) of size $\SI[product-units=single]{10 x 10 x 10}{\micro\meter}^3$.
 
@@
 \noindent\textbf{Initial Segmentation}
-%\label{sec:neuroproof}
-%The segmentation of the Kasthuri dataset was computed by agglomerating 3D supervoxels produced by the watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}. 
-%A recent study by Funke et al.~\cite{funke2017deep} demonstrated superior performance of such methods over existing ones on anisotropic data. 
-%We learn 3D affinities using MALIS loss with a U-net~\cite{ronneberger2015u,Turaga:2009}. 
-%We apply the z-watershed algorithm with suitable parameters to compute a 3D oversegmentation of the volume. 
-%The resulting 3D oversegmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}.
 The segmentation of the Kasthuri dataset is computed by agglomerating 3D supervoxels produced by the z-watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}. 
@@
 
-We consider networks with varying input sizes, optimizers, loss functions, filter sizes, learning rates, and activation functions. 
-The supplemental material includes information on the experiments that determined these final parameters. 
-We provide all parameters of the final network in the supplemental material. 
-There are $11,456,241$ learnable parameters in our final architecture. 
-All the parameters are randomly initialized following the Xavier uniform distribution~\cite{glorot2010understanding}. 
-Training concluded after 330 epochs.
-
-%\noindent\textbf{Training Augmentation.}
 Since our input is an existing segmentation of the EM images, there are very few training examples compared to per-pixel classifiers that train on a unique window for each voxel. 
@@
 We have 20,000 such examples per epoch.
-\\~\\
-\noindent\textbf{Graph Partition}
-%We assign the edges in our graph a weight $w_e = \log{\frac{p_e}{1 - p_e}} + \log{\frac{1 - \beta}{\beta}}$ where $\beta$ is a tunable parameter. 
-%Higher values of $\beta$ encourage over-segmentation.
-Figure~\ref{fig:variation-of-information} shows our results for variables $\beta \in [0.5, 0.99]$. 
-For our multicut analysis we use $\beta = 0.95$ (Sec.~\ref{sec:optimization}).
 

### 2018-05-01 papers/quals2018/4_results.tex
quals: added method and evaluation from eccv submission
quals: major updates to structure

@@
 We use one of these segmentations (green circle) as our input dataset with an agglomeration threshold of 0.3 for all datasets. 
-The results from our method are shown in red for varying the $\beta$ parameter. 
 We show comparisons to an oracle (blue) that correctly partitions the graph from our method based on ground truth.
@@
 
-\begin{table}
+\begin{table*}
 	\caption{The results of our graph pruning approach compared to the baseline graph with all adjacent regions.
@@
 The number of missed splits corresponds to the number of split errors that our method misses compared to an adjacency matrix.}
-\resizebox{\linewidth}{!}{
+\resizebox{0.75\linewidth}{!}{
 	\begin{tabular}{c c c c c} \hline
@@
 	\label{table:skeletonization}
-\end{table}
+\end{table*}
 
@@
 When computing the probability to merge two segments, we randomly rotate and flip the examples three times (in the same fashion as training augmentation).
-The supplemental material contains experiments showing the trade-offs between increased accuracy and runtime when using these augmentation strategies.
+Fig.~\ref{fig:receiver-operating-characteristic} shows the receiver operating characteristic (ROC) curve of our CNN classifier for all test datasets.
+As shown by the ROC curve, the test results on the FlyEM data are better than the results for Kasthuri.
+In part this comes from the disparity in the number of positive to negative merge candidates in the two graphs. 
+The network easily classifies most of the negative examples leaving only a few difficult examples to predict.
+Since there are more negative examples in relation to the positive examples in the FlyEM data, the ROC curve is greater.
 
@@
 \end{figure}
-Fig.~\ref{fig:receiver-operating-characteristic} shows the receiver operating characteristic (ROC) curve of our CNN classifier for all test datasets.
-As shown by the ROC curve, the test results on the FlyEM data are better than the results for Kasthuri.
-In part this comes from the disparity in the number of positive to negative merge candidates in the two graphs. 
-The network easily classifies most of the negative examples leaving only a few difficult examples to predict.
-Since there are more negative examples in relation to the positive examples in the FlyEM data, the ROC curve is greater.
 
@@
 	\centering
-	\includegraphics[width=0.45\linewidth]{./figures/receiver-operating-characteristic.png}
+	\includegraphics[width=0.9\linewidth]{./figures/receiver-operating-characteristic.png}
 	\caption{The receiver operating characteristic (ROC) curves of our classifier on three connectomics datasets. The classifier works best on previously unseen data of the Kasthuri volume.}
@@
 
-%\subsubsection{Generalization to Other Datasets}
-%\noindent\textbf{Generalization to Other Datasets.}
-Our neural network does not take as input the images or affinities so we can transfer network weights from one dataset to the next.
-The classification results are comparable on the FlyEM datasets despite the fact that the data varies in resolution and even animal type from the training set.
-\\~\\
 %\subsection{Graph Optimization Results}
@@
 The graph optimization strategy using multicut increases accuracy over using just the CNN.
-Table \ref{table:multicut} shows the changes in precision, recall, and accuracy for all four datasets compared to the CNN with both the multicut and lifted multicut formulations.
-These results correspond to $\beta = 0.95$ (Sec.~\ref{sec:edge-weights}). 
+Table \ref{table:multicut} shows the changes in precision, recall, and accuracy for all three datasets compared to the CNN with both the multicut and lifted multicut formulations.
 The precision increases on each dataset, although the recall decreases on each datasets.
@@
 
-\begin{table}[h]
+\begin{table*}[h]
 	\caption{Precision, recall, and accuracy changes between CNN only and CNN paired with graph-optimized reconstructions for the training and three test datasets.
@@
 	\centering
-\resizebox{\linewidth}{!}{
+\resizebox{0.75\linewidth}{!}{
 	\begin{tabular}{c c c c | c c c} \hline
@@
 	\label{table:multicut}
-\end{table}
-
-\subsection{Computational Performance}
-%\subsubsection{System} 
-\noindent\textbf{System}
-All performance experiments ran on an Intel Core i7-6800K CPU 3.40 GHz with a Titan X Pascal GPU.
-All code is written in Python and is freely available (link omitted for review).
-We use the Keras deep learning library for our neural networks with Theano backend and cuDNN 7 acceleration for CUDA 8.0.
-
-Every step in our framework is fast enough for large connectomics datasets. 
-On our training data, after downsampling, each segment was skeletonized in 0.56 seconds on average.
-There are 4451 such segments resulting in a total running time of 2,492 seconds on an 800 megavoxel volume. 
-From here, it took just over 31 seconds to generate the edges for our graph.
-On our hardware, inference on the neural network has a throughput of 30 examples per second. 
-Lastly, the multicut algorithm ran for 25.28 seconds while the lifted multicut variant took 36.5 seconds on the graph from this dataset.
+\end{table*}

### 2018-05-01 papers/quals2018/6_compression.tex
quals: major updates to structure

@@
-\section{Compression}
-
-\begin{figure*}[t]
-	\begin{center}
-		\includegraphics[width=0.45\linewidth]{./figures/encoding_diagram_opt.pdf}
-		\hspace{0.08\linewidth}
-		\includegraphics[width=0.45\linewidth]{./figures/window_values.pdf}
-	\end{center}	
-	\caption{Compresso works by dividing up the segmentation data into small blocks.
-On the left we show the intersection of three segments in a $4\times4\times1$ window.
-We extract a boundary map from this segmentation to transform the window into an integral value between $0$ and $2^{16} - 1$.
-The location $i$ requires some additional bookkeeping.
-On the right are the $100$ most common $8 \times 8 \times 1$ windows accounting for $\sim82\%$ of the volume on a representative dataset.}
-	\label{fig:compression}
-\end{figure*}
+% !TEX root =  paper.tex
+\section{Compression of Label Volumes}
 
@@
 Simply put, compression techniques are needed for fast transmission and cost-efficient storage.
-
-General-purpose compression schemes~\cite{collet2016smaller,deutsch1996zlib,google2016brotli,lehmann2016liblzf,oberhumer2005lzo,pavlov2007lzma,seward1998bzip2,vandevenne2016zopfli,welch1984technique,ziv1978compression} are not optimized for this data.
-With Compresso, an algorithm published in MICCAI 2017, we exploit the typical characteristics of label volumes such as large invariant regions without natural relationship between label values. 
-These properties render 2D image compression schemes inadequate since they rely on frequency reduction (using e.g., wavelet or discrete cosine transform) and value prediction of pixels based on local context (differential pulse-code modulation)~\cite{roelofs1999png,skodras2001jpeg}.
-Color space optimization strategies in video codecs~\cite{aimar2005x264} also have no effect on label volumes, even though the spatial properties of a segmentation stack (\textit{z}-axis) are similar to the temporal properties of video data (time-axis).
-A compression scheme designed specifically for label volumes is part of the visualization software Neuroglancer~\cite{google2016compressed}. 
-This method exploits segmentation homogeneity by creating small blocks with $N$ labels and reducing local entropy to $\log_2{N}$ per pixel. 
-Lookup tables then decode the values $[0,N)$ to the original 64-bit labels.
 
@@
 We follow our scheme with LZMA which uses sophisticated probabilistic bit prediction strategies and achieve ratios of $700\times$ on average.
-We compressed an 18 terabyte label volume of 100 microns cubed to 26.2 gigabytes, a ratio of $\sim670\times$.
+We compressed an 18 terabyte label volume of 100 microns cubed to 26.2 gigabytes, a ratio of $\sim687\times$.

### 2018-05-02 papers/quals2018/0_introduction.tex
updates to qualifying exam

@@
 
-One of the critical components of connectomics---the field concerned with reconstructing the wiring diagram of the brain at nanometer resolution---is automatic segmentation of electron microscopy (EM) images of the brain.
-With recent advances in EM acquisition techniques, neuroscientists can now generate a terabyte of image data every hour~\cite{richard2016imaging}.
+One of the critical components of connectomics---the field concerned with reconstructing the wiring diagram of the brain at nanometer resolution---is automatic segmentation of electron microscopy (EM) images.
+With recent advancements in EM acquisition techniques, neuroscientists can now generate a terabyte of image data every hour~\cite{richard2016imaging}.
 These images are typically anisotropic with $4$nm resolution in the $xy$ plane and \numrange{30}{40}nm between slices. 
 At this resolution, we can see the axon terminals and dendritic spines, and the synaptic connections between them.
-Accurate reconstruction of every neuron paired with synapse detection will allow us to create a true graphical representation of the brain and further our understanding of the underlying circuitry.
-These segmentation, or label, volumes assign a 32- or 64-bit integer label to every voxel where voxels have the same label only if they belong to the same neuron.
+Neuroscientists hope to further their understanding of the brain's underlying circuitry with accurate reconstructions of every neuron in these volumes and classification of the synaptic connections.
 
@@
 At this scale, the manual reconstruction techniques of the 80s are simply infeasible.
-Thus, researchers rely on deep learning methods to segment these massive datasets.
+Thus, researchers rely on machine learning methods to segment these massive datasets.
 
 Automatic reconstruction produces label volumes that, uncompressed, are much larger in size than the already massive image datasets.
+These label volumes assign a 32- or 64-bit integer to every voxel where voxels have the same label only if they belong to the same neuron.
 In our paper published in \textit{MICCAI 2017}, we explore the effectiveness of existing general-purpose, image, and video compression techniques on the segmentation datasets.
@@
 
+\begin{figure}
+	\includegraphics[width=\linewidth]{./figures/proposal-header.png}
+	\caption{From an EM image stack, 3D CNNs generate affinities between voxels (left).
+These affinities are agglomerated into superpixels which in turn are merged to form a complete segmentation (center).
+Oftentimes these methods produce errors and thus require error correction to improve the accuracy (right).}
+	\label{fig:overview}
+\end{figure}
+
 Automatic reconstruction techniques need to be fast, scalable, and accurate.
@@
 We can achieve this throughput with parallelization among several GPUs with existing techniques~\cite{funke2017deep,parag2017anisotropic}.
-However, these automatic methods typically only rely on local context for decision making and are agnostic about the underlying biological systems.
+However, these automatic methods typically rely on local context for decision making and are agnostic about the underlying biological systems.
 Thus, they often make errors at scale and currently require human proofreading or other error correction techniques~\cite{haehn2017guided,error_correction_using_CNN}.

### 2018-05-02 papers/quals2018/1_related_work.tex
updates to qualifying exam

@@
 
-\begin{figure*}[t]
-	\begin{center}
-		\includegraphics[width=0.45\linewidth]{./figures/encoding_diagram_opt.pdf}
-		\hspace{0.08\linewidth}
-		\includegraphics[width=0.45\linewidth]{./figures/window_values.pdf}
-	\end{center}	
-	\caption{Compresso works by dividing up the segmentation data into small blocks.
-On the left we show the intersection of three segments in a $4\times4\times1$ window.
-We extract a boundary map from this segmentation to transform the window into an integral value between $0$ and $2^{16} - 1$.
-The location $i$ requires some additional bookkeeping.
-On the right are the $100$ most common $8 \times 8 \times 1$ windows accounting for $\sim82\%$ of the volume on a representative dataset.}
-	\label{fig:compression}
-\end{figure*}
+Large scale image datasets requires fast automatic segmentation methods to match the throughput of the microscope.
+Thus, compressing the data in an efficient manner and accurately constructing the volumes at reasonable speeds become important problems.
+Here we provide a brief overview of existing compression methods and reconstruction techniques for these label volumes.
 
@@
 Additional research builds on top of these region-based methods to correct errors in the segmentation. 
+These input segmentations can contain two types of errors.
+In a \textit{split error}, one neurons contains multiple labels.
+In a \textit{merge error}, two or more neurons receive the same label.
 This can be done either using human proofreading~\cite{haehn2017guided,haehn2014design,mojo2} or automatically~\cite{rolnick2017morphological,error_correction_using_CNN}. 

### 2018-05-02 papers/quals2018/2_method.tex
updates to qualifying exam

@@
 % !TEX root =  paper.tex
-\section{Biologically-Constrained Error Correction}
+\section{Biologically-Constrained Region Merging}
 
@@
 	\centering
-	\includegraphics[width=0.75\linewidth]{./figures/teaser_v4.png}
+	\includegraphics[width=0.65\linewidth]{./figures/teaser_v4.png}
 	\caption{Our framework uses both geometric and topological biological constraints for region merging.
@@
 
-Our method is illustrated in Fig.~\ref{fig:teaser_pipeline}.
-From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with weights $w_e$. 
+\begin{figure}[t]
+	\centering
+	\begin{minipage}{0.45\linewidth}
+		\includegraphics[width=\linewidth]{./figures/skeleton1.png}		
+	\end{minipage}
+	\hfill
+	\begin{minipage}{0.45\linewidth}
+		\includegraphics[width=\linewidth]{./figures/skeleton2.png}		
+	\end{minipage}
+	\begin{minipage}{0.45\linewidth}
+		\includegraphics[width=\linewidth]{./figures/skeleton3.png}		
+	\end{minipage}
+	\hfill
+	\begin{minipage}{0.45\linewidth}
+		\includegraphics[width=\linewidth]{./figures/skeleton4.png}		
+	\end{minipage}
+	\caption{Example skeletons (in black) extracted from segments using a variant of the TEASER algorithm~\cite{sato2000teasar}.
+These skeletons not only capture the shape of the segmentation, but also provide endpoints useful for region merging proposals.}
+	\label{fig:skeletonization}
+\end{figure}
+
+Automatic reconstruction methods need to be fast enough to scale to petabyte datasets while still maintaining a high-level of accuracy.
+The most accurate methods, like flood-filling networks~\cite{januszewski2016flood}, are too slow to scale. 
+Unfortunately, methods that can scale to petabyte datasets typically rely on only local context and can produce errors at scale~\cite{haehn2017scalable}. 
+Therefore, it is necessary to employ error correction strategies on the segmentations from current reconstruction pipelines.
+We propose a biologically-constrained region merging algorithm to correct \textit{split errors} in the initial segmentation.
+
+For our proposed method (Fig.~\ref{fig:teaser_pipeline}), from the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with weights $w_e$. 
 The nodes correspond to labeled segments from the input data with edges between merge candidates.
@@
 To predict the probabilities that two segments belong to the same neuron, we train a feed-forward convolutional network with three \textit{VGG-style} convolution blocks~\cite{chatfield2014return} and two fully connected layers before the final sigmoid activation.
-For the input of the network, we extract a cubic region of interest (ROI) around each endpoint $e$ in $\mathbb{S}_c$ as input to the CNN. 
+For the input of the network, we extract a cubic region of interest (ROI) around each midpoint in $\mathbb{S}_c$ as input to the CNN. 
 There are three channels corresponding to voxels belonging to label one, label two, or either label.
@@
 This reduces the need for generating costly manually-labeled ground truth. 
+\begin{figure}[t]
+	\begin{minipage}{0.4\linewidth}
+		\includegraphics[width=\linewidth]{./figures/constraint_error.png}
+	\end{minipage}
+	\hfill
+	\begin{minipage}{0.55\linewidth}
+		\includegraphics[width=\linewidth]{./figures/constraint_success.png}
+	\end{minipage}
+	\caption{Geometric constraints for region merging.
+We show two region merging proposals.
+On the left, the segments do not belong to the same neuron, as evidenced by the sharp turning radius indicated by the arrow; while on the right, the segments should be merged due to the continuity of the 3D shape.
+Instead of using handcrafted geometric features, we train a convolutional neural networks to automatically learn them from the ground truth labels.}
+	\label{fig:turn-radii}
+\end{figure}
 
+\begin{figure}[t]
+	\centering
+	\begin{minipage}{0.32\linewidth}
+		\includegraphics[width=\linewidth]{./figures/split_error1.png}		
+	\end{minipage}
+	\hfill
+	\begin{minipage}{0.32\linewidth}
+		\includegraphics[width=\linewidth]{./figures/split_error2.png}				
+	\end{minipage}
+	\hfill
+	\begin{minipage}{0.32\linewidth}
+		\includegraphics[width=\linewidth]{./figures/split_error3.png}
+	\end{minipage}
+	\caption{Three erroneously split segments.}
+	\label{fig:merge_candidates}
+\end{figure}
 \subsection{Optimization-Based Graph Partition}
@@
 
-We need to convert the probabilities into the following weighting scheme to solve the multicut problem with this heuristic~\cite{andres2011probabilistic,keuper2015efficient}.
+We need to convert the probabilities into the following weighting scheme to solve the multicut problem with the greedy-edge heuristic~\cite{andres2011probabilistic,keuper2015efficient}.
 Given the probability that the nodes belong to the same neuron is $p_e$, the edge weight $w_e$ is defined as
@@
 We ``collapse'' an edge only if it does not create a cycle in the graph.
+
+\begin{figure*}[t!]
+	\centering
+	\includegraphics[width=0.32\linewidth]{./figures/benchmark/voi-Kasthuri-Luigi-Test.pdf}
+	\includegraphics[width=0.32\linewidth]{./figures/benchmark/voi-FlyEM-Vol--1.pdf}
+	\includegraphics[width=0.32\linewidth]{./figures/benchmark/voi-FlyEM-Vol--2.pdf}
+	\caption{Segmentation benchmark results on three volumes.
+We compare our method (red) to the baseline segmentation (green) and an oracle (blue) that optimally partitions our constructed graph from our method.
+Lower VI scores are better.
+Our method improves the segmentation accuracy over the baseline in all cases.
+		Note that our model is only trained on the Kasthuri training volume and it generalizes well to the FlyEM dataset.}
+	\label{fig:variation-of-information}
+\end{figure*}

### 2018-05-02 papers/quals2018/3_evaluation.tex
updates to qualifying exam

@@
 \section{Experiments}
-
-\begin{figure}[t]
-	\centering
-	\begin{minipage}{0.45\linewidth}
-		\includegraphics[width=\linewidth]{./figures/skeleton1.png}		
-	\end{minipage}
-	\hfill
-	\begin{minipage}{0.45\linewidth}
-		\includegraphics[width=\linewidth]{./figures/skeleton2.png}		
-	\end{minipage}
-	\begin{minipage}{0.45\linewidth}
-		\includegraphics[width=\linewidth]{./figures/skeleton3.png}		
-	\end{minipage}
-	\hfill
-	\begin{minipage}{0.45\linewidth}
-		\includegraphics[width=\linewidth]{./figures/skeleton4.png}		
-	\end{minipage}
-	\caption{Example skeletons (in black) extracted from segments using a variant of the TEASER algorithm~\cite{sato2000teasar}.
-These skeletons not only capture the shape of the segmentation, but also provide endpoints useful for region merging proposals.}
-	\label{fig:skeletonization}
-\end{figure}
-
-\begin{figure}[t]
-	\begin{minipage}{0.4\linewidth}
-		\includegraphics[width=\linewidth]{./figures/constraint_error.png}
-	\end{minipage}
-	\hfill
-	\begin{minipage}{0.55\linewidth}
-		\includegraphics[width=\linewidth]{./figures/constraint_success.png}
-	\end{minipage}
-	\caption{Geometric constraints for region merging.
-We show two region merging proposals.
-On the left, the segments do not belong to the same neuron, as evidenced by the sharp turning radius indicated by the arrow; while on the right, the segments should be merged due to the continuity of the 3D shape.
-Instead of using handcrafted geometric features, we train a convolutional neural networks to automatically learn them from the ground truth labels.}
-	\label{fig:turn-radii}
-\end{figure}
-
-\begin{figure}[t]
-	\centering
-	\begin{minipage}{0.32\linewidth}
-		\includegraphics[width=\linewidth]{./figures/split_error1.png}		
-	\end{minipage}
-	\hfill
-	\begin{minipage}{0.32\linewidth}
-		\includegraphics[width=\linewidth]{./figures/split_error2.png}				
-	\end{minipage}
-	\hfill
-	\begin{minipage}{0.32\linewidth}
-		\includegraphics[width=\linewidth]{./figures/split_error3.png}
-	\end{minipage}
-	\caption{Three erroneously split segments.}
-	\label{fig:merge_candidates}
-\end{figure}
 
@@
 
-Our proposed method is designed for very large connectomics datasets. 
-Popular challenge datasets such as CREMI and SNEMI3D are simply too small for any noticeable change. 
-The following datasets contain 4 times more volume than the CREMI datasets. 
-The first, which we call the Kasthuri dataset, consists of scanning electron microscope images of the neocortex of a mouse brain~\cite{kasthuri2015saturated}. 
+Our first dataset, which we call the Kasthuri dataset, consists of scanning electron microscope images of the neocortex of a mouse brain~\cite{kasthuri2015saturated}. 
 This dataset is $5342 \times 3618 \times 338$ voxels in size. 
@@
 We divide the dataset into two volumes (Vol. 1 and Vol. 2) along the $x$ dimension, where each volume is $\SI[product-units=single]{8.0 x 10.9 x 10.1}{\micro\meter}^3$.
-We train one of these halves and test on the other.
+We train and validate our methods on Vol. 1 and test on Vol. 2.
 Our second dataset, called FlyEM, comes from the mushroom body of a 5-day old adult male \textit{Drosophila} fly imaged by a focused ion-beam milling scanning electron microscopy~\cite{takemura2017connectome}.
@@
 \subsection{Method Configuration}
-\noindent\textbf{Initial Segmentation}
+
+\noindent\textbf{Input Segmentation.}
 The segmentation of the Kasthuri dataset is computed by agglomerating 3D supervoxels produced by the z-watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}. 
-A recent study by Funke et al.~\cite{funke2017deep} demonstrates superior performance of such methods over existing ones on anisotropic data. 
 We learn 3D affinities using MALIS loss with a U-Net~\cite{ronneberger2015u,Turaga:2009}. 
 We apply the z-watershed algorithm with suitable parameters to compute a 3D over-segmentation of the volume. 
-The resulting 3D over-segmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}.
+The resulting 3D oversegmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}.
+
 For the FlyEM data, based on the authors' suggestion~\cite{takemura2017connectome}, we apply a context-aware delayed agglomeration algorithm~\cite{10.1371/journal.pone.0125825} that shows improved performance on this dataset over the pipeline used in the original publication.
 This segmentation framework learns voxel and supervoxel classifiers with an emphasis to minimize under-segmentation error. 
-The algorithm first computes multi-channel 3-D predictions for membranes, cell interiors, and mitochondria, among other cell features. 
-The membrane prediction channel is used to produce an over-segmented volume using 3D watershed, which is then agglomerated hierarchically up to a certain confidence threshold. 
+The algorithm first computes multi-channel 3D predictions for membranes, cell interiors, and mitochondria, among other cell features. 
+The membrane prediction channel is used to produce an oversegmented volume using 3D watershed, which is then agglomerated hierarchically up to a certain confidence threshold. 
 We used exactly the same parameters as the publicly available code for this algorithm.
-%For the Fib-25 challenge dataset, we use the segmentation from Funke et al. as our input~\cite{funke2017deep}.
 \\~\\
-\noindent\textbf{Graph Generation}
+\noindent\textbf{Graph Generation.}
 The two parameters for the graph pruning algorithm (Sec.~\ref{sec:skeletonization}) are $t_{low}$ and $t_{high}$. 
@@
 After considering various thresholds, we find that $t_{low} = \SI{210}{\nano\meter}$ and $t_{high} = \SI{300}{\nano\meter}$ produce expressive graphs with a scalable number of nodes and edges.
-We explore these thresholds in greater detail in the supplemental material.
 During implementation, we use nanometers instead of voxels for these thresholds to have uniform units across all datasets.
-% Connectomics datasets often have lower sample resolutions in $z$ because of limitations during sample preparation. 
-% Using nanometers allows us to have uniform units across all of these datasets and calculate the thresholds in voxels at runtime.
-% Although the voxels vary between different datasets, the physical space remains constant. 
 \\~\\
-\noindent\textbf{Edge Weight Learning}
+\noindent\textbf{Edge Weight Learning.}
 \label{sec:network-parameters}
@@
 Since our input does not require the image data, we can train on the anisotropic Kasthuri data and test on the isotropic FlyEM data.
-
+\\~\\
+\noindent\textbf{Training Augmentation.}
 Since our input is an existing segmentation of the EM images, there are very few training examples compared to per-pixel classifiers that train on a unique window for each voxel. 

### 2018-05-02 papers/quals2018/4_results.tex
updates to qualifying exam

@@
 
-\begin{figure*}[t!]
-	\centering
-	\includegraphics[width=0.32\linewidth]{./figures/benchmark/voi-Kasthuri-Luigi-Test.pdf}
-	\includegraphics[width=0.32\linewidth]{./figures/benchmark/voi-FlyEM-Vol--1.pdf}
-	\includegraphics[width=0.32\linewidth]{./figures/benchmark/voi-FlyEM-Vol--2.pdf}
-	\caption{Segmentation benchmark results on three volumes.
-We compare our method (red) to the baseline segmentation (green) and an oracle (blue) that optimally partitions our constructed graph from our method.
-Lower VI scores are better.
-Our method improves the segmentation accuracy over the baseline in all cases.
-	Note that our model is only trained on the Kasthuri training volume and it generalizes well to the FlyEM dataset.}
-	\label{fig:variation-of-information}
-\end{figure*}
-
 In Fig.~\ref{fig:variation-of-information}, we show the VI results of the pixel-based reconstructions of the Kasthuri and FlyEM data (Sec.~\ref{sec:dataset}) for varying thresholds of agglomeration (green).
-We use one of these segmentations (green circle) as our input dataset with an agglomeration threshold of 0.3 for all datasets. 
 We show comparisons to an oracle (blue) that correctly partitions the graph from our method based on ground truth.
-
-Scores closer to the origin are better for this metric, and in every instance our results are below the green curve.
+Scores closer to the origin are better for this metric, and in every instance our results (red) are below the green curve.
 We see improvements on each data with a reduction in total VI score of $10.4\%$ on the Kasthuri data and $8.9\%$ and $5.4\%$ on the FlyEM datasets.

### 2018-05-02 papers/quals2018/5_proposed.tex
quals: major updates to structure
updates to qualifying exam

@@
+% !TEX root =  paper.tex
 \section{Proposed Work}
@@
 Both of these additional constraints will help with the current problem associated with large-scale reconstruction.
-Namely, that a small percentage of merge errors results in a tangled mess of multiple neurons per segment.
+That is, a small percentage of merge errors results in a tangled mess of multiple neurons per segment.
 
-To further prevent this problem, we will augment our work to correct split errors as well.
-We will generate locations from splits with the following algorithm.
-First, we will locate places where a single skeleton joint has three immediate neighbors (Fig~\ref{fig:split_errors}).
-We will choose two of the neighbors as seed locations for a watershed algorithm that will run on the affinities constrained to the segment.
-This will generate a potential split location between the two seeds.
-We will then extract a region of interest around this split and use that cube as input into our previously trained merge classifier.
-If the classifier says that the two segments should not merge, we will accept the split as is and divide the segment.
-Otherwise we will ignore this split candidate and keep the segment intact.
+To further prevent this problem of undersegmentation, we will augment our current work to correct merge errors as well.
+Generally, correcting merge errors is more difficult than correcting split errors because the space of possible split candidates grows quickly~\cite{parag2015properties}. 
+However, we plan to prune these candidates more efficiently using a skeleton based method that considers the underlying biology.
+Consider Figure~\ref{fig:proposal} that shows an incorrectly merged segment consisting a few neurons.
+We can extract a coarser skeleton from this segment that does not hit every spine but still gets the general shape.
+In particular, it shows three main paths in this one segment.
 
-A benefit of this approach is that we will have one CNN to determine both merge and split decisions.
-This allows us to better tune our parameters with the scarce number of training examples from error correction.
-Figure~\ref{fig:proposed-pipeline} shows our proposed framework that corrects both merge and split errors.
+Once locating these potentially erroneous segments, we will run a watershed algorithm on the affinities that forces the voxels into two segments.
+The surface separating the two segments is our ``split'' candidate.
+We will extract a cubic region of interest around this candidate and input the region into our previously discussed merge classifier.
+If the classifier suggests that the segments belong to one neuron, we will ignore the split candidate.
+Otherwise we will divide this segment based on the candidate.
+With a synaptic classifier, we can further constrain the watershed algorithm to only propose splits where pre- or post-synaptic connections occur on one side.

### 2018-05-02 papers/quals2018/6_compression.tex
updates to qualifying exam

@@
 
+\begin{figure*}[t]
+	\begin{center}
+		\begin{minipage}{0.45\linewidth}
+			\centering
+			\includegraphics[width=\linewidth]{./figures/encoding_diagram_opt.pdf}
+		\end{minipage}
+		\hspace{0.08\linewidth}
+		\begin{minipage}{0.45\linewidth}
+			\centering
+			\includegraphics[width=\linewidth]{./figures/window_values.pdf}
+		\end{minipage}
+	\end{center}	
+	\caption{Compresso works by dividing up the segmentation data into small blocks.
+On the left we show the intersection of three segments in a $4\times4\times1$ window.
+We extract a boundary map from this segmentation to transform the window into an integral value between $0$ and $2^{16} - 1$.
+The location $i$ requires some additional bookkeeping.
+On the right are the $100$ most common $8 \times 8 \times 1$ windows accounting for $\sim82\%$ of the volume on a representative dataset.}
+	\label{fig:compression}
+\end{figure*}
+
 An often overlooked aspect of these segmentation datasets is how to efficiently store the label volumes.
 These label volumes are often 32- or 64-bit to account for the massive number of neurons that interweave through a cubic millimeter.
-Uncompressed, a cubic millimeter of segmentation data is nearly 20 petabytes and oftentimes there are a series of saved interim segmentations.
-Simply put, compression techniques are needed for fast transmission and cost-efficient storage.
+Uncompressed, a cubic millimeter of segmentation data is nearly 20 petabytes.
+Thus, compression techniques are needed for fast transmission and cost-efficient storage.
 
+Published in MICCAI 2017, we proposed Compresso which is specifically designed for compression of EM label volumes.
 Compresso works by decoupling the two important components across the image stack: per-segment shape and per-pixel label.
@@
 However, more care is needed for pixels on the segment boundaries. 
-Consider Figure~\ref{fig:compression}, left, which depicts a difficult boundary to decode. 
+Consider figure~\ref{fig:compression}, left, which depicts a difficult boundary to decode. 
 If a boundary pixel has a non-boundary neighbor to the left or above, then that pixel merely takes on the value of that neighbor. 

### 2018-05-02 papers/quals2018/7_conclusions.tex
updates to qualifying exam

--- 2018-03-14 papers/eccv2018/5_conclusions.tex
@@
 \section{Conclusions}
+
+Several challenges arise as acquisition speeds of EM images improve. 
+First, the data must be quickly reconstructed using automatic techniques.
+These datasets are often 4 or 8 times the size of the already substantial image volumes requiring dedicated compression schemes.
+We propose Compresso, which increases compression ratio significantly over existing strategies.
+Second, errors in the initial segmentation need to be corrected.
+Algorithms that are fast enough to scale to petabyte datasets often rely only on local context and ignore the underlying biology.
+Unfortunately these restrictions significantly reduce the accuracy at scale.
 
@@
 
-An augmented graph would also be helpful for splitting improperly merged segments by adding additional terms to the partitioning cost function. 
+An augmented graph would be helpful for splitting improperly merged segments by adding additional terms to the partitioning cost function. 
 Using skeletons we can apply biological constraints on the topology for neurons that are improperly merged.

### 2018-05-02 papers/quals2018/5_proposed.tex
added proposal figure{

@@
 However, we plan to prune these candidates more efficiently using a skeleton based method that considers the underlying biology.
-Consider Figure~\ref{fig:proposal} that shows an incorrectly merged segment consisting a few neurons.
-We can extract a coarser skeleton from this segment that does not hit every spine but still gets the general shape.
-In particular, it shows three main paths in this one segment.
+Skeletons corresponding to undersegmented labels will have junctions at the failed merge (Fig.~\ref{fig:proposed}). 
+This greatly reduces the search space and will enable correcting split errors in a fraction of the current time.
 
-Once locating these potentially erroneous segments, we will run a watershed algorithm on the affinities that forces the voxels into two segments.
+\begin{figure}
+	\centering
+	\includegraphics[width=0.8\linewidth]{./figures/split-proposal.png}
+	\caption{An example where the input segmentation incorrectly merged two neurons together. The black circle indicates the junction from the skeletonized representation.}
+	\label{fig:proposal}
+\end{figure}
+
+After locating these potentially erroneous segments, we will run a watershed algorithm on the affinities that forces the voxels into two segments.
+This watershed algorithm will provide two seeds on opposite sides of the discovered junction.
 The surface separating the two segments is our ``split'' candidate.
@@
 With a synaptic classifier, we can further constrain the watershed algorithm to only propose splits where pre- or post-synaptic connections occur on one side.
+This process will run recursively for a given segment in case more than two neurons are improperly merged.

### 2018-05-02 papers/quals2018/2_method.tex
papers: restructured layout into two sections

@@
 \section{Biologically-Constrained Region Merging}
+
+Automatic reconstruction methods need to be fast enough to scale to petabyte datasets while still maintaining a high-level of accuracy.
+The most accurate methods, like flood-filling networks~\cite{januszewski2016flood}, are too slow to scale. 
+Unfortunately, methods that can scale to petabyte datasets typically rely on only local context and can produce errors at scale~\cite{haehn2017scalable}. 
+Therefore, it is necessary to employ error correction strategies on the segmentations from current reconstruction pipelines.
+We propose a biologically-constrained region merging algorithm to correct \textit{split errors} in the initial segmentation.
+
+\subsection{Related Works}
+
+A significant amount of connectomics research considers the problem of extracting segmentation information at the voxel level of EM images.
+First, intermediate representations like boundary, affinity or binary segmentation maps are generated from the voxels.
+Random forests with hand-designed features~\cite{kaynig2015large}, or 2D and 3D convolutional networks produce boundary probabilities~\cite{bogovic2013learned,ciresan2012deep,jain2010boundary,seymour2016rhoananet,ronneberger2015u,amelio_segmentation}.
+Often, the affinity between each voxel and its six neighbors are used~\cite{cciccek20163d,lee2015recursive,lee2017superhuman,parag2017anisotropic,turaga2010convolutional}. 
+The 3D U-Net architecture has become popular~\cite{cciccek20163d} and the MALIS cost function is specifically designed to re-weight affinity predictions by their contribution to the segmentation error~\cite{briggman2009maximin}.
+More recently, flood-filling networks~\cite{januszewski2016flood} produce binary segmentations from raw pixels with a recurrent convolutional network at a high computational cost.
+Orthogonal to the representation, model averaging~\cite{zeng2017deepem3d} and data augmentation~\cite{lee2017superhuman} methods can further improve the performance, where Lee et al.~\cite{lee2017superhuman} surpass the estimated human accuracy on the SNEMI3D dataset.
+
+Clustering techniques transform these intermediate representations into segmentations.
+Some early methods apply computationally expensive graph partitioning algorithms with a single node per superpixel~\cite{andres2012globally}.
+Several pixel-based approaches generate probabilities that neighboring pixels belong to the same neuron.
+Often a watershed algorithm will then cluster these pixels into super-pixels~\cite{zlateski2015image}.
+
+Region merging methods can be categorized by the similarity metric between adjacent segments and the merging strategy.
+For the similarity metric, Lee et al.
+and Funke et al.
+rely solely on the accuracy of the predicted affinities and define the metric as the mean affinity between segments~\cite{funke2017deep,lee2017superhuman}.
+Classification-based methods generate the probability to merge two segments from handcrafted~\cite{jain2011learning,seymour2016rhoananet,nunez2014graph,10.1371/journal.pone.0125825,parag2017anisotropic,zlateski2015image} and learned features~\cite{bogovic2013learned}.
+For the merging strategy, most methods use variants of hierarchical agglomeration ~\cite{seymour2016rhoananet,nunez2014graph,10.1371/journal.pone.0125825,parag2017anisotropic,zlateski2015image} to greedily merge a pair of regions at a time.
+Jain et al.
+formulates the agglomeration problem as a reinforcement learning problem ~\cite{jain2011learning} and Pape et al.
+present a scalable multicut algorithm to partition superpixels with global optimization~\cite{beier2017multicut}.
+
+Additional research builds on top of these region-based methods to correct errors in the segmentation. 
+These input segmentations can contain two types of errors.
+In a \textit{split error}, one neurons contains multiple labels.
+In a \textit{merge error}, two or more neurons receive the same label.
+This can be done either using human proofreading~\cite{haehn2017guided,haehn2014design,mojo2} or automatically~\cite{rolnick2017morphological,error_correction_using_CNN}. 
+In both cases, available methods are pixel-based and do not include global biological constraints into the decision making process. 
+Our method can take as input any existing segmentation pipeline.
+
+\subsection{Method}
 
@@
 
-Automatic reconstruction methods need to be fast enough to scale to petabyte datasets while still maintaining a high-level of accuracy.
-The most accurate methods, like flood-filling networks~\cite{januszewski2016flood}, are too slow to scale. 
-Unfortunately, methods that can scale to petabyte datasets typically rely on only local context and can produce errors at scale~\cite{haehn2017scalable}. 
-Therefore, it is necessary to employ error correction strategies on the segmentations from current reconstruction pipelines.
-We propose a biologically-constrained region merging algorithm to correct \textit{split errors} in the initial segmentation.
-
 For our proposed method (Fig.~\ref{fig:teaser_pipeline}), from the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with weights $w_e$. 
@@
 
-\subsection{Skeleton-Based Graph Generation}
+\subsubsection{Skeleton-Based Graph Generation}
 \label{sec:skeletonization}
@@
 
-\subsection{Learning-based Edge Weight}
+\subsubsection{Learning-based Edge Weight}
 \label{sec:edge-weights}
@@
 \end{figure}
-\subsection{Optimization-Based Graph Partition}
+\subsubsection{Optimization-Based Graph Partition}
 
@@
 \end{figure*}
+
+\subsection{Experiments}
+
+We evaluate our method by comparing it to a state-of-the-art pixel-based reconstruction approach using datasets from mouse and fly brains.
+
+\subsubsection{Datasets}
+\label{sec:dataset}
+
+Our first dataset, which we call the Kasthuri dataset, consists of scanning electron microscope images of the neocortex of a mouse brain~\cite{kasthuri2015saturated}. 
+This dataset is $5342 \times 3618 \times 338$ voxels in size. 
+The resolution of the dataset is $\SI[product-units=single]{3 x 3 x 30}{\nano\meter}^3$ per voxel. 
+We divide the dataset into two volumes (Vol. 1 and Vol. 2) along the $x$ dimension, where each volume is $\SI[product-units=single]{8.0 x 10.9 x 10.1}{\micro\meter}^3$.
+We train and validate our methods on Vol. 1 and test on Vol. 2.
+Our second dataset, called FlyEM, comes from the mushroom body of a 5-day old adult male \textit{Drosophila} fly imaged by a focused ion-beam milling scanning electron microscopy~\cite{takemura2017connectome}.
+The original dataset contains a $\SI[product-units=single]{40 x 50 x 120}{\micro\meter}^3$ volume with a resolution of $\SI[product-units=single]{10 x 10 x 10}{\nano\meter}^3$ per voxel. 
+We use two cubes (Vol. 1 and Vol. 2) of size $\SI[product-units=single]{10 x 10 x 10}{\micro\meter}^3$.
+
+\subsubsection{Method Configuration}
+
+\noindent\textbf{Input Segmentation.}
+The segmentation of the Kasthuri dataset is computed by agglomerating 3D supervoxels produced by the z-watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}. 
+We learn 3D affinities using MALIS loss with a U-Net~\cite{ronneberger2015u,Turaga:2009}. 
+We apply the z-watershed algorithm with suitable parameters to compute a 3D over-segmentation of the volume. 
+The resulting 3D oversegmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}.
+
+For the FlyEM data, based on the authors' suggestion~\cite{takemura2017connectome}, we apply a context-aware delayed agglomeration algorithm~\cite{10.1371/journal.pone.0125825} that shows improved performance on this dataset over the pipeline used in the original publication.
+This segmentation framework learns voxel and supervoxel classifiers with an emphasis to minimize under-segmentation error. 
+The algorithm first computes multi-channel 3D predictions for membranes, cell interiors, and mitochondria, among other cell features. 
+The membrane prediction channel is used to produce an oversegmented volume using 3D watershed, which is then agglomerated hierarchically up to a certain confidence threshold. 
+We used exactly the same parameters as the publicly available code for this algorithm.
+\\~\\
+\noindent\textbf{Graph Generation.}
+The two parameters for the graph pruning algorithm (Sec.~\ref{sec:skeletonization}) are $t_{low}$ and $t_{high}$. 
+Ideally, our graph will have an edge for every over-segmented pair of labels with few edges between correctly segmented pairs. 
+After considering various thresholds, we find that $t_{low} = \SI{210}{\nano\meter}$ and $t_{high} = \SI{300}{\nano\meter}$ produce expressive graphs with a scalable number of nodes and edges.
+During implementation, we use nanometers instead of voxels for these thresholds to have uniform units across all datasets.
+\\~\\
+\noindent\textbf{Edge Weight Learning.}
+\label{sec:network-parameters}
+We use half of the Kasthuri dataset for training and validation. 
+We train on 80\% of the potential merge candidates for this volume.
+We validate the CNN classifier on the remaining 20\% of the candidates. 
+Since our input does not require the image data, we can train on the anisotropic Kasthuri data and test on the isotropic FlyEM data.
+\\~\\
+\noindent\textbf{Training Augmentation.}
+Since our input is an existing segmentation of the EM images, there are very few training examples compared to per-pixel classifiers that train on a unique window for each voxel. 
+The Kasthuri dataset represents a region of brain over $\SI[product-units=single]{800}{\micro\meter}^3$ in volume and only yields 640 positive merge examples and 4821 negative ones.
+To avoid overfitting our deep networks, we apply the following augmentations on the training examples.
+During a single batch, we randomly select ten positive and ten negative examples. 
+With probability 0.5, an example is reflected across the $xy$-plane. 
+We then rotate each example by a random angle between $0$ and $360$ degrees using nearest neighbor interpolation. 
+The supplemental material contains experiments demonstrating the benefits of this augmentation strategy.
+We have 20,000 such examples per epoch.
+
+\subsubsection{Error Metrics}
+\label{sec:variation-of-information}
+We evaluate the performance of the different methods using the split variation of information (VI)~\cite{meila2003comparing}.
+Given a ground truth labeling $GT$ and our automatically reconstructed segmentation $SG$, over- and under-segmentation are quantified by the conditional entropies $H(GT | SG)$ and $H(SG | GT)$, respectively.
+Since we are measuring the entropy between two clusterings, lower VI scores are better.
+The sum of these conditional entropies gives the total variation of information.
+
+We use precision and recall to evaluate the convolutional neural network and multicut outputs. 
+Since our method only corrects \textit{split errors}, we define a true positive as a pair of segments that are correctly merged together after our pipeline.
+
+\subsection{Results}
+
+In Fig.~\ref{fig:variation-of-information}, we show the VI results of the pixel-based reconstructions of the Kasthuri and FlyEM data (Sec.~\ref{sec:dataset}) for varying thresholds of agglomeration (green).
+We show comparisons to an oracle (blue) that correctly partitions the graph from our method based on ground truth.
+Scores closer to the origin are better for this metric, and in every instance our results (red) are below the green curve.
+We see improvements on each data with a reduction in total VI score of $10.4\%$ on the Kasthuri data and $8.9\%$ and $5.4\%$ on the FlyEM datasets.
+
+Fig.~\ref{fig:qualitative-results} (left) shows successful merges on the Kasthuri dataset. 
+Several of these examples combine multiple consecutive segments that span the volume.
+In the third example on the left we correct the over-segmentation of a dendrite and attached spine-necks.
+Fig.~\ref{fig:qualitative-results} (right) shows typical failure cases of our method (red circles).
+In two of these examples the algorithm correctly predicts several merges before a single error renders the segment as wrong.
+In the third example (blue circle) a merge error in the initial segmentation propagates to our output.
+We now analyze how each major component of our method contributes to this final result.
+
+\begin{figure}[t]
+	\begin{minipage}{0.45\linewidth}
+		\centering
+		\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-correct1.png}
+		\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-correct2.png}
+		\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-correct3.png}
+		\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-correct4.png}
+		\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-correct5.png}
+	\end{minipage}
+	\begin{minipage}{0.45\linewidth}
+		\centering
+		\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-incorrect1.png}
+		\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-incorrect2.png}
+		\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-incorrect3.png}
+		\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-incorrect4.png}
+	\end{minipage}
+	\caption{(left) Segments of neurons before they were correctly merged by our method.
+(right) Circles indicate areas of wrong merges by our method (red) or by the initial pixel-based segmentation (blue).}
+	\label{fig:qualitative-results}
+\end{figure}
+
+\subsubsection{Empirical Ablation Studies}
+
+\noindent\textbf{Graph Generation.}
+Table \ref{table:skeletonization} shows the results of pruning the skeleton graph using the algorithm discussed in Sec.~\ref{sec:skeletonization}. 
+This edge pruning is essential for the graph partitioning algorithm, which has a non-linear computational complexity dependence on the number of edges. 
+The baseline algorithm considers all adjacent regions for merging. 
+Our method removes a significant portion of these candidates while maintaining a large number of the true merge locations (e.g., 764 compared to 974). 
+Our pruning heuristic removes at least $3.5\times$ the number of edges on all datasets, achieving a maximum removal rate of $4.15\times$.
+However, there are some adjacent over-segmented labels which are not considered.
+
+\begin{table*}
+	\caption{The results of our graph pruning approach compared to the baseline graph with all adjacent regions.
+We show the number of true merge locations (e.g., 974) compared to total number of edges in the graph (e.g., 25,798) for each case.
+The number of missed splits corresponds to the number of split errors that our method misses compared to an adjacency matrix.}
+	\resizebox{0.75\linewidth}{!}{
+		\begin{tabular}{c c c c c} \hline
+			\textbf{Dataset} & \textbf{Segment Adjacency} & \textbf{Skeleton Pruning} & \textbf{Missed Splits} & \textbf{Gained Edges} \\ \hline
+			Kasthuri & 974 / 25,798 & 764 / 6,218 & 307 & 97 \\
+			FlyEM Vol. 1 & 304 / 15,949 & 212 / 4,578 & 105 & 13 \\
+			FlyEM Vol. 2 &  298 / 17,614 & 197 / 4,366 & 120 & 19 \\ \hline
+		\end{tabular}
+	}
+	\centering
+	\label{table:skeletonization}
+\end{table*}
+
+We generate edges in our graph by using information from the skeletons. 
+In particular, we do not enforce the constraint that edges in our graph correspond to adjacent segments.
+Although neurons are continuous, the EM images often have noisy spots which cause an interruption in the input segmentation.
+We still want to reconstruct these neurons despite the fact that the initial segmentation is non-continuous. 
+The second and fourth examples in Fig.~\ref{fig:qualitative-results} show correctly reconstructed neurons where two of the segments are non-adjacent. 
+\\~\\
+\noindent\textbf{Failure Cases}
+There are some pairs of segments which we do not consider for merging because of our reliance on the skeletons.
+Fig.~\ref{fig:skeleton-results} shows two such cases with the closest endpoints circled. 
+In the right example the small segment is carved from the larger segment in a location where there are no skeleton endpoints. 
+There are on average 177 such examples in our datasets.
+\\~\\
+\noindent\textbf{Edge Weight Learning}
+%\subsubsection{Inference Augmentation}
+%\noindent\textbf{Inference Augmentation.}
+Data augmentation at test time can improve accuracy results~\cite{lee2017superhuman,zeng2017deepem3d}.
+When computing the probability to merge two segments, we randomly rotate and flip the examples three times (in the same fashion as training augmentation).
+Fig.~\ref{fig:receiver-operating-characteristic} shows the receiver operating characteristic (ROC) curve of our CNN classifier for all test datasets.
+As shown by the ROC curve, the test results on the FlyEM data are better than the results for Kasthuri.
+In part this comes from the disparity in the number of positive to negative merge candidates in the two graphs. 
+The network easily classifies most of the negative examples leaving only a few difficult examples to predict.
+Since there are more negative examples in relation to the positive examples in the FlyEM data, the ROC curve is greater.
+
+\begin{figure}[t!]
+	\centering
+	\begin{minipage}{0.45\linewidth}
+		\includegraphics[width=\linewidth]{./figures/merge_candidate1.png}	
+	\end{minipage}
+	\hfill
+	\begin{minipage}{0.45\linewidth}	
+		\includegraphics[width=\linewidth]{./figures/merge_candidate2.png}
+	\end{minipage}
+	\begin{minipage}{0.45\linewidth}
+		\includegraphics[width=\linewidth]{./figures/merge_candidate3.png}
+	\end{minipage}
+	\begin{minipage}{0.45\linewidth}
+		\includegraphics[width=\linewidth]{./figures/merge_candidate4.png}
+	\end{minipage}
+	\caption{The top two examples correspond to segment pairs that we incorrectly prune from the graph.
+The distance between the circled endpoints is too great.
+The bottom two examples show pairs of segments that belong to the same neuron but are not adjacent in the input segmentation.
+However, we correctly merge these pairs.}
+	\label{fig:skeleton-results}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.9\linewidth]{./figures/receiver-operating-characteristic.png}
+	\caption{The receiver operating characteristic (ROC) curves of our classifier on three connectomics datasets. The classifier works best on previously unseen data of the Kasthuri volume.}
+	\label{fig:receiver-operating-characteristic}
+\end{figure}
+
+%\subsection{Graph Optimization Results}
+\noindent\textbf{Graph Partition}
+The graph optimization strategy using multicut increases accuracy over using just the CNN.
+Table \ref{table:multicut} shows the changes in precision, recall, and accuracy for all three datasets compared to the CNN with both the multicut and lifted multicut formulations.
+The precision increases on each dataset, although the recall decreases on each datasets.
+Since it is more difficult to correct merge errors than split errors, it is often desirable to sacrifice recall for precision.
+Over the three testing datasets, applying a graph-based partitioning strategy increased the precision by $31.9\%$, $40.9\%$, and $27.8\%$ respectively.
+
+\begin{table*}[h]
+	\caption{Precision, recall, and accuracy changes between CNN only and CNN paired with graph-optimized reconstructions for the training and three test datasets.
+The combined method results in better precision and accuracy.
+The lifted multicut extension provides very slight improvements in recall and accuracy over these three datasets.}
+	\centering
+	\resizebox{0.75\linewidth}{!}{
+		\begin{tabular}{c c c c | c c c} \hline
+			& \multicolumn{3}{c}{\textbf{Multicut}} & \multicolumn{3}{c}{\textbf{Lifted Multicut}} \\ \hline
+			\textbf{Dataset} & $\Delta$ \textbf{Precision} & $\Delta$ \textbf{Recall} & $\Delta$ \textbf{Accuracy} & $\Delta$ \textbf{Precision} & $\Delta$ \textbf{Recall} & $\Delta$ \textbf{Accuracy} \\ \hline
+			Kasthuri  & 31.94\% & -36.24\% & 0.71\% & -1.01\% & 0.60\% & 0.02\% \\
+			FlyEM Vol. 1 & 40.87\% & -42.37\% & 1.26\% & 0.35\% & 0.85\% & 0.04\%  \\
+			FlyEM Vol. 2 & 27.80\% & -44.95\% & 0.33\% & 0.54\% & 0.92\% & 0.04\% \\ \hline
+		\end{tabular}
+	}
+	\label{table:multicut}
+\end{table*}

### 2018-05-02 papers/quals2018/6_compression.tex
papers: restructured layout into two sections

--- 2018-05-01 papers/quals2018/6_compression.tex
@@
-\section{Compression}
+% !TEX root =  paper.tex
+\section{Compression of Label Volumes}
+
+An often overlooked aspect of these segmentation datasets is how to efficiently store the label volumes.
+These label volumes are often 32- or 64-bit to account for the massive number of neurons that interweave through a cubic millimeter.
+Uncompressed, a cubic millimeter of segmentation data is nearly 20 petabytes.
+Thus, compression techniques are needed for fast transmission and cost-efficient storage.
+
+\subsection{Related Works}
+
+General-purpose compression schemes~\cite{collet2016smaller,deutsch1996zlib,google2016brotli,lehmann2016liblzf,oberhumer2005lzo,pavlov2007lzma,seward1998bzip2,vandevenne2016zopfli,welch1984technique,ziv1978compression} are not optimized for this data.
+With Compresso, an algorithm published in MICCAI 2017, we exploit the typical characteristics of label volumes such as large invariant regions without natural relationship between label values. 
+These properties render 2D image compression schemes inadequate since they rely on frequency reduction (using e.g., wavelet or discrete cosine transform) and value prediction of pixels based on local context (differential pulse-code modulation)~\cite{roelofs1999png,skodras2001jpeg}.
+Color space optimization strategies in video codecs~\cite{aimar2005x264} also have no effect on label volumes, even though the spatial properties of a segmentation stack (\textit{z}-axis) are similar to the temporal properties of video data (time-axis).
+A compression scheme designed specifically for label volumes is part of the visualization software Neuroglancer~\cite{google2016compressed}. 
+This method exploits segmentation homogeneity by creating small blocks with $N$ labels and reducing local entropy to $\log_2{N}$ per pixel. 
+Lookup tables then decode the values $[0,N)$ to the original 64-bit labels.
+
+\subsection{Method}
 
@@
 	\begin{center}
-		\includegraphics[width=0.45\linewidth]{./figures/encoding_diagram_opt.pdf}
+		\begin{minipage}{0.45\linewidth}
+			\centering
+			\includegraphics[width=\linewidth]{./figures/encoding_diagram_opt.pdf}
+		\end{minipage}
 		\hspace{0.08\linewidth}
-		\includegraphics[width=0.45\linewidth]{./figures/window_values.pdf}
+		\begin{minipage}{0.45\linewidth}
+			\centering
+			\includegraphics[width=\linewidth]{./figures/window_values.pdf}
+		\end{minipage}
 	\end{center}	
@@
 
-An often overlooked aspect of these segmentation datasets is how to efficiently store the label volumes.
-These label volumes are often 32- or 64-bit to account for the massive number of neurons that interweave through a cubic millimeter.
-Uncompressed, a cubic millimeter of segmentation data is nearly 20 petabytes and oftentimes there are a series of saved interim segmentations.
-Simply put, compression techniques are needed for fast transmission and cost-efficient storage.
-
-General-purpose compression schemes~\cite{collet2016smaller,deutsch1996zlib,google2016brotli,lehmann2016liblzf,oberhumer2005lzo,pavlov2007lzma,seward1998bzip2,vandevenne2016zopfli,welch1984technique,ziv1978compression} are not optimized for this data.
-With Compresso, an algorithm published in MICCAI 2017, we exploit the typical characteristics of label volumes such as large invariant regions without natural relationship between label values. 
-These properties render 2D image compression schemes inadequate since they rely on frequency reduction (using e.g., wavelet or discrete cosine transform) and value prediction of pixels based on local context (differential pulse-code modulation)~\cite{roelofs1999png,skodras2001jpeg}.
-Color space optimization strategies in video codecs~\cite{aimar2005x264} also have no effect on label volumes, even though the spatial properties of a segmentation stack (\textit{z}-axis) are similar to the temporal properties of video data (time-axis).
-A compression scheme designed specifically for label volumes is part of the visualization software Neuroglancer~\cite{google2016compressed}. 
-This method exploits segmentation homogeneity by creating small blocks with $N$ labels and reducing local entropy to $\log_2{N}$ per pixel. 
-Lookup tables then decode the values $[0,N)$ to the original 64-bit labels.
-
+Published in MICCAI 2017, we proposed Compresso which is specifically designed for compression of EM label volumes.
 Compresso works by decoupling the two important components across the image stack: per-segment shape and per-pixel label.
@@
 
+\subsection{Results}
+
 Our compression scheme outperforms all existing methods.
 We follow our scheme with LZMA which uses sophisticated probabilistic bit prediction strategies and achieve ratios of $700\times$ on average.
-We compressed an 18 terabyte label volume of 100 microns cubed to 26.2 gigabytes, a ratio of $\sim670\times$.
+We compressed an 18 terabyte label volume of 100 microns cubed to 26.2 gigabytes, a ratio of $\sim687\times$.

### 2018-05-02 papers/quals2018/1_compression.tex
paper: updated file names to match order

--- 2018-05-02 papers/quals2018/6_compression.tex
@@
 
-Published in MICCAI 2017, we proposed Compresso which is specifically designed for compression of EM label volumes.
+Published in MICCAI 2017, we proposed Compresso which is specifically designed for compression of EM label volumes~\cite{matejek2017compresso}.
 Compresso works by decoupling the two important components across the image stack: per-segment shape and per-pixel label.
@@
 Our compression scheme outperforms all existing methods.
-We follow our scheme with LZMA which uses sophisticated probabilistic bit prediction strategies and achieve ratios of $700\times$ on average.
+We follow our scheme with LZMA which uses sophisticated probabilistic bit prediction strategies and together they achieve ratios of $920\times$ on average.
+This outperforms existing strategies by over 80\%.
+The fundamental principles guiding Compresso are valid for a diverse set of segmentation datasets and we improve on existing methods for MRI and image segmentation datasets. 
 We compressed an 18 terabyte label volume of 100 microns cubed to 26.2 gigabytes, a ratio of $\sim687\times$.

### 2018-05-02 papers/quals2018/0_introduction.tex
quals:  minor updates to first four sections

@@
 At this resolution, we can see the axon terminals and dendritic spines, and the synaptic connections between them.
-Neuroscientists hope to further their understanding of the brain's underlying circuitry with accurate reconstructions of every neuron in these volumes and classification of the synaptic connections.
+Neuroscientists hope to further the understanding of the brain's underlying circuitry with accurate reconstructions of every neuron and classification of every synapse.
 
@@
 With an EM throughput of one terabyte per hour, neuroscientists can image a cubic millimeter of data (two petabytes) in six months~\cite{suissa2016automatic}. 
-At this scale, the manual reconstruction techniques of the 80s are simply infeasible.
-Thus, researchers rely on machine learning methods to segment these massive datasets.
+At this scale, the manual reconstruction techniques of the 80s are infeasible.
+Thus, researchers rely on machine learning methods to segment these massive datasets into label volumes (Fig.~\ref{fig:overview}).
+These label volumes assign a 32- or 64-bit integer to every voxel where voxels have the same label only if they belong to the same neuron.
 
-Automatic reconstruction produces label volumes that, uncompressed, are much larger in size than the already massive image datasets.
-These label volumes assign a 32- or 64-bit integer to every voxel where voxels have the same label only if they belong to the same neuron.
-In our paper published in \textit{MICCAI 2017}, we explore the effectiveness of existing general-purpose, image, and video compression techniques on the segmentation datasets.
-We find that these existing techniques fail to adequately exploit the typical properties of our label volumes.
-Thus, we propose \textit{Compresso}, a new compression algorithm specifically tailored for large label volumes that far exceeds existing strategies.
+Uncompressed, these label volumes are larger in size than the already massive image datasets.
+In our paper published in \textit{MICCAI 2017}, we explore the effectiveness of existing general-purpose, image, and video compression techniques on these segmentation datasets~\cite{matejek2017compresso}.
+We find that these existing techniques fail to adequately exploit the typical properties of these label volumes.
+Thus, we propose \textit{Compresso}, a new compression algorithm specifically tailored for large segmentation datasets, which achieves better compression ratios than all existing methods.
 
@@
 	\includegraphics[width=\linewidth]{./figures/proposal-header.png}
-	\caption{From an EM image stack, 3D CNNs generate affinities between voxels (left).
-These affinities are agglomerated into superpixels which in turn are merged to form a complete segmentation (center).
-Oftentimes these methods produce errors and thus require error correction to improve the accuracy (right).}
+	\caption{From an EM image stack, 3D convolutional neural networks generate affinities between voxels (left).
+A watershed algorithm agglomerates the voxels into supervoxels using these affinities, and these supervoxels are further merged to form a complete segmentation (center).
+These methods often produce errors and require error correction algorithms to improve the accuracy (right).}
 	\label{fig:overview}
@@
 Automatic reconstruction techniques need to be fast, scalable, and accurate.
-Ideally, image acquisition is the bottleneck of the connectomics pipeline so reconstruction occurs at a rate of one terabyte per hour~\cite{haehn2017scalable}.
+Ideally, image acquisition is the bottleneck of the connectomics pipeline so reconstruction should occur at a rate of one terabyte per hour~\cite{haehn2017scalable}.
 We can achieve this throughput with parallelization among several GPUs with existing techniques~\cite{funke2017deep,parag2017anisotropic}.
@@
 
-We propose a novel region merging framework that takes as input an oversegmentation of an EM volume (under review, \textit{ECCV 2018}).
+We propose a novel region merging framework that takes as input an oversegmentation of an EM image stack (under review, \textit{ECCV 2018}).
 Our method imposes both local and global biological constraints onto the output segmentation to more closely match the underlying structure of neuronal processes.
-Additionally, our method is independent of image resolution and acquisition parameters, enabling its application to isotropic and anisotropic data without retraining.
+Additionally, our method is independent of image resolution and acquisition parameters, enabling its application to isotropic and anisotropic datasets without retraining.
 Images generated by electron microscopes often differ in appearance because of variations in staining techniques~\cite{briggman2012volume}.

### 2018-05-02 papers/quals2018/1_compression.tex
quals:  minor updates to first four sections

@@
 % !TEX root =  paper.tex
+\begin{figure*}[t]
+	\begin{center}
+		\begin{minipage}{0.48\linewidth}
+			\centering
+			\includegraphics[width=0.9\linewidth]{./figures/encoding_diagram_opt.pdf}
+		\end{minipage}
+		\begin{minipage}{0.48\linewidth}
+			\centering
+			\includegraphics[width=0.9\linewidth]{./figures/window_values.pdf}
+		\end{minipage}
+	\end{center}	
+	\caption{Compresso works by dividing up the segmentation data into small blocks.
+On the left we show the intersection of three segments in a $4\times4\times1$ window.
+We extract a boundary map from this segmentation to transform the window into an integral value between $0$ and $2^{16} - 1$.
+This window has an encoded value of 50,978 $(2^1 + 2^5 + 2^8 + 2^9 + 2^{10} + 2^{14} + 2^{15})$.
+The location $i$ requires some additional bookkeeping.
+On the right are the $100$ most common $8 \times 8 \times 1$ windows accounting for $\sim82\%$ of the volume on a representative dataset.}
+	\label{fig:compression}
+\end{figure*}
+
 \section{Compression of Label Volumes}
@@
 General-purpose compression schemes~\cite{collet2016smaller,deutsch1996zlib,google2016brotli,lehmann2016liblzf,oberhumer2005lzo,pavlov2007lzma,seward1998bzip2,vandevenne2016zopfli,welch1984technique,ziv1978compression} are not optimized for this data.
-With Compresso, an algorithm published in MICCAI 2017, we exploit the typical characteristics of label volumes such as large invariant regions without natural relationship between label values. 
+These methods do not exploit the typical characteristics of label volumes such as large invariant regions without natural relationship between label values. 
 These properties render 2D image compression schemes inadequate since they rely on frequency reduction (using e.g., wavelet or discrete cosine transform) and value prediction of pixels based on local context (differential pulse-code modulation)~\cite{roelofs1999png,skodras2001jpeg}.
@@
 
-\begin{figure*}[t]
-	\begin{center}
-		\begin{minipage}{0.45\linewidth}
-			\centering
-			\includegraphics[width=\linewidth]{./figures/encoding_diagram_opt.pdf}
-		\end{minipage}
-		\hspace{0.08\linewidth}
-		\begin{minipage}{0.45\linewidth}
-			\centering
-			\includegraphics[width=\linewidth]{./figures/window_values.pdf}
-		\end{minipage}
-	\end{center}	
-	\caption{Compresso works by dividing up the segmentation data into small blocks.
-On the left we show the intersection of three segments in a $4\times4\times1$ window.
-We extract a boundary map from this segmentation to transform the window into an integral value between $0$ and $2^{16} - 1$.
-The location $i$ requires some additional bookkeeping.
-On the right are the $100$ most common $8 \times 8 \times 1$ windows accounting for $\sim82\%$ of the volume on a representative dataset.}
-	\label{fig:compression}
-\end{figure*}
-
-Published in MICCAI 2017, we proposed Compresso which is specifically designed for compression of EM label volumes~\cite{matejek2017compresso}.
+We propose Compresso, which is specifically designed for compression of EM label volumes~\cite{matejek2017compresso}.
 Compresso works by decoupling the two important components across the image stack: per-segment shape and per-pixel label.
 To encode the segment shapes, we consider the boundary pixels between two segments. 
-Removing the per-pixel labels, we produce a boundary map for each slice where a pixel $(x, y, z)$ is 1 if either pixel at $(x + 1, y, z)$ or $(x, y + 1, z)$ belongs to a different segment (Fig~\ref{fig:compression}, left).
+Removing the per-pixel labels, we produce a boundary map for each slice where a pixel $(x, y, z)$ is 1 if either pixel at $(x + 1, y, z)$ or $(x, y + 1, z)$ belongs to a different segment (Fig.~\ref{fig:compression}, left).
 The boundary map is divided into non-overlapping congruent 3D windows. If there are $n$ pixels per window, each window $w$ is assigned an integer $V_w \in [0, 2^n)$ where $V_w$ is defined as:
@@
 This is fewer than the initial number of bits so long as $N \leq 2^{n - 1}$.  
+Therefore, when compressing the label volumes, we can store $f(V_w)$ for every window as well as a lookup function for the $N$ unique $f(V_w)$ values to the original integral value.
 
@@
 By design, all pixels in the same segment have the same label so we store only one label per segment for each slice. 
-We use a connected-component labeling algorithm to store one label per segment \cite{he2009fast}. 
-The algorithm labels all pixels clustered within a component $m$ from $M$ section labels.
+We use a connected-component labeling algorithm to identify each component and store one label per segment \cite{he2009fast}.
 
@@
 Any boundary pixel $(x, y, z)$ with a non-boundary neighbor at $(x - 1, y, z)$ or $(x, y - 1, z)$ shares the same per-pixel label. 
-If both relevant neighbors are boundaries (i.e., like pixel $i$ in Fig.~\ref{fig:compression}) we extract the value we had stored.
+If both relevant neighbors are boundaries (i.e., like pixel $i$ in Fig.~\ref{fig:compression}) we extract the value we previously stored.
 

### 2018-05-02 papers/quals2018/2_error_correction.tex
quals:  minor updates to first four sections

--- 2018-05-02 papers/quals2018/2_method.tex
@@
 Automatic reconstruction methods need to be fast enough to scale to petabyte datasets while still maintaining a high-level of accuracy.
-The most accurate methods, like flood-filling networks~\cite{januszewski2016flood}, are too slow to scale. 
+The most accurate methods, like flood-filling networks~\cite{januszewski2016flood}, are currently far too slow.
 Unfortunately, methods that can scale to petabyte datasets typically rely on only local context and can produce errors at scale~\cite{haehn2017scalable}. 
@@
 These input segmentations can contain two types of errors.
-In a \textit{split error}, one neurons contains multiple labels.
+In a \textit{split error}, one neuron contains multiple labels.
 In a \textit{merge error}, two or more neurons receive the same label.
@@
 \end{figure*}
+
+For our proposed method (Fig.~\ref{fig:teaser_pipeline}), from the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with weights $w_e$. 
+The nodes correspond to labeled segments from the input data with edges between merge candidates.
+We propose the following three steps to formulate and then partition the graph while obeying constraints from the underlying biology.
+First, we only consider merging segments based on a skeletonized representation of the input segmentation (Fig.~\ref{fig:teaser_pipeline}a).
+This enables us to reduce the number of edges in the graph based on prior knowledge on the shape of neuronal processes.
+Second, we train a convolutional neural network that learns biological constraints based on the shapes of the input segmentation (Fig.~\ref{fig:teaser_pipeline}b).
+This network generates probabilities that segments belong to the same neuron based only on the segmentations. 
+An example of one such learned constraint is that neurons have small turning radii (Fig.~\ref{fig:turn-radii}).
+Third, we partition the graph using a lifted multicut formulation with additional acyclic constraints to enforce global biological constraints (Fig.~\ref{fig:teaser_pipeline}c).
+The lifted multicut solution is globally consistent which we then augment to produce a tree-structured graph.
 
@@
 
-For our proposed method (Fig.~\ref{fig:teaser_pipeline}), from the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with weights $w_e$. 
-The nodes correspond to labeled segments from the input data with edges between merge candidates.
-We propose the following three steps to formulate and then partition the graph while obeying constraints from the underlying biology.
-First, we only consider merging segments based on a skeletonized representation of the input segmentation (Fig.~\ref{fig:teaser_pipeline}a).
-This enables us to reduce the number of edges in the graph based on prior knowledge on the shape of neuronal processes.
-Second, we train a convolutional neural network that learns biological constraints based on the shapes of the input segmentation (Fig.~\ref{fig:teaser_pipeline}b).
-This network generates probabilities that segments belong to the same neuron based only on the segmentations. 
-An example of one such learned constraint is that neurons have small turning radii (Fig.~\ref{fig:turn-radii}).
-Third, we partition the graph using a lifted multicut formulation with additional acyclic constraints to enforce global biological constraints (Fig.~\ref{fig:teaser_pipeline}c).
-The lifted multicut solution is globally consistent which we then augment to produce a tree-structured graph.
-
 \subsubsection{Skeleton-Based Graph Generation}
 \label{sec:skeletonization}
+
 Most region merging methods create a region graph by removing small-sized segments and linking each pair of adjacent segments, which can still lead to a large graph size due to the irregular shape of neural structures.
@@
 
-\begin{figure}[t]
-	\centering
-	\begin{minipage}{0.32\linewidth}
-		\includegraphics[width=\linewidth]{./figures/split_error1.png}		
-	\end{minipage}
-	\hfill
-	\begin{minipage}{0.32\linewidth}
-		\includegraphics[width=\linewidth]{./figures/split_error2.png}				
-	\end{minipage}
-	\hfill
-	\begin{minipage}{0.32\linewidth}
-		\includegraphics[width=\linewidth]{./figures/split_error3.png}
-	\end{minipage}
-	\caption{Three erroneously split segments.}
-	\label{fig:merge_candidates}
-\end{figure}
 \subsubsection{Optimization-Based Graph Partition}
@@
 \end{align}
-where $\beta$ is a tunable parameter that encourages over- or under-segmentation. 
+where $\beta$ is a tunable parameter that encourages over or undersegmentation. 
 Since, there are many more lifted edges than adjacent edges, we scale down the lifted weights proportionally to their total number  
@@
 
-\begin{figure*}[t!]
+\begin{figure}[t]
 	\centering
-	\includegraphics[width=0.32\linewidth]{./figures/benchmark/voi-Kasthuri-Luigi-Test.pdf}
-	\includegraphics[width=0.32\linewidth]{./figures/benchmark/voi-FlyEM-Vol--1.pdf}
-	\includegraphics[width=0.32\linewidth]{./figures/benchmark/voi-FlyEM-Vol--2.pdf}
-	\caption{Segmentation benchmark results on three volumes.
-We compare our method (red) to the baseline segmentation (green) and an oracle (blue) that optimally partitions our constructed graph from our method.
-Lower VI scores are better.
-Our method improves the segmentation accuracy over the baseline in all cases.
-		Note that our model is only trained on the Kasthuri training volume and it generalizes well to the FlyEM dataset.}
-	\label{fig:variation-of-information}
-\end{figure*}
+	\begin{minipage}{0.32\linewidth}
+		\includegraphics[width=\linewidth]{./figures/split_error1.png}		
+	\end{minipage}
+	\hfill
+	\begin{minipage}{0.32\linewidth}
+		\includegraphics[width=\linewidth]{./figures/split_error2.png}				
+	\end{minipage}
+	\hfill
+	\begin{minipage}{0.32\linewidth}
+		\includegraphics[width=\linewidth]{./figures/split_error3.png}
+	\end{minipage}
+	\caption{Three erroneously split segments. In each instance, the skeletons for each segment have nearby endpoints indicating a split error.}
+	\label{fig:merge_candidates}
+\end{figure}
 
@@
 For the FlyEM data, based on the authors' suggestion~\cite{takemura2017connectome}, we apply a context-aware delayed agglomeration algorithm~\cite{10.1371/journal.pone.0125825} that shows improved performance on this dataset over the pipeline used in the original publication.
-This segmentation framework learns voxel and supervoxel classifiers with an emphasis to minimize under-segmentation error. 
+This segmentation framework learns voxel and supervoxel classifiers with an emphasis to minimize undersegmentation error. 
 The algorithm first computes multi-channel 3D predictions for membranes, cell interiors, and mitochondria, among other cell features. 
@@
 The two parameters for the graph pruning algorithm (Sec.~\ref{sec:skeletonization}) are $t_{low}$ and $t_{high}$. 
-Ideally, our graph will have an edge for every over-segmented pair of labels with few edges between correctly segmented pairs. 
+Ideally, our graph will have an edge for every oversegmented pair of labels with few edges between correctly segmented pairs. 
 After considering various thresholds, we find that $t_{low} = \SI{210}{\nano\meter}$ and $t_{high} = \SI{300}{\nano\meter}$ produce expressive graphs with a scalable number of nodes and edges.
-During implementation, we use nanometers instead of voxels for these thresholds to have uniform units across all datasets.
+During implementation, we use nanometers instead of voxels to standardize units across all datasets.
 \\~\\
@@
 Since our input does not require the image data, we can train on the anisotropic Kasthuri data and test on the isotropic FlyEM data.
-\\~\\
+
 \noindent\textbf{Training Augmentation.}
@@
 We then rotate each example by a random angle between $0$ and $360$ degrees using nearest neighbor interpolation. 
-The supplemental material contains experiments demonstrating the benefits of this augmentation strategy.
 We have 20,000 such examples per epoch.
@@
 \label{sec:variation-of-information}
-We evaluate the performance of the different methods using the split variation of information (VI)~\cite{meila2003comparing}.
-Given a ground truth labeling $GT$ and our automatically reconstructed segmentation $SG$, over- and under-segmentation are quantified by the conditional entropies $H(GT | SG)$ and $H(SG | GT)$, respectively.
+We evaluate the performance of the different methods using the split variation of information (VI) score~\cite{meila2003comparing}.
+Given a ground truth labeling $GT$ and our automatically reconstructed segmentation $SG$, over and undersegmentation are quantified by the conditional entropies $H(GT | SG)$ and $H(SG | GT)$, respectively.
 Since we are measuring the entropy between two clusterings, lower VI scores are better.
@@
 Since our method only corrects \textit{split errors}, we define a true positive as a pair of segments that are correctly merged together after our pipeline.
+
+\begin{figure*}[t!]
+	\centering
+	\includegraphics[width=0.32\linewidth]{./figures/benchmark/voi-Kasthuri-Luigi-Test.pdf}
+	\includegraphics[width=0.32\linewidth]{./figures/benchmark/voi-FlyEM-Vol--1.pdf}
+	\includegraphics[width=0.32\linewidth]{./figures/benchmark/voi-FlyEM-Vol--2.pdf}
+	\caption{Segmentation benchmark results on three volumes.
+We compare our method (red) to the baseline segmentation (green) and an oracle (blue) that optimally partitions our constructed graph from our method.
+Lower VI scores are better.
+Our method improves the segmentation accuracy over the baseline in all cases.
+		Note that our model is only trained on the Kasthuri training volume and it generalizes well to the FlyEM datasets.}
+	\label{fig:variation-of-information}
+\end{figure*}
 
@@
 We now analyze how each major component of our method contributes to this final result.
+
+\subsubsection{Empirical Ablation Studies}
+
+\noindent\textbf{Graph Generation.}
+Table \ref{table:skeletonization} shows the results of pruning the skeleton graph using the algorithm discussed in Sec.~\ref{sec:skeletonization}. 
+This edge pruning is essential for the graph partitioning algorithm, which has a non-linear computational complexity dependence on the number of edges. 
+The baseline algorithm considers all adjacent regions for merging. 
+Our method removes a significant portion of these candidates while maintaining a large number of the true merge locations (e.g., 764 compared to 974). 
+Our pruning heuristic removes at least $3.5\times$ the number of edges on all datasets, achieving a maximum removal rate of $4.15\times$.
+However, there are some adjacent oversegmented labels which are not considered.
+
+\begin{table*}
+	\caption{The results of our graph pruning approach compared to the baseline graph with all adjacent regions.
+We show the number of true merge locations (e.g., 974) compared to total number of edges in the graph (e.g., 25,798) for each case.
+The number of missed splits corresponds to the number of split errors that our method misses compared to an adjacency matrix.}
+	\resizebox{0.75\linewidth}{!}{
+		\begin{tabular}{c c c c c} \hline
+			\textbf{Dataset} & \textbf{Segment Adjacency} & \textbf{Skeleton Pruning} & \textbf{Missed Splits} & \textbf{Gained Edges} \\ \hline
+			Kasthuri & 974 / 25,798 & 764 / 6,218 & 307 & 97 \\
+			FlyEM Vol. 1 & 304 / 15,949 & 212 / 4,578 & 105 & 13 \\
+			FlyEM Vol. 2 &  298 / 17,614 & 197 / 4,366 & 120 & 19 \\ \hline
+		\end{tabular}
+	}
+	\centering
+	\label{table:skeletonization}
+\end{table*}
 
@@
 
-\subsubsection{Empirical Ablation Studies}
-
-\noindent\textbf{Graph Generation.}
-Table \ref{table:skeletonization} shows the results of pruning the skeleton graph using the algorithm discussed in Sec.~\ref{sec:skeletonization}. 
-This edge pruning is essential for the graph partitioning algorithm, which has a non-linear computational complexity dependence on the number of edges. 
-The baseline algorithm considers all adjacent regions for merging. 
-Our method removes a significant portion of these candidates while maintaining a large number of the true merge locations (e.g., 764 compared to 974). 
-Our pruning heuristic removes at least $3.5\times$ the number of edges on all datasets, achieving a maximum removal rate of $4.15\times$.
-However, there are some adjacent over-segmented labels which are not considered.
-
-\begin{table*}
-	\caption{The results of our graph pruning approach compared to the baseline graph with all adjacent regions.
-We show the number of true merge locations (e.g., 974) compared to total number of edges in the graph (e.g., 25,798) for each case.
-The number of missed splits corresponds to the number of split errors that our method misses compared to an adjacency matrix.}
-	\resizebox{0.75\linewidth}{!}{
-		\begin{tabular}{c c c c c} \hline
-			\textbf{Dataset} & \textbf{Segment Adjacency} & \textbf{Skeleton Pruning} & \textbf{Missed Splits} & \textbf{Gained Edges} \\ \hline
-			Kasthuri & 974 / 25,798 & 764 / 6,218 & 307 & 97 \\
-			FlyEM Vol. 1 & 304 / 15,949 & 212 / 4,578 & 105 & 13 \\
-			FlyEM Vol. 2 &  298 / 17,614 & 197 / 4,366 & 120 & 19 \\ \hline
-		\end{tabular}
-	}
-	\centering
-	\label{table:skeletonization}
-\end{table*}
-
 We generate edges in our graph by using information from the skeletons. 
@@
 \\~\\
-\noindent\textbf{Failure Cases}
+\noindent\textbf{Failure Cases.}
 There are some pairs of segments which we do not consider for merging because of our reliance on the skeletons.
-Fig.~\ref{fig:skeleton-results} shows two such cases with the closest endpoints circled. 
+Fig.~\ref{fig:skeleton-results}, top, shows two such cases with the closest endpoints circled. 
 In the right example the small segment is carved from the larger segment in a location where there are no skeleton endpoints. 
@@
 \\~\\
-\noindent\textbf{Edge Weight Learning}
-%\subsubsection{Inference Augmentation}
-%\noindent\textbf{Inference Augmentation.}
-Data augmentation at test time can improve accuracy results~\cite{lee2017superhuman,zeng2017deepem3d}.
-When computing the probability to merge two segments, we randomly rotate and flip the examples three times (in the same fashion as training augmentation).
+\noindent\textbf{Edge Weight Learning.}
 Fig.~\ref{fig:receiver-operating-characteristic} shows the receiver operating characteristic (ROC) curve of our CNN classifier for all test datasets.
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=0.9\linewidth]{./figures/receiver-operating-characteristic.png}
-	\caption{The receiver operating characteristic (ROC) curves of our classifier on three connectomics datasets. The classifier works best on previously unseen data of the Kasthuri volume.}
-	\label{fig:receiver-operating-characteristic}
-\end{figure}
-
 %\subsection{Graph Optimization Results}
@@
 Over the three testing datasets, applying a graph-based partitioning strategy increased the precision by $31.9\%$, $40.9\%$, and $27.8\%$ respectively.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.9\linewidth]{./figures/receiver-operating-characteristic.png}
+	\caption{The receiver operating characteristic (ROC) curves of our classifier on three connectomics datasets. The classifier works best on previously unseen data of the Kasthuri volume.}
+	\label{fig:receiver-operating-characteristic}
+\end{figure}
 

### 2018-05-02 papers/quals2018/3_proposed.tex
quals:  minor updates to first four sections

--- 2018-05-02 papers/quals2018/5_proposed.tex
@@
 
-There are significantly more biological constraints that we plan to use in the future.
+There is significant room for further research in the compression of label volumes.
+Compresso currently uses windows of size $8 \times 8 \times 1$ based on empirical evidence that these 2D shapes outperform 3D ones.
+However, there is certainly more information we can exploit across the stack.
+Window values in slice $z$ are highly correlated with the corresponding windows in the slices above and below.
+Thus, we can reduce the number of bits stored for these windows.
+For example, consider a window $w$ in slice $z$ where its neighbors in slices $z - 1$ and $z + 1$ have window values of 0 (i.e., no boundary pixels in the window).
+The window in $z$ will have value 0 with very high probability.
+
+There are significantly more biological constraints that we plan to use in the future for region merging and error correction.
 Once we improve our synaptic classifiers, we can ensure that we do not merge dendritic spines with axons. 
@@
 However, we plan to prune these candidates more efficiently using a skeleton based method that considers the underlying biology.
-Skeletons corresponding to undersegmented labels will have junctions at the failed merge (Fig.~\ref{fig:proposed}). 
+Skeletons corresponding to undersegmented labels will have junctions at the failed merge (Fig.~\ref{fig:proposal}). 
 This greatly reduces the search space and will enable correcting split errors in a fraction of the current time.
@@
 	\includegraphics[width=0.8\linewidth]{./figures/split-proposal.png}
-	\caption{An example where the input segmentation incorrectly merged two neurons together. The black circle indicates the junction from the skeletonized representation.}
+	\caption{An example where the input segmentation incorrectly merged two neurons together. The red circle indicates the junction from the skeletonized representation.}
 	\label{fig:proposal}
@@
 This watershed algorithm will provide two seeds on opposite sides of the discovered junction.
-The surface separating the two segments is our ``split'' candidate.
+The surface separating the two segments output by the watershed algorithm is our ``split'' candidate.
 We will extract a cubic region of interest around this candidate and input the region into our previously discussed merge classifier.
 If the classifier suggests that the segments belong to one neuron, we will ignore the split candidate.
-Otherwise we will divide this segment based on the candidate.
+Otherwise we will divide this segment based on the watershed result.
 With a synaptic classifier, we can further constrain the watershed algorithm to only propose splits where pre- or post-synaptic connections occur on one side.

### 2018-05-02 papers/miccai2017/sections/evaluation.tex
miccai: fixed paper references to be in order

@@
 %\appName followed by LZMA compresses the SPL Brain Atlas data by nearly a factor of 640x. 
-The Berkeley Segmentation and PASCAL Visual Object Class datasets are two very common benchmarks in image segmentation~\cite{MartinFTM01,pascal-voc-2012}.
+The Berkeley Segmentation and PASCAL Visual Object Class datasets are two very common benchmarks in image segmentation~\cite{pascal-voc-2012,MartinFTM01}.
 Currently these datasets use GZIP and PNG compression but \appName with LZMA can improve on them by a factor of over 10x and 5x respectively.

### 2018-05-02 papers/miccai2017/sections/introduction.tex
miccai: fixed paper references to be in order

@@
 
-Connectomics---reconstructing the wiring diagram of a mammalian brain at nanometer resolution---results in datasets at the scale of petabytes~\cite{suissapeleg2016,haehn_dojo_2014}.
-Machine learning methods find cell membranes and create cell body labelings for every neuron~\cite{ronneberger2015u,liu2014modular,GALA2014} (Fig.~\ref{fig:data}).
+Connectomics---reconstructing the wiring diagram of a mammalian brain at nanometer resolution---results in datasets at the scale of petabytes~\cite{haehn_dojo_2014,suissapeleg2016}.
+Machine learning methods find cell membranes and create cell body labelings for every neuron~\cite{liu2014modular,GALA2014,ronneberger2015u} (Fig.~\ref{fig:data}).
 %aims to reconstruct the wiring diagram of a mammalian brain at nanometer resolution. This results in datasets at the scale of petabytes~\cite{suissapeleg2016}. 
@@
 The literature currently lacks efficient compression of label volumes. 
-General-purpose compression schemes~\cite{deutsch1996zlib,ziv1978compression,lehmann2016liblzf,oberhumer2005lzo,welch1984technique,seward1998bzip2,pavlov2007lzma,vandevenne2016zopfli,google2016brotli,collet2016smaller} are not optimized for this data.
+General-purpose compression schemes~\cite{collet2016smaller,deutsch1996zlib,google2016brotli,lehmann2016liblzf,oberhumer2005lzo,pavlov2007lzma,seward1998bzip2,vandevenne2016zopfli,welch1984technique,ziv1978compression} are not optimized for this data.
 In this paper, we exploit the typical characteristics of label volumes such as large invariant regions without natural relationship between label values. 

### 2018-05-02 papers/eccv2018/4_results.tex
fixed some consistency issues

@@
 
-\noindent\textbf{Graph Generation.}
+\noindent\textbf{Graph Generation}
 Table \ref{table:skeletonization} shows the results of pruning the skeleton graph using the algorithm discussed in Sec.~\ref{sec:skeletonization}. 

### 2018-05-02 papers/eccv2018/paper.tex
minor edits to first few sections, removed all red Xs
quals: added first draft for qualifying exam proposals
fixed some consistency issues

@@
 %An agglomerative segmentation algorithm merges initial pair of clusters.
-Current state-of-the-art connectome reconstruction pipelines have two major steps: initial pixel-based segmentation with affinity prediction and watershed transform, and refined segmentation by merging oversegmented regions.
-%In the past deTraditionally, neuron segmentation from 3D electron microscopy (EM)
+Current state-of-the-art connectome reconstruction pipelines have two major steps: initial pixel-based segmentation with affinity prediction and watershed transform, and refined segmentation by merging over-segmented regions.
 For the region merging, most methods neglect geometric and topological constraints that are inherent in the graph structure of neural wiring diagrams.

### 2018-05-02 papers/quals2018/4_conclusions.tex
quals: final proposal

--- 2018-03-14 papers/eccv2018/5_conclusions.tex
@@
 
-We present a novel method for improved neuronal reconstruction in connectomics that extends existing pixel-based reconstruction strategies using skeletonized 3D networks. 
+Several challenges arise as the acquisition speeds for EM images improve and enable image stacks petabytes in size.
+Currently, automatic reconstruction techniques segment these image stacks into label volumes where each individual neuron receives a unique label.
+However, these label volumes are larger than the input image data because of the number of unique neurons in volumes of this size.
+Thus, one major challenge is how to efficiently store these large label volumes.
+We propose Compresso, which exploits properties unique to these datasets, and outperforms existing methods in terms of compression ratio.
+
+Current state-of-the-art reconstruction algorithms that are fast enough to scale often rely on local context for merging and are agnostic to the underlying biology.
+We introduce a novel region merging algorithm that uses biological constraints at the local and global level to improve oversegmentations of these image stacks.
+We extract a graph from the oversegmentation and rely on a geometric prior on the shape of neuronal processes to prune the edges in the graph.
+A CNN learns edge weights based on the local region around two segments.
+We produce an improved segmentation from this graph by reformulating the partitioning problem as a multicut one and applying global constraints to the solution.
 We show significant accuracy improvements on datasets from two different species. 
@@
 For example, we could then enforce the constraint that a given segment only has post- or pre-synaptic connections. 
-
-An augmented graph would also be helpful for splitting improperly merged segments by adding additional terms to the partitioning cost function. 
+An augmented graph would be helpful for splitting improperly merged segments by adding additional terms to the partitioning cost function. 
 Using skeletons we can apply biological constraints on the topology for neurons that are improperly merged.
-Finally, we believe that the benefits of top-down enhancements from graph optimization can extend beyond connectomics to other domains, such as medical image segmentation.

### 2018-05-02 papers/quals2018/2_error_correction.tex
quals: removed periods from paragraph headers

@@
 
-\noindent\textbf{Input Segmentation.}
+\noindent\textbf{Input Segmentation}
 The segmentation of the Kasthuri dataset is computed by agglomerating 3D supervoxels produced by the z-watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}. 
@@
 \\~\\
-\noindent\textbf{Graph Generation.}
+\noindent\textbf{Graph Generation}
 The two parameters for the graph pruning algorithm (Sec.~\ref{sec:skeletonization}) are $t_{low}$ and $t_{high}$. 
@@
 \\~\\
-\noindent\textbf{Edge Weight Learning.}
+\noindent\textbf{Edge Weight Learning}
 \label{sec:network-parameters}
@@
 
-\noindent\textbf{Training Augmentation.}
+\noindent\textbf{Training Augmentation}
 Since our input is an existing segmentation of the EM images, there are very few training examples compared to per-pixel classifiers that train on a unique window for each voxel. 
@@
 \\~\\
-\noindent\textbf{Failure Cases.}
+\noindent\textbf{Failure Cases}
 There are some pairs of segments which we do not consider for merging because of our reliance on the skeletons.
@@
 \\~\\
-\noindent\textbf{Edge Weight Learning.}
+\noindent\textbf{Edge Weight Learning}
 Fig.~\ref{fig:receiver-operating-characteristic} shows the receiver operating characteristic (ROC) curve of our CNN classifier for all test datasets.

### 2018-05-24 papers/eccv2018/rebuttal/paper.tex
skeleton: allow locations close to border

--- 2018-05-02 papers/eccv2018/paper.tex
@@
 \usepackage{amsmath,amssymb} % define this before the line numbering.
-\usepackage{ruler}
+%\usepackage{ruler}
 \usepackage{color}
@@
 \mainmatter
-\def\ECCV18SubNumber{534}  % Insert your submission number here
 
-\titlerunning{ECCV-18 submission ID \ECCV18SubNumber}
-
-\authorrunning{ECCV-18 submission ID \ECCV18SubNumber}
-%\title{Scalable Graph-Based Neural \\ Reconstruction for Connectomics}
-%\title{Biologically-Constrained 3D Agglomeration for Connectome Reconstruction}
+%\titlerunning{Biologically-Constrained Region Merging for Connectome Reconstruction}
+%\authorrunning{B. Matejek et al.}
 \title{Biologically-Constrained Region Merging for Connectome Reconstruction}
 
-\author{Anonymous ECCV submission}
-\institute{Paper ID \ECCV18SubNumber}
+%\author{Brian Matejek, Daniel Haehn, Donglai Wei, Toufiq Parag, Hanspeter Pfister}
+%\institute{Harvard University, Cambridge, MA 02138, USA\\
+%	\email{bmatejek,haehn,donglai,paragt,pfister@seas.harvard.edu}}
 
@@
 
-\begin{abstract}
-% maybe better to cut to the point
-%Advancements in electron microscopy image acquisition have created connectomics datasets terabytes in size making manual reconstruction of neuronal structures infeasible.
-%In the past decade in Connectomics, much progress has been made to classify neural membranes or affinities from the raw pixel and to watershed transform them into initial segments.
-%Current state-of-the-art automatic methods classify neural membranes or affinities from the raw pixel followed by agglomeration methods to create full neuron reconstructions.
-%An agglomerative segmentation algorithm merges initial pair of clusters.
-Current state-of-the-art connectome reconstruction pipelines have two major steps: initial pixel-based segmentation with affinity prediction and watershed transform, and refined segmentation by merging over-segmented regions.
-For the region merging, most methods neglect geometric and topological constraints that are inherent in the graph structure of neural wiring diagrams.
-In this work, we use a biologically-constrained graph-based method to better reconstruct neural pathways.
-Given the initial segmentation, we first create a graph with nodes corresponding to segment labels and edges identifying potential locations of split errors based on the skeleton structure of the segmentation.
-Next, we train a convolutional neural network to capture the geometric properties of segment connections and produce edge weights as the probability of merging two nodes.
-Finally, we formulate the region merging as a lifted multicut partitioning problem with topological constraints to avoid cycles.
-We demonstrate the performance of our approach on multiple real-world connectomics datasets with an average variation of information improvement of 8.2\%.
-\keywords{connectomics, biological constraints, region merge, skeletonization, deep learning, lifted multicut}
-\end{abstract}
-
-\input{0_introduction}
-
-\input{1_related_work}
-
-\input{2_method}
-
-\input{3_evaluation}
-
-\input{4_results}
-
-\input{5_conclusions}
-
-\clearpage
+Hello World
 

### 2018-05-24 cnns/analysis.py

@@ -63,7 +63,7 @@ class Architecture:
 
 
 def ParseResults(filename):
-    prefix = filename.split('/')[-1].split('.')[0].strip('skeleton')[1:-24]
+    prefix = filename.split('/')[-1].strip('skeleton-').replace('.results', '').split('-')[0]
 
     # open the results filename
     with open(filename, 'r') as fd:

### 2018-05-24 cnns/skeleton/generate_features.py

@@ -145,13 +145,15 @@ def GenerateFeatures(prefix, threshold, maximum_distance, network_distance, endp
                 if distance < smallest_distances[(label, neighbor_label)]:
                     midpoint = (endpoint.GridPoint() + neighbor_endpoint.GridPoint()) / 2
 
+                    ## FOR CREMI REMOVE THE VALID LOCATION REQUIREMENT
+
                     # make sure the bounding box fits
-                    valid_location = True
-                    for dim in range(NDIMS):
-                        if midpoint[dim]-network_radii[dim] < 0: valid_location = False
-                        if midpoint[dim]+network_radii[dim] > grid_size[dim]: valid_location = False
-                    if not valid_location: continue
-            
+                    # valid_location = True
+                    # for dim in range(NDIMS):
+                    #     if midpoint[dim]-network_radii[dim] < 0: valid_location = False
+                    #     if midpoint[dim]+network_radii[dim] > grid_size[dim]: valid_location = False
+                    # if not valid_location: continue
+
                     smallest_distances[(label,neighbor_label)] = distance
                     smallest_distances[(neighbor_label,label)] = distance
 
@@ -181,13 +183,23 @@ def GenerateFeatures(prefix, threshold, maximum_distance, network_distance, endp
         # extract a bounding box around this midpoint
         midz, midy, midx = midpoints[(label_one,label_two)]
 
-        extracted_segmentation = segmentation[midz-network_radii[IB_Z]:midz+network_radii[IB_Z],midy-network_radii[IB_Y]:midy+network_radii[IB_Y],midx-network_radii[IB_X]:midx+network_radii[IB_X]]
-        extracted_gold = gold[midz-network_radii[IB_Z]:midz+network_radii[IB_Z],midy-network_radii[IB_Y]:midy+network_radii[IB_Y],midx-network_radii[IB_X]:midx+network_radii[IB_X]]
+        zmin = max(0, midz - network_radii[IB_Z])
+        ymin = max(0, midy - network_radii[IB_Y])
+        xmin = max(0, midx - network_radii[IB_X])
+        zmax = min(zres - 1, midz + network_radii[IB_Z] + 1)
+        ymax = min(yres - 1, midy + network_radii[IB_Y] + 1)
+        xmax = min(xres - 1, midx + network_radii[IB_X] + 1)
+
+        extracted_segmentation = segmentation[zmin:zmax,ymin:ymax,xmin:xmax]
[…]

### 2018-05-24 cnns/skeleton/util.py

@@ -77,10 +77,35 @@ def ExtractFeature(segmentation, candidate, width, radii, augment=True):
     # get the data in a more convenient form
     zradius, yradius, xradius = radii
     zpoint, ypoint, xpoint = candidate.location
-    labels = candidate.labels
+    labels = list(candidate.labels)
+    random.shuffle(labels)
+    zres, yres, xres = segmentation.shape
 
-    # extract the small window from this segment
-    example = segmentation[zpoint-zradius:zpoint+zradius+1,ypoint-yradius:ypoint+yradius+1,xpoint-xradius:xpoint+xradius+1]
+    # get the min and max locations
+    zmin = max(0, zpoint - zradius)
+    ymin = max(0, ypoint - yradius)
+    xmin = max(0, xpoint - xradius)
+    zmax = min(zres - 1, zpoint + zradius + 1)
+    ymax = min(yres - 1, ypoint + yradius + 1)
+    xmax = min(xres - 1, xpoint + xradius + 1)
+
+    example = np.zeros((2 * zradius + 1, 2 * yradius + 1, 2 * xradius + 1), dtype=np.int32)
+    segment = segmentation[zmin:zmax,ymin:ymax,xmin:xmax]
+
+    if example.shape == segment.shape:
+        example = segment
+    else:
+        if zmin == 0: zstart = zradius - zpoint
+        else: zstart = 0
+
+        if ymin == 0: ystart = yradius - ypoint
+        else: ystart = 0
+
+        if xmin == 0: xstart = xradius - xpoint
+        else: xstart = 0
+
+        example[zstart:zstart+segment.shape[IB_Z],ystart:ystart+segment.shape[IB_Y],xstart:xstart+segment.shape[IB_X]] = segment
+
 
     # rescale the segment
     example = ScaleSegment(example, width, labels)

### 2018-05-24 graphics/animation.py

@@ -1,0 +1,88 @@
+import numpy as np
+import imageio
+
+from ibex.utilities.constants import *
+
+
+def ColorizeSlice(image):
+    yres, xres = image.shape
+
+    colored_image = np.zeros((yres, xres, 3), dtype=np.uint8)
+
+    colored_image[:,:,0] = (107 * image % 700) % 255
+    colored_image[:,:,1] = (509 * image % 900) % 255
+    colored_image[:,:,2] = (200 * image % 777) % 255
+
+    return colored_image
+
+
+def ColorizeStack(stack):
+    zres, yres, xres = stack.shape
+
+    output_stack = np.zeros((zres, yres, xres, 3), dtype=np.uint8)
+
+    for iz in range(zres):
+        output_stack[iz,:,:,:] = ColorizeSlice(stack[iz,:,:])
+        
+    return output_stack
+
+
+def MakeImage3D(image):
+    yres, xres = image.shape
+
+    output_image = np.zeros((yres, xres, 3), dtype=image.dtype)
+
+    output_image[:,:,0] = image
+    output_image[:,:,1] = image
+    output_image[:,:,2] = image
+
+    return output_image
+
+
+def MakeStack3D(stack):
+    zres, yres, xres = stack.shape
+
+    output_stack = np.zeros((zres, yres, xres, 3), dtype=stack.dtype)
+    output_stack[:,:,:,0] = stack
+    output_stack[:,:,:,1] = stack
+    output_stack[:,:,:,2] = stack
+
+    return output_stack
+
+
+def H52Gif(filename, stack, duration=0.5, axis=IB_Z):
+    images = []
+    
+    if len(stack.shape) != 4: stack = MakeStack3D(stack)
+    zres, yres, xres, _ = stack.shape
+
+    if axis == IB_Z:
+        for iz in range(zres):
+            images.append(stack[iz,:,:,:])
+    elif axis == IB_Y:
+        for iy in range(yres):
+            images.append(stack[:,iy,:,:])
+    elif axis == IB_X:
+        for ix in range(xres):
+            images.append(stack[:,:,ix,:])
+    imageio.mimsave(filename, images, duration=duration)
+
+
+def Images2Gif(filename, images, duration=0.5):
+    imageio.mimsave(filename, images, duration=duration)
+
+
+def Overlay(segmentation, image, alpha):
+    assert (segmentation.shape == image.shape)
+    if len(segmentation.shape) == 2:
[…]

### 2018-05-24 skeletonization/cpp-teaser_skeletons.cpp

@@ -16,7 +16,7 @@ static const int IB_NDIMS = 3;
 
 // variables for the rolling sphere
 
-static const double scale = 1.1;
+static const double scale = 5.1;
 static const double buffer = 80;
 static const long min_path_length = 45;
 

### 2018-05-24 skeletonization/teaser_skeletons.pyx

@@ -51,7 +51,7 @@ def GenerateTeaserSkeletons(prefix):
         # skip the zero label if it occurs
         if not label: continue
 
-        if (label > 130): continue
+        if not label == 19: continue
 
         # perform preprocessing on the segment
         start_time = time.time()

### 2018-05-24 utilities/dataIO.py

@@ -4,7 +4,8 @@ import numpy as np
 from ibex.data_structures import meta_data, skeleton_formats
 from ibex.utilities.constants import *
 from PIL import Image
-#import imageio
+import imageio
+import tifffile
 
 
 def GetWorldBBox(prefix):
@@ -125,5 +126,22 @@ def ReadImage(filename):
     return np.array(Image.open(filename))
 
 
-#def WriteImage(filename, image):
-#    imageio.imwrite(filename, image)
+def WriteImage(filename, image):
+   imageio.imwrite(filename, image)
+
+
+def H52Tiff(stack, output_prefix):
+    zres, _, _ = stack.shape
+
+    for iz in range(zres):
+        image = stack[iz,:,:]
+        tifffile.imsave('{}-{:05d}.tif'.format(output_prefix, iz), image)
+
+
+def H52PNG(stack, output_prefix):
+    zres, _, _ = stack.shape
+
+    for iz in range(zres):
+        image = stack[iz,:,:]
+        im = Image.fromarray(image)
+        im.save('{}-{:05d}.png'.format(output_prefix, iz))

### 2018-08-13 data_structures/skeleton.py
Updated skeletons to output numpy arrays when needed

@@ -12,6 +12,14 @@ class Skeleton:
         self.joints = joints
         self.endpoints = endpoints
 
+    def Endpoints2Array(self):
+        nendpoints = len(self.endpoints)
+
+        array = np.zeros((nendpoints, 3), dtype=np.int64)
+        for ie in range(nendpoints):
+            array[ie] = self.endpoints[ie]
+
+        return array
 
 
 class Skeletons:
@@ -44,6 +52,6 @@ class Skeletons:
                     ix = iv % xres
 
                     if endpoint: endpoints.append((iz, iy, ix))
-                    else: endpoints.append((iz, iy, ix))
+                    else: joints.append((iz, iy, ix))
 
-                skeletons.append(Skeleton(label, joints, endpoints))
+                self.skeletons.append(Skeleton(label, joints, endpoints))

### 2018-08-13 utilities/dataIO.py

@@ -76,7 +76,7 @@ def ReadImageData(prefix):
 
 
 def ReadSkeletons(prefix, skeleton_algorithm='thinning', downsample_resolution=(100, 100, 100), benchmark=False):
-    skeletons = Skeletons(prefix, skeleton_algorithm, downsample_resolution, benchmark)
+    skeletons = skeleton.Skeletons(prefix, skeleton_algorithm, downsample_resolution, benchmark)
 
     return skeletons
 

### 2018-08-13 papers/cvpr2019/0_introduction.tex
papers: added framework for CVPR 2019 submission

--- 2018-03-14 papers/eccv2018/0_introduction.tex
@@
 
-We can make use of both geometric and topological prior information to produce more accurate reconstructions matching the underlying biology (Fig.~\ref{fig:teaser_pipeline}).
+Due to their biological nature, these over-segmented regions are connected with specific geometric and topological properties. 
+For example, L-shaped junctions and arrow-shaped junctions are rare in neural structures.
+Additionally, neurons should not form cycles. 
+Thus, we can both use and learn these shape priors to produce more accurate region merging to match the underlying biology (Fig.~\ref{fig:teaser_pipeline}).
 

### 2018-08-13 papers/cvpr2019/1_related_work.tex
papers: added framework for CVPR 2019 submission

--- 2018-03-14 papers/eccv2018/1_related_work.tex
@@
 In both cases, available methods are pixel-based and do not include global biological constraints into the decision making process.
-Our method can be used as input to any existing error correction framework.
 % Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for traditional image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}.

### 2018-08-13 papers/cvpr2019/2_method.tex
papers: added framework for CVPR 2019 submission

--- 2018-03-19 papers/eccv2018/2_method.tex
@@
 
-For the input of the network, we extract a cubic region of interest (ROI) around each endpoint $e$ in $\mathbb{S}_c$ as input to the CNN. 
+For the input of the network, we extract a cubic region of interest (ROI) around each midpoint $e$ in $\mathbb{S}_c$ as input to the CNN. 
 The CNN receives three input channels for every voxel in the ROI around segments $l_1$ and $l_2$. 

### 2018-08-13 papers/cvpr2019/paper.tex
papers: added framework for CVPR 2019 submission

--- 2017-11-15 papers/cvpr2018/paper.tex
@@
 	%%%%%%%%% TITLE
-\title{Graph-Based Neural Reconstruction from Morphological Skeletons}
-
-%Robust Agglomeration using 3D Skeletonization of Labeled for Connectomics}
+	\title{Biologically-Constrained Region Merging for Connectome Reconstruction}
 
@@
 	\begin{abstract}
-Advancements in electron microscopy image acquisition have created massive connectomics datasets in the terabyte range that make manual reconstruction of neuronal structures infeasible. 
-Current state-of-the-art automatic methods segment neural membranes at the pixel level followed by agglomeration methods to create full neuron reconstructions. 
-However, these approaches widely neglect global geometric properties that are inherent in the graph structure of neural wiring diagrams.
-In this work, we follow bottom-up pixel-based reconstruction by a top-down graph-based method to more accurately approximate neural pathways. 
-Using the membrane labels of the pixel-based segmentation we first generate skeletons in 3D.
-Using this 3D graph we train automatic classifiers for shape description to detect impossible neural pathways by looking at geometric properties.
-We then apply efficient graph-based optimization strategies to improve the segmentation labels.
-We demonstrate the performance of our approach on multiple real-world connectomics datasets with an average variation of information improvement of \FIX{$X\times$}.
-%The paper provides insights into learning shape features for top-down graph-based neuron reconstruction.
+	Current state-of-the-art connectome reconstruction pipelines have two major steps: initial pixel-based segmentation with affinity prediction and watershed transform, and refined segmentation by merging over-segmented regions.
+	For the region merging, most methods neglect geometric and topological constraints that are inherent in the graph structure of neural wiring diagrams.
+	In this work, we use a biologically-constrained graph-based method to better reconstruct neural pathways.
+	Given the initial segmentation, we first create a graph with nodes corresponding to segment labels and edges identifying potential locations of split errors based on the skeleton structure of the segmentation.
+	Next, we train a convolutional neural network to capture the geometric properties of segment connections and produce edge weights as the probability of merging two nodes.
+	Finally, we formulate the region merging as a lifted multicut partitioning problem with topological constraints to avoid cycles.
+	We demonstrate the performance of our approach on multiple real-world connectomics datasets with an average variation of information improvement of 8.2\%.
 	\end{abstract}

### 2018-08-13 papers/cvpr2019/supplemental/skeleton-generation.tex
papers: added framework for CVPR 2019 submission

% !TEX root =  supplemental.tex
\section{Skeletonization}

There are three steps in our skeleton generation pipeline: downsampling, skeletonization, and upsampling. 
Here we explore the advantages and disadvantages of each step both qualitatively by visualing inspecting results and quantitatively by publishing a novel ``Skeleton Benchmark''. 
Lastly, we compare three widely used skeletonization algorithms against our benchmark to determine the relative efficiencies and accuracies on segmented neuronal data.

\subsection{Skeleton Pipeline}

First, we downsample the original image to a resolution of $t_{res}\si{\nm^3}$ where $t_{res}$ is a tunable parameter. 
We experiment with values of $t_{res}$ ranging from $30$ to $200$ and display the results in Sec.~\ref{skeleton-results}.
In general, topologically preserving downsampling is impossible~\cite{kraus2001topology} as holes can collapse when the width of a gap is smaller than the downsampling ratio.
This is particularly common on dendrites where multiple spines protrude closely.

There are two major benefits to downsampling the data before running the skeletonization algorithm.
First, the overall skeletonization running time greatly decreases as a function of downsample resolution.
Two of our baseline skeleton algorithms have running times linear in the number of voxels in the input segmentation.
The third uses Dijkstra's algorithm to find globally distance voxels to form branches of the skeleton ``tree''.
Therefore, the computational complexity is $\mathcal{O}(n \log{n})$ since the number of edges in a structured voxel grid is $\mathcal{O}(n)$.
Sec.~\ref{skeleton-results} further explores the running time of the skeleton algorithms as a function of downsample rate.
Second, downsampling reduces the number of spurious endpoints.
Our input segmentations often have noisy boundaries with small spikes protruding from the surface that do not represent larger dendritic spines.
Downsampling the input segmentations has a smoothing effect that eliminates these small bumps while

The second step is to run the actual skeletonization algorithm

The last step of the algorithm ``upsamples'' the skeleton to the resolution of the original image.
If we downsample in $x$, $y$, and $z$ by $down_x$, $down_y$, and $down_z$ respectively, we cannot merely take a skeleton joint at $(u, v, w)$ and identify $(down_x * u, down_y * v, down_z * w)$ as the upsampled joint since this point may not fall within the original label boundary.
It is during this process that we also identify which skeleton joints are also endpoints.

\subsection{Skeleton Benchmark}

We created a skeleton benchmark to evaluate three different skeletonization approaches with varying downsampling parameters.

\subsection{Skeleton Results}
\label{skeleton-results}

\paragraph{Endpoint Accuracy.}

\paragraph{Running Times.}

### 2018-08-21 skeletonization/benchmark.py
skeletonization: commit before updating topological methods

@@ -2,28 +2,45 @@ import struct
 
 import numpy as np
 
+from ibex.data_structures import skeleton
 from ibex.utilities import dataIO
 
 
 
 # read ground truth
-def SkeletonGroundTruth(prefix, cutoff=500):
-    directory = 'benchmarks/skeleton/{}'.format(prefix)
+def SkeletonGroundTruth(prefix, max_label, cutoff=500):
+    # read the mapping from example number to label
+    example_filename = 'benchmarks/skeleton/{}-skeleton-benchmark-examples.bin'.format(prefix)
+    with open(example_filename, 'rb') as fd:
+        input_cutoff, = struct.unpack('q', fd.read(8))
+        assert (cutoff == input_cutoff)
 
+        example_to_label = np.zeros(input_cutoff, dtype=np.int64)
+        for ie in range(input_cutoff):
+            example_to_label[ie], = struct.unpack('q', fd.read(8))
+
+    skeletons = [None] * max_label
+
+    # read the manually annotated ground truth
+    directory = 'benchmarks/skeleton/{}'.format(prefix)
     for iv in range(cutoff):
         filename = '{}/example-{}.pts'.format(directory, iv)
 
+        # create instance variables for future Skeleton object
+        label = example_to_label[iv]
+        joints = []
+        endpoints = []
+
         with open(filename, 'rb') as fd:
             npoints, = struct.unpack('q', fd.read(8))
-            
+
             for ip in range(npoints):
                 iz, iy, ix, = struct.unpack('qqq', fd.read(24))
+                endpoints.append((iz, iy, ix))
 
+        skeletons[label] = skeleton.Skeleton(label, joints, endpoints)
 
-
-# find the endpoints
-
-
+    return skeletons
 
 
 
@@ -38,17 +55,38 @@ def EvaluateSkeletons(prefix, cutoff=500, resolution=(100, 100, 100)):
 
 
 
+# create a list of endpoints to consider to finetune ground truth
+def InteractiveEditExamples(prefix, cutoff=500, resolution=(100, 100, 100)):
+    # read in the the thinning skeleton
+    thinning_skeletons = dataIO.ReadSkeletons(prefix, skeleton_algorithm='thinning', benchmark=True).skeletons
+    max_label = len(thinning_skeletons)
+
+    # read the ground truth skeletons
+    ground_truth_skeletons = SkeletonGroundTruth(prefix, max_label, cutoff)
+
+    # go through all labels
+    for label in range(max_label):
[…]

### 2018-08-21 skeletonization/cpp-generate_skeletons.cpp

@@ -6,6 +6,7 @@
 #include <math.h>
 #include <set>
 #include <map>
+#include <stack>
 #include <assert.h>
 #include "cpp-MinBinaryHeap.h"
 
@@ -113,8 +114,143 @@ static const long min_path_length = 2;
 
 
 
+
+// helper functions
+
+static void IndexToIndicies(long iv, long &ix, long &iy, long &iz)
+{
+    iz = iv / sheet_size;
+    iy = (iv - iz * sheet_size) / row_size;
+    ix = iv % row_size;
+}
+
+
+
+static long IndicesToIndex(long ix, long iy, long iz)
+{
+    return iz * sheet_size + iy * row_size + ix;
+}
+
+
+
+// find if a path exists between a source and target node
+static bool HasConnectedPath(long *input_segmentation, std::map<long, long> &down_to_up, long label, long source_index, long target_index, long up_zres, long up_yres, long up_xres)
+{
+    // get the ratio between the high resolution and the low resolution
+    float ratioz = (float)(up_zres) / zres;
+    float ratioy = (float)(up_yres) / yres;
+    float ratiox = (float)(up_xres) / xres;
+
+    // get the downsampled location of the source vertex
+    long iz = source_index / (yres * xres);
+    long iy = (source_index - iz * yres * xres) / xres;
+    long ix = source_index % xres;
+
+    // get the downsampled location of the target vertex
+    long ik = target_index / (yres * xres);
+    long ij = (target_index - ik * yres * xres) / xres;
+    long ii = target_index % xres;
+
+    // create upsampled bounds in which to find a path 
+    long zmin = (long) (ratioz * std::min(iz, ik) + 0.5);
+    long ymin = (long) (ratioy * std::min(iy, ij) + 0.5);
+    long xmin = (long) (ratiox * std::min(ix, ii) + 0.5);
+
+    long zmax = (long) (ratioz * (std::max(iz, ik) + 1) + 0.5);
+    long ymax = (long) (ratioy * (std::max(iy, ij) + 1) + 0.5);
+    long xmax = (long) (ratiox * (std::max(ix, ii) + 1) + 0.5);
+/*
+    printf("%ld %ld %ld\n", iz, iy, ix);
+    printf("%ld %ld %ld\n", ik, ij, ii);
+
+    printf("%ld %ld %ld\n", zmin, ymin, xmin);
+    printf("%ld %ld %ld\n", zmax, ymax, xmax);
+*/
[…]

### 2018-08-21 skeletonization/cpp-generate_skeletons.h

@@ -1,3 +1,3 @@
 void CppTopologicalThinning(const char *prefix, long resolution[3], const char *lookup_table_directory, bool benchmark);
 void CppTeaserSkeletonization(const char *prefix, long resolution[3], bool benchmark);
-void CppApplyUpsampleOperation(const char *prefix, long resolution[3], const char *skeleton_algorithm, bool benchmark);
+void CppApplyUpsampleOperation(const char *prefix, long *input_segmentation, long resolution[3], const char *skeleton_algorithm, bool benchmark);

### 2018-08-21 skeletonization/generate_skeletons.pyx

@@ -20,11 +20,14 @@ from medial_axis_util import PostProcess
 cdef extern from 'cpp-generate_skeletons.h':
     void CppTopologicalThinning(const char *prefix, long resolution[3], const char *lookup_table_directory, bool benchmark)
     void CppTeaserSkeletonization(const char *prefix, long resolution[3], bool benchmark)
-    void CppApplyUpsampleOperation(const char *prefix, long resolution[3], const char *skeleton_algorithm, bool benchmark)
+    void CppApplyUpsampleOperation(const char *prefix, long *input_segmentation, long resolution[3], const char *skeleton_algorithm, bool benchmark)
 
 
 # generate skeletons for this volume
 def TopologicalThinning(prefix, resolution=(100, 100, 100), benchmark=False):
+    if benchmark: input_segmentation = dataIO.ReadGoldData(prefix)
+    else: input_segmentation = dataIO.ReadSegmentationData(prefix)
+
     start_time = time.time()
 
     # convert to numpy array for c++ call
@@ -36,6 +39,10 @@ def TopologicalThinning(prefix, resolution=(100, 100, 100), benchmark=False):
 
     # call the topological skeleton algorithm
     CppTopologicalThinning(prefix, &(cpp_resolution[0]), lut_directory, benchmark)
+
+    # call the upsampling operation
+    cdef np.ndarray[long, ndim=3, mode='c'] cpp_input_segmentation = np.ascontiguousarray(input_segmentation, dtype=ctypes.c_int64)
+    CppApplyUpsampleOperation(prefix, &(cpp_input_segmentation[0,0,0]), &(cpp_resolution[0]), 'thinning', benchmark)
 
     print 'Topological thinning time for {}: {}'.format((resolution[0], resolution[1], resolution[2]), time.time() - start_time)
 
@@ -85,7 +92,7 @@ def MedialAxis(prefix, resolution=(100, 100, 100), benchmark=False):
     resolution = np.array(resolution, dtype=np.int64)
     cdef np.ndarray[long, ndim=1, mode='c'] cpp_resolution = np.ascontiguousarray(resolution, dtype=ctypes.c_int64)
 
-    CppApplyUpsampleOperation(prefix, &(cpp_resolution[0]), "medial-axis", benchmark)
+    #CppApplyUpsampleOperation(prefix, &(cpp_resolution[0]), "medial-axis", benchmark)
 
     print 'Medial axis thinning time for {}: {}'.format((resolution[0], resolution[1], resolution[2]), time.time() - start_time)
 

### 2018-08-21 skeletonization/setup.py

@@ -5,7 +5,7 @@ import numpy as np
 extensions = [
     Extension(
         name='generate_skeletons',
-        include_dirs=[np.get_include(), 'cpp-MinBinaryHeap.h'],
+        include_dirs=[np.get_include()],
         sources=['generate_skeletons.pyx', 'cpp-generate_skeletons.cpp', 'cpp-MinBinaryHeap.cpp'],
         extra_compile_args=['-O4', '-std=c++0x'],
         language='c++'

### 2018-08-21 papers/cvpr2019/supplemental/skeleton-generation.tex
papers: added supplemental for cvpr2019

@@
 
-The second step is to run the actual skeletonization algorithm
+The second step is to run the skeletonization algorithm.
+We test three different algorithms.
+As a baseline we use the built in \texttt{scipy:skeletonize\_3d} function that implements the medial surface/axis thinning algorithm of Lee et al.~\cite{lee1994building}.
+This thinning algorithm preserves the topology and uses various post-processing techniques to reduce noise.
+Second, we implement the TEASER skeletonization algorithm from Sato et al.~\cite{sato2000teasar}. 
+This algorithm does not preserve topology but has shown promising results on various biomedical segmentations and variants of the strategy have been used on connectomics label volumes before~\cite{konstantin2018efficient,zhao2014automatic}.
+Lastly, we implement, with the help of the author, a sequential curve-thinning algorithm based on isthmuses~\cite{palagyi2014sequential}.
+This fast algorithm preserves topology and uses efficient lookup tables to reduce unnecessary computation.
 
@@
 
-We created a skeleton benchmark to evaluate three different skeletonization approaches with varying downsampling parameters.
+We created a skeleton benchmark to evaluate the three different skeletonization approaches with varying downsampling parameters.
+We identify all of the endpoint locations
 

### 2018-08-21 algorithms/lifted_multicut.pyx

@@ -69,13 +69,13 @@ def LiftedMulticut(prefix, candidates, edge_weights, beta, threshold, heuristic)
     maintain_edges = np.asarray(tmp_collapsed_edges).astype(dtype=np.bool)
     
     ncandidates = len(candidates)
-    labels = np.zeros(ncandidates, dtype=np.uint8)
-    for ie, candidate in enumerate(candidates):
-        labels[ie] = candidate.ground_truth
+    #labels = np.zeros(ncandidates, dtype=np.uint8)
+    #for ie, candidate in enumerate(candidates):
+    #    labels[ie] = candidate.ground_truth
 
-    print '\nAfter Multicut\n'
+    #print '\nAfter Multicut\n'
 
-    PrecisionAndRecall(labels, 1 - maintain_edges)
+    #PrecisionAndRecall(labels, 1 - maintain_edges)
 
     # collapse the edges returned from multicut
     output_filename = 'multicuts/{}-{:0.2f}-lifted.results'.format(prefix, beta)

### 2018-08-21 algorithms/multicut.pyx

@@ -50,13 +50,13 @@ def Multicut(prefix, candidates, edge_weights, beta, threshold, heuristic):
     maintain_edges = np.asarray(tmp_collapsed_edges).astype(dtype=np.bool)
     
     ncandidates = len(candidates)
-    labels = np.zeros(ncandidates, dtype=np.uint8)
-    for ie, candidate in enumerate(candidates):
-        labels[ie] = candidate.ground_truth
+    #labels = np.zeros(ncandidates, dtype=np.uint8)
+    #for ie, candidate in enumerate(candidates):
+    #    labels[ie] = candidate.ground_truth
 
-    print '\nAfter Multicut\n'
+    #print '\nAfter Multicut\n'
 
-    PrecisionAndRecall(labels, 1 - maintain_edges)
+    #PrecisionAndRecall(labels, 1 - maintain_edges)
 
     # collapse the edges returned from multicut
     output_filename = 'multicuts/{}-{:0.2f}.results'.format(prefix, beta)
@@ -70,6 +70,6 @@ def Multicut(prefix, candidates, edge_weights, beta, threshold, heuristic):
 def RunMulticut(prefix, model_prefix, threshold, maximum_distance, endpoint_distance, network_distance, beta, heuristic=1):
     # read the candidates
     candidates, edge_weights = RetrieveCandidates(prefix, model_prefix, threshold, maximum_distance, endpoint_distance, network_distance)
-
+    
     # run the multicut algorithm
     Multicut(prefix, candidates, edge_weights, beta, threshold, heuristic)

### 2018-08-21 algorithms/util.py

@@ -5,15 +5,16 @@ import ibex.cnns.skeleton.util
 from ibex.evaluation.classification import *
 from ibex.data_structures import unionfind
 from ibex.transforms import seg2seg
-
-
+from ibex.utilities import dataIO
+from ibex.evaluation import comparestacks
 
 def RetrieveCandidates(prefix, model_prefix, threshold, maximum_distance, endpoint_distance, network_distance):
     # get all of the candidates for this brain
     positive_candidates = ibex.cnns.skeleton.util.FindCandidates(prefix, threshold, maximum_distance, endpoint_distance, network_distance, 'positive')
     negative_candidates = ibex.cnns.skeleton.util.FindCandidates(prefix, threshold, maximum_distance, endpoint_distance, network_distance, 'negative')
-
-    candidates = positive_candidates + negative_candidates
+    undetermined_candidates = ibex.cnns.skeleton.util.FindCandidates(prefix, threshold, maximum_distance, endpoint_distance, network_distance, 'undetermined')
+    
+    candidates = positive_candidates + negative_candidates + undetermined_candidates
     ncandidates = len(candidates)
 
     # read the probabilities foor this candidate
@@ -26,11 +27,11 @@ def RetrieveCandidates(prefix, model_prefix, threshold, maximum_distance, endpoi
             edge_weights[iv], = struct.unpack('d', fd.read(8))
 
     # print the statistics
-    print '\nCNN Precision and Recall\n'
-    labels = np.zeros(ncandidates, dtype=np.uint8)
-    for ie, candidate in enumerate(candidates):
-        labels[ie] = candidate.ground_truth
-    PrecisionAndRecall(labels, Prob2Pred(edge_weights))
+    #print '\nCNN Precision and Recall\n'
+    #labels = np.zeros(ncandidates, dtype=np.uint8)
+    #for ie, candidate in enumerate(candidates):
+    #    labels[ie] = candidate.ground_truth
+    #PrecisionAndRecall(labels, Prob2Pred(edge_weights))
 
     return candidates, edge_weights
 
@@ -90,3 +91,11 @@ def CollapseGraph(segmentation, candidates, maintain_edges, probabilities, outpu
         fd.write(struct.pack('q', ncandidates))
         for ie in range(ncandidates):
             fd.write(struct.pack('?', maintain_edges[ie]))
+
+    mapping = np.zeros(max_value, dtype=np.int64)
[…]

### 2018-08-21 cnns/analysis.py

@@ -63,7 +63,7 @@ class Architecture:
 
 
 def ParseResults(filename):
-    prefix = filename.split('/')[-1].strip('skeleton-').replace('.results', '').split('-')[0]
+    prefix = '-'.join(filename.split('skeleton-')[1].split('-')[:-4])
 
     # open the results filename
     with open(filename, 'r') as fd:

### 2018-08-21 cnns/skeleton/forward.py

@@ -58,7 +58,8 @@ def Forward(prefix, model_prefix, threshold, maximum_distance, endpoint_distance
     # get the candidate locations 
     positive_candidates = FindCandidates(prefix, threshold, maximum_distance, endpoint_distance, network_distance, 'positive')
     negative_candidates = FindCandidates(prefix, threshold, maximum_distance, endpoint_distance, network_distance, 'negative')
-    candidates = positive_candidates + negative_candidates
+    undetermined_candidates = FindCandidates(prefix, threshold, maximum_distance, endpoint_distance, network_distance, 'undetermined')
+    candidates = positive_candidates + negative_candidates + undetermined_candidates
     ncandidates = len(candidates)
     
     # compute augmentations
@@ -68,21 +69,23 @@ def Forward(prefix, model_prefix, threshold, maximum_distance, endpoint_distance
     probabilities /= (naugmentations)
     predictions = Prob2Pred(np.squeeze(probabilities))
 
-    # create an array of labels
-    labels = np.zeros(ncandidates, dtype=np.uint8)
-    for ie, candidate in enumerate(candidates):
-        labels[ie] = candidate.ground_truth
-
-    # write the precision and recall values
-    output_filename = '{}-{}-{}-{}nm-{}nm-{}nm.results'.format(model_prefix, prefix, threshold, maximum_distance, endpoint_distance, network_distance)
-    PrecisionAndRecall(labels, predictions, output_filename)
-
+    
     output_filename = '{}-{}-{}-{}nm-{}nm-{}nm.probabilities'.format(model_prefix, prefix, threshold, maximum_distance, endpoint_distance, network_distance)
     with open(output_filename, 'wb') as fd:
         fd.write(struct.pack('i', ncandidates))
         for probability in probabilities:
             fd.write(struct.pack('d', probability))
 
+    # create an array of labels
+    candidates = positive_candidates + negative_candidates
+    ncandidates = len(candidates)
+    labels = np.zeros(ncandidates, dtype=np.uint8)
+    for ie, candidate in enumerate(candidates):
+        labels[ie] = candidate.ground_truth
+
+    # write the precision and recall values
+    output_filename = '{}-{}-{}-{}nm-{}nm-{}nm.results'.format(model_prefix, prefix, threshold, maximum_distance, endpoint_distance, network_distance)
+    PrecisionAndRecall(labels, predictions[:ncandidates], output_filename)
 
         
[…]

### 2018-08-21 cnns/skeleton/generate_features.py

@@ -39,14 +39,13 @@ def SaveCandidates(output_filename, candidates):
 
 
 @jit(nopython=True)
-def FindNeighboringCandidates(segmentation, centroid, candidates, maximum_distance, network_distance, world_res):
+def FindNeighboringCandidates(segmentation, centroid, candidates, maximum_distance, world_res):
     # useful variables
     zres, yres, xres = segmentation.shape
     max_label = np.amax(segmentation) + 1
 
     # get the radii and label for this centroid
     radii = np.int64((maximum_distance / world_res[IB_Z], maximum_distance / world_res[IB_Y], maximum_distance / world_res[IB_X]))
-    network_radii = np.int64((network_distance / world_res[IB_Z], network_distance / world_res[IB_Y], network_distance / world_res[IB_X]))
     label = segmentation[centroid[IB_Z],centroid[IB_Y],centroid[IB_X]]
 
     # iterate through all the pixels close to the centroid
@@ -106,7 +105,7 @@ def GenerateFeatures(prefix, threshold, maximum_distance, network_distance, endp
         # find the candidates near this endpoint
         candidates = set()
         candidates.add(0)
-        FindNeighboringCandidates(thresholded_segmentation, centroid, candidates, maximum_distance, network_distance, world_res)
+        FindNeighboringCandidates(thresholded_segmentation, centroid, candidates, maximum_distance, world_res)
 
         for candidate in candidates:
             # skip extracellular
@@ -145,15 +144,7 @@ def GenerateFeatures(prefix, threshold, maximum_distance, network_distance, endp
                 if distance < smallest_distances[(label, neighbor_label)]:
                     midpoint = (endpoint.GridPoint() + neighbor_endpoint.GridPoint()) / 2
 
-                    ## FOR CREMI REMOVE THE VALID LOCATION REQUIREMENT
-
-                    # make sure the bounding box fits
-                    # valid_location = True
-                    # for dim in range(NDIMS):
-                    #     if midpoint[dim]-network_radii[dim] < 0: valid_location = False
-                    #     if midpoint[dim]+network_radii[dim] > grid_size[dim]: valid_location = False
-                    # if not valid_location: continue
-
+                    # find the closest pair of endpoints
                     smallest_distances[(label,neighbor_label)] = distance
[…]

### 2018-08-21 cnns/skeleton/train.py

@@ -136,7 +136,7 @@ def SkeletonNetwork(parameters, width):
     DenseLayer(model, 1, 0.5, 'sigmoid', False)
 
     if optimizer == 'adam': opt = Adam(lr=initial_learning_rate, decay=decay_rate, beta_1=betas[0], beta_2=betas[1], epsilon=1e-08)
-    elif optimizer == 'nesterov': opt = SGD(lr=initial_learning_rate, decay=decay_rate, momentum=0.9, nesterov=True)
+    elif optimizer == 'nesterov': opt = SGD(lr=initial_learning_rate, decay=decay_rate, momentum=0.99, nesterov=True)
     model.compile(loss=loss_function, optimizer=opt, metrics=['mean_squared_error', 'accuracy'])
     
     return model
@@ -282,7 +282,7 @@ def Train(prefix, model_prefix, threshold, maximum_distance, endpoint_distance, 
     history = model.fit_generator(SkeletonCandidateGenerator(prefix, network_distance, positive_candidates[:positive_cutoff], negative_candidates[:negative_cutoff], parameters, width),\
                     (examples_per_epoch / batch_size), epochs=2500, verbose=1, class_weight=weights, callbacks=callbacks,\
                     validation_data=SkeletonCandidateGenerator(prefix, network_distance, positive_candidates[positive_cutoff:], negative_candidates[negative_cutoff:], parameters, width), \
-                    validation_steps=(examples_per_epoch / batch_size), initial_epoch=starting_epoch)
+                    validation_steps=(examples_per_epoch / batch_size) / 10, initial_epoch=starting_epoch)
 
     # save the fully trained model
     model.save_weights('{}.h5'.format(model_prefix))

### 2018-08-21 cnns/superres/__init__.py

@@ -1,0 +1,3 @@
+# import files from this directory
+from train import Train
+from generate_features import GenerateFeatures

### 2018-08-21 cnns/superres/generate_features.py

@@ -1,0 +1,53 @@
+import numpy as np
+
+from ibex.utilities import dataIO
+from ibex.utilities.constants import *
+
+
+def GenerateFeatures(prefix):
+    # find the level of anisotropy
+    resolution = dataIO.Resolution(prefix)
+    zy = resolution[IB_Z] / resolution[IB_Y]
+    zx = resolution[IB_Z] / resolution[IB_X]
+
+    # assert isotropy in xy
+    assert (zy == zx)
+
+    # read the image 
+    image = dataIO.ReadImageData(prefix)
+    zres, yres, xres = image.shape
+
+    zx_slice = image[:,0,:]
+    zy_slice = image[:,:,0]
+
+    dataIO.WriteImage('{}-zx.png'.format(prefix), zx_slice)
+    dataIO.WriteImage('{}-zy.png'.format(prefix), zy_slice)
+
+    
+    
+    return
+    
+    for iv in range(zy):
+        xcut = image[:,:,iv::zx]
+        ycut = image[:,:,iv::zy]
+
+        xfilename = 'super_resolution/{}-x-{}.h5'.format(prefix, iv + 1)
+        yfilename = 'super_resolution/{}-y-{}.h5'.format(prefix, iv + 1)
+        
+        dataIO.WriteH5File(xcut, xfilename, 'main')
+        dataIO.WriteH5File(ycut, yfilename, 'main')
+
+        for iz in range(zres):
+            xslice = xcut[iz,:,:]
+            yslice = ycut[iz,:,:]
+            zslice = image[iz,:,:]
+            
+            xfilename = 'super_resolution/images/{}-x-{}-{:04d}.png'.format(prefix, iv + 1, iz)
+            yfilename = 'super_resolution/images/{}-y-{}-{:04d}.png'.format(prefix, iv + 1, iz)
+            zfilename = 'super_resolution/images/{}-z-{:04d}.png'.format(prefix, iz)
+            
+            dataIO.WriteImage(xfilename, xslice)
+            dataIO.WriteImage(yfilename, yslice)
+            dataIO.WriteImage(zfilename, zslice)
+            
+        break

### 2018-08-21 cnns/superres/train.py

@@ -1,0 +1,60 @@
+
+
+
+from keras.models import Model
+from keras.optimizers import Adam
+from keras.layers import Convolution2D, Concatenate, Dropout, Input, MaxPooling2D, UpSampling2D
+
+def SimpleNet(input_size):
+    inputs = Input(input_size)
+    conv1 = Convolution2D(64, 3, activation = 'relu', padding = 'same', kernel_initializer = 'he_normal')(inputs)
+    conv1 = Convolution2D(64, 3, activation = 'relu', padding = 'same', kernel_initializer = 'he_normal')(conv1)
+    pool1 = MaxPooling2D(pool_size=(2, 2))(conv1)
+    conv2 = Convolution2D(128, 3, activation = 'relu', padding = 'same', kernel_initializer = 'he_normal')(pool1)
+    conv2 = Convolution2D(128, 3, activation = 'relu', padding = 'same', kernel_initializer = 'he_normal')(conv2)
+    pool2 = MaxPooling2D(pool_size=(2, 2))(conv2)
+    conv3 = Convolution2D(256, 3, activation = 'relu', padding = 'same', kernel_initializer = 'he_normal')(pool2)
+    conv3 = Convolution2D(256, 3, activation = 'relu', padding = 'same', kernel_initializer = 'he_normal')(conv3)
+    pool3 = MaxPooling2D(pool_size=(2, 2))(conv3)
+    conv4 = Convolution2D(512, 3, activation = 'relu', padding = 'same', kernel_initializer = 'he_normal')(pool3)
+    conv4 = Convolution2D(512, 3, activation = 'relu', padding = 'same', kernel_initializer = 'he_normal')(conv4)
+    drop4 = Dropout(0.5)(conv4)
+    pool4 = MaxPooling2D(pool_size=(2, 2))(drop4)
+
+    conv5 = Convolution2D(1024, 3, activation = 'relu', padding = 'same', kernel_initializer = 'he_normal')(pool4)
+    conv5 = Convolution2D(1024, 3, activation = 'relu', padding = 'same', kernel_initializer = 'he_normal')(conv5)
+    drop5 = Dropout(0.5)(conv5)
+
+    up6 = Convolution2D(512, 2, activation = 'relu', padding = 'same', kernel_initializer = 'he_normal')(UpSampling2D(size = (2,2))(drop5))
+    merge6 = Concatenate([drop4,up6])
[…]

### 2018-08-31 papers/cvpr2019/supplemental/skeleton-generation.tex
supplemental: updated information for skeletons

@@
 % !TEX root =  supplemental.tex
-\section{Skeletonization}
+\section{Skeleton Generation}
 
-There are three steps in our skeleton generation pipeline: downsampling, skeletonization, and upsampling. 
-Here we explore the advantages and disadvantages of each step both qualitatively by visualing inspecting results and quantitatively by publishing a novel ``Skeleton Benchmark''. 
-Lastly, we compare three widely used skeletonization algorithms against our benchmark to determine the relative efficiencies and accuracies on segmented neuronal data.
+Our algorithm uses skeletons to represent the volumetric shape of each label in a volume.
+Each skeleton is comprised of ``joints'' which represent voxels belonging to the skeleton.
+We call joints with only one neighbor ``endpoints''.
 
-\subsection{Skeleton Pipeline}
+We employ a multi-step pipeline to generate skeletons for each label in the volume.
+In the first step, we anisotropically downsample each label so that the output volume as an even resolution in all three dimensions.
+Next, we apply a preexisting skeletonization algorithm to reduce the label volume into skeletons that represent the 3D volumetric shape.
+Finally, we upsample the skeleton joints so that they fit inside the full-resolution volume.
+Particular care is taken in the final two steps to identify skeleton the joints that are endpoints.
 
-First, we downsample the original image to a resolution of $t_{res}\si{\nm^3}$ where $t_{res}$ is a tunable parameter. 
-We experiment with values of $t_{res}$ ranging from $30$ to $200$ and display the results in Sec.~\ref{skeleton-results}.
-In general, topologically preserving downsampling is impossible~\cite{kraus2001topology} as holes can collapse when the width of a gap is smaller than the downsampling ratio.
-This is particularly common on dendrites where multiple spines protrude closely.
+Each of the three steps has various parameters, algorithmic strategies, and associated running times. 
+We constructed a skeleton benchmark dataset to test the results of these parameters in terms of accuracy and speed.~\footnote{Our benchmark dataset is freely available at \texttt{omitted for review}.}
+In the following subsections we discuss the various strategies tried for each step and present the results in Sec.~\ref{sec:skeleton-results}.
+Based on this analysis we downsample the label volumes to \SI{100}{\cubic\nano\meter\per\voxel}.
+We use a topological thinning strategy based on preserving isthmuses~\cite{palagyi2014sequential}.
+Finally, we upsample the skeleton joints and enforce that neighbor joints in the downsampled image have a close connected path in the full-resolution volume.
 
-There are two major benefits to downsampling the data before running the skeletonization algorithm.
-First, the overall skeletonization running time greatly decreases as a function of downsample resolution.
-Two of our baseline skeleton algorithms have running times linear in the number of voxels in the input segmentation.
-The third uses Dijkstra's algorithm to find globally distance voxels to form branches of the skeleton ``tree''.
-Therefore, the computational complexity is $\mathcal{O}(n \log{n})$ since the number of edges in a structured voxel grid is $\mathcal{O}(n)$.
-Sec.~\ref{skeleton-results} further explores the running time of the skeleton algorithms as a function of downsample rate.
-Second, downsampling reduces the number of spurious endpoints.
-Our input segmentations often have noisy boundaries with small spikes protruding from the surface that do not represent larger dendritic spines.
-Downsampling the input segmentations has a smoothing effect that eliminates these small bumps while
+\subsection{Downsample Volumes}
 
-The second step is to run the skeletonization algorithm.
-We test three different algorithms.
+The first step in our skeleton generation downsamples the label volumes.
+Often the electron microscopy (EM) images are anisotropic with higher resolution in the $x$ and $y$ dimensions than the $z$. 
+Thus, we anisotropically downsample a segment so that the resultant segment is isotropic.
+At best a skeleton generation algorithm will have a linear runtime in the number of voxels in the segment since each voxel needs to be labeled as skeleton or not.
+Thus, running time decreases as a function of downsample rate.
+One major concern for downsampling is that information (and potentially structure) is lost.
+However, neuronal morphological details are preserved at resolutions as coarse as \SI{100}{\cubic\nano\meter\per\voxel}~\cite{rolnick2017morphological}.
+A second major concern with downsampling is one cannot guarantee the preservation of topology since holes can collapse if their width is smaller than the downsampling factor~\cite{kraus2001topology}.
+We further address this issue in Sec.~\ref{sec:skeleton-upsample}.
+
+When we downsample a binary label volume we use a max-pooling operation.
+Thus, if we downsample by a factor of $5 \times 5 \times 2$ and a single voxel in the cube $(5x, 5y, 2z) \to (5x + 5, 5y + 5, 2z + 2)$ has the label, then the downsampled voxel $(x, y, z)$ will receive that label.
+Therefore, the downsampled voxel $(x, y, z)$ can contain multiple labels.
+
+\subsection{Skeletonization}
+
+We test three different skeletonization algorithms.
 As a baseline we use the built in \texttt{scipy:skeletonize\_3d} function that implements the medial surface/axis thinning algorithm of Lee et al.~\cite{lee1994building}.
@@
 
-The last step of the algorithm ``upsamples'' the skeleton to the resolution of the original image.
-If we downsample in $x$, $y$, and $z$ by $down_x$, $down_y$, and $down_z$ respectively, we cannot merely take a skeleton joint at $(u, v, w)$ and identify $(down_x * u, down_y * v, down_z * w)$ as the upsampled joint since this point may not fall within the original label boundary.
-It is during this process that we also identify which skeleton joints are also endpoints.
+\subsection{Upsample Skeletons}
+\label{sec:skeleton-upsample}
 
@@
 
-We created a skeleton benchmark to evaluate the three different skeletonization approaches with varying downsampling parameters.
-We identify all of the endpoint locations
+\subsection{Results}
+\label{sec:skeleton-results}
 
-\subsection{Skeleton Results}
-\label{skeleton-results}
+Max-pool downsample
 
-\paragraph{Endpoint Accuracy.}
+Upsample technique (closest to center)
 
-\paragraph{Running Times.}
+Naive approach to upsample (with examples)
+
+A* approach for determining connectedness
+
+Discuss increase in running time
+
+Differences between topological thinning and TEASER (show issues  holes in segments)
+
+TEASER doesn't need non naive
+
+%\section{Skeletonization}
+
+%There are three steps in our skeleton generation pipeline: downsampling, skeletonization, and upsampling. 
+%Here we explore the advantages and disadvantages of each step both qualitatively by visualing inspecting results and quantitatively by publishing a novel ``Skeleton Benchmark''. 
+%Lastly, we compare three widely used skeletonization algorithms against our benchmark to determine the relative efficiencies and accuracies on segmented neuronal data.
+
+%\subsection{Skeleton Pipeline}
+
+%First, we downsample the original image to a resolution of $t_{res}\si{\nm^3}$ where $t_{res}$ is a tunable parameter. 
+%We experiment with values of $t_{res}$ ranging from $30$ to $200$ and display the results in Sec.~\ref{skeleton-results}.
+%In general, topologically preserving downsampling is impossible as holes can collapse when the width of a gap is smaller than the downsampling ratio.
+%This is particularly common on dendrites where multiple spines protrude closely.
+
+%There are two major benefits to downsampling the data before running the skeletonization algorithm.
+%First, the overall skeletonization running time greatly decreases as a function of downsample resolution.
+%Two of our baseline skeleton algorithms have running times linear in the number of voxels in the input segmentation.
+%The third uses Dijkstra's algorithm to find globally distance voxels to form branches of the skeleton ``tree''.
+%Therefore, the computational complexity is $\mathcal{O}(n \log{n})$ since the number of edges in a structured voxel grid is $\mathcal{O}(n)$.
+%Sec.~\ref{skeleton-results} further explores the running time of the skeleton algorithms as a function of downsample rate.
+%Second, downsampling reduces the number of spurious endpoints.
+%Our input segmentations often have noisy boundaries with small spikes protruding from the surface that do not represent larger dendritic spines.
+%Downsampling the input segmentations has a smoothing effect that eliminates these small bumps while
+
+%The last step of the algorithm ``upsamples'' the skeleton to the resolution of the original image.
+%If we downsample in $x$, $y$, and $z$ by $down_x$, $down_y$, and $down_z$ respectively, we cannot merely take a skeleton joint at $(u, v, w)$ and identify $(down_x * u, down_y * v, down_z * w)$ as the upsampled joint since this point may not fall within the original label boundary.
+%It is during this process that we also identify which skeleton joints are also endpoints.
+
+%\subsection{Skeleton Benchmark}
+
+%We created a skeleton benchmark to evaluate the three different skeletonization approaches with varying downsampling parameters.
+%We identify all of the endpoint locations
+
+%\subsection{Skeleton Results}
+%\label{skeleton-results}
+
+%\paragraph{Endpoint Accuracy.}
+
+%\paragraph{Running Times.}

### 2018-10-02 papers/eccv2018/rebuttal/paper.tex
eccv: added final rebuttal

@@
 \usepackage{amsmath,amssymb} % define this before the line numbering.
-%\usepackage{ruler}
+\usepackage{ruler}
 \usepackage{color}
@@
 %\authorrunning{B. Matejek et al.}
-\title{Biologically-Constrained Region Merging for Connectome Reconstruction}
-
+\title{Rebuttal: Biologically-Constrained Region Merging for Connectome Reconstruction }
+\def\ECCV18SubNumber{534}  % Insert your submission number here
+\titlerunning{ECCV-18 submission ID \ECCV18SubNumber}
+\authorrunning{ECCV-18 submission ID \ECCV18SubNumber}
+\author{Anonymous ECCV submission}
+\institute{Paper ID \ECCV18SubNumber}
 %\author{Brian Matejek, Daniel Haehn, Donglai Wei, Toufiq Parag, Hanspeter Pfister}
@@
 \maketitle
+% \textcolor{red}{Toufiq's comment on skeletons, feel free to polish, correct,fill in.}
+% Skeletonization is a fundamental step in our algorithm that makes it practical and differentiates out effirt from all others in the community.
 
-Hello World
+\noindent
+We would like to thank the reviewers for their valuable feedback.
+
+\noindent
+\textbf{[R1]} There is a benefit to our method to improving the understanding of the biology.
+One of the main goals of connectomics is to extract the wiring diagram from a brain.
+This requires identifying individual neurons and the synapses between them.
+These pre-synaptic connections occur on dendritic spines and therefore it is essential to correctly segment the spiny components from the main neuron.
+Figure [ADD] in Section [ADD] shows how we improve the segmentation of one of these dendrites.
+
+\noindent
+\textbf{[R2]} The skeleton-based graph generation approach greatly reduces the number of edges in our graph. 
+It also enables us to detect neuronal processes that have non-adjacent labels. 
+This can occur if there is a deformation or image artifact in the corresponding image region.
+We discuss this in Section 5.1 under Graph Generation and show examples in Figure 7, bottom.
+Additionally, since there are is a computational dependence for each subsequent step in the pipeline, it is important to prune the graph of edges between correctly segment processes.
+We discuss the effectiveness of this strategy in Table 1 of the submission.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.45\linewidth]{./figures/CNN-Input.pdf}
+\caption{An example input to our 3D CNN with the three different channels (left).
+We do not use the skeletons as input into our CNN because of some artifacts from the skeletonization algorithm (right).}
+\label{fig:cnn-input}
+\end{figure}
+
+\noindent
+\textbf{[R1, R2]} Figure~\ref{fig:cnn-input}, left, shows a typical input example given to our CNN. 
+We extract a cubic region of interest (ROI) with 1200 nanometer sides.
+The center of the ROI is determined by the skeletons of the corresponding segments.
+We upsample and downsample the ROI as needed to fit the CNN input size of $84\times84\times26$ voxels.
+We have three input channels to our network, shown below the input example.  
+Channel 1 is 0.5 if the corresponding voxel belongs to label 1, channel 2 is 0.5 if the corresponding voxel belongs to label 2, and channel 3 is 0.5 if the voxel belongs to either label 1 or label 2.
+Voxels that do not match the label requirements for a given channel are set to -0.5.
+
+We randomize which label is designated as ``1'' or ``2''. 
+The purpose of the first two channels is to learn typical local shapes for each segment while the third channel learns the local shape for a correctly segmented neuronal processes.
+
+\noindent
+\textbf{[R2]}
+Benefits to using heuristic over integer program
+
+\noindent
+\textbf{[R2]}
+We find long range affinities by running Dijkstra's algorithm on the graph we extract from the skeletons (Sections 3.1 and 3.2). 
+We will clarify this in our revision.
+
+\noindent
+\textbf{[R2, R3]}
+Compare linear program to greedy-edge
+Talk about the heuristic for constraint
+
+\noindent
+\textbf{[R1, R2]}
+CREMI/SNEMI
 
